### 2018-03-01 paper/sample2e.tex
initial paper + running on mnist with nmse

\documentclass[letterpaper]{article}
\usepackage{proceed2e}
\usepackage[margin=1in]{geometry}
\usepackage{mathtools}
\usepackage{amsfonts}

\usepackage{times}

\newtheorem{theorem}{Theorem}

\title{Bayesian LISTA / Uncertainty propagation in deep neural networks for sparse coding}

\author{} % LEAVE BLANK FOR ORIGINAL SUBMISSION.
          % UAI  reviewing is double-blind.

% The author names and affiliations should appear only in the accepted paper.
%
%\author{ {\bf Harry Q.~Bovik\thanks{Footnote for author to give an
%alternate address.}} \\
%Computer Science Dept. \\
%Cranberry University\\
%Pittsburgh, PA 15213 \\
%\And
%{\bf Coauthor}  \\
%Affiliation          \\
%Address \\
%\And
%{\bf Coauthor}   \\
%Affiliation \\
%Address    \\
%(if needed)\\
%}

\begin{document}

\maketitle

\begin{abstract}
We propose the method of propagating the uncertainty through the multilevel soft-thresholding nonlinearity. This allows to use it as a building block for sparse coding deep neural networks. As an example we develop the Bayesian LISTA algorithm. It allows to obtain the variance estimates for parameters and posterior distributions.
\end{abstract}

\section{Uncertainty propagation through LISTA-like neural network with separated layers}

NN scheme:

\begin{align}
&b = W_0y\\
&\widehat{\beta}_0 = h_\lambda(b) \\
&\text{for } l=1:L\\
	&\quad b_l = W_l y \\
	&\quad c_l = b_l + S_l\widehat{\beta}_{l-1} \\
	&\quad \widehat{\beta}_{l} = h_\lambda(c_l) \\
& \widehat{\beta} = \widehat{\beta}_{L}
\end{align}

 \begin{theorem}
 Let $W \in \mathbb{R}^{D \times K}$ be a matrix of Gaussian-distributed random variables: $W_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $y \in \mathbb{R}^K$ be a constant vector. Their multiplication is a vector $b \in \mathbb{R}^{D}$ of random variables $b_d \sim \mathcal{N}(\sum_{k=1}^Ky_km^w_{dk}, \sum_{k=1}^Ky_k^2v^w_{dk})$.
 \end{theorem}

\end{document}

### 2018-03-01 theano/PBP_net_lista/BayesianListaHandler.py

@@ -10,16 +10,25 @@ class BayesianListaHandler(ListaHandler):
         mean_y_train = np.zeros(K)
         std_y_train = np.identity(K)
 
-        self.pbp_instance = pbp.PBP_lista(L, D, K, mean_y_train, std_y_train)
+        self.pbp_instance = pbp.PBP_lista(L, D, K, X, mean_y_train, std_y_train)
 
     def train_iteration(self, beta_train, y_train):
         self.pbp_instance.do_pbp(beta_train, y_train, n_iterations=1)
         self.pbp_instance.sample_ws()
         return self.test(beta_train, y_train)
 
+    def train_iteration_nmse(self, beta_train, y_train):
+        self.pbp_instance.do_pbp(beta_train, y_train, n_iterations=1)
+        self.pbp_instance.sample_ws()
+        return self.test_nmse(beta_train, y_train)
+
     def test(self, beta_test, y_test):
         beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
         return self.mse(beta_test, beta_estimator)
+
+    def test_nmse(self, beta_test, y_test):
+        beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
+        return self.nmse(beta_test, beta_estimator)
 
     def predict(self, y_test):
         beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
@@ -27,3 +36,7 @@ class BayesianListaHandler(ListaHandler):
 
     def mse(self, beta_true, beta_estimator):
         return np.mean(np.sqrt(np.sum((beta_estimator - beta_true)**2, axis=1)))
+
+    def nmse(self, beta_true, beta_estimator):
+        return np.mean(np.sqrt(np.sum((beta_estimator - beta_true)**2, axis=1)) / np.sqrt(np.sum(beta_true**2, axis=1)))
+

### 2018-03-01 theano/PBP_net_lista/pbp.py

@@ -7,13 +7,14 @@ import numpy as np
 import theano
 
 import theano.tensor as T
+from tqdm import tqdm
 
 from PBP_net_lista import prior, network
 
 
 class PBP_lista:
 
-    def __init__(self, L, D, K, mean_y_train, std_y_train):
+    def __init__(self, L, D, K, X_design_matrix, mean_y_train, std_y_train):
 
         self.D = D
         self.K = K
@@ -31,6 +32,16 @@ class PBP_lista:
         params = self.prior.get_initial_params()
 
         thr_lambda = 0.1
+
+        params['W_M'] = []
+        params['S_M'] = []
+
+        W_init = X_design_matrix.T / (1.01 * np.linalg.norm(X_design_matrix, 2) ** 2)
+        S_init = np.identity(D) - np.matmul(W_init, X_design_matrix)
+
+        for i in range(L):
+            params['W_M'].append(W_init)
+            params['S_M'].append(S_init)
 
         self.network = network.Network(params['W_M'], params['W_V'], params['S_M'], params['S_V'], thr_lambda,
                                        params['a'], params['b'], D, K)

### 2018-03-01 theano/PBP_net_lista_single_matrices/SingleBayesianListaHandler.py

@@ -10,16 +10,26 @@ class SingleBayesianListaHandler(ListaHandler):
         mean_y_train = np.zeros(K)
         std_y_train = np.identity(K)
 
-        self.pbp_instance = pbp.PBP_lista(L, D, K, mean_y_train, std_y_train)
+        self.pbp_instance = pbp.PBP_lista(L, D, K, X, mean_y_train, std_y_train)
 
     def train_iteration(self, beta_train, y_train):
         self.pbp_instance.do_pbp(beta_train, y_train, n_iterations=1)
         self.pbp_instance.sample_ws()
         return self.test(beta_train, y_train)
 
+    def train_iteration_nmse(self, beta_train, y_train):
+        self.pbp_instance.do_pbp(beta_train, y_train, n_iterations=1)
+        self.pbp_instance.sample_ws()
+        return self.test_nmse(beta_train, y_train)
+
+
     def test(self, beta_test, y_test):
         beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
         return self.mse(beta_test, beta_estimator)
+
+    def test_nmse(self, beta_test, y_test):
+        beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
+        return self.nmse(beta_test, beta_estimator)
 
     def predict(self, y_test):
         beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
@@ -27,3 +37,6 @@ class SingleBayesianListaHandler(ListaHandler):
 
     def mse(self, beta_true, beta_estimator):
         return np.mean(np.sqrt(np.sum((beta_estimator - beta_true)**2, axis=1)))
+
+    def nmse(self, beta_true, beta_estimator):
+        return np.mean(np.sqrt(np.sum((beta_estimator - beta_true)**2, axis=1)) / np.sqrt(np.sum(beta_true**2, axis=1)))

### 2018-03-01 theano/PBP_net_lista_single_matrices/pbp.py

@@ -13,7 +13,7 @@ from PBP_net_lista_single_matrices import prior, network
 
 class PBP_lista:
 
-    def __init__(self, L, D, K, mean_y_train, std_y_train):
+    def __init__(self, L, D, K, X_design_matrix, mean_y_train, std_y_train):
 
         self.D = D
         self.K = K
@@ -31,6 +31,9 @@ class PBP_lista:
         params = self.prior.get_initial_params()
 
         thr_lambda = 0.1
+
+        params['W_M'] = X_design_matrix.T / (1.01 * np.linalg.norm(X_design_matrix, 2) ** 2)
+        params['S_M'] = np.identity(D) - np.matmul(params['W_M'], X_design_matrix)
 
         self.network = network.Network(params['W_M'], params['W_V'], params['S_M'], params['S_V'], thr_lambda,
                                        params['a'], params['b'], D, K, L)

### 2018-03-01 theano/compare_mnist/compare_mnist_XFHJSDIFGHKL.py

@@ -1,6 +1,7 @@
 import numpy as np
 import theano
 import six.moves.cPickle as pickle
+from tqdm import tqdm
 
 from PBP_net_lista.BayesianListaHandler import BayesianListaHandler
 from PBP_net_lista.DataGenerator import DataGenerator
@@ -37,19 +38,33 @@ class MnistSequentialComparator(object):
 
     def train_iteration(self):
 
+        # self.freq_train_loss.append(
+        #     self.freq_lista.train_iteration(beta_train=self.data.train_data, y_train=self.data.y_train))
+        # self.bayesian_train_loss.append(
+        #     self.bayesian_lista.train_iteration(beta_train=self.data.train_data, y_train=self.data.y_train))
+        # self.shared_bayesian_train_loss.append(
+        #     self.shared_bayesian_lista.train_iteration(beta_train=self.data.train_data, y_train=self.data.y_train))
+
         self.freq_train_loss.append(
-            self.freq_lista.train_iteration(beta_train=self.data.train_data, y_train=self.data.y_train))
+            self.freq_lista.train_iteration_nmse(beta_train=self.data.train_data, y_train=self.data.y_train))
         self.bayesian_train_loss.append(
-            self.bayesian_lista.train_iteration(beta_train=self.data.train_data, y_train=self.data.y_train))
+            self.bayesian_lista.train_iteration_nmse(beta_train=self.data.train_data, y_train=self.data.y_train))
         self.shared_bayesian_train_loss.append(
-            self.shared_bayesian_lista.train_iteration(beta_train=self.data.train_data, y_train=self.data.y_train))
+            self.shared_bayesian_lista.train_iteration_nmse(beta_train=self.data.train_data, y_train=self.data.y_train))
+
+        # self.freq_validation_loss.append(
+        #     self.freq_lista.test(beta_test=self.data.validation_data, y_test=self.data.y_validation))
+        # self.bayesian_validation_loss.append(
+        #     self.bayesian_lista.test(beta_test=self.data.validation_data, y_test=self.data.y_validation))
+        # self.shared_bayesian_validation_loss.append(
+        #     self.shared_bayesian_lista.test(beta_test=self.data.validation_data, y_test=self.data.y_validation))
 
         self.freq_validation_loss.append(
-            self.freq_lista.test(beta_test=self.data.validation_data, y_test=self.data.y_validation))
[…]

### 2018-03-01 theano/compare_mnist/mnist_data.py

@@ -21,9 +21,12 @@ class MnistData(object):
         self.y_train = None
         self.y_validation = None
 
+        self.training_size = 5000
+
     def check_download(self):
         mnist = tf.contrib.learn.datasets.load_dataset("mnist")
-        self.train_data = mnist.train.images
+        random_train_ind = np.random.choice(mnist.train.images.shape[0], self.training_size, replace=False)
+        self.train_data = mnist.train.images[random_train_ind]
         self.train_labels = np.asarray(mnist.train.labels, dtype=np.int32)
         self.dictionary_learn_data = mnist.test.images
         self.dictionary_learn_labels = np.asarray(mnist.test.labels, dtype=np.int32)

### 2018-03-01 theano/freqLISTA/FrequentistListaHandler.py

@@ -1,9 +1,10 @@
 import theano.tensor as T
 import theano
+from tqdm import tqdm
 
 from compare_freq_bayes.ListaHandler import ListaHandler
 from freqLISTA.lista import Lista
-
+import numpy as np
 
 class FrequentistListaHandler(ListaHandler):
     def __init__(self, D, K, L, X, learning_rate):
@@ -14,6 +15,8 @@ class FrequentistListaHandler(ListaHandler):
         lista = Lista(L, D, K, y, X)
 
         cost = lista.mean_squared_error(beta)
+
+        cost_nmse = lista.normalised_mean_squared_error(beta)
 
         g_S = T.grad(cost=cost, wrt=lista.S)
         g_W = T.grad(cost=cost, wrt=lista.W)
@@ -37,13 +40,45 @@ class FrequentistListaHandler(ListaHandler):
             outputs=lista.beta_estimator
         )
 
+        self.compute_nmse = theano.function(
+            inputs=[y, beta],
+            outputs=cost_nmse
+        )
+
     def train_iteration(self, beta_train, y_train):
+
+        permutation = np.random.choice(range(beta_train.shape[0]), beta_train.shape[0],
+                                       replace=False)
+
+        for i in permutation:
+            self.train_model(np.expand_dims(y_train[i], axis=0), np.expand_dims(beta_train[i], axis=0))
+
+        mse = self.test_model(y=y_train, beta=beta_train)
+        return mse
+
+    def train_iteration_nmse(self, beta_train, y_train):
+
+        permutation = np.random.choice(range(beta_train.shape[0]), beta_train.shape[0],
+                                       replace=False)
+
+        for i in permutation:
+            self.train_model(np.expand_dims(y_train[i], axis=0), np.expand_dims(beta_train[i], axis=0))
+
+        nmse = self.compute_nmse(y=y_train, beta=beta_train)
+        return nmse
+
+
+    def train_iteration_batch(self, beta_train, y_train):
         mse = self.train_model(y_train, beta_train)
         return mse
 
     def test(self, beta_test, y_test):
         mse = self.test_model(y=y_test, beta=beta_test)
         return mse
+
+    def test_nmse(self, beta_test, y_test):
+        nmse = self.compute_nmse(y=y_test, beta=beta_test)
+        return nmse
 
     def predict(self, y_test):
         beta_estimator = self.predict_model(y=y_test)

### 2018-03-01 theano/freqLISTA/lista.py

@@ -26,6 +26,9 @@ class Lista(object):
     def mean_squared_error(self, beta):
         return T.mean(T.sqrt(T.sum(T.sqr(self.beta_estimator - beta), axis=1)))
 
+    def normalised_mean_squared_error(self, beta):
+        return T.mean(T.sqrt(T.sum(T.sqr(self.beta_estimator - beta), axis=1)) / T.sqrt(T.sum(T.sqr(beta), axis=1)))
+
     def net(self, y):
         b = T.dot(y, self.W.T)
         beta_estimator_history = [theano_soft_threshold(b, self.thr_lambda)]

### 2018-03-03 paper/BayesianLISTA.tex
added the paper

\documentclass[letterpaper]{article}
\usepackage{proceed2e}
\usepackage[margin=1in]{geometry}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{subfig}
\usepackage{hyperref}

\usepackage{times}
\usepackage{float}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\title{Bayesian LISTA / Uncertainty propagation in deep neural networks for sparse coding}

\author{} % LEAVE BLANK FOR ORIGINAL SUBMISSION.
          % UAI  reviewing is double-blind.

% The author names and affiliations should appear only in the accepted paper.
%
%\author{ {\bf Harry Q.~Bovik\thanks{Footnote for author to give an
%alternate address.}} \\
%Computer Science Dept. \\
%Cranberry University\\
%Pittsburgh, PA 15213 \\
%\And
%{\bf Coauthor}  \\
%Affiliation          \\
%Address \\
%\And
%{\bf Coauthor}   \\
%Affiliation \\
%Address    \\
%(if needed)\\
%}

\author{ {\bf Danil Kuzin} \\
\And
{\bf Olga Isupova}  \\
\And
{\bf Lyudmila Mihaylova}   \\
}

\begin{document}

\maketitle

\begin{abstract}
We propose the method of propagating the uncertainty through the multilevel soft-thresholding nonlinearity. This allows to use it as a building block for sparse coding deep neural networks. As an example we develop the Bayesian LISTA algorithm with probabilistic backpropagation. It allows to obtain the variance estimates for parameters and posterior distributions.
\end{abstract}

\section{Introduction}
Though the idea of Bayesian learning in neural networks is not new \cite{neal2012bayesian}, it has gained its attention only recently, with the development of distributed approximate inference techniques \cite{li2015stochastic, hoffman2013stochastic}  and general boost in popularity of deep learning. In some spheres, such as self-driving cars or healthcare, posterior estimates are very important and Bayesian learning allows to obtain them.

In general, when distributions are included in the network, Bayesian inference complexity scales exponentially with the number of layers, thus making it impossible to be implemented for deep neural networks in general. Nevertheless, recently several techniques were proposed to handle specific types of neural networks. For example, dense layers \cite{hernandez2015probabilistic}, networks with discrete distributions \cite{soudry2014expectation}, recurrent networks \cite{mcdermott2017bayesian}.

There are currently two approaches for Bayesian neural networks: including distributions of weights in the network \cite{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing the uncertainty \cite{gal2016dropout}. We are using the first way.

In this paper we propose the approach to propagate uncertainty through the soft-thresholding nonlinearity. At every layer the current distribution of the target vector is represented as spike-and-slab distribution, this can be effectively combined with Gaussian weights for dense layers and after soft-thresholding it can be closely approximated with distribution from the same family.

The paper is organised as following: first, we describe the uncertainty propagation to obtain the spike-and-slab distribution - output from the network, then we describe how the backpropagation is organised to update distributions of weights and their priors. After that we show how the algorithm is performed on MNIST data and demonstrate the obtained posterior estimates.

Soft thresholding usually appears in LISTA network \cite{gregor2010learning}, so we present our algorithm for it.

The main contributions are: 
\begin{itemize}
\item for the first time we propose uncertainty propagation through the soft-thresholding nonlinearity for Bayesian neural network
\item efficient posterior inference for weights and outputs of neural networks with the soft-thresholding nonlinearity
\item novel Bayesian LISTA network for sparse coding
\end{itemize}

\section{LISTA}

LISTA neural network was proposed for sparse coding to mimic the iterative thresholding algorithms. The current estimate is iteratively combined with the design matrix and then thresholded. Soft thresholding operator for input $v$ with parameter $\lambda$ is defined as
\begin{equation}
h_\lambda(v) = \text{sgn}(v) * \max(|v| - \lambda, 0)
\end{equation} 
When this process is limited to the predefined set of iterations and weights of design matrix combinations are learnt, this can be interpreted as a neural network.

The problem is an underdefined linear regression with assumption of sparse weights:
\begin{equation}
\mathbf{y} = \mathbf{X}\boldsymbol\beta + \varepsilon
\end{equation}
where $\mathbf{y}$ are observations, $\mathbf{X}$ is design matrix, $\boldsymbol\beta$ is unknown vector of weights larger than $\mathbf{y}$ with some of the elements equal to zero to achieve regularisation. $\varepsilon$ is Gaussian noise.

LISTA network has the following scheme
\begin{align}
&\mathbf{b}_0 = \mathbf{W}_0\mathbf{y}\\
&\widehat{\boldsymbol\beta}_0 = h_\lambda(\mathbf{b}_0) \\
&\text{for } l=1:L\\
	&\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y} \\
	&\quad \mathbf{c}_l = \mathbf{b}_l + \mathbf{S}_l\widehat{\boldsymbol\beta}_{l-1} \\
	&\quad \widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l) \\
& \widehat{\boldsymbol\beta} = \widehat{\boldsymbol\beta}_{L}
\end{align}

Matrices $\mathbf{W}_l \in \mathbb{R}^{D \times K}$, $\mathbf{S}_l\in\mathbb{R}^{D \times D}$ are the parameters that are learnt in LISTA. Vectors $\mathbf{c}_l$, $\mathbf{b}_l$ are intermediate vectors that describe propagation within the layer. $\boldsymbol\beta_l$ is the current approximation of the target coefficients vector.

\section{Bayesian LISTA}
To formulate the Bayesian LISTA we start with putting the prior distributions on the unknown weights
\begin{align}
&p(\mathbf{W}) = \prod_{l=1}^L\prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij, l} | 0, \eta^{-1}), \\
&p(\mathbf{S}) = \prod_{l=1}^L\prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd'', l} | 0, \eta^{-1}),
\end{align}
where $w_{ij, l}$ is the component of the matrix $\mathbf{W}_l$, $s_{d'd'', l}$ is the component of the matrix $\mathbf{S}_l$ from the layer $l$.
Likelihood of the output $\mathbf{y}$ is defined as 
\begin{equation}
\label{eq:likelihood}
p(\mathbf{y}; \mathbf{W}, \mathbf{S}, \gamma) = \prod_{d=1}^D\mathcal{N}([\mathbf{y}]_d; [f(\mathbf{y}; \mathbf{W}, \mathbf{S})]_d, \gamma^{-1}),
\end{equation}
where $f(\mathbf{y}; \mathbf{W}, \mathbf{S})$ is the output of the LISTA neural network.
The posterior distribution is 
\begin{equation}
\label{eq:posterior}
p(\mathbf{W}, \mathbf{S}, \gamma, \eta | D) = \frac{p(\mathbf{y} | \mathbf{W},  \mathbf{S}, \gamma) p(\mathbf{W} | \eta )p(\mathbf{S} | \eta) p(\eta) p(\gamma)}{p(\mathbf{y})}
\end{equation}

\section{Uncertainty propagation through soft thresholding}
We initialise the $\widehat{\boldsymbol\beta}_{0}$ with the spike and slab distribution with parameters $\boldsymbol\omega = \mathbf{0}$, $\mathbf{m} = \mathbf{0}$, $\mathbf{v} = \mathbf{1}$. For every layer we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters $\boldsymbol\omega$, $\mathbf{m}$, $\mathbf{v}$
\begin{equation}
[\boldsymbol\beta_{l-1}]_d \sim [\boldsymbol\omega]_d \delta_0 + (1 - [\boldsymbol\omega]_d)\mathcal{N}([\mathbf{m}]_d, [\mathbf{v}]_d)
\end{equation}

Further in this section we show that the value of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with spike and slab distribution and therefore it maintains the same family of distributions and allows to apply the extended probabilistic backpropagation algorithm that is proposed in Section~\ref{sec:backpropagation}: lemma \ref{thm:matrix_const} describes the probabilistic variant of LISTA step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of LISTA step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$. Overall the probabilistic layer is described by theorem \ref{thm:prob_layer}.

\begin{lemma}[Moments of spike and slab]
\label{thm:moments_spsl}
Let the random variable $\xi$ have a spike and slab distribution with probability of spike $\omega$, slab mean $m$ and slab variance $v$. Then its moments are
\begin{align}
\mathbb{E}\xi &= (1-\omega)m \\
%\mathbb{E}\xi^2 &= (1-\omega)(v + m^2) \\
\text{Var }\xi & = (1-\omega)(v + \omega m^2)
\end{align}

\end{lemma}
\begin{proof}
\begin{align}
\mathbb{E}\xi &= \int x (\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v))dx \\
& = \omega \int x \delta_0(x)dx + (1 - \omega)\int x \mathcal{N}(x; m, v)dx \\
& = (1-\omega)m
\end{align}
\begin{align}
\mathbb{E}\xi^2 &= \int x^2 (\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v))dx \\
& = \omega \int x^2 \delta_0(x)dx + (1 - \omega)\int x^2 \mathcal{N}(x; m, v)dx \\
& = (1-\omega)(v + m^2)
\end{align}
\begin{align}
\text{Var }\xi &= \mathbb{E}\xi^2 - \left(\mathbb{E}\xi\right)^2\\
& = (1-\omega)(v + \omega m^2)
\end{align}
\end{proof}

 \begin{lemma}
 \label{thm:matrix_const}
 Let $\mathbf{W} \in \mathbb{R}^{D \times K}$ be a matrix of independent Gaussian-distributed random variables: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y} \in \mathbb{R}^K$ be a constant vector. Then their product $\mathbf{W} \mathbf{y}$ is a vector $\mathbf{b} \in \mathbb{R}^{D}$ of random variables $b_d \sim \mathcal{N}(m^b_d, w^b_d)$, where $m^b_d = \sum_{k=1}^Ky_k m^w_{dk}$, $w^b_d = \sum_{k=1}^Ky_k^2v^w_{dk}$. 
 %If we denote $M^W = [m^w_{dk}]_{d=1:D, k=1:K}$, $V^W = [v^w_{dk}]_{d=1:D, k=1:K}$, then $\mathbf{b}^m = W^My$, $\mathbf{b}^w = W^Vy^2$.
 \end{lemma}
 \begin{proof}
 	The statement follows from the property that the family of normal distributions is closed under linear transformations.
 \end{proof}

  \begin{lemma}
  \label{thm:matrix_vector}
 Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\boldsymbol\beta \in \mathbb{R}^D$ be a vector with spike-and-slab distributed variables: $\beta_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$. Then their product can be approximated as a vector $\mathbf{d} \in \mathbb{R}^{D}$ of random variables $d_d \sim \mathcal{N}(d^d_m, d^d_w)$, where $m^d_d = \sum_{d'=1}^D m^s_{dd'}(1-\omega_{d'})m_{d'}$, $v^d_d = \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} + (1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}]$.
 \end{lemma}
 \begin{proof}
 	We compute the mean and variance of the product $\mathbf{S}\boldsymbol\beta$ and approximate resulting distribution as Gaussian.
\begin{align}
	&\mathbb{E}d_d = \mathbb{E} \left[\sum_{d'=1}^D s_{dd'}\beta_{d'}\right] =  \sum_{d'=1}^D \mathbb{E}[s_{dd'}\beta_{d'}] \\
	&= \sum_{d'=1}^D \mathbb{E}s_{dd'}\mathbb{E}\beta_{d'} = \sum_{d'=1}^D m^s_{dd'}\mathbb{E}\beta_{d'}
\end{align}
\begin{align}
	&\text{Var}d_d = \text{Var} \left[\sum_{d'=1}^D s_{dd'}\beta_{d'}\right] =  \sum_{d'=1}^D \text{Var}[s_{dd'}\beta_{d'}] = \\
	&\sum_{d'=1}^D [(\mathbb{E}s_{dd'})^2 \text{Var}\beta_{d'} + (\mathbb{E}\beta_{d'})^2 \text{Var}s_{dd'} + \text{Var}\beta_{d'} \text{Var}s_{dd'}]
\end{align}
where $\mathbb{E}\beta_{d'}$, $\text{Var}\beta_{d'}$ are computed according to lemma~\ref{thm:moments_spsl}.
 \end{proof}

\begin{lemma}
\label{thm:sum_vectors}
If $\mathbf{b} \in \mathbb{R}^{D}$ and $\mathbf{d} \in \mathbb{R}^{D}$ are both vectors of independent Gaussian-distributed random variables: $b_{d} \sim \mathcal{N}(m^b_{d}, v^b_{d})$, $d_{d} \sim \mathcal{N}(m^d_{d}, v^d_{d})$ then their sum $\mathbf{c} = \mathbf{b} + \mathbf{d}$ is a vector of independent Gaussian-distributed random variables $c_{d} \sim \mathcal{N}(m^c_{d}, v^c_{d})$ with $m^c_{d} = m^b_{d} + m^d_{d}$, $v^c_{d} = v^b_{d} + v^d_{d}$
\end{lemma}
\begin{proof}
Based on properties of Gaussian distributions.
\end{proof}

\begin{lemma}
\label{thm:soft_thresholding}
When a Gaussian-distributed random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft-thresholding function it can be approximated with the spike and slab distribution on $x^*$ with the probability of spike $\omega^*$, slab mean $m^*$ and slab variance $v^*$ (Formulae are given in the proof).
\end{lemma}
\begin{proof}
Soft-thresholding operator is defined as $h_\lambda(v) = \text{sign}(v) * \max(|v| - \lambda, 0)$. We need to compute the parameters of approximating distribution.
\begin{enumerate}
\item The probability of spike $\omega^*$ equals to the probability mass that lies in $(-\lambda, \lambda)$ of the original distribution and is flattened into zero by soft-thresholding operator. As the original distribution is Gaussian, this can be computed as $\omega^* = p(x^*=0) = p(x \in (-\lambda, \lambda)) = \Phi(\frac{\lambda-m}{\sqrt{v}}) - \Phi(\frac{-\lambda-m}{\sqrt{v}})$. 
\item Soft-thresholding shifts elements that are greater than $\lambda$  or less than $-\lambda$ elements towards 0. Let $\psi(\cdot)$ denote the density of the soft-threshold distribution, $\phi(\cdot)$ denote the density of the original Gaussian distribution. Then the first moment of the resulting distribution is $m^* = \int_{-\infty}^{+\infty}x\psi(x)dx = \int_{-\infty}^{0}x\phi(x-\lambda)dx + \int_{0}^{+\infty}x\phi(x+\lambda)dx$. Integrals are computed below.
\begin{align}
&\int_{-\infty}^{0}x\phi(x-\lambda)dx = \\
&-\frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} \\
& + (\lambda+m)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
\end{align}
\begin{align}
&\int_{0}^{+\infty}x\phi(x+\lambda)dx = \\
& = \frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\\
& + (m - \lambda)\left(1 - \Phi\left(-\frac{\lambda-m}{\sqrt{v}}\right)\right)
\end{align}
\item The second moment of the approximating distribution is computed as $s = \int_{-\infty}^{+\infty}x^2\psi(x)dx = \int_{-\infty}^{0}x^2\phi(x-\lambda)dx + \int_{0}^{+\infty}x^2\phi(x+\lambda)dx$.
\begin{align}
&\int_{-\infty}^{0}x^2\phi(x-\lambda)dx = \\
&-\frac{\sqrt{v}}{\sqrt{2\pi}} (\lambda+m)\exp\left\{\frac{-(\lambda+m)^2}{2v}\right\}\\
& + (\sigma^2 + (\lambda+m)^2)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
\end{align}
\begin{align}
&\int_{0}^{+\infty}x^2\phi(x+\lambda)dx = \\
&\frac{\sqrt{v}}{\sqrt{2\pi}} (m - \lambda)\exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\\
& + (\sigma^2 + (m - \lambda)^2)\left(1 - \Phi\left(\frac{\lambda -m}{\sqrt{v}}\right)\right)
\end{align}
Resulting variance is
\begin{equation}
v^* = s- (m^*)^2
\end{equation}
\end{enumerate}
\end{proof}

The proposed operations on Gaussian and spike-and-slab distributions allow to formulate the main result in this section that describes how the uncertainty propagation works.
\begin{theorem}[Bayesian LISTA forward propagation]
\label{thm:prob_layer}
The spike and slab distribution for $\boldsymbol\beta_{l-1}$ with parameters ($\boldsymbol\omega$, $\mathbf{m}$, $\mathbf{w}$) can be propagated through the LISTA layer and the parameters after propagation can be computed as following:
\begin{enumerate}
	\item $\mathbf{b} = Wy$ is computed according to lemma \ref{thm:matrix_const}
	\item $\mathbf{d} = S\boldsymbol\beta_{l-1}$ is computed according to lemma \ref{thm:matrix_vector}
	\item $\mathbf{c} = \mathbf{b} + \mathbf{d}$ is computed according to lemma \ref{thm:sum_vectors}
	\item $\boldsymbol\beta_{l} = h_\lambda(\mathbf{c})$ is computed according to lemma \ref{thm:soft_thresholding}
\end{enumerate}
\end{theorem}

\subsection{Approximation quality}
We have used two approximations in forward propagation of the uncertainty. First, in lemma \ref{thm:matrix_vector} a Gaussian matrix is multiplied by a spike-and-slab vector and their product is approximated with the Gaussian distribution. Second, in lemma \ref{thm:soft_thresholding} the result of soft-thresholding of a Gaussian vector is approximated with the spike-and-slab distribution. In this section we demonstrate that these approximations are close to the real distributions.

Figure \ref{fig:d_testing} demonstrates the comparison of the sampled distribution and approximated distribution for lemma \ref{thm:matrix_vector}. For sampled distribution, 10000 values were sampled from the Gaussian matrix and the Gaussian vector and their product was computed, then one of the dimensionalities was plotted. The approximated distribution was computed according to lemma \ref{thm:matrix_vector}.

Figure \ref{fig:z_new_testing} demonstrates the comparison of the sampled distribution and approximated distribution for lemma \ref{thm:soft_thresholding}. For sampled distribution, 10000 values were sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities was plotted. The approximated distribution was computed according to lemma \ref{thm:soft_thresholding}.
\begin{figure}[t]
\includegraphics[width=\columnwidth]{d_testing}
\caption{Approximation of product of Gaussians.}
\label{fig:d_testing}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{z_new_testing}
\caption{Approximation of propagation through soft thresholding}
\label{fig:z_new_testing}
\end{figure}

\section{Backpropagation}
\label{sec:backpropagation}
\subsection{Likelihood}
The Student-t density, that is required for further derivation, can be parametrised in different ways. In this paper the following parametrisation is used 
\begin{equation}
\mathcal{T}(x; \mu, \beta, \nu) = \frac{\Gamma\left(\frac{\nu + 1}{2}\right)}{\Gamma\left(\frac{\nu}{2}\right)\sqrt{\pi \nu \beta}} \left(1 + \frac{(x - \mu)^2}{\nu\beta}\right)^{-\frac{\nu + 1}{2}}
\end{equation}
where $\Gamma(\cdot)$ denotes the Gamma function.

We use the probabilistic backpropagation algorithm \cite{hernandez2015probabilistic} for computing parameters updates. It is based on assumed density filtering and expectation propagation and allows to update parameters of the distributions based on the derivative of the logarithm of the normalisation constant. 
The exact posterior \ref{eq:posterior} is approximated with a factorised distribution
\begin{align}
\begin{split}
q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{l=1}^L\prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk, l} | m^w_{dk, l}, v^w_{dk, l}) \\
&\times \prod_{l=1}^L\prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd'', l} | m^s_{d'd'', l}, v^s_{d'd'', l}) \\
&\times \text{Gam}(\gamma; \alpha^\gamma, \beta^\gamma) \text{Gam}(\eta; \alpha^\eta, \beta^\eta) 
\end{split}
\end{align}
The normalisation constant of the approximating distribution $q$ with the likelihood~\ref{eq:likelihood} term incorporated can be computed as follows
\begin{align}
Z = \int \prod_{d=1}^{D} \big[&\mathcal{N}(\beta_d | f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) \\
 &q(\mathbf{S}, \mathbf{W}, \eta, \gamma)\big] \mathrm{d}\mathbf{S} \mathrm{d}\mathbf{W} \mathrm{d}\eta \mathrm{d}\gamma
\end{align}
We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\mathbf{z}_L$ - output from the network
\begin{align}
\begin{split}
&Z \approx \int \prod_{d=1}^{D} \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1}) \\
&\times (\omega^{z_L}_d \delta_0([\mathbf{z}_L]_d) + (1 - \omega^{z_L}_d)\mathcal{N}(m^{z_L}_d, v^{z_L}_d))\\
&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}\mathbf{z}_L \mathrm{d}\boldsymbol\gamma \\
&= \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1})  \delta_0([z_L]_d) \\
&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[{z}_L]_d \mathrm{d}\gamma_d \\
& + (1 - \omega^{z_L}_d)\int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1})\mathcal{N}(m^{z_L}_d, v^{z_L}_d)) \\
&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[{z}_L]_d \mathrm{d}\gamma_d\Big] \\
& = \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \mathcal{N}(\beta_d | 0, \gamma_d^{-1})  \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma) d\gamma_d \\
& + (1 - \omega^{z_L}_d)\int \big[\mathcal{T}(\beta_d | [\mathbf{z}_L]_d, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma) \\
&\times \mathcal{N}(m^{z_L}_d, v^{z_L}_d))\big] \mathrm{d}[{z}_L]_d\Big] \\
& \approx \prod_{d=1}^D \Big[\omega^{z_L}_d  \mathcal{T}(\beta_d | 0, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma) \\
&+ (1 - \omega^{z_L}_d)\mathcal{N}(m^{z_L}_d, \frac{\beta^\gamma}{\alpha^\gamma - 1} + v^{z_L})\Big]
\end{split}
\end{align}

Then derivatives of $Z$ are computed w.r.t the weights and hyperparameters of the factorised distribution and then they are used for updates.

\section{Experiments}
\subsection{Synthetic data}
We have generated the random Gaussian design matrix $\mathbf{X}$. Coefficients $\boldsymbol\beta$ are generated from the spike-and-slab distribution with truncated slab: each component of $\boldsymbol\beta$ is zero with probability 0.8 or is from standard Gaussian distribution without interval (-0.1, 0.1) with probability 0.2. The observations are generated accordingly. Size of observations is $K=100$, size of coefficients is $D=784$, number of layers is $L=4$. Size of the training set is $1000$, validation set is $100$.

We compare two versions of the proposed Bayesian LISTA: with shared weight matrices and with individual matrices at each layer --- and LISTA.

The NMSE is presented in figure \ref{fig:validation_synthetic}.
\begin{figure}[t]
\includegraphics[width=\columnwidth]{loss_synthetic}
\caption{Validation NMSE on synthetic data}
\label{fig:validation_synthetic}
\end{figure}

\subsection{MNIST}
Here we evaluate the proposed Bayesian LISTA in terms of predictive performance on the MNIST dataset \cite{lecun2010mnist}. The dataset contains images of handwritten digits of size $28 \times 28 = 784$. The design matrix $\mathbf{X}$ is learned on 5000 images with the minibatch online algorithm (J. Mairal, et al 2009). The resulting size of $\mathbf{X}$ is $100 \times 784$. Then we generate observations as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta$ are images converted to vectors. We use randomly selected 1000 images for training and 100 for validation.

Figure \ref{fig:validation} presents NMSE loss on the validation set.

Proposed Bayesian LISTA networks estimate posterior distribution for $\boldsymbol\beta$. Figure \ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
\begin{figure}[t]
\includegraphics[width=\columnwidth]{loss}
\caption{Validation NMSE}
\label{fig:validation}
\end{figure}
\begin{figure*}[t]
\subfloat[$\beta$ posterior mean]{\includegraphics[width=0.66\columnwidth]{posterior_mean}}
\subfloat[$\beta$ posterior std]{\includegraphics[width=0.66\columnwidth]{posterior_std}}
\subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.66\columnwidth]{posterior_spike_indicator}}
\caption{Posterior for the digit 7.}
\label{fig:posterior_distribution}
\end{figure*}
\begin{figure*}[t]
\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_0}}
\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_1}}
\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_2}}
\caption{Samples from the posterior for the digit 7.}
\label{fig:posterior_samples}
\end{figure*}

\section{Discussion}
As far as we are aware, this is the first implementation of Bayesian deep sparse coding algorithm, there are works on Bayesian sparsity in context of neural networks \cite{he2017bayesian}, but it is not the Bayesian Neural Network. We find not only correct predictions but also useful posterior estimates for the predictions that show how the model is confident in its decision. 
Though EP is not suited for distributed inference, some variations of ADF can be used \cite{li2015stochastic}. This allows the proposed approach to scale.

\bibliographystyle{unsrt}
\bibliography{bibliography}

\end{document}

### 2018-03-07 paper/BayesianLISTA.tex
reorganisation + collect results on synthetic + paper correction

@@
 
-\title{Bayesian LISTA / Uncertainty propagation in deep neural networks for sparse coding}
+\title{Uncertainty propagation in deep neural networks for sparse coding}
 
@@
 
-\begin{lemma}[Moments of spike and slab]
+\begin{lemma}[Moments of spike and slab distribution]
 \label{thm:moments_spsl}
 Let the random variable $\xi$ have a spike and slab distribution with probability of spike $\omega$, slab mean $m$ and slab variance $v$. Then its moments are
+\begin{subequations}
 \begin{align}
 \mathbb{E}\xi &= (1-\omega)m \\
-%\mathbb{E}\xi^2 &= (1-\omega)(v + m^2) \\
-\text{Var }\xi & = (1-\omega)(v + \omega m^2)
+\operatorname{Var}\xi & = (1-\omega)(v + \omega m^2)
 \end{align}
+\end{subequations}
+\end{lemma}
 
-\end{lemma}
 \begin{proof}
-\begin{align}
+\begin{align*}
+\begin{split}
 \mathbb{E}\xi &= \int x (\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v))dx \\
 & = \omega \int x \delta_0(x)dx + (1 - \omega)\int x \mathcal{N}(x; m, v)dx \\
-& = (1-\omega)m
-\end{align}
-\begin{align}
+& = (1-\omega)m \\
 \mathbb{E}\xi^2 &= \int x^2 (\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v))dx \\
 & = \omega \int x^2 \delta_0(x)dx + (1 - \omega)\int x^2 \mathcal{N}(x; m, v)dx \\
-& = (1-\omega)(v + m^2)
-\end{align}
-\begin{align}
-\text{Var }\xi &= \mathbb{E}\xi^2 - \left(\mathbb{E}\xi\right)^2\\
-& = (1-\omega)(v + \omega m^2)
-\end{align}
+& = (1-\omega)(v + m^2) \\
+\operatorname{Var}\xi &= \mathbb{E}\xi^2 - \left(\mathbb{E}\xi\right)^2 = (1-\omega)(v + \omega m^2)
+\end{split}
+\end{align*}
 \end{proof}
 
- \begin{lemma}
+ \begin{lemma}[Product of Gaussian matrix and constant vector]
  \label{thm:matrix_const}
  Let $\mathbf{W} \in \mathbb{R}^{D \times K}$ be a matrix of independent Gaussian-distributed random variables: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y} \in \mathbb{R}^K$ be a constant vector.
-Then their product $\mathbf{W} \mathbf{y}$ is a vector $\mathbf{b} \in \mathbb{R}^{D}$ of random variables $b_d \sim \mathcal{N}(m^b_d, w^b_d)$, where $m^b_d = \sum_{k=1}^Ky_k m^w_{dk}$, $w^b_d = \sum_{k=1}^Ky_k^2v^w_{dk}$.
- %If we denote $M^W = [m^w_{dk}]_{d=1:D, k=1:K}$, $V^W = [v^w_{dk}]_{d=1:D, k=1:K}$, then $\mathbf{b}^m = W^My$, $\mathbf{b}^w = W^Vy^2$.
+Then their product $\mathbf{W} \mathbf{y}$ is a vector $\mathbf{b} \in \mathbb{R}^{D}$ of random variables $b_d \sim \mathcal{N}(m^b_d, w^b_d)$, where
+\begin{subequations}
+\begin{align}
+m^b_d &= \sum_{k=1}^Ky_k m^w_{dk}, \\
+w^b_d &= \sum_{k=1}^Ky_k^2v^w_{dk}.
+ \end{align}
+\end{subequations}
+
  \end{lemma}
@@
 
-  \begin{lemma}
+  \begin{lemma}[Product of Gaussian matrix and Gaussian vector]
   \label{thm:matrix_vector}
  Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\boldsymbol\beta \in \mathbb{R}^D$ be a vector with spike-and-slab distributed variables: $\beta_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
-Then their product can be approximated as a vector $\mathbf{d} \in \mathbb{R}^{D}$ of random variables $d_d \sim \mathcal{N}(d^d_m, d^d_w)$, where $m^d_d = \sum_{d'=1}^D m^s_{dd'}(1-\omega_{d'})m_{d'}$, $v^d_d = \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} + (1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}]$.
+If their product is approximated as a vector $\mathbf{e} \in \mathbb{R}^{D}$ of random variables $e_d \sim \mathcal{N}(m^e_d, w^e_d)$, then
+\begin{subequations}
+\begin{align}
+ m^e_d &= \sum_{d'=1}^D m^s_{dd'}(1-\omega_{d'})m_{d'}, \\
+ \begin{split}
+ v^e_d &= \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} \\
+ & {}+ (1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}].
+ \end{split}
+ \end{align}
+\end{subequations}
  \end{lemma}
  \begin{proof}
- 	We compute the mean and variance of the product $\mathbf{S}\boldsymbol\beta$ and approximate resulting distribution as Gaussian.
-\begin{align}
-	&\mathbb{E}d_d = \mathbb{E} \left[\sum_{d'=1}^D s_{dd'}\beta_{d'}\right] =  \sum_{d'=1}^D \mathbb{E}[s_{dd'}\beta_{d'}] \\
-	&= \sum_{d'=1}^D \mathbb{E}s_{dd'}\mathbb{E}\beta_{d'} = \sum_{d'=1}^D m^s_{dd'}\mathbb{E}\beta_{d'}
-\end{align}
-\begin{align}
-	&\text{Var}d_d = \text{Var} \left[\sum_{d'=1}^D s_{dd'}\beta_{d'}\right] =  \sum_{d'=1}^D \text{Var}[s_{dd'}\beta_{d'}] = \\
-	&\sum_{d'=1}^D [(\mathbb{E}s_{dd'})^2 \text{Var}\beta_{d'} + (\mathbb{E}\beta_{d'})^2 \text{Var}s_{dd'} + \text{Var}\beta_{d'} \text{Var}s_{dd'}]
-\end{align}
-where $\mathbb{E}\beta_{d'}$, $\text{Var}\beta_{d'}$ are computed according to lemma~\ref{thm:moments_spsl}.
+ 	We compute the mean and variance of the product $\mathbf{S}\boldsymbol\beta$ with an assumption of independence of its components and approximate resulting distribution with Gaussian.
+The quality of this approximation is discussed in section \ref{sec:approx_quality}
+\begin{flalign*}
+	\mathbb{E}e_d &= \sum_{d'=1}^D \mathbb{E}[s_{dd'}\beta_{d'}]  = \sum_{d'=1}^D m^s_{dd'}\mathbb{E}\beta_{d'}\\
+	\operatorname{Var}e_d &= \sum_{d'=1}^D \operatorname{Var}[s_{dd'}\beta_{d'}] = \sum_{d'=1}^D [(\mathbb{E}s_{dd'})^2 \operatorname{Var}\beta_{d'} \\
+	&{}+ (\mathbb{E}\beta_{d'})^2 \operatorname{Var}s_{dd'} + \operatorname{Var}\beta_{d'} \operatorname{Var}s_{dd'}]
+\end{flalign*}
+where $\mathbb{E}\beta_{d'}$, $\operatorname{Var}\beta_{d'}$ are computed according to lemma~\ref{thm:moments_spsl}.
  \end{proof}
 
-\begin{lemma}
+\begin{lemma}[Sum of Gaussian vectors]
 \label{thm:sum_vectors}
-If $\mathbf{b} \in \mathbb{R}^{D}$ and $\mathbf{d} \in \mathbb{R}^{D}$ are both vectors of independent Gaussian-distributed random variables: $b_{d} \sim \mathcal{N}(m^b_{d}, v^b_{d})$, $d_{d} \sim \mathcal{N}(m^d_{d}, v^d_{d})$ then their sum $\mathbf{c} = \mathbf{b} + \mathbf{d}$ is a vector of independent Gaussian-distributed random variables $c_{d} \sim \mathcal{N}(m^c_{d}, v^c_{d})$ with $m^c_{d} = m^b_{d} + m^d_{d}$, $v^c_{d} = v^b_{d} + v^d_{d}$
+If $\mathbf{b} \in \mathbb{R}^{D}$ and $\mathbf{e} \in \mathbb{R}^{D}$ are both vectors of independent Gaussian-distributed random variables: $b_{d} \sim \mathcal{N}(m^b_{d}, v^b_{d})$, $e_{d} \sim \mathcal{N}(m^e_{d}, v^e_{d})$ then their sum $\mathbf{c} = \mathbf{b} + \mathbf{e}$ is a vector of independent Gaussian-distributed random variables $c_{d} \sim \mathcal{N}(m^c_{d}, v^c_{d})$ with
+\begin{subequations}
+\begin{align}
+m^c_{d} &= m^b_{d} + m^e_{d}, \\
+v^c_{d} &= v^b_{d} + v^e_{d}.
+ \end{align}
+\end{subequations}
 \end{lemma}
@@
 
-\begin{lemma}
+\begin{lemma}[Gaussian propagation through soft thresholding]
 \label{thm:soft_thresholding}
-When a Gaussian-distributed random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft-thresholding function it can be approximated with the spike and slab distribution on $x^*$ with the probability of spike $\omega^*$, slab mean $m^*$ and slab variance $v^*$ (Formulae are given in the proof).
+When a Gaussian-distributed random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft-thresholding function it can be approximated with the spike and slab distribution on $x^*$ with the probability of spike $\omega^*$, slab mean $m^*$ and slab variance $v^*$ (parameters of the approximating distribution are given in the proof).
 \end{lemma}
 \begin{proof}
-Soft-thresholding operator is defined as $h_\lambda(v) = \text{sign}(v) * \max(|v| - \lambda, 0)$. We need to compute the parameters of approximating distribution.
-\begin{enumerate}
-\item The probability of spike $\omega^*$ equals to the probability mass that lies in $(-\lambda, \lambda)$ of the original distribution and is flattened into zero by soft-thresholding operator.
-As the original distribution is Gaussian, this can be computed as $\omega^* = p(x^*=0) = p(x \in (-\lambda, \lambda)) = \Phi(\frac{\lambda-m}{\sqrt{v}}) - \Phi(\frac{-\lambda-m}{\sqrt{v}})$.
-\item Soft-thresholding shifts elements that are greater than $\lambda$  or less than $-\lambda$ elements towards 0.
+
+The probability of spike $\omega^*$ equals to the probability mass of the original distribution that lies in $(-\lambda, \lambda)$  and is flattened into zero by soft-thresholding operator.
+As the original distribution is Gaussian, this can be computed as
+\begin{align}
+\begin{split}
+\omega^* &= p(x^*=0) = p(x \in [-\lambda, \lambda]) \\
+&= \Phi\left(\frac{\lambda-m}{\sqrt{v}}\right) - \Phi\left(\frac{-\lambda-m}{\sqrt{v}}\right). 
+\end{split}
+\end{align}
+
+Soft-thresholding shifts elements that are greater than $\lambda$  or less than $-\lambda$ elements towards 0.
 Let $\psi(\cdot)$ denote the density of the soft-threshold distribution, $\phi(\cdot)$ denote the density of the original Gaussian distribution.
-Then the first moment of the resulting distribution is $m^* = \int_{-\infty}^{+\infty}x\psi(x)dx = \int_{-\infty}^{0}x\phi(x-\lambda)dx + \int_{0}^{+\infty}x\phi(x+\lambda)dx$.
-Integrals are computed below.
+Then the first moment of the resulting distribution is
+
 \begin{align}
-&\int_{-\infty}^{0}x\phi(x-\lambda)dx = \\
-&-\frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} \\
-& + (\lambda+m)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
+\begin{split}
+m^* &= \int_{-\infty}^{+\infty}x\psi(x)dx= \int_{-\infty}^{0}x\phi(x-\lambda)dx \\
+&{} + \int_{0}^{+\infty}x\phi(x+\lambda)dx.
+\end{split}
 \end{align}
+
+Integrals are computed as
 \begin{align}
-&\int_{0}^{+\infty}x\phi(x+\lambda)dx = \\
-& = \frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\\
+\begin{split}
+&\int_{-\infty}^{0}x\phi(x-\lambda)dx = -\frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} \\
+&{} + (\lambda+m)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
+\end{split}\\
+\begin{split}
+&\int_{0}^{+\infty}x\phi(x+\lambda)dx = \frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\\
 & + (m - \lambda)\left(1 - \Phi\left(-\frac{\lambda-m}{\sqrt{v}}\right)\right)
+\end{split}
 \end{align}
-\item The second moment of the approximating distribution is computed as $s = \int_{-\infty}^{+\infty}x^2\psi(x)dx = \int_{-\infty}^{0}x^2\phi(x-\lambda)dx + \int_{0}^{+\infty}x^2\phi(x+\lambda)dx$.
+
+The second moment of the approximating distribution is computed as
 \begin{align}
+\begin{split}
+s &= \int_{-\infty}^{+\infty}x^2\psi(x)dx = \int_{-\infty}^{0}x^2\phi(x-\lambda)dx \\
+&{}+ \int_{0}^{+\infty}x^2\phi(x+\lambda)dx.
+\end{split}
+\end{align}
+
+Integrals are computed as
+\begin{align}
+\begin{split}
 &\int_{-\infty}^{0}x^2\phi(x-\lambda)dx = \\
@@
 & + (\sigma^2 + (\lambda+m)^2)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
-\end{align}
-\begin{align}
+\end{split}\\
+\begin{split}
 &\int_{0}^{+\infty}x^2\phi(x+\lambda)dx = \\
@@
 & + (\sigma^2 + (m - \lambda)^2)\left(1 - \Phi\left(\frac{\lambda -m}{\sqrt{v}}\right)\right)
+\end{split}
 \end{align}
+
 Resulting variance is
@@
 \end{equation}
-\end{enumerate}
+
 \end{proof}
@@
 \begin{enumerate}
-	\item $\mathbf{b} = Wy$ is computed according to lemma \ref{thm:matrix_const}
-	\item $\mathbf{d} = S\boldsymbol\beta_{l-1}$ is computed according to lemma \ref{thm:matrix_vector}
-	\item $\mathbf{c} = \mathbf{b} + \mathbf{d}$ is computed according to lemma \ref{thm:sum_vectors}
-	\item $\boldsymbol\beta_{l} = h_\lambda(\mathbf{c})$ is computed according to lemma \ref{thm:soft_thresholding}
+	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is computed according to lemma \ref{thm:matrix_const};
+	\item $\mathbf{e} = \mathbf{S}\boldsymbol\beta_{l-1}$ is computed according to lemma \ref{thm:matrix_vector};
+	\item $\mathbf{c} = \mathbf{b} + \mathbf{e}$ is computed according to lemma \ref{thm:sum_vectors};
+	\item $\boldsymbol\beta_{l} = h_\lambda(\mathbf{c})$ is computed according to lemma \ref{thm:soft_thresholding}.
 \end{enumerate}
@@
 \subsection{Approximation quality}
+\label{sec:approx_quality}
 We have used two approximations in forward propagation of the uncertainty.

### 2018-03-07 theano/experiments/active_learning/active_learning_experiment.py

@@ -11,9 +11,9 @@ import matplotlib.pyplot as plt
 
 class ActiveLearningExperiments(object):
     def __init__(self, update_size):
-        self.L = 4
+        self.L = 20
         self.learning_rate = 0.0001
-        self.n_train_iter = 200
+        self.n_train_iter = 100
         self.update_size = update_size
 
         self.freq_validation_loss = []
@@ -27,7 +27,7 @@ class ActiveLearningExperiments(object):
 
     def get_mnist_data_active_learning(self):
         self.K=100
-        n_train, n_pool, n_test = 10, 1000, 100
+        n_train, n_pool, n_test = 50, 100, 100
         data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
         data.check_download()
         data.learn_dictionary()
@@ -127,14 +127,15 @@ if __name__=='__main__':
     tf.set_random_seed(rseed)
 
     n_upd_iter = 5
-    active_learning_experiments = ActiveLearningExperiments(update_size=50)
-    active_learning_experiments.get_synthetic_data_active_learning()
+    active_learning_experiments = ActiveLearningExperiments(update_size=10)
+    #active_learning_experiments.get_synthetic_data_active_learning()
+    active_learning_experiments.get_mnist_data_active_learning()
     active_learning_experiments.init_and_pretrain_lista()
 
     for i in trange(n_upd_iter):
         active_learning_experiments.choose_next_random_from_pool()
         active_learning_experiments.choose_next_train_active_from_pool()
-        for j in range(50):
+        for j in range(100):
             active_learning_experiments.learning_iter()
         active_learning_experiments.update_quality()
 

### 2018-03-07 theano/experiments/mnist/mnist_data.py

@@ -1,0 +1,74 @@
+from time import time
+
+import tensorflow as tf
+import numpy as np
+from sklearn.decomposition import MiniBatchDictionaryLearning
+import matplotlib.pyplot as plt
+
+class MnistData(object):
+    def __init__(self, K=100, train_size=100, valid_size=100):
+        self.train_data = None
+        self.train_labels = None
+        self.dictionary_learn_data = None
+        self.dictionary_learn_labels = None
+        self.validation_data = None
+        self.validation_labels = None
+
+        self.K = K
+        self.X = None
+        self.image_size = (28, 28)
+
+        self.y_train = None
+        self.y_validation = None
+
+        self.training_size = train_size
+        self.validation_size = valid_size
+
+    def check_download(self):
+        mnist = tf.contrib.learn.datasets.load_dataset("mnist")
+        random_train_ind = np.random.choice(mnist.train.images.shape[0], self.training_size, replace=False)
+        self.train_data = mnist.train.images[random_train_ind]
+        #self.train_labels = np.asarray(mnist.train.labels, dtype=np.int32)
+        self.dictionary_learn_data = mnist.test.images
+        #self.dictionary_learn_labels = np.asarray(mnist.test.labels, dtype=np.int32)
+        random_validation_ind = np.random.choice(mnist.validation.images.shape[0], self.validation_size, replace=False)
+        self.validation_data = mnist.validation.images[random_validation_ind]
+        #self.validation_labels = np.asarray(mnist.validation.labels, dtype=np.int32)
+
+        self.normalize()
+
+    def normalize(self):
+        self.train_mean = np.mean(self.train_data, axis=0)
+        self.train_std = np.std(self.train_data, axis=0)
+        self.train_data = (self.train_data - self.train_mean) / self.train_std
+        self.validation_data = (self.validation_data - self.train_mean) / self.train_std
+
+    def learn_dictionary(self):
+        print('Learning the dictionary...')
+        t0 = time()
+        dico = MiniBatchDictionaryLearning(n_components=self.K, alpha=1, n_iter=500)
+        self.X = dico.fit(self.dictionary_learn_data).components_
+        dt = time() - t0
+        print('done in %.2fs.' % dt)
+
+        self.y_train = np.dot(self.train_data, self.X.T)
+        self.y_validation = np.dot(self.validation_data, self.X.T)
+
+    def generate_random_design_matrix(self):
[…]

### 2018-03-07 theano/experiments/synthetic/number_of_layers/collect_results.py

@@ -1,0 +1,121 @@
+import errno
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+
+class NumberOfLayersExperimentReultsCollector(object):
+    def __init__(self):
+        self.L_array = [2, 3, 4, 5, 6, 7, 8, 9, 10]
+        self.random_range = 10
+        self.n_iter = 1000
+
+    def collect_all(self):
+        self.ista_f_meas_train, self.ista_f_meas_validation, self.ista_loss_train, self.ista_loss_validation = \
+            self.collect_ista_fista('ista')
+        self.fista_f_meas_train, self.fista_f_meas_validation, self.fista_loss_train, self.fista_loss_validation = \
+            self.collect_ista_fista('fista')
+        self.freq_f_meas_train, self.freq_f_meas_validation, self.freq_loss_train, self.freq_loss_validation = \
+            self.collect_main('freq')
+        self.sh_bayes_f_meas_train, self.sh_bayes_f_meas_validation, self.sh_bayes_loss_train, self.sh_bayes_loss_validation = \
+            self.collect_main('sh_bayes')
+
+    def collect_ista_fista(self, filename):
+        f_meas_train = np.zeros((self.random_range, len(self.L_array), self.n_iter))
+        f_meas_validation = np.zeros((self.random_range, len(self.L_array), self.n_iter))
+        loss_train = np.zeros((self.random_range, len(self.L_array), self.n_iter))
+        loss_validation = np.zeros((self.random_range, len(self.L_array), self.n_iter))
+
+        for rseed in range(self.random_range):
+            for i, L in enumerate(self.L_array):
+                saved_res = np.load('ista_fista/fista_ista_{}_L_{}_rseed_{}.npz'.format(L, rseed, filename))
+                f_meas_train[rseed, i] = saved_res['train_f_meas']
+                f_meas_validation[rseed, i] = saved_res['validation_f_meas']
+                loss_train[rseed, i] = saved_res['train_loss']
+                loss_validation[rseed, i] = saved_res['validation_loss']
+
+        f_meas_train = np.mean(f_meas_train, axis=0)
+        f_meas_validation = np.mean(f_meas_validation, axis=0)
+        loss_train = np.mean(loss_train, axis=0)
+        loss_validation = np.mean(loss_validation, axis=0)
+
+        f_meas_train = f_meas_train[:, -1]
+        f_meas_validation = f_meas_validation[:, -1]
+        loss_train = loss_train[:, -1]
[…]

### 2018-03-07 theano/experiments/synthetic/undersampling/collect_results.py

@@ -1,0 +1,121 @@
+import errno
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+
+class UndersamplingExperimentReultsCollector(object):
+    def __init__(self):
+        self.K_array = [10, 20, 30, 40, 50, 60, 70, 80, 90, 100]
+        self.random_range = 10
+        self.n_iter = 1000
+
+    def collect_all(self):
+        self.ista_f_meas_train, self.ista_f_meas_validation, self.ista_loss_train, self.ista_loss_validation = \
+            self.collect_ista_fista('ista')
+        self.fista_f_meas_train, self.fista_f_meas_validation, self.fista_loss_train, self.fista_loss_validation = \
+            self.collect_ista_fista('fista')
+        self.freq_f_meas_train, self.freq_f_meas_validation, self.freq_loss_train, self.freq_loss_validation = \
+            self.collect_main('freq')
+        self.sh_bayes_f_meas_train, self.sh_bayes_f_meas_validation, self.sh_bayes_loss_train, self.sh_bayes_loss_validation = \
+            self.collect_main('sh_bayes')
+
+    def collect_ista_fista(self, filename):
+        f_meas_train = np.zeros((self.random_range, len(self.K_array), self.n_iter))
+        f_meas_validation = np.zeros((self.random_range, len(self.K_array), self.n_iter))
+        loss_train = np.zeros((self.random_range, len(self.K_array), self.n_iter))
+        loss_validation = np.zeros((self.random_range, len(self.K_array), self.n_iter))
+
+        for rseed in range(self.random_range):
+            for i, K in enumerate(self.K_array):
+                saved_res = np.load('ista_fista/fista_ista_{}_K_{}_rseed_{}.npz'.format(K, rseed, filename))
+                f_meas_train[rseed, i] = saved_res['train_f_meas']
+                f_meas_validation[rseed, i] = saved_res['validation_f_meas']
+                loss_train[rseed, i] = saved_res['train_loss']
+                loss_validation[rseed, i] = saved_res['validation_loss']
+
+        f_meas_train = np.mean(f_meas_train, axis=0)
+        f_meas_validation = np.mean(f_meas_validation, axis=0)
+        loss_train = np.mean(loss_train, axis=0)
+        loss_validation = np.mean(loss_validation, axis=0)
+
+        f_meas_train = f_meas_train[:, -1]
+        f_meas_validation = f_meas_validation[:, -1]
+        loss_train = loss_train[:, -1]
[…]

### 2018-03-08 paper/BayesianLISTA.tex
updates to text and experiments code

@@
 \begin{equation}
+\label{eq:regression_problem}
 \mathbf{y} = \mathbf{X}\boldsymbol\beta + \varepsilon
@@
 \section{Experiments}
-\subsection{Synthetic data}
-We have generated the random Gaussian design matrix $\mathbf{X}$.
-Coefficients $\boldsymbol\beta$ are generated from the spike-and-slab distribution with truncated slab: each component of $\boldsymbol\beta$ is zero with probability 0.8 or is from standard Gaussian distribution without interval (-0.1, 0.1) with probability 0.2.
-The observations are generated accordingly.
-Size of observations is $K=100$, size of coefficients is $D=784$, number of layers is $L=4$.
-Size of the training set is $1000$, validation set is $100$.
+
+The following quality measures are used:
+\begin{itemize}
+\item $\text{NMSE} (\text{normalised mean square error)})= \dfrac{\|\mathbf{X} - \widehat{\mathbf{X}}\|^2_{F}}{\|\mathbf{X}\|^2_{F}}$, where $\mathbf{X}$ is the true signal, $\widehat{\mathbf{X}}$ is the estimate, computed as the mean of the approximated posterior distribution, $\|\cdot\|_{F}$ is the Frobenius norm of a matrix;
+\item $\text{F-measure} = 2\dfrac{\text{precision}\cdot\text{recall}}{\text{precision} + \text{recall}}$ between non-zero elements of the true signal $\mathbf{X}$ and non-zero elements of the estimate $\widehat{\mathbf{X}}$.
+\end{itemize}
+
+We demonstrate the performance on small datasets to highlight that the proposed algorithm can learn when the dataset size is not sufficient for LISTA.
+
+\subsection{Predictive performance on synthetic data}
+First, the predictive performance of the proposed Bayesian LISTA is analysed on synthetic data.
+We generate $N_\text{train}=500$ sparse coefficients vectors $\boldsymbol\beta_n$ each of size $D = 100$.
+Coefficients $\boldsymbol\beta$ are generated from the spike-and-slab distribution with truncated slab: each component of $\beta_{nd}$ is zero with probability $0.8$ or is from standard Gaussian distribution without interval $(-0.1, 0.1)$ with probability $0.2$.
+Truncation of the zeros allows to remove from support pattern values with insignificant contributions \cite{xin2016maximal}.
+To simulate sparse observations, we have generated the random Gaussian design matrix $\mathbf{X} \in \mathbb{K \times D}$.
+The observations are generated according to the \ref{eq:regression_problem} with zero-mean Gaussian noise with standard deviation $0.5$.
+
+We compare the proposed Bayesian LISTA with original LISTA algorithm \cite{gregor2010learning} and two deterministic algorithms: Iterative Shrinkage and Thresholding Algorithm (ISTA) \cite{daubechies2004iterative} and Fast ISTA (FISTA) \cite{beck2009fast}.
+ISTA and FISTA iterate recursive updates of the $\boldsymbol\beta$ estimator in a way similar to LISTA but without weights updates.
+FISTA adds the momentum to ISTA and improves its convergence speed.
+We limit the number of iterations in these algorithms with $L$ that is the same as the number of layers in Bayesian LISTA and LISTA.
+
+In the Figure \ref{fig:number_of_layers_synthetic} prediction performance for increasing number of layers is presented. The proposed algorithm is superior in terms of NMSE
+
+\begin{figure*}[t]
+\subfloat[NMSE on train]{\includegraphics{graphics/synthetic_number_of_layers/nmse_train}}
+~
+\subfloat[NMSE on validation]{\includegraphics{graphics/synthetic_number_of_layers/nmse_validation}}
+\newline
+\subfloat[F measure on train]{\includegraphics{graphics/synthetic_number_of_layers/f_measure_train}}
+~
+\subfloat[F measure on validation]{\includegraphics{graphics/synthetic_number_of_layers/f_measure_validation}}
+\caption{Number of layers on synthetic data}
+\label{fig:number_of_layers_synthetic}
+\end{figure*}
 
@@
 
-The NMSE is presented in figure \ref{fig:validation_synthetic}.
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{loss_synthetic}
-\caption{Validation NMSE on synthetic data}
-\label{fig:validation_synthetic}
-\end{figure}
+%The NMSE is presented in figure \ref{fig:validation_synthetic}.
+%\begin{figure}[t]
+%\includegraphics[width=\columnwidth]{loss_synthetic}
+%\caption{Validation NMSE on synthetic data}
+%\label{fig:validation_synthetic}
+%\end{figure}
 

### 2018-03-08 theano/experiments/active_learning/check_faster_add_more_at_a_time.py

@@ -13,9 +13,9 @@ import six.moves.cPickle as pickle
 
 class ActiveLearningExperiments(object):
     def __init__(self, update_size):
-        self.L = 20
+        self.L = 8
         self.learning_rate = 0.0001
-        self.n_train_iter = 50
+        self.n_train_iter = 200
         self.update_size = update_size
 
         self.freq_validation_loss = []
@@ -29,7 +29,7 @@ class ActiveLearningExperiments(object):
 
     def get_mnist_data_active_learning(self):
         self.K=100
-        n_train, n_pool, n_test = 50, 100, 100
+        n_train, n_pool, n_test = 10, 1000, 100
         data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
         data.check_download()
         data.learn_dictionary()
@@ -48,7 +48,7 @@ class ActiveLearningExperiments(object):
     def get_synthetic_data_active_learning(self):
         self.D = 100
         self.K = 50
-        n_train, n_pool, n_test = 500, 1000, 100
+        n_train, n_pool, n_test = 900, 500, 100
         data_generator = DataGenerator(self.D, self.K)
         self.train_data_beta, self.train_data_y, _ = data_generator.new_sample(n_train)
         self.pool_data_beta, self.pool_data_y, _ = data_generator.new_sample(n_pool)
@@ -123,44 +123,26 @@ class ActiveLearningExperiments(object):
 
 if __name__=='__main__':
 
-    # #for rseed in trange(10):
-    # rseed = 1
-    # np.random.seed(rseed)
-    # tf.set_random_seed(rseed)
-    #
-    # n_upd_iter = 5
-    # active_learning_experiments = ActiveLearningExperiments(update_size=10)
-    # #active_learning_experiments.get_synthetic_data_active_learning()
-    # active_learning_experiments.get_mnist_data_active_learning()
-    # active_learning_experiments.init_and_pretrain_lista()
-    #
-    # for i in trange(n_upd_iter):
-    #     active_learning_experiments.choose_next_random_from_pool()
-    #     active_learning_experiments.choose_next_train_active_from_pool()
-    #     for j in range(100):
-    #         active_learning_experiments.learning_iter()
-    #     active_learning_experiments.update_quality()
-    #
-    # active_learning_experiments.plot()
-
+    #for rseed in trange(10):
     rseed = 1
     np.random.seed(rseed)
     tf.set_random_seed(rseed)
 
[…]

### 2018-03-08 theano/experiments/active_learning/faster_check_further_adding.py

@@ -13,9 +13,9 @@ import six.moves.cPickle as pickle
 
 class ActiveLearningExperiments(object):
     def __init__(self, update_size):
-        self.L = 20
+        self.L = 8
         self.learning_rate = 0.0001
-        self.n_train_iter = 50
+        self.n_train_iter = 200
         self.update_size = update_size
 
         self.freq_validation_loss = []
@@ -29,7 +29,7 @@ class ActiveLearningExperiments(object):
 
     def get_mnist_data_active_learning(self):
         self.K=100
-        n_train, n_pool, n_test = 50, 100, 100
+        n_train, n_pool, n_test = 10, 1000, 100
         data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
         data.check_download()
         data.learn_dictionary()
@@ -48,7 +48,7 @@ class ActiveLearningExperiments(object):
     def get_synthetic_data_active_learning(self):
         self.D = 100
         self.K = 50
-        n_train, n_pool, n_test = 500, 1000, 100
+        n_train, n_pool, n_test = 900, 500, 100
         data_generator = DataGenerator(self.D, self.K)
         self.train_data_beta, self.train_data_y, _ = data_generator.new_sample(n_train)
         self.pool_data_beta, self.pool_data_y, _ = data_generator.new_sample(n_pool)
@@ -123,44 +123,26 @@ class ActiveLearningExperiments(object):
 
 if __name__=='__main__':
 
-    # #for rseed in trange(10):
-    # rseed = 1
-    # np.random.seed(rseed)
-    # tf.set_random_seed(rseed)
-    #
-    # n_upd_iter = 5
-    # active_learning_experiments = ActiveLearningExperiments(update_size=10)
-    # #active_learning_experiments.get_synthetic_data_active_learning()
-    # active_learning_experiments.get_mnist_data_active_learning()
-    # active_learning_experiments.init_and_pretrain_lista()
-    #
-    # for i in trange(n_upd_iter):
-    #     active_learning_experiments.choose_next_random_from_pool()
-    #     active_learning_experiments.choose_next_train_active_from_pool()
-    #     for j in range(100):
-    #         active_learning_experiments.learning_iter()
-    #     active_learning_experiments.update_quality()
-    #
-    # active_learning_experiments.plot()
-
+    #for rseed in trange(10):
     rseed = 1
     np.random.seed(rseed)
     tf.set_random_seed(rseed)
 
[…]

### 2018-03-08 theano/experiments/active_learning/mnist_test_1.py

@@ -29,7 +29,7 @@ class ActiveLearningExperiments(object):
 
     def get_mnist_data_active_learning(self):
         self.K=100
-        n_train, n_pool, n_test = 50, 100, 100
+        n_train, n_pool, n_test = 50, 500, 100
         data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
         data.check_download()
         data.learn_dictionary()
@@ -150,7 +150,7 @@ if __name__=='__main__':
     saved_file_name = []#'synthetic_D_100_K_50_L_8_200_iter_train_900_train_size.pkl'
 
     n_upd_iter = 10
-    update_size = 1
+    update_size = 10
 
     if not saved_file_name:
         active_learning_experiments = ActiveLearningExperiments(update_size=update_size)
@@ -162,17 +162,12 @@ if __name__=='__main__':
     #    with open('synthetic_D_100_K_50_L_8_200_iter_train_900_train_size.pkl', 'wb') as f:
     #        pickle.dump(active_learning_experiments, f)
 
-    print('freq loss {}'.format(active_learning_experiments.freq_validation_loss))
-    print('bayes loss {}'.format(active_learning_experiments.non_active_shared_bayesian_validation_loss))
-    print('active bayes loss {}'.format(active_learning_experiments.active_bayesian_validation_loss))
 
-    active_learning_experiments.update_size = update_size
+    for i in trange(n_upd_iter):
+        active_learning_experiments.choose_next_random_from_pool()
+        active_learning_experiments.choose_next_train_active_from_pool()
+        for j in range(50):
+            active_learning_experiments.learning_iter()
+        active_learning_experiments.update_quality()
 
-    # for i in trange(n_upd_iter):
-    #     active_learning_experiments.choose_next_random_from_pool()
-    #     active_learning_experiments.choose_next_train_active_from_pool()
-    #     for j in range(200):
-    #         active_learning_experiments.learning_iter()
-    #     active_learning_experiments.update_quality()
-    #
-    # active_learning_experiments.plot()
+    active_learning_experiments.plot()

### 2018-03-08 theano/experiments/active_learning/mnist_test_2.py

@@ -29,7 +29,7 @@ class ActiveLearningExperiments(object):
 
     def get_mnist_data_active_learning(self):
         self.K=100
-        n_train, n_pool, n_test = 50, 100, 100
+        n_train, n_pool, n_test = 50, 500, 100
         data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
         data.check_download()
         data.learn_dictionary()
@@ -162,17 +162,25 @@ if __name__=='__main__':
     #    with open('synthetic_D_100_K_50_L_8_200_iter_train_900_train_size.pkl', 'wb') as f:
     #        pickle.dump(active_learning_experiments, f)
 
-    print('freq loss {}'.format(active_learning_experiments.freq_validation_loss))
-    print('bayes loss {}'.format(active_learning_experiments.non_active_shared_bayesian_validation_loss))
-    print('active bayes loss {}'.format(active_learning_experiments.active_bayesian_validation_loss))
 
-    active_learning_experiments.update_size = update_size
+    for i in trange(n_upd_iter):
+        active_learning_experiments.choose_next_random_from_pool()
+        active_learning_experiments.choose_next_train_active_from_pool()
+        for j in range(10):
+            active_learning_experiments.learning_iter()
+        active_learning_experiments.update_quality()
 
-    # for i in trange(n_upd_iter):
-    #     active_learning_experiments.choose_next_random_from_pool()
-    #     active_learning_experiments.choose_next_train_active_from_pool()
-    #     for j in range(200):
-    #         active_learning_experiments.learning_iter()
-    #     active_learning_experiments.update_quality()
-    #
-    # active_learning_experiments.plot()
+    active_learning_experiments.plot()
+
+    freq_validation_loss = active_learning_experiments.freq_validation_loss
+    non_active_bayes_validation_loss = active_learning_experiments.non_active_shared_bayesian_validation_loss
+    active_bayes_validation_loss = active_learning_experiments.active_bayesian_validation_loss
+    freq_validation_f_measure = active_learning_experiments.freq_validation_f_meas
+    non_active_bayes_validation_f_measure = active_learning_experiments.non_active_shared_bayesian_validation_f_meas
+    active_bayes_validation_f_measure = active_learning_experiments.active_bayesian_validation_f_meas
+    np.savez('mnist_active_test_2', freq_validation_loss=freq_validation_loss,
+             non_active_bayes_validation_loss=non_active_bayes_validation_loss,
[…]

### 2018-03-08 theano/experiments/active_learning/mnist_test_2_rseed_10.py

@@ -29,7 +29,7 @@ class ActiveLearningExperiments(object):
 
     def get_mnist_data_active_learning(self):
         self.K=100
-        n_train, n_pool, n_test = 50, 100, 100
+        n_train, n_pool, n_test = 50, 500, 100
         data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
         data.check_download()
         data.learn_dictionary()
@@ -143,7 +143,7 @@ if __name__=='__main__':
     #
     # active_learning_experiments.plot()
 
-    rseed = 1
+    rseed = 10
     np.random.seed(rseed)
     tf.set_random_seed(rseed)
 
@@ -162,17 +162,25 @@ if __name__=='__main__':
     #    with open('synthetic_D_100_K_50_L_8_200_iter_train_900_train_size.pkl', 'wb') as f:
     #        pickle.dump(active_learning_experiments, f)
 
-    print('freq loss {}'.format(active_learning_experiments.freq_validation_loss))
-    print('bayes loss {}'.format(active_learning_experiments.non_active_shared_bayesian_validation_loss))
-    print('active bayes loss {}'.format(active_learning_experiments.active_bayesian_validation_loss))
 
-    active_learning_experiments.update_size = update_size
+    for i in trange(n_upd_iter):
+        active_learning_experiments.choose_next_random_from_pool()
+        active_learning_experiments.choose_next_train_active_from_pool()
+        for j in range(10):
+            active_learning_experiments.learning_iter()
+        active_learning_experiments.update_quality()
 
-    # for i in trange(n_upd_iter):
-    #     active_learning_experiments.choose_next_random_from_pool()
-    #     active_learning_experiments.choose_next_train_active_from_pool()
-    #     for j in range(200):
-    #         active_learning_experiments.learning_iter()
-    #     active_learning_experiments.update_quality()
-    #
-    # active_learning_experiments.plot()
+    active_learning_experiments.plot()
+
+    freq_validation_loss = active_learning_experiments.freq_validation_loss
+    non_active_bayes_validation_loss = active_learning_experiments.non_active_shared_bayesian_validation_loss
+    active_bayes_validation_loss = active_learning_experiments.active_bayesian_validation_loss
+    freq_validation_f_measure = active_learning_experiments.freq_validation_f_meas
+    non_active_bayes_validation_f_measure = active_learning_experiments.non_active_shared_bayesian_validation_f_meas
[…]

### 2018-03-08 theano/experiments/active_learning/mnist_test_2_rseed_6.py

@@ -29,7 +29,7 @@ class ActiveLearningExperiments(object):
 
     def get_mnist_data_active_learning(self):
         self.K=100
-        n_train, n_pool, n_test = 50, 100, 100
+        n_train, n_pool, n_test = 50, 500, 100
         data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
         data.check_download()
         data.learn_dictionary()
@@ -143,7 +143,7 @@ if __name__=='__main__':
     #
     # active_learning_experiments.plot()
 
-    rseed = 1
+    rseed = 6
     np.random.seed(rseed)
     tf.set_random_seed(rseed)
 
@@ -162,17 +162,25 @@ if __name__=='__main__':
     #    with open('synthetic_D_100_K_50_L_8_200_iter_train_900_train_size.pkl', 'wb') as f:
     #        pickle.dump(active_learning_experiments, f)
 
-    print('freq loss {}'.format(active_learning_experiments.freq_validation_loss))
-    print('bayes loss {}'.format(active_learning_experiments.non_active_shared_bayesian_validation_loss))
-    print('active bayes loss {}'.format(active_learning_experiments.active_bayesian_validation_loss))
 
-    active_learning_experiments.update_size = update_size
+    for i in trange(n_upd_iter):
+        active_learning_experiments.choose_next_random_from_pool()
+        active_learning_experiments.choose_next_train_active_from_pool()
+        for j in range(10):
+            active_learning_experiments.learning_iter()
+        active_learning_experiments.update_quality()
 
-    # for i in trange(n_upd_iter):
-    #     active_learning_experiments.choose_next_random_from_pool()
-    #     active_learning_experiments.choose_next_train_active_from_pool()
-    #     for j in range(200):
-    #         active_learning_experiments.learning_iter()
-    #     active_learning_experiments.update_quality()
-    #
-    # active_learning_experiments.plot()
+    active_learning_experiments.plot()
+
+    freq_validation_loss = active_learning_experiments.freq_validation_loss
+    non_active_bayes_validation_loss = active_learning_experiments.non_active_shared_bayesian_validation_loss
+    active_bayes_validation_loss = active_learning_experiments.active_bayesian_validation_loss
+    freq_validation_f_measure = active_learning_experiments.freq_validation_f_meas
+    non_active_bayes_validation_f_measure = active_learning_experiments.non_active_shared_bayesian_validation_f_meas
[…]

### 2018-03-08 theano/experiments/active_learning/mnist_test_2_rseed_7.py

@@ -29,7 +29,7 @@ class ActiveLearningExperiments(object):
 
     def get_mnist_data_active_learning(self):
         self.K=100
-        n_train, n_pool, n_test = 50, 100, 100
+        n_train, n_pool, n_test = 50, 500, 100
         data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
         data.check_download()
         data.learn_dictionary()
@@ -143,7 +143,7 @@ if __name__=='__main__':
     #
     # active_learning_experiments.plot()
 
-    rseed = 1
+    rseed = 7
     np.random.seed(rseed)
     tf.set_random_seed(rseed)
 
@@ -162,17 +162,25 @@ if __name__=='__main__':
     #    with open('synthetic_D_100_K_50_L_8_200_iter_train_900_train_size.pkl', 'wb') as f:
     #        pickle.dump(active_learning_experiments, f)
 
-    print('freq loss {}'.format(active_learning_experiments.freq_validation_loss))
-    print('bayes loss {}'.format(active_learning_experiments.non_active_shared_bayesian_validation_loss))
-    print('active bayes loss {}'.format(active_learning_experiments.active_bayesian_validation_loss))
 
-    active_learning_experiments.update_size = update_size
+    for i in trange(n_upd_iter):
+        active_learning_experiments.choose_next_random_from_pool()
+        active_learning_experiments.choose_next_train_active_from_pool()
+        for j in range(10):
+            active_learning_experiments.learning_iter()
+        active_learning_experiments.update_quality()
 
-    # for i in trange(n_upd_iter):
-    #     active_learning_experiments.choose_next_random_from_pool()
-    #     active_learning_experiments.choose_next_train_active_from_pool()
-    #     for j in range(200):
-    #         active_learning_experiments.learning_iter()
-    #     active_learning_experiments.update_quality()
-    #
-    # active_learning_experiments.plot()
+    active_learning_experiments.plot()
+
+    freq_validation_loss = active_learning_experiments.freq_validation_loss
+    non_active_bayes_validation_loss = active_learning_experiments.non_active_shared_bayesian_validation_loss
+    active_bayes_validation_loss = active_learning_experiments.active_bayesian_validation_loss
+    freq_validation_f_measure = active_learning_experiments.freq_validation_f_meas
+    non_active_bayes_validation_f_measure = active_learning_experiments.non_active_shared_bayesian_validation_f_meas
[…]

### 2018-03-08 theano/experiments/active_learning/mnist_test_2_rseed_8.py

@@ -29,7 +29,7 @@ class ActiveLearningExperiments(object):
 
     def get_mnist_data_active_learning(self):
         self.K=100
-        n_train, n_pool, n_test = 50, 100, 100
+        n_train, n_pool, n_test = 50, 500, 100
         data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
         data.check_download()
         data.learn_dictionary()
@@ -143,7 +143,7 @@ if __name__=='__main__':
     #
     # active_learning_experiments.plot()
 
-    rseed = 1
+    rseed = 8
     np.random.seed(rseed)
     tf.set_random_seed(rseed)
 
@@ -162,17 +162,25 @@ if __name__=='__main__':
     #    with open('synthetic_D_100_K_50_L_8_200_iter_train_900_train_size.pkl', 'wb') as f:
     #        pickle.dump(active_learning_experiments, f)
 
-    print('freq loss {}'.format(active_learning_experiments.freq_validation_loss))
-    print('bayes loss {}'.format(active_learning_experiments.non_active_shared_bayesian_validation_loss))
-    print('active bayes loss {}'.format(active_learning_experiments.active_bayesian_validation_loss))
 
-    active_learning_experiments.update_size = update_size
+    for i in trange(n_upd_iter):
+        active_learning_experiments.choose_next_random_from_pool()
+        active_learning_experiments.choose_next_train_active_from_pool()
+        for j in range(10):
+            active_learning_experiments.learning_iter()
+        active_learning_experiments.update_quality()
 
-    # for i in trange(n_upd_iter):
-    #     active_learning_experiments.choose_next_random_from_pool()
-    #     active_learning_experiments.choose_next_train_active_from_pool()
-    #     for j in range(200):
-    #         active_learning_experiments.learning_iter()
-    #     active_learning_experiments.update_quality()
-    #
-    # active_learning_experiments.plot()
+    active_learning_experiments.plot()
+
+    freq_validation_loss = active_learning_experiments.freq_validation_loss
+    non_active_bayes_validation_loss = active_learning_experiments.non_active_shared_bayesian_validation_loss
+    active_bayes_validation_loss = active_learning_experiments.active_bayesian_validation_loss
+    freq_validation_f_measure = active_learning_experiments.freq_validation_f_meas
+    non_active_bayes_validation_f_measure = active_learning_experiments.non_active_shared_bayesian_validation_f_meas
[…]

### 2018-03-08 theano/experiments/active_learning/mnist_test_2_rseed_9.py

@@ -29,7 +29,7 @@ class ActiveLearningExperiments(object):
 
     def get_mnist_data_active_learning(self):
         self.K=100
-        n_train, n_pool, n_test = 50, 100, 100
+        n_train, n_pool, n_test = 50, 500, 100
         data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
         data.check_download()
         data.learn_dictionary()
@@ -143,7 +143,7 @@ if __name__=='__main__':
     #
     # active_learning_experiments.plot()
 
-    rseed = 1
+    rseed = 9
     np.random.seed(rseed)
     tf.set_random_seed(rseed)
 
@@ -162,17 +162,25 @@ if __name__=='__main__':
     #    with open('synthetic_D_100_K_50_L_8_200_iter_train_900_train_size.pkl', 'wb') as f:
     #        pickle.dump(active_learning_experiments, f)
 
-    print('freq loss {}'.format(active_learning_experiments.freq_validation_loss))
-    print('bayes loss {}'.format(active_learning_experiments.non_active_shared_bayesian_validation_loss))
-    print('active bayes loss {}'.format(active_learning_experiments.active_bayesian_validation_loss))
 
-    active_learning_experiments.update_size = update_size
+    for i in trange(n_upd_iter):
+        active_learning_experiments.choose_next_random_from_pool()
+        active_learning_experiments.choose_next_train_active_from_pool()
+        for j in range(10):
+            active_learning_experiments.learning_iter()
+        active_learning_experiments.update_quality()
 
-    # for i in trange(n_upd_iter):
-    #     active_learning_experiments.choose_next_random_from_pool()
-    #     active_learning_experiments.choose_next_train_active_from_pool()
-    #     for j in range(200):
-    #         active_learning_experiments.learning_iter()
-    #     active_learning_experiments.update_quality()
-    #
-    # active_learning_experiments.plot()
+    active_learning_experiments.plot()
+
+    freq_validation_loss = active_learning_experiments.freq_validation_loss
+    non_active_bayes_validation_loss = active_learning_experiments.non_active_shared_bayesian_validation_loss
+    active_bayes_validation_loss = active_learning_experiments.active_bayesian_validation_loss
+    freq_validation_f_measure = active_learning_experiments.freq_validation_f_meas
+    non_active_bayes_validation_f_measure = active_learning_experiments.non_active_shared_bayesian_validation_f_meas
[…]

### 2018-03-08 theano/experiments/active_learning/mnist_test_3.py

@@ -29,7 +29,7 @@ class ActiveLearningExperiments(object):
 
     def get_mnist_data_active_learning(self):
         self.K=100
-        n_train, n_pool, n_test = 50, 100, 100
+        n_train, n_pool, n_test = 50, 500, 100
         data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
         data.check_download()
         data.learn_dictionary()
@@ -150,7 +150,7 @@ if __name__=='__main__':
     saved_file_name = []#'synthetic_D_100_K_50_L_8_200_iter_train_900_train_size.pkl'
 
     n_upd_iter = 10
-    update_size = 1
+    update_size = 5
 
     if not saved_file_name:
         active_learning_experiments = ActiveLearningExperiments(update_size=update_size)
@@ -162,17 +162,12 @@ if __name__=='__main__':
     #    with open('synthetic_D_100_K_50_L_8_200_iter_train_900_train_size.pkl', 'wb') as f:
     #        pickle.dump(active_learning_experiments, f)
 
-    print('freq loss {}'.format(active_learning_experiments.freq_validation_loss))
-    print('bayes loss {}'.format(active_learning_experiments.non_active_shared_bayesian_validation_loss))
-    print('active bayes loss {}'.format(active_learning_experiments.active_bayesian_validation_loss))
 
-    active_learning_experiments.update_size = update_size
+    for i in trange(n_upd_iter):
+        active_learning_experiments.choose_next_random_from_pool()
+        active_learning_experiments.choose_next_train_active_from_pool()
+        for j in range(50):
+            active_learning_experiments.learning_iter()
+        active_learning_experiments.update_quality()
 
-    # for i in trange(n_upd_iter):
-    #     active_learning_experiments.choose_next_random_from_pool()
-    #     active_learning_experiments.choose_next_train_active_from_pool()
-    #     for j in range(200):
-    #         active_learning_experiments.learning_iter()
-    #     active_learning_experiments.update_quality()
-    #
-    # active_learning_experiments.plot()
+    active_learning_experiments.plot()

### 2018-03-08 theano/experiments/mnist/collect_results.py

@@ -1,0 +1,166 @@
+import errno
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+
+class MnistExperimentResultsCollector(object):
+    def __init__(self):
+        self.n_iter = 500
+
+    def collect_all(self):
+        self.ista_f_meas_train, self.ista_f_meas_validation, self.ista_loss_train, self.ista_loss_validation, \
+        self.ista_f_meas_train_std, self.ista_f_meas_validation_std, self.ista_loss_train_std, self.ista_loss_validation_std = \
+            self.collect_ista_fista('ista')
+        self.fista_f_meas_train, self.fista_f_meas_validation, self.fista_loss_train, self.fista_loss_validation, \
+        self.fista_f_meas_train_std, self.fista_f_meas_validation_std, self.fista_loss_train_std, self.fista_loss_validation_std, = \
+            self.collect_ista_fista('fista')
+        self.freq_f_meas_train, self.freq_f_meas_validation, self.freq_loss_train, self.freq_loss_validation, \
+        self.freq_f_meas_train_std, self.freq_f_meas_validation_std, self.freq_loss_train_std, self.freq_loss_validation_std = \
+            self.collect_main('freq')
+        self.sh_bayes_f_meas_train, self.sh_bayes_f_meas_validation, self.sh_bayes_loss_train, self.sh_bayes_loss_validation,\
+        self.sh_bayes_f_meas_train_std, self.sh_bayes_f_meas_validation_std, self.sh_bayes_loss_train_std, self.sh_bayes_loss_validation_std = \
+            self.collect_main('sh_bayes')
+
+    def collect(self, filename_prefix):
+        saved_bayes_weights = np.load('{}_bayes_weights.npz'.format(filename_prefix))
+        bayes_S_M = saved_bayes_weights['bayes_S_M']
+        bayes_S_V = saved_bayes_weights['bayes_S_V']
+        bayes_W_M = saved_bayes_weights['bayes_W_M']
+        bayes_W_V = saved_bayes_weights['bayes_W_V']
+
+        saved_beta_est = np.load('{}_beta_est.npz'.format(filename_prefix))
+        freq_beta_train_est=saved_beta_est['freq_beta_train_est']
+        freq_beta_validation_est=saved_beta_est['freq_beta_validation_est']
+        shared_beta_train_est=saved_beta_est['shared_beta_train_est']
+        shared_beta_validation_est=saved_beta_est['shared_beta_validation_est']
[…]

### 2018-03-08 theano/experiments/mnist/mnist_100_train_20_layers_K_250_script_ista_fista.py

@@ -1,0 +1,55 @@
+import errno
+import numpy as np
+import six.moves.cPickle as pickle
+
+import matplotlib.pyplot as plt
+from tqdm import tqdm, trange
+
+import os
+
+from compare_freq_bayes.compare_sequential_with_ista_fista import SequentialComparatorIstaFista
+from experiments.synthetic.experiments_parameters import load_long_experiment
+from compare_mnist.mnist_data import MnistData
+
+class MnistSequentialComparatorIstaFista(SequentialComparatorIstaFista):
+    def __init__(self, K, L, learning_rate=0.0001, n_train_sample=1, n_validation_sample=1,
+                 train_freq=False, train_bayes=False, train_shared_bayes=False, use_ista=True, use_fista=True, save_history=False):
+
+        self.data = MnistData(K=K)
+        self.data.check_download()
+        self.data.learn_dictionary()
+        self.D = self.data.train_data.shape[1]
+
+        super().__init__(self.D, K, L, learning_rate, n_train_sample, n_validation_sample,
+                 train_freq, train_bayes, train_shared_bayes, use_ista, use_fista, save_history)
+
+        self.beta_train = self.data.train_data
+        self.y_train = self.data.y_train
+        self.beta_validation = self.data.validation_data
+        self.y_validation = self.data.y_validation
+
+
+if __name__ == '__main__':
+    try:
+        os.makedirs('ista_fista')
+    except OSError as e:
+        if e.errno != errno.EEXIST:
+            raise
+
+    np.random.seed(1)
+
+    K = 100
+    L = 20
+
+    comparator = MnistSequentialComparatorIstaFista(K, L, learning_rate=0.0001, n_train_sample=100,
+                                      n_validation_sample=100, train_freq=False,
+                                      train_bayes=False, train_shared_bayes=False, use_ista=True, use_fista=True, save_history=True)
+    n_iter = 500
+
+    for _ in tqdm(range(n_iter)):
+        comparator.train_iteration()
+
+    comparator.plot_quality_history()
+
+
+    comparator.save_numpy('ista_fista/results')

### 2018-03-08 theano/experiments/mnist/saving_mnist_output.py

@@ -1,0 +1,27 @@
+freq_train_loss = comparator.freq_train_loss
+freq_validation_loss = comparator.freq_validation_loss
+shared_bayesian_train_loss = comparator.shared_bayesian_train_loss
+shared_bayesian_validation_loss = comparator.shared_bayesian_validation_loss
+freq_train_f_measure = comparator.freq_train_f_meas
+freq_validation_f_measure = comparator.freq_validation_f_meas
+shared_bayesian_f_measure = comparator.shared_bayesian_train_f_meas
+shared_bayesian_train_f_measure = comparator.shared_bayesian_train_f_meas
+shared_bayesian_validation_f_measure = comparator.shared_bayesian_validation_f_meas
+freq_beta_train_est = comparator.freq_lista.predict(comparator.data.y_train)
+freq_beta_validation_est = comparator.freq_lista.predict(comparator.data.y_validation)
+shared_beta_train_est = comparator.shared_bayesian_lista.predict(comparator.data.y_train)
+shared_beta_validation_est = comparator.shared_bayesian_lista.predict(comparator.data.y_validation)
+true_beta_train = comparator.data.train_data
+true_beta_validation = comparator.data.validation_data
+y_train = comparator.data.y_train
+y_validation = comparator.data.y_validation
+D = comparator.data.train_data.shape[1]
+train_size = comparator.data.train_data.shape[0]
+bayes_W_M = comparator.shared_bayesian_lista.pbp_instance.network.params_W_M.get_value()
+bayes_W_V = comparator.shared_bayesian_lista.pbp_instance.network.params_W_V.get_value()
+bayes_S_M = comparator.shared_bayesian_lista.pbp_instance.network.params_S_M.get_value()
+bayes_S_V = comparator.shared_bayesian_lista.pbp_instance.network.params_S_V.get_value()
+np.savez('mnist_100_train_20_layers_K_250_bayes_weights', D = D, K = K, L = L, bayes_S_M = bayes_S_M, bayes_S_V = bayes_S_V, bayes_W_M = bayes_W_M, bayes_W_V = bayes_W_V)
[…]

### 2018-03-08 paper/BayesianLISTA.tex
added second synthetic experiment

@@
 
-In the Figure \ref{fig:number_of_layers_synthetic} prediction performance for increasing number of layers is presented. The proposed algorithm is superior in terms of NMSE
+In the Figure \ref{fig:number_of_layers_synthetic} prediction performance for different number of layers $L$ is presented. The observation size is set as $K=50$.
 
-\begin{figure*}[t]
-\subfloat[NMSE on train]{\includegraphics{graphics/synthetic_number_of_layers/nmse_train}}
+In the Figure \ref{fig:unsersampling_synthetic} prediction performance for different observation sizes $K$ is presented. The number of layers is set as $L=4$.
+
+\begin{figure}[t]
+\subfloat[NMSE on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
 ~
-\subfloat[NMSE on validation]{\includegraphics{graphics/synthetic_number_of_layers/nmse_validation}}
+\subfloat[NMSE on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}}
 \newline
-\subfloat[F measure on train]{\includegraphics{graphics/synthetic_number_of_layers/f_measure_train}}
+\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
 ~
-\subfloat[F measure on validation]{\includegraphics{graphics/synthetic_number_of_layers/f_measure_validation}}
+\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}}
 \caption{Number of layers on synthetic data}
 \label{fig:number_of_layers_synthetic}
-\end{figure*}
+\end{figure}
 
-We compare two versions of the proposed Bayesian LISTA: with shared weight matrices and with individual matrices at each layer --- and LISTA.
+\begin{figure}[t]
+\subfloat[NMSE on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_train}}
+~
+\subfloat[NMSE on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_validation}}
+\newline
+\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
+~
+\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}}
+\caption{Size of observations on synthetic data}
+\label{fig:unsersampling_synthetic}
+\end{figure}
+
+%We compare two versions of the proposed Bayesian LISTA: with shared weight matrices and with individual matrices at each layer --- and LISTA.
 

### 2018-03-08 paper/BayesianLISTA.tex
updatees to tex

@@
 
+\usepackage{natbib}
+
 \newtheorem{theorem}{Theorem}
 \newtheorem{lemma}{Lemma}
+
+\allowdisplaybreaks
 
@@
 \section{Introduction}
-Though the idea of Bayesian learning in neural networks is not new \cite{neal2012bayesian}, it has gained its attention only recently, with the development of distributed approximate inference techniques \cite{li2015stochastic, hoffman2013stochastic}  and general boost in popularity of deep learning.
+Though the idea of Bayesian learning in neural networks is not new \citep{neal2012bayesian}, it has gained its attention only recently, with the development of distributed approximate inference techniques \citep{li2015stochastic, hoffman2013stochastic}  and general boost in popularity of deep learning.
 In some spheres, such as self-driving cars or healthcare, posterior estimates are very important and Bayesian learning allows to obtain them.
 
-In general, when distributions are included in the network, Bayesian inference complexity scales exponentially with the number of layers, thus making it impossible to be implemented for deep neural networks in general.
+In general, when distributions are included in the network, Bayesian inference complexity scales exponentially with the number of layers, thus making it difficult to be implemented for deep neural networks in general.
 Nevertheless, recently several techniques were proposed to handle specific types of neural networks.
-For example, dense layers \cite{hernandez2015probabilistic}, networks with discrete distributions \cite{soudry2014expectation}, recurrent networks \cite{mcdermott2017bayesian}.
+For example, dense layers \citep{hernandez2015probabilistic}, networks with discrete distributions \citep{soudry2014expectation}, recurrent networks \citep{mcdermott2017bayesian}.
 
-There are currently two approaches for Bayesian neural networks: including distributions of weights in the network \cite{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing the uncertainty \cite{gal2016dropout}.
-We are using the first way.
+There are currently two approaches for Bayesian neural networks: distributions of weights can be included in the network \citep{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing the uncertainty \citep{gal2016dropout}.
+In this paper we are using the first way and impose distributions on weights and parameters to obtain posterior estimates of parameters, weights and predictions with uncertainty estimated.
 
+Sparse coding problem can be viewed as the linear regression problem with the additional assumption that some of the basis representation coefficients should be zeros.
+It arises in different applications, such as compressive sensing~\cite{candes2008introduction}, image and video processing~\cite{mairal2014sparse}, non-invasive brain activity areas discovery \cite{baillet1997bayesian}.
+
+The usual approach in neural networks for sparse coding is to use the soft thresholding nonlinearity, that shifts current estimates towards zero \citep{lecun2010mnist}.
+It allows to obtain predictions containing zeros.
 In this paper we propose the approach to propagate uncertainty through the soft-thresholding nonlinearity.
-At every layer the current distribution of the target vector is represented as spike-and-slab distribution, this can be effectively combined with Gaussian weights for dense layers and after soft-thresholding it can be closely approximated with distribution from the same family.
+At every layer the current distribution of the target vector is represented as spike-and-slab distribution \citep{mitchell1988bayesian}, and we show that it can be effectively combined with Gaussian weights for dense layers and after soft-thresholding it can be closely approximated with distribution from the same family.
+
+The proposed method of uncertainty propagation for sparse coding allows to derive the gradients of the normalisation constant logarithm of the model likelihood which is used in probabilistic backpropagation to update weights distribution, therefore it can be applied to Bayesian neural networks for sparse coding.
 
 The paper is organised as following: first, we describe the uncertainty propagation to obtain the spike-and-slab distribution - output from the network, then we describe how the backpropagation is organised to update distributions of weights and their priors.
-After that we show how the algorithm is performed on MNIST data and demonstrate the obtained posterior estimates.
-
-Soft thresholding usually appears in LISTA network \cite{gregor2010learning}, so we present our algorithm for it.
+After that we show how the algorithm is performed on \textsc{mnist} data and demonstrate the obtained posterior estimates.
 
@@
 \item efficient posterior inference for weights and outputs of neural networks with the soft-thresholding nonlinearity
-\item novel Bayesian LISTA network for sparse coding
+\item novel Bayesian neural network network for sparse coding
 \end{itemize}
 
-\section{LISTA}
+\section{Neural networks for sparse coding}
 
-LISTA neural network was proposed for sparse coding to mimic the iterative thresholding algorithms.
-The current estimate is iteratively combined with the design matrix and then thresholded.
-Soft thresholding operator for input $v$ with parameter $\lambda$ is defined as
-\begin{equation}
-h_\lambda(v) = \text{sgn}(v) * \max(|v| - \lambda, 0)
-\end{equation} 
-When this process is limited to the predefined set of iterations and weights of design matrix combinations are learnt, this can be interpreted as a neural network.
-
-The problem is an underdefined linear regression with assumption of sparse weights:
+The problem of sparse coding is the linear regression with assumption of sparse weights
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{y}$ are observations, $\mathbf{X}$ is design matrix, $\boldsymbol\beta$ is unknown vector of weights larger than $\mathbf{y}$ with some of the elements equal to zero to achieve regularisation.
-$\varepsilon$ is Gaussian noise.
+where $\mathbf{y} \in \mathbb{R}^K$ is the observation, $\mathbf{X} \in \mathbb{R}^{K \times D}$ is the design matrix, $\boldsymbol\beta \in \mathbb{R}^D$ is unknown vector of weights such that $K < D$ with some of its elements $\beta_d$ equal to zero to achieve regularisation.
+$\varepsilon \in \mathbb{R}^K$ is the independent Gaussian noise.
 
-LISTA network has the following scheme
+One of the popular families of the sparse coding algorithms is the iterative shrinkage algorithms, and notably the Iterative Shrinkage and Thresholding Algorithm(\textsc{ista}) \citep{daubechies2004iterative}.
+It iteratively obtains the new approximation of the coefficients vector $\widehat{\boldsymbol\beta}_l$ as the linear transformation of the input $\mathbf{y}$ with previous approximation $\widehat{\boldsymbol\beta}_{l-1}$ and then propagates the new approximation through the soft thresholding function $h_\lambda(\cdot)$
+\begin{equation}
+h_\lambda(v) = \text{sgn}(v) \max(|v| - \lambda, 0)
+\end{equation}
+where $\lambda$ is a shrinkage parameter.
+The linear transformation is
+\begin{equation}
+\widehat{\boldsymbol\beta}_l = \mathbf{W}\mathbf{y} + \mathbf{S}_l\widehat{\boldsymbol\beta}_{l-1}
+\end{equation}
+with weights $\mathbf{W} = \mathbf{X}^\top / E$, $E$ - upper bound on the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$ and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$.
+
+Learned \textsc{ista} (\textsc{lista}) \citep{gregor2010learning} algorithm allows to learn the values of matrices $\mathbf{W}$, $\mathbf{S}$.
+To achieve this, \textsc{ista} algorithm is limited with the fixed amount of iterations, $L$ and interpreted as a recurrent neural network.
+Overall, it has the following scheme
 \begin{align}
-&\mathbf{b}_0 = \mathbf{W}_0\mathbf{y}\\
+&\mathbf{b} = \mathbf{W}\mathbf{y}\\
 &\widehat{\boldsymbol\beta}_0 = h_\lambda(\mathbf{b}_0) \\
 &\text{for } l=1:L\\
-	&\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y} \\
-	&\quad \mathbf{c}_l = \mathbf{b}_l + \mathbf{S}_l\widehat{\boldsymbol\beta}_{l-1} \\
+	&\quad \mathbf{c}_l = \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1} \\
 	&\quad \widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l) \\
@@
 
-Matrices $\mathbf{W}_l \in \mathbb{R}^{D \times K}$, $\mathbf{S}_l\in\mathbb{R}^{D \times D}$ are the parameters that are learnt in LISTA.
-Vectors $\mathbf{c}_l$, $\mathbf{b}_l$ are intermediate vectors that describe propagation within the layer.
+Matrices $\mathbf{W}$, $\mathbf{S}$ are the parameters that are initialised as in \textsc{ista} and then updated with the backpropagation algorithm.
+Vectors $\mathbf{c}_l$, $\mathbf{b}$ are intermediate vectors that describe forward propagation.
 $\boldsymbol\beta_l$ is the current approximation of the target coefficients vector.
 
-\section{Bayesian LISTA}
-To formulate the Bayesian LISTA we start with putting the prior distributions on the unknown weights
+\section{Bayesian neural network for sparse coding}
+To formulate the Bayesian version of \textsc{lista} we impose the prior distributions on the unknown weights
 \begin{align}
-&p(\mathbf{W}) = \prod_{l=1}^L\prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij, l} | 0, \eta^{-1}), \\
-&p(\mathbf{S}) = \prod_{l=1}^L\prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd'', l} | 0, \eta^{-1}),
+&p(\mathbf{W}) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij, l} | 0, \eta^{-1}), \\
+&p(\mathbf{S}) = \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd'', l} | 0, \eta^{-1}),
 \end{align}
@@
 \end{equation}
-where $f(\mathbf{y}; \mathbf{W}, \mathbf{S})$ is the output of the LISTA neural network.
+where $f(\mathbf{y}; \mathbf{W}, \mathbf{S})$ is the output of the \textsc{lista} neural network.
 The posterior distribution is 
@@
 \end{equation}
+The shrinkage parameter $\lambda$ is a hyperparameter of the model.
 
@@
 
-Further in this section we show that the value of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with spike and slab distribution and therefore it maintains the same family of distributions and allows to apply the extended probabilistic backpropagation algorithm that is proposed in Section~\ref{sec:backpropagation}: lemma \ref{thm:matrix_const} describes the probabilistic variant of LISTA step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of LISTA step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$.
+Further in this section we show that the value of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with spike and slab distribution and therefore it maintains the same family of distributions and allows to apply the extended probabilistic backpropagation algorithm that is proposed in Section~\ref{sec:backpropagation}: lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$.
 Overall the probabilistic layer is described by theorem \ref{thm:prob_layer}.
@@
 The proposed operations on Gaussian and spike-and-slab distributions allow to formulate the main result in this section that describes how the uncertainty propagation works.
-\begin{theorem}[Bayesian LISTA forward propagation]
+\begin{theorem}[Bayesian \textsc{lista} forward propagation]
 \label{thm:prob_layer}
-The spike and slab distribution for $\boldsymbol\beta_{l-1}$ with parameters ($\boldsymbol\omega$, $\mathbf{m}$, $\mathbf{w}$) can be propagated through the LISTA layer and the parameters after propagation can be computed as following:
+The spike and slab distribution for $\boldsymbol\beta$ with can be propagated through the \textsc{lista} layer and the parameters after propagation can be computed as following:
 \begin{enumerate}
@@
 Figure \ref{fig:d_testing} demonstrates the comparison of the sampled distribution and approximated distribution for lemma \ref{thm:matrix_vector}.
-For sampled distribution, 10000 values were sampled from the Gaussian matrix and the Gaussian vector and their product was computed, then one of the dimensionalities was plotted.
+For sampled distribution, $10000$ values were sampled from the Gaussian matrix and the Gaussian vector and their product was computed, then one of the dimensionalities was plotted.
 The approximated distribution was computed according to lemma \ref{thm:matrix_vector}.
@@
 Figure \ref{fig:z_new_testing} demonstrates the comparison of the sampled distribution and approximated distribution for lemma \ref{thm:soft_thresholding}.
-For sampled distribution, 10000 values were sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities was plotted.
+For sampled distribution, $10000$ values were sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities was plotted.
 The approximated distribution was computed according to lemma \ref{thm:soft_thresholding}.
@@
 \subsection{Likelihood}
-The Student-t density, that is required for further derivation, can be parametrised in different ways. In this paper the following parametrisation is used 
+We use the probabilistic backpropagation algorithm \citep{hernandez2015probabilistic} for computing parameters updates.
+It is based on assumed density filtering and expectation propagation and allows to update parameters of the distributions based on the derivative of the logarithm of the normalisation constant.
+The exact posterior \ref{eq:posterior} is approximated with a factorised distribution
+\begin{align}
+\begin{split}
+q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk, l} | m^w_{dk, l}, v^w_{dk, l}) \\
+&\times \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd'', l} | m^s_{d'd'', l}, v^s_{d'd'', l}) \\
+&\times \text{Gam}(\gamma; \alpha^\gamma, \beta^\gamma) \text{Gam}(\eta; \alpha^\eta, \beta^\eta) 
+\end{split}
+\end{align}
+The normalisation constant of the approximating distribution $q$ with the likelihood~\ref{eq:likelihood} term incorporated can be computed as follows
+\begin{align}
+\label{eq:Z}
+\begin{split}
+Z = \int \prod_{d=1}^{D} \big[&\mathcal{N}(\beta_d | f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) \\
+ &q(\mathbf{S}, \mathbf{W}, \eta, \gamma)\big] \mathrm{d}\mathbf{S} \mathrm{d}\mathbf{W} \mathrm{d}\eta \mathrm{d}\gamma
+ \end{split}
+\end{align}
+We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\mathbf{z}_L$ - output from the network
+\begin{align}
+&Z \approx \int \prod_{d=1}^{D} \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1}) \nonumber \\
+&\times (\omega^{z_L}_d \delta_0([\mathbf{z}_L]_d) + (1 - \omega^{z_L}_d)\mathcal{N}(m^{z_L}_d, v^{z_L}_d)) \nonumber\\
+&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}\mathbf{z}_L \mathrm{d}\boldsymbol\gamma  \nonumber\\
+&= \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1})  \delta_0([z_L]_d) \nonumber \\
+&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[{z}_L]_d \mathrm{d}\gamma_d  \nonumber\\
+& + (1 - \omega^{z_L}_d)\int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1})\mathcal{N}(m^{z_L}_d, v^{z_L}_d))  \nonumber\\
+&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[{z}_L]_d \mathrm{d}\gamma_d\Big]  \nonumber\\
+& = \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \mathcal{N}(\beta_d | 0, \gamma_d^{-1})  \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma) d\gamma_d  \nonumber\\
+& + (1 - \omega^{z_L}_d)\int \big[\mathcal{T}(\beta_d | [\mathbf{z}_L]_d, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma)  \nonumber\\
+&\times \mathcal{N}(m^{z_L}_d, v^{z_L}_d))\big] \mathrm{d}[{z}_L]_d\Big]  \nonumber\\
+& \approx \prod_{d=1}^D \Big[\omega^{z_L}_d  \mathcal{T}(\beta_d | 0, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma) \nonumber \\ 
+\label{eq:Z_approx}
+&+ (1 - \omega^{z_L}_d)\mathcal{N}(m^{z_L}_d, \frac{\beta^\gamma}{\alpha^\gamma - 1} + v^{z_L})\Big]
+\end{align}
+
+The Student t density, can be parametrised in different ways. In this paper the following parametrisation is used 
 \begin{equation}
@@
 
-We use the probabilistic backpropagation algorithm \cite{hernandez2015probabilistic} for computing parameters updates.
-It is based on assumed density filtering and expectation propagation and allows to update parameters of the distributions based on the derivative of the logarithm of the normalisation constant.
-The exact posterior \ref{eq:posterior} is approximated with a factorised distribution
-\begin{align}
-\begin{split}
-q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{l=1}^L\prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk, l} | m^w_{dk, l}, v^w_{dk, l}) \\
-&\times \prod_{l=1}^L\prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd'', l} | m^s_{d'd'', l}, v^s_{d'd'', l}) \\
-&\times \text{Gam}(\gamma; \alpha^\gamma, \beta^\gamma) \text{Gam}(\eta; \alpha^\eta, \beta^\eta) 
-\end{split}
-\end{align}
-The normalisation constant of the approximating distribution $q$ with the likelihood~\ref{eq:likelihood} term incorporated can be computed as follows
-\begin{align}
-Z = \int \prod_{d=1}^{D} \big[&\mathcal{N}(\beta_d | f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) \\
- &q(\mathbf{S}, \mathbf{W}, \eta, \gamma)\big] \mathrm{d}\mathbf{S} \mathrm{d}\mathbf{W} \mathrm{d}\eta \mathrm{d}\gamma
-\end{align}
-We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\mathbf{z}_L$ - output from the network
-\begin{align}
-\begin{split}
-&Z \approx \int \prod_{d=1}^{D} \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1}) \\
-&\times (\omega^{z_L}_d \delta_0([\mathbf{z}_L]_d) + (1 - \omega^{z_L}_d)\mathcal{N}(m^{z_L}_d, v^{z_L}_d))\\
-&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}\mathbf{z}_L \mathrm{d}\boldsymbol\gamma \\
-&= \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1})  \delta_0([z_L]_d) \\
-&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[{z}_L]_d \mathrm{d}\gamma_d \\
-& + (1 - \omega^{z_L}_d)\int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1})\mathcal{N}(m^{z_L}_d, v^{z_L}_d)) \\
-&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[{z}_L]_d \mathrm{d}\gamma_d\Big] \\
-& = \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \mathcal{N}(\beta_d | 0, \gamma_d^{-1})  \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma) d\gamma_d \\
-& + (1 - \omega^{z_L}_d)\int \big[\mathcal{T}(\beta_d | [\mathbf{z}_L]_d, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma) \\
-&\times \mathcal{N}(m^{z_L}_d, v^{z_L}_d))\big] \mathrm{d}[{z}_L]_d\Big] \\
-& \approx \prod_{d=1}^D \Big[\omega^{z_L}_d  \mathcal{T}(\beta_d | 0, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma) \\
-&+ (1 - \omega^{z_L}_d)\mathcal{N}(m^{z_L}_d, \frac{\beta^\gamma}{\alpha^\gamma - 1} + v^{z_L})\Big]
-\end{split}
-\end{align}
-
 Then derivatives of $Z$ are computed w.r.t the weights and hyperparameters of the factorised distribution and then they are used for updates.
+\subsection{Hyperparameter optimisation}
+The only hyperparameter in the proposed Bayesian \textsc{lista} is the shrinkage parameter $\lambda$.
+It can be optimised using the Type II maximum likelihood procedure.
+The Type II likelihood, i.e.
+the evidence $p(\boldsymbol\beta | \mathbf{y}, \lambda)$, of the Bayesian \textsc{lista} is equal to the normalisation constant $Z$ (\ref{eq:Z}) computed for the whole training dataset $\boldsymbol\beta$.
+Given the approximation~(\ref{eq:Z_approx}) the optimal hyperparameter $\lambda$ can be found by a gradient-based optimiser.
 
@@
 \begin{itemize}
-\item $\text{NMSE} (\text{normalised mean square error)})= \dfrac{\|\mathbf{X} - \widehat{\mathbf{X}}\|^2_{F}}{\|\mathbf{X}\|^2_{F}}$, where $\mathbf{X}$ is the true signal, $\widehat{\mathbf{X}}$ is the estimate, computed as the mean of the approximated posterior distribution, $\|\cdot\|_{F}$ is the Frobenius norm of a matrix;
+\item $\text{\textsc{nmse}} (\text{normalised mean square error)})= \dfrac{\|\mathbf{X} - \widehat{\mathbf{X}}\|^2_{F}}{\|\mathbf{X}\|^2_{F}}$, where $\mathbf{X}$ is the true signal, $\widehat{\mathbf{X}}$ is the estimate, computed as the mean of the approximated posterior distribution, $\|\cdot\|_{F}$ is the Frobenius norm of a matrix;
 \item $\text{F-measure} = 2\dfrac{\text{precision}\cdot\text{recall}}{\text{precision} + \text{recall}}$ between non-zero elements of the true signal $\mathbf{X}$ and non-zero elements of the estimate $\widehat{\mathbf{X}}$.
@@
 
-We demonstrate the performance on small datasets to highlight that the proposed algorithm can learn when the dataset size is not sufficient for LISTA.
+We demonstrate the performance on small datasets to highlight that the proposed algorithm can learn when the dataset size is not sufficient for \textsc{lista}.
 
 \subsection{Predictive performance on synthetic data}
-First, the predictive performance of the proposed Bayesian LISTA is analysed on synthetic data.
+First, the predictive performance of the proposed Bayesian \textsc{lista} is analysed on synthetic data.
 We generate $N_\text{train}=500$ sparse coefficients vectors $\boldsymbol\beta_n$ each of size $D = 100$.
 Coefficients $\boldsymbol\beta$ are generated from the spike-and-slab distribution with truncated slab: each component of $\beta_{nd}$ is zero with probability $0.8$ or is from standard Gaussian distribution without interval $(-0.1, 0.1)$ with probability $0.2$.
-Truncation of the zeros allows to remove from support pattern values with insignificant contributions \cite{xin2016maximal}.
-To simulate sparse observations, we have generated the random Gaussian design matrix $\mathbf{X} \in \mathbb{K \times D}$.
+Truncation of the zeros allows to remove from support pattern values with insignificant contributions \citep{xin2016maximal}.
+To simulate sparse observations, we have generated the random Gaussian design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$.
 The observations are generated according to the \ref{eq:regression_problem} with zero-mean Gaussian noise with standard deviation $0.5$.
 
-We compare the proposed Bayesian LISTA with original LISTA algorithm \cite{gregor2010learning} and two deterministic algorithms: Iterative Shrinkage and Thresholding Algorithm (ISTA) \cite{daubechies2004iterative} and Fast ISTA (FISTA) \cite{beck2009fast}.
-ISTA and FISTA iterate recursive updates of the $\boldsymbol\beta$ estimator in a way similar to LISTA but without weights updates.
-FISTA adds the momentum to ISTA and improves its convergence speed.
-We limit the number of iterations in these algorithms with $L$ that is the same as the number of layers in Bayesian LISTA and LISTA.
+We compare the proposed Bayesian \textsc{lista} with original \textsc{lista} algorithm \citep{gregor2010learning} and two deterministic algorithms: \textsc{ista} and Fast \textsc{ista} (\textsc{fista}) \citep{beck2009fast}.
+\textsc{fista} adds the momentum to \textsc{ista} and improves its convergence speed.
+We limit the number of iterations in these algorithms with $L$ that is the same as the number of layers in Bayesian \textsc{lista} and \textsc{lista}.
 
@@
 \begin{figure}[t]
-\subfloat[NMSE on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
+\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
 ~
-\subfloat[NMSE on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}}
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}}
 \newline
@@
 \begin{figure}[t]
-\subfloat[NMSE on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_train}}
+\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_train}}
 ~
-\subfloat[NMSE on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_validation}}
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_validation}}
 \newline
@@
 \subsection{MNIST}
-Here we evaluate the proposed Bayesian LISTA in terms of predictive performance on the MNIST dataset \cite{lecun2010mnist}.
+Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \citep{lecun2010mnist}.
 The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
-The design matrix $\mathbf{X}$ is learned on 5000 images with the minibatch online algorithm (J.
-Mairal, et al 2009).
+The design matrix $\mathbf{X}$ is learned on 5000 images with the minibatch online algorithm \citep{mairal2009online}.
 The resulting size of $\mathbf{X}$ is $100 \times 784$.
@@
 
-Figure \ref{fig:validation} presents NMSE loss on the validation set.
+Figure \ref{fig:validation} presents \textsc{nmse} loss on the validation set.
 
-Proposed Bayesian LISTA networks estimate posterior distribution for $\boldsymbol\beta$.
+Proposed Bayesian \textsc{lista} networks estimate posterior distribution for $\boldsymbol\beta$.
 Figure \ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
@@
 \includegraphics[width=\columnwidth]{loss}
-\caption{Validation NMSE}
+\caption{Validation \textsc{nmse}}
 \label{fig:validation}
@@
 \section{Discussion}
-As far as we are aware, this is the first implementation of Bayesian deep sparse coding algorithm, there are works on Bayesian sparsity in context of neural networks \cite{he2017bayesian}, but it is not the Bayesian Neural Network.
+As far as we are aware, this is the first implementation of Bayesian deep sparse coding algorithm, there are works on Bayesian sparsity in context of neural networks \citep{he2017bayesian}, but it is not the Bayesian Neural Network.
 We find not only correct predictions but also useful posterior estimates for the predictions that show how the model is confident in its decision.
-Though EP is not suited for distributed inference, some variations of ADF can be used \cite{li2015stochastic}. This allows the proposed approach to scale.
+Though EP is not suited for distributed inference, some variations of ADF can be used \citep{li2015stochastic}. This allows the proposed approach to scale.
 
-\bibliographystyle{unsrt}
+\bibliographystyle{agsm}
 \bibliography{bibliography}

### 2018-03-09 paper/BayesianLISTA.tex
paper - abstract and introduction reviewed

@@
 \usepackage{natbib}
+
+\usepackage{bbm}
 
@@
 \begin{abstract}
-We propose the method of propagating the uncertainty through the multilevel soft-thresholding nonlinearity.
-This allows to use it as a building block for sparse coding deep neural networks.
-As an example we develop the Bayesian LISTA algorithm with probabilistic backpropagation.
-It allows to obtain the variance estimates for parameters and posterior distributions.
+Bayesian neural networks impose prior distributions on weights of a network and infer a posterior distribution of an output, rather than a point prediction as in the conventional neural networks.
+Therefore, Bayesian neural networks estimate both an output for an unseen data and uncertainty of this prediction.
+Uncertainty of the prediction is a result of propagating weight uncertainty via layers of a network.
+We propose a method of propagating uncertainty through the multilevel soft-thresholding nonlinearity.
+The method expands the area of Bayesian neural networks.
+It allows the soft-thresholding nonlinearity to be used as a building block for novel Bayesian sparse coding deep neural networks.
+As an example we design a Bayesian Learned Iterative Shrinkage-Thresdholding Algorithm (\textsc{LISTA}) network.
+We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.
+A series of experiments show that the proposed framework provide both accurate predictions and reasonable estimates of uncertainty in these predictions.
 \end{abstract}
@@
 \section{Introduction}
-Though the idea of Bayesian learning in neural networks is not new \citep{neal2012bayesian}, it has gained its attention only recently, with the development of distributed approximate inference techniques \citep{li2015stochastic, hoffman2013stochastic}  and general boost in popularity of deep learning.
-In some spheres, such as self-driving cars or healthcare, posterior estimates are very important and Bayesian learning allows to obtain them.
+Though the idea of Bayesian learning in neural networks is not new \citep{neal2012bayesian}, it has regained its attention recently with the development of distributed approximate inference techniques \citep{li2015stochastic, hoffman2013stochastic}  and general boost in popularity of deep learning.
+In some spheres, such as self-driving cars or healthcare, uncertainty estimates are very important and Bayesian learning allows to obtain them.
 
-In general, when distributions are included in the network, Bayesian inference complexity scales exponentially with the number of layers, thus making it difficult to be implemented for deep neural networks in general.
+In general, when distributions are included in a network, Bayesian inference complexity scales exponentially with the number of layers.
+Thus, in general it is infeasible to apply conventional Bayesian inference algorithms for deep neural networks.
 Nevertheless, recently several techniques were proposed to handle specific types of neural networks.
-For example, dense layers \citep{hernandez2015probabilistic}, networks with discrete distributions \citep{soudry2014expectation}, recurrent networks \citep{mcdermott2017bayesian}.
+For example, feed-forward networks with rectified linear units nonlinearity~\citep{hernandez2015probabilistic}, networks with discrete distributions~\citep{soudry2014expectation}, recurrent networks~\citep{mcdermott2017bayesian}.
 
-There are currently two approaches for Bayesian neural networks: distributions of weights can be included in the network \citep{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing the uncertainty \citep{gal2016dropout}.
-In this paper we are using the first way and impose distributions on weights and parameters to obtain posterior estimates of parameters, weights and predictions with uncertainty estimated.
+There are currently two approaches for Bayesian neural networks: distributions of weights can be included in the network \citep{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing uncertainty \citep{gal2016dropout}.
+In this paper we use the first way and impose distributions on weights and parameters to obtain posterior estimates of parameters, weights and predictions with uncertainty estimated.
 
-Sparse coding problem can be viewed as the linear regression problem with the additional assumption that some of the basis representation coefficients should be zeros.
-It arises in different applications, such as compressive sensing~\cite{candes2008introduction}, image and video processing~\cite{mairal2014sparse}, non-invasive brain activity areas discovery \cite{baillet1997bayesian}.
+The sparse coding and sparse inverse problems can be viewed as linear regression problems with the additional assumption that many of the basis representation coefficients should be zeros.
+They arise in different applications, such as compressive sensing~\citep{candes2008introduction}, image and video processing~\citep{mairal2014sparse}, non-invasive brain activity areas discovery \citep{baillet1997bayesian, jas2017learning}.
 
-The usual approach in neural networks for sparse coding is to use the soft thresholding nonlinearity, that shifts current estimates towards zero \citep{lecun2010mnist}.
-It allows to obtain predictions containing zeros.
+The usual approach in neural networks for sparse coding is to use the soft-thresholding nonlinearity, that shifts current estimates towards zero \citep{lecun2010mnist}.
 In this paper we propose the approach to propagate uncertainty through the soft-thresholding nonlinearity.
-At every layer the current distribution of the target vector is represented as spike-and-slab distribution \citep{mitchell1988bayesian}, and we show that it can be effectively combined with Gaussian weights for dense layers and after soft-thresholding it can be closely approximated with distribution from the same family.
+At every layer the current distribution of the target vector is represented as a spike-and-slab distribution \citep{mitchell1988bayesian}.
+We show that it can be effectively combined with Gaussian weights for dense layers.
+The distribution of the target vector propagated through a dense layer and soft-thresholding nonlinearity can then be closely approximated with a distribution from the same family.
 
-The proposed method of uncertainty propagation for sparse coding allows to derive the gradients of the normalisation constant logarithm of the model likelihood which is used in probabilistic backpropagation to update weights distribution, therefore it can be applied to Bayesian neural networks for sparse coding.
+The proposed method of uncertainty propagation for sparse coding allows to derive the gradients of the logarithms of normalisation constants, which are used in probabilistic backpropagation to update weights distribution.
+We then develop a highly efficient Bayesian inference algorithm based on the probabilistic backpropagation paradigm while significantly expanding it.
 
-The paper is organised as following: first, we describe the uncertainty propagation to obtain the spike-and-slab distribution - output from the network, then we describe how the backpropagation is organised to update distributions of weights and their priors.
-After that we show how the algorithm is performed on \textsc{mnist} data and demonstrate the obtained posterior estimates.
+The main contributions of this paper can be summarised~as: 
+\begin{itemize}
+\item for the first time we propose uncertainty propagation through the soft-thresholding nonlinearity for a Bayesian neural network
+\item efficient posterior inference for weights and outputs of neural networks with the soft-thresholding nonlinearity
+\item novel Bayesian neural network for sparse coding
+\end{itemize}
 
-The main contributions are: 
-\begin{itemize}
-\item for the first time we propose uncertainty propagation through the soft-thresholding nonlinearity for Bayesian neural network
-\item efficient posterior inference for weights and outputs of neural networks with the soft-thresholding nonlinearity
-\item novel Bayesian neural network network for sparse coding
-\end{itemize}
+The paper is organised as following: first, we review neural networks for sparse coding and present a novel Bayesian neural network.
+We then describe uncertainty propagation to obtain the spike-and-slab distribution for an output of a network and how probabilistic backpropagation is organised to update distributions of weights.
+After that, we show the experimental results of the algorithm.
 
@@
 
-\bibliographystyle{agsm}
 \bibliography{bibliography}
+\bibliographystyle{icml2018}
 

### 2018-03-09 paper/BayesianLISTA.tex
experiment results processing

--- 2018-03-08 paper/BayesianLISTA.tex
@@
 
-\subsection{MNIST}
+\subsection{Predictive performance on synthetic data}
 Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \citep{lecun2010mnist}.
@@
 The design matrix $\mathbf{X}$ is learned on 5000 images with the minibatch online algorithm \citep{mairal2009online}.
-The resulting size of $\mathbf{X}$ is $100 \times 784$.
+The resulting size of $\mathbf{X}$ is $K \times 784$.
 Then we generate observations as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta$ are images converted to vectors.
-We use randomly selected 1000 images for training and 100 for validation.
+We use randomly selected $100$ images for training and $100$ for validation.
 
-Figure \ref{fig:validation} presents \textsc{nmse} loss on the validation set.
+Figures \ref{fig:mnist_100}, \ref{fig:mnist_250} presents \textsc{nmse} loss on the validation set with dictionaries $100$ and $250$.
 
@@
 Figure \ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
+
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{loss}
-\caption{Validation \textsc{nmse}}
-\label{fig:validation}
+\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
+~
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
+\newline
+\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
+~
+\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
+\caption{\textsc{mnist} with dictionary $100$}
+\label{fig:mnist_100}
 \end{figure}
+
+\begin{figure}[t]
+\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_train}}
+~
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_valid}}
+\newline
+\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
+~
+\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_valid}}
+\caption{\textsc{mnist} with dictionary $250$}
+\label{fig:mnist_250}
+\end{figure}
+
+%\begin{figure}[t]
+%\includegraphics[width=\columnwidth]{loss}
+%\caption{Validation \textsc{nmse}}
+%\label{fig:validation}
+%\end{figure}
 \begin{figure*}[t]

### 2018-03-09 theano/PBP_net_lista/test_network_layer.py

@@ -73,38 +73,38 @@ class TestNetwork_layer(TestCase):
     #             plt.title('compute B matrix for column %d' % d)
     #             plt.show()
 
-    # def test_compute_D(self):
-    #
-    #     sample_z = np.zeros((self.sample_size, self.D), dtype=np.float64)
-    #     for i in range(self.sample_size):
-    #         sample_z[i, :] = random_spike_and_slab(self.z_m, np.sqrt(self.z_v), self.z_omega)
-    #
-    #     sample_S = np.zeros((self.sample_size, self.D, self.D), dtype=np.float64)
-    #     for i in range(self.sample_size):
-    #         sample_S[i, :, :] = np.random.normal(self.S_M, np.sqrt(self.S_V))
-    #
-    #     z_m = T.vector()
-    #     z_v = T.vector()
-    #     z_omega = T.vector()
-    #
-    #     compute_D_func = theano.function([z_omega, z_m, z_v], self.layer.compute_D(z_omega, z_m, z_v))
-    #     theano_D_m, theano_D_v = compute_D_func(self.z_omega, self.z_m, self.z_v)
-    #
-    #     true_D_sample = np.zeros((self.sample_size, self.D), dtype=np.float64)
-    #     for i in range(self.sample_size):
-    #         true_D_sample[i, :] = np.dot(sample_S[i, :, :], sample_z[i, :])
-    #
-    #     est_D_sample = np.zeros((self.sample_size, self.D), dtype=np.float64)
-    #     for i in range(self.sample_size):
-    #         est_D_sample[i, :] = np.random.normal(theano_D_m, np.sqrt(theano_D_v))
-    #
-    #     if self.plot:
-    #         d = 5
-    #         sns.distplot(true_D_sample[:, d], label='true')
-    #         sns.distplot(est_D_sample[:, d], label='estimated')
-    #         plt.legend()
-    #         plt.title('compute D matrix for column %d' % d)
-    #         plt.savefig('d_testing.eps', format='eps')
+    def test_compute_D(self):
+
+        sample_z = np.zeros((self.sample_size, self.D), dtype=np.float64)
+        for i in range(self.sample_size):
+            sample_z[i, :] = random_spike_and_slab(self.z_m, np.sqrt(self.z_v), self.z_omega)
+
+        sample_S = np.zeros((self.sample_size, self.D, self.D), dtype=np.float64)
[…]

### 2018-03-09 theano/experiments/active_learning/collect_results.py

@@ -1,0 +1,164 @@
+import errno
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+
+class ActiveExperimentMnistResultsCollector(object):
+    def __init__(self):
+        self.n_rseed = 10
+        self.n_upd_iter = 10
+        self.freq_validation_loss = np.zeros((self.n_rseed, self.n_upd_iter+1))
+        self.non_active_bayes_validation_loss = np.zeros((self.n_rseed, self.n_upd_iter+1))
+        self.active_bayes_validation_loss = np.zeros((self.n_rseed, self.n_upd_iter+1))
+        self.freq_validation_f_measure = np.zeros((self.n_rseed, self.n_upd_iter+1))
+        self.non_active_bayes_validation_f_measure = np.zeros((self.n_rseed, self.n_upd_iter+1))
+        self.active_bayes_validation_f_measure = np.zeros((self.n_rseed, self.n_upd_iter+1))
+
+    def collect_all(self):
+        for rseed in range(self.n_rseed):
+            res = np.load('mnist_results/mnist_active_rseed_{}.npz'.format(rseed))
+            self.freq_validation_loss[rseed] = res['freq_validation_loss']
+            self.non_active_bayes_validation_loss[rseed] = res['non_active_bayes_validation_loss']
+            self.active_bayes_validation_loss[rseed] = res['active_bayes_validation_loss']
+            self.freq_validation_f_measure[rseed] = res['freq_validation_f_measure']
+            self.non_active_bayes_validation_f_measure[rseed] = res['non_active_bayes_validation_f_measure']
+            self.active_bayes_validation_f_measure[rseed] = res['active_bayes_validation_f_measure']
+
+    def plot_each(self):
+        for rseed in range(self.n_rseed):
+            res = np.load('mnist_results/mnist_active_rseed_{}.npz'.format(rseed))
+
+            plt.plot(res['active_bayes_validation_loss'], label='active')
+            plt.plot(res['non_active_bayes_validation_loss'], label='non active')
+            plt.legend()
+            plt.show()
+
+    def plot_all(self):
+        try:
+            os.makedirs('mnist_results_plots')
+        except OSError as e:
+            if e.errno != errno.EEXIST:
+                raise
+
+        linewidth = .25
+        markersize = 5.
+        std_multiplier = 1
+
+        non_active_bayes_marker = 'v'
+        non_active_bayes_color = 'red'
[…]

### 2018-03-09 theano/experiments/mnist/collect_results.py

@@ -7,21 +7,25 @@ class MnistExperimentResultsCollector(object):
     def __init__(self):
         self.n_iter = 500
 
-    def collect_all(self):
-        self.ista_f_meas_train, self.ista_f_meas_validation, self.ista_loss_train, self.ista_loss_validation, \
-        self.ista_f_meas_train_std, self.ista_f_meas_validation_std, self.ista_loss_train_std, self.ista_loss_validation_std = \
-            self.collect_ista_fista('ista')
-        self.fista_f_meas_train, self.fista_f_meas_validation, self.fista_loss_train, self.fista_loss_validation, \
-        self.fista_f_meas_train_std, self.fista_f_meas_validation_std, self.fista_loss_train_std, self.fista_loss_validation_std, = \
-            self.collect_ista_fista('fista')
+    def collect_all(self, undersampling):
+        self.ista_f_meas_train, self.ista_f_meas_validation, self.ista_loss_train, self.ista_loss_validation = \
+            self.collect_ista_fista('ista_fista/results_{}_K_ista.npz'.format(undersampling))
+        self.fista_f_meas_train, self.fista_f_meas_validation, self.fista_loss_train, self.fista_loss_validation = \
+            self.collect_ista_fista('ista_fista/results_{}_K_fista.npz'.format(undersampling))
         self.freq_f_meas_train, self.freq_f_meas_validation, self.freq_loss_train, self.freq_loss_validation, \
-        self.freq_f_meas_train_std, self.freq_f_meas_validation_std, self.freq_loss_train_std, self.freq_loss_validation_std = \
-            self.collect_main('freq')
-        self.sh_bayes_f_meas_train, self.sh_bayes_f_meas_validation, self.sh_bayes_loss_train, self.sh_bayes_loss_validation,\
-        self.sh_bayes_f_meas_train_std, self.sh_bayes_f_meas_validation_std, self.sh_bayes_loss_train_std, self.sh_bayes_loss_validation_std = \
-            self.collect_main('sh_bayes')
+        self.sh_bayes_f_meas_train, self.sh_bayes_f_meas_validation, self.sh_bayes_loss_train, self.sh_bayes_loss_validation = \
+            self.collect_main('normalised_results/mnist_100_train_20_layers_K_{}'.format(undersampling))
 
-    def collect(self, filename_prefix):
+    def collect_ista_fista(self, fileprefix):
+        saved_res = np.load(fileprefix)
[…]

### 2018-03-09 theano/experiments/synthetic/number_of_layers/collect_results.py

@@ -133,9 +133,9 @@ class NumberOfLayersExperimentReultsCollector(object):
         plt.plot(self.L_array, self.sh_bayes_f_meas_train, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.L_array, self.sh_bayes_f_meas_train, yerr=2 * self.sh_bayes_f_meas_train_std, color=sh_bayes_color)
         plt.legend()
-        plt.savefig('results/f_measure_train.eps', format='eps')
         plt.xlabel(r'K')
         plt.ylabel(r'F measure')
+        plt.savefig('results/f_measure_train.eps', format='eps')
         plt.show()
 
         plt.plot(self.L_array, self.ista_f_meas_validation, label=ista_label, color=ista_color, marker=ista_marker, linewidth=linewidth, markersize=markersize)
@@ -147,9 +147,9 @@ class NumberOfLayersExperimentReultsCollector(object):
         plt.plot(self.L_array, self.sh_bayes_f_meas_validation, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.L_array, self.sh_bayes_f_meas_validation, yerr=3 * self.sh_bayes_f_meas_validation_std, color=sh_bayes_color)
         plt.legend()
-        plt.savefig('results/f_measure_validation.eps', format='eps')
         plt.xlabel(r'K')
         plt.ylabel(r'F measure')
+        plt.savefig('results/f_measure_validation.eps', format='eps')
         plt.show()
 
         plt.plot(self.L_array, self.ista_loss_train, label=ista_label, color=ista_color, marker=ista_marker, linewidth=linewidth, markersize=markersize)
@@ -161,9 +161,9 @@ class NumberOfLayersExperimentReultsCollector(object):
         plt.plot(self.L_array, self.sh_bayes_loss_train, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.L_array, self.sh_bayes_loss_train, yerr=3 * self.sh_bayes_loss_train_std, color=sh_bayes_color)
         plt.legend()
-        plt.savefig('results/nmse_train.eps', format='eps')
         plt.xlabel(r'K')
         plt.ylabel(r'NMSE')
[…]

### 2018-03-09 theano/experiments/synthetic/undersampling/collect_results.py

@@ -134,9 +134,9 @@ class UndersamplingExperimentReultsCollector(object):
         plt.plot(self.K_array, self.sh_bayes_f_meas_train, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.K_array, self.sh_bayes_f_meas_train, yerr=2 * self.sh_bayes_f_meas_train_std, color=sh_bayes_color)
         plt.legend()
-        plt.savefig('results/f_measure_train.eps', format='eps')
         plt.xlabel(r'K')
         plt.ylabel(r'F measure')
+        plt.savefig('results/f_measure_train.eps', format='eps')
         plt.show()
 
         plt.plot(self.K_array, self.ista_f_meas_validation, label=ista_label, color=ista_color, marker=ista_marker, linewidth=linewidth, markersize=markersize)
@@ -148,9 +148,9 @@ class UndersamplingExperimentReultsCollector(object):
         plt.plot(self.K_array, self.sh_bayes_f_meas_validation, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.K_array, self.sh_bayes_f_meas_validation, yerr=3 * self.sh_bayes_f_meas_validation_std, color=sh_bayes_color)
         plt.legend()
-        plt.savefig('results/f_measure_validation.eps', format='eps')
         plt.xlabel(r'K')
         plt.ylabel(r'F measure')
+        plt.savefig('results/f_measure_validation.eps', format='eps')
         plt.show()
 
         plt.plot(self.K_array, self.ista_loss_train, label=ista_label, color=ista_color, marker=ista_marker, linewidth=linewidth, markersize=markersize)
@@ -162,9 +162,9 @@ class UndersamplingExperimentReultsCollector(object):
         plt.plot(self.K_array, self.sh_bayes_loss_train, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.K_array, self.sh_bayes_loss_train, yerr=3 * self.sh_bayes_loss_train_std, color=sh_bayes_color)
         plt.legend()
-        plt.savefig('results/nmse_train.eps', format='eps')
         plt.xlabel(r'K')
         plt.ylabel(r'NMSE')
[…]

### 2018-03-09 paper/BayesianLISTA.tex
paper - almost upto experiments, corrected formulae

@@
 
-The problem of sparse coding is the linear regression with assumption of sparse weights
+The sparse coding and sparse inverse problems are the linear regression with the assumption of sparse weights
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{y} \in \mathbb{R}^K$ is the observation, $\mathbf{X} \in \mathbb{R}^{K \times D}$ is the design matrix, $\boldsymbol\beta \in \mathbb{R}^D$ is unknown vector of weights such that $K < D$ with some of its elements $\beta_d$ equal to zero to achieve regularisation.
+where $\mathbf{y} \in \mathbb{R}^K$ is the observation, $\mathbf{X} \in \mathbb{R}^{K \times D}$ is the design matrix, $\boldsymbol\beta \in \mathbb{R}^D$ is the unknown vector of weight with many elements $\beta_d$ equal to zero.
 $\varepsilon \in \mathbb{R}^K$ is the independent Gaussian noise.
@@
 One of the popular families of the sparse coding algorithms is the iterative shrinkage algorithms, and notably the Iterative Shrinkage and Thresholding Algorithm(\textsc{ista}) \citep{daubechies2004iterative}.
-It iteratively obtains the new approximation of the coefficients vector $\widehat{\boldsymbol\beta}_l$ as the linear transformation of the input $\mathbf{y}$ with previous approximation $\widehat{\boldsymbol\beta}_{l-1}$ and then propagates the new approximation through the soft thresholding function $h_\lambda(\cdot)$
+It iteratively obtains the new approximation of the coefficient vector $\widehat{\boldsymbol\beta}_l$ at the iteration $l$ as the linear transformation of the input $\mathbf{y}$ with previous approximation $\widehat{\boldsymbol\beta}_{l-1}$ and then propagates the new approximation through the soft thresholding function $h_\lambda(\cdot)$
 \begin{equation}
@@
 \end{equation}
-with weights $\mathbf{W} = \mathbf{X}^\top / E$, $E$ - upper bound on the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$ and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$.
+with weights $\mathbf{W} = \mathbf{X}^\top / E$, $E$ - upper bound on the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$ and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$ ($\mathbf{I}_{D \times D}$ is the identity matrix of size $D$).
 
-Learned \textsc{ista} (\textsc{lista}) \citep{gregor2010learning} algorithm allows to learn the values of matrices $\mathbf{W}$, $\mathbf{S}$.
+The Learned \textsc{ista} (\textsc{lista}) \citep{gregor2010learning} algorithm allows to learn the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
 To achieve this, \textsc{ista} algorithm is limited with the fixed amount of iterations, $L$ and interpreted as a recurrent neural network.
-Overall, it has the following scheme
+Overall, it has the following scheme of predicting a coefficient vector $\boldsymbol\beta$ for an observation $\mathbf{y}$
 \begin{align}
@@
 Vectors $\mathbf{c}_l$, $\mathbf{b}$ are intermediate vectors that describe forward propagation.
-$\boldsymbol\beta_l$ is the current approximation of the target coefficients vector.
+$\boldsymbol\beta_l$ is the current approximation of the target coefficient vector at the layer $l$.
 
 \section{Bayesian neural network for sparse coding}
-To formulate the Bayesian version of \textsc{lista} we impose the prior distributions on the unknown weights
+This section presents the proposed Bayesian neural network for sparse coding. To formulate the Bayesian version of \textsc{lista} we impose the prior distributions on the unknown weights
 \begin{align}
-&p(\mathbf{W}) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij, l} | 0, \eta^{-1}), \\
-&p(\mathbf{S}) = \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd'', l} | 0, \eta^{-1}),
+&p(\mathbf{W}) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij} | 0, \eta^{-1}), \\
+&p(\mathbf{S}) = \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} | 0, \eta^{-1}),
 \end{align}
-where $w_{ij, l}$ is the component of the matrix $\mathbf{W}_l$, $s_{d'd'', l}$ is the component of the matrix $\mathbf{S}_l$ from the layer $l$.
-Likelihood of the output $\mathbf{y}$ is defined as 
-\begin{equation}
+where $w_{ij}$ is a component of the matrix $\mathbf{W}$, $s_{d'd''}$ is a component of the matrix $\mathbf{S}$, $\eta$ is the precision of the Gaussian distribution.
+The likelihood of $\mathbf{B}$ is defined as 
+\begin{align}
+p(&\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) \nonumber \\
 \label{eq:likelihood}
-p(\mathbf{y}; \mathbf{W}, \mathbf{S}, \gamma) = \prod_{d=1}^D\mathcal{N}([\mathbf{y}]_d; [f(\mathbf{y}; \mathbf{W}, \mathbf{S})]_d, \gamma^{-1}),
-\end{equation}
-where $f(\mathbf{y}; \mathbf{W}, \mathbf{S})$ is the output of the \textsc{lista} neural network.
-The posterior distribution is 
-\begin{equation}
+= &\prod_{n=1}^N\prod_{d=1}^D\mathcal{N}(\beta_d^{(n)}; [f(\mathbf{y^{(n)}}; \mathbf{W}, \mathbf{S}, \lambda)]_d, \gamma^{-1}),
+\end{align}
+where $[\cdot]_d$ is the d-th component of a vector, $f(\mathbf{y}^{(n)}; \mathbf{W}, \mathbf{S}, \lambda)$ is the output of the Bayesian \textsc{lista} neural network, $\gamma$ is the precision of the Gaussian distribution.
+The prior of the introduced Gaussian precisions are set to the Gamma distribution with parameters $a^{\cdot}$ and $b^{\cdot}$:
+\begin{align}
+&p(\gamma) = \text{Gam}\left(\gamma; a^{\gamma}, b^{\gamma}\right), \\
+&p(\eta) = \text{Gam}\left(\eta; 	a^{\eta}, b^{\eta}\right)
+\end{align}
+
+The posterior distribution is then
+\begin{align}
+p(&\mathbf{W}, \mathbf{S}, \gamma, \eta | \mathbf{B}, \mathbf{Y}, \lambda) \nonumber \\
 \label{eq:posterior}
-p(\mathbf{W}, \mathbf{S}, \gamma, \eta | D) = \frac{p(\mathbf{y} | \mathbf{W},  \mathbf{S}, \gamma) p(\mathbf{W} | \eta )p(\mathbf{S} | \eta) p(\eta) p(\gamma)}{p(\mathbf{y})}
-\end{equation}
+= & \frac{p(\mathbf{B} | \mathbf{Y}, \mathbf{W},  \mathbf{S}, \gamma, \lambda) p(\mathbf{W} | \eta )p(\mathbf{S} | \eta) p(\eta) p(\gamma)}{p(\mathbf{B} | \mathbf{Y}, \lambda)}
+\end{align}
 The shrinkage parameter $\lambda$ is a hyperparameter of the model.
@@
 \section{Uncertainty propagation through soft thresholding}
-We initialise the $\widehat{\boldsymbol\beta}_{0}$ with the spike and slab distribution with parameters $\boldsymbol\omega = \mathbf{0}$, $\mathbf{m} = \mathbf{0}$, $\mathbf{v} = \mathbf{1}$.
-For every layer we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters $\boldsymbol\omega$, $\mathbf{m}$, $\mathbf{v}$
+For every layer of the Baysian \textsc{LISTA} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters $\boldsymbol\omega$, $\mathbf{m}$, $\mathbf{v}$
 \begin{equation}
-[\boldsymbol\beta_{l-1}]_d \sim [\boldsymbol\omega]_d \delta_0 + (1 - [\boldsymbol\omega]_d)\mathcal{N}([\mathbf{m}]_d, [\mathbf{v}]_d)
+[\boldsymbol\beta_{l-1}]_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d),
 \end{equation}
+where $\omega_d$, $m_d$, and $v_d$ are components of vectors $\boldsymbol\omega$, $\mathbf{m}$, and $\mathbf{v}$, respectively.
+We initialise $\widehat{\boldsymbol\beta}_{0}$ with the spike and slab distribution with parameters $\boldsymbol\omega = \mathbf{0}$, $\mathbf{m} = \mathbf{0}$, $\mathbf{v} = \mathbf{1}$.
 
-Further in this section we show that the value of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with spike and slab distribution and therefore it maintains the same family of distributions and allows to apply the extended probabilistic backpropagation algorithm that is proposed in Section~\ref{sec:backpropagation}: lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$.
+Further in this section we show that the value of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with a spike and slab distribution and, therefore, it maintains the same family of distributions and allows to apply the probabilistic backpropagation algorithm that is proposed in Section~\ref{sec:backpropagation}: lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft-thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$.
 Overall the probabilistic layer is described by theorem \ref{thm:prob_layer}.
@@
 
-  \begin{lemma}[Product of Gaussian matrix and Gaussian vector]
+  \begin{lemma}[Product of Gaussian matrix and spike and slab vector]
   \label{thm:matrix_vector}
@@
 \label{sec:approx_quality}
-We have used two approximations in forward propagation of the uncertainty.
+We have used two approximations in forward propagation of uncertainty.
 First, in lemma \ref{thm:matrix_vector} a Gaussian matrix is multiplied by a spike-and-slab vector and their product is approximated with the Gaussian distribution.
@@
 Figure \ref{fig:d_testing} demonstrates the comparison of the sampled distribution and approximated distribution for lemma \ref{thm:matrix_vector}.
-For sampled distribution, $10000$ values were sampled from the Gaussian matrix and the Gaussian vector and their product was computed, then one of the dimensionalities was plotted.
-The approximated distribution was computed according to lemma \ref{thm:matrix_vector}.
+For sampled distribution, $10000$ values were sampled from the Gaussian matrix and the spike and slab vector and their product is computed, then one of the dimensionalities is plotted.
+The approximated distribution is computed according to lemma \ref{thm:matrix_vector}.
 
 Figure \ref{fig:z_new_testing} demonstrates the comparison of the sampled distribution and approximated distribution for lemma \ref{thm:soft_thresholding}.
-For sampled distribution, $10000$ values were sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities was plotted.
-The approximated distribution was computed according to lemma \ref{thm:soft_thresholding}.
+For sampled distribution, $10000$ values are sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities is plotted.
+The approximated distribution is computed according to lemma \ref{thm:soft_thresholding}.
 \begin{figure}[t]
@@
 \subsection{Likelihood}
-We use the probabilistic backpropagation algorithm \citep{hernandez2015probabilistic} for computing parameters updates.
-It is based on assumed density filtering and expectation propagation and allows to update parameters of the distributions based on the derivative of the logarithm of the normalisation constant.
-The exact posterior \ref{eq:posterior} is approximated with a factorised distribution
+For Bayesian inference we significantly expend the probabilistic backpropagation algorithm~\citep{hernandez2015probabilistic} for computing parameter updates.
+It is based on assumed density filtering (ADF) and expectation propagation (EP) and allows to update parameters of the distributions based on the derivative of the logarithm of a normalisation constant.
+ADF is based on iteratively incorporating factors from the true posterior to a factorised approximating distribution, whereas in EP factors in an approximating distribution are iteratively replaced by factors from the true posterior.
+
+The exact posterior (\ref{eq:posterior}) is approximated with a factorised distribution
 \begin{align}
 \begin{split}
-q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk, l} | m^w_{dk, l}, v^w_{dk, l}) \\
-&\times \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd'', l} | m^s_{d'd'', l}, v^s_{d'd'', l}) \\
-&\times \text{Gam}(\gamma; \alpha^\gamma, \beta^\gamma) \text{Gam}(\eta; \alpha^\eta, \beta^\eta) 
+q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} | m^w_{dk}, v^w_{dk}) \\
+&\times \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} | m^s_{d'd''}, v^s_{d'd''}) \\
+&\times \text{Gam}(\gamma; a^\gamma, b^\gamma) \text{Gam}(\eta; a^\eta, b^\eta) 
 \end{split}
 \end{align}
-The normalisation constant of the approximating distribution $q$ with the likelihood~\ref{eq:likelihood} term incorporated can be computed as follows
+
+With the likelihood factors~(\ref{eq:likelihood}) of the true posterior we employ the ADF approach and iteratively incorporate them into the approximating distribution $q$.
+The normalisation constant of the approximating distribution $q$ with the likelihood term for the data point $n$ incorporated can be computed as follows (to simplify notation the superscript $(n)$ is omitted)
 \begin{align}
@@
 Z = \int \prod_{d=1}^{D} \big[&\mathcal{N}(\beta_d | f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) \\
- &q(\mathbf{S}, \mathbf{W}, \eta, \gamma)\big] \mathrm{d}\mathbf{S} \mathrm{d}\mathbf{W} \mathrm{d}\eta \mathrm{d}\gamma
+ &q(\mathbf{W}, \mathbf{S}, \gamma, \eta)\big] \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
  \end{split}
 \end{align}
-We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\mathbf{z}_L$ - output from the network
+We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\mathbf{z}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximated with the spike and slab distribution with parameters $\boldsymbol\omega^{z_L}$, $\mathbf{m}^{z_l}$, and $\mathbf{v}^{z_L}$
 \begin{align}
-&Z \approx \int \prod_{d=1}^{D} \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1}) \nonumber \\
-&\times (\omega^{z_L}_d \delta_0([\mathbf{z}_L]_d) + (1 - \omega^{z_L}_d)\mathcal{N}(m^{z_L}_d, v^{z_L}_d)) \nonumber\\
-&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}\mathbf{z}_L \mathrm{d}\boldsymbol\gamma  \nonumber\\
-&= \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1})  \delta_0([z_L]_d) \nonumber \\
-&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[{z}_L]_d \mathrm{d}\gamma_d  \nonumber\\
-& + (1 - \omega^{z_L}_d)\int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma_d^{-1})\mathcal{N}(m^{z_L}_d, v^{z_L}_d))  \nonumber\\
-&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[{z}_L]_d \mathrm{d}\gamma_d\Big]  \nonumber\\
-& = \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \mathcal{N}(\beta_d | 0, \gamma_d^{-1})  \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma) d\gamma_d  \nonumber\\
+&Z \approx \int \prod_{d=1}^{D} \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma^{-1}) \nonumber \\
+&\times (\omega^{z_L}_d \delta_0([\mathbf{z}_L]_d) + (1 - \omega^{z_L}_d)\mathcal{N}([\mathbf{z}_L]_d | m^{z_L}_d, v^{z_L}_d)) \nonumber\\
+&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}\mathbf{z}_L \mathrm{d}\gamma  \nonumber\\
+&= \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma^{-1})  \delta_0([\mathbf{z}_L]_d) \nonumber \\
+&\times \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[\mathbf{z}_L]_d \mathrm{d}\gamma  \nonumber\\
+& + (1 - \omega^{z_L}_d)\int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma^{-1})\nonumber\\
+&\times \mathcal{N}([\mathbf{z}_L]_d | m^{z_L}_d, v^{z_L}_d)) \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[\mathbf{z}_L]_d \mathrm{d}\gamma\Big]  \nonumber\\
+& = \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \mathcal{N}(\beta_d | 0, \gamma^{-1})  \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma) d\gamma  \nonumber\\
 & + (1 - \omega^{z_L}_d)\int \big[\mathcal{T}(\beta_d | [\mathbf{z}_L]_d, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma)  \nonumber\\
-&\times \mathcal{N}(m^{z_L}_d, v^{z_L}_d))\big] \mathrm{d}[{z}_L]_d\Big]  \nonumber\\
+&\times \mathcal{N}([\mathbf{z_L}]_d| m^{z_L}_d, v^{z_L}_d))\big] \mathrm{d}[\mathbf{z}_L]_d\Big]  \nonumber\\
 & \approx \prod_{d=1}^D \Big[\omega^{z_L}_d  \mathcal{T}(\beta_d | 0, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma) \nonumber \\ 
 \label{eq:Z_approx}
-&+ (1 - \omega^{z_L}_d)\mathcal{N}(m^{z_L}_d, \frac{\beta^\gamma}{\alpha^\gamma - 1} + v^{z_L})\Big]
+&+ (1 - \omega^{z_L}_d)\mathcal{N}(\beta_d | m^{z_L}_d, \frac{\beta^\gamma}{\alpha^\gamma - 1} + v^{z_L})\Big]
 \end{align}
 
-The Student t density, can be parametrised in different ways. In this paper the following parametrisation is used 
+The Student t density can be parametrised in different ways. In this paper the following parametrisation is used 
 \begin{equation}
@@
 
-Then derivatives of $Z$ are computed w.r.t the weights and hyperparameters of the factorised distribution and then they are used for updates.
+Then derivatives of $Z$ are computed w.r.t the weights and Gaussian precision parameters of the factorised distribution and then they are used for updates. [REWRITE]
+
+[ADD ON EP UPDATE OF PRIOR INCORPORATED]
+
 \subsection{Hyperparameter optimisation}
@@
 \section{Experiments}
+The proposed Bayesian \textsc{LISTA} is evaluated in the context of the sparse inverse problem[CITE?], where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
+
+We compare the proposed Bayesian \textsc{LISTA} with the classical  \textsc{LISTA}~\citep{gregor2010learning} in terms of the predictive accuracy. As baselines we also use ISTA[CITE] and FISTA[CITE].
 
@@
 
-We demonstrate the performance on small datasets to highlight that the proposed algorithm can learn when the dataset size is not sufficient for \textsc{lista}.
+We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn anything.
 
@@
 
-\subsection{Predictive performance on synthetic data}
+\subsection{Predictive performance on \textsc{mnist} data}
 Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \citep{lecun2010mnist}.

### 2018-03-09 paper/BayesianLISTA.tex
updated active experiments section, conclusions and disscussion section

@@
 Bayesian neural networks impose prior distributions on weights of a network and infer a posterior distribution of an output, rather than a point prediction as in the conventional neural networks.
-Therefore, Bayesian neural networks estimate both an output for an unseen data and uncertainty of this prediction.
+Therefore, Bayesian neural networks estimate both an output for a test data and uncertainty of this prediction.
 Uncertainty of the prediction is a result of propagating weight uncertainty via layers of a network.
-We propose a method of propagating uncertainty through the multilevel soft-thresholding nonlinearity.
-The method expands the area of Bayesian neural networks.
-It allows the soft-thresholding nonlinearity to be used as a building block for novel Bayesian sparse coding deep neural networks.
-As an example we design a Bayesian Learned Iterative Shrinkage-Thresdholding Algorithm (\textsc{LISTA}) network.
+We propose a method of propagating uncertainty through the soft-thresholding nonlinearity.
+The method expands the area of Bayesian neural networks and allows the soft-thresholding nonlinearity to be used in novel Bayesian sparse coding deep neural networks.
+As an example we design a Bayesian Learned Iterative Shrinkage-Thresdholding Algorithm (Bayesian \textsc{lista}) network.
 We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.
@@
 
-The usual approach in neural networks for sparse coding is to use the soft-thresholding nonlinearity, that shifts current estimates towards zero \citep{lecun2010mnist}.
+The usual approach in neural networks for sparse coding is to use the soft-thresholding nonlinearity, that shifts current estimates towards zero \citep{gregor2010learning}.
 In this paper we propose the approach to propagate uncertainty through the soft-thresholding nonlinearity.
@@
 
-The main contributions of this paper can be summarised~as: 
+The main contributions of this paper can be summarised~as (ITEMS NEED VERBS): 
 \begin{itemize}
@@
 
-The paper is organised as following: first, we review neural networks for sparse coding and present a novel Bayesian neural network.
-We then describe uncertainty propagation to obtain the spike-and-slab distribution for an output of a network and how probabilistic backpropagation is organised to update distributions of weights.
-After that, we show the experimental results of the algorithm.
+The paper is organised as following: first, we review neural networks for sparse coding in section \ref{sec:nn_sc} and present a novel Bayesian neural network in section \ref{sec:bayesian_lista}.
+We then describe uncertainty propagation to obtain the spike-and-slab distribution for an output of a network in section \ref{sec:fprop} and how probabilistic backpropagation is organised to update distributions of weights in section \ref{sec:backpropagation}.
+After that, we show the experimental results of the algorithm in section \ref{sec:experiments} and finish with discussion and conclusions in sections \ref{sec:discussion} and \ref{sec:conclusions}.
 
 \section{Neural networks for sparse coding}
-
+\label{sec:nn_sc}
 The sparse coding and sparse inverse problems are the linear regression with the assumption of sparse weights
@@
 \section{Bayesian neural network for sparse coding}
+\label{sec:bayesian_lista}
+
 This section presents the proposed Bayesian neural network for sparse coding. To formulate the Bayesian version of \textsc{lista} we impose the prior distributions on the unknown weights
@@
 \section{Uncertainty propagation through soft thresholding}
-For every layer of the Baysian \textsc{LISTA} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters $\boldsymbol\omega$, $\mathbf{m}$, $\mathbf{v}$
+\label{sec:fprop}
+For every layer of the Baysian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters $\boldsymbol\omega$, $\mathbf{m}$, $\mathbf{v}$
 \begin{equation}
@@
 
-Then derivatives of $Z$ are computed w.r.t the weights and Gaussian precision parameters of the factorised distribution and then they are used for updates. [REWRITE]
+Then derivatives of $Z$ are computed w.r.t the weights and Gaussian precision parameters of the factorised distribution and then they are used for updates. [REWRITE AND ADD ABOUT RECURRENT ESTIMATION]
 
@@
 \section{Experiments}
-The proposed Bayesian \textsc{LISTA} is evaluated in the context of the sparse inverse problem[CITE?], where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
+\label{sec:experiments}
+The proposed Bayesian \textsc{lista} is evaluated in the context of the sparse inverse problem[CITE?], where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
 
-We compare the proposed Bayesian \textsc{LISTA} with the classical  \textsc{LISTA}~\citep{gregor2010learning} in terms of the predictive accuracy. As baselines we also use ISTA[CITE] and FISTA[CITE].
+We compare the proposed Bayesian \textsc{lista} with the classical \textsc{lista}~\citep{gregor2010learning} in terms of the predictive accuracy.
+As baselines we also use \textsc{ista} \citep{daubechies2004iterative} and fast \textsc{ista} (\textsc{fista}) \citep{beck2009fast}.
+\textsc{fista} adds the momentum to \textsc{ista} and improves its convergence speed.
+We limit the number of iterations in these algorithms with $L$ that is the same as the number of layers in Bayesian \textsc{lista} and \textsc{lista}.
 
@@
 The observations are generated according to the \ref{eq:regression_problem} with zero-mean Gaussian noise with standard deviation $0.5$.
-
-We compare the proposed Bayesian \textsc{lista} with original \textsc{lista} algorithm \citep{gregor2010learning} and two deterministic algorithms: \textsc{ista} and Fast \textsc{ista} (\textsc{fista}) \citep{beck2009fast}.
-\textsc{fista} adds the momentum to \textsc{ista} and improves its convergence speed.
-We limit the number of iterations in these algorithms with $L$ that is the same as the number of layers in Bayesian \textsc{lista} and \textsc{lista}.
+$\lambda$ is assumed fixed as $0.1$.
 
@@
 \begin{figure}[t]
-\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
-~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}}
+%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
+%~
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}}
 \newline
-\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
-~
-\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}}
+%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
+%~
+\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}}
 \caption{Number of layers on synthetic data}
@@
 \begin{figure}[t]
-\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_train}}
-~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_validation}}
+%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_train}}
+%~
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/synthetic_undersampling/nmse_validation}}
 \newline
-\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
-~
-\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}}
+%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
+%~
+\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}}
 \caption{Size of observations on synthetic data}
@@
 \subsection{Predictive performance on \textsc{mnist} data}
-Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \citep{lecun2010mnist}.
+Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \citep{lecun1998gradient}.
 The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
@@
 We use randomly selected $100$ images for training and $100$ for validation.
+$\lambda$ is assumed fixed as $0.1$.
 
-Figures \ref{fig:mnist_100}, \ref{fig:mnist_250} presents \textsc{nmse} loss on the validation set with dictionaries $100$ and $250$.
+Figures \ref{fig:mnist_100}, \ref{fig:mnist_250} present \textsc{nmse} loss on the validation set with dictionaries $100$ and $250$.
 
 Proposed Bayesian \textsc{lista} networks estimate posterior distribution for $\boldsymbol\beta$.
-Figure \ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
+Figure \ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and ?igure \ref{fig:posterior_distribution} shows the parameters of this posterior.
 
 \begin{figure}[t]
-\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
-~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
+%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
+%~
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
 \newline
-\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
-~
-\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
+%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
+%~
+\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
 \caption{\textsc{mnist} with dictionary $100$}
@@
 \begin{figure}[t]
-\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_train}}
-~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_valid}}
+%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_train}}
+%~
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/250_normalised_nmse_valid}}
 \newline
-\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
-~
-\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_valid}}
+%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
+%~
+\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/250_normalised_f_measure_valid}}
 \caption{\textsc{mnist} with dictionary $250$}
@@
 
+\subsection{Active learning on \textsc{mnist}}
+To demonstrate the potential scenario that can benefit from uncertainty estimates of the Bayesian \textsc{lista} we consider the active learning example \citep{settles.tr09}.
+Active learning area researches ways to select new training subsets to reduce total number of required supervision.
+One of the approaches for active learning is uncertainty sampling when the data with the least certain predictions is used for training.
+The uncertainty can be measured with entropy or variance.
+In our example no closed form for entropy of spike and slab exist, therefore we use variance from lemma \ref{thm:moments_spsl} as a measure of uncertainty.
+
+The data in this example is the same \textsc{mnist} dataset with learnt dictionary of size $K=100$.
+It is divided into train data of size $50$, pool data of size $500$,  and test data of size $100$.
+The algorithm learns on the train data for $50$ iterations.
+After that, the Bayesian \textsc{lista} algorithm iteratively estimates the variance of the predictions on the pool data, selects the element with the maximum variance, moves it from pool set to the training set and runs additional training iteration.
+Overall, $10$ pool iterations are performed.
+
+The performance on the actively updated train data is compared with the performance on the randomly updated train data, when at every iteration the random element is moved from pool set to train set.
+Both algorithms of new data sampling were run with $20$ random seeds and their performance was averaged.
+Figure \ref{fig:active_learning_mnist} demonstrates their performance.
+\begin{figure}[t]
+\subfloat[\textsc{nmse}]{\includegraphics[width=\columnwidth]{graphics/active_mnist/nmse_validation}} \\
+\subfloat[F measure]{\includegraphics[width=\columnwidth]{graphics/active_mnist/f_measure_validation}}
+\caption{Active learning on \textsc{mnist}.}
+\label{fig:active_learning_mnist}
+\end{figure}
+
 \section{Discussion}
-As far as we are aware, this is the first implementation of Bayesian deep sparse coding algorithm, there are works on Bayesian sparsity in context of neural networks \citep{he2017bayesian}, but it is not the Bayesian Neural Network.
+\label{sec:discussion}
+As far as authors aware, this is the first implementation of Bayesian deep sparse coding algorithm.
+Although there are works on Bayesian sparsity in context of neural networks \citep{he2017bayesian}, they are not the Bayesian neural networks in the same sense as Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
 We find not only correct predictions but also useful posterior estimates for the predictions that show how the model is confident in its decision.
-Though EP is not suited for distributed inference, some variations of ADF can be used \citep{li2015stochastic}. This allows the proposed approach to scale.
 
+The inference is based on expectation propagation algorithm and though it is not suited for distributed inference, stochastic variant of assumed density filtering can potentially be used \citep{li2015stochastic}.
+This would allow the proposed approach to scale.
+
+The original \textsc{lista} algorithm can be used for inverse sparse problems with both overcomplete dictionaries as in the original paper, or undercomplete dictionaries \citep{borgerding2017amp}.
+Though this paper presents only results with undercomplete dictionaries, this is not the limitation of the method and it can be used for overcomplete dictionaries in a similar manner.
+
+\section{Conclusions and future work}
+\label{sec:conclusions}
+We have presented the new method for propagating the uncertainty through the soft thresholding function.
+To achieve this goal we have approximated the outputs of the soft thresholding function with spike and slab distribution, and we have shown that this distribution can stay within the same family after linear transformation with Gaussian weights and inputs.
+This allowed us to propose the Bayesian \textsc{lista} algorithm that learns the distributions of the weights and parameters and makes the uncertainty estimates of the outputs.
+The forward propagation in the algorithm is based on the proposed uncertainty propagation method, the backward propagation is based on the probabilistic backpropagation method, that was modified to account for likelihood of the Bayesian \textsc{lista} and its recurrent nature.
+
+Experiments on the synthetic and \textsc{mnist} datasets demonstrate that in addition to the posterior estimates the algorithm can achieve better quality of predictions than the original \textsc{lista} when the available data is small.
+Experiments on active learning demonstrate that the posterior estimates by the algorithm are adequate as the uncertainty estimated with it allows to more optimally select training points.
+
+In future we plan to estimate of shrinkage parameter $\lambda$ within the backpropagation with ADF, use minibatches for learning and use stochastic expectation propagation for distributed inference. 
 \bibliography{bibliography}

### 2018-03-09 paper/BayesianLISTA.tex
the first sentence corrected

@@
 \begin{abstract}
-Bayesian neural networks impose prior distributions on weights of a network and infer a posterior distribution of an output, rather than a point prediction as in the conventional neural networks.
+In the Bayesian neural network framework prior distributions are imposed on weights of a network and a posterior distribution of an output is inferred, rather than a point prediction in the conventional neural networks.
 Therefore, Bayesian neural networks estimate both an output for a test data and uncertainty of this prediction.

### 2018-03-09 paper/BayesianLISTA.tex
Abstract and introduction reviewed, start to reogranise lemmas

--- 2018-03-09 paper/BayesianLISTA.tex
@@
 \begin{abstract}
-Bayesian neural networks impose prior distributions on weights of a network and infer a posterior distribution of an output, rather than a point prediction as in the conventional neural networks.
+In the Bayesian neural network framework prior distributions are imposed on weights of a network and a posterior distribution of an output is inferred, rather than a point prediction provided by conventional neural networks.
 Therefore, Bayesian neural networks estimate both an output for a test data and uncertainty of this prediction.
 Uncertainty of the prediction is a result of propagating weight uncertainty via layers of a network.
-We propose a method of propagating uncertainty through the soft-thresholding nonlinearity.
-The method expands the area of Bayesian neural networks and allows the soft-thresholding nonlinearity to be used in novel Bayesian sparse coding deep neural networks.
+We propose a novel method of propagating uncertainty through the soft-thresholding nonlinearity.
+The method expands the area of Bayesian neural networks and enables the soft-thresholding nonlinearity to be included in Bayesian deep neural networks for the first time.
 As an example we design a Bayesian Learned Iterative Shrinkage-Thresdholding Algorithm (Bayesian \textsc{lista}) network.
 We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.
-A series of experiments show that the proposed framework provide both accurate predictions and reasonable estimates of uncertainty in these predictions.
+A series of experiments on sparse coding show that the proposed framework provide both accurate predictions and quantified estimates of uncertainty in these predictions.
 \end{abstract}
@@
 In general, when distributions are included in a network, Bayesian inference complexity scales exponentially with the number of layers.
-Thus, in general it is infeasible to apply conventional Bayesian inference algorithms for deep neural networks.
-Nevertheless, recently several techniques were proposed to handle specific types of neural networks.
+Thus, it is infeasible to apply conventional Bayesian inference algorithms for deep neural networks.
+Nevertheless, recently several techniques have been proposed to handle specific types of neural networks.
 For example, feed-forward networks with rectified linear units nonlinearity~\citep{hernandez2015probabilistic}, networks with discrete distributions~\citep{soudry2014expectation}, recurrent networks~\citep{mcdermott2017bayesian}.
 
-There are currently two approaches for Bayesian neural networks: distributions of weights can be included in the network \citep{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing uncertainty \citep{gal2016dropout}.
-In this paper we use the first way and impose distributions on weights and parameters to obtain posterior estimates of parameters, weights and predictions with uncertainty estimated.
+There are currently two approaches in Bayesian neural networks: explicit distributions of weights can be included in a network \citep{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing uncertainty \citep{gal2016dropout}.
+In this paper we use the first way and impose distributions on weights to obtain posterior estimates of weights and predictions with uncertainty estimated.
 
-The sparse coding and sparse inverse problems can be viewed as linear regression problems with the additional assumption that many of the basis representation coefficients should be zeros.
-They arise in different applications, such as compressive sensing~\citep{candes2008introduction}, image and video processing~\citep{mairal2014sparse}, non-invasive brain activity areas discovery \citep{baillet1997bayesian, jas2017learning}.
+Sparse coding can be viewed as a linear regression problem with the additional assumption that many of the basis representation coefficients should be zeros.
+They arise in different applications, such as compressive sensing~\citep{candes2008introduction}, image and video processing~\citep{mairal2014sparse}, neuroscience~\citep{baillet1997bayesian, jas2017learning}.
 
-The usual approach in neural networks for sparse coding is to use the soft-thresholding nonlinearity, that shifts current estimates towards zero \citep{gregor2010learning}.
-In this paper we propose the approach to propagate uncertainty through the soft-thresholding nonlinearity.
+Neural networks address the sparse coding problem with the soft-thresholding nonlinearity, that shifts current estimates towards zero \citep{gregor2010learning}.
+In this paper we propose a method to propagate uncertainty through the soft-thresholding nonlinearity.
 At every layer the current distribution of the target vector is represented as a spike-and-slab distribution \citep{mitchell1988bayesian}.
-We show that it can be effectively combined with Gaussian weights for dense layers.
+We show that it can be effectively combined with Gaussian weights of dense layers.
 The distribution of the target vector propagated through a dense layer and soft-thresholding nonlinearity can then be closely approximated with a distribution from the same family.
 
-The proposed method of uncertainty propagation for sparse coding allows to derive the gradients of the logarithms of normalisation constants, which are used in probabilistic backpropagation to update weights distribution.
+The proposed method of uncertainty propagation for the soft-thresholding nonlinearity allows us to derive the gradients of the logarithms of normalisation constants, which can be used to update weights distribution.
 We then develop a highly efficient Bayesian inference algorithm based on the probabilistic backpropagation paradigm while significantly expanding it.
 
-The main contributions of this paper can be summarised~as (ITEMS NEED VERBS): 
+The main contributions of this paper can be summarised~as: 
 \begin{itemize}
-\item for the first time we propose uncertainty propagation through the soft-thresholding nonlinearity for a Bayesian neural network
-\item efficient posterior inference for weights and outputs of neural networks with the soft-thresholding nonlinearity
-\item novel Bayesian neural network for sparse coding
+\item for the first time we propose a method for uncertainty propagation through the soft-thresholding nonlinearity for a Bayesian neural network
+\item we develop efficient posterior inference for weights and outputs of neural networks with the soft-thresholding nonlinearity
+\item we design a novel Bayesian neural network for sparse coding
 \end{itemize}
@@
 \label{sec:fprop}
-For every layer of the Baysian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters $\boldsymbol\omega$, $\mathbf{m}$, $\mathbf{v}$
+For every layer of the Baysian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters: $\boldsymbol\omega$ is a probability of a spike, $\mathbf{m}$ is a mean of a slab Gaussian distribution, and $\mathbf{v}$ is a variance of the slab distribution:
 \begin{equation}
@@
 \end{equation}
-where $\omega_d$, $m_d$, and $v_d$ are components of vectors $\boldsymbol\omega$, $\mathbf{m}$, and $\mathbf{v}$, respectively.
-We initialise $\widehat{\boldsymbol\beta}_{0}$ with the spike and slab distribution with parameters $\boldsymbol\omega = \mathbf{0}$, $\mathbf{m} = \mathbf{0}$, $\mathbf{v} = \mathbf{1}$.
+where $\omega_d$, $m_d$, and $v_d$ are components of vectors $\boldsymbol\omega$, $\mathbf{m}$, and $\mathbf{v}$, respectively, $\delta_0$ is the delta-function that represents a spike. 
+We initialise $\widehat{\boldsymbol\beta}_{0}$ with the spike and slab distribution with parameters $\boldsymbol\omega = \mathbf{0}$, $\mathbf{m} = \mathbf{0}$, and $\mathbf{v} = \mathbf{1}$.
 
-Further in this section we show that the value of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with a spike and slab distribution and, therefore, it maintains the same family of distributions and allows to apply the probabilistic backpropagation algorithm that is proposed in Section~\ref{sec:backpropagation}: lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft-thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$.
+Later in this section we show that the value of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with a spike and slab distribution and, therefore, it maintains the same family of distributions.
+This leads to the proposed probabilistic backpropagation algorithm that is described in Section~\ref{sec:backpropagation}.
+We now describe how to propagate uncertainty through the layers of the Bayesian \textsc{lista} step by step stating meanwhile theoretical facts required for the method.
+
+%lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft-thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$.
 Overall the probabilistic layer is described by theorem \ref{thm:prob_layer}.
@@
 \label{thm:moments_spsl}
-Let the random variable $\xi$ have a spike and slab distribution with probability of spike $\omega$, slab mean $m$ and slab variance $v$. Then its moments are
+Let a random variable $\xi$ have a spike and slab distribution with probability of spike $\omega$, slab mean $m$ and slab variance $v$. Then its moments are
 \begin{subequations}
@@
 \begin{split}
-\mathbb{E}\xi &= \int x (\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v))dx \\
+\mathbb{E}\xi &= \int x \big(\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v)\big)dx \\
 & = \omega \int x \delta_0(x)dx + (1 - \omega)\int x \mathcal{N}(x; m, v)dx \\
 & = (1-\omega)m \\
-\mathbb{E}\xi^2 &= \int x^2 (\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v))dx \\
+\mathbb{E}\xi^2 &= \int x^2 \big(\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v)\big)dx \\
 & = \omega \int x^2 \delta_0(x)dx + (1 - \omega)\int x^2 \mathcal{N}(x; m, v)dx \\

### 2018-03-09 paper/BayesianLISTA.tex
return old lemma overview to keep it complete for now

@@
 
-%lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft-thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$.
+Lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft-thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$.
 Overall the probabilistic layer is described by theorem \ref{thm:prob_layer}.

### 2018-03-09 paper/BayesianLISTA.tex
conclusion reviewed

@@
 \label{sec:discussion}
-As far as authors aware, this is the first implementation of Bayesian deep sparse coding algorithm.
+As far as the authors aware, this is the first implementation of Bayesian deep sparse coding algorithm.
 Although there are works on Bayesian sparsity in context of neural networks \citep{he2017bayesian}, they are not the Bayesian neural networks in the same sense as Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
-We find not only correct predictions but also useful posterior estimates for the predictions that show how the model is confident in its decision.
+We find not only correct predictions but also useful posterior estimates for the predictions that show how the model is confident in its decisions.
 
-The inference is based on expectation propagation algorithm and though it is not suited for distributed inference, stochastic variant of assumed density filtering can potentially be used \citep{li2015stochastic}.
+%The inference is based on the expectation propagation algorithm and though it is not suited for distributed inference, stochastic variant of assumed density filtering can potentially be used \citep{li2015stochastic}.
 This would allow the proposed approach to scale.
 
-The original \textsc{lista} algorithm can be used for inverse sparse problems with both overcomplete dictionaries as in the original paper, or undercomplete dictionaries \citep{borgerding2017amp}.
-Though this paper presents only results with undercomplete dictionaries, this is not the limitation of the method and it can be used for overcomplete dictionaries in a similar manner.
+The \textsc{lista}-based algorithms can be applied for the sparse coding problem with both overcomplete dictionaries as in the original paper \citep{gregor2010learning}, and undercomplete dictionaries \citep{borgerding2017amp}.
+Though this paper presents only results with undercomplete dictionaries, this is not the limitation of the proposed method and it can be used for overcomplete dictionaries in a similar manner.
 
@@
 \label{sec:conclusions}
-We have presented the new method for propagating the uncertainty through the soft thresholding function.
-To achieve this goal we have approximated the outputs of the soft thresholding function with spike and slab distribution, and we have shown that this distribution can stay within the same family after linear transformation with Gaussian weights and inputs.
-This allowed us to propose the Bayesian \textsc{lista} algorithm that learns the distributions of the weights and parameters and makes the uncertainty estimates of the outputs.
-The forward propagation in the algorithm is based on the proposed uncertainty propagation method, the backward propagation is based on the probabilistic backpropagation method, that was modified to account for likelihood of the Bayesian \textsc{lista} and its recurrent nature.
+We have presented the new method for propagating the uncertainty through the soft thresholding function. %To achieve this goal 
+We have approximated the outputs of the function with a spike and slab distribution, and we have shown that this distribution can stay within the same family after linear transformation with Gaussian weights and inputs of a neural network.
+This allowed us to propose the Bayesian \textsc{lista} network and efficient inference algorithm that learns the distributions of the weights and makes the uncertainty estimates of the outputs.
+The forward propagation in the algorithm is based on the proposed uncertainty propagation method, the backward propagation is based on the probabilistic backpropagation method, that was remarkably expanded to account for multidimensionality of inputs and outputs, likelihood of the Bayesian \textsc{lista} and its recurrent nature.
 
-Experiments on the synthetic and \textsc{mnist} datasets demonstrate that in addition to the posterior estimates the algorithm can achieve better quality of predictions than the original \textsc{lista} when the available data is small.
-Experiments on active learning demonstrate that the posterior estimates by the algorithm are adequate as the uncertainty estimated with it allows to more optimally select training points.
+Experiments on the synthetic and \textsc{mnist} datasets demonstrate that the proposed algorithm preserves the predictive accuracy of non-Bayesian methods while also providing posterior estimates.
+We also show that when the training data is very small the proposed algorithm significantly outperforms the classical \textsc{lista} in terms of predictive accuracy.
+Experiments on active learning demonstrate that the proposed Baysian \textsc{lista} gives accurate posterior estimates that can be used for selection of a next data point where a label should be obtain for.
 
-In future we plan to estimate of shrinkage parameter $\lambda$ within the backpropagation with ADF, use minibatches for learning and use stochastic expectation propagation for distributed inference. 
+The shrinkage parameter $\lambda$ is currently treated as a deterministic hyperparameter for the Baysian \textsc{lista}.
+In future we plan to incorporate it inside the model treating it as a random variable.
+For this we need to extend both the uncertainty propagation method to include uncertainty of $\lambda$ and the probabilistic backpropagation algorithm to estimate its posterior.
+We will study stochastic expectation propagation applicability in order to replace ADF that may improve further the quality of posterior estimates~\citep{li2015stochastic}.
 \bibliography{bibliography}

### 2018-03-09 paper/BayesianLISTA.tex
required rewrite performed

@@
 
-Then derivatives of $Z$ are computed w.r.t the weights and Gaussian precision parameters of the factorised distribution and then they are used for updates. [REWRITE AND ADD ABOUT RECURRENT ESTIMATION]
+Parameters of the approximating posterior distribution are then updated with the derivates of this normalisation constant. [ADD ABOUT RECURRENT ESTIMATION]
 

### 2018-03-09 paper/BayesianLISTA.tex
updated text and pictures

--- 2018-03-09 paper/BayesianLISTA.tex
@@
 \label{sec:experiments}
-The proposed Bayesian \textsc{lista} is evaluated in the context of the sparse inverse problem[CITE?], where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
+The proposed Bayesian \textsc{lista} is evaluated in the context of the sparse inverse problem, where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
 
 We compare the proposed Bayesian \textsc{lista} with the classical \textsc{lista}~\citep{gregor2010learning} in terms of the predictive accuracy.
-As baselines we also use \textsc{ista} \citep{daubechies2004iterative} and fast \textsc{ista} (\textsc{fista}) \citep{beck2009fast}.
+As baselines we also use \textsc{ista} \citep{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \citep{beck2009fast}.
 \textsc{fista} adds the momentum to \textsc{ista} and improves its convergence speed.
 We limit the number of iterations in these algorithms with $L$ that is the same as the number of layers in Bayesian \textsc{lista} and \textsc{lista}.
-
-The following quality measures are used:
-\begin{itemize}
-\item $\text{\textsc{nmse}} (\text{normalised mean square error)})= \dfrac{\|\mathbf{X} - \widehat{\mathbf{X}}\|^2_{F}}{\|\mathbf{X}\|^2_{F}}$, where $\mathbf{X}$ is the true signal, $\widehat{\mathbf{X}}$ is the estimate, computed as the mean of the approximated posterior distribution, $\|\cdot\|_{F}$ is the Frobenius norm of a matrix;
-\item $\text{F-measure} = 2\dfrac{\text{precision}\cdot\text{recall}}{\text{precision} + \text{recall}}$ between non-zero elements of the true signal $\mathbf{X}$ and non-zero elements of the estimate $\widehat{\mathbf{X}}$.
-\end{itemize}
-
+To measure the performance of the algorithms the normalised mean square error(\textsc{nmse}) and F measure are used.
+\textsc{nmse} for a batch of data $\{\boldsymbol\beta^{(n)}\}_{n=1}^{N}$ and estimators $\{\widehat{\boldsymbol\beta}^{(n)}\}_{n=1}^{N}$ is computed as
+\begin{equation}
+\text{\textsc{nmse}} = \frac{1}{N}\sum\limits_{n=1}^N\sqrt{\frac{\sum\limits_{d=1}^D\left(\widehat{\beta}_{d}^{(n)} - \beta_d^{(n)}\right)^2}{\sum\limits_{d=1}^D\left(\beta_{d}^{(n)}\right)^2}}
+\end{equation}
+In sparse coding it is usually more important to obtain the correct locations of spikes (i.e zeros) and slabs (i.e.
+non-zeros) in the estimator than to minimise \textsc{nmse}.
+The problem is therefore viewed as a skewed two-class classification problem where the number of spikes is higher than the number of slabs.
+F measure is used to evaluate the accuracy of such problems.
+F measure is computed as the harmonic mean of precision and recall
+\begin{equation}
+\text{F measure} = 2\dfrac{\text{precision}\cdot\text{recall}}{\text{precision} + \text{recall}}
+\end{equation} 
+where precision is the fraction of estimated slab locations that are correct, recall is the fraction of true slab locations among all predicted slab locations.
 We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn anything.
@@
 
-Figures \ref{fig:mnist_100}, \ref{fig:mnist_250} present \textsc{nmse} loss on the validation set with dictionaries $100$ and $250$.
+Figure \ref{fig:mnist_250} presents \textsc{nmse} loss on the validation set with dictionary of size $250$.
 
 Proposed Bayesian \textsc{lista} networks estimate posterior distribution for $\boldsymbol\beta$.
-Figure \ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and ?igure \ref{fig:posterior_distribution} shows the parameters of this posterior.
+Figure \ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
 
-\begin{figure}[t]
-%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
-%~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
-\newline
-%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
-%~
-\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
-\caption{\textsc{mnist} with dictionary $100$}
-\label{fig:mnist_100}
-\end{figure}
+%\begin{figure}[t]
+%%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
+%%~
+%\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
+%\newline
+%%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
+%%~
+%\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
+%\caption{\textsc{mnist} with dictionary $100$}
+%\label{fig:mnist_100}
+%\end{figure}
 

### 2018-03-09 theano/experiments/mnist/collect_results.py

@@ -114,7 +114,7 @@ class MnistExperimentResultsCollector(object):
         plt.plot()
         plt.legend()
         plt.ylabel(r'F measure')
-        plt.xlabel(r'n iter')
+        plt.xlabel(r'Number of iterations')
         plt.savefig('results/normalised_f_measure_valid.eps', format='eps')
         plt.show()
 
@@ -135,8 +135,8 @@ class MnistExperimentResultsCollector(object):
         plt.plot(self.sh_bayes_loss_validation, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.plot()
         plt.legend()
-        plt.ylabel(r'NMSE')
-        plt.xlabel(r'n iter')
+        plt.ylabel(r'\textsc{nmse}')
+        plt.xlabel(r'Number of iterations')
         plt.savefig('results/normalised_nmse_valid.eps', format='eps')
         plt.show()
 

### 2018-03-09 theano/experiments/synthetic/number_of_layers/collect_results.py

@@ -110,19 +110,19 @@ class NumberOfLayersExperimentReultsCollector(object):
 
         ista_marker= 'o'
         ista_color='blue'
-        ista_label='ista'
+        ista_label=r'\textsc{ista}'
 
         fista_marker= 'v'
         fista_color='red'
-        fista_label='fista'
+        fista_label=r'\textsc{fista}'
 
         freq_marker= 's'
         freq_color='black'
-        freq_label='freq lista'
+        freq_label=r'\textsc{lista}'
 
         sh_bayes_marker='d'
         sh_bayes_color='green'
-        sh_bayes_label='sh bayes'
+        sh_bayes_label=r'Bayesian \textsc{lista}'
 
         plt.plot(self.L_array, self.ista_f_meas_train, label=ista_label, color=ista_color, marker=ista_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.L_array, self.ista_f_meas_train, yerr=std_multiplier * self.ista_f_meas_train_std, color=ista_color)
@@ -133,7 +133,7 @@ class NumberOfLayersExperimentReultsCollector(object):
         plt.plot(self.L_array, self.sh_bayes_f_meas_train, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.L_array, self.sh_bayes_f_meas_train, yerr=2 * self.sh_bayes_f_meas_train_std, color=sh_bayes_color)
         plt.legend()
-        plt.xlabel(r'K')
+        plt.xlabel(r'L')
         plt.ylabel(r'F measure')
         plt.savefig('results/f_measure_train.eps', format='eps')
         plt.show()
@@ -147,7 +147,7 @@ class NumberOfLayersExperimentReultsCollector(object):
         plt.plot(self.L_array, self.sh_bayes_f_meas_validation, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.L_array, self.sh_bayes_f_meas_validation, yerr=3 * self.sh_bayes_f_meas_validation_std, color=sh_bayes_color)
         plt.legend()
-        plt.xlabel(r'K')
+        plt.xlabel(r'L')
         plt.ylabel(r'F measure')
[…]

### 2018-03-09 theano/experiments/synthetic/undersampling/collect_results.py

@@ -111,19 +111,19 @@ class UndersamplingExperimentReultsCollector(object):
 
         ista_marker= 'o'
         ista_color='blue'
-        ista_label='ista'
+        ista_label=r'\textsc{ista}'
 
         fista_marker= 'v'
         fista_color='red'
-        fista_label='fista'
+        fista_label=r'\textsc{fista}'
 
         freq_marker= 's'
         freq_color='black'
-        freq_label='freq lista'
+        freq_label=r'\textsc{lista}'
 
         sh_bayes_marker='d'
         sh_bayes_color='green'
-        sh_bayes_label='sh bayes'
+        sh_bayes_label=r'Bayesian \textsc{lista}'
 
         plt.plot(self.K_array, self.ista_f_meas_train, label=ista_label, color=ista_color, marker=ista_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.K_array, self.ista_f_meas_train, yerr=std_multiplier * self.ista_f_meas_train_std, color=ista_color)
@@ -163,7 +163,7 @@ class UndersamplingExperimentReultsCollector(object):
         plt.errorbar(self.K_array, self.sh_bayes_loss_train, yerr=3 * self.sh_bayes_loss_train_std, color=sh_bayes_color)
         plt.legend()
         plt.xlabel(r'K')
-        plt.ylabel(r'NMSE')
+        plt.ylabel(r'\textsc{nmse}')
         plt.savefig('results/nmse_train.eps', format='eps')
         plt.show()
 
@@ -177,7 +177,7 @@ class UndersamplingExperimentReultsCollector(object):
         plt.errorbar(self.K_array, self.sh_bayes_loss_validation, yerr=3 * self.sh_bayes_loss_validation_std, color=sh_bayes_color)
         plt.legend()
         plt.xlabel(r'K')
-        plt.ylabel(r'NMSE')
+        plt.ylabel(r'\textsc{nmse}')
         plt.savefig('results/nmse_validation.eps', format='eps')
         plt.show()
 

### 2018-03-09 paper/BayesianLISTA.tex
soft-thresholding -> soft thresholding

@@
 
-\author{ {\bf Danil Kuzin} \\
-\And
-{\bf Olga Isupova}  \\
-\And
-{\bf Lyudmila Mihaylova}   \\
-}
+%\author{ {\bf Danil Kuzin} \\
+%\And
+%{\bf Olga Isupova}  \\
+%\And
+%{\bf Lyudmila Mihaylova}   \\
+%}
 
@@
 Therefore, Bayesian neural networks estimate both an output for a test data and uncertainty of this prediction.
-Uncertainty of the prediction is a result of propagating weight uncertainty via layers of a network.
-We propose a novel method of propagating uncertainty through the soft-thresholding nonlinearity.
-The method expands the area of Bayesian neural networks and enables the soft-thresholding nonlinearity to be included in Bayesian deep neural networks for the first time.
+Uncertainty of the prediction is a result of propagating weight uncertainty through layers of a network.
+We propose a novel method of propagating uncertainty through the soft thresholding nonlinearity.
+The method expands the area of Bayesian neural networks and enables the soft thresholding nonlinearity to be included in Bayesian deep neural networks for the first time.
 As an example we design a Bayesian Learned Iterative Shrinkage-Thresdholding Algorithm (Bayesian \textsc{lista}) network.
 We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.
-A series of experiments on sparse coding show that the proposed framework provide both accurate predictions and quantified estimates of uncertainty in these predictions.
+A series of experiments on sparse coding shows that the proposed framework provide both accurate predictions and quantified estimates of uncertainty in these predictions.
 \end{abstract}
@@
 
-Neural networks address the sparse coding problem with the soft-thresholding nonlinearity, that shifts current estimates towards zero \citep{gregor2010learning}.
-In this paper we propose a method to propagate uncertainty through the soft-thresholding nonlinearity.
+Neural networks address the sparse coding problem with the soft thresholding nonlinearity, that shifts current estimates towards zero \citep{gregor2010learning}.
+In this paper we propose a method to propagate uncertainty through the soft thresholding nonlinearity.
 At every layer the current distribution of the target vector is represented as a spike-and-slab distribution \citep{mitchell1988bayesian}.
 We show that it can be effectively combined with Gaussian weights of dense layers.
-The distribution of the target vector propagated through a dense layer and soft-thresholding nonlinearity can then be closely approximated with a distribution from the same family.
+The distribution of the target vector propagated through a dense layer and soft thresholding nonlinearity can then be closely approximated with a distribution from the same family.
 
-The proposed method of uncertainty propagation for the soft-thresholding nonlinearity allows us to derive the gradients of the logarithms of normalisation constants, which can be used to update weights distribution.
+The proposed method of uncertainty propagation for the soft thresholding nonlinearity allows us to derive the gradients of the logarithms of normalisation constants, which can be used to update weights distribution.
 We then develop a highly efficient Bayesian inference algorithm based on the probabilistic backpropagation paradigm while significantly expanding it.
@@
 \begin{itemize}
-\item for the first time we propose a method for uncertainty propagation through the soft-thresholding nonlinearity for a Bayesian neural network
-\item we develop efficient posterior inference for weights and outputs of neural networks with the soft-thresholding nonlinearity
-\item we design a novel Bayesian neural network for sparse coding
+\item for the first time we propose a method for uncertainty propagation through the soft thresholding nonlinearity for a Bayesian neural network;
+\item we develop efficient posterior inference for weights and outputs of neural networks with the soft thresholding nonlinearity;
+\item we design a novel Bayesian neural network for sparse coding.
 \end{itemize}
@@
 
-Lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft-thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$.
+Lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$.
 Overall the probabilistic layer is described by theorem \ref{thm:prob_layer}.
@@
 \label{thm:soft_thresholding}
-When a Gaussian-distributed random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft-thresholding function it can be approximated with the spike and slab distribution on $x^*$ with the probability of spike $\omega^*$, slab mean $m^*$ and slab variance $v^*$ (parameters of the approximating distribution are given in the proof).
+When a Gaussian-distributed random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft thresholding function it can be approximated with the spike and slab distribution on $x^*$ with the probability of spike $\omega^*$, slab mean $m^*$ and slab variance $v^*$ (parameters of the approximating distribution are given in the proof).
 \end{lemma}
@@
 
-The probability of spike $\omega^*$ equals to the probability mass of the original distribution that lies in $(-\lambda, \lambda)$  and is flattened into zero by soft-thresholding operator.
+The probability of spike $\omega^*$ equals to the probability mass of the original distribution that lies in $(-\lambda, \lambda)$  and is flattened into zero by soft thresholding operator.
 As the original distribution is Gaussian, this can be computed as
@@
 
-Soft-thresholding shifts elements that are greater than $\lambda$  or less than $-\lambda$ elements towards 0.
-Let $\psi(\cdot)$ denote the density of the soft-threshold distribution, $\phi(\cdot)$ denote the density of the original Gaussian distribution.
+Soft thresholding shifts elements that are greater than $\lambda$  or less than $-\lambda$ elements towards 0.
+Let $\psi(\cdot)$ denote the density of the soft thresholded distribution, $\phi(\cdot)$ denote the density of the original Gaussian distribution.
 Then the first moment of the resulting distribution is
@@
 First, in lemma \ref{thm:matrix_vector} a Gaussian matrix is multiplied by a spike-and-slab vector and their product is approximated with the Gaussian distribution.
-Second, in lemma \ref{thm:soft_thresholding} the result of soft-thresholding of a Gaussian vector is approximated with the spike-and-slab distribution.
+Second, in lemma \ref{thm:soft_thresholding} the result of soft thresholding of a Gaussian vector is approximated with the spike-and-slab distribution.
 In this section we demonstrate that these approximations are close to the real distributions.

### 2018-03-09 paper/BayesianLISTA.tex
changed mnist to nonnormlized

@@
 
-Figure \ref{fig:mnist_250} presents \textsc{nmse} loss on the validation set with dictionary of size $250$.
+Figures \ref{fig:mnist_100} and \ref{fig:mnist_250} present quality on the validation set with dictionaries of size $100$ and $250$.
 
@@
 
-%\begin{figure}[t]
-%%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
-%%~
-%\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
-%\newline
-%%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
-%%~
-%\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
-%\caption{\textsc{mnist} with dictionary $100$}
-%\label{fig:mnist_100}
-%\end{figure}
+\begin{figure}[t]
+%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
+%~
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
+\newline
+%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
+%~
+\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
+\caption{\textsc{mnist} with dictionary $100$}
+\label{fig:mnist_100}
+\end{figure}
 

### 2018-03-09 theano/compare_mnist/mnist_data.py

@@ -24,7 +24,7 @@ class MnistData(object):
         self.training_size = train_size
         self.validation_size = valid_size
 
-    def check_download(self):
+    def check_download(self, normalise):
         mnist = tf.contrib.learn.datasets.load_dataset("mnist")
         random_train_ind = np.random.choice(mnist.train.images.shape[0], self.training_size, replace=False)
         self.train_data = mnist.train.images[random_train_ind]
@@ -35,7 +35,8 @@ class MnistData(object):
         self.validation_data = mnist.validation.images[random_validation_ind]
         #self.validation_labels = np.asarray(mnist.validation.labels, dtype=np.int32)
 
-        self.normalize()
+        if normalise:
+            self.normalize()
 
     def normalize(self):
         self.train_mean = np.mean(np.append(self.train_data, self.validation_data, axis=0), axis=0)

### 2018-03-09 theano/experiments/mnist/collect_results_nonnormalised.py

@@ -1,0 +1,147 @@
+import errno
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+
+class MnistExperimentResultsCollector(object):
+    def __init__(self):
+        self.n_iter = 500
+
+    def collect_all(self, undersampling):
+        self.ista_f_meas_train, self.ista_f_meas_validation, self.ista_loss_train, self.ista_loss_validation = \
+            self.collect_ista_fista('ista_fista/results_{}_K_ista.npz'.format(undersampling))
+        self.fista_f_meas_train, self.fista_f_meas_validation, self.fista_loss_train, self.fista_loss_validation = \
+            self.collect_ista_fista('ista_fista/results_{}_K_fista.npz'.format(undersampling))
+        self.freq_f_meas_train, self.freq_f_meas_validation, self.freq_loss_train, self.freq_loss_validation, \
+        self.sh_bayes_f_meas_train, self.sh_bayes_f_meas_validation, self.sh_bayes_loss_train, self.sh_bayes_loss_validation = \
+            self.collect_main('non_normalised_results/mnist_100_train_20_layers_K_{}'.format(undersampling))
+
+    def collect_ista_fista(self, fileprefix):
+        saved_res = np.load(fileprefix)
+        f_meas_train = saved_res['train_f_meas']
+        f_meas_validation = saved_res['validation_f_meas']
+        loss_train = saved_res['train_loss']
+        loss_validation = saved_res['validation_loss']
+
+        return f_meas_train, f_meas_validation, loss_train, loss_validation
+
+    def collect_main(self, filename_prefix):
+        saved_bayes_weights = np.load('{}_bayes_weights.npz'.format(filename_prefix))
+        bayes_S_M = saved_bayes_weights['bayes_S_M']
+        bayes_S_V = saved_bayes_weights['bayes_S_V']
+        bayes_W_M = saved_bayes_weights['bayes_W_M']
+        bayes_W_V = saved_bayes_weights['bayes_W_V']
+
+        saved_beta_est = np.load('{}_beta_est.npz'.format(filename_prefix))
+        freq_beta_train_est=saved_beta_est['freq_beta_train_est']
+        freq_beta_validation_est=saved_beta_est['freq_beta_validation_est']
+        shared_beta_train_est=saved_beta_est['shared_beta_train_est']
+        shared_beta_validation_est=saved_beta_est['shared_beta_validation_est']
+        true_beta_train=saved_beta_est['true_beta_train']
[…]

### 2018-03-09 theano/experiments/mnist/mnist_100_train_20_layers_K_250_ista_fista.py

@@ -16,7 +16,7 @@ class MnistSequentialComparatorIstaFista(SequentialComparatorIstaFista):
                  train_freq=False, train_bayes=False, train_shared_bayes=False, use_ista=True, use_fista=True, save_history=False):
 
         self.data = MnistData(K=K)
-        self.data.check_download()
+        self.data.check_download(normalise=False)
         self.data.learn_dictionary()
         self.D = self.data.train_data.shape[1]
 
@@ -38,7 +38,7 @@ if __name__ == '__main__':
 
     np.random.seed(1)
 
-    K = 100
+    K = 250
     L = 20
 
     comparator = MnistSequentialComparatorIstaFista(K, L, learning_rate=0.0001, n_train_sample=100,
@@ -52,4 +52,4 @@ if __name__ == '__main__':
     comparator.plot_quality_history()
 
 
-    comparator.save_numpy('ista_fista/results')
+    comparator.save_numpy('ista_fista/results_{}_K'.format(K))

### 2018-03-09 theano/experiments/mnist/posterior_plotter.py

@@ -61,25 +61,26 @@ if __name__ == '__main__':
 
     np.random.seed(1)
 
-    bayes_weights = np.load('./normalised_results/mnist_100_train_20_layers_K_250_bayes_weights.npz')
-    dictionary = np.load('./normalised_results/mnist_100_train_20_layers_K_250_dictionary.npz')
-    data = np.load('./normalised_results/mnist_100_train_20_layers_K_250_beta_est.npz')
+    bayes_weights = np.load('./non_normalised_results/mnist_100_train_20_layers_K_250_bayes_weights.npz')
+    data = np.load('./non_normalised_results/mnist_100_train_20_layers_K_250_beta_est.npz')
 
     y_validation = data['y_validation']
     beta_validation = data['true_beta_validation']
 
-    bayes_lista = SingleBayesianListaHandler(bayes_weights['D'],
-                                             bayes_weights['K'], bayes_weights['L'], dictionary['X'])
-
-    bayes_lista.pbp_instance.network.params_W_M.set_value(bayes_weights['bayes_W_M'])
-    bayes_lista.pbp_instance.network.params_W_V.set_value(bayes_weights['bayes_W_V'])
-    bayes_lista.pbp_instance.network.params_S_M.set_value(bayes_weights['bayes_S_M'])
-    bayes_lista.pbp_instance.network.params_S_V.set_value(bayes_weights['bayes_S_V'])
 
 
-    plotter = PosteriorPlotter()
-
-    example_num = 0
-
-    plotter.plot_posterior_samples_mnist(bayes_lista, y_validation[example_num], 3)
-    plotter.plot_posterior_parameters_mnist(bayes_lista, y_validation[example_num])
+    # bayes_lista = SingleBayesianListaHandler(bayes_weights['D'],
+    #                                          bayes_weights['K'], bayes_weights['L'], dictionary['X'])
+    #
+    # bayes_lista.pbp_instance.network.params_W_M.set_value(bayes_weights['bayes_W_M'])
+    # bayes_lista.pbp_instance.network.params_W_V.set_value(bayes_weights['bayes_W_V'])
+    # bayes_lista.pbp_instance.network.params_S_M.set_value(bayes_weights['bayes_S_M'])
+    # bayes_lista.pbp_instance.network.params_S_V.set_value(bayes_weights['bayes_S_V'])
+    #
+    #
+    # plotter = PosteriorPlotter()
+    #
+    # example_num = 0
+    #
[…]

### 2018-03-09 paper/BayesianLISTA.tex
small updates to text

@@
 
-\section{Introduction}
+\section{\uppercase{Introduction}}
 Though the idea of Bayesian learning in neural networks is not new \citep{neal2012bayesian}, it has regained its attention recently with the development of distributed approximate inference techniques \citep{li2015stochastic, hoffman2013stochastic}  and general boost in popularity of deep learning.
@@
 
-\section{Neural networks for sparse coding}
+\section{\uppercase{Neural networks for sparse coding}}
 \label{sec:nn_sc}
@@
 
-\section{Bayesian neural network for sparse coding}
+\section{\uppercase{Bayesian neural network for sparse coding}}
 \label{sec:bayesian_lista}
@@
 This section presents the proposed Bayesian neural network for sparse coding. To formulate the Bayesian version of \textsc{lista} we impose the prior distributions on the unknown weights
+\begin{subequations}
+\label{eq:ws}
 \begin{align}
@@
 \end{align}
+\end{subequations}
 where $w_{ij}$ is a component of the matrix $\mathbf{W}$, $s_{d'd''}$ is a component of the matrix $\mathbf{S}$, $\eta$ is the precision of the Gaussian distribution.
@@
 The prior of the introduced Gaussian precisions are set to the Gamma distribution with parameters $a^{\cdot}$ and $b^{\cdot}$:
+\begin{subequations}
+\label{eq:gamma_eta}
 \begin{align}
@@
 \end{align}
+\end{subequations}
 
@@
 
-\section{Uncertainty propagation through soft thresholding}
+\section{\uppercase{Uncertainty propagation through soft thresholding}}
 \label{sec:fprop}
@@
 \begin{equation}
-[\boldsymbol\beta_{l-1}]_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d),
+[\widehat{\boldsymbol\beta}_{l-1}]_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d),
 \end{equation}
@@
   \label{thm:matrix_vector}
- Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\boldsymbol\beta \in \mathbb{R}^D$ be a vector with spike-and-slab distributed variables: $\beta_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
+ Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta }\in \mathbb{R}^D$ be a vector with spike-and-slab distributed variables: $\widehat{\beta}_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
 If their product is approximated as a vector $\mathbf{e} \in \mathbb{R}^{D}$ of random variables $e_d \sim \mathcal{N}(m^e_d, w^e_d)$, then
@@
  \begin{proof}
- 	We compute the mean and variance of the product $\mathbf{S}\boldsymbol\beta$ with an assumption of independence of its components and approximate resulting distribution with Gaussian.
+ 	We compute the mean and variance of the product $\mathbf{S}\widehat{\boldsymbol\beta}$ with an assumption of independence of its components and approximate resulting distribution with Gaussian.
 The quality of this approximation is discussed in section \ref{sec:approx_quality}
 \begin{flalign*}
-	\mathbb{E}e_d &= \sum_{d'=1}^D \mathbb{E}[s_{dd'}\beta_{d'}]  = \sum_{d'=1}^D m^s_{dd'}\mathbb{E}\beta_{d'}\\
-	\operatorname{Var}e_d &= \sum_{d'=1}^D \operatorname{Var}[s_{dd'}\beta_{d'}] = \sum_{d'=1}^D [(\mathbb{E}s_{dd'})^2 \operatorname{Var}\beta_{d'} \\
-	&{}+ (\mathbb{E}\beta_{d'})^2 \operatorname{Var}s_{dd'} + \operatorname{Var}\beta_{d'} \operatorname{Var}s_{dd'}]
+	\mathbb{E}e_d &= \sum_{d'=1}^D \mathbb{E}[s_{dd'}\widehat{\beta}_{d'}]  = \sum_{d'=1}^D m^s_{dd'}\mathbb{E}\widehat{\beta}_{d'}\\
+	\operatorname{Var}e_d &= \sum_{d'=1}^D \operatorname{Var}[s_{dd'}\widehat{\beta}_{d'}] = \sum_{d'=1}^D [(\mathbb{E}s_{dd'})^2 \operatorname{Var}\widehat{\beta}_{d'} \\
+	&{}+ (\mathbb{E}\widehat{\beta}_{d'})^2 \operatorname{Var}s_{dd'} + \operatorname{Var}\widehat{\beta}_{d'} \operatorname{Var}s_{dd'}]
 \end{flalign*}
-where $\mathbb{E}\beta_{d'}$, $\operatorname{Var}\beta_{d'}$ are computed according to lemma~\ref{thm:moments_spsl}.
+where $\mathbb{E}\widehat{\beta}_{d'}$, $\operatorname{Var}\widehat{\beta}_{d'}$ are computed according to lemma~\ref{thm:moments_spsl}.
  \end{proof}
@@
 \label{thm:prob_layer}
-The spike and slab distribution for $\boldsymbol\beta$ with can be propagated through the \textsc{lista} layer and the parameters after propagation can be computed as following:
+The spike and slab distribution for $\widehat{\boldsymbol\beta}$ with can be propagated through the \textsc{lista} layer and the parameters after propagation can be computed as following:
 \begin{enumerate}
 	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is computed according to lemma \ref{thm:matrix_const};
-	\item $\mathbf{e} = \mathbf{S}\boldsymbol\beta_{l-1}$ is computed according to lemma \ref{thm:matrix_vector};
+	\item $\mathbf{e} = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is computed according to lemma \ref{thm:matrix_vector};
 	\item $\mathbf{c} = \mathbf{b} + \mathbf{e}$ is computed according to lemma \ref{thm:sum_vectors};
-	\item $\boldsymbol\beta_{l} = h_\lambda(\mathbf{c})$ is computed according to lemma \ref{thm:soft_thresholding}.
+	\item $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c})$ is computed according to lemma \ref{thm:soft_thresholding}.
 \end{enumerate}
@@
 
-\subsection{Approximation quality}
+\subsection{\uppercase{Approximation quality}}
 \label{sec:approx_quality}
@@
 
-\section{Backpropagation}
+\section{\uppercase{Backpropagation}}
 \label{sec:backpropagation}
-\subsection{Likelihood}
-For Bayesian inference we significantly expend the probabilistic backpropagation algorithm~\citep{hernandez2015probabilistic} for computing parameter updates.
-It is based on assumed density filtering (ADF) and expectation propagation (EP) and allows to update parameters of the distributions based on the derivative of the logarithm of a normalisation constant.
-ADF is based on iteratively incorporating factors from the true posterior to a factorised approximating distribution, whereas in EP factors in an approximating distribution are iteratively replaced by factors from the true posterior.
 
@@
 \begin{align}
+\label{eq:approximating_dsitribution}
 \begin{split}
@@
 \end{align}
+
+For Bayesian inference we expand the probabilistic backpropagation algorithm~\citep{hernandez2015probabilistic} for computing parameter updates.
+It is based on assumed density filtering (ADF) and expectation propagation (EP) and allows to update parameters of the distributions based on the derivative of the logarithm of a normalisation constant.
+ADF is based on iterative incorporation of factors from the true posterior $p$ (\ref{eq:posterior}) into the factorised approximating distribution $q$ (\ref{eq:approximating_dsitribution}), whereas in EP factors in the $q$ are iteratively replaced by factors from $p$.
+
+When a factor $p$ is incorporated into $q$, $q$ as a function of Gaussian-distributed weights $W$  and $S$ has the following form:
+\begin{equation}
+q(\cdot) = Z^{-1}f(\cdot)\mathcal{N}(\cdot; m, v)
+\end{equation}
+where $Z$ is the normalisation constant and $f(\cdot)$ - arbitrary function.
+
+According to \cite{minka2001thesis}, new parameters of Gaussian distribution for$ \cdot$ can be computed as
+\begin{align}
+m^{\text{new}} &= m + v \frac{\partial \log Z}{\partial m}, \\
+v^{\text{new}} &= v - v^2\left[ \left(\frac{\partial \log Z}{\partial m}\right)^2 - 2 \frac{\partial \log Z}{\partial v}\right]
+\end{align}
+
+Then to find new values of $W$, $S$ we need to compute the $Z$ every time when the factor of the true posterior is incorporated in $q$.
+
+\subsection{\uppercase{Likelihood}}
 
@@
 \end{align}
-We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\mathbf{z}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximated with the spike and slab distribution with parameters $\boldsymbol\omega^{z_L}$, $\mathbf{m}^{z_l}$, and $\mathbf{v}^{z_L}$
+We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximated with the spike and slab distribution with parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}_L}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}_L}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}_L}$
 \begin{align}
-&Z \approx \int \prod_{d=1}^{D} \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma^{-1}) \nonumber \\
-&\times (\omega^{z_L}_d \delta_0([\mathbf{z}_L]_d) + (1 - \omega^{z_L}_d)\mathcal{N}([\mathbf{z}_L]_d | m^{z_L}_d, v^{z_L}_d)) \nonumber\\
-&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}\mathbf{z}_L \mathrm{d}\gamma  \nonumber\\
-&= \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma^{-1})  \delta_0([\mathbf{z}_L]_d) \nonumber \\
-&\times \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[\mathbf{z}_L]_d \mathrm{d}\gamma  \nonumber\\
-& + (1 - \omega^{z_L}_d)\int \big[\mathcal{N}(\beta_d | [\mathbf{z}_L]_d, \gamma^{-1})\nonumber\\
-&\times \mathcal{N}([\mathbf{z}_L]_d | m^{z_L}_d, v^{z_L}_d)) \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[\mathbf{z}_L]_d \mathrm{d}\gamma\Big]  \nonumber\\
-& = \prod_{d=1}^{D} \Big[\omega^{z_L}_d \int \mathcal{N}(\beta_d | 0, \gamma^{-1})  \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma) d\gamma  \nonumber\\
-& + (1 - \omega^{z_L}_d)\int \big[\mathcal{T}(\beta_d | [\mathbf{z}_L]_d, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma)  \nonumber\\
-&\times \mathcal{N}([\mathbf{z_L}]_d| m^{z_L}_d, v^{z_L}_d))\big] \mathrm{d}[\mathbf{z}_L]_d\Big]  \nonumber\\
-& \approx \prod_{d=1}^D \Big[\omega^{z_L}_d  \mathcal{T}(\beta_d | 0, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma) \nonumber \\ 
+&Z \approx \int \prod_{d=1}^{D} \big[\mathcal{N}(\beta_d | [\widehat{\boldsymbol\beta}_L]_d, \gamma^{-1}) \nonumber \\
+&\times (\omega^{\widehat{\boldsymbol\beta}_L}_d \delta_0([\widehat{\boldsymbol\beta}_L]_d) + (1 - \omega^{\widehat{\boldsymbol\beta}_L}_d)\mathcal{N}([\widehat{\boldsymbol\beta}_L]_d | m^{\widehat{\boldsymbol\beta}_L}_d, v^{\widehat{\boldsymbol\beta}_L}_d)) \nonumber\\
+&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}\widehat{\boldsymbol\beta}_L \mathrm{d}\gamma  \nonumber\\
+&= \prod_{d=1}^{D} \Big[\omega^{\widehat{\boldsymbol\beta}_L}_d \int \big[\mathcal{N}(\beta_d | [\widehat{\boldsymbol\beta}_L]_d, \gamma^{-1})  \delta_0([\widehat{\boldsymbol\beta}_L]_d) \nonumber \\
+&\times \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[\widehat{\boldsymbol\beta}_L]_d \mathrm{d}\gamma  \nonumber\\
+& + (1 - \omega^{\widehat{\boldsymbol\beta}_L}_d)\int \big[\mathcal{N}(\beta_d | [\widehat{\boldsymbol\beta}_L]_d, \gamma^{-1})\nonumber\\
+&\times \mathcal{N}([\widehat{\boldsymbol\beta}_L]_d | m^{\widehat{\boldsymbol\beta}_L}_d, v^{\widehat{\boldsymbol\beta}_L}_d)) \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[\widehat{\boldsymbol\beta}_L]_d \mathrm{d}\gamma\Big]  \nonumber\\
+& = \prod_{d=1}^{D} \Big[\omega^{\widehat{\boldsymbol\beta}_L}_d \int \mathcal{N}(\beta_d | 0, \gamma^{-1})  \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma) d\gamma  \nonumber\\
+& + (1 - \omega^{\widehat{\boldsymbol\beta}_L}_d)\int \big[\mathcal{T}(\beta_d | [\widehat{\boldsymbol\beta}_L]_d, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma)  \nonumber\\
+&\times \mathcal{N}([\mathbf{\widehat{\boldsymbol\beta}_L}]_d| m^{\widehat{\boldsymbol\beta}_L}_d, v^{\widehat{\boldsymbol\beta}_L}_d))\big] \mathrm{d}[\widehat{\boldsymbol\beta}_L]_d\Big]  \nonumber\\
+& \approx \prod_{d=1}^D \Big[\omega^{\widehat{\boldsymbol\beta}_L}_d  \mathcal{T}(\beta_d | 0, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma) \nonumber \\ 
 \label{eq:Z_approx}
-&+ (1 - \omega^{z_L}_d)\mathcal{N}(\beta_d | m^{z_L}_d, \frac{\beta^\gamma}{\alpha^\gamma - 1} + v^{z_L})\Big]
+&+ (1 - \omega^{\widehat{\boldsymbol\beta}_L}_d)\mathcal{N}(\beta_d | m^{\widehat{\boldsymbol\beta}_L}_d, \frac{\beta^\gamma}{\alpha^\gamma - 1} + v^{\widehat{\boldsymbol\beta}_L})\Big]
 \end{align}
@@
 
-[ADD ON EP UPDATE OF PRIOR INCORPORATED]
+\subsection{\uppercase{Prior}}
+Prior factors from $p$ (\ref{eq:ws}, \ref{eq:gamma_eta}) are incorporated into $q$ with the EP algorithm, i.e.
+they replace the corresponding approximating factors from $q$ and then $q$ is updated to minimise its KL divergence with $q$ that has the true factor incorporated.
 
-\subsection{Hyperparameter optimisation}
+\subsection{\uppercase{Hyperparameter optimisation}}
 The only hyperparameter in the proposed Bayesian \textsc{lista} is the shrinkage parameter $\lambda$.
@@
 
-\section{Experiments}
+\section{\uppercase{Experiments}}
 \label{sec:experiments}
@@
 
-\subsection{Predictive performance on synthetic data}
+\subsection{\uppercase{Predictive performance on synthetic data}}
 First, the predictive performance of the proposed Bayesian \textsc{lista} is analysed on synthetic data.
@@
 
-\subsection{Predictive performance on \textsc{mnist} data}
+\subsection{\uppercase{Predictive performance on mnist data}}
 Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \citep{lecun1998gradient}.
@@
 
-\subsection{Active learning on \textsc{mnist}}
+\subsection{\uppercase{Active learning on mnist}}
 To demonstrate the potential scenario that can benefit from uncertainty estimates of the Bayesian \textsc{lista} we consider the active learning example \citep{settles.tr09}.
@@
 
-\section{Discussion}
+\section{\uppercase{Discussion}}
 \label{sec:discussion}
@@
 
-\section{Conclusions and future work}
+\section{\uppercase{Conclusions and future work}}
 \label{sec:conclusions}
@@
 The shrinkage parameter $\lambda$ is currently treated as a deterministic hyperparameter for the Baysian \textsc{lista}.
-In future we plan to incorporate it inside the model treating it as a random variable.
+In future we plan to incorporate it into the model treating it as a random variable.
 For this we need to extend both the uncertainty propagation method to include uncertainty of $\lambda$ and the probabilistic backpropagation algorithm to estimate its posterior.

### 2018-03-10 paper/BayesianLISTA.tex
trying to interpret results

@@
 \label{sec:nn_sc}
-The sparse coding and sparse inverse problems are the linear regression with the assumption of sparse weights
+The sparse coding problem is the linear regression with the assumption of sparse weights
 \begin{equation}
@@
 \label{sec:experiments}
-The proposed Bayesian \textsc{lista} is evaluated in the context of the sparse inverse problem, where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
+The proposed Bayesian \textsc{lista} is evaluated in the context of the sparse coding problem with underdefined dictionary, where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
 
@@
 where precision is the fraction of estimated slab locations that are correct, recall is the fraction of true slab locations among all predicted slab locations.
-We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn anything.
+We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn.
 
@@
 
-In the Figure \ref{fig:number_of_layers_synthetic} prediction performance for different number of layers $L$ is presented. The observation size is set as $K=50$.
+In the Figure \ref{fig:number_of_layers_synthetic} prediction performance for different number of layers $L$ is presented.
+The observation size is set as $K=50$.
+In both experiments the performance of the Bayesian \textsc{lista} is better than the performance of \textsc{lista}.
+Although the baseline \textsc{ista} and \textsc{fista} show better performance in terms of F measure, Bayesian \textsc{lista} has lower \textsc{nmse}.
 
-In the Figure \ref{fig:unsersampling_synthetic} prediction performance for different observation sizes $K$ is presented. The number of layers is set as $L=4$.
+In the Figure \ref{fig:unsersampling_synthetic} prediction performance for different observation sizes $K$ is presented.
+The number of layers is set as $L=4$ which is the value of the poorest performance of Bayesian \textsc{lista} according to the previous experiment.
+Bayesian \textsc{lista} provides better results than {lista} for $K \ge 30$ and better results than other algorithms for $K \ge 70$.
 
@@
 Figures \ref{fig:mnist_100} and \ref{fig:mnist_250} present quality on the validation set with dictionaries of size $100$ and $250$.
+When $K=100$ Bayesian \textsc{lista} shows better performance that other algorithms and on $K=250$ it  converges to similar values as \textsc{lista}.
 
@@
 %\end{figure}
-\begin{figure*}[t]
-\subfloat[$\beta$ posterior mean]{\includegraphics[width=0.66\columnwidth]{posterior_mean}}
-\subfloat[$\beta$ posterior std]{\includegraphics[width=0.66\columnwidth]{posterior_std}}
-\subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.66\columnwidth]{posterior_spike_indicator}}
+\begin{figure}[t]
+\subfloat[$\beta$ posterior mean]{\includegraphics[width=0.33\columnwidth]{posterior_mean}}~
+\subfloat[$\beta$ posterior std]{\includegraphics[width=0.33\columnwidth]{posterior_std}}~
+\subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.33\columnwidth]{posterior_spike_indicator}}
 \caption{Posterior for the digit 7.}
 \label{fig:posterior_distribution}
-\end{figure*}
-\begin{figure*}[t]
-\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_0}}
-\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_1}}
-\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_2}}
+\end{figure}
+\begin{figure}[t]
+\subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_0}}~
+\subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_1}}~
+\subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_2}}
 \caption{Samples from the posterior for the digit 7.}
 \label{fig:posterior_samples}
-\end{figure*}
+\end{figure}
 
@@
 Both algorithms of new data sampling were run with $20$ random seeds and their performance was averaged.
-Figure \ref{fig:active_learning_mnist} demonstrates their performance.
+Figure \ref{fig:active_learning_mnist} demonstrates their performance.The uncertainty sampling has some advantage compared to random sampling, this means that the posterior variance is adequately estimated.
 \begin{figure}[t]
@@
 \label{sec:discussion}
-As far as the authors aware, this is the first implementation of Bayesian deep sparse coding algorithm.
+To the best of our knowledge, this is the first implementation of Bayesian deep sparse coding algorithm.
 Although there are works on Bayesian sparsity in context of neural networks \citep{he2017bayesian}, they are not the Bayesian neural networks in the same sense as Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.

### 2018-03-10 paper/BayesianLISTA.tex
minor text fixes

@@
 In this paper we propose a method to propagate uncertainty through the soft thresholding nonlinearity.
-At every layer the current distribution of the target vector is represented as a spike-and-slab distribution \citep{mitchell1988bayesian}.
+At every layer the current distribution of the target vector is represented as a spike and slab distribution \citep{mitchell1988bayesian}.
 We show that it can be effectively combined with Gaussian weights of dense layers.
@@
 The paper is organised as following: first, we review neural networks for sparse coding in section \ref{sec:nn_sc} and present a novel Bayesian neural network in section \ref{sec:bayesian_lista}.
-We then describe uncertainty propagation to obtain the spike-and-slab distribution for an output of a network in section \ref{sec:fprop} and how probabilistic backpropagation is organised to update distributions of weights in section \ref{sec:backpropagation}.
+We then describe uncertainty propagation to obtain the spike and slab distribution for an output of a network in section \ref{sec:fprop} and how probabilistic backpropagation is organised to update distributions of weights in section \ref{sec:backpropagation}.
 After that, we show the experimental results of the algorithm in section \ref{sec:experiments} and finish with discussion and conclusions in sections \ref{sec:discussion} and \ref{sec:conclusions}.
@@
 Vectors $\mathbf{c}_l$, $\mathbf{b}$ are intermediate vectors that describe forward propagation.
-$\boldsymbol\beta_l$ is the current approximation of the target coefficient vector at the layer $l$.
 
@@
 We have used two approximations in forward propagation of uncertainty.
-First, in lemma \ref{thm:matrix_vector} a Gaussian matrix is multiplied by a spike-and-slab vector and their product is approximated with the Gaussian distribution.
-Second, in lemma \ref{thm:soft_thresholding} the result of soft thresholding of a Gaussian vector is approximated with the spike-and-slab distribution.
+First, in lemma \ref{thm:matrix_vector} a Gaussian matrix is multiplied by a spike and slab vector and their product is approximated with the Gaussian distribution.
+Second, in lemma \ref{thm:soft_thresholding} the result of soft thresholding of a Gaussian vector is approximated with the spike and slab distribution.
 In this section we demonstrate that these approximations are close to the real distributions.
@@
 We generate $N_\text{train}=500$ sparse coefficients vectors $\boldsymbol\beta_n$ each of size $D = 100$.
-Coefficients $\boldsymbol\beta$ are generated from the spike-and-slab distribution with truncated slab: each component of $\beta_{nd}$ is zero with probability $0.8$ or is from standard Gaussian distribution without interval $(-0.1, 0.1)$ with probability $0.2$.
+Coefficients $\boldsymbol\beta$ are generated from the spike and slab distribution with truncated slab: each component of $\beta_{nd}$ is zero with probability $0.8$ or is from standard Gaussian distribution without interval $(-0.1, 0.1)$ with probability $0.2$.
 Truncation of the zeros allows to remove from support pattern values with insignificant contributions \citep{xin2016maximal}.

### 2018-03-10 paper/BayesianLISTA.tex
uncertainty propagation section is redone

--- 2018-03-09 paper/BayesianLISTA.tex
@@
 \begin{align}
+\label{eq:first_layer}
 &\mathbf{b} = \mathbf{W}\mathbf{y}\\
-&\widehat{\boldsymbol\beta}_0 = h_\lambda(\mathbf{b}_0) \\
+\label{eq:thr_first}
+&\widehat{\boldsymbol\beta}_0 = h_\lambda(\mathbf{b}) \\
 &\text{for } l=1:L\\
+\label{eq:l_dense_layer}
 	&\quad \mathbf{c}_l = \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1} \\
+\label{eq:l_thr}
 	&\quad \widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l) \\
@@
 \end{align}
-where $[\cdot]_d$ is the d-th component of a vector, $f(\mathbf{y}^{(n)}; \mathbf{W}, \mathbf{S}, \lambda)$ is the output of the Bayesian \textsc{lista} neural network, $\gamma$ is the precision of the Gaussian distribution.
+where $[\cdot]_d$ denotes the d-th component of a vector, $f(\mathbf{y}^{(n)}; \mathbf{W}, \mathbf{S}, \lambda)$ is the output of the Bayesian \textsc{lista} neural network, $\gamma$ is the precision of the Gaussian distribution.
 The prior of the introduced Gaussian precisions are set to the Gamma distribution with parameters $a^{\cdot}$ and $b^{\cdot}$:
@@
 
-Later in this section we show that the value of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with a spike and slab distribution and, therefore, it maintains the same family of distributions.
-This leads to the proposed probabilistic backpropagation algorithm that is described in Section~\ref{sec:backpropagation}.
+Later in this section, we show that the output $\widehat{\boldsymbol\beta}_l$ of the next layer can be approximated with a spike and slab distribution and, therefore, it maintains the same family of distributions.
+This leads to the proposed probabilistic backpropagation algorithm that is presented in Section~\ref{sec:backpropagation}.
 We now describe how to propagate uncertainty through the layers of the Bayesian \textsc{lista} step by step stating meanwhile theoretical facts required for the method.
 
-Lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$.
-Overall the probabilistic layer is described by theorem \ref{thm:prob_layer}.
+\subsection{\uppercase{Initialisation dense layer}}
+The first step in the Bayesian \textsc{lista} is (\ref{eq:first_layer}). The matrix $\mathbf{W}$ consists of Gaussian-distributed components and $y$ is a deterministic vector.
 
-\begin{lemma}[Moments of spike and slab distribution]
+ \begin{lemma}[Product of Gaussian matrix and constant vector]
+ \label{thm:matrix_const}
+Let $\mathbf{W} \in \mathbb{R}^{D \times K}$ be a matrix of independent Gaussian-distributed random variables: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y} \in \mathbb{R}^K$ be a constant vector.
+Then their product $\mathbf{W} \mathbf{y}$ is a vector $\mathbf{b} \in \mathbb{R}^{D}$ of random variables $b_d \sim \mathcal{N}(m^b_d, w^b_d)$, where
+\begin{subequations}
+\begin{align}
+m^b_d &= \sum_{k=1}^Ky_k m^w_{dk}, \\
+w^b_d &= \sum_{k=1}^Ky_k^2v^w_{dk}.
+ \end{align}
+\end{subequations}
+
+ \end{lemma}
+ \begin{proof}
+ 	The statement follows from the property that the family of normal distributions is closed under linear transformations.
+ \end{proof}
+
+According to Lemma~\ref{thm:matrix_const}, $\mathbf{b}$ in~(\ref{eq:first_layer}) is a vector of Gaussian-distributed components.
+
+\subsection{\uppercase{Soft thresholding nonlinearity}}
+At the second step (\ref{eq:thr_first}) of the Bayesian \textsc{lista} the Gaussian vector $\mathbf{b}$ is taken as an input of the soft thresholding function.
+
+When a Gaussian-distributed random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft thresholding function: $x^* = h_{\lambda}(x)$ the probability mass of a resulting random variable $x^*$ is split into two parts.
+The values of $x$ from the interval $[-\lambda, \lambda]$ are converted to $0$ by the soft thresholding operator.
+Therefore, the probability mass of the original distribution that lies in $[-\lambda, \lambda]$ is squeezed into the probability of $x^*$ being zero.
+The values of $x$ from outside of the $[-\lambda, \lambda]$ interval are shifted towards $0$.
+Therefore, the distribution of $x^* \neq 0$ represents the tails of the original Gaussian distribution.
+
+\begin{lemma}[Propagation of a Gaussian distribution through soft thresholding]
+\label{thm:soft_thresholding}
+The distribution of $x^*$ can be parametrised by the probability of being zero, $\omega^*$, the mean $m^*$ and the variance $v^*$ of the truncated Gaussian distribution.
+\end{lemma}
+\begin{proof}
+
+The probability of a zero $\omega^*$ equals to the probability mass of the original distribution from the interval $[-\lambda, \lambda]$
+\begin{align}
+\begin{split}
+\omega^* &= \mathbb{P}(x^*=0) = \mathbb{P}(x \in [-\lambda, \lambda]) \\
+&= \Phi\left(\frac{\lambda-m}{\sqrt{v}}\right) - \Phi\left(\frac{-\lambda-m}{\sqrt{v}}\right). 
+\end{split}
+\end{align}
+where $\Phi(\cdot)$ is the standard Gaussian cumulative distribution function.
+
+The soft thresholding function shifts elements that are greater than $\lambda$  or less than $-\lambda$ towards $0$.
+Let $\psi(\cdot)$ denote the density of the soft thresholded distribution on $x^* \neq 0$, $\phi(\cdot)$ denote the density of the original Gaussian distribution on $x$.
+Then the first moment of $x^* \neq 0$ is:
+
+\begin{align}
+\label{eq:thr_first_moment}
+\begin{split}
+m^* &= \int_{-\infty}^{+\infty}x\psi(x)dx= \int_{-\infty}^{0}x\phi(x-\lambda)dx \\
+&{} + \int_{0}^{+\infty}x\phi(x+\lambda)dx,
+\end{split}
+\end{align}
+where
+\begin{align}
+&\int_{-\infty}^{0}x\phi(x-\lambda)dx = -\frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} \nonumber\\
+&{} + (\lambda+m)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)\\
+&\int_{0}^{+\infty}x\phi(x+\lambda)dx = \frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\nonumber\\
+& + (m - \lambda)\left(1 - \Phi\left(-\frac{\lambda-m}{\sqrt{v}}\right)\right)
+\end{align}
+
+The second moment of $x^* \neq 0$ is given as
+\begin{align}
+\label{eq:thr_second_moment}
+\begin{split}
+s &= \int_{-\infty}^{+\infty}x^2\psi(x)dx = \int_{-\infty}^{0}x^2\phi(x-\lambda)dx \\
+&{}+ \int_{0}^{+\infty}x^2\phi(x+\lambda)dx,
+\end{split}
+\end{align}
+where
+\begin{align}
+\begin{split}
+&\int_{-\infty}^{0}x^2\phi(x-\lambda)dx = \\
+&-\frac{\sqrt{v}}{\sqrt{2\pi}} (\lambda+m)\exp\left\{\frac{-(\lambda+m)^2}{2v}\right\}\\
+& + (\sigma^2 + (\lambda+m)^2)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
+\end{split}\\
+\begin{split}
+&\int_{0}^{+\infty}x^2\phi(x+\lambda)dx = \\
+&\frac{\sqrt{v}}{\sqrt{2\pi}} (m - \lambda)\exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\\
+& + (\sigma^2 + (m - \lambda)^2)\left(1 - \Phi\left(\frac{\lambda -m}{\sqrt{v}}\right)\right)
+\end{split}
+\end{align}
+
+The resulting variance is then
+\begin{equation}
+v^* = s- (m^*)^2
+\end{equation}
+\end{proof}
+
+Based on the results of Lemma~\ref{thm:soft_thresholding} we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ from (\ref{eq:thr_first}) with a spike and slab distribution with parameters derived in the lemma: spike probability $\omega$ is equal to $\omega^*$, slab mean $m$ and variance $v$ are set to the corresponding parameters of the truncated Gaussian $m^*$ and $v^*$.
+
+\subsection{\uppercase{Main layers}}
+The distributions of the inputs at the step (\ref{eq:l_dense_layer}) of the Baysian \textsc{lista} for each $l$ are: the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian-distributed components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
+
+In order to determine the distribution of the output $\mathbf{c}_l$ we first formulate two lemmas.
+
+\begin{lemma}[Moments of a spike and slab distribution]
 \label{thm:moments_spsl}
@@
 
- \begin{lemma}[Product of Gaussian matrix and constant vector]
- \label{thm:matrix_const}
- Let $\mathbf{W} \in \mathbb{R}^{D \times K}$ be a matrix of independent Gaussian-distributed random variables: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y} \in \mathbb{R}^K$ be a constant vector.
-Then their product $\mathbf{W} \mathbf{y}$ is a vector $\mathbf{b} \in \mathbb{R}^{D}$ of random variables $b_d \sim \mathcal{N}(m^b_d, w^b_d)$, where
+\begin{lemma}[Product of a Gaussian matrix and a spike and slab vector]
+  \label{thm:matrix_vector}
+Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta }\in \mathbb{R}^D$ be a vector with spike-and-slab distributed variables: $\widehat{\beta}_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
+The components of the matrix $\mathbf{S}$ and the vector $\widehat{\boldsymbol\beta}$ are mutual independent.
+Let $\mathbf{e} \in \mathbb{R}^{D}$ denote the product $\mathbf{S} \widehat{\boldsymbol\beta}$.
+Then the marginal mean and variance of elements $e_d$ of the vector $\mathbf{e}$ are:
 \begin{subequations}
 \begin{align}
-m^b_d &= \sum_{k=1}^Ky_k m^w_{dk}, \\
-w^b_d &= \sum_{k=1}^Ky_k^2v^w_{dk}.
- \end{align}
-\end{subequations}
-
- \end{lemma}
- \begin{proof}
- 	The statement follows from the property that the family of normal distributions is closed under linear transformations.
- \end{proof}
-
-  \begin{lemma}[Product of Gaussian matrix and spike and slab vector]
-  \label{thm:matrix_vector}
- Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta }\in \mathbb{R}^D$ be a vector with spike-and-slab distributed variables: $\widehat{\beta}_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
-If their product is approximated as a vector $\mathbf{e} \in \mathbb{R}^{D}$ of random variables $e_d \sim \mathcal{N}(m^e_d, w^e_d)$, then
-\begin{subequations}
-\begin{align}
- m^e_d &= \sum_{d'=1}^D m^s_{dd'}(1-\omega_{d'})m_{d'}, \\
+ \mathbb{E}e_d &= \sum_{d'=1}^D m^s_{dd'}(1-\omega_{d'})m_{d'}, \\
  \begin{split}
- v^e_d &= \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} \\
+ \operatorname{Var}e_d &= \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} \\
  & {}+ (1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}].
@@
  \begin{proof}
- 	We compute the mean and variance of the product $\mathbf{S}\widehat{\boldsymbol\beta}$ with an assumption of independence of its components and approximate resulting distribution with Gaussian.
-The quality of this approximation is discussed in section \ref{sec:approx_quality}
 \begin{flalign*}
@@
  \end{proof}
+
+Let $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at the step (\ref{eq:l_dense_layer}) of the Baysian \textsc{lista}.
+We assume that $\mathbf{S}$ and $\widehat{\boldsymbol\beta}_{l-1}$ are mutually independent.
+Then according to the Central Limit Theorem $[ \mathbf{e}_l ]_d$ can be approximated as a Gaussian-distributed variable when $D$ is sufficiently large.
+The parameters of the of the approximating Gaussian distribution are set to the marginal mean and variance given in Lemma~\ref{thm:matrix_vector}.
+The quality of this approximation is discussed in section \ref{sec:approx_quality}.
+
+The output $\mathbf{c}_l$ at the step (\ref{eq:l_dense_layer}) is then represented as a sum of two Gaussian-distributed vectors: $\mathbf{b}$ and $\mathbf{e}_l$
 
@@
 
-\begin{lemma}[Gaussian propagation through soft thresholding]
-\label{thm:soft_thresholding}
-When a Gaussian-distributed random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft thresholding function it can be approximated with the spike and slab distribution on $x^*$ with the probability of spike $\omega^*$, slab mean $m^*$ and slab variance $v^*$ (parameters of the approximating distribution are given in the proof).
-\end{lemma}
-\begin{proof}
+Therefore, $\mathbf{c}_l$ is a vector of Gaussian-distributed components, which parameters can be found according to Lemma~\ref{thm:sum_vectors}.
 
-The probability of spike $\omega^*$ equals to the probability mass of the original distribution that lies in $(-\lambda, \lambda)$  and is flattened into zero by soft thresholding operator.
-As the original distribution is Gaussian, this can be computed as
-\begin{align}
-\begin{split}
-\omega^* &= p(x^*=0) = p(x \in [-\lambda, \lambda]) \\
-&= \Phi\left(\frac{\lambda-m}{\sqrt{v}}\right) - \Phi\left(\frac{-\lambda-m}{\sqrt{v}}\right). 
-\end{split}
-\end{align}
+Then $\widehat{\boldsymbol\beta}_{l}$ at the step (\ref{eq:l_thr}) of the Baysian \textsc{lista} is the result of soft thresholding of a Gaussian distribution, which is approximated with the spike and slab distribution,  similar to the step (\ref{eq:thr_first}).
 
-Soft thresholding shifts elements that are greater than $\lambda$  or less than $-\lambda$ elements towards 0.
-Let $\psi(\cdot)$ denote the density of the soft thresholded distribution, $\phi(\cdot)$ denote the density of the original Gaussian distribution.
-Then the first moment of the resulting distribution is
+\subsection{\uppercase{Bayesian lista forward propagation}}
+We have covered all steps of the Bayesian \textsc{lista} and derived distributions for outputs of these steps.
+Now we can formulate the main result of this section that describes how the proposed uncertainty propagation works.
 
-\begin{align}
-\begin{split}
-m^* &= \int_{-\infty}^{+\infty}x\psi(x)dx= \int_{-\infty}^{0}x\phi(x-\lambda)dx \\
-&{} + \int_{0}^{+\infty}x\phi(x+\lambda)dx.
-\end{split}
-\end{align}
-
-Integrals are computed as
-\begin{align}
-\begin{split}
-&\int_{-\infty}^{0}x\phi(x-\lambda)dx = -\frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} \\
-&{} + (\lambda+m)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
-\end{split}\\
-\begin{split}
-&\int_{0}^{+\infty}x\phi(x+\lambda)dx = \frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\\
-& + (m - \lambda)\left(1 - \Phi\left(-\frac{\lambda-m}{\sqrt{v}}\right)\right)
-\end{split}
-\end{align}
-
-The second moment of the approximating distribution is computed as
-\begin{align}
-\begin{split}
-s &= \int_{-\infty}^{+\infty}x^2\psi(x)dx = \int_{-\infty}^{0}x^2\phi(x-\lambda)dx \\
-&{}+ \int_{0}^{+\infty}x^2\phi(x+\lambda)dx.
-\end{split}
-\end{align}
-
-Integrals are computed as
-\begin{align}
-\begin{split}
-&\int_{-\infty}^{0}x^2\phi(x-\lambda)dx = \\
-&-\frac{\sqrt{v}}{\sqrt{2\pi}} (\lambda+m)\exp\left\{\frac{-(\lambda+m)^2}{2v}\right\}\\
-& + (\sigma^2 + (\lambda+m)^2)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
-\end{split}\\
-\begin{split}
-&\int_{0}^{+\infty}x^2\phi(x+\lambda)dx = \\
-&\frac{\sqrt{v}}{\sqrt{2\pi}} (m - \lambda)\exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\\
-& + (\sigma^2 + (m - \lambda)^2)\left(1 - \Phi\left(\frac{\lambda -m}{\sqrt{v}}\right)\right)
-\end{split}
-\end{align}
-
-Resulting variance is
-\begin{equation}
-v^* = s- (m^*)^2
-\end{equation}
-
-\end{proof}
-
-The proposed operations on Gaussian and spike-and-slab distributions allow to formulate the main result in this section that describes how the uncertainty propagation works.
-\begin{theorem}[Bayesian \textsc{lista} forward propagation]
-\label{thm:prob_layer}
-The spike and slab distribution for $\widehat{\boldsymbol\beta}$ with can be propagated through the \textsc{lista} layer and the parameters after propagation can be computed as following:
 \begin{enumerate}
-	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is computed according to lemma \ref{thm:matrix_const};
-	\item $\mathbf{e} = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is computed according to lemma \ref{thm:matrix_vector};
-	\item $\mathbf{c} = \mathbf{b} + \mathbf{e}$ is computed according to lemma \ref{thm:sum_vectors};
-	\item $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c})$ is computed according to lemma \ref{thm:soft_thresholding}.
+	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:matrix_const};
+	\item $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is approximated with the Gaussian distribution, which parameters are computed according to lemma \ref{thm:matrix_vector};
+	\item $\mathbf{c} = \mathbf{b} + \mathbf{e}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:sum_vectors};
+	\item $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c})$ is approximated with the spike and slab distribution, which parameters are computed according to lemma \ref{thm:soft_thresholding}.
 \end{enumerate}
-\end{theorem}
 

### 2018-03-10 paper/BayesianLISTA.tex
image size reduced and captions amended

@@
 \label{sec:experiments}
-The proposed Bayesian \textsc{lista} is evaluated in the context of the sparse coding problem with underdefined dictionary, where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
+The proposed Bayesian \textsc{lista} is evaluated in the context of the sparse coding problem with an undercomplete dictionary, where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
 
@@
 \begin{figure}[t]
+\centering
 %\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
 %~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}}
-\newline
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}}
 %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
 %~
-\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}}
-\caption{Number of layers on synthetic data}
+\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}}
+\caption{Predictive accuracy on different number of layers (for neural networks) or iterations (for baselines) on the synthetic data}
 \label{fig:number_of_layers_synthetic}
@@
 \begin{figure}[t]
+\centering
 %\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_train}}
 %~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/synthetic_undersampling/nmse_validation}}
-\newline
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_validation}}
 %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
 %~
-\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}}
-\caption{Size of observations on synthetic data}
+\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}}
+\caption{Predictive performance on different size of observations on the synthetic data}
 \label{fig:unsersampling_synthetic}
@@
 \begin{figure}[t]
+\centering
 %\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
 %~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
-\newline
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
 %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
 %~
-\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
-\caption{\textsc{mnist} with dictionary $100$}
+\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
+\caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 100$}
 \label{fig:mnist_100}
@@
 \begin{figure}[t]
+\centering
 %\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_train}}
 %~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/250_normalised_nmse_valid}}
-\newline
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_valid}}
 %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
 %~
-\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/250_normalised_f_measure_valid}}
-\caption{\textsc{mnist} with dictionary $250$}
+\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_valid}}
+\caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 250$}
 \label{fig:mnist_250}
@@
 \begin{figure}[t]
+\centering
 \subfloat[$\beta$ posterior mean]{\includegraphics[width=0.33\columnwidth]{posterior_mean}}~
@@
 \subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.33\columnwidth]{posterior_spike_indicator}}
-\caption{Posterior for the digit 7.}
+\caption{Posterior parameters for an image of digit 7.}
 \label{fig:posterior_distribution}
@@
 \begin{figure}[t]
+\centering
 \subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_0}}~
@@
 \subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_2}}
-\caption{Samples from the posterior for the digit 7.}
+\caption{Samples from the posterior for an image of digit 7.}
 \label{fig:posterior_samples}
@@
 
-\subsection{\uppercase{Active learning on mnist}}
+\subsection{\uppercase{Active learning}}
 To demonstrate the potential scenario that can benefit from uncertainty estimates of the Bayesian \textsc{lista} we consider the active learning example \citep{settles.tr09}.
@@
 \begin{figure}[t]
-\subfloat[\textsc{nmse}]{\includegraphics[width=\columnwidth]{graphics/active_mnist/nmse_validation}} \\
-\subfloat[F measure]{\includegraphics[width=\columnwidth]{graphics/active_mnist/f_measure_validation}}
-\caption{Active learning on \textsc{mnist}.}
+\centering
+\subfloat[\textsc{nmse}]{\includegraphics[width=0.5\columnwidth]{graphics/active_mnist/nmse_validation}}%
+\subfloat[F measure]{\includegraphics[width=0.5\columnwidth]{graphics/active_mnist/f_measure_validation}}
+\caption{Performance in the active learning experiment on the \textsc{mnist} data. }
 \label{fig:active_learning_mnist}

### 2018-03-10 paper/BayesianLISTA.tex
fontsize on figures is enlarged

@@
 %~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_nmse_valid}}
 %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
 %~
-\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
+\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_f_measure_valid}}
 \caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 100$}
@@
 %~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_valid}}
+\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_nmse_valid}}
 %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
 %~
-\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_valid}}
+\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_f_measure_valid}}
 \caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 250$}

### 2018-03-10 theano/experiments/active_learning/collect_results.py

@@ -16,7 +16,7 @@ class ActiveExperimentMnistResultsCollector(object):
 
     def collect_all(self):
         for rseed in range(self.n_rseed):
-            res = np.load('mnist_results/mnist_active_rseed_{}.npz'.format(rseed))
+            res = np.load('mnist_results_normalised/mnist_active_rseed_{}.npz'.format(rseed))
             self.freq_validation_loss[rseed] = res['freq_validation_loss']
             self.non_active_bayes_validation_loss[rseed] = res['non_active_bayes_validation_loss']
             self.active_bayes_validation_loss[rseed] = res['active_bayes_validation_loss']
@@ -26,7 +26,7 @@ class ActiveExperimentMnistResultsCollector(object):
 
     def plot_each(self):
         for rseed in range(self.n_rseed):
-            res = np.load('mnist_results/mnist_active_rseed_{}.npz'.format(rseed))
+            res = np.load('mnist_results_normalised/mnist_active_rseed_{}.npz'.format(rseed))
 
             plt.plot(res['active_bayes_validation_loss'], label='active')
             plt.plot(res['non_active_bayes_validation_loss'], label='non active')
@@ -43,6 +43,8 @@ class ActiveExperimentMnistResultsCollector(object):
         linewidth = .25
         markersize = 5.
         std_multiplier = 1
+        label_fontsize = 18
+        legend_fontsize = 14
 
         non_active_bayes_marker = 'v'
         non_active_bayes_color = 'red'
@@ -70,9 +72,9 @@ class ActiveExperimentMnistResultsCollector(object):
         plt.errorbar(np.arange(0, self.n_upd_iter + 1), np.mean(self.non_active_bayes_validation_loss, axis=0),
                      yerr=std_multiplier * np.std(self.non_active_bayes_validation_loss, axis=0), color=non_active_bayes_color)
 
-        plt.legend()
-        plt.xlabel(r'K')
-        plt.ylabel(r'NMSE')
+        plt.legend(fontsize=legend_fontsize)
+        plt.xlabel(r'K', fontsize=label_fontsize)
+        plt.ylabel(r'NMSE', fontsize=label_fontsize)
         plt.savefig('mnist_results_plots/nmse_validation.eps', format='eps')
         plt.show()
 
@@ -90,9 +92,9 @@ class ActiveExperimentMnistResultsCollector(object):
[…]

### 2018-03-10 theano/experiments/mnist/collect_results_nonnormalised.py

@@ -77,6 +77,8 @@ class MnistExperimentResultsCollector(object):
         linewidth = 1.
         markersize = 5.
         std_multiplier = 2
+        label_fontsize = 18
+        legend_fontsize = 14
 
         ista_marker= None
         ista_color='blue'
@@ -101,9 +103,9 @@ class MnistExperimentResultsCollector(object):
         plt.plot(self.freq_f_meas_train, label=freq_label, color=freq_color, marker=freq_marker, linewidth=linewidth, markersize=markersize)
         plt.plot(self.sh_bayes_f_meas_train, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.plot()
-        plt.legend()
-        plt.ylabel(r'F measure')
-        plt.xlabel(r'n iter')
+        plt.legend(fontsize=legend_fontsize)
+        plt.ylabel(r'F measure', fontsize=label_fontsize)
+        plt.xlabel(r'n iter', fontsize=label_fontsize)
         plt.savefig('results/normalised_f_measure_train.eps', format='eps')
         plt.show()
 
@@ -112,9 +114,9 @@ class MnistExperimentResultsCollector(object):
         plt.plot(self.freq_f_meas_validation, label=freq_label, color=freq_color, marker=freq_marker, linewidth=linewidth, markersize=markersize)
         plt.plot(self.sh_bayes_f_meas_validation, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.plot()
-        plt.legend()
-        plt.ylabel(r'F measure')
-        plt.xlabel(r'Number of iterations')
+        plt.legend(fontsize=legend_fontsize)
+        plt.ylabel(r'F measure', fontsize=label_fontsize)
+        plt.xlabel(r'Number of iterations', fontsize=label_fontsize)
         plt.savefig('results/normalised_f_measure_valid.eps', format='eps')
         plt.show()
 
@@ -123,9 +125,9 @@ class MnistExperimentResultsCollector(object):
         plt.plot(self.freq_loss_train, label=freq_label, color=freq_color, marker=freq_marker, linewidth=linewidth, markersize=markersize)
[…]

### 2018-03-10 theano/experiments/synthetic/number_of_layers/collect_results.py

@@ -107,6 +107,8 @@ class NumberOfLayersExperimentReultsCollector(object):
         linewidth = .25
         markersize = 5.
         std_multiplier = 2
+        label_fontsize = 18
+        legend_fontsize = 14
 
         ista_marker= 'o'
         ista_color='blue'
@@ -132,9 +134,9 @@ class NumberOfLayersExperimentReultsCollector(object):
         plt.errorbar(self.L_array, self.freq_f_meas_train, yerr=2 * self.freq_f_meas_train_std, color=freq_color)
         plt.plot(self.L_array, self.sh_bayes_f_meas_train, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.L_array, self.sh_bayes_f_meas_train, yerr=2 * self.sh_bayes_f_meas_train_std, color=sh_bayes_color)
-        plt.legend()
-        plt.xlabel(r'L')
-        plt.ylabel(r'F measure')
+        plt.legend(fontsize=legend_fontsize)
+        plt.xlabel(r'L', fontsize=label_fontsize)
+        plt.ylabel(r'F measure', fontsize=label_fontsize)
         plt.savefig('results/f_measure_train.eps', format='eps')
         plt.show()
 
@@ -146,9 +148,9 @@ class NumberOfLayersExperimentReultsCollector(object):
         plt.errorbar(self.L_array, self.freq_f_meas_validation, yerr=3 * self.freq_f_meas_validation_std, color=freq_color)
         plt.plot(self.L_array, self.sh_bayes_f_meas_validation, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.L_array, self.sh_bayes_f_meas_validation, yerr=3 * self.sh_bayes_f_meas_validation_std, color=sh_bayes_color)
-        plt.legend()
-        plt.xlabel(r'L')
-        plt.ylabel(r'F measure')
+        plt.legend(fontsize=legend_fontsize)
+        plt.xlabel(r'L', fontsize=label_fontsize)
+        plt.ylabel(r'F measure', fontsize=label_fontsize)
         plt.savefig('results/f_measure_validation.eps', format='eps')
         plt.show()
 
@@ -160,9 +162,9 @@ class NumberOfLayersExperimentReultsCollector(object):
[…]

### 2018-03-10 theano/experiments/synthetic/undersampling/collect_results.py

@@ -108,6 +108,8 @@ class UndersamplingExperimentReultsCollector(object):
         linewidth = .25
         markersize = 5.
         std_multiplier = 2
+        label_fontsize = 18
+        legend_fontsize = 14
 
         ista_marker= 'o'
         ista_color='blue'
@@ -133,9 +135,9 @@ class UndersamplingExperimentReultsCollector(object):
         plt.errorbar(self.K_array, self.freq_f_meas_train, yerr=2 * self.freq_f_meas_train_std, color=freq_color)
         plt.plot(self.K_array, self.sh_bayes_f_meas_train, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.K_array, self.sh_bayes_f_meas_train, yerr=2 * self.sh_bayes_f_meas_train_std, color=sh_bayes_color)
-        plt.legend()
-        plt.xlabel(r'K')
-        plt.ylabel(r'F measure')
+        plt.legend(fontsize=legend_fontsize)
+        plt.xlabel(r'K', fontsize=label_fontsize)
+        plt.ylabel(r'F measure', fontsize=label_fontsize)
         plt.savefig('results/f_measure_train.eps', format='eps')
         plt.show()
 
@@ -147,9 +149,9 @@ class UndersamplingExperimentReultsCollector(object):
         plt.errorbar(self.K_array, self.freq_f_meas_validation, yerr=3 * self.freq_f_meas_validation_std, color=freq_color)
         plt.plot(self.K_array, self.sh_bayes_f_meas_validation, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.errorbar(self.K_array, self.sh_bayes_f_meas_validation, yerr=3 * self.sh_bayes_f_meas_validation_std, color=sh_bayes_color)
-        plt.legend()
-        plt.xlabel(r'K')
-        plt.ylabel(r'F measure')
+        plt.legend(fontsize=legend_fontsize)
+        plt.xlabel(r'K', fontsize=label_fontsize)
+        plt.ylabel(r'F measure', fontsize=label_fontsize)
         plt.savefig('results/f_measure_validation.eps', format='eps')
         plt.show()
 
@@ -161,9 +163,9 @@ class UndersamplingExperimentReultsCollector(object):
[…]

### 2018-03-10 paper/BayesianLISTA.tex
minor fix
word check

@@
 Therefore, Bayesian neural networks estimate both an output for a test data and uncertainty of this prediction.
-Uncertainty of the prediction is a result of propagating weight uncertainty through layers of a network.
+Uncertainty of the prediction is a result of weight uncertainty propagation through the layers of a network.
 We propose a novel method of propagating uncertainty through the soft thresholding nonlinearity.
@@
 We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.
-A series of experiments on sparse coding shows that the proposed framework provide both accurate predictions and quantified estimates of uncertainty in these predictions.
+A series of experiments on sparse coding shows that the proposed framework provides both accurate predictions and quantified estimates of uncertainty in these predictions.
 \end{abstract}
@@
 \label{sec:fprop}
-For every layer of the Baysian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters: $\boldsymbol\omega$ is a probability of a spike, $\mathbf{m}$ is a mean of a slab Gaussian distribution, and $\mathbf{v}$ is a variance of the slab distribution:
+For every layer of the Bayesian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters: $\boldsymbol\omega$ is a probability of a spike, $\mathbf{m}$ is a mean of a slab Gaussian distribution, and $\mathbf{v}$ is a variance of the slab distribution:
 \begin{equation}
@@
 \end{equation}
-where $\omega_d$, $m_d$, and $v_d$ are components of vectors $\boldsymbol\omega$, $\mathbf{m}$, and $\mathbf{v}$, respectively, $\delta_0$ is the delta-function that represents a spike. 
+where $\omega_d$, $m_d$, and $v_d$ are the components of vectors $\boldsymbol\omega$, $\mathbf{m}$, and $\mathbf{v}$, respectively, $\delta_0$ is the delta-function that represents a spike. 
 We initialise $\widehat{\boldsymbol\beta}_{0}$ with the spike and slab distribution with parameters $\boldsymbol\omega = \mathbf{0}$, $\mathbf{m} = \mathbf{0}$, and $\mathbf{v} = \mathbf{1}$.
@@
 \subsection{\uppercase{Main layers}}
-The distributions of the inputs at the step (\ref{eq:l_dense_layer}) of the Baysian \textsc{lista} for each $l$ are: the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian-distributed components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
+The distributions of the inputs at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista} for each $l$ are: the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian-distributed components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
 
@@
 
-Let $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at the step (\ref{eq:l_dense_layer}) of the Baysian \textsc{lista}.
+Let $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista}.
 We assume that $\mathbf{S}$ and $\widehat{\boldsymbol\beta}_{l-1}$ are mutually independent.
@@
 
-Then $\widehat{\boldsymbol\beta}_{l}$ at the step (\ref{eq:l_thr}) of the Baysian \textsc{lista} is the result of soft thresholding of a Gaussian distribution, which is approximated with the spike and slab distribution,  similar to the step (\ref{eq:thr_first}).
+Then $\widehat{\boldsymbol\beta}_{l}$ at the step (\ref{eq:l_thr}) of the Bayesian \textsc{lista} is the result of soft thresholding of a Gaussian distribution, which is approximated with the spike and slab distribution,  similar to the step (\ref{eq:thr_first}).
 
@@
 
-Parameters of the approximating posterior distribution are then updated with the derivates of this normalisation constant. [ADD ABOUT RECURRENT ESTIMATION]
+Parameters of the approximating posterior distribution are then updated with the derivatives of this normalisation constant.
 
@@
 We also show that when the training data is very small the proposed algorithm significantly outperforms the classical \textsc{lista} in terms of predictive accuracy.
-Experiments on active learning demonstrate that the proposed Baysian \textsc{lista} gives accurate posterior estimates that can be used for selection of a next data point where a label should be obtain for.
+Experiments on active learning demonstrate that the proposed Bayesian \textsc{lista} gives accurate posterior estimates that can be used for selection of a next data point where a label should be obtain for.
 
-The shrinkage parameter $\lambda$ is currently treated as a deterministic hyperparameter for the Baysian \textsc{lista}.
+The shrinkage parameter $\lambda$ is currently treated as a deterministic hyperparameter for the Bayesian \textsc{lista}.
 In future we plan to incorporate it into the model treating it as a random variable.

### 2018-03-10 paper/BayesianLISTA.tex
minor fixes

@@
 The method expands the area of Bayesian neural networks and enables the soft thresholding nonlinearity to be included in Bayesian deep neural networks for the first time.
-As an example we design a Bayesian Learned Iterative Shrinkage-Thresdholding Algorithm (Bayesian \textsc{lista}) network.
+As an example we design a Bayesian Learned Iterative Shrinkage-Thresholding Algorithm (Bayesian \textsc{lista}) network.
 We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.
@@
 The soft thresholding function shifts elements that are greater than $\lambda$  or less than $-\lambda$ towards $0$.
-Let $\psi(\cdot)$ denote the density of the soft thresholded distribution on $x^* \neq 0$, $\phi(\cdot)$ denote the density of the original Gaussian distribution on $x$.
+Let $\psi(\cdot)$ denote the density of the soft-thresholded distribution on $x^* \neq 0$, $\phi(\cdot)$ denote the density of the original Gaussian distribution on $x$.
 Then the first moment of $x^* \neq 0$ is:

### 2018-03-10 paper/BayesianLISTA.tex
figure captions fixed

@@
 \subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}}
-\caption{Predictive accuracy on different number of layers (for neural networks) or iterations (for baselines) on the synthetic data}
+\caption{Predictive accuracy for different numbers of layers (for neural networks) or iterations (for baselines) on the synthetic data}
 \label{fig:number_of_layers_synthetic}
@@
 \subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}}
-\caption{Predictive performance on different size of observations on the synthetic data}
+\caption{Predictive performance for different sizes of observations on the synthetic data}
 \label{fig:unsersampling_synthetic}
@@
 \subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_f_measure_valid}}
-\caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 100$}
+\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with dictionary size $K = 100$}
 \label{fig:mnist_100}
@@
 \subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_f_measure_valid}}
-\caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 250$}
+\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with dictionary size $K = 250$}
 \label{fig:mnist_250}
@@
 \subfloat[F measure]{\includegraphics[width=0.5\columnwidth]{graphics/active_mnist/f_measure_validation}}
-\caption{Performance in the active learning experiment on the \textsc{mnist} data. }
+\caption{Performance for the active learning experiment on the \textsc{mnist} data. }
 \label{fig:active_learning_mnist}

### 2018-03-10 paper/BayesianLISTA.tex
checked experiments by Olya

--- 2018-03-10 paper/BayesianLISTA.tex
@@
 
-\title{Uncertainty propagation in deep neural networks for sparse coding}
+\title{Uncertainty propagation in neural networks for sparse coding}
 
@@
 We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.
-A series of experiments on sparse coding shows that the proposed framework provides both accurate predictions and quantified estimates of uncertainty in these predictions.
+A series of experiments on sparse coding shows that the proposed framework provide both accurate predictions and quantified estimates of uncertainty in these predictions.
 \end{abstract}
@@
 \label{sec:fprop}
-For every layer of the Bayesian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters: $\boldsymbol\omega$ is a probability of a spike, $\mathbf{m}$ is a mean of a slab Gaussian distribution, and $\mathbf{v}$ is a variance of the slab distribution:
+For every layer of the Baysian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters: $\boldsymbol\omega$ is a probability of a spike, $\mathbf{m}$ is a mean of a slab Gaussian distribution, and $\mathbf{v}$ is a variance of the slab distribution:
 \begin{equation}
@@
 \end{equation}
-where $\omega_d$, $m_d$, and $v_d$ are the components of vectors $\boldsymbol\omega$, $\mathbf{m}$, and $\mathbf{v}$, respectively, $\delta_0$ is the delta-function that represents a spike. 
-We initialise $\widehat{\boldsymbol\beta}_{0}$ with the spike and slab distribution with parameters $\boldsymbol\omega = \mathbf{0}$, $\mathbf{m} = \mathbf{0}$, and $\mathbf{v} = \mathbf{1}$.
+where $\omega_d$, $m_d$, and $v_d$ are components of vectors $\boldsymbol\omega$, $\mathbf{m}$, and $\mathbf{v}$, respectively, $\delta_0$ is the delta-function that represents a spike.
 
@@
 
- \begin{lemma}[Product of Gaussian matrix and constant vector]
+ \begin{lemma}[Product of Gaussian matrix and deterministic vector]
  \label{thm:matrix_const}
-Let $\mathbf{W} \in \mathbb{R}^{D \times K}$ be a matrix of independent Gaussian-distributed random variables: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y} \in \mathbb{R}^K$ be a constant vector.
+Let $\mathbf{W} \in \mathbb{R}^{D \times K}$ be a matrix of independent Gaussian-distributed random variables: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y} \in \mathbb{R}^K$ be a deterministic vector.
 Then their product $\mathbf{W} \mathbf{y}$ is a vector $\mathbf{b} \in \mathbb{R}^{D}$ of random variables $b_d \sim \mathcal{N}(m^b_d, w^b_d)$, where
@@
 \subsection{\uppercase{Main layers}}
-The distributions of the inputs at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista} for each $l$ are: the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian-distributed components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
+The distributions of the inputs at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista} for each $l$ are: the vector $\mathbf{b}$ and matrix $\mathbf{S}$ that consist of Gaussian-distributed components and $\widehat{\boldsymbol\beta}_{l-1}$, which is a vector of the spike and slab random variables.
 
@@
 
-Let $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista}.
+Let $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at the step (\ref{eq:l_dense_layer}) of the Baysian \textsc{lista}.
 We assume that $\mathbf{S}$ and $\widehat{\boldsymbol\beta}_{l-1}$ are mutually independent.
@@
 
-Then $\widehat{\boldsymbol\beta}_{l}$ at the step (\ref{eq:l_thr}) of the Bayesian \textsc{lista} is the result of soft thresholding of a Gaussian distribution, which is approximated with the spike and slab distribution,  similar to the step (\ref{eq:thr_first}).
+Then $\widehat{\boldsymbol\beta}_{l}$ at the step (\ref{eq:l_thr}) of the Baysian \textsc{lista} is the result of soft thresholding of a Gaussian distribution, which is approximated with the spike and slab distribution,  similar to the step (\ref{eq:thr_first}).
 
@@
 It is based on assumed density filtering (ADF) and expectation propagation (EP) and allows to update parameters of the distributions based on the derivative of the logarithm of a normalisation constant.
-ADF is based on iterative incorporation of factors from the true posterior $p$ (\ref{eq:posterior}) into the factorised approximating distribution $q$ (\ref{eq:approximating_dsitribution}), whereas in EP factors in the $q$ are iteratively replaced by factors from $p$.
+ADF iteratively incorporates factors from the true posterior $p$ (\ref{eq:posterior}) into the factorised approximating distribution $q$ (\ref{eq:approximating_dsitribution}), whereas in EP factors in the $q$ are iteratively replaced by factors from $p$.
 
@@
 \begin{equation}
-q(\cdot) = Z^{-1}f(\cdot)\mathcal{N}(\cdot; m, v)
+q(a) = Z^{-1}f(a)\mathcal{N}(a; m, v)
 \end{equation}
-where $Z$ is the normalisation constant and $f(\cdot)$ - arbitrary function.
+where $Z$ is the normalisation constant and $f(a)$ - arbitrary function, $a \in \{w_{dk}, s_{d'd''}; \forall d, k, d', d''\}$.
 
-According to \cite{minka2001thesis}, new parameters of Gaussian distribution for$ \cdot$ can be computed as
+According to \cite{minka2001thesis}, new parameters of Gaussian distribution for $a$ can be computed as
 \begin{align}
@@
 
-Then to find new values of $W$, $S$ we need to compute the $Z$ every time when the factor of the true posterior is incorporated in $q$.
+Then to find new values of $W$, $S$ we need to compute derivatives of the logarithm of $Z$ when the factor of the true posterior is incorporated in $q$.
 
@@
 
-Parameters of the approximating posterior distribution are then updated with the derivatives of this normalisation constant.
+Parameters of the approximating posterior distribution are then updated with the derivates of this normalisation constant.
 
 \subsection{\uppercase{Prior}}
-Prior factors from $p$ (\ref{eq:ws}, \ref{eq:gamma_eta}) are incorporated into $q$ with the EP algorithm, i.e.
+Prior factors from $p$ (\ref{eq:ws}), (\ref{eq:gamma_eta}) are incorporated into $q$ with the EP algorithm~\citep{hernandez2015probabilistic}, i.e.
 they replace the corresponding approximating factors from $q$ and then $q$ is updated to minimise its KL divergence with $q$ that has the true factor incorporated.
@@
 \textsc{fista} adds the momentum to \textsc{ista} and improves its convergence speed.
-We limit the number of iterations in these algorithms with $L$ that is the same as the number of layers in Bayesian \textsc{lista} and \textsc{lista}.
+We set the number of iterations in these algorithms and the number of layers in Bayesian and classical \textsc{lista} networks to $L$.
 To measure the performance of the algorithms the normalised mean square error(\textsc{nmse}) and F measure are used.
-\textsc{nmse} for a batch of data $\{\boldsymbol\beta^{(n)}\}_{n=1}^{N}$ and estimators $\{\widehat{\boldsymbol\beta}^{(n)}\}_{n=1}^{N}$ is computed as
+\textsc{nmse} for a batch of data $\{\boldsymbol\beta^{(n)}\}_{n=1}^{N}$ and estimates $\{\widehat{\boldsymbol\beta}^{(n)}\}_{n=1}^{N}$ is computed as
 \begin{equation}
@@
 \end{equation}
-In sparse coding it is usually more important to obtain the correct locations of spikes (i.e zeros) and slabs (i.e.
-non-zeros) in the estimator than to minimise \textsc{nmse}.
+In sparse coding it is also important to obtain the correct locations of spikes (i.e zeros) and slabs (i.e.
+non-zeros) in the estimates.
 The problem is therefore viewed as a skewed two-class classification problem where the number of spikes is higher than the number of slabs.
 F measure is used to evaluate the accuracy of such problems.
-F measure is computed as the harmonic mean of precision and recall
+It is defined as the harmonic mean of precision and recall
 \begin{equation}
@@
 First, the predictive performance of the proposed Bayesian \textsc{lista} is analysed on synthetic data.
-We generate $N_\text{train}=500$ sparse coefficients vectors $\boldsymbol\beta_n$ each of size $D = 100$.
-Coefficients $\boldsymbol\beta$ are generated from the spike and slab distribution with truncated slab: each component of $\beta_{nd}$ is zero with probability $0.8$ or is from standard Gaussian distribution without interval $(-0.1, 0.1)$ with probability $0.2$.
-Truncation of the zeros allows to remove from support pattern values with insignificant contributions \citep{xin2016maximal}.
-To simulate sparse observations, we have generated the random Gaussian design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$.
-The observations are generated according to the \ref{eq:regression_problem} with zero-mean Gaussian noise with standard deviation $0.5$.
-$\lambda$ is assumed fixed as $0.1$.
+We generate $N_\text{train}=500$ sparse coefficients vectors $\boldsymbol\beta^{(n)}$ each of size $D = 100$.
+Coefficients $\boldsymbol\beta^{(n)}$ are generated from the spike and slab distribution with truncated slab: each component of $[\beta^{(n)}]_{d}$ is zero with the probability $0.8$ or is from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability $0.2$.
+To simulate sparse observations, we generate the random Gaussian design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$.
+The observations are generated according to (\ref{eq:regression_problem}) with zero-mean Gaussian noise with standard deviation $0.5$.
+The shrinkage parameter is set to~$\lambda = 0.1$.
 
-In the Figure \ref{fig:number_of_layers_synthetic} prediction performance for different number of layers $L$ is presented.
-The observation size is set as $K=50$.
-In both experiments the performance of the Bayesian \textsc{lista} is better than the performance of \textsc{lista}.
-Although the baseline \textsc{ista} and \textsc{fista} show better performance in terms of F measure, Bayesian \textsc{lista} has lower \textsc{nmse}.
+In Figure \ref{fig:number_of_layers_synthetic} predictive performance for different number of layers $L$ is presented.
+The observation size is set to $K=50$.
+The Bayesian \textsc{lista} outperforms \textsc{lista} in terms of both measures.
+Although the baselines \textsc{ista} and \textsc{fista} show better performance in terms of F measure, the Bayesian \textsc{lista} has the lowest \textsc{nmse}.
 
-In the Figure \ref{fig:unsersampling_synthetic} prediction performance for different observation sizes $K$ is presented.
-The number of layers is set as $L=4$ which is the value of the poorest performance of Bayesian \textsc{lista} according to the previous experiment.
-Bayesian \textsc{lista} provides better results than {lista} for $K \ge 30$ and better results than other algorithms for $K \ge 70$.
+Figure~\ref{fig:unsersampling_synthetic} gives the results of predictive performance for different observation sizes $K$.
+The number of layers is set as $L=4$.
+In the previous experiment both Bayesian and classical \textsc{lista} shows similar results with this number of layers.
+The results of Figure~\ref{fig:unsersampling_synthetic} confirms this competitive behaviour between two \textsc{lista} networks.
+Baselines show similar results in terms of F measure and underperform in terms of \textsc{nmse}.
+
+The experiments on synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy while additionally estimating uncertainty of predictions.
 
@@
 Then we generate observations as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta$ are images converted to vectors.
-We use randomly selected $100$ images for training and $100$ for validation.
-$\lambda$ is assumed fixed as $0.1$.
+We use $100$ images for training and $100$ for validation.
+The shrinkage parameter $\lambda$ is fixed as $0.1$.
 
 Figures \ref{fig:mnist_100} and \ref{fig:mnist_250} present quality on the validation set with dictionaries of size $100$ and $250$.
-When $K=100$ Bayesian \textsc{lista} shows better performance that other algorithms and on $K=250$ it  converges to similar values as \textsc{lista}.
+The experiment with $K=100$ presents ``severe'' conditions for the algorithms: the very limited size of the training dataset combined with the small dimensionality of observations.
+The Baysian \textsc{lista} is able to learn even under these conditions, significantly outperforming \textsc{lista} that demonstrate very poor results.
+Under easier condition of the second experiment with $K=250$ both \textsc{lista} networks converge to the similar results.
+However, the Bayesian \textsc{lista} demonstrates remarkably better convergence rate.
+Both baselines are unable to learn in these experiments.
 
-Proposed Bayesian \textsc{lista} networks estimate posterior distribution for $\boldsymbol\beta$.
-Figure \ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
+The proposed Bayesian \textsc{lista} network also estimates the posterior distribution for $\boldsymbol\beta$.
+Figure~\ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
 
@@
 \subsection{\uppercase{Active learning}}
-To demonstrate the potential scenario that can benefit from uncertainty estimates of the Bayesian \textsc{lista} we consider the active learning example \citep{settles.tr09}.
-Active learning area researches ways to select new training subsets to reduce total number of required supervision.
-One of the approaches for active learning is uncertainty sampling when the data with the least certain predictions is used for training.
-The uncertainty can be measured with entropy or variance.
-In our example no closed form for entropy of spike and slab exist, therefore we use variance from lemma \ref{thm:moments_spsl} as a measure of uncertainty.
+To demonstrate a potential scenario that can benefit from uncertainty estimates of the Bayesian \textsc{lista} we consider the active learning example \citep{settles.tr09}.
+The active learning area researches ways to select new training subsets to reduce the total number of required supervision.
+One of the popular approaches in active learning is uncertainty sampling when the data with the least certain predictions is chosen to obtain a new label for.
+Uncertainty is usually measured with entropy.
+In our case of the spike and slab distributed data points there is no closed form for entropy.
+Therefore, we use variance from Lemma~\ref{thm:moments_spsl} as a measure of uncertainty.
 
 The data in this example is the same \textsc{mnist} dataset with learnt dictionary of size $K=100$.
-It is divided into train data of size $50$, pool data of size $500$,  and test data of size $100$.
-The algorithm learns on the train data for $50$ iterations.
-After that, the Bayesian \textsc{lista} algorithm iteratively estimates the variance of the predictions on the pool data, selects the element with the maximum variance, moves it from pool set to the training set and runs additional training iteration.
-Overall, $10$ pool iterations are performed.
+We use the train data of size $50$, the pool data of size $500$,  and the test data of size $100$.
+The algorithm learns on the train data for $50$ iterations and it is evaluated on the test data.
+To actively collect a next data point from the pool, the algorithm is used to predict a point with the highest uncertainty.
+The selected point is moved from the pool to the train data and the algorithm performs additional $10$ iterations on the updated train data.
+Overall, $10$ pool additions are performed.
+After every addition the performance is measured on the test data.
 
-The performance on the actively updated train data is compared with the performance on the randomly updated train data, when at every iteration the random element is moved from pool set to train set.
-Both algorithms of new data sampling were run with $20$ random seeds and their performance was averaged.
-Figure \ref{fig:active_learning_mnist} demonstrates their performance.The uncertainty sampling has some advantage compared to random sampling, this means that the posterior variance is adequately estimated.
+We compare actively updated approach of adding new points from the pool with the random approach that picks a new data point from the pool at random.
+The overall procedure is repeated for $20$ times with new randomly selected initial datasets.
+
+Figure \ref{fig:active_learning_mnist} demonstrates performance of the active and non-active methods of updates with the Bayesian \textsc{lista}.
+The active approach with uncertainty sampling steadily demonstrates better results in terms of both quality measures.
+This means that the posterior distribution learnt by the Bayesian \textsc{lista} is adequately estimated.
 \begin{figure}[t]
@@
 We also show that when the training data is very small the proposed algorithm significantly outperforms the classical \textsc{lista} in terms of predictive accuracy.
-Experiments on active learning demonstrate that the proposed Bayesian \textsc{lista} gives accurate posterior estimates that can be used for selection of a next data point where a label should be obtain for.
+Experiments on active learning demonstrate that the proposed Baysian \textsc{lista} gives accurate posterior estimates that can be used for selection of a next data point where a label should be obtain for.
 
-The shrinkage parameter $\lambda$ is currently treated as a deterministic hyperparameter for the Bayesian \textsc{lista}.
+The shrinkage parameter $\lambda$ is currently treated as a deterministic hyperparameter for the Baysian \textsc{lista}.
 In future we plan to incorporate it into the model treating it as a random variable.
-For this we need to extend both the uncertainty propagation method to include uncertainty of $\lambda$ and the probabilistic backpropagation algorithm to estimate its posterior.
-We will study stochastic expectation propagation applicability in order to replace ADF that may improve further the quality of posterior estimates~\citep{li2015stochastic}.
+For this we will extend both the uncertainty propagation method to include uncertainty of $\lambda$ and the probabilistic backpropagation algorithm to estimate its posterior.
+We will study stochastic expectation propagation applicability in order to replace ADF that may further improve the quality of posterior estimates~\citep{li2015stochastic}.
 \bibliography{bibliography}

### 2018-03-10 paper/BayesianLISTA.tex

@@
 The method expands the area of Bayesian neural networks and enables the soft thresholding nonlinearity to be included in Bayesian deep neural networks for the first time.
-As an example we design a Bayesian Learned Iterative Shrinkage-Thresdholding Algorithm (Bayesian \textsc{lista}) network.
+As an example we design a Bayesian Learned Iterative Shrinkage-Thresholding Algorithm (Bayesian \textsc{lista}) network.
 We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.
-A series of experiments on sparse coding shows that the proposed framework provide both accurate predictions and quantified estimates of uncertainty in these predictions.
+A series of experiments on sparse coding shows that the proposed framework provides both accurate predictions and quantified estimates of uncertainty in these predictions.
 \end{abstract}
@@
 \end{equation}
-where $\omega_d$, $m_d$, and $v_d$ are components of vectors $\boldsymbol\omega$, $\mathbf{m}$, and $\mathbf{v}$, respectively, $\delta_0$ is the delta-function that represents a spike.
+where $\omega_d$, $m_d$, and $v_d$ are the components of vectors $\boldsymbol\omega$, $\mathbf{m}$, and $\mathbf{v}$, respectively, $\delta_0$ is the delta-function that represents a spike.
 
@@
 
-Parameters of the approximating posterior distribution are then updated with the derivates of this normalisation constant.
+Parameters of the approximating posterior distribution are then updated with the derivatives of this normalisation constant.
 
@@
 We will study stochastic expectation propagation applicability in order to replace ADF that may further improve the quality of posterior estimates~\citep{li2015stochastic}.
+
 \bibliography{bibliography}

### 2018-03-10 paper/BayesianLISTA.tex
minor corrections

@@
 \begin{split}
-\omega^* &= \mathbb{P}(x^*=0) = \mathbb{P}(x \in [-\lambda, \lambda]) \\
+\omega^* &=\operatorname{P}(x^*=0) = \operatorname{P}(x \in [-\lambda, \lambda]) \\
 &= \Phi\left(\frac{\lambda-m}{\sqrt{v}}\right) - \Phi\left(\frac{-\lambda-m}{\sqrt{v}}\right). 
@@
 The approximated distribution is computed according to lemma \ref{thm:soft_thresholding}.
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{d_testing}
-\caption{Approximation of product of Gaussians.}
-\label{fig:d_testing}
-\end{figure}
+
+%\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_nmse_valid}}
+
+%\begin{figure}[t]
+%\includegraphics[width=\columnwidth]{d_testing}
+%\caption{Approximation of product of Gaussians.}
+%\label{fig:d_testing}
+%\end{figure}
+%
+%\begin{figure}[t]
+%\includegraphics[width=\columnwidth]{z_new_testing}
+%\caption{Approximation of propagation through soft thresholding}
+%\label{fig:z_new_testing}
+%\end{figure}
 
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{z_new_testing}
-\caption{Approximation of propagation through soft thresholding}
-\label{fig:z_new_testing}
+\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}}
+%\label{fig:d_testing}
+\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}}
+%\caption{Approximation of propagation through soft thresholding}
+%\label{fig:z_new_testing}
 \end{figure}
@@
 The number of layers is set as $L=4$.
-In the previous experiment both Bayesian and classical \textsc{lista} shows similar results with this number of layers.
+In the previous experiment Bayesian and classical \textsc{lista} show similar results with this number of layers.
 The results of Figure~\ref{fig:unsersampling_synthetic} confirms this competitive behaviour between two \textsc{lista} networks.
@@
 
-The experiments on synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy while additionally estimating uncertainty of predictions.
+Overall, the experiments on synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
 
@@
 Figures \ref{fig:mnist_100} and \ref{fig:mnist_250} present quality on the validation set with dictionaries of size $100$ and $250$.
-The experiment with $K=100$ presents ``severe'' conditions for the algorithms: the very limited size of the training dataset combined with the small dimensionality of observations.
-The Baysian \textsc{lista} is able to learn even under these conditions, significantly outperforming \textsc{lista} that demonstrate very poor results.
-Under easier condition of the second experiment with $K=250$ both \textsc{lista} networks converge to the similar results.
+The experiment with $K=100$ presents severe conditions for the algorithms: the very limited size of the training dataset combined with the small dimensionality of observations.
+The Bayesian \textsc{lista} is able to learn under these conditions, outperforming \textsc{lista} that demonstrates poor results.
+Under better conditions of the second experiment with $K=250$ both \textsc{lista} networks converge to the similar results.
 However, the Bayesian \textsc{lista} demonstrates remarkably better convergence rate.
-Both baselines are unable to learn in these experiments.
+Both baselines are unable to perform well in these experiments.
 

### 2018-03-10 paper/BayesianLISTA.tex
figure corrections

@@
 \begin{figure}[t]
-\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}}
+\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
 %\label{fig:d_testing}
-\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}}
-%\caption{Approximation of propagation through soft thresholding}
+\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
+\caption{Approximations of Bayesian \textsc{lista}}
 %\label{fig:z_new_testing}

### 2018-04-12 paper/BayesianLISTA.tex
minor text updates check if they were in paper

@@
 
+\begin{figure}[!t]
+\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
+%\label{fig:d_testing}
+\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
+\caption{Approximations of Bayesian \textsc{lista}}
+%\label{fig:z_new_testing}
+\end{figure}
+
 \subsection{\uppercase{Bayesian lista forward propagation}}
@@
 	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:matrix_const};
+	\item $\widehat{\boldsymbol\beta}_{0} = h_\lambda(\mathbf{b})$ is approximated with the spike and slab distribution, which parameters are computed according to lemma \ref{thm:soft_thresholding}.
 	\item $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is approximated with the Gaussian distribution, which parameters are computed according to lemma \ref{thm:matrix_vector};
-	\item $\mathbf{c} = \mathbf{b} + \mathbf{e}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:sum_vectors};
-	\item $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c})$ is approximated with the spike and slab distribution, which parameters are computed according to lemma \ref{thm:soft_thresholding}.
+	\item $\mathbf{c}_l = \mathbf{b} + \mathbf{e}_l$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:sum_vectors};
+	\item $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$ is approximated with the spike and slab distribution, which parameters are computed according to lemma \ref{thm:soft_thresholding}.
 \end{enumerate}
@@
 %\end{figure}
-
-\begin{figure}[t]
-\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
-%\label{fig:d_testing}
-\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
-\caption{Approximations of Bayesian \textsc{lista}}
-%\label{fig:z_new_testing}
-\end{figure}
 

### 2018-04-24 review_uai_2018/response_to_reviews.tex
started response to reviewers

\documentclass{article}
\usepackage[letterpaper, margin=1in]{geometry}
\begin{document}

\title{UAI 2018 Reply to Reviewers}
\date{}
\maketitle

\section*{Reviewer 1}
\begin{quote}
\textit{It's not so surprising that probabilistic versions of ISTA should do better in the limited dictionary case. What I'm curious about is how fast the proposed algorithm is, not in terms of iterations, but wall clock time.}
\end{quote}
We should check the clock time.

\begin{quote}
\textit{Please enlarge the figures, as they are very hard to read.}
\end{quote}
We should enlarge the figures.

\begin{quote}
\textit{\ldots light experimental results \ldots}
\end{quote}
We can try to add heavier experiments, but time is limited by one week.

\begin{quote}
\textit{What's the intuitive reason for baseline ISTA/FISTA to have better performance in the synthetic data case?}
\end{quote}
Check this.

\begin{quote}
\textit{What is the expected difference between Bayesian and non-Bayesian as the number of layers increases (ie, you expect the gap to close, stay the same, etc.)?}
\end{quote}
Check this.

\begin{quote}
\textit{Do you expect it to be possible to replace the soft thresholding with some other nonlinearity and to produce a similar algorithms? This isn't something I expect to be done easily, but do you expect it to be feasible, or is the combination of soft threshold with the spike/slab distribution critical?}
\end{quote}
Check different nonlinearities used in sparse coding and think about them. (In tensoflow LISTA from mborgerding were several examples.)

In the context of sparse coding, we can approximate other nonlinearity (from those examples) with the spike and slab distribution. However, this approximation might be better or worse for other nonlinearities, this would require a bit of study. This is an interesting future direction to check how close the spike and slab distribution can approximate other nonlinearities used in sparse coding.

The spike and slab distribution is critical for sparse coding and nonlinearities that enforce data to be sparse. There is no intuition or motivation to use this distribution for networks with dense data.

\section*{Reviewer 2}
\begin{quote}
\textit{It's not clear that a machine learning venue is appropriate.}
\end{quote}
In [1] the original LISTA paper is used as an eample of unsupervised learning in deep learning. In [2] it is used for image super-resolution. In [3] general improvements to original paper are proposed. Sparse coding and sparse models in general are of interest in ML community - Wipf NIPS 2017.

[1] LeCun, Y., Bengio, Y., Hinton, G. (2015). Deep learning. nature, 521(7553), 436.
[2] Wang, Z., Liu, D., Yang, J., Han, W., Huang, T. (2015). Deep networks for image super-resolution with sparse prior. In Proceedings of the IEEE International Conference on Computer Vision (pp. 370-378).
[3] Sprechmann, P., Bronstein, A. M., Sapiro, G. (2015). Learning efficient sparse and low rank models. IEEE transactions on pattern analysis and machine intelligence, 37(9), 1821-1833.
[4] Papyan, V., Romano, Y., Elad, M. (2017). Convolutional neural networks analyzed via convolutional sparse coding. JMLR.

\begin{quote}
\textit{I found the writing unclear and confusing, as the authors switch back and forth between a neural network interpretation of LISTA, and the standard sparse coding interpretation. I imagine both interpretations would be standard for e.g. a signal processing audience?}
\end{quote}
I don't fully understand. I don't think we can do anything with this point in the reply.

\begin{quote}
\textit{I am unclear on how one can compute NMSE/F-measure for MNIST in figure 5/8, unless the ground truth sparsity is known i.e. if this is not real data. Is the experiment composed of real data and synthetic weights?}
\end{quote}
We need to explain again the setup of the experiments, that we know ground truth.

\begin{quote}
\textit{While the focus is on estimation, for real data, would be useful to see prediction results (again, I am assuming ground truth is not known).}
\end{quote}
I don't fully understand. Think about this.

Combine with the previous. Predictive performance is evaluated.

\begin{quote}
\textit{There are some unnecessary propositions e.g. Proposition 1/4, which refer to textbook results. Perhaps a simple citation is enough to save some space?}
\end{quote}
I don't think we can do anything with this point in the reply. Join this with reviever 3 and move proofs to appendix.

\section*{Reviewer 3}
\begin{quote}
\textit{What qualifies equation (11) to be a likelihood distribution?}
\end{quote}
What? Wikipedia: In Bayesian inference, one can speak about the likelihood of any proposition or random variable given another random variable: for example the likelihood of a parameter value or of a statistical model (see marginal likelihood), given specified data or other evidence

I think the question is why do we have this Gaussian noise model. We can say something that this is now normally people are introducing the Bayesian models. Give examples Bayesian linear regression, Probabilistic Backpropagation.

\begin{quote}
\textit{The uncertainty propagation in section 4 refers to a distribution over $\beta$. Which distribution are the authors referring to? Conditioned upon $Y,W,S,\gamma,\lambda$ as in (13)? Related: perhaps the method is better explained as a variational approximation on $p(B,W,S,\gamma,\lambda|Y)$?}
\end{quote}
Section 4 refers to distribution over $\widehat{\beta}$, which is the output of each layer of the neural network and ultimately the output of the whole network, which is denoted as $f(y; W, S, \lambda)$ in eq. (11). This $\widehat{\beta}$ is an approximation of the true $\beta$.

Yes, the distribution over $\widehat{\beta}$ is conditioned on $Y, W, S, \lambda$, but it is not conditioned on $\gamma$ as this is the noise variable that relates $\beta$, which we have during the training as a target and $\widehat{\beta}$, which is the output of the neural network.

The proposed inference is a variational approximation of the true posterior in the context of expectation propagation and ADF frameworks.

\begin{quote}
\textit{The exact meaning of “Then we generate observations as $y = X \beta$, where $\beta$ are images converted to vectors.”(Section 6.2) is not quite clear. Are the $\beta$ now flattened images, or the same sparse representations? Which dimensionality do they have?}
\end{quote}
Each beta is a flattened image of size $(784 \times 1)$

\begin{quote}
\textit{Why do the authors restrict themselves to so few training and validation images (100 each)?}
\end{quote}
Check this

Bayesian models in general show themselves espesially useful when dealing with limited data, when the frequentist counterparts may suffer from inadequate maximum likelihood estimates. Therefore, we were particurlarly interested in study on limited data, where the frequentist LISTA might have lower accuracy, to better show how Bayesian LISTA may provide benefits over the frequentist LISTA. We expected the frequentist LISTA to have very good results when there is a lot of data, which has been shown in the original paper and extensions.

We appreciate that it would be useful to have also confirmation that on larger datasets both LISTAs show competitive results. We will add the experiments on larger datasets in the revised version of the paper if it is accepted.

\begin{quote}
\textit{Why is $\lambda$ fixed to 0.1?}
\end{quote}
It was epmirically set. This value looks reasonable, since we use normalised data. As we mention in the paper the type II maximum likelihood can be used to find this value.
Try to implement this maximisation.
Try another value. (to add something like the results does not depend too much on this value.)

\begin{quote}
\textit{In the Discussion, the use with overcomplete dictionaries is mentioned as possible but no reasoning is given as to why undercomplete dictionaries were used and why they deviated from the method of the original paper.}
\end{quote}
Both overcomplete and undercomplete cases represent very important problems that conveniently can be solved with the same methods. In our previous work we dealt with undercomplete dictionaries and therefore we had the experiments with undercomplete dictionaries. Due to the space limit we couldn't include experiments for both cases.

Check this

\begin{quote}
\textit{Furthermore, the Figures are very small to a point where they are illegible on a DIN A4 printout.
If some of the proofs and calculations were moved to an Appendix, there would be room for readable Figures and more explanations in Sections 3 and 6.}
\end{quote}
Good idea

\section*{ToDo List}
\begin{enumerate}
  \item Enlarge the figures.
  \item Check motivation of LISTA in ML.
  \item Check reviwer 3 without lambda
  \item Check the clock time.
  \item Explain why baseline ISTA/FISTA is better in the synthetic data case.
  \item Think about the gap in performance when number of layers increases.
  \item Think if the method is expandable for different nonlinearities and distributions.
  \item Think about prediction results on real data as in review 2.
  \item Check reviewer 3 lambda.
  \item Consider heavier experiments.
  \item Think about different interpretations of lista as it waas uncelar in review 2.
\end{enumerate}

\end{document}

### 2018-04-24 paper/BayesianLISTA.tex
old minor change to paper

--- 2018-03-10 paper/BayesianLISTA.tex
@@
 \begin{enumerate}
-	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:matrix_const};
-	\item $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is approximated with the Gaussian distribution, which parameters are computed according to lemma \ref{thm:matrix_vector};
+	\item \textit{Initialisation dense layer}. $\mathbf{b} = \mathbf{W}\mathbf{y}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:matrix_const};
+	\item \textit{Initialisation soft thresholding layer}.
+$\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is approximated with the Gaussian distribution, which parameters are computed according to lemma \ref{thm:matrix_vector};
 	\item $\mathbf{c} = \mathbf{b} + \mathbf{e}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:sum_vectors};

### 2018-04-26 review_uai_2018/response_to_reviews.tex
upd revie

@@
 \usepackage[letterpaper, margin=1in]{geometry}
+\usepackage{color}
 \begin{document}
@@
 \end{quote}
-We should check the clock time.
+\textcolor{blue}{We'll check the clock time.}
 
@@
 \end{quote}
-We should enlarge the figures.
+We will enlarge the figures and move some of the proofs from section 4 to appendix to get space for figures.
 
-\begin{quote}
-\textit{\ldots light experimental results \ldots}
-\end{quote}
-We can try to add heavier experiments, but time is limited by one week.
+% \begin{quote}
+% \textit{\ldots light experimental results \ldots}
+% \end{quote}
+% We can try to add heavier experiments, but time is limited by one week.
 
@@
 \end{quote}
-Check this.
+\textcolor{blue}{We'll think about it. May be because of priors.}
 
@@
 \end{quote}
-Check this.
+\textcolor{blue}{It's related with previous question. We'll think how to answer it. Really, we don't know. But maybe gap will reduce as prior will influence less?}
 
@@
 \end{quote}
-Check different nonlinearities used in sparse coding and think about them. (In tensoflow LISTA from mborgerding were several examples.)
+Soft-thresholding nonlinearity seems to be the most popular as it is optimal in some sense [1].
+There are several nonlinearities that are used in sparse coding, for example some of them are described in sec.
+IV-B of [2].
+We can approximate other nonlinearities with the spike and slab distribution to see if these approximations are different in quality.
+This is an interesting future direction.
 
-In the context of sparse coding, we can approximate other nonlinearity (from those examples) with the spike and slab distribution.
-However, this approximation might be better or worse for other nonlinearities, this would require a bit of study.
-This is an interesting future direction to check how close the spike and slab distribution can approximate other nonlinearities used in sparse coding.
+The main motivation of the spike and slab distribution is to get sparse approximations, that is critical for sparse coding.
+There is an alternative Bernoulli-Gaussian distribution, that leads to similar results.
+There is no intuition or motivation to use these distributions for networks with dense data.
 
-The spike and slab distribution is critical for sparse coding and nonlinearities that enforce data to be sparse.
-There is no intuition or motivation to use this distribution for networks with dense data.
+[1] Tibshirani, R. (1996). Regression shrinkage and selection via the lasso. Journal of the Royal Statistical Society, 267-288.
+[2] Borgerding, M., Schniter, P., Rangan, S. (2017). AMP-Inspired Deep Networks for Sparse Linear Inverse Problems. IEEE Transactions on Signal Processing, 65(16), 4293-4308.
 
@@
 \end{quote}
-In [1] the original LISTA paper is used as an eample of unsupervised learning in deep learning.
+We understand that the topic of deep sparse coding may indeed lay on the border between signal processing and machine learning.
+But there were recent papers in the area of deep sparse coding published in machine learning community, we'll list some of them below.
+And we believe that as our method allows to estimate the uncertainty of the deep sparse coding algorithms, it suits the UAI conference.
+
+In [1] the original LISTA paper is used as an example of unsupervised learning in deep learning.
 In [2] it is used for image super-resolution.
 In [3] general improvements to original paper are proposed.
-Sparse coding and sparse models in general are of interest in ML community - Wipf NIPS 2017.
+Other deep sparse coding and sparse models in general are of recent interest in ML community [4], [5].
 
-[1] LeCun, Y., Bengio, Y., Hinton, G. (2015). Deep learning. nature, 521(7553), 436.
-[2] Wang, Z., Liu, D., Yang, J., Han, W., Huang, T.
-(2015).
-Deep networks for image super-resolution with sparse prior.
-In Proceedings of the IEEE International Conference on Computer Vision (pp.
-370-378).
-[3] Sprechmann, P., Bronstein, A. M., Sapiro, G. (2015). Learning efficient sparse and low rank models. IEEE transactions on pattern analysis and machine intelligence, 37(9), 1821-1833.
+[1] LeCun, Y., Bengio, Y., Hinton, G. (2015). Deep learning. Nature.
+[2] Wang, Z., Liu, D., Yang, J., Han, W., Huang, T. (2015). Deep networks for image super-resolution with sparse prior. ICCV.
+[3] Sprechmann, P., Bronstein, A. M., Sapiro, G. (2015). Learning efficient sparse and low rank models. TPAMI.
 [4] Papyan, V., Romano, Y., Elad, M. (2017). Convolutional neural networks analyzed via convolutional sparse coding. JMLR.
+[5] He, H., Xin, B., Ikehata, S., Wipf, D. (2017). From Bayesian Sparsity to Gated Recurrent Nets. NIPS.
 
@@
 \end{quote}
-I don't fully understand. I don't think we can do anything with this point in the reply.
+\textcolor{blue}{I don't fully understand. I don't think we can do anything with this point in the reply.}
 
@@
 if this is not real data.
-Is the experiment composed of real data and synthetic weights?}
+Is the experiment composed of real data and synthetic weights?
+While the focus is on estimation, for real data, would be useful to see prediction results (again, I am assuming ground truth is not known).}
 \end{quote}
-We need to explain again the setup of the experiments, that we know ground truth.
-
-\begin{quote}
-\textit{While the focus is on estimation, for real data, would be useful to see prediction results (again, I am assuming ground truth is not known).}
-\end{quote}
-I don't fully understand. Think about this.
-
-Combine with the previous. Predictive performance is evaluated.
+\textcolor{blue}{We need to explain again the setup of the experiments, that we know ground truth. Predictive performance is evaluated.}
 
@@
 \end{quote}
-I don't think we can do anything with this point in the reply. Join this with reviever 3 and move proofs to appendix.
+\textcolor{blue}{I don't think we can do anything with this point in the reply.} We'll move proofs to appendix.
 
@@
 \end{quote}
-What?
-Wikipedia: In Bayesian inference, one can speak about the likelihood of any proposition or random variable given another random variable: for example the likelihood of a parameter value or of a statistical model (see marginal likelihood), given specified data or other evidence
-
-I think the question is why do we have this Gaussian noise model.
+\textcolor{blue}{This is an awkwardly formulated question.
+Maybe the question is why do we have this Gaussian noise model.
 We can say something that this is now normally people are introducing the Bayesian models.
-Give examples Bayesian linear regression, Probabilistic Backpropagation.
+Give example of Probabilistic Backpropagation.}
 
@@
 \end{quote}
-Check this
-
 Bayesian models in general show themselves espesially useful when dealing with limited data, when the frequentist counterparts may suffer from inadequate maximum likelihood estimates.
@@
 \end{quote}
+\textcolor{blue}{We are running experiments with this}
 It was epmirically set. This value looks reasonable, since we use normalised data. As we mention in the paper the type II maximum likelihood can be used to find this value.
-Try to implement this maximisation.
-Try another value. (to add something like the results does not depend too much on this value.)
 
@@
 
-Check this
-
 \begin{quote}
@@
 \end{quote}
-Good idea
+We'll move some proofs to the appendix and enlarge the figures.
 
-\section*{ToDo List}
-\begin{enumerate}
-  \item Enlarge the figures.
-  \item Check motivation of LISTA in ML.
-  \item Check reviwer 3 without lambda
-  \item Check the clock time.
-  \item Explain why baseline ISTA/FISTA is better in the synthetic data case.
-  \item Think about the gap in performance when number of layers increases.
-  \item Think if the method is expandable for different nonlinearities and distributions.
-  \item Think about prediction results on real data as in review 2.
-  \item Check reviewer 3 lambda.
-  \item Consider heavier experiments.
-  \item Think about different interpretations of lista as it waas uncelar in review 2.
-\end{enumerate}
+% \section*{ToDo List}
+% \begin{enumerate}
+%   \item Enlarge the figures.
+%   \item Check motivation of LISTA in ML.
+%   \item Check reviwer 3 without lambda
+%   \item Check the clock time.
+%   \item Explain why baseline ISTA/FISTA is better in the synthetic data case.
+%   \item Think about the gap in performance when number of layers increases.
+%   \item Think if the method is expandable for different nonlinearities and distributions.
+%   \item Think about prediction results on real data as in review 2.
+%   \item Check reviewer 3 lambda.
+%   \item Consider heavier experiments.
+%   \item Think about different interpretations of lista as it waas uncelar in review 2.
+% \end{enumerate}
 

### 2018-05-12 theano/algorithms/PBP_net/net_pbp.py
more experiments

@@ -1,0 +1,198 @@
+
+import numpy as np
+
+import pickle
+
+import gzip
+
+from PBP_net import pbp
+
+
+class net_pbp:
+
+    def __init__(self, X_train, y_train, n_hidden, n_epochs = 40,
+        normalize = False):
+
+        """
+            Constructor for the class implementing a Bayesian neural network
+            trained with the probabilistic back propagation method.
+
+            @param X_train      Matrix with the features for the training data.
+            @param y_train      Vector with the target variables for the
+                                training data.
+            @param n_hidden     Vector with the number of neurons for each
+                                hidden layer.
+            @param n_epochs     Numer of epochs for which to train the
+                                network. The recommended value 40 should be
+                                enough.
+            @param normalize    Whether to normalize the input features. This
+                                is recommended unles the input vector is for
+                                example formed by binary features (a
+                                fingerprint). In that case we do not recommend
+                                to normalize the features.
+        """
+
+        # We normalize the training data to have zero mean and unit standard
+        # deviation in the training set if necessary
+
+        if normalize:
+            self.std_X_train = np.std(X_train, 0)
+            self.std_X_train[ self.std_X_train == 0 ] = 1
+            self.mean_X_train = np.mean(X_train, 0)
+        else:
+            self.std_X_train = np.ones(X_train.shape[ 1 ])
+            self.mean_X_train = np.zeros(X_train.shape[ 1 ])
+
+        X_train = (X_train - np.full(X_train.shape, self.mean_X_train)) / \
+            np.full(X_train.shape, self.std_X_train)
+
+        self.mean_y_train = np.mean(y_train)
+        self.std_y_train = np.std(y_train)
+
+        y_train_normalized = (y_train - self.mean_y_train) / self.std_y_train
+
+        # We construct the network
+
+        n_units_per_layer = \
+            np.concatenate(([ X_train.shape[ 1 ] ], n_hidden, [ 1 ]))
+        self.pbp_instance = \
+            pbp.PBP(n_units_per_layer, self.mean_y_train, self.std_y_train)
+
+        # We iterate the learning process
+
+        self.pbp_instance.do_pbp(X_train, y_train_normalized, n_epochs)
+
+        # We are done!
+
+    def re_train(self, X_train, y_train, n_epochs):
+
+        """
+            Function that re-trains the network on some data.
+
+            @param X_train      Matrix with the features for the training data.
+            @param y_train      Vector with the target variables for the
[…]

### 2018-05-12 theano/algorithms/PBP_net/network.py

@@ -1,0 +1,144 @@
+
+import numpy as np
+
+import theano
+
+import theano.tensor as T
+
+from PBP_net import network_layer
+
+
+class Network:
+
+    def __init__(self, m_w_init, v_w_init, a_init, b_init):
+
+        # We create the different layers
+
+        self.layers = []
+
+        if len(m_w_init) > 1:
+            for m_w, v_w in zip(m_w_init[ : -1 ], v_w_init[ : -1 ]):
+                self.layers.append(network_layer.Network_layer(m_w, v_w, True))
+
+        self.layers.append(network_layer.Network_layer(m_w_init[ -1 ],
+            v_w_init[ -1 ], False))
+
+        # We create mean and variance parameters from all layers
+
+        self.params_m_w = []
+        self.params_v_w = []
+        self.params_w = []
+        for layer in self.layers:
+            self.params_m_w.append(layer.m_w)
+            self.params_v_w.append(layer.v_w)
+            self.params_w.append(layer.w)
+
+        # We create the theano variables for a and b
+
+        self.a = theano.shared(float(a_init))
+        self.b = theano.shared(float(b_init))
+
+    def output_deterministic(self, x):
+
+        # Recursively compute output
+
+        for layer in self.layers:
+            x = layer.output_deterministic(x)
+
+        return x
+
+    def output_probabilistic(self, m):
+
+        v = T.zeros_like(m)
+
+        # Recursively compute output
+
+        for layer in self.layers:
+            m, v = layer.output_probabilistic(m, v)
+
+        return (m[ 0 ], v[ 0 ])
+
+    def logZ_Z1_Z2(self, x, y):
+
+        m, v = self.output_probabilistic(x)
+
+
+
+        v_final = v + self.b / (self.a - 1)
+        v_final1 = v + self.b / self.a
+        v_final2 = v + self.b / (self.a + 1)
+
+        logZ = -0.5 * (T.log(v_final) + (y - m)**2 / v_final)
+        logZ1 = -0.5 * (T.log(v_final1) + (y - m)**2 / v_final1)
+        logZ2 = -0.5 * (T.log(v_final2) + (y - m)**2 / v_final2)
+
+        return (logZ, logZ1, logZ2)
+
+    def generate_updates(self, logZ, logZ1, logZ2):
+
+        updates = []
+        for i in range(len(self.params_m_w)):
[…]

### 2018-05-12 theano/algorithms/PBP_net/pbp.py

@@ -1,0 +1,140 @@
+
+import sys
+
+import math
+
+import numpy as np
+
+import theano
+
+import theano.tensor as T
+
+from PBP_net import network, prior
+
+
+class PBP:
+
+    def __init__(self, layer_sizes, mean_y_train, std_y_train):
+
+        var_targets = 1
+        self.std_y_train = std_y_train
+        self.mean_y_train = mean_y_train
+
+        # We initialize the prior
+
+        self.prior = prior.Prior(layer_sizes, var_targets)
+
+        # We create the network
+
+        params = self.prior.get_initial_params()
+        self.network = network.Network(params[ 'm_w' ], params[ 'v_w' ],
+            params[ 'a' ], params[ 'b' ])
+
+        # We create the input and output variables in theano
+
+        self.x = T.vector('x')
+        self.y = T.scalar('y')
+        
+        # A function for computing the value of logZ, logZ1 and logZ2
+
+        self.logZ, self.logZ1, self.logZ2 = \
+            self.network.logZ_Z1_Z2(self.x, self.y)
+
+        # We create a theano function for updating the posterior
+
+        self.adf_update = theano.function([ self.x, self.y ], self.logZ,
+            updates = self.network.generate_updates(self.logZ, self.logZ1,
+            self.logZ2))
+
+        # We greate a theano function for the network predictive distribution
+
+        self.predict_probabilistic = theano.function([ self.x ],
+            self.network.output_probabilistic(self.x))
+
+        self.predict_deterministic = theano.function([ self.x ],
+            self.network.output_deterministic(self.x))
+
+    def do_pbp(self, X_train, y_train, n_iterations):
+
+        if n_iterations > 0:
+
+            # We first do a single pass
+
+            self.do_first_pass(X_train, y_train)
+
+            # We refine the prior
+
+            params = self.network.get_params()
+            params = self.prior.refine_prior(params)
+            self.network.set_params(params)
+
+            sys.stdout.write('{}\n'.format(0))
+            sys.stdout.flush()
+
+            for i in range(int(n_iterations) - 1):
+
+                # We do one more pass
+
+                params = self.prior.get_params()
+                self.do_first_pass(X_train, y_train)
+
+                # We refine the prior
+
+                params = self.network.get_params()
+                params = self.prior.refine_prior(params)
+                self.network.set_params(params)
+
[…]

### 2018-05-12 theano/algorithms/PBP_net_lista/BayesianListaHandler.py

@@ -1,0 +1,71 @@
+
+import numpy as np
+
+from algorithms.ListaHandler import ListaHandler
+from algorithms.PBP_net_lista import pbp
+
+
+class BayesianListaHandler(ListaHandler):
+    def __init__(self, D, K, L, X, initial_lambda):
+        super().__init__(D, K, L, X, initial_lambda)
+
+        mean_y_train = np.zeros(K)
+        std_y_train = np.identity(K)
+
+        self.pbp_instance = pbp.PBP_lista(L, D, K, X, mean_y_train, std_y_train, initial_lambda)
+
+    # def train_iteration(self, beta_train, y_train, sample_mean=False):
+    #     self.pbp_instance.do_pbp(beta_train, y_train, n_iterations=1)
+    #     if sample_mean:
+    #         self.pbp_instance.sample_mean_ws()
+    #     else:
+    #         self.pbp_instance.sample_ws()
+    #     return self.test(beta_train, y_train)
+
+    def train_iteration(self, beta_train, y_train, sample_mean=True):
+        self.pbp_instance.do_pbp(beta_train, y_train, n_iterations=1)
+        if sample_mean:
+            self.pbp_instance.sample_mean_ws()
+        else:
+            self.pbp_instance.sample_ws()
+        return self.test(beta_train, y_train)
+
+    # def test(self, beta_test, y_test):
+    #     beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
+    #     return self.mse(beta_test, beta_estimator)
+
+    def test(self, beta_test, y_test):
+        beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
+
+        return self.nmse(beta_test, beta_estimator), self.f_measure(beta_test, beta_estimator)
+
+    def predict(self, y_test):
+        beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
+        return beta_estimator
+
+    # def mse(self, beta_true, beta_estimator):
+    #     return np.mean(np.sqrt(np.sum((beta_estimator - beta_true)**2, axis=1)))
+
+    def nmse(self, beta_true, beta_estimator):
+        return np.mean(np.sqrt(np.sum((beta_estimator - beta_true)**2, axis=1)) / np.sqrt(np.sum(beta_true**2, axis=1)))
+
+    def f_measure(self, beta_true, beta_estimator):
+        true_zero_loc = beta_true == 0
+        true_nonzero_loc = beta_true != 0
[…]

### 2018-05-12 theano/algorithms/PBP_net_lista/net_lista.py

@@ -1,0 +1,201 @@
+
+import numpy as np
+
+import pickle
+
+import gzip
+
+from PBP_net_lista import pbp
+
+
+class net_lista:
+
+    def __init__(self, Beta_train, Y_train, L, n_epochs = 40,
+        normalize = False):
+
+        """
+            Constructor for the class implementing a Bayesian neural network
+            trained with the probabilistic back propagation method.
+
+            @param X_train      Matrix with the features for the training data.
+            @param y_train      Vector with the target variables for the
+                                training data.
+            @param n_hidden     Vector with the number of neurons for each
+                                hidden layer.
+            @param n_epochs     Numer of epochs for which to train the
+                                network. The recommended value 40 should be
+                                enough.
+            @param normalize    Whether to normalize the input features. This
+                                is recommended unles the input vector is for
+                                example formed by binary features (a
+                                fingerprint). In that case we do not recommend
+                                to normalize the features.
+        """
+
+        # We normalize the training data to have zero mean and unit standard
+        # deviation in the training set if necessary
+
+        if normalize:
+            self.std_Beta_train = np.std(Beta_train, 0)
+            self.std_Beta_train[ self.std_Beta_train == 0 ] = 1
+            self.mean_Beta_train = np.mean(Beta_train, 0)
+        else:
+            self.std_Beta_train = np.ones(Beta_train.shape[ 1 ])
+            self.mean_Beta_train = np.zeros(Beta_train.shape[ 1 ])
+
+        Beta_train = (Beta_train - np.full(Beta_train.shape, self.mean_Beta_train)) / \
+            np.full(Beta_train.shape, self.std_Beta_train)
+
+        self.mean_Y_train = np.mean(Y_train, axis=0)
+        self.std_Y_train = np.std(Y_train, axis=0)
+
+        Y_train_normalized = (Y_train - self.mean_Y_train) / self.std_Y_train
+
+        # We construct the network
+
+        # n_units_per_layer = \
+        #     np.concatenate(([ X_train.shape[ 1 ] ], n_hidden, [ 1 ]))
+
+        N, D = Beta_train.shape
+        N, K = Y_train.shape
+        self.pbp_instance = \
+            pbp.PBP_lista(L, D, K, self.mean_Y_train, self.std_Y_train)
+
+        # We iterate the learning process
+
+        self.pbp_instance.do_pbp(Beta_train, Y_train_normalized, n_epochs)
+
+        # We are done!
+
+    def re_train(self, X_train, y_train, n_epochs):
+
+        """
[…]

### 2018-05-12 theano/algorithms/PBP_net_lista/pbp.py

@@ -1,0 +1,229 @@
+import sys
+
+import math
+
+import numpy as np
+
+import theano
+
+import theano.tensor as T
+from tqdm import tqdm
+
+from algorithms.PBP_net_lista import prior, network
+
+
+class PBP_lista:
+
+    def __init__(self, L, D, K, X_design_matrix, mean_y_train, std_y_train, initial_lambda):
+
+        self.D = D
+        self.K = K
+
+        var_targets = 1
+        self.std_y_train = std_y_train
+        self.mean_y_train = mean_y_train
+
+        # We initialize the prior
+
+        self.prior = prior.Prior(L, D, K, var_targets)
+
+        # We create the network
+
+        params = self.prior.get_initial_params()
+
+        thr_lambda = initial_lambda
+
+        params['W_M'] = []
+        params['S_M'] = []
+
+        W_init = X_design_matrix.T / (1.01 * np.linalg.norm(X_design_matrix, 2) ** 2)
+        S_init = np.identity(D) - np.matmul(W_init, X_design_matrix)
+
+        for i in range(L):
+            params['W_M'].append(W_init)
+            params['S_M'].append(S_init)
+
+        self.network = network.Network(params['W_M'], params['W_V'], params['S_M'], params['S_V'], thr_lambda,
+                                       params['a'], params['b'], D, K)
+
+        # We create the input and output variables in theano
+
+        self.y = T.vector('y')
+        self.beta = T.vector('beta')
+
+        # A function for computing the value of logZ, logZ1 and logZ2
+
+        self.logZ, self.logZ1, self.logZ2, self.test_student, self.test_student1, self.test_student2, self.test_norm, \
+            self.test_norm1, self.test_norm2, self.a_j, self.b_j, self.beta_temp, self.mu_student, \
+            self.v_student, self.v_studen1, self.v_student2, self.nu_student, self.nu_student1, self.nu_student2, \
+            self.v_final, self.v_final1, self.v_final2 = \
+            self.network.logZ_Z1_Z2(self.beta, self.y)
+
+        # We create a theano function for updating the posterior
+
+        self.adf_update = theano.function([self.beta, self.y], self.logZ,
+                                          updates=self.network.generate_updates(self.logZ, self.logZ1,
+                                                                                self.logZ2))
+
+        # We greate a theano function for the network predictive distribution
+
+        self.predict_probabilistic = theano.function([self.y],
+                                                     self.network.output_probabilistic(self.y))
+
+        self.predict_deterministic = theano.function([self.y],
[…]

### 2018-05-12 theano/algorithms/PBP_net_lista/prior.py

@@ -1,0 +1,224 @@
+
+import numpy as np
+
+class Prior:
+
+    def __init__(self, L, D, K, var_targets):
+
+        # We refine the factor for the prior variance on the weights
+
+        n_samples = 3.0
+        v_observed = 1.0
+        self.a_w = 2.0 * n_samples
+        self.b_w = 2.0 * n_samples * v_observed
+        self.a_s = 2.0 * n_samples
+        self.b_s = 2.0 * n_samples * v_observed
+
+        # We refine the factor for the prior variance on the noise
+
+        n_samples = 3.0
+        a_sigma = 2.0 * n_samples
+        b_sigma = 2.0 * n_samples * var_targets
+
+        self.a_sigma_hat_nat = a_sigma - 1
+        self.b_sigma_hat_nat = -b_sigma
+
+        # We refine the gaussian prior on the weights
+
+        self.rnd_m_w = []
+        self.m_w_hat_nat = []
+        self.v_w_hat_nat = []
+        self.a_w_hat_nat = []
+        self.b_w_hat_nat = []
+
+        self.rnd_m_s = []
+        self.m_s_hat_nat = []
+        self.v_s_hat_nat = []
+        self.a_s_hat_nat = []
+        self.b_s_hat_nat = []
+
+        for l in range(L):
+            self.rnd_m_w.append(np.random.randn(D, K))
+            self.m_w_hat_nat.append(np.zeros((D, K)))
+            self.v_w_hat_nat.append((self.a_w - 1) / self.b_w * np.ones((D, K)))
+            self.a_w_hat_nat.append(np.zeros((D, K)))
+            self.b_w_hat_nat.append(np.zeros((D, K)))
+
+            self.rnd_m_s.append(np.random.randn(D, D))
+            self.m_s_hat_nat.append(np.zeros((D, D)))
+            self.v_s_hat_nat.append((self.a_s - 1) / self.b_s * np.ones((D, D)))
+            self.a_s_hat_nat.append(np.zeros((D, D)))
+            self.b_s_hat_nat.append(np.zeros((D, D)))
+
+    def get_initial_params(self):
+
+        m_w = []
+        v_w = []
+        m_s = []
+        v_s = []
+
+        for i in range(len(self.rnd_m_w)):
+            m_w.append(self.rnd_m_w[ i ])
+            v_w.append(1.0 / self.v_w_hat_nat[ i ])
+            m_s.append(self.rnd_m_s[i])
+            v_s.append(1.0 / self.v_s_hat_nat[i])
+
+
[…]

### 2018-05-12 theano/algorithms/PBP_net_lista/test_PBP_net_lista.py

@@ -1,0 +1,45 @@
+from PBP_net_lista.net_lista import net_lista
+import numpy as np
+
+import seaborn as sns
+import matplotlib.pyplot as plt
+
+from PBP_net_lista.DataGenerator import DataGenerator
+from PBP_net_lista.test_network_layer import random_spike_and_slab
+
+np.random.seed(1)
+
+D = 10
+K = 5
+N_train = 100000
+N_test = 1
+
+# theano.config.exception_verbosity='high'
+# theano.config.optimizer='None'
+
+dataGenerator = DataGenerator(D, K)
+Beta_train, Y_train, _ = dataGenerator.new_sample(N_train)
+Beta_test, Y_test, _ = dataGenerator.new_sample(N_test)
+
+L = 3
+
+net = net_lista(Beta_train, Y_train, L)
+w, m, v, v_noise = net.predict(Y_test)
+net.sample_weights()
+beta = net.predict_deterministic(Y_test)
+print("w:{}\n, m:{}\n, v:{}\n, v_noise:{}\n, beta: {}\n".format(w, m, v, v_noise, beta))
+
+n = 0
+
+sample_size = 100000
+
+sample_z = np.zeros((sample_size, D), dtype=np.float64)
+for i in range(sample_size):
+    sample_z[i, :] = random_spike_and_slab(m[n], np.sqrt(v[n]), w[n])
+
+for d in range(D):
+    print("Sample {0}. Parameters for dim{1}. w:{2}, m:{3}, v:{4}, beta:{5}\n".format(n, d, w[n, d], m[n, d], v[n, d], Beta_test[n, d]))
+    sns.distplot(sample_z[:, d])
+    plt.plot((Beta_test[n, d], Beta_test[n, d]), (0, 1), 'k-')
+    plt.show()
+

### 2018-05-12 theano/algorithms/PBP_net_lista_single_matrices/DataGenerator.py

@@ -1,0 +1,47 @@
+import numpy as np
+
+
+class DataGenerator:
+
+    def __init__(self, D, K, sparsity=0.8, beta_scale=1, noise_scale=0.5):
+        self.D = D  # beta
+        self.K = K  # y
+        self.beta_scale = beta_scale
+        self.noise_scale = noise_scale
+        self.sparsity = sparsity
+
+        self.X = np.random.randn(K, D)
+
+    def sample_slab(self, N, borders=(-0.1, 0.1)):
+        slab = np.zeros((N, self.D))
+        for i1 in range(N):
+            for i2 in range(self.D):
+                sampled = False
+                while not sampled:
+                    sample = np.random.normal(loc=0, scale=self.beta_scale, size=None)
+                    if sample < borders[0] or sample > borders[1]:
+                        slab[i1, i2] = sample
+                        sampled = True
+        return slab
+
+    def sample_omega(self, N):
+        omega = np.zeros((N, self.D))
+        eps = 1e-3
+        for n in range(N):
+            sampled = False
+            while not sampled:
+                omega[n] = np.random.binomial(1, self.sparsity, size=(1, self.D))
+                if np.sum(1-omega[n]) > eps and np.sum(omega[n]) > eps:
+                    sampled = True
+        return omega
+
+
+    def new_sample(self, N):
+        Y = np.zeros((N, self.K))
+        omega = self.sample_omega(N)
+        Beta = (1-omega) * self.sample_slab(N)
+        Noise = np.random.normal(loc=0, scale=self.noise_scale, size=(N, self.K))
+        for n in np.arange(N):
+            Y[n] = np.dot(self.X, Beta[n]) + Noise[n]
+
+        return Beta, Y, Noise

### 2018-05-12 theano/algorithms/PBP_net_lista_single_matrices/SingleBayesianListaHandler.py

@@ -1,0 +1,76 @@
+from algorithms.PBP_net_lista_single_matrices import pbp
+from algorithms.ListaHandler import ListaHandler
+import numpy as np
+
+
+class SingleBayesianListaHandler(ListaHandler):
+    def __init__(self, D, K, L, X, initial_lambda):
+        super().__init__(D, K, L, X, initial_lambda)
+
+        mean_y_train = np.zeros(K)
+        std_y_train = np.identity(K)
+
+        self.pbp_instance = pbp.PBP_lista(L, D, K, X, mean_y_train, std_y_train, initial_lambda)
+
+    # def train_iteration(self, beta_train, y_train, sample_mean=False):
+    #     self.pbp_instance.do_pbp(beta_train, y_train, n_iterations=1)
+    #     if sample_mean:
+    #         self.pbp_instance.sample_mean_ws()
+    #     else:
+    #         self.pbp_instance.sample_ws()
+    #     return self.test(beta_train, y_train)
+
+    def train_iteration(self, beta_train, y_train, sample_mean=True):
+        self.pbp_instance.do_pbp(beta_train, y_train, n_iterations=1)
+        if sample_mean:
+            self.pbp_instance.sample_mean_ws()
+        else:
+            self.pbp_instance.sample_ws()
+        return self.test(beta_train, y_train)
+
+
+    # def test(self, beta_test, y_test):
+    #     beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
+    #     return self.mse(beta_test, beta_estimator)
+
+    def test(self, beta_test, y_test):
+        beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
+        return self.nmse(beta_test, beta_estimator), self.f_measure(beta_test, beta_estimator)
+
+    def predict(self, y_test):
+        beta_estimator = self.pbp_instance.get_deterministic_output(y_test)
+        return beta_estimator
+
+    def predict_probabilistic(self, y_test):
+        w_list = []
+        m_list = []
+        v_list = []
+        for i in range(y_test.shape[0]):
+            w, m, v = self.pbp_instance.predict_probabilistic(y_test[i])
+            w_list.append(w)
+            m_list.append(m)
+            v_list.append(v)
+        return np.array(w_list), np.array(m_list), np.array(v_list)
+    # def mse(self, beta_true, beta_estimator):
[…]

### 2018-05-12 theano/algorithms/PBP_net_lista_single_matrices/net_lista.py

@@ -1,0 +1,201 @@
+
+import numpy as np
+
+import pickle
+
+import gzip
+
+from PBP_net_lista_single_matrices import pbp
+
+
+class net_lista:
+
+    def __init__(self, Beta_train, Y_train, L, n_epochs = 40,
+        normalize = False):
+
+        """
+            Constructor for the class implementing a Bayesian neural network
+            trained with the probabilistic back propagation method.
+
+            @param X_train      Matrix with the features for the training data.
+            @param y_train      Vector with the target variables for the
+                                training data.
+            @param n_hidden     Vector with the number of neurons for each
+                                hidden layer.
+            @param n_epochs     Numer of epochs for which to train the
+                                network. The recommended value 40 should be
+                                enough.
+            @param normalize    Whether to normalize the input features. This
+                                is recommended unles the input vector is for
+                                example formed by binary features (a
+                                fingerprint). In that case we do not recommend
+                                to normalize the features.
+        """
+
+        # We normalize the training data to have zero mean and unit standard
+        # deviation in the training set if necessary
+
+        if normalize:
+            self.std_Beta_train = np.std(Beta_train, 0)
+            self.std_Beta_train[ self.std_Beta_train == 0 ] = 1
+            self.mean_Beta_train = np.mean(Beta_train, 0)
+        else:
+            self.std_Beta_train = np.ones(Beta_train.shape[ 1 ])
+            self.mean_Beta_train = np.zeros(Beta_train.shape[ 1 ])
+
+        Beta_train = (Beta_train - np.full(Beta_train.shape, self.mean_Beta_train)) / \
+            np.full(Beta_train.shape, self.std_Beta_train)
+
+        self.mean_Y_train = np.mean(Y_train, axis=0)
+        self.std_Y_train = np.std(Y_train, axis=0)
+
+        Y_train_normalized = (Y_train - self.mean_Y_train) / self.std_Y_train
+
+        # We construct the network
+
+        # n_units_per_layer = \
+        #     np.concatenate(([ X_train.shape[ 1 ] ], n_hidden, [ 1 ]))
+
+        N, D = Beta_train.shape
+        N, K = Y_train.shape
+        self.pbp_instance = \
+            pbp.PBP_lista(L, D, K, self.mean_Y_train, self.std_Y_train)
+
+        # We iterate the learning process
+
+        self.pbp_instance.do_pbp(Beta_train, Y_train_normalized, n_epochs)
+
[…]

### 2018-05-12 theano/algorithms/PBP_net_lista_single_matrices/network_layer.py

@@ -1,0 +1,75 @@
+import theano
+
+import theano.tensor as T
+
+import numpy as np
+
+def n_cdf(x):
+    return 0.5 * (1.0 + T.erf(x / T.sqrt(2.0)))
+
+def n_pdf(x, mu, sigma):
+    return 1 / T.sqrt(2 * np.pi * sigma) * T.exp(-0.5 * (x - mu) ** 2 / sigma)
+
+def student_pdf(x, mu, beta, nu):
+    return T.gamma(0.5 * (nu + 1)) / (T.gamma(0.5 * nu) * T.sqrt(np.pi * nu * beta)) * T.power(
+        (1 + 1 / nu * (x - mu) ** 2 / beta), -0.5 * (nu + 1))
+
+def theano_soft_threshold(v, thr_lambda):
+    return T.sgn(v) * T.maximum(abs(v) - thr_lambda, T.zeros_like(v))
+
+class Network_layer:
+
+    def __init__(self, thr_lambda):
+        self.thr_lambda = thr_lambda
+
+    def compute_B(self, y, W_M, W_V):
+        B_m = T.dot(W_M, y)
+        B_v = T.dot(W_V, y ** 2)
+        return B_m, B_v
+
+    def compute_D(self, z_w_prev, z_m_prev, z_v_prev, S_M, S_V):
+        var_z_prev = (1 - z_w_prev) * z_v_prev + (1 - z_w_prev) * z_w_prev * (z_m_prev ** 2)
+        D_m = T.dot(S_M, (1 - z_w_prev) * z_m_prev)
+        D_v = T.dot(S_M ** 2, var_z_prev) + T.dot(S_V, ((1 - z_w_prev) ** 2) * (z_m_prev ** 2)) + \
+              T.dot(S_V, var_z_prev)
+        return D_m, D_v
+
+    def compute_C(self, B_m, B_v, D_m, D_v):
+        C_m = B_m + D_m
+        C_v = B_v + D_v
+        return C_m, C_v
+
+    def compute_new_z(self, C_m, C_v):
+        z_new_m = 1 / T.sqrt(2 * np.pi) * T.sqrt(C_v) * T.exp(-((self.thr_lambda - C_m) ** 2) / (2 * C_v)) - \
+                  1 / T.sqrt(2 * np.pi) * T.sqrt(C_v) * T.exp(-((self.thr_lambda + C_m) ** 2) / (2 * C_v)) + \
[…]

### 2018-05-12 theano/algorithms/PBP_net_lista_single_matrices/prior.py

@@ -1,0 +1,197 @@
+
+import numpy as np
+
+class Prior:
+
+    def __init__(self, L, D, K, var_targets):
+
+        # We refine the factor for the prior variance on the weights
+
+        n_samples = 3.0
+        v_observed = 1.0
+        #v_observed = 10000.0
+        self.a_w = 2.0 * n_samples
+        self.b_w = 2.0 * n_samples * v_observed
+        self.a_s = 2.0 * n_samples
+        self.b_s = 2.0 * n_samples * v_observed
+
+        # We refine the factor for the prior variance on the noise
+
+        n_samples = 3.0
+        a_sigma = 2.0 * n_samples
+        b_sigma = 2.0 * n_samples * var_targets
+
+        self.a_sigma_hat_nat = a_sigma - 1
+        self.b_sigma_hat_nat = -b_sigma
+
+        # We refine the gaussian prior on the weights
+
+        self.rnd_m_w = np.random.randn(D, K)
+        self.m_w_hat_nat = np.zeros((D, K))
+        self.v_w_hat_nat = (self.a_w - 1) / self.b_w * np.ones((D, K))
+        self.a_w_hat_nat = np.zeros((D, K))
+        self.b_w_hat_nat = np.zeros((D, K))
+
+        self.rnd_m_s = np.random.randn(D, D)
+        self.m_s_hat_nat = np.zeros((D, D))
+        self.v_s_hat_nat = (self.a_s - 1) / self.b_s * np.ones((D, D))
+        self.a_s_hat_nat = np.zeros((D, D))
+        self.b_s_hat_nat = np.zeros((D, D))
+
+    def get_initial_params(self):
+
+        m_w = self.rnd_m_w
+        v_w = 1.0 / self.v_w_hat_nat
+        m_s = self.rnd_m_s
+        v_s = 1.0 / self.v_s_hat_nat
+
+        return {'W_M': m_w, 'W_V': v_w, 'S_M': m_s, 'S_V': v_s, 'a': self.a_sigma_hat_nat + 1,
+                'b': -self.b_sigma_hat_nat}
+
+    def get_params(self):
+
+        m_w = self.m_w_hat_nat / self.v_w_hat_nat
+        v_w = 1.0 / self.v_w_hat_nat
+        m_s = self.m_s_hat_nat / self.v_s_hat_nat
+        v_s = 1.0 / self.v_s_hat_nat
+
[…]

### 2018-05-12 theano/algorithms/PBP_net_lista_single_matrices/test_compute_C.py

@@ -1,0 +1,66 @@
+from unittest import TestCase
+from PBP_net_lista.network_layer import compute_C
+
+import theano
+import theano.tensor as T
+import numpy as np
+
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+
+
+class TestNetwork_layer(TestCase):
+
+    def test_compute_C(self):
+        np.random.seed(1000)
+        D = 10
+        np_B_m = 2.5 * np.random.rand(D)
+        np_B_v = 1.5 * np.random.rand(D)
+        np_D_m = 8 * np.random.rand(D)
+        np_D_v = 31 * np.random.rand(D)
+
+        sample_size = 10000
+
+        sample_B = np.zeros((sample_size, D), dtype=np.float64)
+        for i in range(sample_size):
+            sample_B[i, :] = np.random.normal(np_B_m, np.sqrt(np_B_v))
+
+        sample_D = np.zeros((sample_size, D), dtype=np.float64)
+        for i in range(sample_size):
+            sample_D[i, :] = np.random.normal(np_D_m, np.sqrt(np_D_v))
+
+        B_m = T.vector()
+        B_v = T.vector()
+
+        D_m = T.vector()
+        D_v = T.vector()
+
+        C_m, C_v = compute_C(B_m, B_v, D_m, D_v)
+
+        f = theano.function([B_m, B_v, D_m, D_v], [C_m, C_v])
+
+        theano_C_m, theano_C_v = f(np_B_m, np_B_v, np_D_m, np_D_v)
+
+        true_C_sample = sample_B + sample_D
+
+
+        est_C_sample = np.zeros((sample_size, D), dtype=np.float64)
+        for i in range(sample_size):
+            est_C_sample[i, :] = np.random.normal(theano_C_m, np.sqrt(theano_C_v))
+
+        d = 5
+        sns.distplot(true_C_sample[:, d], label='true')
+        sns.distplot(est_C_sample[:, d], label='estimated')
+        plt.legend()
+        plt.title('compute C vector for column %d' %d)
+        plt.show()
+
+
+
+
+
+
+
+
+

### 2018-05-12 theano/algorithms/PBP_net_lista_single_matrices/test_compute_D.py

@@ -1,0 +1,127 @@
+from unittest import TestCase
+from PBP_net_lista.network_layer import compute_D
+
+import theano
+import theano.tensor as T
+import numpy as np
+
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+
+# def random_spike_and_slab(mean, std, omega_prob):
+#     omega = np.random.binomial(np.ones_like(omega_prob).astype(np.int), omega_prob)
+#
+#     beta = np.random.normal(mean, std) * (np.ones_like(omega) - omega)
+#
+#     return beta
+
+
+def compute_D_normal(S_M, S_V, z_m_prev, z_v_prev):
+    D_m = T.dot(S_M, z_m_prev)
+    D_v = T.dot(S_M ** 2, z_v_prev) + T.dot(S_V, z_m_prev ** 2) + \
+          T.dot(S_V, z_v_prev)
+    return D_m, D_v
+
+
+class TestNetwork_layer(TestCase):
+
+    def test_compute_D(self):
+        np.random.seed(1000)
+        D = 10
+        np_z_m = 3 * np.ones((D,), dtype=np.float64)
+        np_z_v = 1.5 * np.ones((D,), dtype=np.float64)
+        np_z_omega = np.random.rand(D)#0.8 * np.ones((D,), dtype=np.float64)#
+        np_S_M = np.random.randint(5, 10, size=(D, D)).astype(np.float64)
+        np_S_V = 3 * np.random.rand(D, D)
+
+        sample_size = 10000
+
+        sample_z = np.zeros((sample_size, D), dtype=np.float64)
+        for i in range(sample_size):
+            sample_z[i, :] = random_spike_and_slab(np_z_m, np.sqrt(np_z_v), np_z_omega)
+
+        sample_S = np.zeros((sample_size, D, D), dtype=np.float64)
+        for i in range(sample_size):
+            sample_S[i, :, :] = np.random.normal(np_S_M, np.sqrt(np_S_V))
+
+        z_m = T.vector()
+        z_v = T.vector()
+        z_omega = T.vector()
+
+        S_M = T.matrix()
+        S_V = T.matrix()
+
+        D_m, D_v = compute_D(S_M, S_V, z_omega, z_m, z_v)
+
+        f = theano.function([S_M, S_V, z_omega, z_m, z_v], [D_m, D_v])
+
+        theano_D_m, theano_D_v = f(np_S_M, np_S_V, np_z_omega, np_z_m, np_z_v)
+
[…]

### 2018-05-12 theano/algorithms/PBP_net_lista_single_matrices/test_compute_new_z.py

@@ -1,0 +1,66 @@
+from unittest import TestCase
+from PBP_net_lista.network_layer import compute_new_z
+
+import theano
+import theano.tensor as T
+import numpy as np
+
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+from PBP_net_lista.test_compute_D import random_spike_and_slab
+
+
+def soft_threshold(v, thr_lambda):
+    return np.sign(v) * np.maximum(abs(v) - thr_lambda, np.zeros_like(v))
+
+
+class TestNetwork_layer(TestCase):
+
+    def test_compute_new_z(self):
+        np.random.seed(1000)
+        D = 10
+        np_C_m = -6.5 * np.ones(D, dtype=np.float64)
+        np_C_v = 5 * np.ones(D, dtype=np.float64)
+        np_lambda = 1
+
+        sample_size = 100000
+
+        sample_C = np.zeros((sample_size, D), dtype=np.float64)
+        for i in range(sample_size):
+            sample_C[i, :] = np.random.normal(np_C_m, np.sqrt(np_C_v))
+
+        C_m = T.vector()
+        C_v = T.vector()
+
+        lambda_thr = T.scalar()
+
+        z_m, z_v, z_omega = compute_new_z(C_m, C_v, lambda_thr)
+
+        f = theano.function([C_m, C_v, lambda_thr], [z_m, z_v, z_omega])
+
+        theano_z_m, theano_z_v, theano_z_omega = f(np_C_m, np_C_v, np_lambda)
+
+
+        true_z_sample = soft_threshold(sample_C, np_lambda)
+
+
+        est_z_sample = np.zeros((sample_size, D), dtype=np.float64)
+        for i in range(sample_size):
+            est_z_sample[i, :] = random_spike_and_slab(theano_z_m, np.sqrt(theano_z_v), theano_z_omega)
+
+        d = 3
+        sns.distplot(true_z_sample[:, d], label='true')
+        sns.distplot(est_z_sample[:, d], label='estimated')
+        plt.legend()
+        plt.title('compute z_new vector for column %d' %d)
+        plt.show()
+
+
+
+
+
+
+
+
+

### 2018-05-12 theano/algorithms/PBP_net_lista_single_matrices/test_prior.py

@@ -1,0 +1,15 @@
+import numpy as np
+
+import prior
+import theano
+
+L = 2
+D = 10
+K = 5
+var_targets = 3.0
+
+pr = prior.Prior(L, D, K, var_targets)
+print(pr)
+
+params = pr.get_initial_params()
+print(params)

### 2018-05-12 theano/algorithms/fista/fIstaHandler.py

@@ -1,0 +1,48 @@
+from algorithms.PBP_net_lista import pbp
+from algorithms.ListaHandler import ListaHandler
+import numpy as np
+
+from algorithms.fista.fista import Fista
+from algorithms.ista.ista import Ista
+
+
+class FistaHandler(ListaHandler):
+    def __init__(self, D, K, L, X, initial_lambda):
+        super().__init__(D, K, L, X, initial_lambda)
+
+        self.fista = Fista(L, D, K, X, initial_lambda)
+
+    def test(self, beta_test, y_test):
+        beta_estimator = self.predict(y_test)
+        return self.nmse(beta_test, beta_estimator), self.f_measure(beta_test, beta_estimator)
+
+    def predict(self, y_test):
+        beta_estimator = self.fista.predict(y_test)
+        return beta_estimator
+
+    def nmse(self, beta_true, beta_estimator):
+        return np.mean(np.sqrt(np.sum((beta_estimator - beta_true)**2, axis=1)) / np.sqrt(np.sum(beta_true**2, axis=1)))
+
+    def f_measure(self, beta_true, beta_estimator):
+        true_zero_loc = beta_true == 0
+        true_nonzero_loc = beta_true != 0
+        est_zero_loc = beta_estimator == 0
+        est_nonzero_loc = beta_estimator != 0
+
+        tp = np.sum(true_nonzero_loc * est_nonzero_loc)
+        fp = np.sum(true_zero_loc * est_nonzero_loc)
+        fn = np.sum(true_nonzero_loc * est_zero_loc)
+
+        precision = tp / (tp + fp)
+        recall = tp / (tp + fn)
+
+        if precision + recall > 0:
+            return 2 * (precision * recall / (precision + recall))
+        else:
+            return 0
+
+    def train_iteration(self, beta_train, y_train):
+        return self.test(beta_train, y_train)
+
+
+

### 2018-05-12 theano/algorithms/freqLISTA/run_lista.py

@@ -1,0 +1,271 @@
+import timeit
+
+from PBP_net_lista.DataGenerator import DataGenerator
+from freqLISTA.lista import Lista
+import numpy as np
+import theano.tensor as T
+import theano
+import six.moves.cPickle as pickle
+
+import os
+import sys
+
+import matplotlib.pyplot as plt
+
+
+def load_data(n_train_batches, n_valid_batches, n_test_batches, D, K, data_generator):
+    def create_data(dataGenerator, n, borrow=True):
+        beta, y, _ = dataGenerator.new_sample(n)
+        shared_y = theano.shared(np.asarray(y, dtype=theano.config.floatX), borrow=borrow)
+        shared_beta = theano.shared(np.asarray(beta, dtype=theano.config.floatX), borrow=borrow)
+        return shared_beta, shared_y
+
+    beta_train, y_train = create_data(dataGenerator, n_train_batches)
+    beta_test, y_test = create_data(dataGenerator, n_valid_batches)
+    beta_valid, y_valid = create_data(dataGenerator, n_test_batches)
+
+    return [(beta_train, y_train), (beta_valid, y_valid), (beta_test, y_test)]
+
+
+def sgd_optimization_lista(beta_train, y_train, X, n_train_batches=10, learning_rate=0.13, n_epochs=1000,
+                           batch_size=600, D=10, K=5, L=6):
+    print('... building the model')
+    index = T.lscalar()
+
+    y = T.matrix('y')
+    beta = T.matrix('beta')
+
+    lista = Lista(L, D, K, y, X)
+
+    cost = lista.mean_squared_error(beta)
+
+    g_S = T.grad(cost=cost, wrt=lista.S)
+    g_W = T.grad(cost=cost, wrt=lista.W)
+
+    updates = [(lista.S, lista.S - learning_rate * g_S),
+               (lista.W, lista.W - learning_rate * g_W)]
+
+    train_model = theano.function(
+        inputs=[index],
+        outputs=cost,
+        updates=updates,
+        givens={
+            y: y_train[index * batch_size: (index + 1) * batch_size],
+            beta: beta_train[index * batch_size: (index + 1) * batch_size]
+        }
+    )
+
+    print('... training the model')
+
+    start_time = timeit.default_timer()
+
+    done_looping = False
+    epoch = 0
+    while (epoch < n_epochs) and (not done_looping):
+        epoch = epoch + 1
+        for minibatch_index in range(n_train_batches):
[…]

### 2018-05-12 theano/algorithms/freqLISTA/tests/test_f_measure.py

@@ -1,0 +1,213 @@
+import unittest
+import numpy as np
+import theano
+import theano.tensor as T
+
+
+
+class TestIBCCIterable(unittest.TestCase):
+
+#    def setUp(self):
+
+
+    def test_theano_eq(self):
+        a = np.array([0, 1, 0])
+        b = T.vector('b')
+        true_zero_loc = T.eq(b, 0)
+        f = theano.function(inputs=[b], outputs=true_zero_loc)
+        c = f(a)
+        self.assertTrue(np.allclose(c, np.array([1, 0, 1])))
+
+    def test_theano_neq(self):
+        a = np.array([0, 1, 0])
+        b = T.vector('b')
+        true_nonzero_loc = T.neq(b, 0)
+        f = theano.function(inputs=[b], outputs=true_nonzero_loc)
+        c = f(a)
+        self.assertTrue(np.allclose(c, np.array([0, 1, 0])))
+
+    def test_theano_tp(self):
+        true_signal = np.array([0, 1, 0])
+        est_signal = np.array([0, 1, 1])
+        correct_tp = np.sum((true_signal == 1) * (est_signal == 1))
+        true_b = T.vector('true_b')
+        est_b = T.vector('est_b')
+
+        true_nonzero_loc = T.neq(true_b, 0)
+        est_nonzero_loc = T.neq(est_b, 0)
+
+        tp = T.sum(true_nonzero_loc * est_nonzero_loc)
+        f = theano.function(inputs=[true_b, est_b], outputs=tp)
+        c = f(true_signal, est_signal)
+        self.assertTrue(np.allclose(c, correct_tp))
+
+    def test_theano_fp(self):
+        true_signal = np.array([0, 1, 0])
+        est_signal = np.array([0, 1, 1])
+        correct_fp = np.sum((true_signal == 0) * (est_signal == 1))
+        true_b = T.vector('true_b')
+        est_b = T.vector('est_b')
+
+        true_zero_loc = T.eq(true_b, 0)
+        est_nonzero_loc = T.neq(est_b, 0)
+
+        fp = T.sum(true_zero_loc * est_nonzero_loc)
+        f = theano.function(inputs=[true_b, est_b], outputs=fp)
+        c = f(true_signal, est_signal)
+        self.assertTrue(np.allclose(c, correct_fp))
+
+    def test_theano_fn(self):
+        true_signal = np.array([0, 1, 0])
+        est_signal = np.array([0, 1, 1])
[…]

### 2018-05-12 theano/comparator/compare_sequential.py

@@ -17,9 +17,9 @@ from algorithms.ista.IstaHandler import IstaHandler
 
 
 class SequentialComparator(object):
-    def __init__(self, D, K, L, learning_rate=0.0001, n_train_sample=1, n_validation_sample=1,
-                 train_freq=True, train_bayes=True, train_shared_bayes=True, use_ista=True, use_fista=True,
-                 save_history=False, initial_lambda=0.1):
+    def __init__(self, D, K, L, learning_rate, n_train_sample, n_validation_sample,
+                 train_freq, train_bayes, train_shared_bayes, use_ista, use_fista,
+                 save_history, initial_lambda):
 
         self.D = D
         self.K = K

### 2018-05-12 theano/compare_mnist/mnist_data.py

@@ -6,7 +6,7 @@ from sklearn.decomposition import MiniBatchDictionaryLearning
 import matplotlib.pyplot as plt
 
 class MnistData(object):
-    def __init__(self, K=100, train_size=100, valid_size=100):
+    def __init__(self, K, train_size, valid_size):
         self.train_data = None
         self.train_labels = None
         self.dictionary_learn_data = None

### 2018-05-12 theano/experiments/active_learning/mnist_test_2_seed_10_nonnormalise.py

@@ -1,0 +1,186 @@
+from tqdm import trange
+
+from PBP_net_lista.DataGenerator import DataGenerator
+from PBP_net_lista_single_matrices.SingleBayesianListaHandler import SingleBayesianListaHandler
+from compare_mnist.mnist_data import MnistData
+from freqLISTA.FrequentistListaHandler import FrequentistListaHandler
+import numpy as np
+import tensorflow as tf
+
+import matplotlib.pyplot as plt
+
+import six.moves.cPickle as pickle
+
+class ActiveLearningExperiments(object):
+    def __init__(self, update_size):
+        self.L = 20
+        self.learning_rate = 0.0001
+        self.n_train_iter = 50
+        self.update_size = update_size
+
+        self.freq_validation_loss = []
+        self.freq_validation_f_meas = []
+
+        self.active_bayesian_validation_loss = []
+        self.active_bayesian_validation_f_meas = []
+
+        self.non_active_shared_bayesian_validation_loss = []
+        self.non_active_shared_bayesian_validation_f_meas = []
+
+    def get_mnist_data_active_learning(self):
+        self.K=250
+        n_train, n_pool, n_test = 50, 500, 100
+        data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
+        data.check_download(normalise=False)
+        data.learn_dictionary()
+        self.D = data.train_data.shape[1]
+
+        self.train_data_beta, self.train_data_y = data.train_data[:n_train], data.y_train[:n_train]
+        self.pool_data_beta, self.pool_data_y = data.train_data[n_train+1:], data.y_train[n_train+1:]
+        self.test_data_beta, self.test_data_y = data.validation_data, data.y_validation
+        self.active_pool_data_beta, self.active_pool_data_y = self.pool_data_beta, self.pool_data_y
+        self.active_train_data_beta, self.active_train_data_y = self.train_data_beta, self.train_data_y
+
+        self.X = data.X
+        # return train_data_beta, train_data_y, pool_data_beta, pool_data_y, test_data_beta, test_data_y
+
+
+    def get_synthetic_data_active_learning(self):
+        self.D = 100
+        self.K = 50
+        n_train, n_pool, n_test = 500, 1000, 100
+        data_generator = DataGenerator(self.D, self.K)
+        self.train_data_beta, self.train_data_y, _ = data_generator.new_sample(n_train)
[…]

### 2018-05-12 theano/experiments/active_learning/mnist_test_2_seed_8_nonnormalise.py

@@ -1,0 +1,186 @@
+from tqdm import trange
+
+from PBP_net_lista.DataGenerator import DataGenerator
+from PBP_net_lista_single_matrices.SingleBayesianListaHandler import SingleBayesianListaHandler
+from compare_mnist.mnist_data import MnistData
+from freqLISTA.FrequentistListaHandler import FrequentistListaHandler
+import numpy as np
+import tensorflow as tf
+
+import matplotlib.pyplot as plt
+
+import six.moves.cPickle as pickle
+
+class ActiveLearningExperiments(object):
+    def __init__(self, update_size):
+        self.L = 20
+        self.learning_rate = 0.0001
+        self.n_train_iter = 50
+        self.update_size = update_size
+
+        self.freq_validation_loss = []
+        self.freq_validation_f_meas = []
+
+        self.active_bayesian_validation_loss = []
+        self.active_bayesian_validation_f_meas = []
+
+        self.non_active_shared_bayesian_validation_loss = []
+        self.non_active_shared_bayesian_validation_f_meas = []
+
+    def get_mnist_data_active_learning(self):
+        self.K=250
+        n_train, n_pool, n_test = 50, 500, 100
+        data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
+        data.check_download(normalise=False)
+        data.learn_dictionary()
+        self.D = data.train_data.shape[1]
+
+        self.train_data_beta, self.train_data_y = data.train_data[:n_train], data.y_train[:n_train]
+        self.pool_data_beta, self.pool_data_y = data.train_data[n_train+1:], data.y_train[n_train+1:]
+        self.test_data_beta, self.test_data_y = data.validation_data, data.y_validation
+        self.active_pool_data_beta, self.active_pool_data_y = self.pool_data_beta, self.pool_data_y
+        self.active_train_data_beta, self.active_train_data_y = self.train_data_beta, self.train_data_y
+
+        self.X = data.X
+        # return train_data_beta, train_data_y, pool_data_beta, pool_data_y, test_data_beta, test_data_y
+
+
+    def get_synthetic_data_active_learning(self):
+        self.D = 100
+        self.K = 50
+        n_train, n_pool, n_test = 500, 1000, 100
+        data_generator = DataGenerator(self.D, self.K)
+        self.train_data_beta, self.train_data_y, _ = data_generator.new_sample(n_train)
[…]

### 2018-05-12 theano/experiments/active_learning/mnist_test_2_seed_9_nonnormalise.py

@@ -1,0 +1,186 @@
+from tqdm import trange
+
+from PBP_net_lista.DataGenerator import DataGenerator
+from PBP_net_lista_single_matrices.SingleBayesianListaHandler import SingleBayesianListaHandler
+from compare_mnist.mnist_data import MnistData
+from freqLISTA.FrequentistListaHandler import FrequentistListaHandler
+import numpy as np
+import tensorflow as tf
+
+import matplotlib.pyplot as plt
+
+import six.moves.cPickle as pickle
+
+class ActiveLearningExperiments(object):
+    def __init__(self, update_size):
+        self.L = 20
+        self.learning_rate = 0.0001
+        self.n_train_iter = 50
+        self.update_size = update_size
+
+        self.freq_validation_loss = []
+        self.freq_validation_f_meas = []
+
+        self.active_bayesian_validation_loss = []
+        self.active_bayesian_validation_f_meas = []
+
+        self.non_active_shared_bayesian_validation_loss = []
+        self.non_active_shared_bayesian_validation_f_meas = []
+
+    def get_mnist_data_active_learning(self):
+        self.K=250
+        n_train, n_pool, n_test = 50, 500, 100
+        data = MnistData(K=self.K, train_size=n_train + n_pool, valid_size=n_test)
+        data.check_download(normalise=False)
+        data.learn_dictionary()
+        self.D = data.train_data.shape[1]
+
+        self.train_data_beta, self.train_data_y = data.train_data[:n_train], data.y_train[:n_train]
+        self.pool_data_beta, self.pool_data_y = data.train_data[n_train+1:], data.y_train[n_train+1:]
+        self.test_data_beta, self.test_data_y = data.validation_data, data.y_validation
+        self.active_pool_data_beta, self.active_pool_data_y = self.pool_data_beta, self.pool_data_y
+        self.active_train_data_beta, self.active_train_data_y = self.train_data_beta, self.train_data_y
+
+        self.X = data.X
+        # return train_data_beta, train_data_y, pool_data_beta, pool_data_y, test_data_beta, test_data_y
+
+
+    def get_synthetic_data_active_learning(self):
+        self.D = 100
+        self.K = 50
+        n_train, n_pool, n_test = 500, 1000, 100
+        data_generator = DataGenerator(self.D, self.K)
+        self.train_data_beta, self.train_data_y, _ = data_generator.new_sample(n_train)
[…]

### 2018-05-12 theano/experiments/mnist/collect_results_nonnormalised.py

@@ -1,149 +1,0 @@
-import errno
-import numpy as np
-import os
-import matplotlib.pyplot as plt
-
-class MnistExperimentResultsCollector(object):
-    def __init__(self):
-        self.n_iter = 500
-
-    def collect_all(self, undersampling):
-        self.ista_f_meas_train, self.ista_f_meas_validation, self.ista_loss_train, self.ista_loss_validation = \
-            self.collect_ista_fista('ista_fista/results_{}_K_ista.npz'.format(undersampling))
-        self.fista_f_meas_train, self.fista_f_meas_validation, self.fista_loss_train, self.fista_loss_validation = \
-            self.collect_ista_fista('ista_fista/results_{}_K_fista.npz'.format(undersampling))
-        self.freq_f_meas_train, self.freq_f_meas_validation, self.freq_loss_train, self.freq_loss_validation, \
-        self.sh_bayes_f_meas_train, self.sh_bayes_f_meas_validation, self.sh_bayes_loss_train, self.sh_bayes_loss_validation = \
-            self.collect_main('non_normalised_results/mnist_100_train_20_layers_K_{}'.format(undersampling))
-
-    def collect_ista_fista(self, fileprefix):
-        saved_res = np.load(fileprefix)
-        f_meas_train = saved_res['train_f_meas']
-        f_meas_validation = saved_res['validation_f_meas']
-        loss_train = saved_res['train_loss']
-        loss_validation = saved_res['validation_loss']
-
-        return f_meas_train, f_meas_validation, loss_train, loss_validation
-
-    def collect_main(self, filename_prefix):
-        saved_bayes_weights = np.load('{}_bayes_weights.npz'.format(filename_prefix))
-        bayes_S_M = saved_bayes_weights['bayes_S_M']
-        bayes_S_V = saved_bayes_weights['bayes_S_V']
-        bayes_W_M = saved_bayes_weights['bayes_W_M']
-        bayes_W_V = saved_bayes_weights['bayes_W_V']
-
-        saved_beta_est = np.load('{}_beta_est.npz'.format(filename_prefix))
-        freq_beta_train_est=saved_beta_est['freq_beta_train_est']
-        freq_beta_validation_est=saved_beta_est['freq_beta_validation_est']
-        shared_beta_train_est=saved_beta_est['shared_beta_train_est']
-        shared_beta_validation_est=saved_beta_est['shared_beta_validation_est']
-        true_beta_train=saved_beta_est['true_beta_train']
[…]

### 2018-05-12 theano/experiments/mnist/mnist_100_train_20_layers_K_100_ista_fista.py

@@ -1,55 +1,0 @@
-import errno
-import numpy as np
-import six.moves.cPickle as pickle
-
-import matplotlib.pyplot as plt
-from tqdm import tqdm, trange
-
-import os
-
-from compare_freq_bayes.compare_sequential_with_ista_fista import SequentialComparatorIstaFista
-from experiments.synthetic.experiments_parameters import load_long_experiment
-from compare_mnist.mnist_data import MnistData
-
-class MnistSequentialComparatorIstaFista(SequentialComparatorIstaFista):
-    def __init__(self, K, L, learning_rate=0.0001, n_train_sample=1, n_validation_sample=1,
-                 train_freq=False, train_bayes=False, train_shared_bayes=False, use_ista=True, use_fista=True, save_history=False):
-
-        self.data = MnistData(K=K)
-        self.data.check_download(normalise=False)
-        self.data.learn_dictionary()
-        self.D = self.data.train_data.shape[1]
-
-        super().__init__(self.D, K, L, learning_rate, n_train_sample, n_validation_sample,
-                 train_freq, train_bayes, train_shared_bayes, use_ista, use_fista, save_history)
-
-        self.beta_train = self.data.train_data
-        self.y_train = self.data.y_train
-        self.beta_validation = self.data.validation_data
-        self.y_validation = self.data.y_validation
-
-
-if __name__ == '__main__':
-    try:
-        os.makedirs('ista_fista')
-    except OSError as e:
-        if e.errno != errno.EEXIST:
-            raise
-
-    np.random.seed(1)
-
-    K = 100
-    L = 20
-
-    comparator = MnistSequentialComparatorIstaFista(K, L, learning_rate=0.0001, n_train_sample=100,
-                                      n_validation_sample=100, train_freq=False,
-                                      train_bayes=False, train_shared_bayes=False, use_ista=True, use_fista=True, save_history=True)
-    n_iter = 500
-
-    for _ in tqdm(range(n_iter)):
-        comparator.train_iteration()
-
-    comparator.plot_quality_history()
-
-
-    comparator.save_numpy('ista_fista/results_{}_K'.format(K))

### 2018-05-12 theano/experiments/mnist/mnist_100_train_20_layers_K_100_script.py

@@ -1,97 +1,0 @@
-import numpy as np
-import six.moves.cPickle as pickle
-from tqdm import tqdm
-
-from comparator.compare_sequential import SequentialComparator
-from compare_mnist.mnist_data import MnistData
-
-
-class MnistSequentialComparator_DFGHJDF(SequentialComparator):
-    def __init__(self, K, L, learning_rate=0.0001, n_train_sample=1, n_validation_sample=1,
-                 train_freq=True, train_bayes=True, train_shared_bayes=True, save_history=False):
-
-        self.data = MnistData(K=K)
-        self.data.check_download(normalise=False)
-        self.data.learn_dictionary()
-        self.D = self.data.train_data.shape[1]
-
-        super().__init__(self.D, K, L, learning_rate, n_train_sample, n_validation_sample,
-                 train_freq, train_bayes, train_shared_bayes, save_history)
-
-        self.beta_train = self.data.train_data
-        self.y_train = self.data.y_train
-        self.beta_validation = self.data.validation_data
-        self.y_validation = self.data.y_validation
-
-if __name__ == '__main__':
-
-    np.random.seed(1)
-
-    K = 100
-    L = 20
-
-    # batch_size = 5000
-    # validation_size = 100
-
-    saved_comparator_file_name = []#'test_S_convergence.pkl'
-
-
-    if not saved_comparator_file_name:
-        comparator = MnistSequentialComparator_DFGHJDF(K, L, learning_rate=0.0001,
-                                                       train_bayes=False, save_history=True,
-                                                       n_train_sample=100, n_validation_sample=100)
-    else:
-        comparator = pickle.load(open(saved_comparator_file_name, 'rb'))
-
-
-
-
-    n_iter = 300#500
-
-    for _ in tqdm(range(n_iter)):
-       comparator.train_iteration()
-
-    comparator.plot_quality_history()
-
-    lista_time = comparator.recorders['lista'].time
-    sh_bayes_time = comparator.recorders['shared_bayes'].time
-    lista_nmse = comparator.recorders['lista'].validation_loss
[…]

### 2018-05-12 theano/experiments/mnist/mnist_100_train_20_layers_K_250_ista_fista.py

@@ -1,55 +1,0 @@
-import errno
-import numpy as np
-import six.moves.cPickle as pickle
-
-import matplotlib.pyplot as plt
-from tqdm import tqdm, trange
-
-import os
-
-from compare_freq_bayes.compare_sequential_with_ista_fista import SequentialComparatorIstaFista
-from experiments.synthetic.experiments_parameters import load_long_experiment
-from compare_mnist.mnist_data import MnistData
-
-class MnistSequentialComparatorIstaFista(SequentialComparatorIstaFista):
-    def __init__(self, K, L, learning_rate=0.0001, n_train_sample=1, n_validation_sample=1,
-                 train_freq=False, train_bayes=False, train_shared_bayes=False, use_ista=True, use_fista=True, save_history=False):
-
-        self.data = MnistData(K=K)
-        self.data.check_download(normalise=False)
-        self.data.learn_dictionary()
-        self.D = self.data.train_data.shape[1]
-
-        super().__init__(self.D, K, L, learning_rate, n_train_sample, n_validation_sample,
-                 train_freq, train_bayes, train_shared_bayes, use_ista, use_fista, save_history)
-
-        self.beta_train = self.data.train_data
-        self.y_train = self.data.y_train
-        self.beta_validation = self.data.validation_data
-        self.y_validation = self.data.y_validation
-
-
-if __name__ == '__main__':
-    try:
-        os.makedirs('ista_fista')
-    except OSError as e:
-        if e.errno != errno.EEXIST:
-            raise
-
-    np.random.seed(1)
-
-    K = 250
-    L = 20
-
-    comparator = MnistSequentialComparatorIstaFista(K, L, learning_rate=0.0001, n_train_sample=100,
-                                      n_validation_sample=100, train_freq=False,
-                                      train_bayes=False, train_shared_bayes=False, use_ista=True, use_fista=True, save_history=True)
-    n_iter = 500
-
-    for _ in tqdm(range(n_iter)):
-        comparator.train_iteration()
-
-    comparator.plot_quality_history()
-
-
-    comparator.save_numpy('ista_fista/results_{}_K'.format(K))

### 2018-05-12 theano/experiments/mnist/mnist_100_train_20_layers_K_250_script.py

@@ -1,99 +1,0 @@
-import numpy as np
-import six.moves.cPickle as pickle
-from tqdm import tqdm
-
-from comparator.compare_sequential import SequentialComparator
-from compare_mnist.mnist_data import MnistData
-
-
-class MnistSequentialComparator_DFGHJDF(SequentialComparator):
-    def __init__(self, K, L, learning_rate=0.0001, n_train_sample=1, n_validation_sample=1,
-                 train_freq=True, train_bayes=True, train_shared_bayes=True, save_history=False):
-
-        self.data = MnistData(K=K)
-        self.data.check_download(normalise=False)
-        self.data.learn_dictionary()
-        self.D = self.data.train_data.shape[1]
-
-        super().__init__(self.D, K, L, learning_rate, n_train_sample, n_validation_sample,
-                 train_freq, train_bayes, train_shared_bayes, save_history)
-
-        self.beta_train = self.data.train_data
-        self.y_train = self.data.y_train
-        self.beta_validation = self.data.validation_data
-        self.y_validation = self.data.y_validation
-
-if __name__ == '__main__':
-
-    np.random.seed(1)
-
-    K = 250
-    L = 20
-
-    # batch_size = 5000
-    # validation_size = 100
-
-    saved_comparator_file_name = []#'test_S_convergence.pkl'
-
-
-    if not saved_comparator_file_name:
-        comparator = MnistSequentialComparator_DFGHJDF(K, L, learning_rate=0.0001,
-                                                       train_bayes=False, save_history=True,
-                                                       n_train_sample=100, n_validation_sample=100)
-    else:
-        comparator = pickle.load(open(saved_comparator_file_name, 'rb'))
-
-
-
-
-    n_iter = 500
-
-    for _ in tqdm(range(n_iter)):
-       comparator.train_iteration()
-
-
-    lista_time = comparator.recorders['lista'].time
-    sh_bayes_time = comparator.recorders['shared_bayes'].time
-    lista_nmse = comparator.recorders['lista'].validation_loss
-    lista_f_meas = comparator.recorders['lista'].validation_f_meas
[…]

### 2018-05-12 theano/experiments/mnist/old/collect_results_nonnormalised.py

@@ -1,0 +1,149 @@
+import errno
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+
+class MnistExperimentResultsCollector(object):
+    def __init__(self):
+        self.n_iter = 500
+
+    def collect_all(self, undersampling):
+        self.ista_f_meas_train, self.ista_f_meas_validation, self.ista_loss_train, self.ista_loss_validation = \
+            self.collect_ista_fista('ista_fista/results_{}_K_ista.npz'.format(undersampling))
+        self.fista_f_meas_train, self.fista_f_meas_validation, self.fista_loss_train, self.fista_loss_validation = \
+            self.collect_ista_fista('ista_fista/results_{}_K_fista.npz'.format(undersampling))
+        self.freq_f_meas_train, self.freq_f_meas_validation, self.freq_loss_train, self.freq_loss_validation, \
+        self.sh_bayes_f_meas_train, self.sh_bayes_f_meas_validation, self.sh_bayes_loss_train, self.sh_bayes_loss_validation = \
+            self.collect_main('non_normalised_results/mnist_100_train_20_layers_K_{}'.format(undersampling))
+
+    def collect_ista_fista(self, fileprefix):
+        saved_res = np.load(fileprefix)
+        f_meas_train = saved_res['train_f_meas']
+        f_meas_validation = saved_res['validation_f_meas']
+        loss_train = saved_res['train_loss']
+        loss_validation = saved_res['validation_loss']
+
+        return f_meas_train, f_meas_validation, loss_train, loss_validation
+
+    def collect_main(self, filename_prefix):
+        saved_bayes_weights = np.load('{}_bayes_weights.npz'.format(filename_prefix))
+        bayes_S_M = saved_bayes_weights['bayes_S_M']
+        bayes_S_V = saved_bayes_weights['bayes_S_V']
+        bayes_W_M = saved_bayes_weights['bayes_W_M']
+        bayes_W_V = saved_bayes_weights['bayes_W_V']
+
+        saved_beta_est = np.load('{}_beta_est.npz'.format(filename_prefix))
+        freq_beta_train_est=saved_beta_est['freq_beta_train_est']
+        freq_beta_validation_est=saved_beta_est['freq_beta_validation_est']
+        shared_beta_train_est=saved_beta_est['shared_beta_train_est']
+        shared_beta_validation_est=saved_beta_est['shared_beta_validation_est']
+        true_beta_train=saved_beta_est['true_beta_train']
[…]

### 2018-05-12 theano/experiments/mnist/old/mnist_100_train_20_layers_K_250_ista_fista.py

@@ -1,0 +1,55 @@
+import errno
+import numpy as np
+import six.moves.cPickle as pickle
+
+import matplotlib.pyplot as plt
+from tqdm import tqdm, trange
+
+import os
+
+from compare_freq_bayes.compare_sequential_with_ista_fista import SequentialComparatorIstaFista
+from experiments.synthetic.experiments_parameters import load_long_experiment
+from compare_mnist.mnist_data import MnistData
+
+class MnistSequentialComparatorIstaFista(SequentialComparatorIstaFista):
+    def __init__(self, K, L, learning_rate=0.0001, n_train_sample=1, n_validation_sample=1,
+                 train_freq=False, train_bayes=False, train_shared_bayes=False, use_ista=True, use_fista=True, save_history=False):
+
+        self.data = MnistData(K=K)
+        self.data.check_download(normalise=False)
+        self.data.learn_dictionary()
+        self.D = self.data.train_data.shape[1]
+
+        super().__init__(self.D, K, L, learning_rate, n_train_sample, n_validation_sample,
+                 train_freq, train_bayes, train_shared_bayes, use_ista, use_fista, save_history)
+
+        self.beta_train = self.data.train_data
+        self.y_train = self.data.y_train
+        self.beta_validation = self.data.validation_data
+        self.y_validation = self.data.y_validation
+
+
+if __name__ == '__main__':
+    try:
+        os.makedirs('ista_fista')
+    except OSError as e:
+        if e.errno != errno.EEXIST:
+            raise
+
+    np.random.seed(1)
+
+    K = 250
+    L = 20
+
+    comparator = MnistSequentialComparatorIstaFista(K, L, learning_rate=0.0001, n_train_sample=100,
+                                      n_validation_sample=100, train_freq=False,
+                                      train_bayes=False, train_shared_bayes=False, use_ista=True, use_fista=True, save_history=True)
+    n_iter = 500
+
+    for _ in tqdm(range(n_iter)):
+        comparator.train_iteration()
+
+    comparator.plot_quality_history()
+
+
+    comparator.save_numpy('ista_fista/results_{}_K'.format(K))

### 2018-05-12 theano/experiments/mnist/old/mnist_100_train_20_layers_K_250_script.py

@@ -1,0 +1,99 @@
+import numpy as np
+import six.moves.cPickle as pickle
+from tqdm import tqdm
+
+from comparator.compare_sequential import SequentialComparator
+from compare_mnist.mnist_data import MnistData
+
+
+class MnistSequentialComparator_DFGHJDF(SequentialComparator):
+    def __init__(self, K, L, learning_rate=0.0001, n_train_sample=1, n_validation_sample=1,
+                 train_freq=True, train_bayes=True, train_shared_bayes=True, save_history=False):
+
+        self.data = MnistData(K=K)
+        self.data.check_download(normalise=False)
+        self.data.learn_dictionary()
+        self.D = self.data.train_data.shape[1]
+
+        super().__init__(self.D, K, L, learning_rate, n_train_sample, n_validation_sample,
+                 train_freq, train_bayes, train_shared_bayes, save_history)
+
+        self.beta_train = self.data.train_data
+        self.y_train = self.data.y_train
+        self.beta_validation = self.data.validation_data
+        self.y_validation = self.data.y_validation
+
+if __name__ == '__main__':
+
+    np.random.seed(1)
+
+    K = 250
+    L = 20
+
+    # batch_size = 5000
+    # validation_size = 100
+
+    saved_comparator_file_name = []#'test_S_convergence.pkl'
+
+
+    if not saved_comparator_file_name:
+        comparator = MnistSequentialComparator_DFGHJDF(K, L, learning_rate=0.0001,
+                                                       train_bayes=False, save_history=True,
+                                                       n_train_sample=100, n_validation_sample=100)
+    else:
+        comparator = pickle.load(open(saved_comparator_file_name, 'rb'))
+
+
+
+
+    n_iter = 500
+
+    for _ in tqdm(range(n_iter)):
+       comparator.train_iteration()
+
+
+    lista_time = comparator.recorders['lista'].time
+    sh_bayes_time = comparator.recorders['shared_bayes'].time
+    lista_nmse = comparator.recorders['lista'].validation_loss
+    lista_f_meas = comparator.recorders['lista'].validation_f_meas
[…]

### 2018-05-12 theano/experiments/mnist/old/posterior_plotter.py

@@ -1,0 +1,86 @@
+import numpy as np
+from PBP_net_lista.test_network_layer import random_spike_and_slab
+import matplotlib.pyplot as plt
+import six.moves.cPickle as pickle
+from PBP_net_lista_single_matrices.SingleBayesianListaHandler import SingleBayesianListaHandler
+
+
+class PosteriorPlotter(object):
+
+    def plot_posterior_samples_mnist(self, bayes_lista, y, n_samples):
+        w, m, v = bayes_lista.pbp_instance.predict_probabilistic(y)
+        for sample_num in range(n_samples):
+            beta_est_sample = random_spike_and_slab(m, np.sqrt(v), w)
+            plt.figure()
+            plt.imshow(np.reshape(beta_est_sample, (28, 28)), cmap='gray')
+            plt.axis('off')
+            plt.savefig('posterior_sample_{}.pdf'.format(sample_num), format='pdf', bbox_inches='tight')
+            plt.show()
+
+    def plot_posterior_parameters_mnist(self, bayes_lista, y):
+        w, m, v = bayes_lista.pbp_instance.predict_probabilistic(y)
+
+        plt.figure()
+        plt.imshow(np.reshape(m, (28, 28)))
+        plt.colorbar()
+        plt.axis('off')
+        plt.savefig('posterior_mean.pdf', format='pdf', bbox_inches='tight')
+        plt.show()
+
+        plt.figure()
+        plt.imshow(np.reshape(np.sqrt(v), (28, 28)))
+        plt.colorbar()
+        plt.axis('off')
+        plt.savefig('posterior_std.pdf', format='pdf', bbox_inches='tight')
+        plt.show()
+
+        plt.figure()
+        plt.imshow(np.reshape(w, (28, 28)))
+        plt.colorbar()
+        plt.axis('off')
+        plt.savefig('posterior_spike_indicator.pdf', format='pdf', bbox_inches='tight')
+        plt.show()
+
+    def plot_loss(self, comparator):
+        plt.figure()
+        plt.semilogy(comparator.freq_train_loss, label="freq train loss")
+        #plt.semilogy(comparator.bayesian_train_loss, label="bayes train loss")
+        plt.semilogy(comparator.shared_bayesian_train_loss, label="shared bayes train loss")
+
+        plt.semilogy(comparator.freq_validation_loss, label="freq valid loss")
[…]

### 2018-05-12 theano/experiments/synthetic_overcomplete/experiments_parameters.py

@@ -1,0 +1,10 @@
+def load_long_experiment():
+    D = 100
+    K = 500
+    L = 4
+
+    rseed = 1
+    n_iter = 1000
+    batch_size = 1000
+    validation_size = 100
+    return rseed, D, K, L, batch_size, validation_size, n_iter

### 2018-05-12 theano/experiments/synthetic_overcomplete/lambda/run_long.py

@@ -1,0 +1,101 @@
+import numpy as np
+import six.moves.cPickle as pickle
+
+import matplotlib
+matplotlib.use('TkAgg')
+import matplotlib.pyplot as plt
+from tqdm import tqdm, trange
+import os
+from comparator.compare_sequential import SequentialComparator
+from experiments.synthetic_overcomplete.experiments_parameters import load_long_experiment
+
+rseed, D, K, L, batch_size, validation_size, n_iter = load_long_experiment()
+np.random.seed(rseed)
+lambda_array = [0.001, 0.01, 0.1, 1, 10, 100, 1000]
+
+freq_train_loss = np.zeros((len(lambda_array), n_iter))
+freq_validation_loss = np.zeros((len(lambda_array), n_iter))
+freq_train_f_measure = np.zeros((len(lambda_array), n_iter))
+freq_validation_f_measure = np.zeros((len(lambda_array), n_iter))
+freq_time = np.zeros((len(lambda_array), n_iter))
+
+sh_bayes_train_loss = np.zeros((len(lambda_array), n_iter))
+sh_bayes_validation_loss = np.zeros((len(lambda_array), n_iter))
+sh_bayes_train_f_measure = np.zeros((len(lambda_array), n_iter))
+sh_bayes_validation_f_measure = np.zeros((len(lambda_array), n_iter))
+sh_bayes_time = np.zeros((len(lambda_array), n_iter))
+
+ista_train_loss = np.zeros((len(lambda_array), n_iter))
+ista_validation_loss = np.zeros((len(lambda_array), n_iter))
+ista_train_f_measure = np.zeros((len(lambda_array), n_iter))
+ista_validation_f_measure = np.zeros((len(lambda_array), n_iter))
+
+fista_train_loss = np.zeros((len(lambda_array), n_iter))
+fista_validation_loss = np.zeros((len(lambda_array), n_iter))
+fista_train_f_measure = np.zeros((len(lambda_array), n_iter))
+fista_validation_f_measure = np.zeros((len(lambda_array), n_iter))
+
+for rseed in range(1):
+    np.random.seed(rseed)
+    for i, lam in enumerate(tqdm(lambda_array)):
+        comparator = SequentialComparator(D, K, L, learning_rate=0.0001, n_train_sample=batch_size,
+                                          n_validation_sample=validation_size, train_freq=True, train_bayes=False,
+                                          train_shared_bayes=True, use_ista=True, use_fista=True, save_history=False,
[…]

### 2018-05-12 theano/experiments/synthetic_overcomplete/undersampling/collect_results.py

@@ -1,0 +1,166 @@
+import errno
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+
+class UndersamplingExperimentReultsCollector(object):
+    def __init__(self):
+        self.K_array = [10, 20, 30, 40, 50, 60, 70, 80, 90, 100]
+        self.random_range = 1
+        self.n_iter = 1000
+
+    def collect_all(self):
+        self.ista_f_meas_train, self.ista_f_meas_validation, self.ista_loss_train, self.ista_loss_validation, \
+        self.ista_f_meas_train_std, self.ista_f_meas_validation_std, self.ista_loss_train_std, self.ista_loss_validation_std = \
+            self.collect_main('ista')
+        self.fista_f_meas_train, self.fista_f_meas_validation, self.fista_loss_train, self.fista_loss_validation, \
+        self.fista_f_meas_train_std, self.fista_f_meas_validation_std, self.fista_loss_train_std, self.fista_loss_validation_std, = \
+            self.collect_main('fista')
+        self.freq_f_meas_train, self.freq_f_meas_validation, self.freq_loss_train, self.freq_loss_validation, \
+        self.freq_f_meas_train_std, self.freq_f_meas_validation_std, self.freq_loss_train_std, self.freq_loss_validation_std = \
+            self.collect_main('freq')
+        self.sh_bayes_f_meas_train, self.sh_bayes_f_meas_validation, self.sh_bayes_loss_train, self.sh_bayes_loss_validation,\
+        self.sh_bayes_f_meas_train_std, self.sh_bayes_f_meas_validation_std, self.sh_bayes_loss_train_std, self.sh_bayes_loss_validation_std = \
+            self.collect_main('sh_bayes')
+
+
+    def collect_main(self, alg_name):
+        f_meas_train = np.zeros((self.random_range, len(self.K_array), self.n_iter))
+        f_meas_validation = np.zeros((self.random_range, len(self.K_array), self.n_iter))
+        loss_train = np.zeros((self.random_range, len(self.K_array), self.n_iter))
+        loss_validation = np.zeros((self.random_range, len(self.K_array), self.n_iter))
+
+        for i in range(self.random_range):
+            saved_res = np.load('{}/undersampling_measures.npz'.format(i))
+            loss_train[i] = saved_res['{}_train_loss'.format(alg_name)]
[…]

### 2018-05-12 theano/experiments/synthetic_overcomplete/undersampling/run_long.py

@@ -1,0 +1,100 @@
+import numpy as np
+import six.moves.cPickle as pickle
+
+import matplotlib
+matplotlib.use('TkAgg')
+import matplotlib.pyplot as plt
+from tqdm import tqdm, trange
+import os
+from comparator.compare_sequential import SequentialComparator
+from experiments.synthetic_overcomplete.experiments_parameters import load_long_experiment
+
+rseed, D, _, L, batch_size, validation_size, n_iter = load_long_experiment()
+np.random.seed(rseed)
+K_array = [10, 20, 30, 40, 50, 60, 70, 80, 90, 100]
+
+freq_train_loss = np.zeros((len(K_array), n_iter))
+freq_validation_loss = np.zeros((len(K_array), n_iter))
+freq_train_f_measure = np.zeros((len(K_array), n_iter))
+freq_validation_f_measure = np.zeros((len(K_array), n_iter))
+freq_time = np.zeros((len(K_array), n_iter))
+
+sh_bayes_train_loss = np.zeros((len(K_array), n_iter))
+sh_bayes_validation_loss = np.zeros((len(K_array), n_iter))
+sh_bayes_train_f_measure = np.zeros((len(K_array), n_iter))
+sh_bayes_validation_f_measure = np.zeros((len(K_array), n_iter))
+sh_bayes_time = np.zeros((len(K_array), n_iter))
+
+ista_train_loss = np.zeros((len(K_array), n_iter))
+ista_validation_loss = np.zeros((len(K_array), n_iter))
+ista_train_f_measure = np.zeros((len(K_array), n_iter))
+ista_validation_f_measure = np.zeros((len(K_array), n_iter))
+
+fista_train_loss = np.zeros((len(K_array), n_iter))
+fista_validation_loss = np.zeros((len(K_array), n_iter))
+fista_train_f_measure = np.zeros((len(K_array), n_iter))
+fista_validation_f_measure = np.zeros((len(K_array), n_iter))
+
+for rseed in range(1):
+    np.random.seed(rseed)
+    for i, K in enumerate(tqdm(K_array)):
+        comparator = SequentialComparator(D, K, L, learning_rate=0.0001, n_train_sample=batch_size,
+                                          n_validation_sample=validation_size, train_freq=True, train_bayes=False,
+                                          train_shared_bayes=True, use_ista=True, use_fista=True, save_history=False)
+        for _ in trange(n_iter):
+            comparator.train_iteration()
+
[…]

### 2018-05-12 paper/BayesianLISTA.tex

--- 2018-03-10 paper/BayesianLISTA.tex
@@
 \usepackage{hyperref}
+\usepackage{xcolor}
 
@@
 
-Based on the results of Lemma~\ref{thm:soft_thresholding} we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ from (\ref{eq:thr_first}) with a spike and slab distribution with parameters derived in the lemma: spike probability $\omega$ is equal to $\omega^*$, slab mean $m$ and variance $v$ are set to the corresponding parameters of the truncated Gaussian $m^*$ and $v^*$.
+Based on the results of Lemma~\ref{thm:soft_thresholding} we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ from (\ref{eq:thr_first}) with a spike and slab distribution with parameters derived in the lemma: the spike probability $\omega$ is equal to $\omega^*$, the slab mean $m$ and variance $v$ are set to the corresponding parameters of the truncated Gaussian $m^*$ and $v^*$.
 
@@
 \end{flalign*}
-where $\mathbb{E}\widehat{\beta}_{d'}$, $\operatorname{Var}\widehat{\beta}_{d'}$ are computed according to lemma~\ref{thm:moments_spsl}.
+where $\mathbb{E}\widehat{\beta}_{d'}$ and $\operatorname{Var}\widehat{\beta}_{d'}$ are computed according to Lemma~\ref{thm:moments_spsl}.
  \end{proof}
 
-Let $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista}.
+{\color{red} Let $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista}}.
 We assume that $\mathbf{S}$ and $\widehat{\boldsymbol\beta}_{l-1}$ are mutually independent.
@@
 
+\begin{figure}[!t]
+\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
+%\label{fig:d_testing}
+\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
+\caption{Approximations of the Bayesian \textsc{lista}}
+%\label{fig:z_new_testing}
+\end{figure}
+
 \subsection{\uppercase{Bayesian lista forward propagation}}
@@
 \begin{enumerate}
-	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:matrix_const};
-	\item $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is approximated with the Gaussian distribution, which parameters are computed according to lemma \ref{thm:matrix_vector};
-	\item $\mathbf{c} = \mathbf{b} + \mathbf{e}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:sum_vectors};
-	\item $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c})$ is approximated with the spike and slab distribution, which parameters are computed according to lemma \ref{thm:soft_thresholding}.
+	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is the Gaussian distribution with parameters computed according to Lemma \ref{thm:matrix_const};
+	\item $\widehat{\boldsymbol\beta}_{0} = h_\lambda(\mathbf{b})$ is approximated with the spike and slab distribution, which parameters are computed according to Lemma \ref{thm:soft_thresholding}.
+	\item $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is approximated with the Gaussian distribution, which parameters are computed according to Lemma \ref{thm:matrix_vector};
+	\item $\mathbf{c}_l = \mathbf{b} + \mathbf{e}_l$ is the Gaussian distribution with parameters computed according to Lemma \ref{thm:sum_vectors};
+	\item $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$ is approximated with the spike and slab distribution, which parameters are computed according to Lemma \ref{thm:soft_thresholding}.
 \end{enumerate}
@@
 We have used two approximations in forward propagation of uncertainty.
-First, in lemma \ref{thm:matrix_vector} a Gaussian matrix is multiplied by a spike and slab vector and their product is approximated with the Gaussian distribution.
-Second, in lemma \ref{thm:soft_thresholding} the result of soft thresholding of a Gaussian vector is approximated with the spike and slab distribution.
+First, {\color{red} in Lemma \ref{thm:matrix_vector}} a Gaussian matrix is multiplied by a spike and slab vector and their product is approximated with the Gaussian distribution.
+Second, {\color{red} in Lemma \ref{thm:soft_thresholding}} the result of soft thresholding of a Gaussian vector is approximated with the spike and slab distribution.
 In this section we demonstrate that these approximations are close to the real distributions.
 
-Figure \ref{fig:d_testing} demonstrates the comparison of the sampled distribution and approximated distribution for lemma \ref{thm:matrix_vector}.
-For sampled distribution, $10000$ values were sampled from the Gaussian matrix and the spike and slab vector and their product is computed, then one of the dimensionalities is plotted.
-The approximated distribution is computed according to lemma \ref{thm:matrix_vector}.
+Figure \ref{fig:d_testing} demonstrates the comparison of the sampled distribution and approximated distribution for Lemma \ref{thm:matrix_vector}.
+For the sampled distribution, $10000$ values are sampled from the Gaussian matrix and the spike and slab vector and their product is computed, then one of the dimensionalities is plotted.
+The approximated distribution is computed according to Lemma \ref{thm:matrix_vector}.
 
-Figure \ref{fig:z_new_testing} demonstrates the comparison of the sampled distribution and approximated distribution for lemma \ref{thm:soft_thresholding}.
-For sampled distribution, $10000$ values are sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities is plotted.
-The approximated distribution is computed according to lemma \ref{thm:soft_thresholding}.
+Figure \ref{fig:z_new_testing} demonstrates the comparison of the sampled distribution and approximated distribution for Lemma \ref{thm:soft_thresholding}.
+For the sampled distribution, $10000$ values are sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities is plotted.
+The approximated distribution is computed according to Lemma \ref{thm:soft_thresholding}.
 
@@
 
-\begin{figure}[t]
-\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
-%\label{fig:d_testing}
-\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
-\caption{Approximations of Bayesian \textsc{lista}}
-%\label{fig:z_new_testing}
-\end{figure}
-
 \section{\uppercase{Backpropagation}}
@@
 For Bayesian inference we expand the probabilistic backpropagation algorithm~\citep{hernandez2015probabilistic} for computing parameter updates.
-It is based on assumed density filtering (ADF) and expectation propagation (EP) and allows to update parameters of the distributions based on the derivative of the logarithm of a normalisation constant.
+It is based on assumed density filtering (ADF) and expectation propagation (EP) and allows to update parameters of the distributions based on the derivatives of the logarithm of a normalisation constant.
 ADF iteratively incorporates factors from the true posterior $p$ (\ref{eq:posterior}) into the factorised approximating distribution $q$ (\ref{eq:approximating_dsitribution}), whereas in EP factors in the $q$ are iteratively replaced by factors from $p$.
 
-When a factor $p$ is incorporated into $q$, $q$ as a function of Gaussian-distributed weights $W$  and $S$ has the following form:
+When a factor from $p$ is incorporated into $q$, $q$ as a function of Gaussian-distributed weights $\mathbf{W}$ and $\mathbf{S}$ has the following form:
 \begin{equation}
@@
 \end{equation}
-where $Z$ is the normalisation constant and $f(a)$ - arbitrary function, $a \in \{w_{dk}, s_{d'd''}; \forall d, k, d', d''\}$.
+where $Z$ is the normalisation constant and $f(a)$ is an arbitrary function, $a \in \{w_{dk}, s_{d'd''}; \forall d, k, d', d''\}$.
 
-According to \cite{minka2001thesis}, new parameters of Gaussian distribution for $a$ can be computed as
+According to \cite{minka2001thesis}, new parameters of the Gaussian distribution for $a$ can be computed as
 \begin{align}
@@
 
-Then to find new values of $W$, $S$ we need to compute derivatives of the logarithm of $Z$ when the factor of the true posterior is incorporated in $q$.
+Then to find new values of $\mathbf{W}$ and $\mathbf{S}$ we need to compute derivatives of the logarithm of $Z$ when the factor of the true posterior is incorporated in $q$.
 
@@
 \end{align}
-We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximated with the spike and slab distribution with parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}_L}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}_L}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}_L}$
+We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximated with the spike and slab distribution with the parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}_L}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}_L}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}_L}$
 \begin{align}
@@
 \textsc{fista} adds the momentum to \textsc{ista} and improves its convergence speed.
-We set the number of iterations in these algorithms and the number of layers in Bayesian and classical \textsc{lista} networks to $L$.
-To measure the performance of the algorithms the normalised mean square error(\textsc{nmse}) and F measure are used.
+We set the number of iterations in these algorithms and the number of layers in the Bayesian and classical \textsc{lista} networks to $L$.
+To measure the performance of the algorithms the normalised mean square error (\textsc{nmse}) and F measure are used.
 \textsc{nmse} for a batch of data $\{\boldsymbol\beta^{(n)}\}_{n=1}^{N}$ and estimates $\{\widehat{\boldsymbol\beta}^{(n)}\}_{n=1}^{N}$ is computed as
@@
 \begin{equation}
-\text{F measure} = 2\dfrac{\text{precision}\cdot\text{recall}}{\text{precision} + \text{recall}}
+\text{F measure} = 2\dfrac{\text{precision}\cdot\text{recall}}{\text{precision} + \text{recall}},
 \end{equation}
 where precision is the fraction of estimated slab locations that are correct, recall is the fraction of true slab locations among all predicted slab locations.
-We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn.
+We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for the \textsc{lista} to learn.
 
@@
 We generate $N_\text{train}=500$ sparse coefficients vectors $\boldsymbol\beta^{(n)}$ each of size $D = 100$.
-Coefficients $\boldsymbol\beta^{(n)}$ are generated from the spike and slab distribution with truncated slab: each component of $[\beta^{(n)}]_{d}$ is zero with the probability $0.8$ or is from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability $0.2$.
+Coefficients $\boldsymbol\beta^{(n)}$ are generated from the spike and slab distribution with truncated slab: each component $[\beta^{(n)}]_{d}$ is zero with the probability $0.8$ or is from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability $0.2$.
 To simulate sparse observations, we generate the random Gaussian design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$.
-The observations are generated according to (\ref{eq:regression_problem}) with zero-mean Gaussian noise with standard deviation $0.5$.
+The observations are generated according to (\ref{eq:regression_problem}) with the zero-mean Gaussian noise with the standard deviation $0.5$.
 The shrinkage parameter is set to~$\lambda = 0.1$.
@@
 
-Overall, the experiments on synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
+Overall, the experiments on the synthetic data demonstrate that the Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
 
@@
 The experiment with $K=100$ presents severe conditions for the algorithms: the very limited size of the training dataset combined with the small dimensionality of observations.
-The Bayesian \textsc{lista} is able to learn under these conditions, outperforming \textsc{lista} that demonstrates poor results.
+The Bayesian \textsc{lista} is able to learn under these conditions, outperforming the \textsc{lista} that demonstrates poor results.
 Under better conditions of the second experiment with $K=250$ both \textsc{lista} networks converge to the similar results.
@@
 \subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_f_measure_valid}}
-\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with dictionary size $K = 100$}
+\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the dictionary size $K = 100$}
 \label{fig:mnist_100}
@@
 \subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_f_measure_valid}}
-\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with dictionary size $K = 250$}
+\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the dictionary size $K = 250$}
 \label{fig:mnist_250}
@@
 \subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.33\columnwidth]{posterior_spike_indicator}}
-\caption{Posterior parameters for an image of digit 7.}
+\caption{Posterior parameters for an image of the digit 7.}
 \label{fig:posterior_distribution}
@@
 \subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_2}}
-\caption{Samples from the posterior for an image of digit 7.}
+\caption{Samples from the posterior for an image of the digit 7.}
 \label{fig:posterior_samples}
@@
 The active learning area researches ways to select new training subsets to reduce the total number of required supervision.
-One of the popular approaches in active learning is uncertainty sampling when the data with the least certain predictions is chosen to obtain a new label for.
+One of the popular approaches in active learning is uncertainty sampling when the data with the least certain predictions is chosen to obtain a new label at.
 Uncertainty is usually measured with entropy.
 In our case of the spike and slab distributed data points there is no closed form for entropy.
-Therefore, we use variance from Lemma~\ref{thm:moments_spsl} as a measure of uncertainty.
+Therefore, we use a variance from Lemma~\ref{thm:moments_spsl} as a measure of uncertainty.
 
-The data in this example is the same \textsc{mnist} dataset with learnt dictionary of size $K=100$.
-We use the train data of size $50$, the pool data of size $500$,  and the test data of size $100$.
-The algorithm learns on the train data for $50$ iterations and it is evaluated on the test data.
+The data in this example is the same \textsc{mnist} dataset with the learnt dictionary of size $K=100$.
+We use the training data of size $50$, the pool data of size $500$,  and the test data of size $100$.
+The algorithm learns on the training data for $50$ iterations and it is evaluated on the test data.
 To actively collect a next data point from the pool, the algorithm is used to predict a point with the highest uncertainty.
-The selected point is moved from the pool to the train data and the algorithm performs additional $10$ iterations on the updated train data.
+The selected point is moved from the pool to the training data and the algorithm performs additional $10$ iterations on the updated training data.
 Overall, $10$ pool additions are performed.
@@
 
-We compare actively updated approach of adding new points from the pool with the random approach that picks a new data point from the pool at random.
+We compare the actively updated approach of adding new points from the pool with the random approach that picks a new data point from the pool at random.
 The overall procedure is repeated for $20$ times with new randomly selected initial datasets.
@@
 The active approach with uncertainty sampling steadily demonstrates better results in terms of both quality measures.
-This means that the posterior distribution learnt by the Bayesian \textsc{lista} is adequately estimated.
+This means that the posterior distribution learnt by the Bayesian \textsc{lista} is an adequate estimate of the true posterior.
 \begin{figure}[t]
@@
 \label{sec:discussion}
-To the best of our knowledge, this is the first implementation of Bayesian deep sparse coding algorithm.
-Although there are works on Bayesian sparsity in context of neural networks \citep{he2017bayesian}, they are not the Bayesian neural networks in the same sense as Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
+To the best of our knowledge, this is the first implementation of a Bayesian deep sparse coding algorithm.
+Although there are works on Bayesian sparsity in context of neural networks \citep{he2017bayesian}, they are not the Bayesian neural networks in the same sense as the Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
 We find not only correct predictions but also useful posterior estimates for the predictions that show how the model is confident in its decisions.
@@
 We also show that when the training data is very small the proposed algorithm significantly outperforms the classical \textsc{lista} in terms of predictive accuracy.
-Experiments on active learning demonstrate that the proposed Bayesian \textsc{lista} gives accurate posterior estimates that can be used for selection of a next data point where a label should be obtain for.
+Experiments on active learning demonstrate that the proposed Bayesian \textsc{lista} gives accurate posterior estimates that can be used for selection of a next data point where a label should be obtain at.
 

### 2018-05-12 review_uai_2018/response_to_reviews.tex

@@
 \usepackage{color}
+\usepackage{mathtools}
 \begin{document}
@@
 \section*{Reviewer 1}
-\begin{quote}
-\textit{It's not so surprising that probabilistic versions of ISTA should do better in the limited dictionary case.
-What I'm curious about is how fast the proposed algorithm is, not in terms of iterations, but wall clock time.}
-\end{quote}
-\textcolor{blue}{We'll check the clock time.}
+Thank you for the helpful suggestions.
 
-\begin{quote}
-\textit{Please enlarge the figures, as they are very hard to read.}
-\end{quote}
-We will enlarge the figures and move some of the proofs from section 4 to appendix to get space for figures.
+Q: It's not so surprising that probabilistic versions of ISTA should do better in the limited dictionary case.
+What I'm curious about is how fast the proposed algorithm is, not in terms of iterations, but wall clock time.
 
-% \begin{quote}
-% \textit{\ldots light experimental results \ldots}
-% \end{quote}
-% We can try to add heavier experiments, but time is limited by one week.
+A: We will add the wall clock time comparison.
+Preliminary results show that LISTA and Bayesian LISTA require the same running time to achieve similar accuracy.
+One iteration of Bayesian LISTA takes more time, but the convergence rate is also higher for Bayesian LISTA.
+\newline
+\newline
 
-\begin{quote}
-\textit{What's the intuitive reason for baseline ISTA/FISTA to have better performance in the synthetic data case?}
-\end{quote}
-\textcolor{blue}{We'll think about it. May be because of priors.}
+Q: Please enlarge the figures, as they are very hard to read.
 
-\begin{quote}
-\textit{What is the expected difference between Bayesian and non-Bayesian as the number of layers increases (ie, you expect the gap to close, stay the same, etc.)?}
-\end{quote}
-\textcolor{blue}{It's related with previous question. We'll think how to answer it. Really, we don't know. But maybe gap will reduce as prior will influence less?}
+A: We will enlarge the figures and move some of the proofs from section 4 to appendix to get space for figures.
+\newline
+\newline
 
-\begin{quote}
-\textit{Do you expect it to be possible to replace the soft thresholding with some other nonlinearity and to produce a similar algorithms?
-This isn't something I expect to be done easily, but do you expect it to be feasible, or is the combination of soft threshold with the spike/slab distribution critical?}
-\end{quote}
-Soft-thresholding nonlinearity seems to be the most popular as it is optimal in some sense [1].
-There are several nonlinearities that are used in sparse coding, for example some of them are described in sec.
+Q: What's the intuitive reason for baseline ISTA/FISTA to have better performance in the synthetic data case?
+
+A: We believe this is because there is not enough data for LISTA and Bayesian LISTA to learn the matrices.
+\newline
+\newline
+
+Q: What is the expected difference between Bayesian and non-Bayesian as the number of layers increases (ie, you expect the gap to close, stay the same, etc.)?
+
+A: Based on the current results, we expect the gap to stay the same, we will add experiments with more layers.
+\newline
+\newline
+
+Q: Do you expect it to be possible to replace the soft thresholding with some other nonlinearity and to produce a similar algorithms?
+This isn't something I expect to be done easily, but do you expect it to be feasible, or is the combination of soft threshold with the spike/slab distribution critical?
+
+A: In sparse coding the soft-thresholding nonlinearity is the most popular as it is used in the optimal solution of the lasso method [1].
+There are several other nonlinearities that are used in sparse coding, for example some of them are described in sec.
 IV-B of [2].
@@
 
-The main motivation of the spike and slab distribution is to get sparse approximations, that is critical for sparse coding.
-There is an alternative Bernoulli-Gaussian distribution, that leads to similar results.
-There is no intuition or motivation to use these distributions for networks with dense data.
+The main motivation of using the spike and slab distribution is to obtain approximations of the sparse unknown vector $\beta$, that is critical for sparse coding.
+There is no intuition or motivation to use these distributions for networks with dense output.
 
-[1] Tibshirani, R. (1996). Regression shrinkage and selection via the lasso. Journal of the Royal Statistical Society, 267-288.
-[2] Borgerding, M., Schniter, P., Rangan, S. (2017). AMP-Inspired Deep Networks for Sparse Linear Inverse Problems. IEEE Transactions on Signal Processing, 65(16), 4293-4308.
+[1] Tibshirani, R. (1996). Regression shrinkage and selection via the lasso. Journal of the Royal Statistical Society.
+
+[2] Borgerding, M., Schniter, P., Rangan, S. (2017). AMP-Inspired Deep Networks for Sparse Linear Inverse Problems. IEEE Transactions on Signal Processing.
 
 \section*{Reviewer 2}
-\begin{quote}
-\textit{It's not clear that a machine learning venue is appropriate.}
-\end{quote}
-We understand that the topic of deep sparse coding may indeed lay on the border between signal processing and machine learning.
-But there were recent papers in the area of deep sparse coding published in machine learning community, we'll list some of them below.
-And we believe that as our method allows to estimate the uncertainty of the deep sparse coding algorithms, it suits the UAI conference.
+Thank you for the helpful suggestions.
 
-In [1] the original LISTA paper is used as an example of unsupervised learning in deep learning.
-In [2] it is used for image super-resolution.
-In [3] general improvements to original paper are proposed.
-Other deep sparse coding and sparse models in general are of recent interest in ML community [4], [5].
+Q: It's not clear that a machine learning venue is appropriate.
+...
+I found the writing unclear and confusing, as the authors switch back and forth between a neural network interpretation of LISTA, and the standard sparse coding interpretation.
+I imagine both interpretations would be standard for e.g.
+a signal processing audience?
 
-[1] LeCun, Y., Bengio, Y., Hinton, G. (2015). Deep learning. Nature.
-[2] Wang, Z., Liu, D., Yang, J., Han, W., Huang, T. (2015). Deep networks for image super-resolution with sparse prior. ICCV.
-[3] Sprechmann, P., Bronstein, A. M., Sapiro, G. (2015). Learning efficient sparse and low rank models. TPAMI.
+A: We thank the reviewer for raising this important question.
+Indeed, the field of sparse coding is on the border between signal processing and machine learning.
+Recently different works on deep sparse coding have been of interest in the machine learning community [1] -- [5].
+
+We believe since our method allows to estimate the uncertainty of the deep sparse coding algorithms, it suits the UAI conference.
+
+[1] Wang, Z., Liu, D., Yang, J., Han, W., Huang, T. (2015). Deep networks for image super-resolution with sparse prior. ICCV.
+
+[2] Sprechmann, P., Bronstein, A. M., Sapiro, G. (2015). Learning efficient sparse and low rank models. TPAMI.
+
+[3] Moreau, T., Bruna, J. (2017). Understanding Trainable Sparse Coding via Matrix Factorization. ICLR.
+
 [4] Papyan, V., Romano, Y., Elad, M. (2017). Convolutional neural networks analyzed via convolutional sparse coding. JMLR.
+
 [5] He, H., Xin, B., Ikehata, S., Wipf, D. (2017). From Bayesian Sparsity to Gated Recurrent Nets. NIPS.
+\newline
+\newline
 
-\begin{quote}
-\textit{I found the writing unclear and confusing, as the authors switch back and forth between a neural network interpretation of LISTA, and the standard sparse coding interpretation.
-I imagine both interpretations would be standard for e.g.
-a signal processing audience?}
-\end{quote}
-\textcolor{blue}{I don't fully understand. I don't think we can do anything with this point in the reply.}
-
-\begin{quote}
-\textit{I am unclear on how one can compute NMSE/F-measure for MNIST in figure 5/8, unless the ground truth sparsity is known i.e.
+Q: I am unclear on how one can compute NMSE/F-measure for MNIST in figure 5/8, unless the ground truth sparsity is known i.e.
 if this is not real data.
 Is the experiment composed of real data and synthetic weights?
-While the focus is on estimation, for real data, would be useful to see prediction results (again, I am assuming ground truth is not known).}
-\end{quote}
-\textcolor{blue}{We need to explain again the setup of the experiments, that we know ground truth. Predictive performance is evaluated.}
+While the focus is on estimation, for real data, would be useful to see prediction results (again, I am assuming ground truth is not known).
 
-\begin{quote}
-\textit{There are some unnecessary propositions e.g. Proposition 1/4, which refer to textbook results. Perhaps a simple citation is enough to save some space?}
-\end{quote}
-\textcolor{blue}{I don't think we can do anything with this point in the reply.} We'll move proofs to appendix.
+A: For MNIST we simulate sparse measurements $y$, therefore we know the ground truth for sparse $\beta$. Sections 6.1 and 6.2 are devoted to experiments on predictive performance.
+\newline
+\newline
+
+Q: There are some unnecessary propositions e.g. Proposition 1/4, which refer to textbook results. Perhaps a simple citation is enough to save some space?
+
+A: We will move proofs to the appendix.
 
 \section*{Reviewer 3}
-\begin{quote}
-\textit{What qualifies equation (11) to be a likelihood distribution?}
-\end{quote}
-\textcolor{blue}{This is an awkwardly formulated question.
-Maybe the question is why do we have this Gaussian noise model.
-We can say something that this is now normally people are introducing the Bayesian models.
-Give example of Probabilistic Backpropagation.}
+Thank you for the helpful suggestions.
 
-\begin{quote}
-\textit{The uncertainty propagation in section 4 refers to a distribution over $\beta$.
+Q: What qualifies equation (11) to be a likelihood distribution?
+
+A: We assume that $\beta$, which are available for the training dataset, are outputs of the neural net corrupted by the additive Gaussian-distributed noise. Therefore, (11) is the Gaussian likelihood.
+\newline
+\newline
+
+Q: The uncertainty propagation in section 4 refers to a distribution over $\beta$.
 Which distribution are the authors referring to?
 Conditioned upon $Y,W,S,\gamma,\lambda$ as in (13)?
-Related: perhaps the method is better explained as a variational approximation on $p(B,W,S,\gamma,\lambda|Y)$?}
-\end{quote}
-Section 4 refers to distribution over $\widehat{\beta}$, which is the output of each layer of the neural network and ultimately the output of the whole network, which is denoted as $f(y; W, S, \lambda)$ in eq.
+Related: perhaps the method is better explained as a variational approximation on $p(B,W,S,\gamma,\lambda|Y)$?
+
+A: Section 4 refers to distribution over $\widehat{\beta}$, which is the output of each layer of the neural network and ultimately the output of the whole network, which is denoted as $f(y; W, S, \lambda)$ in eq.
 (11).
@@
 
-Yes, the distribution over $\widehat{\beta}$ is conditioned on $Y, W, S, \lambda$, but it is not conditioned on $\gamma$ as this is the noise variable that relates $\beta$, which we have during the training as a target and $\widehat{\beta}$, which is the output of the neural network.
+Yes, the distribution over $\widehat{\beta}$ is conditioned on $Y, W, S, \lambda$, but it is not conditioned on $\gamma$ as this is the precision of the noise that relates $\beta$, which we have during training as a target, and $\widehat{\beta}$, which is the output of the neural network.
 
-The proposed inference is a variational approximation of the true posterior in the context of expectation propagation and ADF frameworks.
+The proposed inference is a variational approximation of the true posterior in the context of EP and ADF frameworks.
+\newline
+\newline
 
-\begin{quote}
-\textit{The exact meaning of “Then we generate observations as $y = X \beta$, where $\beta$ are images converted to vectors.”(Section 6.2) is not quite clear.
+Q: The exact meaning of “Then we generate observations as $y = X \beta$, where $\beta$ are images converted to vectors.”(Section 6.2) is not quite clear.
 Are the $\beta$ now flattened images, or the same sparse representations?
-Which dimensionality do they have?}
-\end{quote}
-Each beta is a flattened image of size $(784 \times 1)$
+Which dimensionality do they have?
 
-\begin{quote}
-\textit{Why do the authors restrict themselves to so few training and validation images (100 each)?}
-\end{quote}
-Bayesian models in general show themselves espesially useful when dealing with limited data, when the frequentist counterparts may suffer from inadequate maximum likelihood estimates.
-Therefore, we were particurlarly interested in study on limited data, where the frequentist LISTA might have lower accuracy, to better show how Bayesian LISTA may provide benefits over the frequentist LISTA.
-We expected the frequentist LISTA to have very good results when there is a lot of data, which has been shown in the original paper and extensions.
+A: Yes, each beta is a flattened image of size $(784 \times 1)$
+\newline
+\newline
 
-We appreciate that it would be useful to have also confirmation that on larger datasets both LISTAs show competitive results.
-We will add the experiments on larger datasets in the revised version of the paper if it is accepted.
+Q: Why do the authors restrict themselves to so few training and validation images (100 each)?
 
-\begin{quote}
-\textit{Why is $\lambda$ fixed to 0.1?}
-\end{quote}
-\textcolor{blue}{We are running experiments with this}
-It was epmirically set. This value looks reasonable, since we use normalised data. As we mention in the paper the type II maximum likelihood can be used to find this value.
+A: Bayesian models in general show themselves especially useful dealing with limited data, when the frequentist counterparts may suffer from inadequate maximum likelihood estimates.
+Therefore, we were particularly interested in study on limited data, where the frequentist LISTA might have lower accuracy, to better show how Bayesian LISTA may provide benefits over the frequentist LISTA.
+We expect the frequentist LISTA to have very good results when there is a lot of data, which has been shown in the original paper and extensions.
 
-\begin{quote}
-\textit{In the Discussion, the use with overcomplete dictionaries is mentioned as possible but no reasoning is given as to why undercomplete dictionaries were used and why they deviated from the method of the original paper.}
-\end{quote}
-Both overcomplete and undercomplete cases represent very important problems that conveniently can be solved with the same methods.
+We appreciate that it would be useful to have also confirmation that on larger datasets the frequentist and Bayesian LISTA show competitive results. We will add the experiments on larger datasets.
+\newline
+\newline
+
+Q: Why is $\lambda$ fixed to 0.1?
+
+A: It was empirically set based on grid search. This value looks reasonable, since we use normalised data. As we mention in the paper the type II maximum likelihood can be used to find this value.
+\newline
+\newline
+
+Q: In the Discussion, the use with overcomplete dictionaries is mentioned as possible but no reasoning is given as to why undercomplete dictionaries were used and why they deviated from the method of the original paper.
+
+A: Both overcomplete and undercomplete cases represent very important problems that conveniently can be solved with the same methods.
 In our previous work we dealt with undercomplete dictionaries and therefore we had the experiments with undercomplete dictionaries.
-Due to the space limit we couldn't include experiments for both cases.
+Due to the space limit we could not include experiments for both cases.
+\newline
+\newline
 
-\begin{quote}
-\textit{Furthermore, the Figures are very small to a point where they are illegible on a DIN A4 printout.
-If some of the proofs and calculations were moved to an Appendix, there would be room for readable Figures and more explanations in Sections 3 and 6.}
-\end{quote}
-We'll move some proofs to the appendix and enlarge the figures.
+Q: The paper contains a number of grammatical errors and typos
 
-% \section*{ToDo List}
-% \begin{enumerate}
-%   \item Enlarge the figures.
-%   \item Check motivation of LISTA in ML.
-%   \item Check reviwer 3 without lambda
-%   \item Check the clock time.
-%   \item Explain why baseline ISTA/FISTA is better in the synthetic data case.
-%   \item Think about the gap in performance when number of layers increases.
-%   \item Think if the method is expandable for different nonlinearities and distributions.
-%   \item Think about prediction results on real data as in review 2.
-%   \item Check reviewer 3 lambda.
-%   \item Consider heavier experiments.
-%   \item Think about different interpretations of lista as it waas uncelar in review 2.
-% \end{enumerate}
+A: Thank you for pointing this. We will check and correct them.
+\newline
+\newline
+
+Q: Furthermore, the Figures are very small to a point where they are illegible on a DIN A4 printout.
+If some of the proofs and calculations were moved to an Appendix, there would be room for readable Figures and more explanations in Sections 3 and 6.
+
+A: We will move some proofs to the appendix and enlarge the figures.
 

### 2018-05-13 paper/BayesianLISTA.tex
paper "finished" reading for seeking grammatical mistakes

@@
 
-In general, when distributions are included in a network, Bayesian inference complexity scales exponentially with the number of layers.
+In general, when distributions are included in a network, the complexity of Bayesian inference scales exponentially with the number of layers.
 Thus, it is infeasible to apply conventional Bayesian inference algorithms for deep neural networks.
 Nevertheless, recently several techniques have been proposed to handle specific types of neural networks.
-For example, feed-forward networks with rectified linear units nonlinearity~\citep{hernandez2015probabilistic}, networks with discrete distributions~\citep{soudry2014expectation}, recurrent networks~\citep{mcdermott2017bayesian}.
+For example, feed-forward networks with the rectified linear unit nonlinearity~\citep{hernandez2015probabilistic}, networks with discrete distributions~\citep{soudry2014expectation}, recurrent networks~\citep{mcdermott2017bayesian}.
 
@@
 
-Neural networks address the sparse coding problem with the soft thresholding nonlinearity, that shifts current estimates towards zero \citep{gregor2010learning}.
+Neural networks address the sparse coding problem with the soft thresholding nonlinearity that shifts current estimates towards zero \citep{gregor2010learning}.
 In this paper we propose a method to propagate uncertainty through the soft thresholding nonlinearity.
@@
 We show that it can be effectively combined with Gaussian weights of dense layers.
-The distribution of the target vector propagated through a dense layer and soft thresholding nonlinearity can then be closely approximated with a distribution from the same family.
+The distribution of the target vector propagated through a dense layer and the soft thresholding nonlinearity can then be closely approximated with a distribution from the same family.
 
-The proposed method of uncertainty propagation for the soft thresholding nonlinearity allows us to derive the gradients of the logarithms of normalisation constants, which can be used to update weights distribution.
+The proposed method of uncertainty propagation for the soft thresholding nonlinearity allows us to derive the gradients of the logarithms of normalisation constants, which can be used to update a weight distribution.
 We then develop a highly efficient Bayesian inference algorithm based on the probabilistic backpropagation paradigm while significantly expanding it.
@@
 \item for the first time we propose a method for uncertainty propagation through the soft thresholding nonlinearity for a Bayesian neural network;
-\item we develop efficient posterior inference for weights and outputs of neural networks with the soft thresholding nonlinearity;
+\item we develop an efficient posterior inference algorithm for weights and outputs of neural networks with the soft thresholding nonlinearity;
 \item we design a novel Bayesian neural network for sparse coding.
@@
 \end{equation}
-where $\mathbf{y} \in \mathbb{R}^K$ is the observation, $\mathbf{X} \in \mathbb{R}^{K \times D}$ is the design matrix, $\boldsymbol\beta \in \mathbb{R}^D$ is the unknown vector of weight with many elements $\beta_d$ equal to zero.
-$\varepsilon \in \mathbb{R}^K$ is the independent Gaussian noise.
+where $\mathbf{y} \in \mathbb{R}^K$ is the observation, $\mathbf{X} \in \mathbb{R}^{K \times D}$ is the design matrix, $\boldsymbol\beta \in \mathbb{R}^D$ is the unknown vector of weights with many elements $\beta_d$ equal to zero, $\varepsilon \in \mathbb{R}^K$ is the independent Gaussian noise.
 
-One of the popular families of the sparse coding algorithms is the iterative shrinkage algorithms, and notably the Iterative Shrinkage and Thresholding Algorithm(\textsc{ista}) \citep{daubechies2004iterative}.
-It iteratively obtains the new approximation of the coefficient vector $\widehat{\boldsymbol\beta}_l$ at the iteration $l$ as the linear transformation of the input $\mathbf{y}$ with previous approximation $\widehat{\boldsymbol\beta}_{l-1}$ and then propagates the new approximation through the soft thresholding function $h_\lambda(\cdot)$
+One of the popular families of the sparse coding algorithms is the iterative shrinkage algorithms, and notably the Iterative Shrinkage and Thresholding Algorithm (\textsc{ista}) \citep{daubechies2004iterative}.
+It iteratively obtains the new approximation of the coefficient vector $\widehat{\boldsymbol\beta}_l$ at the iteration $l$ as the linear transformation of the input $\mathbf{y}$ with the previous approximation $\widehat{\boldsymbol\beta}_{l-1}$ and then propagates the new approximation through the soft thresholding function $h_\lambda(\cdot)$
 \begin{equation}
@@
 \end{equation}
-with weights $\mathbf{W} = \mathbf{X}^\top / E$, $E$ - upper bound on the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$ and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$ ($\mathbf{I}_{D \times D}$ is the identity matrix of size $D$).
+with weights $\mathbf{W} = \mathbf{X}^\top / E$, $E$ - upper bound of the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$ and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$ ($\mathbf{I}_{D \times D}$ is the identity matrix of size $D$).
 
-The Learned \textsc{ista} (\textsc{lista}) \citep{gregor2010learning} algorithm allows to learn the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
-To achieve this, \textsc{ista} algorithm is limited with the fixed amount of iterations, $L$ and interpreted as a recurrent neural network.
+The Learned \textsc{ista} (\textsc{lista}) \citep{gregor2010learning} algorithm allows to learn the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
+To achieve this, the \textsc{ista} algorithm is limited with the fixed amount of iterations, $L$, and interpreted as a recurrent neural network.
 Overall, it has the following scheme of predicting a coefficient vector $\boldsymbol\beta$ for an observation $\mathbf{y}$
@@
 
-Matrices $\mathbf{W}$, $\mathbf{S}$ are the parameters that are initialised as in \textsc{ista} and then updated with the backpropagation algorithm.
+Matrices $\mathbf{W}$, $\mathbf{S}$ are the parameters that are initialised as in the \textsc{ista} and then updated with the backpropagation algorithm.
 Vectors $\mathbf{c}_l$, $\mathbf{b}$ are intermediate vectors that describe forward propagation.
@@
 
-This section presents the proposed Bayesian neural network for sparse coding. To formulate the Bayesian version of \textsc{lista} we impose the prior distributions on the unknown weights
+This section presents the proposed Bayesian neural network for sparse coding. To formulate the Bayesian version of the \textsc{lista} we impose the prior distributions on the unknown weights
 \begin{subequations}
@@
 where $[\cdot]_d$ denotes the d-th component of a vector, $f(\mathbf{y}^{(n)}; \mathbf{W}, \mathbf{S}, \lambda)$ is the output of the Bayesian \textsc{lista} neural network, $\gamma$ is the precision of the Gaussian distribution.
-The prior of the introduced Gaussian precisions are set to the Gamma distribution with parameters $a^{\cdot}$ and $b^{\cdot}$:
+The prior of the introduced Gaussian precisions are set to the Gamma distribution with parameters~$a^{\cdot}$ and~$b^{\cdot}$:
 \begin{subequations}
@@
 When a Gaussian-distributed random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft thresholding function: $x^* = h_{\lambda}(x)$ the probability mass of a resulting random variable $x^*$ is split into two parts.
-The values of $x$ from the interval $[-\lambda, \lambda]$ are converted to $0$ by the soft thresholding operator.
+The values of $x$ from the interval $[-\lambda, \lambda]$ are converted to~$0$ by the soft thresholding operator.
 Therefore, the probability mass of the original distribution that lies in $[-\lambda, \lambda]$ is squeezed into the probability of $x^*$ being zero.
-The values of $x$ from outside of the $[-\lambda, \lambda]$ interval are shifted towards $0$.
+The values of $x$ from outside of the $[-\lambda, \lambda]$ interval are shifted towards~$0$.
 Therefore, the distribution of $x^* \neq 0$ represents the tails of the original Gaussian distribution.
@@
 
-The soft thresholding function shifts elements that are greater than $\lambda$  or less than $-\lambda$ towards $0$.
+The soft thresholding function shifts elements that are greater than $\lambda$  or less than $-\lambda$ towards~$0$.
 Let $\psi(\cdot)$ denote the density of the soft-thresholded distribution on $x^* \neq 0$, $\phi(\cdot)$ denote the density of the original Gaussian distribution on $x$.
@@
 In the previous experiment Bayesian and classical \textsc{lista} show similar results with this number of layers.
-The results of Figure~\ref{fig:unsersampling_synthetic} confirms this competitive behaviour between two \textsc{lista} networks.
+The results of Figure~\ref{fig:unsersampling_synthetic} confirm this competitive behaviour between two \textsc{lista} networks.
 Baselines show similar results in terms of F measure and underperform in terms of \textsc{nmse}.

### 2018-05-13 paper/BayesianLISTA.tex
move proofs to supplementary, shorten derivations

@@
 \usepackage{mathtools}
+\usepackage{xfrac}
 \usepackage{amsfonts}
@@
 \subsection{\uppercase{Initialisation dense layer}}
-The first step in the Bayesian \textsc{lista} is (\ref{eq:first_layer}). The matrix $\mathbf{W}$ consists of Gaussian-distributed components and $y$ is a deterministic vector.
-
- \begin{lemma}[Product of Gaussian matrix and deterministic vector]
- \label{thm:matrix_const}
-Let $\mathbf{W} \in \mathbb{R}^{D \times K}$ be a matrix of independent Gaussian-distributed random variables: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y} \in \mathbb{R}^K$ be a deterministic vector.
-Then their product $\mathbf{W} \mathbf{y}$ is a vector $\mathbf{b} \in \mathbb{R}^{D}$ of random variables $b_d \sim \mathcal{N}(m^b_d, w^b_d)$, where
-\begin{subequations}
-\begin{align}
-m^b_d &= \sum_{k=1}^Ky_k m^w_{dk}, \\
-w^b_d &= \sum_{k=1}^Ky_k^2v^w_{dk}.
- \end{align}
-\end{subequations}
-
- \end{lemma}
- \begin{proof}
- 	The statement follows from the property that the family of normal distributions is closed under linear transformations.
- \end{proof}
-
-According to Lemma~\ref{thm:matrix_const}, $\mathbf{b}$ in~(\ref{eq:first_layer}) is a vector of Gaussian-distributed components.
+The first step in the Bayesian \textsc{lista} is (\ref{eq:first_layer}).
+The matrix $\mathbf{W}$ consists of Gaussian-distributed components: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $y$ is a deterministic vector.
+Since the sum of independent Gaussian-distributed variables is a Gaussian variable~\citep{eisenberg2008sum}, $\mathbf{b}$ is a vector of Gaussian-distributed components $b_d \sim \mathcal{N}(m^b_d, v^b_d)$
+\begin{equation}
+\label{eq:matrix_vector_product}
+m^b_d = \sum_{k=1}^Ky_k m^w_{dk}, \qquad
+v^b_d = \sum_{k=1}^Ky_k^2v^w_{dk}.
+\end{equation}
 
@@
 \label{thm:soft_thresholding}
-The distribution of $x^*$ can be parametrised by the probability of being zero, $\omega^*$, the mean $m^*$ and the variance $v^*$ of the truncated Gaussian distribution.
+The distribution of $x^*$ can be parametrised by the probability of being zero, $\omega^*$, the mean $m^*$ and the variance $v^*$ of the truncated Gaussian distribution
 \end{lemma}
-\begin{proof}
 
-The probability of a zero $\omega^*$ equals to the probability mass of the original distribution from the interval $[-\lambda, \lambda]$
-\begin{align}
-\begin{split}
-\omega^* &=\operatorname{P}(x^*=0) = \operatorname{P}(x \in [-\lambda, \lambda]) \\
-&= \Phi\left(\frac{\lambda-m}{\sqrt{v}}\right) - \Phi\left(\frac{-\lambda-m}{\sqrt{v}}\right).
-\end{split}
-\end{align}
-where $\Phi(\cdot)$ is the standard Gaussian cumulative distribution function.
-
-The soft thresholding function shifts elements that are greater than $\lambda$  or less than $-\lambda$ towards~$0$.
-Let $\psi(\cdot)$ denote the density of the soft-thresholded distribution on $x^* \neq 0$, $\phi(\cdot)$ denote the density of the original Gaussian distribution on $x$.
-Then the first moment of $x^* \neq 0$ is:
-
-\begin{align}
-\label{eq:thr_first_moment}
-\begin{split}
-m^* &= \int_{-\infty}^{+\infty}x\psi(x)dx= \int_{-\infty}^{0}x\phi(x-\lambda)dx \\
-&{} + \int_{0}^{+\infty}x\phi(x+\lambda)dx,
-\end{split}
-\end{align}
-where
-\begin{align}
-&\int_{-\infty}^{0}x\phi(x-\lambda)dx = -\frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} \nonumber\\
-&{} + (\lambda+m)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)\\
-&\int_{0}^{+\infty}x\phi(x+\lambda)dx = \frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\nonumber\\
-& + (m - \lambda)\left(1 - \Phi\left(-\frac{\lambda-m}{\sqrt{v}}\right)\right)
-\end{align}
-
-The second moment of $x^* \neq 0$ is given as
-\begin{align}
-\label{eq:thr_second_moment}
-\begin{split}
-s &= \int_{-\infty}^{+\infty}x^2\psi(x)dx = \int_{-\infty}^{0}x^2\phi(x-\lambda)dx \\
-&{}+ \int_{0}^{+\infty}x^2\phi(x+\lambda)dx,
-\end{split}
-\end{align}
-where
-\begin{align}
-\begin{split}
-&\int_{-\infty}^{0}x^2\phi(x-\lambda)dx = \\
-&-\frac{\sqrt{v}}{\sqrt{2\pi}} (\lambda+m)\exp\left\{\frac{-(\lambda+m)^2}{2v}\right\}\\
-& + (\sigma^2 + (\lambda+m)^2)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
-\end{split}\\
-\begin{split}
-&\int_{0}^{+\infty}x^2\phi(x+\lambda)dx = \\
-&\frac{\sqrt{v}}{\sqrt{2\pi}} (m - \lambda)\exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\\
-& + (\sigma^2 + (m - \lambda)^2)\left(1 - \Phi\left(\frac{\lambda -m}{\sqrt{v}}\right)\right)
-\end{split}
-\end{align}
-
-The resulting variance is then
-\begin{equation}
-v^* = s- (m^*)^2
-\end{equation}
-\end{proof}
-
+The proof of Lemma~\ref{thm:soft_thresholding} and expressions for $\omega^*$, $m^*$ and $v^*$ are given in the supplementary materials.
 Based on the results of Lemma~\ref{thm:soft_thresholding} we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ from (\ref{eq:thr_first}) with a spike and slab distribution with parameters derived in the lemma: the spike probability $\omega$ is equal to $\omega^*$, the slab mean $m$ and variance $v$ are set to the corresponding parameters of the truncated Gaussian $m^*$ and $v^*$.
@@
 
-\begin{proof}
-\begin{align*}
-\begin{split}
-\mathbb{E}\xi &= \int x \big(\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v)\big)dx \\
-& = \omega \int x \delta_0(x)dx + (1 - \omega)\int x \mathcal{N}(x; m, v)dx \\
-& = (1-\omega)m \\
-\mathbb{E}\xi^2 &= \int x^2 \big(\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v)\big)dx \\
-& = \omega \int x^2 \delta_0(x)dx + (1 - \omega)\int x^2 \mathcal{N}(x; m, v)dx \\
-& = (1-\omega)(v + m^2) \\
-\operatorname{Var}\xi &= \mathbb{E}\xi^2 - \left(\mathbb{E}\xi\right)^2 = (1-\omega)(v + \omega m^2)
-\end{split}
-\end{align*}
-\end{proof}
-
 \begin{lemma}[Product of a Gaussian matrix and a spike and slab vector]
@@
  \end{lemma}
- \begin{proof}
-\begin{flalign*}
-	\mathbb{E}e_d &= \sum_{d'=1}^D \mathbb{E}[s_{dd'}\widehat{\beta}_{d'}]  = \sum_{d'=1}^D m^s_{dd'}\mathbb{E}\widehat{\beta}_{d'}\\
-	\operatorname{Var}e_d &= \sum_{d'=1}^D \operatorname{Var}[s_{dd'}\widehat{\beta}_{d'}] = \sum_{d'=1}^D [(\mathbb{E}s_{dd'})^2 \operatorname{Var}\widehat{\beta}_{d'} \\
-	&{}+ (\mathbb{E}\widehat{\beta}_{d'})^2 \operatorname{Var}s_{dd'} + \operatorname{Var}\widehat{\beta}_{d'} \operatorname{Var}s_{dd'}]
-\end{flalign*}
-where $\mathbb{E}\widehat{\beta}_{d'}$ and $\operatorname{Var}\widehat{\beta}_{d'}$ are computed according to Lemma~\ref{thm:moments_spsl}.
- \end{proof}
 
-{\color{red} Let $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista}}.
+The proofs of Lemmas~\ref{thm:moments_spsl} and~\ref{thm:matrix_vector} are given in the supplementary materials.
+
+Let $\mathbf{e}_l$ denote the product $\mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista}.
 We assume that $\mathbf{S}$ and $\widehat{\boldsymbol\beta}_{l-1}$ are mutually independent.
@@
 
-The output $\mathbf{c}_l$ at the step (\ref{eq:l_dense_layer}) is then represented as a sum of two Gaussian-distributed vectors: $\mathbf{b}$ and $\mathbf{e}_l$
-
-\begin{lemma}[Sum of Gaussian vectors]
-\label{thm:sum_vectors}
-If $\mathbf{b} \in \mathbb{R}^{D}$ and $\mathbf{e} \in \mathbb{R}^{D}$ are both vectors of independent Gaussian-distributed random variables: $b_{d} \sim \mathcal{N}(m^b_{d}, v^b_{d})$, $e_{d} \sim \mathcal{N}(m^e_{d}, v^e_{d})$ then their sum $\mathbf{c} = \mathbf{b} + \mathbf{e}$ is a vector of independent Gaussian-distributed random variables $c_{d} \sim \mathcal{N}(m^c_{d}, v^c_{d})$ with
-\begin{subequations}
-\begin{align}
-m^c_{d} &= m^b_{d} + m^e_{d}, \\
-v^c_{d} &= v^b_{d} + v^e_{d}.
- \end{align}
-\end{subequations}
-\end{lemma}
-\begin{proof}
-Based on properties of Gaussian distributions.
-\end{proof}
-
-Therefore, $\mathbf{c}_l$ is a vector of Gaussian-distributed components, which parameters can be found according to Lemma~\ref{thm:sum_vectors}.
+The output $\mathbf{c}_l$ at the step (\ref{eq:l_dense_layer}) is then represented as a sum of two Gaussian-distributed vectors: $\mathbf{b}$ and $\mathbf{e}_l$, i.e.
+it is a Gaussian-distributed vector with components $c_{d} \sim \mathcal{N}(m^c_{d}, v^c_{d})$
+\begin{equation}
+\label{eq:sum_vectors}
+m^c_{d} = m^b_{d} + m^e_{d}, \qquad
+v^c_{d} = v^b_{d} + v^e_{d}.
+\end{equation}
 
@@
 \begin{enumerate}
-	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is the Gaussian distribution with parameters computed according to Lemma \ref{thm:matrix_const};
+	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is the Gaussian distribution with parameters computed according to (\ref{eq:matrix_vector_product});
 	\item $\widehat{\boldsymbol\beta}_{0} = h_\lambda(\mathbf{b})$ is approximated with the spike and slab distribution, which parameters are computed according to Lemma \ref{thm:soft_thresholding}.
 	\item $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is approximated with the Gaussian distribution, which parameters are computed according to Lemma \ref{thm:matrix_vector};
-	\item $\mathbf{c}_l = \mathbf{b} + \mathbf{e}_l$ is the Gaussian distribution with parameters computed according to Lemma \ref{thm:sum_vectors};
+	\item $\mathbf{c}_l = \mathbf{b} + \mathbf{e}_l$ is the Gaussian distribution with parameters computed according to (\ref{eq:sum_vectors});
 	\item $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$ is approximated with the spike and slab distribution, which parameters are computed according to Lemma \ref{thm:soft_thresholding}.
@@
 We have used two approximations in forward propagation of uncertainty.
-First, {\color{red} in Lemma \ref{thm:matrix_vector}} a Gaussian matrix is multiplied by a spike and slab vector and their product is approximated with the Gaussian distribution.
-Second, {\color{red} in Lemma \ref{thm:soft_thresholding}} the result of soft thresholding of a Gaussian vector is approximated with the spike and slab distribution.
+First, at the step (\ref{eq:l_dense_layer}) during the computation of $\mathbf{e}_l$, a Gaussian matrix is multiplied by a spike and slab vector and their product is approximated with the Gaussian distribution.
+Second, at the steps (\ref{eq:thr_first}) and (\ref{eq:l_thr}) the result of soft thresholding of a Gaussian vector is approximated with the spike and slab distribution.
 In this section we demonstrate that these approximations are close to the real distributions.
@@
 For the sampled distribution, $10000$ values are sampled from the Gaussian matrix and the spike and slab vector and their product is computed, then one of the dimensionalities is plotted.
-The approximated distribution is computed according to Lemma \ref{thm:matrix_vector}.
+The parameters of the approximated distribution is computed according to Lemma \ref{thm:matrix_vector}.
 
@@
 For the sampled distribution, $10000$ values are sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities is plotted.
-The approximated distribution is computed according to Lemma \ref{thm:soft_thresholding}.
+The parameters of the approximated distribution is computed according to Lemma \ref{thm:soft_thresholding}.
 
@@
 \end{align}
-We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximated with the spike and slab distribution with the parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}_L}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}_L}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}_L}$
+We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta} = \widehat{\boldsymbol\beta}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximate with the spike and slab distribution with the parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}_L}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}_L}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}_L}$
 \begin{align}
-&Z \approx \int \prod_{d=1}^{D} \big[\mathcal{N}(\beta_d | [\widehat{\boldsymbol\beta}_L]_d, \gamma^{-1}) \nonumber \\
-&\times (\omega^{\widehat{\boldsymbol\beta}_L}_d \delta_0([\widehat{\boldsymbol\beta}_L]_d) + (1 - \omega^{\widehat{\boldsymbol\beta}_L}_d)\mathcal{N}([\widehat{\boldsymbol\beta}_L]_d | m^{\widehat{\boldsymbol\beta}_L}_d, v^{\widehat{\boldsymbol\beta}_L}_d)) \nonumber\\
-&\times \text{Gam} (\gamma_d; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}\widehat{\boldsymbol\beta}_L \mathrm{d}\gamma  \nonumber\\
-&= \prod_{d=1}^{D} \Big[\omega^{\widehat{\boldsymbol\beta}_L}_d \int \big[\mathcal{N}(\beta_d | [\widehat{\boldsymbol\beta}_L]_d, \gamma^{-1})  \delta_0([\widehat{\boldsymbol\beta}_L]_d) \nonumber \\
-&\times \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[\widehat{\boldsymbol\beta}_L]_d \mathrm{d}\gamma  \nonumber\\
-& + (1 - \omega^{\widehat{\boldsymbol\beta}_L}_d)\int \big[\mathcal{N}(\beta_d | [\widehat{\boldsymbol\beta}_L]_d, \gamma^{-1})\nonumber\\
-&\times \mathcal{N}([\widehat{\boldsymbol\beta}_L]_d | m^{\widehat{\boldsymbol\beta}_L}_d, v^{\widehat{\boldsymbol\beta}_L}_d)) \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma)\big]\mathrm{d}[\widehat{\boldsymbol\beta}_L]_d \mathrm{d}\gamma\Big]  \nonumber\\
-& = \prod_{d=1}^{D} \Big[\omega^{\widehat{\boldsymbol\beta}_L}_d \int \mathcal{N}(\beta_d | 0, \gamma^{-1})  \text{Gam} (\gamma; \alpha^\gamma, \beta^\gamma) d\gamma  \nonumber\\
-& + (1 - \omega^{\widehat{\boldsymbol\beta}_L}_d)\int \big[\mathcal{T}(\beta_d | [\widehat{\boldsymbol\beta}_L]_d, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma)  \nonumber\\
-&\times \mathcal{N}([\mathbf{\widehat{\boldsymbol\beta}_L}]_d| m^{\widehat{\boldsymbol\beta}_L}_d, v^{\widehat{\boldsymbol\beta}_L}_d))\big] \mathrm{d}[\widehat{\boldsymbol\beta}_L]_d\Big]  \nonumber\\
-& \approx \prod_{d=1}^D \Big[\omega^{\widehat{\boldsymbol\beta}_L}_d  \mathcal{T}(\beta_d | 0, \frac{\beta^\gamma}{\alpha^\gamma}, 2\alpha^\gamma) \nonumber \\
+&Z \approx \int \prod_{d=1}^{D} \left[\mathcal{N}\left(\beta_d | \widehat{\beta}_d, \gamma^{-1}\right) \nonumber \right.\\
+&\times \left(\omega^{\widehat{\boldsymbol\beta}}_d \delta_0\left(\widehat{\beta}_d\right) + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\widehat{\beta}_d | m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right)\right) \nonumber\\
+&\times \left.\vphantom{\mathcal{N}(\beta_d | \widehat{\beta}_d} \text{Gam} \left(\gamma_d; \alpha^\gamma, \beta^\gamma\right)\right]\mathrm{d}\widehat{\boldsymbol\beta} \mathrm{d}\gamma  \nonumber\\
+& = \prod_{d=1}^{D} \left[\omega^{\widehat{\boldsymbol\beta}}_d \int \mathcal{N}\left(\beta_d | 0, \gamma^{-1}\right)  \text{Gam} \left(\gamma; \alpha^\gamma, \beta^\gamma\right) d\gamma  \nonumber \right.\\
+& + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\int \left[\mathcal{T}\left(\beta_d | \widehat{\beta}_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right)  \nonumber \right.\\
+&\times \left.\left.
+\vphantom{\int}  \mathcal{N}\left(\widehat{\beta}_d | m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right)\right] \mathrm{d}\widehat{\boldsymbol\beta}_d\right]  \nonumber\\
+& \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d | 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) \nonumber \right.\\
 \label{eq:Z_approx}
-&+ (1 - \omega^{\widehat{\boldsymbol\beta}_L}_d)\mathcal{N}(\beta_d | m^{\widehat{\boldsymbol\beta}_L}_d, \frac{\beta^\gamma}{\alpha^\gamma - 1} + v^{\widehat{\boldsymbol\beta}_L})\Big]
+& + \left.
+\vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d | m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}\right)\right],
 \end{align}
-
-The Student t density can be parametrised in different ways. In this paper the following parametrisation is used
+where we have approximated the Student's t density $\mathcal{T}\left(\beta_d | \widehat{\beta}_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right)$ with a Gaussian density with the same mean and variance.
+The Student's t density can be parametrised in different ways.
+In this paper the following parametrisation is used
 \begin{equation}
@@
 \label{sec:experiments}
-The proposed Bayesian \textsc{lista} is evaluated in the context of the sparse coding problem with an undercomplete dictionary, where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
+The proposed Bayesian \textsc{lista} is evaluated in the context of the sparse coding problem with an overcomplete dictionary, where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
 
@@
 
-The \textsc{lista}-based algorithms can be applied for the sparse coding problem with both overcomplete dictionaries as in the original paper \citep{gregor2010learning}, and undercomplete dictionaries \citep{borgerding2017amp}.
-Though this paper presents only results with undercomplete dictionaries, this is not the limitation of the proposed method and it can be used for overcomplete dictionaries in a similar manner.
+The \textsc{lista}-based algorithms can be applied for the sparse coding problem with both overcomplete dictionaries (i.e., $D > K$) as in the original paper \citep{gregor2010learning}, and undercomplete dictionaries (i.e., $D < K$).
+Section~\ref{sec:experiments} provides experiments for the overcomplete case, we give experiments for the undercomplete case in the supplementary material.
 

### 2018-05-13 paper/supplementary.tex
move proofs to supplementary, shorten derivations

\documentclass[twoside,11pt]{article} 
\usepackage{jmlr2e}
\usepackage{amsmath}
\usepackage{bbm} % for indicator function
\usepackage{cancel} % for cancelto
\usepackage{graphicx}
\graphicspath{{./graphics/}}
\usepackage{subfig}

\firstpageno{1}

\begin{document}

\title{Supplementary materials for the paper ``Uncertainty propagation in neural networks for sparse coding''}

%\author{ Olga Isupova \AND Danil Kuzin }

\maketitle

\section{Proofs}

\begin{lemma}[Propagation of a Gaussian distribution through soft thresholding]
\label{thm:soft_thresholding}
The distribution of $x^*$ can be parametrised by the probability of being zero, $\omega^*$, the mean $m^*$ and the variance $v^*$ of the truncated Gaussian distribution.
\end{lemma}
\begin{proof}

The probability of a zero $\omega^*$ equals to the probability mass of the original distribution from the interval $[-\lambda, \lambda]$
\begin{align}
\begin{split}
\omega^* &=\operatorname{P}(x^*=0) = \operatorname{P}(x \in [-\lambda, \lambda]) \\
&= \Phi\left(\frac{\lambda-m}{\sqrt{v}}\right) - \Phi\left(\frac{-\lambda-m}{\sqrt{v}}\right).
\end{split}
\end{align}
where $\Phi(\cdot)$ is the standard Gaussian cumulative distribution function.

The soft thresholding function shifts elements that are greater than $\lambda$  or less than $-\lambda$ towards~$0$. Let $\psi(\cdot)$ denote the density of the soft-thresholded distribution on $x^* \neq 0$, $\phi(\cdot)$ denote the density of the original Gaussian distribution on $x$. Then the first moment of $x^* \neq 0$ is:

\begin{align}
\label{eq:thr_first_moment}
\begin{split}
m^* &= \int_{-\infty}^{+\infty}x\psi(x)dx= \int_{-\infty}^{0}x\phi(x-\lambda)dx \\
&{} + \int_{0}^{+\infty}x\phi(x+\lambda)dx,
\end{split}
\end{align}
where
\begin{align}
&\int_{-\infty}^{0}x\phi(x-\lambda)dx = -\frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} \nonumber\\
&{} + (\lambda+m)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)\\
&\int_{0}^{+\infty}x\phi(x+\lambda)dx = \frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\nonumber\\
& + (m - \lambda)\left(1 - \Phi\left(-\frac{\lambda-m}{\sqrt{v}}\right)\right)
\end{align}

The second moment of $x^* \neq 0$ is given as
\begin{align}
\label{eq:thr_second_moment}
\begin{split}
s &= \int_{-\infty}^{+\infty}x^2\psi(x)dx = \int_{-\infty}^{0}x^2\phi(x-\lambda)dx \\
&{}+ \int_{0}^{+\infty}x^2\phi(x+\lambda)dx,
\end{split}
\end{align}
where
\begin{align}
\begin{split}
&\int_{-\infty}^{0}x^2\phi(x-\lambda)dx = \\
&-\frac{\sqrt{v}}{\sqrt{2\pi}} (\lambda+m)\exp\left\{\frac{-(\lambda+m)^2}{2v}\right\}\\
& + (\sigma^2 + (\lambda+m)^2)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
\end{split}\\
\begin{split}
&\int_{0}^{+\infty}x^2\phi(x+\lambda)dx = \\
&\frac{\sqrt{v}}{\sqrt{2\pi}} (m - \lambda)\exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\\
& + (\sigma^2 + (m - \lambda)^2)\left(1 - \Phi\left(\frac{\lambda -m}{\sqrt{v}}\right)\right)
\end{split}
\end{align}

The resulting variance is then
\begin{equation}
v^* = s- (m^*)^2
\end{equation}
\end{proof}

\begin{lemma}[Moments of a spike and slab distribution]
\label{thm:moments_spsl}
Let a random variable $\xi$ have a spike and slab distribution with probability of spike $\omega$, slab mean $m$ and slab variance $v$. Then its moments are
\begin{subequations}
\begin{align}
\mathbb{E}\xi &= (1-\omega)m \\
\operatorname{Var}\xi & = (1-\omega)(v + \omega m^2)
\end{align}
\end{subequations}
\end{lemma}

\begin{proof}
\begin{align*}
\begin{split}
\mathbb{E}\xi &= \int x \big(\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v)\big)dx \\
& = \omega \int x \delta_0(x)dx + (1 - \omega)\int x \mathcal{N}(x; m, v)dx \\
& = (1-\omega)m \\
\mathbb{E}\xi^2 &= \int x^2 \big(\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v)\big)dx \\
& = \omega \int x^2 \delta_0(x)dx + (1 - \omega)\int x^2 \mathcal{N}(x; m, v)dx \\
& = (1-\omega)(v + m^2) \\
\operatorname{Var}\xi &= \mathbb{E}\xi^2 - \left(\mathbb{E}\xi\right)^2 = (1-\omega)(v + \omega m^2)
\end{split}
\end{align*}
\end{proof}

\begin{lemma}[Product of a Gaussian matrix and a spike and slab vector]
  \label{thm:matrix_vector}
Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta }\in \mathbb{R}^D$ be a vector with spike-and-slab distributed variables: $\widehat{\beta}_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$. The components of the matrix $\mathbf{S}$ and the vector $\widehat{\boldsymbol\beta}$ are mutual independent. Let $\mathbf{e} \in \mathbb{R}^{D}$ denote the product $\mathbf{S} \widehat{\boldsymbol\beta}$. Then the marginal mean and variance of elements $e_d$ of the vector $\mathbf{e}$ are:
\begin{subequations}
\begin{align}
 \mathbb{E}e_d &= \sum_{d'=1}^D m^s_{dd'}(1-\omega_{d'})m_{d'}, \\
 \begin{split}
 \operatorname{Var}e_d &= \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} \\
 & {}+ (1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}].
 \end{split}
 \end{align}
\end{subequations}
 \end{lemma}
 \begin{proof}
\begin{flalign*}
	\mathbb{E}e_d &= \sum_{d'=1}^D \mathbb{E}[s_{dd'}\widehat{\beta}_{d'}]  = \sum_{d'=1}^D m^s_{dd'}\mathbb{E}\widehat{\beta}_{d'}\\
	\operatorname{Var}e_d &= \sum_{d'=1}^D \operatorname{Var}[s_{dd'}\widehat{\beta}_{d'}] = \sum_{d'=1}^D [(\mathbb{E}s_{dd'})^2 \operatorname{Var}\widehat{\beta}_{d'} \\
	&{}+ (\mathbb{E}\widehat{\beta}_{d'})^2 \operatorname{Var}s_{dd'} + \operatorname{Var}\widehat{\beta}_{d'} \operatorname{Var}s_{dd'}]
\end{flalign*}
where $\mathbb{E}\widehat{\beta}_{d'}$ and $\operatorname{Var}\widehat{\beta}_{d'}$ are computed according to Lemma~\ref{thm:moments_spsl}.
 \end{proof}

%\bibliography{bibliography}
%\bibliographystyle{icml2018}

\end{document}

### 2018-05-13 paper/BayesianLISTA.tex
paper: nips style and attempts to shorten the text

@@
-\documentclass[letterpaper]{article}
-\usepackage{proceed2e}
-\usepackage[margin=1in]{geometry}
+\documentclass{article}
 \usepackage{mathtools}
@@
 \usepackage{natbib}
+\usepackage{nips_2018}
 
@@
 
-\section{\uppercase{Introduction}}
+\section{Introduction}
 Though the idea of Bayesian learning in neural networks is not new \citep{neal2012bayesian}, it has regained its attention recently with the development of distributed approximate inference techniques \citep{li2015stochastic, hoffman2013stochastic}  and general boost in popularity of deep learning.
@@
 
-The main contributions of this paper can be summarised~as:
-\begin{itemize}
-\item for the first time we propose a method for uncertainty propagation through the soft thresholding nonlinearity for a Bayesian neural network;
-\item we develop an efficient posterior inference algorithm for weights and outputs of neural networks with the soft thresholding nonlinearity;
-\item we design a novel Bayesian neural network for sparse coding.
-\end{itemize}
+The main contributions of this paper are: (\textit{i}) for the first time we propose a method for uncertainty propagation through the soft thresholding nonlinearity for a Bayesian neural network; (\textit{ii}) we develop an efficient posterior inference algorithm for weights and outputs of neural networks with the soft thresholding nonlinearity; (\textit{iii}) we design a novel Bayesian neural network for sparse coding.
 
-The paper is organised as following: first, we review neural networks for sparse coding in section \ref{sec:nn_sc} and present a novel Bayesian neural network in section \ref{sec:bayesian_lista}.
+%The paper is organised as following: first, we review neural networks for sparse coding in section \ref{sec:nn_sc} and present a novel Bayesian neural network in section \ref{sec:bayesian_lista}.
 We then describe uncertainty propagation to obtain the spike and slab distribution for an output of a network in section \ref{sec:fprop} and how probabilistic backpropagation is organised to update distributions of weights in section \ref{sec:backpropagation}.
@@
 
-\section{\uppercase{Neural networks for sparse coding}}
+\section{Neural networks for sparse coding}
 \label{sec:nn_sc}
@@
 \begin{equation}
-\widehat{\boldsymbol\beta}_l = \mathbf{W}\mathbf{y} + \mathbf{S}_l\widehat{\boldsymbol\beta}_{l-1}
+\widehat{\boldsymbol\beta}_l = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}
 \end{equation}
@@
 Matrices $\mathbf{W}$, $\mathbf{S}$ are the parameters that are initialised as in the \textsc{ista} and then updated with the backpropagation algorithm.
-Vectors $\mathbf{c}_l$, $\mathbf{b}$ are intermediate vectors that describe forward propagation.
+Vectors $\mathbf{c}_l$, $\mathbf{b}$ are auxiliary vectors that describe forward propagation.
 
-\section{\uppercase{Bayesian neural network for sparse coding}}
+\section{Bayesian neural network for sparse coding}
 \label{sec:bayesian_lista}
@@
 This section presents the proposed Bayesian neural network for sparse coding. To formulate the Bayesian version of the \textsc{lista} we impose the prior distributions on the unknown weights
-\begin{subequations}
+\begin{equation}
 \label{eq:ws}
-\begin{align}
-&p(\mathbf{W}) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij} | 0, \eta^{-1}), \\
-&p(\mathbf{S}) = \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} | 0, \eta^{-1}),
-\end{align}
-\end{subequations}
+p(\mathbf{W}) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij} | 0, \eta^{-1}), \qquad
+p(\mathbf{S}) = \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} | 0, \eta^{-1}),
+\end{equation}
 where $w_{ij}$ is a component of the matrix $\mathbf{W}$, $s_{d'd''}$ is a component of the matrix $\mathbf{S}$, $\eta$ is the precision of the Gaussian distribution.
 The likelihood of $\mathbf{B}$ is defined as
-\begin{align}
-p(&\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) \nonumber \\
+\begin{equation}
 \label{eq:likelihood}
-= &\prod_{n=1}^N\prod_{d=1}^D\mathcal{N}(\beta_d^{(n)}; [f(\mathbf{y^{(n)}}; \mathbf{W}, \mathbf{S}, \lambda)]_d, \gamma^{-1}),
-\end{align}
+p(\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) = \prod_{n=1}^N\prod_{d=1}^D\mathcal{N}(\beta_d^{(n)}; [f(\mathbf{y^{(n)}}; \mathbf{W}, \mathbf{S}, \lambda)]_d, \gamma^{-1}),
+\end{equation}
 where $[\cdot]_d$ denotes the d-th component of a vector, $f(\mathbf{y}^{(n)}; \mathbf{W}, \mathbf{S}, \lambda)$ is the output of the Bayesian \textsc{lista} neural network, $\gamma$ is the precision of the Gaussian distribution.
 The prior of the introduced Gaussian precisions are set to the Gamma distribution with parameters~$a^{\cdot}$ and~$b^{\cdot}$:
-\begin{subequations}
+\begin{equation}
 \label{eq:gamma_eta}
-\begin{align}
-&p(\gamma) = \text{Gam}\left(\gamma; a^{\gamma}, b^{\gamma}\right), \\
-&p(\eta) = \text{Gam}\left(\eta; 	a^{\eta}, b^{\eta}\right)
-\end{align}
-\end{subequations}
+p(\gamma) = \text{Gam}\left(\gamma; a^{\gamma}, b^{\gamma}\right), \qquad
+p(\eta) = \text{Gam}\left(\eta; 	a^{\eta}, b^{\eta}\right)
+\end{equation}
 
 The posterior distribution is then
-\begin{align}
-p(&\mathbf{W}, \mathbf{S}, \gamma, \eta | \mathbf{B}, \mathbf{Y}, \lambda) \nonumber \\
+\begin{equation}
 \label{eq:posterior}
-= & \frac{p(\mathbf{B} | \mathbf{Y}, \mathbf{W},  \mathbf{S}, \gamma, \lambda) p(\mathbf{W} | \eta )p(\mathbf{S} | \eta) p(\eta) p(\gamma)}{p(\mathbf{B} | \mathbf{Y}, \lambda)}
-\end{align}
+p(\mathbf{W}, \mathbf{S}, \gamma, \eta | \mathbf{B}, \mathbf{Y}, \lambda) = \frac{p(\mathbf{B} | \mathbf{Y}, \mathbf{W},  \mathbf{S}, \gamma, \lambda) p(\mathbf{W} | \eta )p(\mathbf{S} | \eta) p(\eta) p(\gamma)}{p(\mathbf{B} | \mathbf{Y}, \lambda)}
+\end{equation}
 The shrinkage parameter $\lambda$ is a hyperparameter of the model.
 
-\section{\uppercase{Uncertainty propagation through soft thresholding}}
+\section{Uncertainty propagation through soft thresholding}
 \label{sec:fprop}
@@
 
-\subsection{\uppercase{Initialisation dense layer}}
+\subsection{Initialisation dense layer}
 The first step in the Bayesian \textsc{lista} is (\ref{eq:first_layer}).
@@
 
-\subsection{\uppercase{Soft thresholding nonlinearity}}
+\subsection{Soft thresholding nonlinearity}
 At the second step (\ref{eq:thr_first}) of the Bayesian \textsc{lista} the Gaussian vector $\mathbf{b}$ is taken as an input of the soft thresholding function.
@@
 Based on the results of Lemma~\ref{thm:soft_thresholding} we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ from (\ref{eq:thr_first}) with a spike and slab distribution with parameters derived in the lemma: the spike probability $\omega$ is equal to $\omega^*$, the slab mean $m$ and variance $v$ are set to the corresponding parameters of the truncated Gaussian $m^*$ and $v^*$.
+The quality of this approximation is discussed in the supplementary materials.
 
-\subsection{\uppercase{Main layers}}
+\subsection{Main layers}
 The distributions of the inputs at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista} for each $l$ are: the vector $\mathbf{b}$ and matrix $\mathbf{S}$ that consist of Gaussian-distributed components and $\widehat{\boldsymbol\beta}_{l-1}$, which is a vector of the spike and slab random variables.
-
 In order to determine the distribution of the output $\mathbf{c}_l$ we first formulate two lemmas.
@@
 Let a random variable $\xi$ have a spike and slab distribution with probability of spike $\omega$, slab mean $m$ and slab variance $v$. Then its moments are
-\begin{subequations}
-\begin{align}
-\mathbb{E}\xi &= (1-\omega)m \\
-\operatorname{Var}\xi & = (1-\omega)(v + \omega m^2)
-\end{align}
-\end{subequations}
+\begin{equation}
+\mathbb{E}\xi = (1-\omega)m, \qquad \operatorname{Var}\xi = (1-\omega)(v + \omega m^2)
+\end{equation}
 \end{lemma}
@@
  \begin{split}
- \operatorname{Var}e_d &= \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} \\
- & {}+ (1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}].
+ \operatorname{Var}e_d &= \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} + (1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}].
  \end{split}
@@
 The parameters of the of the approximating Gaussian distribution are set to the marginal mean and variance given in Lemma~\ref{thm:matrix_vector}.
-The quality of this approximation is discussed in section \ref{sec:approx_quality}.
+The supplementary materials provide a discussion of the quality of this approximation.
 
@@
 
-\begin{figure}[!t]
-\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
-%\label{fig:d_testing}
-\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
-\caption{Approximations of the Bayesian \textsc{lista}}
-%\label{fig:z_new_testing}
-\end{figure}
-
-\subsection{\uppercase{Bayesian lista forward propagation}}
+\subsection{Bayesian \textsc{lista} forward propagation}
 We have covered all steps of the Bayesian \textsc{lista} and derived distributions for outputs of these steps.
@@
 \end{enumerate}
-
-\subsection{\uppercase{Approximation quality}}
-\label{sec:approx_quality}
-We have used two approximations in forward propagation of uncertainty.
-First, at the step (\ref{eq:l_dense_layer}) during the computation of $\mathbf{e}_l$, a Gaussian matrix is multiplied by a spike and slab vector and their product is approximated with the Gaussian distribution.
-Second, at the steps (\ref{eq:thr_first}) and (\ref{eq:l_thr}) the result of soft thresholding of a Gaussian vector is approximated with the spike and slab distribution.
-In this section we demonstrate that these approximations are close to the real distributions.
-
-Figure \ref{fig:d_testing} demonstrates the comparison of the sampled distribution and approximated distribution for Lemma \ref{thm:matrix_vector}.
-For the sampled distribution, $10000$ values are sampled from the Gaussian matrix and the spike and slab vector and their product is computed, then one of the dimensionalities is plotted.
-The parameters of the approximated distribution is computed according to Lemma \ref{thm:matrix_vector}.
-
-Figure \ref{fig:z_new_testing} demonstrates the comparison of the sampled distribution and approximated distribution for Lemma \ref{thm:soft_thresholding}.
-For the sampled distribution, $10000$ values are sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities is plotted.
-The parameters of the approximated distribution is computed according to Lemma \ref{thm:soft_thresholding}.
 
@@
 
-\section{\uppercase{Backpropagation}}
+\section{Backpropagation}
 \label{sec:backpropagation}
@@
 \begin{split}
-q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} | m^w_{dk}, v^w_{dk}) \\
-&\times \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} | m^s_{d'd''}, v^s_{d'd''}) \\
+q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} | m^w_{dk}, v^w_{dk}) \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} | m^s_{d'd''}, v^s_{d'd''}) \\
 &\times \text{Gam}(\gamma; a^\gamma, b^\gamma) \text{Gam}(\eta; a^\eta, b^\eta)
@@
 \end{equation}
-where $Z$ is the normalisation constant and $f(a)$ is an arbitrary function, $a \in \{w_{dk}, s_{d'd''}; \forall d, k, d', d''\}$.
+where $Z$ is the normalisation constant and $f(a)$ is an arbitrary function, $a \in \{w_{dk}, s_{d'd''}\}$.
 
 According to \cite{minka2001thesis}, new parameters of the Gaussian distribution for $a$ can be computed as
-\begin{align}
-m^{\text{new}} &= m + v \frac{\partial \log Z}{\partial m}, \\
-v^{\text{new}} &= v - v^2\left[ \left(\frac{\partial \log Z}{\partial m}\right)^2 - 2 \frac{\partial \log Z}{\partial v}\right]
-\end{align}
+\begin{equation}
+m^{\text{new}} = m + v \frac{\partial \log Z}{\partial m}, \qquad
+v^{\text{new}} = v - v^2\left[ \left(\frac{\partial \log Z}{\partial m}\right)^2 - 2 \frac{\partial \log Z}{\partial v}\right]
+\end{equation}
 
 Then to find new values of $\mathbf{W}$ and $\mathbf{S}$ we need to compute derivatives of the logarithm of $Z$ when the factor of the true posterior is incorporated in $q$.
-
-\subsection{\uppercase{Likelihood}}
 
@@
 \begin{align}
+Z & = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d | f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta \nonumber\\
 \label{eq:Z}
-\begin{split}
-Z = \int \prod_{d=1}^{D} \big[&\mathcal{N}(\beta_d | f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) \\
- &q(\mathbf{W}, \mathbf{S}, \gamma, \eta)\big] \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
- \end{split}
+& \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d | 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d | m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}\right)\right].
 \end{align}
-We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta} = \widehat{\boldsymbol\beta}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximate with the spike and slab distribution with the parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}_L}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}_L}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}_L}$
-\begin{align}
-&Z \approx \int \prod_{d=1}^{D} \left[\mathcal{N}\left(\beta_d | \widehat{\beta}_d, \gamma^{-1}\right) \nonumber \right.\\
-&\times \left(\omega^{\widehat{\boldsymbol\beta}}_d \delta_0\left(\widehat{\beta}_d\right) + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\widehat{\beta}_d | m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right)\right) \nonumber\\
-&\times \left.\vphantom{\mathcal{N}(\beta_d | \widehat{\beta}_d} \text{Gam} \left(\gamma_d; \alpha^\gamma, \beta^\gamma\right)\right]\mathrm{d}\widehat{\boldsymbol\beta} \mathrm{d}\gamma  \nonumber\\
-& = \prod_{d=1}^{D} \left[\omega^{\widehat{\boldsymbol\beta}}_d \int \mathcal{N}\left(\beta_d | 0, \gamma^{-1}\right)  \text{Gam} \left(\gamma; \alpha^\gamma, \beta^\gamma\right) d\gamma  \nonumber \right.\\
-& + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\int \left[\mathcal{T}\left(\beta_d | \widehat{\beta}_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right)  \nonumber \right.\\
-&\times \left.\left.
-\vphantom{\int}  \mathcal{N}\left(\widehat{\beta}_d | m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right)\right] \mathrm{d}\widehat{\boldsymbol\beta}_d\right]  \nonumber\\
-& \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d | 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) \nonumber \right.\\
-\label{eq:Z_approx}
-& + \left.
-\vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d | m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}\right)\right],
-\end{align}
-where we have approximated the Student's t density $\mathcal{T}\left(\beta_d | \widehat{\beta}_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right)$ with a Gaussian density with the same mean and variance.
-The Student's t density can be parametrised in different ways.
-In this paper the following parametrisation is used
-\begin{equation}
-\mathcal{T}(x; \mu, \beta, \nu) = \frac{\Gamma\left(\frac{\nu + 1}{2}\right)}{\Gamma\left(\frac{\nu}{2}\right)\sqrt{\pi \nu \beta}} \left(1 + \frac{(x - \mu)^2}{\nu\beta}\right)^{-\frac{\nu + 1}{2}}
-\end{equation}
-where $\Gamma(\cdot)$ denotes the Gamma function.
-
 Parameters of the approximating posterior distribution are then updated with the derivatives of this normalisation constant.
 
-\subsection{\uppercase{Prior}}
 Prior factors from $p$ (\ref{eq:ws}), (\ref{eq:gamma_eta}) are incorporated into $q$ with the EP algorithm~\citep{hernandez2015probabilistic}, i.e.
@@
 
-\subsection{\uppercase{Hyperparameter optimisation}}
-The only hyperparameter in the proposed Bayesian \textsc{lista} is the shrinkage parameter $\lambda$.
-It can be optimised using the Type II maximum likelihood procedure.
-The Type II likelihood, i.e.
-the evidence $p(\boldsymbol\beta | \mathbf{y}, \lambda)$, of the Bayesian \textsc{lista} is equal to the normalisation constant $Z$ (\ref{eq:Z}) computed for the whole training dataset $\boldsymbol\beta$.
-Given the approximation~(\ref{eq:Z_approx}) the optimal hyperparameter $\lambda$ can be found by a gradient-based optimiser.
-
-\section{\uppercase{Experiments}}
+\section{Experiments}
 \label{sec:experiments}
@@
 To measure the performance of the algorithms the normalised mean square error (\textsc{nmse}) and F measure are used.
-\textsc{nmse} for a batch of data $\{\boldsymbol\beta^{(n)}\}_{n=1}^{N}$ and estimates $\{\widehat{\boldsymbol\beta}^{(n)}\}_{n=1}^{N}$ is computed as
-\begin{equation}
-\text{\textsc{nmse}} = \frac{1}{N}\sum\limits_{n=1}^N\sqrt{\frac{\sum\limits_{d=1}^D\left(\widehat{\beta}_{d}^{(n)} - \beta_d^{(n)}\right)^2}{\sum\limits_{d=1}^D\left(\beta_{d}^{(n)}\right)^2}}
-\end{equation}
-In sparse coding it is also important to obtain the correct locations of spikes (i.e zeros) and slabs (i.e.
-non-zeros) in the estimates.
-The problem is therefore viewed as a skewed two-class classification problem where the number of spikes is higher than the number of slabs.
-F measure is used to evaluate the accuracy of such problems.
-It is defined as the harmonic mean of precision and recall
-\begin{equation}
-\text{F measure} = 2\dfrac{\text{precision}\cdot\text{recall}}{\text{precision} + \text{recall}},
-\end{equation}
-where precision is the fraction of estimated slab locations that are correct, recall is the fraction of true slab locations among all predicted slab locations.
 We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for the \textsc{lista} to learn.
 
-\subsection{\uppercase{Predictive performance on synthetic data}}
+\begin{figure}[t!]
+\centering
+%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
+%~
+\subfloat[\textsc{nmse} for different $L$]{\includegraphics[width=0.4\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}
+\label{fig:nmse_n_layers_synthetic}}
+%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
+%~
+\subfloat[F measure for different $L$]{\includegraphics[width=0.4\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}
+\label{fig:f_meas_n_layers_synthetic}}\\[-13pt]
+\subfloat[\textsc{nmse} for different $K$]{\includegraphics[width=0.4\columnwidth]{graphics/synthetic_undersampling/nmse_validation}
+\label{fig:nmse_undersampling_synthetic}}
+%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
+%~
+\subfloat[F measure for different $K$]{\includegraphics[width=0.4\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}
+\label{fig:f_meas_undesampling_synthetic}}
+\caption{Predictive accuracy on the synthetic data: the top row for different numbers of layers (for neural networks) or iterations (for baselines),  the bottom row for different sizes of observations}
+\label{fig:number_of_layers_synthetic}
+\end{figure}
+
+\subsection{Predictive performance on synthetic data}
 First, the predictive performance of the proposed Bayesian \textsc{lista} is analysed on synthetic data.
@@
 
-In Figure \ref{fig:number_of_layers_synthetic} predictive performance for different number of layers $L$ is presented.
+In Figures \ref{fig:nmse_n_layers_synthetic} and \ref{fig:f_meas_n_layers_synthetic} predictive performance for different number of layers $L$ is presented.
 The observation size is set to $K=50$.
@@
 
-Figure~\ref{fig:unsersampling_synthetic} gives the results of predictive performance for different observation sizes $K$.
+Figures~\ref{fig:nmse_undersampling_synthetic} and~\ref{fig:f_meas_undesampling_synthetic} give the results of predictive performance for different observation sizes $K$.
 The number of layers is set as $L=4$.
 In the previous experiment Bayesian and classical \textsc{lista} show similar results with this number of layers.
-The results of Figure~\ref{fig:unsersampling_synthetic} confirm this competitive behaviour between two \textsc{lista} networks.
+The results of Figures~\ref{fig:nmse_undersampling_synthetic} and~\ref{fig:f_meas_undesampling_synthetic} confirm this competitive behaviour between two \textsc{lista} networks.
 Baselines show similar results in terms of F measure and underperform in terms of \textsc{nmse}.
-
 Overall, the experiments on the synthetic data demonstrate that the Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
-
-\begin{figure}[t]
-\centering
-%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
-%~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}}
-%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
-%~
-\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}}
-\caption{Predictive accuracy for different numbers of layers (for neural networks) or iterations (for baselines) on the synthetic data}
-\label{fig:number_of_layers_synthetic}
-\end{figure}
-
-\begin{figure}[t]
-\centering
-%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_train}}
-%~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_validation}}
-%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
-%~
-\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}}
-\caption{Predictive performance for different sizes of observations on the synthetic data}
-\label{fig:unsersampling_synthetic}
-\end{figure}
 
@@
 
-\subsection{\uppercase{Predictive performance on mnist data}}
+\begin{figure}[t!]
+\centering
+%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
+%~
+\subfloat[\textsc{nmse} for $K = 100$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/100_non_normalised_nmse_valid}}
+%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
+%~
+\subfloat[F measure for $K = 100$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/100_non_normalised_f_measure_valid}}\\[-13pt]
+\subfloat[\textsc{nmse} for $K = 250$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/250_non_normalised_nmse_valid}}
+%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
+%~
+\subfloat[F measure for $K = 250$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/250_non_normalised_f_measure_valid}}
+\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the dictionary size $K = 100$ (the top row) and $K = 250$ (the bottom row)}
+\label{fig:mnist}
+\end{figure}
+
+\subsection{Predictive performance on \textsc{mnist} data}
 Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \citep{lecun1998gradient}.
@@
 
-Figures \ref{fig:mnist_100} and \ref{fig:mnist_250} present quality on the validation set with dictionaries of size $100$ and $250$.
+Figure \ref{fig:mnist} present quality on the validation set with dictionaries of size $100$ and $250$.
 The experiment with $K=100$ presents severe conditions for the algorithms: the very limited size of the training dataset combined with the small dimensionality of observations.
@@
 Both baselines are unable to perform well in these experiments.
+The proposed Bayesian \textsc{lista} network also estimates the posterior distribution for $\boldsymbol\beta$.
+The parameters of the posterior distribution and samples from it are given in the supplementary materials.
 
-The proposed Bayesian \textsc{lista} network also estimates the posterior distribution for $\boldsymbol\beta$.
-Figure~\ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
-
-\begin{figure}[t]
-\centering
-%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
-%~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_nmse_valid}}
-%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
-%~
-\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_f_measure_valid}}
-\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the dictionary size $K = 100$}
-\label{fig:mnist_100}
-\end{figure}
-
-\begin{figure}[t]
-\centering
-%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_train}}
-%~
-\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_nmse_valid}}
-%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
-%~
-\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_f_measure_valid}}
-\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the dictionary size $K = 250$}
-\label{fig:mnist_250}
-\end{figure}
-
-%\begin{figure}[t]
-%\includegraphics[width=\columnwidth]{loss}
-%\caption{Validation \textsc{nmse}}
-%\label{fig:validation}
-%\end{figure}
-\begin{figure}[t]
-\centering
-\subfloat[$\beta$ posterior mean]{\includegraphics[width=0.33\columnwidth]{posterior_mean}}~
-\subfloat[$\beta$ posterior std]{\includegraphics[width=0.33\columnwidth]{posterior_std}}~
-\subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.33\columnwidth]{posterior_spike_indicator}}
-\caption{Posterior parameters for an image of the digit 7.}
-\label{fig:posterior_distribution}
-\end{figure}
-\begin{figure}[t]
-\centering
-\subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_0}}~
-\subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_1}}~
-\subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_2}}
-\caption{Samples from the posterior for an image of the digit 7.}
-\label{fig:posterior_samples}
-\end{figure}
-
-\subsection{\uppercase{Active learning}}
+\subsection{Active learning}
 To demonstrate a potential scenario that can benefit from uncertainty estimates of the Bayesian \textsc{lista} we consider the active learning example \citep{settles.tr09}.
@@
 After every addition the performance is measured on the test data.
-
 We compare the actively updated approach of adding new points from the pool with the random approach that picks a new data point from the pool at random.
@@
 \centering
-\subfloat[\textsc{nmse}]{\includegraphics[width=0.5\columnwidth]{graphics/active_mnist/nmse_validation}}%
-\subfloat[F measure]{\includegraphics[width=0.5\columnwidth]{graphics/active_mnist/f_measure_validation}}
+\subfloat[\textsc{nmse}]{\includegraphics[width=0.4\columnwidth]{graphics/active_mnist/nmse_validation}}%
+\subfloat[F measure]{\includegraphics[width=0.4\columnwidth]{graphics/active_mnist/f_measure_validation}}
 \caption{Performance for the active learning experiment on the \textsc{mnist} data. }
@@
 
-\section{\uppercase{Discussion}}
+\section{Discussion}
 \label{sec:discussion}
@@
 
-\section{\uppercase{Conclusions and future work}}
+\section{Conclusions and future work}
 \label{sec:conclusions}

### 2018-05-13 paper/supplementary.tex
paper: nips style and attempts to shorten the text

@@
-\documentclass[twoside,11pt]{article} 
-\usepackage{jmlr2e}
+\documentclass{article} 
+\usepackage[preprint]{nips_2018}
 \usepackage{amsmath}
@@
 
-%\author{ Olga Isupova \AND Danil Kuzin }
+%\author{ }
 
@@
 
+\section{Approximation quality}
+\label{sec:approx_quality}
+
+\begin{figure}[!t]
+\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
+%\label{fig:d_testing}
+\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
+\caption{Approximations of the Bayesian \textsc{lista}}
+%\label{fig:z_new_testing}
+\end{figure}
+
+We have used two approximations in forward propagation of uncertainty.
+First, at the step (\ref{eq:l_dense_layer}) during the computation of $\mathbf{e}_l$, a Gaussian matrix is multiplied by a spike and slab vector and their product is approximated with the Gaussian distribution.
+Second, at the steps (\ref{eq:thr_first}) and (\ref{eq:l_thr}) the result of soft thresholding of a Gaussian vector is approximated with the spike and slab distribution.
+In this section we demonstrate that these approximations are close to the real distributions.
+
+Figure \ref{fig:d_testing} demonstrates the comparison of the sampled distribution and approximated distribution for Lemma \ref{thm:matrix_vector}.
+For the sampled distribution, $10000$ values are sampled from the Gaussian matrix and the spike and slab vector and their product is computed, then one of the dimensionalities is plotted.
+The parameters of the approximated distribution is computed according to Lemma \ref{thm:matrix_vector}.
+
+Figure \ref{fig:z_new_testing} demonstrates the comparison of the sampled distribution and approximated distribution for Lemma \ref{thm:soft_thresholding}.
+For the sampled distribution, $10000$ values are sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities is plotted.
+The parameters of the approximated distribution is computed according to Lemma \ref{thm:soft_thresholding}.
+
+\section{Derivation for the normalisation constant}
+When the likelihood term for a single data point is incorporated into the approximating distribution $q$, the normalisation constant of $q$ is expressed as
+\begin{equation}
+\label{eq:Z}
+Z = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d | f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
+\end{equation}
+We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta} = \widehat{\boldsymbol\beta}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximate with the spike and slab distribution with the parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}_L}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}_L}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}_L}$
+\begin{align}
+Z &\approx \int \prod_{d=1}^{D} \mathcal{N}\left(\beta_d | \widehat{\beta}_d, \gamma^{-1}\right) \left(\omega^{\widehat{\boldsymbol\beta}}_d \delta_0\left(\widehat{\beta}_d\right) + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\widehat{\beta}_d | m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right)\right) \text{Gam} \left(\gamma_d; \alpha^\gamma, \beta^\gamma\right)\mathrm{d}\widehat{\boldsymbol\beta} \mathrm{d}\gamma  \nonumber\\
+& = \prod_{d=1}^{D} \left[\omega^{\widehat{\boldsymbol\beta}}_d \int \mathcal{N}\left(\beta_d | 0, \gamma^{-1}\right)  \text{Gam} \left(\gamma; \alpha^\gamma, \beta^\gamma\right) d\gamma  \nonumber \right.\\
+&\quad + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\int \mathcal{T}\left(\beta_d | \widehat{\beta}_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) 
+\left. \vphantom{\int}  \mathcal{N}\left(\widehat{\beta}_d | m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right) \mathrm{d}\widehat{\boldsymbol\beta}_d\right]  \nonumber\\
+\label{eq:Z_approx}
+& \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d | 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d | m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}\right)\right],
+\end{align}
+where we have approximated the Student's t density $\mathcal{T}\left(\beta_d | \widehat{\beta}_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right)$ with a Gaussian density with the same mean and variance.
+The Student's t density can be parametrised in different ways.
+In this work the following parametrisation is used
+\begin{equation}
+\mathcal{T}(x; \mu, \beta, \nu) = \frac{\Gamma\left(\frac{\nu + 1}{2}\right)}{\Gamma\left(\frac{\nu}{2}\right)\sqrt{\pi \nu \beta}} \left(1 + \frac{(x - \mu)^2}{\nu\beta}\right)^{-\frac{\nu + 1}{2}}
+\end{equation}
+where $\Gamma(\cdot)$ denotes the Gamma function.
+
+\section{Hyperparameter optimisation}
+The only hyperparameter in the proposed Bayesian \textsc{lista} is the shrinkage parameter $\lambda$.
+It can be optimised using the Type II maximum likelihood procedure.
+The Type II likelihood, i.e.
+the evidence $p(\boldsymbol\beta | \mathbf{y}, \lambda)$, of the Bayesian \textsc{lista} is equal to the normalisation constant $Z$ (\ref{eq:Z}) computed for the whole training dataset $\boldsymbol\beta$.
+Given the approximation~(\ref{eq:Z_approx}) the optimal hyperparameter $\lambda$ can be found by a gradient-based optimiser.
+
+\section{Performance measures}
+\textsc{nmse} for a batch of data $\{\boldsymbol\beta^{(n)}\}_{n=1}^{N}$ and estimates $\{\widehat{\boldsymbol\beta}^{(n)}\}_{n=1}^{N}$ is computed as
+\begin{equation}
+\text{\textsc{nmse}} = \frac{1}{N}\sum\limits_{n=1}^N\sqrt{\frac{\sum\limits_{d=1}^D\left(\widehat{\beta}_{d}^{(n)} - \beta_d^{(n)}\right)^2}{\sum\limits_{d=1}^D\left(\beta_{d}^{(n)}\right)^2}}
+\end{equation}
+In sparse coding it is also important to obtain the correct locations of spikes (i.e zeros) and slabs (i.e.
+non-zeros) in the estimates.
+The problem is therefore viewed as a skewed two-class classification problem where the number of spikes is higher than the number of slabs.
+F measure is used to evaluate the accuracy of such problems.
+It is defined as the harmonic mean of precision and recall
+\begin{equation}
+\text{F measure} = 2\dfrac{\text{precision}\cdot\text{recall}}{\text{precision} + \text{recall}},
+\end{equation}
+where precision is the fraction of estimated slab locations that are correct, recall is the fraction of true slab locations among all predicted slab locations.
+
+\section{Posterior estimation for the \textsc{mnist} data}
+Figure~\ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
+
+\begin{figure}[t]
+\centering
+\subfloat[$\beta$ posterior mean]{\includegraphics[width=0.33\columnwidth]{posterior_mean}}~
+\subfloat[$\beta$ posterior std]{\includegraphics[width=0.33\columnwidth]{posterior_std}}~
+\subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.33\columnwidth]{posterior_spike_indicator}}
+\caption{Posterior parameters for an image of the digit 7.}
+\label{fig:posterior_distribution}
+\end{figure}
+\begin{figure}[t]
+\centering
+\subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_0}}~
+\subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_1}}~
+\subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_2}}
+\caption{Samples from the posterior for an image of the digit 7.}
+\label{fig:posterior_samples}
+\end{figure}
+
 %\bibliography{bibliography}

### 2018-05-13 paper/BayesianLISTA.tex
paper: further corrections

@@
 There are currently two approaches in Bayesian neural networks: explicit distributions of weights can be included in a network \citep{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing uncertainty \citep{gal2016dropout}.
-In this paper we use the first way and impose distributions on weights to obtain posterior estimates of weights and predictions with uncertainty estimated.
+In this paper we use the former and impose distributions on weights to obtain the posterior of weights and predictions with uncertainty estimated.
 
@@
 \label{eq:regression_problem}
-\mathbf{y} = \mathbf{X}\boldsymbol\beta + \varepsilon
+\mathbf{y} = \mathbf{X}\boldsymbol\beta + \boldsymbol\varepsilon
 \end{equation}
-where $\mathbf{y} \in \mathbb{R}^K$ is the observation, $\mathbf{X} \in \mathbb{R}^{K \times D}$ is the design matrix, $\boldsymbol\beta \in \mathbb{R}^D$ is the unknown vector of weights with many elements $\beta_d$ equal to zero, $\varepsilon \in \mathbb{R}^K$ is the independent Gaussian noise.
+where $\mathbf{y} \in \mathbb{R}^K$ is the observation, $\mathbf{X} \in \mathbb{R}^{K \times D}$ is the design matrix, $\boldsymbol\beta \in \mathbb{R}^D$ is the unknown vector of weights with many elements $\beta_d$ equal to zero, $\boldsymbol\varepsilon \in \mathbb{R}^K$ is the independent Gaussian noise.
 
@@
 \end{equation}
-with weights $\mathbf{W} = \mathbf{X}^\top / E$, $E$ - upper bound of the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$ and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$ ($\mathbf{I}_{D \times D}$ is the identity matrix of size $D$).
+with weights $\mathbf{W} = \mathbf{X}^\top / E$, where $E$ is the upper bound of the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$, and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$ ($\mathbf{I}_{D \times D}$ is the identity matrix of size $D$).
 
-The Learned \textsc{ista} (\textsc{lista}) \citep{gregor2010learning} algorithm allows to learn the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
-To achieve this, the \textsc{ista} algorithm is limited with the fixed amount of iterations, $L$, and interpreted as a recurrent neural network.
-Overall, it has the following scheme of predicting a coefficient vector $\boldsymbol\beta$ for an observation $\mathbf{y}$
+The Learned \textsc{ista} (\textsc{lista}) \citep{gregor2010learning} allows to learn the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
+To achieve this, the \textsc{ista} is limited with the fixed amount of iterations, $L$, and interpreted as a recurrent neural network.
+It has the following scheme of predicting a coefficient vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$
 \begin{align}
@@
 Matrices $\mathbf{W}$, $\mathbf{S}$ are the parameters that are initialised as in the \textsc{ista} and then updated with the backpropagation algorithm.
-Vectors $\mathbf{c}_l$, $\mathbf{b}$ are auxiliary vectors that describe forward propagation.
+Vectors $\mathbf{c}_l$ and $\mathbf{b}$ are auxiliary vectors that describe forward propagation.
 
@@
 \label{eq:ws}
-p(\mathbf{W}) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij} | 0, \eta^{-1}), \qquad
-p(\mathbf{S}) = \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} | 0, \eta^{-1}),
+p(\mathbf{W}) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij} ; 0, \eta^{-1}), \qquad
+p(\mathbf{S}) = \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; 0, \eta^{-1}),
 \end{equation}
-where $w_{ij}$ is a component of the matrix $\mathbf{W}$, $s_{d'd''}$ is a component of the matrix $\mathbf{S}$, $\eta$ is the precision of the Gaussian distribution.
+where $\eta$ is the precision of the Gaussian distribution.
 The likelihood of $\mathbf{B}$ is defined as
@@
 \end{equation}
-where $\omega_d$, $m_d$, and $v_d$ are the components of vectors $\boldsymbol\omega$, $\mathbf{m}$, and $\mathbf{v}$, respectively, $\delta_0$ is the delta-function that represents a spike.
+where $\delta_0$ is the delta-function that represents a spike.
 
@@
 This leads to the proposed probabilistic backpropagation algorithm that is presented in Section~\ref{sec:backpropagation}.
-We now describe how to propagate uncertainty through the layers of the Bayesian \textsc{lista} step by step stating meanwhile theoretical facts required for the method.
+We now describe how to propagate uncertainty through the layers of the Bayesian \textsc{lista} step by step.
 
@@
 The first step in the Bayesian \textsc{lista} is (\ref{eq:first_layer}).
-The matrix $\mathbf{W}$ consists of Gaussian-distributed components: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $y$ is a deterministic vector.
+The matrix $\mathbf{W}$ consists of Gaussian-distributed components: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y}$ is a deterministic vector.
 Since the sum of independent Gaussian-distributed variables is a Gaussian variable~\citep{eisenberg2008sum}, $\mathbf{b}$ is a vector of Gaussian-distributed components $b_d \sim \mathcal{N}(m^b_d, v^b_d)$
@@
 
-When a Gaussian-distributed random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft thresholding function: $x^* = h_{\lambda}(x)$ the probability mass of a resulting random variable $x^*$ is split into two parts.
+When a Gaussian random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft thresholding function: $x^* = h_{\lambda}(x)$, the probability mass of the resulting random variable $x^*$ is split into two parts.
 The values of $x$ from the interval $[-\lambda, \lambda]$ are converted to~$0$ by the soft thresholding operator.
@@
 The values of $x$ from outside of the $[-\lambda, \lambda]$ interval are shifted towards~$0$.
-Therefore, the distribution of $x^* \neq 0$ represents the tails of the original Gaussian distribution.
+The distribution of $x^* \neq 0$ then represents the tails of the original Gaussian distribution.
 
-\begin{lemma}[Propagation of a Gaussian distribution through soft thresholding]
+\begin{lemma}[Propagation of a Gaussian variable through soft thresholding]
 \label{thm:soft_thresholding}
-The distribution of $x^*$ can be parametrised by the probability of being zero, $\omega^*$, the mean $m^*$ and the variance $v^*$ of the truncated Gaussian distribution
+The distribution of $x^*$ can be parametrised by the probability of being zero, $\omega^*$, the mean $m^*$ and the variance $v^*$ of the truncated Gaussian distribution.
 \end{lemma}
@@
 \subsection{Main layers}
-The distributions of the inputs at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista} for each $l$ are: the vector $\mathbf{b}$ and matrix $\mathbf{S}$ that consist of Gaussian-distributed components and $\widehat{\boldsymbol\beta}_{l-1}$, which is a vector of the spike and slab random variables.
+The distributions of the inputs at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista} for each $l$ are: the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
 In order to determine the distribution of the output $\mathbf{c}_l$ we first formulate two lemmas.
@@
 \label{thm:moments_spsl}
-Let a random variable $\xi$ have a spike and slab distribution with probability of spike $\omega$, slab mean $m$ and slab variance $v$. Then its moments are
+Let a random variable $\xi$ have a spike and slab distribution with the probability of spike $\omega$, the slab mean $m$ and slab variance $v$. Then its moments are
 \begin{equation}
@@
 Let $\mathbf{e} \in \mathbb{R}^{D}$ denote the product $\mathbf{S} \widehat{\boldsymbol\beta}$.
-Then the marginal mean and variance of elements $e_d$ of the vector $\mathbf{e}$ are:
+Then the marginal mean and variance of the elements $e_d$ of the vector $\mathbf{e}$ are:
 \begin{subequations}
@@
 
-The output $\mathbf{c}_l$ at the step (\ref{eq:l_dense_layer}) is then represented as a sum of two Gaussian-distributed vectors: $\mathbf{b}$ and $\mathbf{e}_l$, i.e.
+The output $\mathbf{c}_l$ at the step (\ref{eq:l_dense_layer}) is then represented as a sum of two Gaussian-distributed vectors: $\mathbf{b}$ and~$\mathbf{e}_l$, i.e.
 it is a Gaussian-distributed vector with components $c_{d} \sim \mathcal{N}(m^c_{d}, v^c_{d})$
@@
 
-Then $\widehat{\boldsymbol\beta}_{l}$ at the step (\ref{eq:l_thr}) of the Bayesian \textsc{lista} is the result of soft thresholding of a Gaussian distribution, which is approximated with the spike and slab distribution,  similar to the step (\ref{eq:thr_first}).
+Then $\widehat{\boldsymbol\beta}_{l}$ at the step (\ref{eq:l_thr}) of the Bayesian \textsc{lista} is the result of soft thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to the step (\ref{eq:thr_first}).
 
@@
 We have covered all steps of the Bayesian \textsc{lista} and derived distributions for outputs of these steps.
-Now we can formulate the main result of this section that describes how the proposed uncertainty propagation works.
+Now we can formulate the main result of this section that describes how the proposed uncertainty propagation scheme works.
 
@@
 
-The exact posterior (\ref{eq:posterior}) is approximated with a factorised distribution
+The exact intractable posterior (\ref{eq:posterior}) is approximated with a factorised distribution
 \begin{align}
@@
 \begin{split}
-q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} | m^w_{dk}, v^w_{dk}) \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} | m^s_{d'd''}, v^s_{d'd''}) \\
+q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} ; m^w_{dk}, v^w_{dk}) \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; m^s_{d'd''}, v^s_{d'd''}) \\
 &\times \text{Gam}(\gamma; a^\gamma, b^\gamma) \text{Gam}(\eta; a^\eta, b^\eta)
@@
 
-When a factor from $p$ is incorporated into $q$, $q$ as a function of Gaussian-distributed weights $\mathbf{W}$ and $\mathbf{S}$ has the following form:
+When a factor from $p$ is incorporated into $q$, $q$ as a function of weights $\mathbf{W}$ and $\mathbf{S}$ has the form:
 \begin{equation}
@@
 \begin{equation}
+\label{eq:param_update}
 m^{\text{new}} = m + v \frac{\partial \log Z}{\partial m}, \qquad
@@
 
-Then to find new values of $\mathbf{W}$ and $\mathbf{S}$ we need to compute derivatives of the logarithm of $Z$ when the factor of the true posterior is incorporated in $q$.
+Then to find new values of $\mathbf{W}$ and $\mathbf{S}$ we need to compute derivatives of the logarithm of $Z$ when the factor of the true posterior $p$ is incorporated in $q$.
 
@@
 \begin{align}
-Z & = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d | f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta \nonumber\\
+Z & = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta \nonumber\\
 \label{eq:Z}
-& \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d | 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d | m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}\right)\right].
+& \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right].
 \end{align}
-Parameters of the approximating posterior distribution are then updated with the derivatives of this normalisation constant.
+Parameters of the approximating posterior distribution are then updated with the derivatives of this normalisation constant according to (\ref{eq:param_update}).
 
 Prior factors from $p$ (\ref{eq:ws}), (\ref{eq:gamma_eta}) are incorporated into $q$ with the EP algorithm~\citep{hernandez2015probabilistic}, i.e.
-they replace the corresponding approximating factors from $q$ and then $q$ is updated to minimise its KL divergence with $q$ that has the true factor incorporated.
+they replace the corresponding approximating factors from $q$ and then $q$ is updated to minimise the KL divergence.
 
@@
 We compare the proposed Bayesian \textsc{lista} with the classical \textsc{lista}~\citep{gregor2010learning} in terms of the predictive accuracy.
-As baselines we also use \textsc{ista} \citep{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \citep{beck2009fast}.
-\textsc{fista} adds the momentum to \textsc{ista} and improves its convergence speed.
+As baselines we also use the \textsc{ista} \citep{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \citep{beck2009fast}.
+The \textsc{fista} adds the momentum to the \textsc{ista} and improves its convergence speed.
 We set the number of iterations in these algorithms and the number of layers in the Bayesian and classical \textsc{lista} networks to $L$.
@@
 First, the predictive performance of the proposed Bayesian \textsc{lista} is analysed on synthetic data.
-We generate $N_\text{train}=500$ sparse coefficients vectors $\boldsymbol\beta^{(n)}$ each of size $D = 100$.
-Coefficients $\boldsymbol\beta^{(n)}$ are generated from the spike and slab distribution with truncated slab: each component $[\beta^{(n)}]_{d}$ is zero with the probability $0.8$ or is from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability $0.2$.
+We generate $N_\text{train}=1000$ and $N_{\text{test}} = 100$ sparse coefficients vectors $\boldsymbol\beta^{(n)}$ each of size $D = 100$.
+Coefficients $\boldsymbol\beta^{(n)}$ are generated from the spike and slab distribution with the truncated slab: each component $\beta^{(n)}_{d}$ is zero with the probability $0.8$ or is from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability $0.2$.
 To simulate sparse observations, we generate the random Gaussian design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$.
@@
 The shrinkage parameter is set to~$\lambda = 0.1$.
+We train the algorithms using the training data of size $N_\text{train}$ and measure performance on the test data of size $N_{\text{test}}$.
 
@@
 The observation size is set to $K=50$.
-The Bayesian \textsc{lista} outperforms \textsc{lista} in terms of both measures.
+The Bayesian \textsc{lista} outperforms the \textsc{lista} in terms of both measures.
 Although the baselines \textsc{ista} and \textsc{fista} show better performance in terms of F measure, the Bayesian \textsc{lista} has the lowest \textsc{nmse}.
@@
 The number of layers is set as $L=4$.
-In the previous experiment Bayesian and classical \textsc{lista} show similar results with this number of layers.
+In the previous experiment the Bayesian and classical \textsc{lista} show similar results with this number of layers.
 The results of Figures~\ref{fig:nmse_undersampling_synthetic} and~\ref{fig:f_meas_undesampling_synthetic} confirm this competitive behaviour between two \textsc{lista} networks.
@@
 The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
-The design matrix $\mathbf{X}$ is learned on 5000 images with the minibatch online algorithm \citep{mairal2009online}.
+The design matrix $\mathbf{X}$ is generated as standard random Gaussian.
 The resulting size of $\mathbf{X}$ is $K \times 784$.
-Then we generate observations as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta$ are images converted to vectors.
-We use $100$ images for training and $100$ for validation.
+Then we generate observations as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta \in \mathbb{R}^{784}$ are flatten images.
+We use $100$ images for training and $100$ for test.
 The shrinkage parameter $\lambda$ is fixed as $0.1$.
@@
 
-The data in this example is the same \textsc{mnist} dataset with the learnt dictionary of size $K=100$.
+The data in this example is the \textsc{mnist} dataset with the learnt dictionary of size $K=100$.
 We use the training data of size $50$, the pool data of size $500$,  and the test data of size $100$.
@@
 We compare the actively updated approach of adding new points from the pool with the random approach that picks a new data point from the pool at random.
-The overall procedure is repeated for $20$ times with new randomly selected initial datasets.
+The procedure is repeated for $20$ times with new randomly selected initial datasets.
 
@@
 Although there are works on Bayesian sparsity in context of neural networks \citep{he2017bayesian}, they are not the Bayesian neural networks in the same sense as the Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
-We find not only correct predictions but also useful posterior estimates for the predictions that show how the model is confident in its decisions.
+We find not only correct predictions but also useful posterior estimates for the predictions.
 
@@
 
-The \textsc{lista}-based algorithms can be applied for the sparse coding problem with both overcomplete dictionaries (i.e., $D > K$) as in the original paper \citep{gregor2010learning}, and undercomplete dictionaries (i.e., $D < K$).
+The \textsc{lista}-based algorithms can be applied for the sparse coding problem with both overcomplete (i.e., $D > K$) as in the original paper \citep{gregor2010learning}, and undercomplete (i.e., $D < K$) dictionaries.
 Section~\ref{sec:experiments} provides experiments for the overcomplete case, we give experiments for the undercomplete case in the supplementary material.
@@
 \label{sec:conclusions}
-We have presented the new method for propagating the uncertainty through the soft thresholding function. %To achieve this goal
+We have presented the new method for propagating uncertainty through the soft thresholding function. %To achieve this goal
 We have approximated the outputs of the function with a spike and slab distribution, and we have shown that this distribution can stay within the same family after linear transformation with Gaussian weights and inputs of a neural network.

### 2018-05-14 theano/experiments/mnist_sparse_coding/mnist_100_train_20_layers_script.py
updated and added some pictures

@@ -1,0 +1,50 @@
+import numpy as np
+import six.moves.cPickle as pickle
+from tqdm import tqdm
+
+
+from experiments.mnist_sparse_coding.mnist_sequential_comparator import MnistSequentialComparatorSparseCoding
+
+if __name__ == '__main__':
+
+    np.random.seed(1)
+
+    D = 400
+    L = 20
+
+    comparator = MnistSequentialComparatorSparseCoding(D, L, learning_rate=0.0001, n_train_sample=100, n_validation_sample=100,
+                                           train_freq=True, train_bayes=False, train_shared_bayes=True, use_ista=True,
+                                           use_fista=True, save_history=False, initial_lambda=0.1)
+
+    n_iter = 50
+
+    for _ in tqdm(range(n_iter)):
+        comparator.train_iteration()
+
+    lista_time = comparator.recorders['lista'].time
+    sh_bayes_time = comparator.recorders['shared_bayes'].time
+    lista_nmse = comparator.recorders['lista'].validation_loss
+    lista_f_meas = comparator.recorders['lista'].validation_f_meas
+    sh_bayes_nmse = comparator.recorders['shared_bayes'].validation_loss
+    sh_bayes_f_meas = comparator.recorders['shared_bayes'].validation_f_meas
+    ista_time = comparator.recorders['ista'].time
+    fista_time = comparator.recorders['fista'].time
+    ista_nmse = comparator.recorders['ista'].validation_loss
+    fista_nmse = comparator.recorders['fista'].validation_loss
+    ista_f_meas = comparator.recorders['ista'].validation_f_meas
+    fista_f_meas = comparator.recorders['fista'].validation_f_meas
+
+    np.savez('time_100_train_20_layers',
+             lista_time=lista_time,
+             sh_bayes_time=sh_bayes_time,
+             lista_nmse=lista_nmse,
+             lista_f_meas=lista_f_meas,
+             sh_bayes_nmse=sh_bayes_nmse,
+             sh_bayes_f_meas=sh_bayes_f_meas,
+             ista_time=ista_time,
+             fista_time=fista_time,
+             ista_nmse=ista_nmse,
+             fista_nmse=fista_nmse,
+             ista_f_meas=ista_f_meas,
+             fista_f_meas=fista_f_meas
+             )

### 2018-05-14 theano/experiments/synthetic/number_of_layers/collect_results.py

@@ -6,22 +6,57 @@ import matplotlib.pyplot as plt
 class NumberOfLayersExperimentReultsCollector(object):
     def __init__(self):
         self.L_array = [2, 3, 4, 5, 6, 7, 8, 9, 10]
+        self.L_array_extra = [15, 20]
         self.random_range = 10
         self.n_iter = 1000
 
     def collect_all(self):
-        self.ista_f_meas_train, self.ista_f_meas_validation, self.ista_loss_train, self.ista_loss_validation, \
-        self.ista_f_meas_train_std, self.ista_f_meas_validation_std, self.ista_loss_train_std, self.ista_loss_validation_std = \
+        _, self.ista_f_meas_validation_first, _, self.ista_loss_validation_first,  \
+        _, self.ista_f_meas_validation_std_first, _, self.ista_loss_validation_std_first = \
             self.collect_main('ista')
-        self.fista_f_meas_train, self.fista_f_meas_validation, self.fista_loss_train, self.fista_loss_validation, \
-        self.fista_f_meas_train_std, self.fista_f_meas_validation_std, self.fista_loss_train_std, self.fista_loss_validation_std, = \
+        _, self.fista_f_meas_validation_first, _, self.fista_loss_validation_first, \
+        _, self.fista_f_meas_validation_std_first, _, self.fista_loss_validation_std_first, = \
             self.collect_main('fista')
-        self.freq_f_meas_train, self.freq_f_meas_validation, self.freq_loss_train, self.freq_loss_validation, \
-        self.freq_f_meas_train_std, self.freq_f_meas_validation_std, self.freq_loss_train_std, self.freq_loss_validation_std = \
+        _, self.freq_f_meas_validation_first, _, self.freq_loss_validation_first, \
+        _, self.freq_f_meas_validation_std_first, _, self.freq_loss_validation_std_first = \
             self.collect_main('freq')
-        self.sh_bayes_f_meas_train, self.sh_bayes_f_meas_validation, self.sh_bayes_loss_train, self.sh_bayes_loss_validation,\
-        self.sh_bayes_f_meas_train_std, self.sh_bayes_f_meas_validation_std, self.sh_bayes_loss_train_std, self.sh_bayes_loss_validation_std = \
+        _, self.sh_bayes_f_meas_validation_first, _, self.sh_bayes_loss_validation_first,\
[…]

### 2018-05-14 theano/experiments/synthetic/number_of_layers/run_long_extra_rseed_3.py

@@ -8,10 +8,10 @@ from tqdm import tqdm, trange
 
 from comparator.compare_sequential import SequentialComparator
 from experiments.synthetic.experiments_parameters import load_long_experiment
-
+from algorithms.PBP_net_lista_single_matrices.DataGenerator import DataGenerator
 rseed, D, K, _, batch_size, validation_size, n_iter = load_long_experiment()
 np.random.seed(rseed)
-L_array = [20, 30, 40, 50]
+L_array = [15, 20]
 
 freq_train_loss = np.zeros((len(L_array), n_iter))
 freq_validation_loss = np.zeros((len(L_array), n_iter))
@@ -38,8 +38,10 @@ fista_validation_f_measure = np.zeros((len(L_array), n_iter))
 rseed = 3
 np.random.seed(rseed)
 for i, L in enumerate(tqdm(L_array)):
-    comparator = SequentialComparator(D, K, L, learning_rate=0.0001, n_train_sample=batch_size,
-                                      n_validation_sample=validation_size, train_freq=True, train_bayes=False,
+    data_generator = DataGenerator(D, K, sparsity=0.8, beta_scale=1, noise_scale=0.5)
+    data_generator.beta_train, data_generator.y_train, _ = data_generator.new_sample(N=batch_size)
+    data_generator.beta_validation, data_generator.y_validation, _ = data_generator.new_sample(N=validation_size)
+    comparator = SequentialComparator(D, K, L, learning_rate=0.0001, data=data_generator, train_freq=True, train_bayes=False,
                                       train_shared_bayes=True, use_ista=True, use_fista=True, save_history=False, initial_lambda=0.1)
     for _ in trange(n_iter):
         comparator.train_iteration()

### 2018-05-14 theano/experiments/synthetic/number_of_layers/run_long_extra_rseed_8.py

@@ -8,10 +8,10 @@ from tqdm import tqdm, trange
 
 from comparator.compare_sequential import SequentialComparator
 from experiments.synthetic.experiments_parameters import load_long_experiment
-
+from algorithms.PBP_net_lista_single_matrices.DataGenerator import DataGenerator
 rseed, D, K, _, batch_size, validation_size, n_iter = load_long_experiment()
 np.random.seed(rseed)
-L_array = [20, 30, 40, 50]
+L_array = [15, 20]
 
 freq_train_loss = np.zeros((len(L_array), n_iter))
 freq_validation_loss = np.zeros((len(L_array), n_iter))
@@ -38,8 +38,10 @@ fista_validation_f_measure = np.zeros((len(L_array), n_iter))
 rseed = 8
 np.random.seed(rseed)
 for i, L in enumerate(tqdm(L_array)):
-    comparator = SequentialComparator(D, K, L, learning_rate=0.0001, n_train_sample=batch_size,
-                                      n_validation_sample=validation_size, train_freq=True, train_bayes=False,
+    data_generator = DataGenerator(D, K, sparsity=0.8, beta_scale=1, noise_scale=0.5)
+    data_generator.beta_train, data_generator.y_train, _ = data_generator.new_sample(N=batch_size)
+    data_generator.beta_validation, data_generator.y_validation, _ = data_generator.new_sample(N=validation_size)
+    comparator = SequentialComparator(D, K, L, learning_rate=0.0001, data=data_generator, train_freq=True, train_bayes=False,
                                       train_shared_bayes=True, use_ista=True, use_fista=True, save_history=False, initial_lambda=0.1)
     for _ in trange(n_iter):
         comparator.train_iteration()

### 2018-05-14 paper/supplementary.tex
paper: further corrections

@@
 \documentclass{article} 
-\usepackage[preprint]{nips_2018}
-\usepackage{amsmath}
-\usepackage{bbm} % for indicator function
-\usepackage{cancel} % for cancelto
-\usepackage{graphicx}
+\usepackage{nips_2018}
+\usepackage{mathtools}
+\usepackage{xfrac}
+\usepackage{amsfonts}
+\usepackage{amsthm}
+\usepackage{subfig}
+\usepackage{hyperref}
+\usepackage{xcolor}
+
+\usepackage{times}
+\usepackage{float}
+
 \graphicspath{{./graphics/}}
@@
 
-\firstpageno{1}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
 
@@
 \end{equation}
-We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta} = \widehat{\boldsymbol\beta}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximate with the spike and slab distribution with the parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}_L}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}_L}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}_L}$
+We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta} = \widehat{\boldsymbol\beta}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximate with the spike and slab distribution with the parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}}$
 \begin{align}
@@
 \label{eq:Z_approx}
-& \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d | 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d | m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}\right)\right],
+& \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d | 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d | m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right],
 \end{align}
@@
 \centering
-\subfloat[$\beta$ posterior mean]{\includegraphics[width=0.33\columnwidth]{posterior_mean}}~
-\subfloat[$\beta$ posterior std]{\includegraphics[width=0.33\columnwidth]{posterior_std}}~
-\subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.33\columnwidth]{posterior_spike_indicator}}
-\caption{Posterior parameters for an image of the digit 7.}
-\label{fig:posterior_distribution}
-\end{figure}
-\begin{figure}[t]
-\centering
 \subfloat[]{\includegraphics[width=0.33\columnwidth]{posterior_sample_0}}~
@@
 
+\begin{figure}[t]
+\centering
+\subfloat[$\beta$ posterior mean]{\includegraphics[width=0.33\columnwidth]{posterior_mean}}~
+\subfloat[$\beta$ posterior std]{\includegraphics[width=0.33\columnwidth]{posterior_std}}~
+\subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.33\columnwidth]{posterior_spike_indicator}}
+\caption{Posterior parameters for an image of the digit 7.}
+\label{fig:posterior_distribution}
+\end{figure}
+
 %\bibliography{bibliography}

### 2018-05-14 paper/BayesianLISTA.tex
updates reading

@@
 \usepackage{bbm}
+\usepackage{algorithm, algorithmic}
 
@@
 \section{Introduction}
-Though the idea of Bayesian learning in neural networks is not new \citep{neal2012bayesian}, it has regained its attention recently with the development of distributed approximate inference techniques \citep{li2015stochastic, hoffman2013stochastic}  and general boost in popularity of deep learning.
-In some spheres, such as self-driving cars or healthcare, uncertainty estimates are very important and Bayesian learning allows to obtain them.
+The idea of Bayesian learning in neural networks \citep{neal2012bayesian} has recently regained its attention with the development of distributed approximate inference techniques \citep{li2015stochastic, hoffman2013stochastic} and general boost in popularity of deep learning.
+In addition to algorithms' predictions themselves, Bayesian learning naturally provides the uncertainty estimates of these predictions.
+These uncertainty estimates are vital in spheres that affect people's health, such as self-driving cars or medicine.
 
-In general, when distributions are included in a network, the complexity of Bayesian inference scales exponentially with the number of layers.
+In general, when distributions are included in the network, the complexity of Bayesian inference scales exponentially with the number of layers.
 Thus, it is infeasible to apply conventional Bayesian inference algorithms for deep neural networks.
@@
 There are currently two approaches in Bayesian neural networks: explicit distributions of weights can be included in a network \citep{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing uncertainty \citep{gal2016dropout}.
-In this paper we use the former and impose distributions on weights to obtain the posterior of weights and predictions with uncertainty estimated.
+In this paper we use the former approach and impose prior distributions on the neural network's weights to obtain the posterior distributions of weights and posterior predictive distributions of target variables.
 
-Sparse coding can be viewed as a linear regression problem with the additional assumption that many of the basis representation coefficients should be zeros.
-They arise in different applications, such as compressive sensing~\citep{candes2008introduction}, image and video processing~\citep{mairal2014sparse}, neuroscience~\citep{baillet1997bayesian, jas2017learning}.
+In this paper, we consider the area of sparse coding.
+The sparse coding problem can be viewed as a linear regression problem with the additional assumption that the majority of the basis representation coefficients should be zeros.
+Such problems arise in different applications, such as compressive sensing~\citep{candes2008introduction}, image and video processing~\citep{mairal2014sparse, wang2015deep}, neuroscience~\citep{baillet1997bayesian, jas2017learning}.
 
-Neural networks address the sparse coding problem with the soft thresholding nonlinearity that shifts current estimates towards zero \citep{gregor2010learning}.
+One of the modern approaches for the sparse coding problem utilises neural networks with soft thresholding nonlinearity~\citep{gregor2010learning, sprechmann2015learning}.
+At every layer this nonlinearity shifts current estimates of the target vectors towards zero, which allows to achieve sparsity of the target vectors.
 In this paper we propose a method to propagate uncertainty through the soft thresholding nonlinearity.
-At every layer the current distribution of the target vector is represented as a spike and slab distribution \citep{mitchell1988bayesian}.
-We show that it can be effectively combined with Gaussian weights of dense layers.
+At every layer the current distribution of the target vector is represented as a spike and slab distribution \citep{mitchell1988bayesian}, which represents the probabilities of each variable being zero, or Gaussian-distributed.
+We show that the spike and slab distribution of traget vectors can be effectively combined with Gaussian weights of dense layers.
 The distribution of the target vector propagated through a dense layer and the soft thresholding nonlinearity can then be closely approximated with a distribution from the same family.
+Overall, this approach allows to make the Bayesian inference for the sparse coding neural network feasible.
 
@@
 It has the following scheme of predicting a coefficient vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$
-\begin{align}
-\label{eq:first_layer}
-&\mathbf{b} = \mathbf{W}\mathbf{y}\\
-\label{eq:thr_first}
-&\widehat{\boldsymbol\beta}_0 = h_\lambda(\mathbf{b}) \\
-&\text{for } l=1:L\\
-\label{eq:l_dense_layer}
-	&\quad \mathbf{c}_l = \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1} \\
-\label{eq:l_thr}
-	&\quad \widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l) \\
-& \widehat{\boldsymbol\beta} = \widehat{\boldsymbol\beta}_{L}
-\end{align}
+
+\begin{algorithm}
+  \caption{\textsc{lista}}
+  \label{alg:lista}
+  \begin{algorithmic}[1]
+    \STATE Initialisation dense layer $\mathbf{b} \gets \mathbf{W}\mathbf{y}$ \label{eq:first_layer}
+    \STATE Initialisation soft thresholding nonlinearity $\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$ \label{eq:thr_first}
+		\FOR{$l=1$ \TO $L$}
+			\STATE Main dense layer $\mathbf{c}_l \gets \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ \label{eq:l_dense_layer}
+			\STATE Main soft thresholding nonlinearity $\widehat{\boldsymbol\beta}_{l} \gets h_\lambda(\mathbf{c}_l)$ \label{eq:l_thr}
+		\ENDFOR
+		\STATE Output $\widehat{\boldsymbol\beta} \gets \widehat{\boldsymbol\beta}_{L}$
+  \end{algorithmic}
+\end{algorithm}
+
+% \begin{align}
+% \label{eq:first_layer}
+% &\mathbf{b} = \mathbf{W}\mathbf{y}\\
+% \label{eq:thr_first}
+% &\widehat{\boldsymbol\beta}_0 = h_\lambda(\mathbf{b}) \\
+% &\text{for } l=1:L\\
+% \label{eq:l_dense_layer}
+% 	&\quad \mathbf{c}_l = \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1} \\
+% \label{eq:l_thr}
+% 	&\quad \widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l) \\
+% & \widehat{\boldsymbol\beta} = \widehat{\boldsymbol\beta}_{L}
+% \end{align}
 

### 2018-05-14 paper/BayesianLISTA.tex
supplementary lambda added, ref to alg corrected in the paper

@@
 To achieve this, the \textsc{ista} is limited with the fixed amount of iterations, $L$, and interpreted as a recurrent neural network.
-It has the following scheme of predicting a coefficient vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$
+A coefficient vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$ is predicted according to Algorithm~\ref{alg:lista}.
 
-\begin{algorithm}
+\begin{algorithm}[h]
   \caption{\textsc{lista}}
@@
 \subsection{Initialisation dense layer}
-The first step in the Bayesian \textsc{lista} is (\ref{eq:first_layer}).
-The matrix $\mathbf{W}$ consists of Gaussian-distributed components: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y}$ is a deterministic vector.
+At step \ref{eq:first_layer} in the Bayesian \textsc{lista} (Algorithm~\ref{alg:lista}) the matrix $\mathbf{W}$ consists of Gaussian-distributed components: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y}$ is a deterministic vector.
 Since the sum of independent Gaussian-distributed variables is a Gaussian variable~\citep{eisenberg2008sum}, $\mathbf{b}$ is a vector of Gaussian-distributed components $b_d \sim \mathcal{N}(m^b_d, v^b_d)$
@@
 \subsection{Soft thresholding nonlinearity}
-At the second step (\ref{eq:thr_first}) of the Bayesian \textsc{lista} the Gaussian vector $\mathbf{b}$ is taken as an input of the soft thresholding function.
+At step~\ref{eq:thr_first} of the Bayesian \textsc{lista} (Algorithm~\ref{alg:lista}) the Gaussian vector $\mathbf{b}$ is taken as an input of the soft thresholding function.
 
@@
 The proof of Lemma~\ref{thm:soft_thresholding} and expressions for $\omega^*$, $m^*$ and $v^*$ are given in the supplementary materials.
-Based on the results of Lemma~\ref{thm:soft_thresholding} we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ from (\ref{eq:thr_first}) with a spike and slab distribution with parameters derived in the lemma: the spike probability $\omega$ is equal to $\omega^*$, the slab mean $m$ and variance $v$ are set to the corresponding parameters of the truncated Gaussian $m^*$ and $v^*$.
+Based on the results of Lemma~\ref{thm:soft_thresholding} we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ at step~\ref{eq:thr_first} with a spike and slab distribution with parameters derived in the lemma: the spike probability $\omega$ is equal to $\omega^*$, the slab mean $m$ and variance $v$ are set to the corresponding parameters of the truncated Gaussian $m^*$ and $v^*$.
 The quality of this approximation is discussed in the supplementary materials.
@@
 \subsection{Main layers}
-The distributions of the inputs at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista} for each $l$ are: the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
+The distributions of the inputs at step \ref{eq:l_dense_layer} of the Bayesian \textsc{lista} (Algorithm~\ref{alg:lista}) for each $l$ are: the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
 In order to determine the distribution of the output $\mathbf{c}_l$ we first formulate two lemmas.
@@
 
-Let $\mathbf{e}_l$ denote the product $\mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at the step (\ref{eq:l_dense_layer}) of the Bayesian \textsc{lista}.
+Let $\mathbf{e}_l$ denote the product $\mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at step \ref{eq:l_dense_layer} of the Bayesian \textsc{lista}.
 We assume that $\mathbf{S}$ and $\widehat{\boldsymbol\beta}_{l-1}$ are mutually independent.
@@
 
-The output $\mathbf{c}_l$ at the step (\ref{eq:l_dense_layer}) is then represented as a sum of two Gaussian-distributed vectors: $\mathbf{b}$ and~$\mathbf{e}_l$, i.e.
+The output $\mathbf{c}_l$ at step \ref{eq:l_dense_layer} is then represented as a sum of two Gaussian-distributed vectors: $\mathbf{b}$ and~$\mathbf{e}_l$, i.e.
 it is a Gaussian-distributed vector with components $c_{d} \sim \mathcal{N}(m^c_{d}, v^c_{d})$
@@
 
-Then $\widehat{\boldsymbol\beta}_{l}$ at the step (\ref{eq:l_thr}) of the Bayesian \textsc{lista} is the result of soft thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to the step (\ref{eq:thr_first}).
+Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of the Bayesian \textsc{lista} (Algorithm~\ref{alg:lista}) is the result of soft thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first}.
 

### 2018-05-14 paper/BayesianLISTA.tex
added missing figure

--- 2018-05-14 paper/BayesianLISTA.tex
@@
 \begin{abstract}
-In the Bayesian neural network framework prior distributions are imposed on weights of a network and a posterior distribution of an output is inferred, rather than a point prediction provided by conventional neural networks.
-Therefore, Bayesian neural networks estimate both an output for a test data and uncertainty of this prediction.
-Uncertainty of the prediction is a result of weight uncertainty propagation through the layers of a network.
+In the Bayesian neural network framework prior distributions are imposed on weights of a network and a posterior distribution of an output is inferred.
+Therefore, Bayesian neural networks estimate the uncertainty of their predictions.
+The uncertainty of the prediction is a result of weight uncertainty propagation through the layers of a network.
 We propose a novel method of propagating uncertainty through the soft thresholding nonlinearity.
 The method expands the area of Bayesian neural networks and enables the soft thresholding nonlinearity to be included in Bayesian deep neural networks for the first time.
-As an example we design a Bayesian Learned Iterative Shrinkage-Thresholding Algorithm (Bayesian \textsc{lista}) network.
+As an example we design a Bayesian Learned Iterative Shrinkage-Thresholding network (Bayesian \textsc{lista}).
 We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.

### 2018-05-14 theano/experiments/mnist/collect_results.py

@@ -74,30 +74,32 @@ class MnistExperimentResultsCollector(object):
         plt.savefig('results/nmse_valid.eps', format='eps')
         plt.show()
 
-        plt.plot(self.ista_time, self.ista_validation_f_measure, label=ista_label, color=ista_color, marker=ista_marker, linewidth=linewidth, markersize=markersize)
-        plt.plot(self.fista_time, self.fista_validation_f_measure, label=fista_label, color=fista_color, marker=fista_marker, linewidth=linewidth, markersize=markersize)
+        # plt.plot(self.ista_time, self.ista_validation_f_measure, label=ista_label, color=ista_color, marker=ista_marker, linewidth=linewidth, markersize=markersize)
+        # plt.plot(self.fista_time, self.fista_validation_f_measure, label=fista_label, color=fista_color, marker=fista_marker, linewidth=linewidth, markersize=markersize)
         plt.plot(self.freq_time, self.freq_validation_f_measure, label=freq_label, color=freq_color, marker=freq_marker, linewidth=linewidth, markersize=markersize)
         plt.plot(self.shared_bayesian_time, self.shared_bayesian_validation_f_measure, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.plot()
         plt.legend()
         plt.ylabel(r'F measure')
-        plt.xlabel(r'Number of iterations')
+        plt.xlabel(r'Time, s')
+        plt.xlim([0, 2500])
         plt.savefig('results/f_measure_valid_time.eps', format='eps')
         plt.show()
 
-        plt.plot(self.ista_time, self.ista_validation_loss, label=ista_label, color=ista_color, marker=ista_marker, linewidth=linewidth, markersize=markersize)
-        plt.plot(self.fista_time, self.fista_validation_loss, label=fista_label, color=fista_color, marker=fista_marker, linewidth=linewidth, markersize=markersize)
+        # plt.plot(self.ista_time, self.ista_validation_loss, label=ista_label, color=ista_color, marker=ista_marker, linewidth=linewidth, markersize=markersize)
+        # plt.plot(self.fista_time, self.fista_validation_loss, label=fista_label, color=fista_color, marker=fista_marker, linewidth=linewidth, markersize=markersize)
[…]

### 2018-05-14 paper/supplementary.tex

@@
 The probability of a zero $\omega^*$ equals to the probability mass of the original distribution from the interval $[-\lambda, \lambda]$
-\begin{align}
-\begin{split}
-\omega^* &=\operatorname{P}(x^*=0) = \operatorname{P}(x \in [-\lambda, \lambda]) \\
-&= \Phi\left(\frac{\lambda-m}{\sqrt{v}}\right) - \Phi\left(\frac{-\lambda-m}{\sqrt{v}}\right).
-\end{split}
-\end{align}
+\begin{equation}
+\omega^* =\operatorname{P}(x^*=0) = \operatorname{P}(x \in [-\lambda, \lambda]) = \Phi\left(\frac{\lambda-m}{\sqrt{v}}\right) - \Phi\left(\frac{-\lambda-m}{\sqrt{v}}\right).
+\end{equation}
 where $\Phi(\cdot)$ is the standard Gaussian cumulative distribution function.
@@
 
-\begin{align}
+\begin{equation}
 \label{eq:thr_first_moment}
-\begin{split}
-m^* &= \int_{-\infty}^{+\infty}x\psi(x)dx= \int_{-\infty}^{0}x\phi(x-\lambda)dx \\
-&{} + \int_{0}^{+\infty}x\phi(x+\lambda)dx,
-\end{split}
-\end{align}
+m^* = \int_{-\infty}^{+\infty}x\psi(x)dx= \int_{-\infty}^{0}x\phi(x-\lambda)dx + \int_{0}^{+\infty}x\phi(x+\lambda)dx,
+\end{equation}
 where
 \begin{align}
-&\int_{-\infty}^{0}x\phi(x-\lambda)dx = -\frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} \nonumber\\
-&{} + (\lambda+m)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)\\
-&\int_{0}^{+\infty}x\phi(x+\lambda)dx = \frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\nonumber\\
-& + (m - \lambda)\left(1 - \Phi\left(-\frac{\lambda-m}{\sqrt{v}}\right)\right)
+&\int_{-\infty}^{0}x\phi(x-\lambda)dx = -\frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} + (\lambda+m)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)\\
+&\int_{0}^{+\infty}x\phi(x+\lambda)dx = \frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(m - \lambda)^2}{2v}\right\} + (m - \lambda)\left(1 - \Phi\left(-\frac{\lambda-m}{\sqrt{v}}\right)\right)
 \end{align}
@@
 The second moment of $x^* \neq 0$ is given as
-\begin{align}
+\begin{equation}
 \label{eq:thr_second_moment}
-\begin{split}
-s &= \int_{-\infty}^{+\infty}x^2\psi(x)dx = \int_{-\infty}^{0}x^2\phi(x-\lambda)dx \\
-&{}+ \int_{0}^{+\infty}x^2\phi(x+\lambda)dx,
-\end{split}
-\end{align}
+s = \int_{-\infty}^{+\infty}x^2\psi(x)dx = \int_{-\infty}^{0}x^2\phi(x-\lambda)dx + \int_{0}^{+\infty}x^2\phi(x+\lambda)dx,
+\end{equation}
 where
@@
 &\int_{-\infty}^{0}x^2\phi(x-\lambda)dx = \\
-&-\frac{\sqrt{v}}{\sqrt{2\pi}} (\lambda+m)\exp\left\{\frac{-(\lambda+m)^2}{2v}\right\}\\
-& + (\sigma^2 + (\lambda+m)^2)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
+&-\frac{\sqrt{v}}{\sqrt{2\pi}} (\lambda+m)\exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} + (\sigma^2 + (\lambda+m)^2)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
 \end{split}\\
@@
 &\int_{0}^{+\infty}x^2\phi(x+\lambda)dx = \\
-&\frac{\sqrt{v}}{\sqrt{2\pi}} (m - \lambda)\exp\left\{\frac{-(m - \lambda)^2}{2v}\right\}\\
-& + (\sigma^2 + (m - \lambda)^2)\left(1 - \Phi\left(\frac{\lambda -m}{\sqrt{v}}\right)\right)
+&\frac{\sqrt{v}}{\sqrt{2\pi}} (m - \lambda)\exp\left\{\frac{-(m - \lambda)^2}{2v}\right\} + (\sigma^2 + (m - \lambda)^2)\left(1 - \Phi\left(\frac{\lambda -m}{\sqrt{v}}\right)\right)
 \end{split}
@@
 	\mathbb{E}e_d &= \sum_{d'=1}^D \mathbb{E}[s_{dd'}\widehat{\beta}_{d'}]  = \sum_{d'=1}^D m^s_{dd'}\mathbb{E}\widehat{\beta}_{d'}\\
-	\operatorname{Var}e_d &= \sum_{d'=1}^D \operatorname{Var}[s_{dd'}\widehat{\beta}_{d'}] = \sum_{d'=1}^D [(\mathbb{E}s_{dd'})^2 \operatorname{Var}\widehat{\beta}_{d'} \\
-	&{}+ (\mathbb{E}\widehat{\beta}_{d'})^2 \operatorname{Var}s_{dd'} + \operatorname{Var}\widehat{\beta}_{d'} \operatorname{Var}s_{dd'}]
+	\operatorname{Var}e_d &= \sum_{d'=1}^D \operatorname{Var}[s_{dd'}\widehat{\beta}_{d'}] \\
+	&= \sum_{d'=1}^D [(\mathbb{E}s_{dd'})^2 \operatorname{Var}\widehat{\beta}_{d'}
+	+ (\mathbb{E}\widehat{\beta}_{d'})^2 \operatorname{Var}s_{dd'} + \operatorname{Var}\widehat{\beta}_{d'} \operatorname{Var}s_{dd'}]
 \end{flalign*}
@@
 
-\begin{figure}[!t]
+\begin{figure}[h]
 \subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
@@
 We have used two approximations in forward propagation of uncertainty.
-First, at the step (\ref{eq:l_dense_layer}) during the computation of $\mathbf{e}_l$, a Gaussian matrix is multiplied by a spike and slab vector and their product is approximated with the Gaussian distribution.
-Second, at the steps (\ref{eq:thr_first}) and (\ref{eq:l_thr}) the result of soft thresholding of a Gaussian vector is approximated with the spike and slab distribution.
+First, at the step 2 of Algorithm 1 during the computation of $\mathbf{e}_l$, a Gaussian matrix is multiplied by a spike and slab vector and their product is approximated with the Gaussian distribution.
+Second, at the steps 2 and 5 of Algorithm 1 the result of soft thresholding of a Gaussian vector is approximated with the spike and slab distribution.
 In this section we demonstrate that these approximations are close to the real distributions.
@@
 \label{eq:Z}
-Z = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d | f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
+Z = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
 \end{equation}
@@
 \begin{align}
-Z &\approx \int \prod_{d=1}^{D} \mathcal{N}\left(\beta_d | \widehat{\beta}_d, \gamma^{-1}\right) \left(\omega^{\widehat{\boldsymbol\beta}}_d \delta_0\left(\widehat{\beta}_d\right) + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\widehat{\beta}_d | m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right)\right) \text{Gam} \left(\gamma_d; \alpha^\gamma, \beta^\gamma\right)\mathrm{d}\widehat{\boldsymbol\beta} \mathrm{d}\gamma  \nonumber\\
-& = \prod_{d=1}^{D} \left[\omega^{\widehat{\boldsymbol\beta}}_d \int \mathcal{N}\left(\beta_d | 0, \gamma^{-1}\right)  \text{Gam} \left(\gamma; \alpha^\gamma, \beta^\gamma\right) d\gamma  \nonumber \right.\\
-&\quad + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\int \mathcal{T}\left(\beta_d | \widehat{\beta}_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) 
-\left. \vphantom{\int}  \mathcal{N}\left(\widehat{\beta}_d | m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right) \mathrm{d}\widehat{\boldsymbol\beta}_d\right]  \nonumber\\
+Z &\approx \int \prod_{d=1}^{D} \mathcal{N}\left(\beta_d ; \widehat{\beta}_d, \gamma^{-1}\right) \left(\omega^{\widehat{\boldsymbol\beta}}_d \delta_0\left(\widehat{\beta}_d\right) + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\widehat{\beta}_d ; m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right)\right) \text{Gam} \left(\gamma_d; \alpha^\gamma, \beta^\gamma\right)\mathrm{d}\widehat{\boldsymbol\beta} \mathrm{d}\gamma  \nonumber\\
+& = \prod_{d=1}^{D} \left[\omega^{\widehat{\boldsymbol\beta}}_d \int \mathcal{N}\left(\beta_d ; 0, \gamma^{-1}\right)  \text{Gam} \left(\gamma; \alpha^\gamma, \beta^\gamma\right) d\gamma  \nonumber \right.\\
+&\quad + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\int \mathcal{T}\left(\beta_d ; \widehat{\beta}_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) 
+\left. \vphantom{\int}  \mathcal{N}\left(\widehat{\beta}_d ; m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right) \mathrm{d}\widehat{\boldsymbol\beta}_d\right]  \nonumber\\
 \label{eq:Z_approx}
-& \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d | 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d | m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right],
+& \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right],
 \end{align}
-where we have approximated the Student's t density $\mathcal{T}\left(\beta_d | \widehat{\beta}_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right)$ with a Gaussian density with the same mean and variance.
+where we have approximated the Student's t density $\mathcal{T}\left(\beta_d ; \widehat{\beta}_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right)$ with a Gaussian density with the same mean and variance.
 The Student's t density can be parametrised in different ways.
@@
 Given the approximation~(\ref{eq:Z_approx}) the optimal hyperparameter $\lambda$ can be found by a gradient-based optimiser.
+
+In our experiments we use $\lambda = 0.1$, which is determined by grid optimisation (Figure~\ref{fig:lambda_opt}).
+
+\begin{figure}[h]
+\centering
+\subfloat[]{\includegraphics[width=0.4\columnwidth]{./synthetic_lambda/nmse_validation}}~
+\subfloat[]{\includegraphics[width=0.4\columnwidth]{./synthetic_lambda/f_measure_validation}}~
+\caption{Grid optimisation for the shrinkage parameter $\lambda$ on the synthetic data.}
+\label{fig:lambda_opt}
+\end{figure}
 
@@
 
-\begin{figure}[t]
+\begin{figure}[h]
 \centering

### 2018-05-14 paper/BayesianLISTA.tex
updated mnist results to 100

@@
 \begin{abstract}
-In the Bayesian neural network framework prior distributions are imposed on weights of a network and a posterior distribution of an output is inferred.
-Therefore, Bayesian neural networks estimate the uncertainty of their predictions.
+In the Bayesian learning for neural networks, prior distributions are imposed on weights of networks and posterior distributions of outputs are inferred.
+The posterior distributions obtained with Bayesian neural networks allow to estimate the uncertainty of predictions.
 The uncertainty of the prediction is a result of weight uncertainty propagation through the layers of a network.
@@
 We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.
-A series of experiments on sparse coding shows that the proposed framework provides both accurate predictions and quantified estimates of uncertainty in these predictions.
+A series of experiments on sparse coding shows that the proposed framework provides both accurate predictions and sensible estimates of uncertainty in these predictions.
 \end{abstract}

### 2018-05-14 theano/experiments/mnist/collect_results.py

@@ -101,5 +101,5 @@ class MnistExperimentResultsCollector(object):
 
 if __name__=='__main__':
     collector = MnistExperimentResultsCollector()
-    collector.collect_main('time_1000_train_20_layers_K_150')
+    collector.collect_main('time_100_train_20_layers_K_250')
     collector.plot_all()

### 2018-05-14 paper/supplementary.tex
supplementary added time

@@
 
-\section{Posterior estimation for the \textsc{mnist} data}
-Figure~\ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
+\section{Additional results on the \textsc{mnist} data}
+In contrast to \textsc{lista} and baselines, the Bayesian \textsc{lista} provides a posterior estimate.
+Figure~\ref{fig:posterior_samples} shows samples from the posterior for one of the test data points and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
 
@@
 
+Here we also provide the comparison of the Bayesian and non-Bayesian \textsc{lista} networks in terms of the clock time (Figure ).
+
 %\bibliography{bibliography}

### 2018-05-14 theano/experiments/mnist/collect_results.py
updated graphics

@@ -50,6 +50,9 @@ class MnistExperimentResultsCollector(object):
         sh_bayes_color='green'
         sh_bayes_label='bayes LISTA'
 
+        label_fontsize = 24
+        legend_fontsize = 14
+
         plt.rc('text', usetex=True)
 
         plt.plot(self.ista_validation_f_measure, label=ista_label, color=ista_color, marker=ista_marker, linewidth=linewidth, markersize=markersize)
@@ -57,9 +60,9 @@ class MnistExperimentResultsCollector(object):
         plt.plot(self.freq_validation_f_measure, label=freq_label, color=freq_color, marker=freq_marker, linewidth=linewidth, markersize=markersize)
         plt.plot(self.shared_bayesian_validation_f_measure, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.plot()
-        plt.legend()
-        plt.ylabel(r'F measure')
-        plt.xlabel(r'Number of iterations')
+        plt.legend(fontsize=legend_fontsize)
+        plt.ylabel(r'F measure', fontsize=label_fontsize)
+        plt.xlabel(r'Number of iterations', fontsize=label_fontsize)
         plt.savefig('results/f_measure_valid.eps', format='eps')
         plt.show()
 
@@ -68,9 +71,9 @@ class MnistExperimentResultsCollector(object):
         plt.plot(self.freq_validation_loss, label=freq_label, color=freq_color, marker=freq_marker, linewidth=linewidth, markersize=markersize)
         plt.plot(self.shared_bayesian_validation_loss, label=sh_bayes_label, color=sh_bayes_color, marker=sh_bayes_marker, linewidth=linewidth, markersize=markersize)
         plt.plot()
-        plt.legend()
-        plt.ylabel(r'\textsc{nmse}')
-        plt.xlabel(r'Number of iterations')
+        plt.legend(fontsize=legend_fontsize)
+        plt.ylabel(r'\textsc{nmse}', fontsize=label_fontsize)
+        plt.xlabel(r'Number of iterations', fontsize=label_fontsize)
         plt.savefig('results/nmse_valid.eps', format='eps')
         plt.show()
 
@@ -79,9 +82,9 @@ class MnistExperimentResultsCollector(object):
[…]

### 2018-05-14 theano/experiments/synthetic/lambda_thr/collect_results.py

@@ -70,7 +70,7 @@ class LambdaExperimentResultsCollector(object):
         linewidth = .25
         markersize = 5.
         std_multiplier = 2
-        label_fontsize = 18
+        label_fontsize = 24
         legend_fontsize = 14
 
         ista_marker= 'o'

### 2018-05-14 theano/experiments/synthetic/lambda_thr/collect_time.py

@@ -93,7 +93,7 @@ class LambdaExperimentTimeCollector(LambdaExperimentResultsCollector):
         linewidth = .25
         markersize = 5.
         std_multiplier = 2
-        label_fontsize = 18
+        label_fontsize = 24
         legend_fontsize = 14
 
         ista_marker= 'o'

### 2018-05-14 theano/experiments/synthetic/number_of_layers/collect_results.py

@@ -142,7 +142,7 @@ class NumberOfLayersExperimentReultsCollector(object):
         linewidth = .25
         markersize = 5.
         std_multiplier = 2
-        label_fontsize = 18
+        label_fontsize = 24
         legend_fontsize = 14
 
         ista_marker= 'o'

### 2018-05-14 theano/experiments/synthetic/undersampling/collect_results.py

@@ -71,7 +71,7 @@ class UndersamplingExperimentReultsCollector(object):
         linewidth = .25
         markersize = 5.
         std_multiplier = 2
-        label_fontsize = 18
+        label_fontsize = 24
         legend_fontsize = 14
 
         ista_marker= 'o'

### 2018-05-14 paper/supplementary.tex

--- 2018-05-14 paper/supplementary.tex
@@
 \begin{figure}[h]
-\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
+\centering
+\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.4\columnwidth]{d_testing}\label{fig:d_testing}}
 %\label{fig:d_testing}
-\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
+\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.4\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
 \caption{Approximations of the Bayesian \textsc{lista}}
@@
 
-\section{Posterior estimation for the \textsc{mnist} data}
-Figure~\ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
+\section{Additional results on the \textsc{mnist} data}
+In contrast to \textsc{lista} and baselines, the Bayesian \textsc{lista} provides a posterior estimate for a test data point.
+Figure~\ref{fig:posterior_samples} shows samples from the posterior for the test image of the digit $7$ and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
 
@@
 
+Here we also provide the comparison of the Bayesian and non-Bayesian \textsc{lista} networks in terms of the clock time for the experiment with $K = 250$ on the \textsc{mnist} data (Figure~\ref{fig:mnist_time}).
+
+\begin{figure}[h]
+\centering
+\subfloat[]{\includegraphics[width=0.4\columnwidth]{./mnist/250_nmse_valid_time}}~
+\subfloat[]{\includegraphics[width=0.4\columnwidth]{./mnist/250_f_measure_valid_time}}~
+\caption{Predictive performance over clock time on the \textsc{mnist} data with the observation size $K = 250$.}
+\label{fig:mnist_time}
+\end{figure}
+
 %\bibliography{bibliography}

### 2018-05-14 paper/BayesianLISTA.tex
paper: corrected dictionary to observations, supplementary ref

@@
 
-\begin{figure}[t!]
-\centering
-%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
-%~
-\subfloat[\textsc{nmse} for $K = 100$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/100_non_normalised_nmse_valid}}
-%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
-%~
-\subfloat[F measure for $K = 100$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/100_non_normalised_f_measure_valid}}\\[-13pt]
-\subfloat[\textsc{nmse} for $K = 250$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/250_non_normalised_nmse_valid}}
-%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
-%~
-\subfloat[F measure for $K = 250$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/250_non_normalised_f_measure_valid}}
-\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the dictionary size $K = 100$ (the top row) and $K = 250$ (the bottom row)}
-\label{fig:mnist}
-\end{figure}
-
 \subsection{Predictive performance on \textsc{mnist} data}
@@
 
-Figure \ref{fig:mnist} present quality on the validation set with dictionaries of size $100$ and $250$.
+Figure \ref{fig:mnist} present quality on the validation set with observation sizes $100$ and $250$.
 The experiment with $K=100$ presents severe conditions for the algorithms: the very limited size of the training dataset combined with the small dimensionality of observations.
@@
 Both baselines are unable to perform well in these experiments.
-The proposed Bayesian \textsc{lista} network also estimates the posterior distribution for $\boldsymbol\beta$.
-The parameters of the posterior distribution and samples from it are given in the supplementary materials.
+Further results on investigation of the predicted posterior and clock time comparison are given in the supplementary materials.
+
+\begin{figure}[h]
+\centering
+%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
+%~
+\subfloat[\textsc{nmse} for $K = 100$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/100_nmse_valid}}
+%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
+%~
+\subfloat[F measure for $K = 100$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/100_f_measure_valid}}\\[-13pt]
+\subfloat[\textsc{nmse} for $K = 250$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/250_nmse_valid}}
+%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
+%~
+\subfloat[F measure for $K = 250$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/250_f_measure_valid}}
+\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the observation size $K = 100$ (the top row) and $K = 250$ (the bottom row)}
+\label{fig:mnist}
+\end{figure}
 
@@
 
-The data in this example is the \textsc{mnist} dataset with the learnt dictionary of size $K=100$.
+The data in this example is the \textsc{mnist} dataset with the observation size $K=100$.
 We use the training data of size $50$, the pool data of size $500$,  and the test data of size $100$.
@@
 This means that the posterior distribution learnt by the Bayesian \textsc{lista} is an adequate estimate of the true posterior.
-\begin{figure}[t]
+\begin{figure}[h]
 \centering
@@
 We find not only correct predictions but also useful posterior estimates for the predictions.
-
-%The inference is based on the expectation propagation algorithm and though it is not suited for distributed inference, stochastic variant of assumed density filtering can potentially be used \citep{li2015stochastic}.
-This would allow the proposed approach to scale.
-
-The \textsc{lista}-based algorithms can be applied for the sparse coding problem with both overcomplete (i.e., $D > K$) as in the original paper \citep{gregor2010learning}, and undercomplete (i.e., $D < K$) dictionaries.
-Section~\ref{sec:experiments} provides experiments for the overcomplete case, we give experiments for the undercomplete case in the supplementary material.
 

### 2018-05-16 paper/BayesianLISTA.tex
updated intro

@@
 
-\usepackage{natbib}
-\usepackage{nips_2018}
+\usepackage[square,numbers]{natbib}
+\usepackage[nonatbib]{nips_2018}
 
@@
 \begin{abstract}
-In the Bayesian learning for neural networks, prior distributions are imposed on weights of networks and posterior distributions of outputs are inferred.
-The posterior distributions obtained with Bayesian neural networks allow to estimate the uncertainty of predictions.
-The uncertainty of the prediction is a result of weight uncertainty propagation through the layers of a network.
-We propose a novel method of propagating uncertainty through the soft thresholding nonlinearity.
+The Bayesian learning allows to estimate the uncertainty of predictions in neural networks by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
+We propose a novel method of propagating the uncertainty through the soft thresholding nonlinearity.
 The method expands the area of Bayesian neural networks and enables the soft thresholding nonlinearity to be included in Bayesian deep neural networks for the first time.
-As an example we design a Bayesian Learned Iterative Shrinkage-Thresholding network (Bayesian \textsc{lista}).
+As an example, we design a Bayesian Learned Iterative Shrinkage-Thresholding network (Bayesian \textsc{lista}).
 We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.
@@
 \section{Introduction}
-The idea of Bayesian learning in neural networks \citep{neal2012bayesian} has recently regained its attention with the development of distributed approximate inference techniques \citep{li2015stochastic, hoffman2013stochastic} and general boost in popularity of deep learning.
+The idea of Bayesian learning in neural networks \cite{neal2012bayesian} has recently regained its attention with the development of distributed approximate inference techniques \cite{li2015stochastic, hoffman2013stochastic} and general boost in popularity of deep learning.
 In addition to algorithms' predictions themselves, Bayesian learning naturally provides the uncertainty estimates of these predictions.
@@
 Nevertheless, recently several techniques have been proposed to handle specific types of neural networks.
-For example, feed-forward networks with the rectified linear unit nonlinearity~\citep{hernandez2015probabilistic}, networks with discrete distributions~\citep{soudry2014expectation}, recurrent networks~\citep{mcdermott2017bayesian}.
+For example, feed-forward networks with the rectified linear unit nonlinearity~\cite{hernandez2015probabilistic}, networks with discrete distributions~\cite{soudry2014expectation}, recurrent networks~\cite{mcdermott2017bayesian}.
 
-There are currently two approaches in Bayesian neural networks: explicit distributions of weights can be included in a network \citep{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing uncertainty \citep{gal2016dropout}.
+There are currently two approaches in Bayesian neural networks: explicit distributions of weights can be included in a network \cite{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing uncertainty \cite{gal2016dropout}.
 In this paper we use the former approach and impose prior distributions on the neural network's weights to obtain the posterior distributions of weights and posterior predictive distributions of target variables.
@@
 The sparse coding problem can be viewed as a linear regression problem with the additional assumption that the majority of the basis representation coefficients should be zeros.
-Such problems arise in different applications, such as compressive sensing~\citep{candes2008introduction}, image and video processing~\citep{mairal2014sparse, wang2015deep}, neuroscience~\citep{baillet1997bayesian, jas2017learning}.
+This sparsity assumption may be represented as $l1$ penalty~\cite{tibshirani1996regression}, or, in Bayesian interpretation, as prior that has sharp peak at zero~\cite{tipping2001sparse}.
+One of the modern approaches for the sparse coding problem utilises neural networks with soft thresholding nonlinearity~\cite{gregor2010learning, sprechmann2015learning}.
+At every layer this nonlinearity shifts current estimates of the target vectors towards zero, which allows to achieve sparsity of the target vectors.
+Such problems arise in different applications, such as compressive sensing~\cite{candes2008introduction}, image and video processing~\cite{mairal2014sparse, wang2015deep}, neuroscience~\cite{baillet1997bayesian, jas2017learning}.
 
-One of the modern approaches for the sparse coding problem utilises neural networks with soft thresholding nonlinearity~\citep{gregor2010learning, sprechmann2015learning}.
-At every layer this nonlinearity shifts current estimates of the target vectors towards zero, which allows to achieve sparsity of the target vectors.
 In this paper we propose a method to propagate uncertainty through the soft thresholding nonlinearity.
-At every layer the current distribution of the target vector is represented as a spike and slab distribution \citep{mitchell1988bayesian}, which represents the probabilities of each variable being zero, or Gaussian-distributed.
-We show that the spike and slab distribution of traget vectors can be effectively combined with Gaussian weights of dense layers.
+At every layer the current distribution of the target vector is represented as a spike and slab distribution \cite{mitchell1988bayesian}, which represents the probabilities of each variable being zero, or Gaussian-distributed.
+We show that the spike and slab distribution of target vectors can be effectively combined with Gaussian weights of dense layers.
 The distribution of the target vector propagated through a dense layer and the soft thresholding nonlinearity can then be closely approximated with a distribution from the same family.
 Overall, this approach allows to make the Bayesian inference for the sparse coding neural network feasible.
-
 The proposed method of uncertainty propagation for the soft thresholding nonlinearity allows us to derive the gradients of the logarithms of normalisation constants, which can be used to update a weight distribution.
@@
 
-%The paper is organised as following: first, we review neural networks for sparse coding in section \ref{sec:nn_sc} and present a novel Bayesian neural network in section \ref{sec:bayesian_lista}.
+The paper is organised as following: first, we review neural networks for sparse coding in section \ref{sec:nn_sc} and present a novel Bayesian neural network in section \ref{sec:bayesian_lista}.
 We then describe uncertainty propagation to obtain the spike and slab distribution for an output of a network in section \ref{sec:fprop} and how probabilistic backpropagation is organised to update distributions of weights in section \ref{sec:backpropagation}.
@@
 
-One of the popular families of the sparse coding algorithms is the iterative shrinkage algorithms, and notably the Iterative Shrinkage and Thresholding Algorithm (\textsc{ista}) \citep{daubechies2004iterative}.
+One of the popular families of the sparse coding algorithms is the iterative shrinkage algorithms, and notably the Iterative Shrinkage and Thresholding Algorithm (\textsc{ista}) \cite{daubechies2004iterative}.
 It iteratively obtains the new approximation of the coefficient vector $\widehat{\boldsymbol\beta}_l$ at the iteration $l$ as the linear transformation of the input $\mathbf{y}$ with the previous approximation $\widehat{\boldsymbol\beta}_{l-1}$ and then propagates the new approximation through the soft thresholding function $h_\lambda(\cdot)$
@@
 
-The Learned \textsc{ista} (\textsc{lista}) \citep{gregor2010learning} allows to learn the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
+The Learned \textsc{ista} (\textsc{lista}) \cite{gregor2010learning} allows to learn the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
 To achieve this, the \textsc{ista} is limited with the fixed amount of iterations, $L$, and interpreted as a recurrent neural network.
@@
 At step \ref{eq:first_layer} in the Bayesian \textsc{lista} (Algorithm~\ref{alg:lista}) the matrix $\mathbf{W}$ consists of Gaussian-distributed components: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y}$ is a deterministic vector.
-Since the sum of independent Gaussian-distributed variables is a Gaussian variable~\citep{eisenberg2008sum}, $\mathbf{b}$ is a vector of Gaussian-distributed components $b_d \sim \mathcal{N}(m^b_d, v^b_d)$
+Since the sum of independent Gaussian-distributed variables is a Gaussian variable~\cite{eisenberg2008sum}, $\mathbf{b}$ is a vector of Gaussian-distributed components $b_d \sim \mathcal{N}(m^b_d, v^b_d)$
 \begin{equation}
@@
 
-For Bayesian inference we expand the probabilistic backpropagation algorithm~\citep{hernandez2015probabilistic} for computing parameter updates.
+For Bayesian inference we expand the probabilistic backpropagation algorithm~\cite{hernandez2015probabilistic} for computing parameter updates.
 It is based on assumed density filtering (ADF) and expectation propagation (EP) and allows to update parameters of the distributions based on the derivatives of the logarithm of a normalisation constant.
@@
 
-Prior factors from $p$ (\ref{eq:ws}), (\ref{eq:gamma_eta}) are incorporated into $q$ with the EP algorithm~\citep{hernandez2015probabilistic}, i.e.
+Prior factors from $p$ (\ref{eq:ws}), (\ref{eq:gamma_eta}) are incorporated into $q$ with the EP algorithm~\cite{hernandez2015probabilistic}, i.e.
 they replace the corresponding approximating factors from $q$ and then $q$ is updated to minimise the KL divergence.
@@
 
-We compare the proposed Bayesian \textsc{lista} with the classical \textsc{lista}~\citep{gregor2010learning} in terms of the predictive accuracy.
-As baselines we also use the \textsc{ista} \citep{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \citep{beck2009fast}.
+We compare the proposed Bayesian \textsc{lista} with the classical \textsc{lista}~\cite{gregor2010learning} in terms of the predictive accuracy.
+As baselines we also use the \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
 The \textsc{fista} adds the momentum to the \textsc{ista} and improves its convergence speed.
@@
 \subsection{Predictive performance on \textsc{mnist} data}
-Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \citep{lecun1998gradient}.
+Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \cite{lecun1998gradient}.
 The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
@@
 \subsection{Active learning}
-To demonstrate a potential scenario that can benefit from uncertainty estimates of the Bayesian \textsc{lista} we consider the active learning example \citep{settles.tr09}.
+To demonstrate a potential scenario that can benefit from uncertainty estimates of the Bayesian \textsc{lista} we consider the active learning example \cite{settles.tr09}.
 The active learning area researches ways to select new training subsets to reduce the total number of required supervision.
@@
 To the best of our knowledge, this is the first implementation of a Bayesian deep sparse coding algorithm.
-Although there are works on Bayesian sparsity in context of neural networks \citep{he2017bayesian}, they are not the Bayesian neural networks in the same sense as the Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
+Although there are works on Bayesian sparsity in context of neural networks \cite{he2017bayesian}, they are not the Bayesian neural networks in the same sense as the Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
 We find not only correct predictions but also useful posterior estimates for the predictions.
@@
 For this we will extend both the uncertainty propagation method to include uncertainty of $\lambda$ and the probabilistic backpropagation algorithm to estimate its posterior.
-We will study stochastic expectation propagation applicability in order to replace ADF that may further improve the quality of posterior estimates~\citep{li2015stochastic}.
+We will study stochastic expectation propagation applicability in order to replace ADF that may further improve the quality of posterior estimates~\cite{li2015stochastic}.
 
+\small
 \bibliography{bibliography}
-\bibliographystyle{icml2018}
+\bibliographystyle{unsrtnat}
 

### 2018-05-16 paper/BayesianLISTA.tex
hack whitespace and e.g. added in the text
reading text for NIPS

@@
 \allowdisplaybreaks
+
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicreturn}{\textbf{Output:}}
+
+% \setlength{\belowcaptionskip}{-15pt}
+%  \usepackage[small,compact]{titlesec}
+%  \titlespacing{\section}{0pt}{1ex}{0.8ex}
+%  \titlespacing{\subsection}{0pt}{0.5ex}{0ex}
+%  \titlespacing{\subsubsection}{0pt}{0.2ex}{0ex}
+%  \expandafter\def\expandafter\normalsize\expandafter{%
+%      \normalsize
+%      \setlength\abovedisplayskip{2pt}
+%      \setlength\belowdisplayskip{2pt}
+%      \setlength\abovedisplayshortskip{0pt}
+%      \setlength\belowdisplayshortskip{0pt}
+%  }
+%  \renewcommand{\baselinestretch}{0.99}
 
@@
 In addition to algorithms' predictions themselves, Bayesian learning naturally provides the uncertainty estimates of these predictions.
-These uncertainty estimates are vital in spheres that affect people's health, such as self-driving cars or medicine.
+These uncertainty estimates are vital, e.g., in spheres that affect people's health, such as self-driving cars or medicine.
 
 In general, when distributions are included in the network, the complexity of Bayesian inference scales exponentially with the number of layers.
-Thus, it is infeasible to apply conventional Bayesian inference algorithms for deep neural networks.
-Nevertheless, recently several techniques have been proposed to handle specific types of neural networks.
+Nevertheless, recently several techniques have been proposed to handle specific types of neural networks without this exponential growth.
 For example, feed-forward networks with the rectified linear unit nonlinearity~\cite{hernandez2015probabilistic}, networks with discrete distributions~\cite{soudry2014expectation}, recurrent networks~\cite{mcdermott2017bayesian}.
@@
 The distribution of the target vector propagated through a dense layer and the soft thresholding nonlinearity can then be closely approximated with a distribution from the same family.
-Overall, this approach allows to make the Bayesian inference for the sparse coding neural network feasible.
 The proposed method of uncertainty propagation for the soft thresholding nonlinearity allows us to derive the gradients of the logarithms of normalisation constants, which can be used to update a weight distribution.
@@
 \label{sec:nn_sc}
-The sparse coding problem is the linear regression with the assumption of sparse weights
+The neural network approach to sparse coding is based on earlier Iterative Shrinkage and Thresholding Algorithm (\textsc{ista}) \cite{daubechies2004iterative}.
+It addresses the sparse coding problem as the linear regression problem with $l1$ penalty that promotes sparsity.
+For the linear regression model with observations $\mathbf{y} \in \mathbb{R}^K$, the design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$, and the sparse unknown vector of weights $\boldsymbol\beta \in \mathbb{R}^D$, \textsc{ista} minimises the energy function $E(\cdot)$ to find $\boldsymbol\beta$
 \begin{equation}
 \label{eq:regression_problem}
-\mathbf{y} = \mathbf{X}\boldsymbol\beta + \boldsymbol\varepsilon
+E(\mathbf{y}, \boldsymbol\beta) = ||\mathbf{X}\boldsymbol\beta - \mathbf{y}||_2^2 + \alpha ||\boldsymbol\beta||_1,
 \end{equation}
-where $\mathbf{y} \in \mathbb{R}^K$ is the observation, $\mathbf{X} \in \mathbb{R}^{K \times D}$ is the design matrix, $\boldsymbol\beta \in \mathbb{R}^D$ is the unknown vector of weights with many elements $\beta_d$ equal to zero, $\boldsymbol\varepsilon \in \mathbb{R}^K$ is the independent Gaussian noise.
+where $\alpha$ is the parameter that controls the influence of sparse penalty.
 
-One of the popular families of the sparse coding algorithms is the iterative shrinkage algorithms, and notably the Iterative Shrinkage and Thresholding Algorithm (\textsc{ista}) \cite{daubechies2004iterative}.
-It iteratively obtains the new approximation of the coefficient vector $\widehat{\boldsymbol\beta}_l$ at the iteration $l$ as the linear transformation of the input $\mathbf{y}$ with the previous approximation $\widehat{\boldsymbol\beta}_{l-1}$ and then propagates the new approximation through the soft thresholding function $h_\lambda(\cdot)$
+At every iteration $l$, \textsc{ista} obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ of the input $\mathbf{y}$ with the previous estimate and then propagates the result of the linear transformation through the soft thresholding function $h_\lambda(\cdot)$
 \begin{equation}
-h_\lambda(v) = \text{sgn}(v) \max(|v| - \lambda, 0)
+h_\lambda(\mathbf{b}) = \text{sgn}(\mathbf{b}) \max(|\mathbf{b}| - \lambda, 0),
 \end{equation}
 where $\lambda$ is a shrinkage parameter.
-The linear transformation is
-\begin{equation}
-\widehat{\boldsymbol\beta}_l = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}
-\end{equation}
-with weights $\mathbf{W} = \mathbf{X}^\top / E$, where $E$ is the upper bound of the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$, and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$ ($\mathbf{I}_{D \times D}$ is the identity matrix of size $D$).
+In \textsc{ista}, weights of the linear transformation are assumed fixed: $\mathbf{W} = \mathbf{X}^\top / E$, where $E$ is the upper bound of the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$, and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$, where $\mathbf{I}_{D \times D}$ is the identity matrix of size $D$.
 
 The Learned \textsc{ista} (\textsc{lista}) \cite{gregor2010learning} allows to learn the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
-To achieve this, the \textsc{ista} is limited with the fixed amount of iterations, $L$, and interpreted as a recurrent neural network.
+To achieve this, the \textsc{ista} is limited with the fixed amount of iterations $L$, and interpreted as a recurrent neural network: every iteration of \textsc{ista} corresponds to the layer of \textsc{lista}.
 A coefficient vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$ is predicted according to Algorithm~\ref{alg:lista}.
@@
 \begin{algorithm}[h]
-  \caption{\textsc{lista}}
+  \caption{\textsc{lista} forward propagation}
   \label{alg:lista}
   \begin{algorithmic}[1]
-    \STATE Initialisation dense layer $\mathbf{b} \gets \mathbf{W}\mathbf{y}$ \label{eq:first_layer}
-    \STATE Initialisation soft thresholding nonlinearity $\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$ \label{eq:thr_first}
+    \REQUIRE observations $\mathbf{y}$, weights $\mathbf{W}, \mathbf{S}$, number of layers $L$
+    \STATE \textit{Initialisation.} Dense layer $\mathbf{b} \gets \mathbf{W}\mathbf{y}$ \label{eq:first_layer}
+    \STATE \textit{Initialisation.} Soft thresholding nonlinearity $\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$ \label{eq:thr_first}
 		\FOR{$l=1$ \TO $L$}
-			\STATE Main dense layer $\mathbf{c}_l \gets \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ \label{eq:l_dense_layer}
-			\STATE Main soft thresholding nonlinearity $\widehat{\boldsymbol\beta}_{l} \gets h_\lambda(\mathbf{c}_l)$ \label{eq:l_thr}
+			\STATE Dense layer $\mathbf{c}_l \gets \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ \label{eq:l_dense_layer}
+			\STATE Soft thresholding nonlinearity $\widehat{\boldsymbol\beta}_{l} \gets h_\lambda(\mathbf{c}_l)$ \label{eq:l_thr}
 		\ENDFOR
-		\STATE Output $\widehat{\boldsymbol\beta} \gets \widehat{\boldsymbol\beta}_{L}$
+		\RETURN $\widehat{\boldsymbol\beta} \gets \widehat{\boldsymbol\beta}_{L}$
   \end{algorithmic}
@@
 
-Matrices $\mathbf{W}$, $\mathbf{S}$ are the parameters that are initialised as in the \textsc{ista} and then updated with the backpropagation algorithm.
+In \textsc{lista}, matrices $\mathbf{W}$, $\mathbf{S}$ are the parameters that are initialised as in the \textsc{ista} and then updated with the backpropagation algorithm.
 Vectors $\mathbf{c}_l$ and $\mathbf{b}$ are auxiliary vectors that describe forward propagation.
@@
 \label{sec:bayesian_lista}
-
-This section presents the proposed Bayesian neural network for sparse coding. To formulate the Bayesian version of the \textsc{lista} we impose the prior distributions on the unknown weights
+To formulate the Bayesian version of the \textsc{lista} we impose the prior distributions on the unknown weights
 \begin{equation}
@@
 where $\eta$ is the precision of the Gaussian distribution.
-The likelihood of $\mathbf{B}$ is defined as
+
+For every layer of the Bayesian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with spike probability $\boldsymbol\omega$, slab mean $\mathbf{m}$, and slab variance $\mathbf{v}$
+\begin{equation}
+[\widehat{\boldsymbol\beta}_{l-1}]_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d),
+\end{equation}
+where $\delta_0$ is the delta-function that represents a spike, $[\cdot]_d$ denotes the $d$-th component of a vector.
+In Section \ref{sec:fprop}, we show that the output of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with a spike and slab distribution and, therefore, the output of the \textsc{lista} network $\widehat{\boldsymbol\beta}_{L}$ has the spike and slab distribution.
+
+To introduce the uncertainty of predictions, we assume that the true $\boldsymbol\beta$ has a Gaussian distribution centered at the output of the \textsc{lista} network with precision $\gamma$.
+Then the likelihood of $\mathbf{B}$ is defined as
 \begin{equation}
 \label{eq:likelihood}
-p(\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) = \prod_{n=1}^N\prod_{d=1}^D\mathcal{N}(\beta_d^{(n)}; [f(\mathbf{y^{(n)}}; \mathbf{W}, \mathbf{S}, \lambda)]_d, \gamma^{-1}),
+p(\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) = \prod_{n=1}^N\prod_{d=1}^D\mathcal{N}\left(\beta_d^{(n)}; \left[\widehat{\boldsymbol\beta}_{L}^{(n)}\right]_d, \gamma^{-1}\right)
 \end{equation}
-where $[\cdot]_d$ denotes the d-th component of a vector, $f(\mathbf{y}^{(n)}; \mathbf{W}, \mathbf{S}, \lambda)$ is the output of the Bayesian \textsc{lista} neural network, $\gamma$ is the precision of the Gaussian distribution.
-The prior of the introduced Gaussian precisions are set to the Gamma distribution with parameters~$a^{\cdot}$ and~$b^{\cdot}$:
+The introduced Gaussian precisions have Gamma prior distributions with parameters~$a^{\cdot}$ and~$b^{\cdot}$
 \begin{equation}
@@
 \label{sec:fprop}
-For every layer of the Bayesian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with parameters: $\boldsymbol\omega$ is a probability of a spike, $\mathbf{m}$ is a mean of a slab Gaussian distribution, and $\mathbf{v}$ is a variance of the slab distribution:
-\begin{equation}
-[\widehat{\boldsymbol\beta}_{l-1}]_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d),
-\end{equation}
-where $\delta_0$ is the delta-function that represents a spike.
+We demonstrate that the output of every \textsc{lista} layer $\widehat{\boldsymbol\beta}_l$ can be approximated with a spike and slab distribution.
+This leads to the proposed probabilistic backpropagation algorithm that is presented in Section~\ref{sec:backpropagation}.
 
-Later in this section, we show that the output $\widehat{\boldsymbol\beta}_l$ of the next layer can be approximated with a spike and slab distribution and, therefore, it maintains the same family of distributions.
-This leads to the proposed probabilistic backpropagation algorithm that is presented in Section~\ref{sec:backpropagation}.
-We now describe how to propagate uncertainty through the layers of the Bayesian \textsc{lista} step by step.
-
-\subsection{Initialisation dense layer}
-At step \ref{eq:first_layer} in the Bayesian \textsc{lista} (Algorithm~\ref{alg:lista}) the matrix $\mathbf{W}$ consists of Gaussian-distributed components: $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y}$ is a deterministic vector.
+\subsection{Initialisation}
+At step \ref{eq:first_layer} of the \textsc{lista} (Algorithm~\ref{alg:lista}) the matrix $\mathbf{W}$ consists of Gaussian-distributed components $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y}$ is a deterministic vector.
 Since the sum of independent Gaussian-distributed variables is a Gaussian variable~\cite{eisenberg2008sum}, $\mathbf{b}$ is a vector of Gaussian-distributed components $b_d \sim \mathcal{N}(m^b_d, v^b_d)$
@@
 
-\subsection{Soft thresholding nonlinearity}
-At step~\ref{eq:thr_first} of the Bayesian \textsc{lista} (Algorithm~\ref{alg:lista}) the Gaussian vector $\mathbf{b}$ is taken as an input of the soft thresholding function.
+At step~\ref{eq:thr_first} of the \textsc{lista} (Algorithm~\ref{alg:lista}) the Gaussian vector $\mathbf{b}$ is taken as an input of the soft thresholding function.
 
-When a Gaussian random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft thresholding function: $x^* = h_{\lambda}(x)$, the probability mass of the resulting random variable $x^*$ is split into two parts.
+When a Gaussian random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft thresholding function $x^* = h_{\lambda}(x)$, the probability mass of the resulting random variable $x^*$ is split into two parts.
 The values of $x$ from the interval $[-\lambda, \lambda]$ are converted to~$0$ by the soft thresholding operator.
@@
 The proof of Lemma~\ref{thm:soft_thresholding} and expressions for $\omega^*$, $m^*$ and $v^*$ are given in the supplementary materials.
-Based on the results of Lemma~\ref{thm:soft_thresholding} we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ at step~\ref{eq:thr_first} with a spike and slab distribution with parameters derived in the lemma: the spike probability $\omega$ is equal to $\omega^*$, the slab mean $m$ and variance $v$ are set to the corresponding parameters of the truncated Gaussian $m^*$ and $v^*$.
+Based on the results of Lemma~\ref{thm:soft_thresholding}, we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ at step~\ref{eq:thr_first} with a spike and slab distribution with parameters derived in the lemma: the spike probability $\omega$ is equal to $\omega^*$, the slab mean $m$ and variance $v$ are set to the corresponding parameters of the truncated Gaussian $m^*$ and $v^*$.
 The quality of this approximation is discussed in the supplementary materials.
@@
 \subsection{Main layers}
-The distributions of the inputs at step \ref{eq:l_dense_layer} of the Bayesian \textsc{lista} (Algorithm~\ref{alg:lista}) for each $l$ are: the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
+At step \ref{eq:l_dense_layer} of the \textsc{lista} (Algorithm~\ref{alg:lista}) the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
 In order to determine the distribution of the output $\mathbf{c}_l$ we first formulate two lemmas.
@@
   \label{thm:matrix_vector}
-Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta }\in \mathbb{R}^D$ be a vector with spike-and-slab distributed variables: $\widehat{\beta}_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
-The components of the matrix $\mathbf{S}$ and the vector $\widehat{\boldsymbol\beta}$ are mutual independent.
+Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta }\in \mathbb{R}^D$ be a vector with spike-and-slab-distributed variables: $\widehat{\beta}_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
+The components of the matrix $\mathbf{S}$ and the vector $\widehat{\boldsymbol\beta}$ are mutually independent.
 Let $\mathbf{e} \in \mathbb{R}^{D}$ denote the product $\mathbf{S} \widehat{\boldsymbol\beta}$.

### 2018-05-17 paper/BayesianLISTA.tex
updated second part

@@
 We then describe uncertainty propagation to obtain the spike and slab distribution for an output of a network in section \ref{sec:fprop} and how probabilistic backpropagation is organised to update distributions of weights in section \ref{sec:backpropagation}.
-After that, we show the experimental results of the algorithm in section \ref{sec:experiments} and finish with discussion and conclusions in sections \ref{sec:discussion} and \ref{sec:conclusions}.
+After that, we show the experimental results of the algorithm in section \ref{sec:experiments} and finish with discussion and conclusions in section \ref{sec:conclusions}.
 
@@
 
-At every iteration $l$, \textsc{ista} obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ of the input $\mathbf{y}$ with the previous estimate and then propagates the result of the linear transformation through the soft thresholding function $h_\lambda(\cdot)$
+At every iteration $l$, \textsc{ista} obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ of the input $\mathbf{y}$ with the previous estimate propagated through the soft thresholding function $h_\lambda(\cdot)$
 \begin{equation}
@@
 where $\delta_0$ is the delta-function that represents a spike, $[\cdot]_d$ denotes the $d$-th component of a vector.
-In Section \ref{sec:fprop}, we show that the output of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with a spike and slab distribution and, therefore, the output of the \textsc{lista} network $\widehat{\boldsymbol\beta}_{L}$ has the spike and slab distribution.
+In Section \ref{sec:fprop}, we show that the output of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with a spike and slab distribution and, therefore, the output of the \textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
 
@@
 
-For Bayesian inference we expand the probabilistic backpropagation algorithm~\cite{hernandez2015probabilistic} for computing parameter updates.
-It is based on assumed density filtering (ADF) and expectation propagation (EP) and allows to update parameters of the distributions based on the derivatives of the logarithm of a normalisation constant.
-ADF iteratively incorporates factors from the true posterior $p$ (\ref{eq:posterior}) into the factorised approximating distribution $q$ (\ref{eq:approximating_dsitribution}), whereas in EP factors in the $q$ are iteratively replaced by factors from $p$.
+For Bayesian inference we expand the probabilistic backpropagation algorithm~\cite{hernandez2015probabilistic} for updating parameters of distributions.
+They are updated with assumed density filtering (ADF) and expectation propagation (EP) algorithms based on the derivatives of the logarithm of a normalisation constant.
+ADF iteratively incorporates factors from the true posterior $p$ in (\ref{eq:posterior}) into the factorised approximating distribution $q$ in (\ref{eq:approximating_dsitribution}), whereas EP iteratively replaces factors in $q$ by factors from $p$.
 
-When a factor from $p$ is incorporated into $q$, $q$ as a function of weights $\mathbf{W}$ and $\mathbf{S}$ has the form:
+When a factor from $p$ is incorporated into $q$, $q$ as a function of weights $\mathbf{W}$ and $\mathbf{S}$ has the form
 \begin{equation}
@@
 The normalisation constant of the approximating distribution $q$ with the likelihood term for the data point $n$ incorporated can be computed as follows (to simplify notation the superscript $(n)$ is omitted)
-\begin{align}
-Z & = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta \nonumber\\
+\begin{equation}
+Z  = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; \widehat{\boldsymbol\beta}_{L}, \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
+\end{equation}
+Assuming the spike and slab distribution for $\widehat{\boldsymbol\beta}$, the normalisation constant can be approximated as \footnote{full derivation of the normalisation constant is given in supplementary materials}
+\begin{equation}
 \label{eq:Z}
-& \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right].
-\end{align}
+Z \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right].
+\end{equation}
 Parameters of the approximating posterior distribution are then updated with the derivatives of this normalisation constant according to (\ref{eq:param_update}).
@@
 We set the number of iterations in these algorithms and the number of layers in the Bayesian and classical \textsc{lista} networks to $L$.
-To measure the performance of the algorithms the normalised mean square error (\textsc{nmse}) and F measure are used.
+To measure the performance of the algorithms the normalised mean square error (\textsc{nmse}) and F measure are used\footnote{\textsc{nmse} and F measure are defined in supplementary materials}.
 We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for the \textsc{lista} to learn.
@@
 First, the predictive performance of the proposed Bayesian \textsc{lista} is analysed on synthetic data.
-We generate $N_\text{train}=1000$ and $N_{\text{test}} = 100$ sparse coefficients vectors $\boldsymbol\beta^{(n)}$ each of size $D = 100$.
-Coefficients $\boldsymbol\beta^{(n)}$ are generated from the spike and slab distribution with the truncated slab: each component $\beta^{(n)}_{d}$ is zero with the probability $0.8$ or is from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability $0.2$.
+We generate $N_\text{train}=1000$ and $N_{\text{test}} = 100$ sparse coefficient vectors $\boldsymbol\beta^{(n)}$ of size $D = 100$  from the spike and slab distribution with the truncated slab: each component $\beta^{(n)}_{d}$ is zero with probability $0.8$ or is sampled from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with probability $0.2$.
 To simulate sparse observations, we generate the random Gaussian design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$.
@@
 The Bayesian \textsc{lista} outperforms the \textsc{lista} in terms of both measures.
-Although the baselines \textsc{ista} and \textsc{fista} show better performance in terms of F measure, the Bayesian \textsc{lista} has the lowest \textsc{nmse}.
+Although the baseline \textsc{ista} and \textsc{fista} show better performance in terms of F measure, the Bayesian \textsc{lista} has the lowest \textsc{nmse}.
 
@@
 \subsection{Predictive performance on \textsc{mnist} data}
-Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \cite{lecun1998gradient}.
+In this experiment we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \cite{lecun1998gradient}.
 The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
@@
 The resulting size of $\mathbf{X}$ is $K \times 784$.
-Then we generate observations as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta \in \mathbb{R}^{784}$ are flatten images.
+Then we generate observations as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta \in \mathbb{R}^{784}$ are flattened images.
 We use $100$ images for training and $100$ for test.
@@
 
-Figure \ref{fig:mnist} present quality on the validation set with observation sizes $100$ and $250$.
+Figure \ref{fig:mnist} presents quality results on the validation set with observation sizes $100$ and $250$.
 The experiment with $K=100$ presents severe conditions for the algorithms: the very limited size of the training dataset combined with the small dimensionality of observations.
 The Bayesian \textsc{lista} is able to learn under these conditions, outperforming the \textsc{lista} that demonstrates poor results.
-Under better conditions of the second experiment with $K=250$ both \textsc{lista} networks converge to the similar results.
+Under better conditions of the second experiment with $K=250$, both \textsc{lista} networks converge to the similar results.
 However, the Bayesian \textsc{lista} demonstrates remarkably better convergence rate.
@@
 \subsection{Active learning}
-To demonstrate a potential scenario that can benefit from uncertainty estimates of the Bayesian \textsc{lista} we consider the active learning example \cite{settles.tr09}.
+To demonstrate a potential scenario that can benefit from uncertainty estimates of the Bayesian \textsc{lista}, we consider the active learning example \cite{settles.tr09}.
 The active learning area researches ways to select new training subsets to reduce the total number of required supervision.
-One of the popular approaches in active learning is uncertainty sampling when the data with the least certain predictions is chosen to obtain a new label at.
-Uncertainty is usually measured with entropy.
-In our case of the spike and slab distributed data points there is no closed form for entropy.
-Therefore, we use a variance from Lemma~\ref{thm:moments_spsl} as a measure of uncertainty.
+One of the popular approaches in active learning is uncertainty sampling, when the data with the least certain predictions is chosen for labelling.
+We use a variance from Lemma~\ref{thm:moments_spsl} as a measure of uncertainty.
 
@@
 
-\section{Discussion}
-\label{sec:discussion}
+\section{Conclusions and future work}
+\label{sec:conclusions}
 To the best of our knowledge, this is the first implementation of a Bayesian deep sparse coding algorithm.
@@
 
-\section{Conclusions and future work}
-\label{sec:conclusions}
 We have presented the new method for propagating uncertainty through the soft thresholding function. %To achieve this goal
@@
 For this we will extend both the uncertainty propagation method to include uncertainty of $\lambda$ and the probabilistic backpropagation algorithm to estimate its posterior.
-We will study stochastic expectation propagation applicability in order to replace ADF that may further improve the quality of posterior estimates~\cite{li2015stochastic}.
 

### 2018-05-17 paper/BayesianLISTA.tex
small text fix

@@
 \label{eq:likelihood}
-p(\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) = \prod_{n=1}^N\prod_{d=1}^D\mathcal{N}\left(\beta_d^{(n)}; \left[\widehat{\boldsymbol\beta}_{L}^{(n)}\right]_d, \gamma^{-1}\right)
+p(\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) = \prod_{n=1}^N\prod_{d=1}^D\mathcal{N}\left(\beta_d^{(n)}; \left[\widehat{\boldsymbol\beta}^{(n)}\right]_d, \gamma^{-1}\right)
 \end{equation}
@@
 \begin{equation}
-Z  = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; \widehat{\boldsymbol\beta}_{L}, \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
+Z  = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; \widehat{\boldsymbol\beta}, \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
 \end{equation}
@@
 \label{eq:Z}
-Z \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right].
+Z \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right],
 \end{equation}
-Parameters of the approximating posterior distribution are then updated with the derivatives of this normalisation constant according to (\ref{eq:param_update}).
+where $\{\omega^{\widehat{\boldsymbol\beta}}_d, m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\}$ are the parameters of the spike and slab distribution for $\widehat{\boldsymbol\beta}_d$.
+Parameters of the approximating posterior distribution $q$ are then updated with the derivatives of this normalisation constant according to (\ref{eq:param_update}).
 

### 2018-05-17 paper/BayesianLISTA.tex
small text fix

@@
 \label{eq:likelihood}
-p(\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) = \prod_{n=1}^N\prod_{d=1}^D\mathcal{N}\left(\beta_d^{(n)}; \left[\widehat{\boldsymbol\beta}^{(n)}\right]_d, \gamma^{-1}\right)
+p(\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) = \prod_{n=1}^N\prod_{d=1}^D\mathcal{N}\left(\beta_d^{(n)}; [\widehat{\boldsymbol\beta}^{(n)}]_d, \gamma^{-1}\right)
 \end{equation}
@@
 \end{equation}
-Assuming the spike and slab distribution for $\widehat{\boldsymbol\beta}$, the normalisation constant can be approximated as \footnote{full derivation of the normalisation constant is given in supplementary materials}
+Assuming the spike and slab distribution for $\widehat{\boldsymbol\beta}$, the normalisation constant can be approximated as \footnote{Full derivation of the normalisation constant is given in supplementary materials.}
 \begin{equation}
@@
 \end{equation}
-where $\{\omega^{\widehat{\boldsymbol\beta}}_d, m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\}$ are the parameters of the spike and slab distribution for $\widehat{\boldsymbol\beta}_d$.
+where $\{\omega^{\widehat{\boldsymbol\beta}}_d, m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\}$ are the parameters of the spike and slab distribution for $[\widehat{\boldsymbol\beta}]_d$.
 Parameters of the approximating posterior distribution $q$ are then updated with the derivatives of this normalisation constant according to (\ref{eq:param_update}).
@@
 We set the number of iterations in these algorithms and the number of layers in the Bayesian and classical \textsc{lista} networks to $L$.
-To measure the performance of the algorithms the normalised mean square error (\textsc{nmse}) and F measure are used\footnote{\textsc{nmse} and F measure are defined in supplementary materials}.
+To measure the performance of the algorithms the normalised mean square error (\textsc{nmse}) and F measure are used\footnote{\textsc{nmse} and F measure are defined in supplementary materials.}.
 We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for the \textsc{lista} to learn.

### 2018-05-17 paper/BayesianLISTA.tex
paper. abstract and introduction

@@
 \begin{abstract}
+Despite the recent overwhelming success of deep learning uncertainty estimation is still a challenge for most modern deep learning methods.
 The Bayesian learning allows to estimate the uncertainty of predictions in neural networks by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
@@
 There are currently two approaches in Bayesian neural networks: explicit distributions of weights can be included in a network \cite{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing uncertainty \cite{gal2016dropout}.
-In this paper we use the former approach and impose prior distributions on the neural network's weights to obtain the posterior distributions of weights and posterior predictive distributions of target variables.
+We use the former approach and impose prior distributions on the neural network's weights to obtain the posterior distributions of weights and posterior predictive distributions of target variables.
 
@@
 The sparse coding problem can be viewed as a linear regression problem with the additional assumption that the majority of the basis representation coefficients should be zeros.
-This sparsity assumption may be represented as $l1$ penalty~\cite{tibshirani1996regression}, or, in Bayesian interpretation, as prior that has sharp peak at zero~\cite{tipping2001sparse}.
-One of the modern approaches for the sparse coding problem utilises neural networks with soft thresholding nonlinearity~\cite{gregor2010learning, sprechmann2015learning}.
+This sparsity assumption may be represented as $l1$ penalty~\cite{tibshirani1996regression}, or, in Bayesian interpretation, as a prior that has a sharp peak at zero~\cite{tipping2001sparse}.
+One of the modern approaches for sparse coding utilises neural networks with the soft thresholding nonlinearity~\cite{gregor2010learning, sprechmann2015learning}.
 At every layer this nonlinearity shifts current estimates of the target vectors towards zero, which allows to achieve sparsity of the target vectors.
-Such problems arise in different applications, such as compressive sensing~\cite{candes2008introduction}, image and video processing~\cite{mairal2014sparse, wang2015deep}, neuroscience~\cite{baillet1997bayesian, jas2017learning}.
+Sparse coding is widely used in different applications, such as compressive sensing~\cite{candes2008introduction}, image and video processing~\cite{mairal2014sparse, wang2015deep}, neuroscience~\cite{baillet1997bayesian, jas2017learning}.
 

### 2018-05-17 paper/BayesianLISTA.tex
paper further read

@@
 
-In this paper we propose a method to propagate uncertainty through the soft thresholding nonlinearity.
+In this paper, we propose a method to propagate uncertainty through the soft thresholding nonlinearity.
 At every layer the current distribution of the target vector is represented as a spike and slab distribution \cite{mitchell1988bayesian}, which represents the probabilities of each variable being zero, or Gaussian-distributed.
@@
 
-The paper is organised as following: first, we review neural networks for sparse coding in section \ref{sec:nn_sc} and present a novel Bayesian neural network in section \ref{sec:bayesian_lista}.
+We introduce a novel Bayesian neural network in section \ref{sec:bayesian_lista} after reviewing neural networks for sparse coding in section \ref{sec:nn_sc}.
+The proposed forward uncertainty propagation and probabilistic backpropagation methods are given in sections \ref{sec:fprop} and \ref{sec:backpropagation}.
+We show the experimental results in section \ref{sec:experiments} and finish with discussion and conclusions in section \ref{sec:conclusions}.
+
+%The paper is organised as following: first, we review neural networks for sparse coding in section \ref{sec:nn_sc} and present a novel Bayesian neural network in section \ref{sec:bayesian_lista}.
 We then describe uncertainty propagation to obtain the spike and slab distribution for an output of a network in section \ref{sec:fprop} and how probabilistic backpropagation is organised to update distributions of weights in section \ref{sec:backpropagation}.
@@
 The neural network approach to sparse coding is based on earlier Iterative Shrinkage and Thresholding Algorithm (\textsc{ista}) \cite{daubechies2004iterative}.
-It addresses the sparse coding problem as the linear regression problem with $l1$ penalty that promotes sparsity.
+It addresses the sparse coding problem as the linear regression problem with the $l1$ penalty that promotes sparsity.
 For the linear regression model with observations $\mathbf{y} \in \mathbb{R}^K$, the design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$, and the sparse unknown vector of weights $\boldsymbol\beta \in \mathbb{R}^D$, \textsc{ista} minimises the energy function $E(\cdot)$ to find $\boldsymbol\beta$
@@
 \end{equation}
-where $\alpha$ is the parameter that controls the influence of sparse penalty.
+where $\alpha$ is the parameter that controls the influence of the sparse penalty.
 
-At every iteration $l$, \textsc{ista} obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ of the input $\mathbf{y}$ with the previous estimate propagated through the soft thresholding function $h_\lambda(\cdot)$
+At every iteration $l$, \textsc{ista} obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ that is propagated through the soft thresholding function $h_\lambda(\cdot)$
 \begin{equation}
@@
 
-The Learned \textsc{ista} (\textsc{lista}) \cite{gregor2010learning} allows to learn the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
-To achieve this, the \textsc{ista} is limited with the fixed amount of iterations $L$, and interpreted as a recurrent neural network: every iteration of \textsc{ista} corresponds to the layer of \textsc{lista}.
+In contrast to \textsc{ista}, Learned \textsc{ista} (\textsc{lista}) \cite{gregor2010learning} learns the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
+To achieve this, the \textsc{ista} is limited with the fixed amount of iterations $L$, and interpreted as a recurrent neural network: every iteration $l$ of \textsc{ista} corresponds to the layer $l$ of \textsc{lista}.
 A coefficient vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$ is predicted according to Algorithm~\ref{alg:lista}.
@@
 \label{sec:bayesian_lista}
-To formulate the Bayesian version of the \textsc{lista} we impose the prior distributions on the unknown weights
+To formulate the Bayesian version of \textsc{lista} we impose the prior distributions on the unknown weights
 \begin{equation}
@@
 
-For every layer of the Bayesian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l-1}$ has the spike and slab distribution with spike probability $\boldsymbol\omega$, slab mean $\mathbf{m}$, and slab variance $\mathbf{v}$
+For every layer $l$ of Bayesian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l}$ has the spike and slab distribution with the spike probability $\boldsymbol\omega$, the slab mean $\mathbf{m}$, and the slab variance $\mathbf{v}$
 \begin{equation}
-[\widehat{\boldsymbol\beta}_{l-1}]_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d),
+[\widehat{\boldsymbol\beta}_{l}]_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d),
 \end{equation}
 where $\delta_0$ is the delta-function that represents a spike, $[\cdot]_d$ denotes the $d$-th component of a vector.
-In Section \ref{sec:fprop}, we show that the output of the next layer $\widehat{\boldsymbol\beta}_l$ can be approximated with a spike and slab distribution and, therefore, the output of the \textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
+In section \ref{sec:fprop}, we show that the output of the next layer $\widehat{\boldsymbol\beta}_{l+1}$ can be approximated with a spike and slab distribution and, therefore, the output of the Bayesian \textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
 
-To introduce the uncertainty of predictions, we assume that the true $\boldsymbol\beta$ has a Gaussian distribution centered at the output of the \textsc{lista} network with precision $\gamma$.
+To introduce the uncertainty of predictions, we assume that the true $\boldsymbol\beta$ has a Gaussian distribution centered at the output of the Bayesian \textsc{lista} network with precision $\gamma$.
 Then the likelihood of $\mathbf{B}$ is defined as
@@
 \end{equation}
-The introduced Gaussian precisions have Gamma prior distributions with parameters~$a^{\cdot}$ and~$b^{\cdot}$
+We specify Gamma prior distributions with parameters~$a^{\cdot}$ and~$b^{\cdot}$ on the introduced Gaussian precisions 
 \begin{equation}
@@
 \label{sec:fprop}
-We demonstrate that the output of every \textsc{lista} layer $\widehat{\boldsymbol\beta}_l$ can be approximated with a spike and slab distribution.
-This leads to the proposed probabilistic backpropagation algorithm that is presented in Section~\ref{sec:backpropagation}.
+We modify \textsc{lista} forward propagation (Algorithm~\ref{alg:lista}) to include probability distributions of the random variables introduced in section~\ref{sec:bayesian_lista}.
+We demonstrate that the output of every Bayesian \textsc{lista} layer $\widehat{\boldsymbol\beta}_l$ can be closely approximated with a spike and slab distribution.
+This leads to the proposed probabilistic backpropagation algorithm that is presented in section~\ref{sec:backpropagation}.
 
 \subsection{Initialisation}
-At step \ref{eq:first_layer} of the \textsc{lista} (Algorithm~\ref{alg:lista}) the matrix $\mathbf{W}$ consists of Gaussian-distributed components $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y}$ is a deterministic vector.
+At step \ref{eq:first_layer} of \textsc{lista} (Algorithm~\ref{alg:lista}) the matrix $\mathbf{W}$ consists of Gaussian-distributed components $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y}$ is a deterministic vector.
 Since the sum of independent Gaussian-distributed variables is a Gaussian variable~\cite{eisenberg2008sum}, $\mathbf{b}$ is a vector of Gaussian-distributed components $b_d \sim \mathcal{N}(m^b_d, v^b_d)$
@@
 
-At step~\ref{eq:thr_first} of the \textsc{lista} (Algorithm~\ref{alg:lista}) the Gaussian vector $\mathbf{b}$ is taken as an input of the soft thresholding function.
+At step~\ref{eq:thr_first} of \textsc{lista} (Algorithm~\ref{alg:lista}) the Gaussian vector $\mathbf{b}$ is taken as an input of the soft thresholding function.
 
@@
 \subsection{Main layers}
-At step \ref{eq:l_dense_layer} of the \textsc{lista} (Algorithm~\ref{alg:lista}) the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
+At step \ref{eq:l_dense_layer} of \textsc{lista} (Algorithm~\ref{alg:lista}) the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
 In order to determine the distribution of the output $\mathbf{c}_l$ we first formulate two lemmas.
@@
 Let $\mathbf{e} \in \mathbb{R}^{D}$ denote the product $\mathbf{S} \widehat{\boldsymbol\beta}$.
-Then the marginal mean and variance of the elements $e_d$ of the vector $\mathbf{e}$ are:
+Then the marginal mean and variance of the elements $e_d$ of the vector $\mathbf{e}$ are
 \begin{subequations}
@@
 
-Let $\mathbf{e}_l$ denote the product $\mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at step \ref{eq:l_dense_layer} of the Bayesian \textsc{lista}.
+Let $\mathbf{e}_l$ denote the product $\mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at step \ref{eq:l_dense_layer} of \textsc{lista}.
 We assume that $\mathbf{S}$ and $\widehat{\boldsymbol\beta}_{l-1}$ are mutually independent.
@@
 
-Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of the Bayesian \textsc{lista} (Algorithm~\ref{alg:lista}) is the result of soft thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first}.
+Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of \textsc{lista} (Algorithm~\ref{alg:lista}) is the result of soft thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first}.
 
 \subsection{Bayesian \textsc{lista} forward propagation}
-We have covered all steps of the Bayesian \textsc{lista} and derived distributions for outputs of these steps.
+We have covered all steps of Bayesian \textsc{lista} and derived distributions for outputs of these steps.
 Now we can formulate the main result of this section that describes how the proposed uncertainty propagation scheme works.
@@
 For Bayesian inference we expand the probabilistic backpropagation algorithm~\cite{hernandez2015probabilistic} for updating parameters of distributions.
-They are updated with assumed density filtering (ADF) and expectation propagation (EP) algorithms based on the derivatives of the logarithm of a normalisation constant.
+They are updated with the assumed density filtering (ADF) and expectation propagation (EP) algorithms based on the derivatives of the logarithm of a normalisation constant.
 ADF iteratively incorporates factors from the true posterior $p$ in (\ref{eq:posterior}) into the factorised approximating distribution $q$ in (\ref{eq:approximating_dsitribution}), whereas EP iteratively replaces factors in $q$ by factors from $p$.
@@
 \end{equation}
-Assuming the spike and slab distribution for $\widehat{\boldsymbol\beta}$, the normalisation constant can be approximated as \footnote{Full derivation of the normalisation constant is given in supplementary materials.}
+Assuming the spike and slab distribution for $\widehat{\boldsymbol\beta}$, the normalisation constant can be approximated as \footnote{Full derivation of the normalisation constant is given in the supplementary materials.}
 \begin{equation}
@@
 
-Prior factors from $p$ (\ref{eq:ws}), (\ref{eq:gamma_eta}) are incorporated into $q$ with the EP algorithm~\cite{hernandez2015probabilistic}, i.e.
-they replace the corresponding approximating factors from $q$ and then $q$ is updated to minimise the KL divergence.
+Prior factors (\ref{eq:ws}), (\ref{eq:gamma_eta}) from $p$ are incorporated into $q$ with the EP algorithm~\cite{hernandez2015probabilistic}, i.e.
+they replace the corresponding approximating factors from $q$, and then $q$ is updated to minimise the KL divergence.
 
@@
 \label{sec:experiments}
-The proposed Bayesian \textsc{lista} is evaluated in the context of the sparse coding problem with an overcomplete dictionary, where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
+The proposed Bayesian \textsc{lista} model is evaluated in the context of the sparse coding problem with an overcomplete dictionary, where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
 
-We compare the proposed Bayesian \textsc{lista} with the classical \textsc{lista}~\cite{gregor2010learning} in terms of the predictive accuracy.
-As baselines we also use the \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
-The \textsc{fista} adds the momentum to the \textsc{ista} and improves its convergence speed.
-We set the number of iterations in these algorithms and the number of layers in the Bayesian and classical \textsc{lista} networks to $L$.
-To measure the performance of the algorithms the normalised mean square error (\textsc{nmse}) and F measure are used\footnote{\textsc{nmse} and F measure are defined in supplementary materials.}.
-We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for the \textsc{lista} to learn.
+We compare Bayesian \textsc{lista} with \textsc{lista}~\cite{gregor2010learning} in terms of predictive accuracy.
+As baselines we also use \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
+\textsc{fista} adds the momentum to the \textsc{ista} and improves its convergence speed.
+We set the number of iterations in these algorithms and the number of layers in Bayesian and classic \textsc{lista} networks to $L$.
+To measure the performance of the algorithms the normalised mean square error (\textsc{nmse}) and F measure are used\footnote{\textsc{nmse} and F measure are defined in the supplementary materials.}.
+We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn.
 
-\begin{figure}[t!]
+\subsection{Predictive performance on synthetic data}
+First, the predictive performance of Bayesian \textsc{lista} is analysed on synthetic data.
+We generate $N_\text{train}=1000$ and $N_{\text{test}} = 100$ sparse coefficient vectors $\boldsymbol\beta^{(n)}$ of size $D = 100$  from the spike and slab distribution with the truncated slab: each component $\beta^{(n)}_{d}$ is zero with the probability~$0.8$ or is sampled from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability~$0.2$.
+To simulate observations $\mathbf{y}^{(n)}$, we generate the random Gaussian design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$.
+The observations are generated according to (\ref{eq:regression_problem}) with the zero-mean Gaussian noise with the standard deviation $0.5$.
+The shrinkage parameter is set to~$\lambda = 0.1$.
+We train the algorithms using the training data of size $N_\text{train}$ and measure performance on the test data of size $N_{\text{test}}$.
+
+In Figures \ref{fig:nmse_n_layers_synthetic} and \ref{fig:f_meas_n_layers_synthetic} predictive performance for different number of layers $L$ is presented.
+The observation size is set to $K=50$.
+Bayesian \textsc{lista} outperforms \textsc{lista} in terms of both measures.
+Although the baselines \textsc{ista} and \textsc{fista} show better performance in terms of F measure, Bayesian \textsc{lista} has the lowest \textsc{nmse}.
+
+\begin{figure}[h]
 \centering
@@
 
-\subsection{Predictive performance on synthetic data}
-First, the predictive performance of the proposed Bayesian \textsc{lista} is analysed on synthetic data.
-We generate $N_\text{train}=1000$ and $N_{\text{test}} = 100$ sparse coefficient vectors $\boldsymbol\beta^{(n)}$ of size $D = 100$  from the spike and slab distribution with the truncated slab: each component $\beta^{(n)}_{d}$ is zero with probability $0.8$ or is sampled from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with probability $0.2$.
-To simulate sparse observations, we generate the random Gaussian design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$.
-The observations are generated according to (\ref{eq:regression_problem}) with the zero-mean Gaussian noise with the standard deviation $0.5$.
-The shrinkage parameter is set to~$\lambda = 0.1$.
-We train the algorithms using the training data of size $N_\text{train}$ and measure performance on the test data of size $N_{\text{test}}$.
-
-In Figures \ref{fig:nmse_n_layers_synthetic} and \ref{fig:f_meas_n_layers_synthetic} predictive performance for different number of layers $L$ is presented.
-The observation size is set to $K=50$.
-The Bayesian \textsc{lista} outperforms the \textsc{lista} in terms of both measures.
-Although the baseline \textsc{ista} and \textsc{fista} show better performance in terms of F measure, the Bayesian \textsc{lista} has the lowest \textsc{nmse}.
-
 Figures~\ref{fig:nmse_undersampling_synthetic} and~\ref{fig:f_meas_undesampling_synthetic} give the results of predictive performance for different observation sizes $K$.
 The number of layers is set as $L=4$.
-In the previous experiment the Bayesian and classical \textsc{lista} show similar results with this number of layers.
+In the previous experiment, Bayesian and classic \textsc{lista} show similar results with this number of layers.
 The results of Figures~\ref{fig:nmse_undersampling_synthetic} and~\ref{fig:f_meas_undesampling_synthetic} confirm this competitive behaviour between two \textsc{lista} networks.
 Baselines show similar results in terms of F measure and underperform in terms of \textsc{nmse}.
-Overall, the experiments on the synthetic data demonstrate that the Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
+Overall, the experiments on the synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
 
@@
 \subsection{Predictive performance on \textsc{mnist} data}
-In this experiment we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \cite{lecun1998gradient}.
+In this experiment we evaluate Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \cite{lecun1998gradient}.
 The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
@@
 
-Figure \ref{fig:mnist} presents quality results on the validation set with observation sizes $100$ and $250$.
+Figure \ref{fig:mnist} presents quality results on the test set with observation sizes $100$ and $250$.
 The experiment with $K=100$ presents severe conditions for the algorithms: the very limited size of the training dataset combined with the small dimensionality of observations.
-The Bayesian \textsc{lista} is able to learn under these conditions, outperforming the \textsc{lista} that demonstrates poor results.
+Bayesian \textsc{lista} is able to learn under these conditions, outperforming \textsc{lista} that demonstrates poor results.
 Under better conditions of the second experiment with $K=250$, both \textsc{lista} networks converge to the similar results.
-However, the Bayesian \textsc{lista} demonstrates remarkably better convergence rate.
+However, Bayesian \textsc{lista} demonstrates remarkably better convergence rate.
 Both baselines are unable to perform well in these experiments.
@@
 
-\begin{figure}[h]
+\begin{figure}[t!]
 \centering
@@
 \subsection{Active learning}
-To demonstrate a potential scenario that can benefit from uncertainty estimates of the Bayesian \textsc{lista}, we consider the active learning example \cite{settles.tr09}.
+To demonstrate a potential scenario that can benefit from uncertainty estimates of Bayesian \textsc{lista}, we consider the active learning example \cite{settles.tr09}.
 The active learning area researches ways to select new training subsets to reduce the total number of required supervision.
@@
 
-Figure \ref{fig:active_learning_mnist} demonstrates performance of the active and non-active methods of updates with the Bayesian \textsc{lista}.
+Figure \ref{fig:active_learning_mnist} demonstrates performance of the active and non-active methods of updates with Bayesian \textsc{lista}.
 The active approach with uncertainty sampling steadily demonstrates better results in terms of both quality measures.
-This means that the posterior distribution learnt by the Bayesian \textsc{lista} is an adequate estimate of the true posterior.
+This means that the posterior distribution learnt by Bayesian \textsc{lista} is an adequate estimate of the true posterior.
 \begin{figure}[h]
@@
 To the best of our knowledge, this is the first implementation of a Bayesian deep sparse coding algorithm.
-Although there are works on Bayesian sparsity in context of neural networks \cite{he2017bayesian}, they are not the Bayesian neural networks in the same sense as the Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
+Although there are works on Bayesian sparsity in context of neural networks \cite{he2017bayesian}, they are not the Bayesian neural networks in the same sense as Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
 We find not only correct predictions but also useful posterior estimates for the predictions.
@@
 This allowed us to propose the Bayesian \textsc{lista} network and efficient inference algorithm that learns the distributions of the weights and makes the uncertainty estimates of the outputs.
-The forward propagation in the algorithm is based on the proposed uncertainty propagation method, the backward propagation is based on the probabilistic backpropagation method, that was remarkably expanded to account for multidimensionality of inputs and outputs, likelihood of the Bayesian \textsc{lista} and its recurrent nature.
+The forward propagation in the algorithm is based on the proposed uncertainty propagation method, the backward propagation is based on the probabilistic backpropagation method, that was remarkably expanded to account for multidimensionality of inputs and outputs, likelihood of Bayesian \textsc{lista} and its recurrent nature.
 
 Experiments on the synthetic and \textsc{mnist} datasets demonstrate that the proposed algorithm preserves the predictive accuracy of non-Bayesian methods while also providing posterior estimates.
-We also show that when the training data is very small the proposed algorithm significantly outperforms the classical \textsc{lista} in terms of predictive accuracy.
-Experiments on active learning demonstrate that the proposed Bayesian \textsc{lista} gives accurate posterior estimates that can be used for selection of a next data point where a label should be obtain at.
+We also show that when the training data is very small the proposed algorithm significantly outperforms \textsc{lista} in terms of predictive accuracy.
+Experiments on active learning demonstrate that the proposed Bayesian \textsc{lista} model gives accurate posterior estimates that can be used to select new training data points.
 
-The shrinkage parameter $\lambda$ is currently treated as a deterministic hyperparameter for the Bayesian \textsc{lista}.
+%The shrinkage parameter $\lambda$ is currently treated as a deterministic hyperparameter for Bayesian \textsc{lista}.
 In future we plan to incorporate it into the model treating it as a random variable.

### 2018-05-18 paper/BayesianLISTA.tex
initial nips submission

@@
 \begin{abstract}
-Despite the recent overwhelming success of deep learning uncertainty estimation is still a challenge for most modern deep learning methods.
+While deep learning has an overwhelming success, uncertainty estimation is still a challenge for most modern deep learning methods.
 The Bayesian learning allows to estimate the uncertainty of predictions in neural networks by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
@@
 
-To introduce the uncertainty of predictions, we assume that the true $\boldsymbol\beta$ has a Gaussian distribution centered at the output of the Bayesian \textsc{lista} network with precision $\gamma$.
+To introduce the uncertainty of predictions, we assume that the true $\boldsymbol\beta$ is an output $f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$ of the Bayesian \textsc{lista} network corrupted by the additive Gaussian zero-mean noise with the precision~$\gamma$.
 Then the likelihood of $\mathbf{B}$ is defined as
@@
 \label{eq:likelihood}
-p(\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) = \prod_{n=1}^N\prod_{d=1}^D\mathcal{N}\left(\beta_d^{(n)}; [\widehat{\boldsymbol\beta}^{(n)}]_d, \gamma^{-1}\right)
+p(\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) = \prod_{n=1}^N\prod_{d=1}^D\mathcal{N}\left(\beta_d^{(n)}; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}\right)
 \end{equation}
@@
 \begin{equation}
-Z  = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; \widehat{\boldsymbol\beta}, \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
+Z  = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
 \end{equation}
@@
 
-\section{Conclusions and future work}
+\section{Conclusions}
 \label{sec:conclusions}
@@
 We also show that when the training data is very small the proposed algorithm significantly outperforms \textsc{lista} in terms of predictive accuracy.
-Experiments on active learning demonstrate that the proposed Bayesian \textsc{lista} model gives accurate posterior estimates that can be used to select new training data points.
+Active learning experiments demonstrate that Bayesian \textsc{lista} gives accurate posterior estimates that can be used to select new training data points.
 

### 2018-05-18 paper/supplementary.tex
initial nips submission

@@
 \usepackage{subfig}
+
+\allowdisplaybreaks
 
@@
 
-We have used two approximations in forward propagation of uncertainty.
-First, at the step 2 of Algorithm 1 during the computation of $\mathbf{e}_l$, a Gaussian matrix is multiplied by a spike and slab vector and their product is approximated with the Gaussian distribution.
-Second, at the steps 2 and 5 of Algorithm 1 the result of soft thresholding of a Gaussian vector is approximated with the spike and slab distribution.
+We have used two approximations in forward propagation of uncertainty (section 4.3 of the main paper).
+First, at step 3 during the computation of $\mathbf{e}_l$, a Gaussian matrix is multiplied by a spike and slab vector and their product is approximated with the Gaussian distribution.
+Second, at steps 2 and 5 the result of soft thresholding of a Gaussian vector is approximated with the spike and slab distribution.
 In this section we demonstrate that these approximations are close to the real distributions.
 
-Figure \ref{fig:d_testing} demonstrates the comparison of the sampled distribution and approximated distribution for Lemma \ref{thm:matrix_vector}.
+Figure \ref{fig:d_testing} demonstrates the comparison of the sampled distribution and approximated distribution for the first approximation at step 3.
 For the sampled distribution, $10000$ values are sampled from the Gaussian matrix and the spike and slab vector and their product is computed, then one of the dimensionalities is plotted.
@@
 
-Figure \ref{fig:z_new_testing} demonstrates the comparison of the sampled distribution and approximated distribution for Lemma \ref{thm:soft_thresholding}.
+Figure \ref{fig:z_new_testing} demonstrates the comparison of the sampled distribution and approximated distribution for the second approximation at steps 2 and 5.
 For the sampled distribution, $10000$ values are sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities is plotted.
@@
 \label{eq:Z}
-Z = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda), \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
+Z = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
 \end{equation}
-We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta} = \widehat{\boldsymbol\beta}_L = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$, that is the output from the network and approximate with the spike and slab distribution with the parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}}$
+We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta} = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$ that is the output from the network.
+According to the proposed uncertainty propagation scheme $\widehat{\boldsymbol\beta}$ is approximated with the spike and slab distribution with the parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}}$
 \begin{align}
-Z &\approx \int \prod_{d=1}^{D} \mathcal{N}\left(\beta_d ; \widehat{\beta}_d, \gamma^{-1}\right) \left(\omega^{\widehat{\boldsymbol\beta}}_d \delta_0\left(\widehat{\beta}_d\right) + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\widehat{\beta}_d ; m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right)\right) \text{Gam} \left(\gamma_d; \alpha^\gamma, \beta^\gamma\right)\mathrm{d}\widehat{\boldsymbol\beta} \mathrm{d}\gamma  \nonumber\\
+Z &\approx \int \text{Gam} \left(\gamma; \alpha^\gamma, \beta^\gamma\right) \prod_{d=1}^{D} \left[ \mathcal{N}\left(\beta_d ; [\widehat{\boldsymbol\beta}]_d, \gamma^{-1}\right) \right.\\
+&\quad \left.
+\times  \left(\omega^{\widehat{\boldsymbol\beta}}_d \delta_0\left([\widehat{\boldsymbol\beta}]_d\right) + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left([\widehat{\boldsymbol\beta}]_d ; m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right)\right) \right] \mathrm{d}\widehat{\boldsymbol\beta} \mathrm{d}\gamma  \nonumber\\
 & = \prod_{d=1}^{D} \left[\omega^{\widehat{\boldsymbol\beta}}_d \int \mathcal{N}\left(\beta_d ; 0, \gamma^{-1}\right)  \text{Gam} \left(\gamma; \alpha^\gamma, \beta^\gamma\right) d\gamma  \nonumber \right.\\
-&\quad + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\int \mathcal{T}\left(\beta_d ; \widehat{\beta}_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) 
-\left. \vphantom{\int}  \mathcal{N}\left(\widehat{\beta}_d ; m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right) \mathrm{d}\widehat{\boldsymbol\beta}_d\right]  \nonumber\\
+&\quad + \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\int \mathcal{T}\left(\beta_d ; [\widehat{\boldsymbol\beta}]_d, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) 
+\left.
+\vphantom{\int}  \mathcal{N}\left([\widehat{\boldsymbol\beta}]_d ; m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\right) \mathrm{d}[\widehat{\boldsymbol\beta}]_d\right]  \nonumber\\
 \label{eq:Z_approx}
@@
 \begin{equation}
-\text{\textsc{nmse}} = \frac{1}{N}\sum\limits_{n=1}^N\sqrt{\frac{\sum\limits_{d=1}^D\left(\widehat{\beta}_{d}^{(n)} - \beta_d^{(n)}\right)^2}{\sum\limits_{d=1}^D\left(\beta_{d}^{(n)}\right)^2}}
+\text{\textsc{nmse}} = \frac{1}{N}\sum\limits_{n=1}^N\sqrt{\frac{\sum\limits_{d=1}^D\left([\widehat{\boldsymbol\beta}^{(n)}]_{d} - \beta_d^{(n)}\right)^2}{\sum\limits_{d=1}^D\left(\beta_{d}^{(n)}\right)^2}}
 \end{equation}

### 2018-05-18 paper/BayesianLISTA.tex
spell checker and supplementary corrected

@@
 In contrast to \textsc{ista}, Learned \textsc{ista} (\textsc{lista}) \cite{gregor2010learning} learns the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
-To achieve this, the \textsc{ista} is limited with the fixed amount of iterations $L$, and interpreted as a recurrent neural network: every iteration $l$ of \textsc{ista} corresponds to the layer $l$ of \textsc{lista}.
+To achieve this, the \textsc{ista} is limited with the fixed amount of iterations $L$ and interpreted as a recurrent neural network: every iteration $l$ of \textsc{ista} corresponds to the layer $l$ of \textsc{lista}.
 A coefficient vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$ is predicted according to Algorithm~\ref{alg:lista}.
@@
 
-For every layer $l$ of Bayesian \textsc{lista} we assume that $\widehat{\boldsymbol\beta}_{l}$ has the spike and slab distribution with the spike probability $\boldsymbol\omega$, the slab mean $\mathbf{m}$, and the slab variance $\mathbf{v}$
+For every layer $l$ of Bayesian \textsc{lista}, we assume that $\widehat{\boldsymbol\beta}_{l}$ has the spike and slab distribution with the spike probability $\boldsymbol\omega$, the slab mean $\mathbf{m}$, and the slab variance $\mathbf{v}$
 \begin{equation}

### 2018-05-18 paper/supplementary.tex
spell checker and supplementary corrected

@@
 
-The probability of a zero $\omega^*$ equals to the probability mass of the original distribution from the interval $[-\lambda, \lambda]$
+The probability $\omega^*$ of zero equals to the probability mass of the original distribution from the interval $[-\lambda, \lambda]$
 \begin{equation}
@@
 Let $\psi(\cdot)$ denote the density of the soft-thresholded distribution on $x^* \neq 0$, $\phi(\cdot)$ denote the density of the original Gaussian distribution on $x$.
-Then the first moment of $x^* \neq 0$ is:
+Then the first moment of $x^* \neq 0$ is
 
@@
 \label{eq:thr_first_moment}
-m^* = \int_{-\infty}^{+\infty}x\psi(x)dx= \int_{-\infty}^{0}x\phi(x-\lambda)dx + \int_{0}^{+\infty}x\phi(x+\lambda)dx,
+m^* = \int_{-\infty}^{+\infty}t\psi(t)\mathrm{d}t= \int_{-\infty}^{0}t\phi(t-\lambda)\mathrm{d}t + \int_{0}^{+\infty}t\phi(t+\lambda)\mathrm{d}t,
 \end{equation}
@@
 \begin{align}
-&\int_{-\infty}^{0}x\phi(x-\lambda)dx = -\frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} + (\lambda+m)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)\\
-&\int_{0}^{+\infty}x\phi(x+\lambda)dx = \frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(m - \lambda)^2}{2v}\right\} + (m - \lambda)\left(1 - \Phi\left(-\frac{\lambda-m}{\sqrt{v}}\right)\right)
+&\int_{-\infty}^{0}t\phi(t-\lambda)\mathrm{d}t = -\frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} + (\lambda+m)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)\\
+&\int_{0}^{+\infty}t\phi(t+\lambda)\mathrm{d}t = \frac{\sqrt{v}}{\sqrt{2\pi}} \exp\left\{\frac{-(m - \lambda)^2}{2v}\right\} + (m - \lambda)\left(1 - \Phi\left(-\frac{\lambda-m}{\sqrt{v}}\right)\right)
 \end{align}
@@
 \label{eq:thr_second_moment}
-s = \int_{-\infty}^{+\infty}x^2\psi(x)dx = \int_{-\infty}^{0}x^2\phi(x-\lambda)dx + \int_{0}^{+\infty}x^2\phi(x+\lambda)dx,
+s = \int_{-\infty}^{+\infty}t^2\psi(t)\mathrm{d}t = \int_{-\infty}^{0}t^2\phi(t-\lambda)\mathrm{d}t + \int_{0}^{+\infty}t^2\phi(t+\lambda)\mathrm{d}t,
 \end{equation}
@@
 \begin{split}
-&\int_{-\infty}^{0}x^2\phi(x-\lambda)dx = \\
+&\int_{-\infty}^{0}t^2\phi(t-\lambda)\mathrm{d}t = \\
 &-\frac{\sqrt{v}}{\sqrt{2\pi}} (\lambda+m)\exp\left\{\frac{-(\lambda+m)^2}{2v}\right\} + (\sigma^2 + (\lambda+m)^2)\Phi\left(-\frac{\lambda+m}{\sqrt{v}}\right)
@@
 \begin{split}
-&\int_{0}^{+\infty}x^2\phi(x+\lambda)dx = \\
+&\int_{0}^{+\infty}t^2\phi(t+\lambda)\mathrm{d}t = \\
 &\frac{\sqrt{v}}{\sqrt{2\pi}} (m - \lambda)\exp\left\{\frac{-(m - \lambda)^2}{2v}\right\} + (\sigma^2 + (m - \lambda)^2)\left(1 - \Phi\left(\frac{\lambda -m}{\sqrt{v}}\right)\right)
@@
 \label{thm:moments_spsl}
-Let a random variable $\xi$ have a spike and slab distribution with probability of spike $\omega$, slab mean $m$ and slab variance $v$. Then its moments are
+Let a random variable $\xi$ have a spike and slab distribution with the probability of spike $\omega$, the slab mean $m$ and slab variance $v$. Then its moments are
 \begin{subequations}
@@
 \begin{split}
-\mathbb{E}\xi &= \int x \big(\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v)\big)dx \\
-& = \omega \int x \delta_0(x)dx + (1 - \omega)\int x \mathcal{N}(x; m, v)dx \\
+\mathbb{E}\xi &= \int t \big(\omega \delta_0(t) + (1 - \omega)\mathcal{N}(t; m, v)\big)\mathrm{d}t \\
+& = \omega \int t \delta_0(t)\mathrm{d}t + (1 - \omega)\int t \mathcal{N}(t; m, v)\mathrm{d}t \\
 & = (1-\omega)m \\
-\mathbb{E}\xi^2 &= \int x^2 \big(\omega \delta_0(x) + (1 - \omega)\mathcal{N}(x; m, v)\big)dx \\
-& = \omega \int x^2 \delta_0(x)dx + (1 - \omega)\int x^2 \mathcal{N}(x; m, v)dx \\
+\mathbb{E}\xi^2 &= \int t^2 \big(\omega \delta_0(t) + (1 - \omega)\mathcal{N}(t; m, v)\big)\mathrm{d}t \\
+& = \omega \int t^2 \delta_0(t)\mathrm{d}t + (1 - \omega)\int t^2 \mathcal{N}(t; m, v)\mathrm{d}t \\
 & = (1-\omega)(v + m^2) \\
@@
 Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta }\in \mathbb{R}^D$ be a vector with spike-and-slab distributed variables: $\widehat{\beta}_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
-The components of the matrix $\mathbf{S}$ and the vector $\widehat{\boldsymbol\beta}$ are mutual independent.
+The components of the matrix $\mathbf{S}$ and the vector $\widehat{\boldsymbol\beta}$ are mutually independent.
 Let $\mathbf{e} \in \mathbb{R}^{D}$ denote the product $\mathbf{S} \widehat{\boldsymbol\beta}$.
-Then the marginal mean and variance of elements $e_d$ of the vector $\mathbf{e}$ are:
+Then the marginal mean and variance of elements $e_d$ of the vector $\mathbf{e}$ are
 \begin{subequations}
@@
 \subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.4\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
-\caption{Approximations of the Bayesian \textsc{lista}}
+\caption{Approximation quality in Bayesian \textsc{lista}}
 %\label{fig:z_new_testing}
@@
 For the sampled distribution, $10000$ values are sampled from the Gaussian matrix and the spike and slab vector and their product is computed, then one of the dimensionalities is plotted.
-The parameters of the approximated distribution is computed according to Lemma \ref{thm:matrix_vector}.
+The parameters of the approximated distribution are computed according to Lemma \ref{thm:matrix_vector}.
 
@@
 For the sampled distribution, $10000$ values are sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities is plotted.
-The parameters of the approximated distribution is computed according to Lemma \ref{thm:soft_thresholding}.
+The parameters of the approximated distribution are computed according to Lemma \ref{thm:soft_thresholding}.
 
 \section{Derivation for the normalisation constant}
-When the likelihood term for a single data point is incorporated into the approximating distribution $q$, the normalisation constant of $q$ is expressed as
+When the likelihood term for a single data point is incorporated into the approximating distribution~$q$, the normalisation constant of $q$ is expressed as
 \begin{equation}
@@
 \end{equation}
-We sample $\mathbf{W}$, $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta} = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$ that is the output from the network.
-According to the proposed uncertainty propagation scheme $\widehat{\boldsymbol\beta}$ is approximated with the spike and slab distribution with the parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}}$
+We sample weights $\mathbf{W}$ and $\mathbf{S}$ from $q$ and get $\widehat{\boldsymbol\beta} = f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$ that is the output from the network.
+According to the proposed uncertainty propagation scheme $\widehat{\boldsymbol\beta}$ is approximated with the spike and slab distribution with the parameters $\boldsymbol\omega^{\widehat{\boldsymbol\beta}}$, $\mathbf{m}^{\widehat{\boldsymbol\beta}}$, and $\mathbf{v}^{\widehat{\boldsymbol\beta}}$.
+Then we approximate the normalisation constant
 \begin{align}
@@
 \section{Hyperparameter optimisation}
-The only hyperparameter in the proposed Bayesian \textsc{lista} is the shrinkage parameter $\lambda$.
+The only hyperparameter in the proposed Bayesian \textsc{lista} model is the shrinkage parameter $\lambda$.
 It can be optimised using the Type II maximum likelihood procedure.
 The Type II likelihood, i.e.
-the evidence $p(\boldsymbol\beta | \mathbf{y}, \lambda)$, of the Bayesian \textsc{lista} is equal to the normalisation constant $Z$ (\ref{eq:Z}) computed for the whole training dataset $\boldsymbol\beta$.
+the evidence $p(\mathbf{B} | \mathbf{Y}, \lambda)$, of the Bayesian \textsc{lista} is equal to the normalisation constant $Z$ (\ref{eq:Z}) computed for the whole training dataset $\{\mathbf{Y}, \mathbf{B}\}$.
 Given the approximation~(\ref{eq:Z_approx}) the optimal hyperparameter $\lambda$ can be found by a gradient-based optimiser.
@@
 \end{equation}
-In sparse coding it is also important to obtain the correct locations of spikes (i.e zeros) and slabs (i.e.
+In sparse coding it is also important to obtain the correct locations of spikes (i.e.
+zeros) and slabs (i.e.
 non-zeros) in the estimates.
@@
 
-\section{Additional results on the \textsc{mnist} data}
-In contrast to \textsc{lista} and baselines, the Bayesian \textsc{lista} provides a posterior estimate for a test data point.
+\section{Additional results on \textsc{mnist} data}
+In contrast to \textsc{lista} and baselines, Bayesian \textsc{lista} provides a posterior estimate for a test data point.
 Figure~\ref{fig:posterior_samples} shows samples from the posterior for the test image of the digit $7$ and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
@@
 \centering
-\subfloat[$\beta$ posterior mean]{\includegraphics[width=0.33\columnwidth]{posterior_mean}}~
-\subfloat[$\beta$ posterior std]{\includegraphics[width=0.33\columnwidth]{posterior_std}}~
-\subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.33\columnwidth]{posterior_spike_indicator}}
+\subfloat[$\boldsymbol\beta$ posterior mean]{\includegraphics[width=0.33\columnwidth]{posterior_mean}}~
+\subfloat[$\boldsymbol\beta$ posterior std]{\includegraphics[width=0.33\columnwidth]{posterior_std}}~
+\subfloat[$\boldsymbol\beta$ posterior spike indicator]{\includegraphics[width=0.33\columnwidth]{posterior_spike_indicator}}
 \caption{Posterior parameters for an image of the digit 7.}

### 2018-07-30 review_nips_2018/response_to_reviews_nips.tex
started responses

\documentclass{article}
\usepackage{nips_2018}
\usepackage{color}
\usepackage{mathtools}
\begin{document}

\title{NIPS 2018 Reply to Reviewers}
\date{}
\maketitle

\section*{Reviewer 1}
Q: What is the motivation for being Bayesian about the LISTA algorithm. How does in the uncertainty in the Bayesian LISTA procedure relate to the original linear model.

A: The LISTA algorithm introduces the weights in the model. Their point estimates are being inferred during the training phase, this leads to the uncertainty of the estimation. In our Bayesian model we infer the posterior distributions over these weights to estimate this uncertainty.
\newline
\newline

Q: how does the sparse promoting prior interact with the sparsity promoting non-linearity.

A: In the LISTA model the sequential estimates of beta are obtained at each layer using the previous estimate. At every layer the estimate becomes more sparse due to soft-thresholding non-linearity. We do not specify sparsity priors over the beta_l - we show that show that the distribution of these estimates can be approximated with spike-and-slab distribution, i.e. it sparsity naturally arises from Gaussian prior on NN weights and soft thresholding nonlinearity.
\newline
\newline

Q: The approximations in section 4 are part of the approximate inference

A: Yes, they are part of the inference procedure, the model remains the same as in section 3. These approximations are similar to mean-field approximations in variational inference.
\newline
\newline

Q: The assumption of mutual independence over the elements of S and beta_{l-1}

A: Generally speaking, correlation is partially removed due to the soft-thresholding on the previous layer. It requires further research to establish the influence of remaining correlation on the quality of approximation.
\newline
\newline

\section*{Reviewer 3}

\end{document}

### 2018-07-30 review_nips_2018/response_to_reviews_nips.tex
small corrections to rebuttal

@@
 At every layer the estimate becomes more sparse due to soft-thresholding non-linearity.
-We do not specify sparsity priors over the beta_l - we show that show that the distribution of these estimates can be approximated with spike-and-slab distribution, i.e.
-it sparsity naturally arises from Gaussian prior on NN weights and soft thresholding nonlinearity.
+We do not specify sparsity priors over the $beta_l$ - we show that the distribution of these estimates can be approximated with the spike-and-slab distribution, i.e.
+its sparsity naturally arises from the Gaussian prior on NN weights and sparsity promoting soft thresholding nonlinearity.
 \newline
@@
 
-Q: The assumption of mutual independence over the elements of S and beta_{l-1}
+Q: The assumption of mutual independence over the elements of $S$ and $beta_{l-1}$
 

### 2018-07-30 review_nips_2018/response_to_reviews_nips.tex
even smaller corrections to rebuttal

@@
 At every layer the estimate becomes more sparse due to soft-thresholding non-linearity.
-We do not specify sparsity priors over the $beta_l$ - we show that the distribution of these estimates can be approximated with the spike-and-slab distribution, i.e.
+We do not specify sparsity priors over the $\beta_l$ - we show that the distribution of these estimates can be approximated with the spike-and-slab distribution, i.e.
 its sparsity naturally arises from the Gaussian prior on NN weights and sparsity promoting soft thresholding nonlinearity.
@@
 
-Q: The assumption of mutual independence over the elements of $S$ and $beta_{l-1}$
+Q: The assumption of mutual independence over the elements of $S$ and $\beta_{l-1}$
 

### 2018-07-30 review_nips_2018/response_to_reviews_nips.tex
updated response for nips

@@
 \documentclass{article}
-\usepackage{nips_2018}
+\usepackage{nips_2018_author_response}
 \usepackage{color}
@@
 
-\title{NIPS 2018 Reply to Reviewers}
-\date{}
-\maketitle
+We would like to thank you the reviewers for their time and valuable suggestions.
 
-\section*{Reviewer 1}
-Q: What is the motivation for being Bayesian about the LISTA algorithm. How does in the uncertainty in the Bayesian LISTA procedure relate to the original linear model.
+\textbf{Reviewer 1}
 
-A: The LISTA algorithm introduces the weights in the model.
+\textbf{Q:} ``What is the motivation for being Bayesian about the LISTA algorithm. How does in the uncertainty in the Bayesian LISTA procedure relate to the original linear model.'' 
+\textbf{A:} The LISTA algorithm introduces the weights in the model.
 Their point estimates are being inferred during the training phase, this leads to the uncertainty of the estimation.
 In our Bayesian model we infer the posterior distributions over these weights to estimate this uncertainty.
-\newline
-\newline
 
-Q: how does the sparse promoting prior interact with the sparsity promoting non-linearity.
-
-A: In the LISTA model the sequential estimates of beta are obtained at each layer using the previous estimate.
+\textbf{Q:} ``how does the sparse promoting prior interact with the sparsity promoting non-linearity.'' 
+\textbf{A:} In the LISTA model the sequential estimates of beta are obtained at each layer using the previous estimate.
 At every layer the estimate becomes more sparse due to soft-thresholding non-linearity.
@@
 its sparsity naturally arises from the Gaussian prior on NN weights and sparsity promoting soft thresholding nonlinearity.
-\newline
-\newline
 
-Q: The approximations in section 4 are part of the approximate inference
+\textbf{Q:} ``The approximations in section 4 are part of the approximate inference.''  
+\textbf{A:} Yes, they are part of the inference procedure, the model remains the same as in section 3. These approximations are similar to mean-field approximations in variational inference.
 
-A: Yes, they are part of the inference procedure, the model remains the same as in section 3. These approximations are similar to mean-field approximations in variational inference.
-\newline
-\newline
+\textbf{Q:} ``The assumption of mutual independence over the elements of $S$ and $\beta_{l-1}$'' 
+\textbf{A:} Generally speaking, correlation is partially removed due to the soft-thresholding on the previous layer.
+It requires further research to establish the influence of remaining correlation on the quality of approximation.
 
-Q: The assumption of mutual independence over the elements of $S$ and $\beta_{l-1}$
+\textbf{Reviewer 2}
 
-A: Generally speaking, correlation is partially removed due to the soft-thresholding on the previous layer.
-It requires further research to establish the influence of remaining correlation on the quality of approximation.
-\newline
-\newline
+\textbf{Q:} ``the contribution is quite incremental, with most of the method relying on existing tools for probabilistic back-propagation'' 
+\textbf{A:} The main contribution of the paper is in the forward pass, i.e.
+modelling distributions of the weights and how they propagate through the layers of a NN.
+We have shown that normally distributed weights propagated though the soft-thresholding non-linearity can be approximated with the spike and slab distribution.
+Although our inference is based on ideas from probabilistic back-propagation, we expanded this framework.
+In the original work, PBP was developed only for ReLU non-linearity, we developed it for soft-thresholding non-linearity.
+Also in contrast to the original work we deal with the multidimensional output of a NN and our NN is recurrent.
 
-\section*{Reviewer 3}
+\textbf{Q:} ``Bayesian LISTA outperforms LISTA on NMSE (esp. with more layers/iterations), while LISTA yields better F- measures.''  
+\textbf{A:} LISTA gets better F-measure only for number of measurements $K = \{10, 20\}$ for the synthetic data.
+In all the other experiments Bayesian LISTA shows either competitive results with LISTA or outperforms it.
+
+\textbf{Q:} ``the MNIST experiment presented in the paper is about generating random Gaussian linear combinations of the MNIST images, and then trying to recover the original coefficients.
+No sparsity is imposed.''
+\textbf{A:} Sparsity in the MNIST experiment is in images themselves. Flatten images represent vectors with a lot of zeros corresponding to background pixels.
+
+\textbf{Reviewer 3}
+
+\textbf{Q:} `` The update rules for the backpropagation algorithm should be given for each parameter, at least in the supplementary.'' 
+\textbf{A:} We included details of the backpropagation algorithm that are distinguish and original for this paper.
+The general idea and formula of updating parameters based on derivatives of the normalisation constant is not new, therefore, we provided only derivation for the normalisation constant, which is different.
+We will add full details in the supplementary to make the paper self-contained.
+Thank you for your suggestion.
+
+\textbf{Q:} ``My main concern is that the loss used to train the network is not detailed.'' 
+\textbf{A:} Proposed Bayesian LISTA does not directly minimise any loss while training the network, we rather minimise the KL-divergence between approximating and posterior distribution on parameters.
+Backpropagation is used for the ADF updates of the parameters for computing derivatives of the normalisation constant.
+LISTA minimises the squared error between the predicted output and the given output for training network.
+Eq.
+(1) provides the general formulation of the sparse coding problem.
+It is not used for training networks.
+The parameter $\lambda$ was introduced in ISTA.
+The value $0.1$ was shown as this was found optimal for all algorithms on the synthetic data (plots are given in the supplementary).
+
+\textbf{Q:} ``Only 200 samples are used from the 60,000 available, suggesting that the proposed technique scale poorly.
+The results are also displayed relatively to the number of training iteration and not with varying number L of layers/iterations as in the previous experiment''
+\textbf{A:} A limited number of samples are used to show benefits of using a Bayesian method such as Bayesian LISTA over a frequentist method such as LISTA.
+As shown in the example of increasing the number of measurements when the data is not scarce, Bayesian LISTA and LISTA provides competitive results.
+The similar behaviour is demonstrated when we increase the size of training data.
+We will add the experiments with varying L as suggested.
+Thank you.
 

### 2018-08-01 review_nips_2018/response_to_reviews_nips.tex
updated rebuttal

@@
 
-We would like to thank you the reviewers for their time and valuable suggestions.
+We would like to thank the reviewers for their time and valuable suggestions.
 
@@
 
-\textbf{Q:} ``What is the motivation for being Bayesian about the LISTA algorithm. How does in the uncertainty in the Bayesian LISTA procedure relate to the original linear model.'' 
+\textbf{Q:} \textit{What is the motivation for being Bayesian about the LISTA algorithm? How does in the uncertainty in the Bayesian LISTA procedure relate to the original linear model?}
 \textbf{A:} The LISTA algorithm introduces the weights in the model.
 Their point estimates are being inferred during the training phase, this leads to the uncertainty of the estimation.
-In our Bayesian model we infer the posterior distributions over these weights to estimate this uncertainty.
+In the proposed Bayesian model we infer the posterior distributions over these weights to estimate this uncertainty.
 
-\textbf{Q:} ``how does the sparse promoting prior interact with the sparsity promoting non-linearity.'' 
-\textbf{A:} In the LISTA model the sequential estimates of beta are obtained at each layer using the previous estimate.
+\textbf{Q:} \textit{How does the sparse promoting prior interact with the sparsity promoting non-linearity?}
+\textbf{A:} In the LISTA model the sequential estimates of $\boldsymbol{\beta}$ are obtained at each layer using the previous estimate.
 At every layer the estimate becomes more sparse due to soft-thresholding non-linearity.
-We do not specify sparsity priors over the $\beta_l$ - we show that the distribution of these estimates can be approximated with the spike-and-slab distribution, i.e.
+We do not specify sparsity priors over the $\boldsymbol{\beta}_l$, we show that the distribution of these estimates can be approximated with the spike-and-slab distribution, i.e.
 its sparsity naturally arises from the Gaussian prior on NN weights and sparsity promoting soft thresholding nonlinearity.
 
-\textbf{Q:} ``The approximations in section 4 are part of the approximate inference.''  
+\textbf{Q:} \textit{... whether the approximations in section 4 are part of the approximate inference} 
 \textbf{A:} Yes, they are part of the inference procedure, the model remains the same as in section 3. These approximations are similar to mean-field approximations in variational inference.
 
-\textbf{Q:} ``The assumption of mutual independence over the elements of $S$ and $\beta_{l-1}$'' 
+\textbf{Q:} \textit{Is the assumption of mutual independence over the elements of $\mathbf{S}$ and $\boldsymbol{\beta}_{l-1}$?}
 \textbf{A:} Generally speaking, correlation is partially removed due to the soft-thresholding on the previous layer.
@@
 
-\textbf{Q:} ``the contribution is quite incremental, with most of the method relying on existing tools for probabilistic back-propagation'' 
-\textbf{A:} The main contribution of the paper is in the forward pass, i.e.
-modelling distributions of the weights and how they propagate through the layers of a NN.
-We have shown that normally distributed weights propagated though the soft-thresholding non-linearity can be approximated with the spike and slab distribution.
-Although our inference is based on ideas from probabilistic back-propagation, we expanded this framework.
+\textbf{Q:} \textit{... the contribution is quite incremental, with most of the method relying on existing tools for probabilistic back-propagation}
+\textbf{A:} The main contribution of the paper consists in the proposed way to model the distributions of the weights and their propagation through the layers of a NN.
+We have shown that normally distributed weights propagated though soft-thresholding non-linearity can be approximated with the spike and slab distribution.
+Although our inference is based on ideas from probabilistic backpropagation, we expanded this framework.
 In the original work, PBP was developed only for ReLU non-linearity, we developed it for soft-thresholding non-linearity.
-Also in contrast to the original work we deal with the multidimensional output of a NN and our NN is recurrent.
+Also in contrast to the original work we dealt with the multidimensional output of a NN and considered NNs are recurrent.
 
-\textbf{Q:} ``Bayesian LISTA outperforms LISTA on NMSE (esp. with more layers/iterations), while LISTA yields better F- measures.''  
-\textbf{A:} LISTA gets better F-measure only for number of measurements $K = \{10, 20\}$ for the synthetic data.
+\textbf{Q:} \textit{Bayesian LISTA outperforms LISTA on NMSE (esp. with more layers/iterations), while LISTA yields better F- measures} 
+\textbf{A:} LISTA gets better F-measure only for the number of measurements $K = \{10, 20\}$ for the synthetic data.
 In all the other experiments Bayesian LISTA shows either competitive results with LISTA or outperforms it.
 
-\textbf{Q:} ``the MNIST experiment presented in the paper is about generating random Gaussian linear combinations of the MNIST images, and then trying to recover the original coefficients.
-No sparsity is imposed.''
+\textbf{Q:} \textit{...
+the MNIST experiment presented in the paper is about generating random Gaussian linear combinations of the MNIST images, and then trying to recover the original coefficients.
+No sparsity is imposed}
 \textbf{A:} Sparsity in the MNIST experiment is in images themselves. Flatten images represent vectors with a lot of zeros corresponding to background pixels.
@@
 
-\textbf{Q:} `` The update rules for the backpropagation algorithm should be given for each parameter, at least in the supplementary.'' 
-\textbf{A:} We included details of the backpropagation algorithm that are distinguish and original for this paper.
+\textbf{Q:} \textit{The update rules for the backpropagation algorithm should be given for each parameter, at least in the supplementary} 
+\textbf{A:} We included details of the backpropagation algorithm that are original for this paper.
 The general idea and formula of updating parameters based on derivatives of the normalisation constant is not new, therefore, we provided only derivation for the normalisation constant, which is different.
@@
 
-\textbf{Q:} ``My main concern is that the loss used to train the network is not detailed.'' 
+\textbf{Q:} \textit{My main concern is that the loss used to train the network is not detailed}
 \textbf{A:} Proposed Bayesian LISTA does not directly minimise any loss while training the network, we rather minimise the KL-divergence between approximating and posterior distribution on parameters.
@@
 The parameter $\lambda$ was introduced in ISTA.
-The value $0.1$ was shown as this was found optimal for all algorithms on the synthetic data (plots are given in the supplementary).
+The value $\lambda=0.1$ was shown to be optimal for all algorithms on the synthetic data (plots are given in the supplementary).
 
-\textbf{Q:} ``Only 200 samples are used from the 60,000 available, suggesting that the proposed technique scale poorly.
-The results are also displayed relatively to the number of training iteration and not with varying number L of layers/iterations as in the previous experiment''
+\textbf{Q:} \textit{Only 200 samples are used from the 60,000 available, suggesting that the proposed technique scale poorly.
+The results are also displayed relatively to the number of training iteration and not with varying number $L$ of layers/iterations as in the previous experiment...}
 \textbf{A:} A limited number of samples are used to show benefits of using a Bayesian method such as Bayesian LISTA over a frequentist method such as LISTA.
-As shown in the example of increasing the number of measurements when the data is not scarce, Bayesian LISTA and LISTA provides competitive results.
+As shown in the example of increasing the number of measurements when the data is not scarce, Bayesian LISTA and LISTA provide competitive results in terms of accuracy of point estimates.
 The similar behaviour is demonstrated when we increase the size of training data.
-We will add the experiments with varying L as suggested.
+We will add the experiments with varying $L$ as suggested.
 Thank you.

### 2018-10-23 icassp_2019/paper.tex
started icassp version

--- 2018-05-18 paper/BayesianLISTA.tex
@@
 \documentclass{article}
+\usepackage{spconf,amsmath,graphicx}
 \usepackage{mathtools}
@@
 \usepackage{xcolor}
-
 \usepackage{times}
 \usepackage{float}
-
-\usepackage[square,numbers]{natbib}
-\usepackage[nonatbib]{nips_2018}
-
-\usepackage{bbm}
 \usepackage{algorithm, algorithmic}
@@
 
-\allowdisplaybreaks
+\title{Bayesian neural networks for sparse coding}
 
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicreturn}{\textbf{Output:}}
+\name{Danil Kuzin$^{\dagger}$ \qquad Olga Isupova$^{\star}$ \qquad Lyudmila Mihaylova$^{\dagger}$}
 
-% \setlength{\belowcaptionskip}{-15pt}
-%  \usepackage[small,compact]{titlesec}
-%  \titlespacing{\section}{0pt}{1ex}{0.8ex}
-%  \titlespacing{\subsection}{0pt}{0.5ex}{0ex}
-%  \titlespacing{\subsubsection}{0pt}{0.2ex}{0ex}
-%  \expandafter\def\expandafter\normalsize\expandafter{%
-%      \normalsize
-%      \setlength\abovedisplayskip{2pt}
-%      \setlength\belowdisplayskip{2pt}
-%      \setlength\abovedisplayshortskip{0pt}
-%      \setlength\belowdisplayshortskip{0pt}
-%  }
-%  \renewcommand{\baselinestretch}{0.99}
-
-\title{Uncertainty propagation in neural networks for sparse coding}
-
-\author{} % LEAVE BLANK FOR ORIGINAL SUBMISSION.
-          % UAI  reviewing is double-blind.
-
-% The author names and affiliations should appear only in the accepted paper.
-%
-%\author{ {\bf Harry Q.~Bovik\thanks{Footnote for author to give an
-%alternate address.}} \\
-%Computer Science Dept. \\
-%Cranberry University\\
-%Pittsburgh, PA 15213 \\
-%\And
-%{\bf Coauthor}  \\
-%Affiliation          \\
-%Address \\
-%\And
-%{\bf Coauthor}   \\
-%Affiliation \\
-%Address    \\
-%(if needed)\\
-%}
-
-%\author{ {\bf Danil Kuzin} \\
-%\And
-%{\bf Olga Isupova}  \\
-%\And
-%{\bf Lyudmila Mihaylova}   \\
-%}
+\address{$^{\star}$ Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield S1 3JD, UK (e-mail: dkuzin1@sheffield.ac.uk; l.s.mihaylova@sheffield.ac.uk).\\
+  		    $^{\dagger}$ Department of Engineering Science, University of Oxford, Oxford OX1 2JD, UK (e-mail: olga.isupova@eng.ox.ac.uk)}
 
@@
 
+\begin{keywords}
+Sparse regression, Bayesian neural networks, uncertainty estimation, compressive sensing
+\end{keywords}
+
 \section{Introduction}
+\label{sec:intro}
+
   The idea of Bayesian learning in neural networks \cite{neal2012bayesian} has recently regained its attention with the development of distributed approximate inference techniques \cite{li2015stochastic, hoffman2013stochastic} and general boost in popularity of deep learning.
@@
 We show the experimental results in section \ref{sec:experiments} and finish with discussion and conclusions in section \ref{sec:conclusions}.
-
-%The paper is organised as following: first, we review neural networks for sparse coding in section \ref{sec:nn_sc} and present a novel Bayesian neural network in section \ref{sec:bayesian_lista}.
-We then describe uncertainty propagation to obtain the spike and slab distribution for an output of a network in section \ref{sec:fprop} and how probabilistic backpropagation is organised to update distributions of weights in section \ref{sec:backpropagation}.
-After that, we show the experimental results of the algorithm in section \ref{sec:experiments} and finish with discussion and conclusions in section \ref{sec:conclusions}.
 
@@
   \end{algorithm}
-
-% \begin{align}
-% \label{eq:first_layer}
-% &\mathbf{b} = \mathbf{W}\mathbf{y}\\
-% \label{eq:thr_first}
-% &\widehat{\boldsymbol\beta}_0 = h_\lambda(\mathbf{b}) \\
-% &\text{for } l=1:L\\
-% \label{eq:l_dense_layer}
-% 	&\quad \mathbf{c}_l = \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1} \\
-% \label{eq:l_thr}
-% 	&\quad \widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l) \\
-% & \widehat{\boldsymbol\beta} = \widehat{\boldsymbol\beta}_{L}
-% \end{align}
 
@@
 
-%The shrinkage parameter $\lambda$ is currently treated as a deterministic hyperparameter for Bayesian \textsc{lista}.
-In future we plan to incorporate it into the model treating it as a random variable.
-For this we will extend both the uncertainty propagation method to include uncertainty of $\lambda$ and the probabilistic backpropagation algorithm to estimate its posterior.
+% Below is an example of how to insert images. Delete the ``\vspace'' line,
+% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
+% with a suitable PostScript file name.
+% -------------------------------------------------------------------------
+% \begin{figure}[htb]
 
-\small
+% \begin{minipage}[b]{1.0\linewidth}
+%   \centering
+%   \centerline{\includegraphics[width=8.5cm]{image1}}
+% %  \vspace{2.0cm}
+%   \centerline{(a) Result 1}\medskip
+% \end{minipage}
+% %
+% \begin{minipage}[b]{.48\linewidth}
+%   \centering
+%   \centerline{\includegraphics[width=4.0cm]{image3}}
+% %  \vspace{1.5cm}
+%   \centerline{(b) Results 3}\medskip
+% \end{minipage}
+% \hfill
+% \begin{minipage}[b]{0.48\linewidth}
+%   \centering
+%   \centerline{\includegraphics[width=4.0cm]{image4}}
+% %  \vspace{1.5cm}
+%   \centerline{(c) Result 4}\medskip
+% \end{minipage}
+% %
+% \caption{Example of placing a figure with experimental results.}
+% \label{fig:res}
+% %
+% \end{figure}
+
+% % To start a new column (but not a new page) and help balance the last-page
+% % column length use \vfill\pagebreak.
+% % -------------------------------------------------------------------------
+% %\vfill
+% %\pagebreak
+
+% \section{COPYRIGHT FORMS}
+% \label{sec:copyright}
+
+% You must submit your fully completed, signed IEEE electronic copyright release
+% form when you submit your paper. We {\bf must} have this form before your paper
+% can be published in the proceedings.
+
+% \section{RELATION TO PRIOR WORK}
+% \label{sec:prior}
+
+% The text of the paper should contain discussions on how the paper's
+% contributions are related to prior work in the field. It is important
+% to put new work in  context, to give credit to foundational work, and
+% to provide details associated with the previous work that have appeared
+% in the literature. This discussion may be a separate, numbered section
+% or it may appear elsewhere in the body of the manuscript, but it must
+% be present.
+
+% You should differentiate what is new and how your work expands on
+% or takes a different path from the prior studies. An example might
+% read something to the effect: "The work presented here has focused
+% on the formulation of the ABC algorithm, which takes advantage of
+% non-uniform time-frequency domain analysis of data. The work by
+% Smith and Cohen \cite{Lamp86} considers only fixed time-domain analysis and
+% the work by Jones et al \cite{C2} takes a different approach based on
+% fixed frequency partitioning. While the present study is related
+% to recent approaches in time-frequency analysis [3-5], it capitalizes
+% on a new feature space, which was not considered in these earlier
+% studies."
+
+% \vfill\pagebreak
+
+% \section{REFERENCES}
+% \label{sec:refs}
+
+% List and number all bibliographical references at the end of the
+% paper. The references can be numbered in alphabetic order or in
+% order of appearance in the document. When referring to them in
+% the text, type the corresponding reference number in square
+% brackets as shown at the end of this sentence \cite{C2}. An
+% additional final page (the fifth page, in most cases) is
+% allowed, but must contain only references to the prior
+% literature.
+
+% % References should be produced using the bibtex program from suitable
+% % BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
+% % style file from IEEE produces unsorted bibliography list.
+% % -------------------------------------------------------------------------
+\bibliographystyle{IEEEbib}
 \bibliography{bibliography}
-\bibliographystyle{unsrtnat}
 

### 2018-10-23 icassp_2019/paper.tex
Update icassp_2019/paper.tex
minor

@@
 
-\address{$^{\star}$ Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield S1 3JD, UK (e-mail: dkuzin1@sheffield.ac.uk; l.s.mihaylova@sheffield.ac.uk).\\
-  		    $^{\dagger}$ Department of Engineering Science, University of Oxford, Oxford OX1 2JD, UK (e-mail: olga.isupova@eng.ox.ac.uk)}
+\address{$^{\star}$ Department of Automatic Control and Systems Engineering,\\
+University of Sheffield, Sheffield S1 3JD, UK\\
+e-mail: dkuzin1@sheffield.ac.uk; l.s.mihaylova@sheffield.ac.uk.\\
+$^{\dagger}$ Department of Engineering Science,\\
+University of Oxford, Oxford OX1 2JD, UK\\
+e-mail: olga.isupova@eng.ox.ac.uk}
 

### 2018-10-23 icassp_2019/paper.tex
attempt to shorten, forward propagation mainly successful

@@
 \newtheorem{lemma}{Lemma}
+
+\allowdisplaybreaks
 
@@
   While deep learning has an overwhelming success, uncertainty estimation is still a challenge for most modern deep learning methods.
-The Bayesian learning allows to estimate the uncertainty of predictions in neural networks by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
+Bayesian learning allows to estimate the uncertainty of predictions in neural networks by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
 We propose a novel method of propagating the uncertainty through the soft thresholding nonlinearity.
@@
 As an example, we design a Bayesian Learned Iterative Shrinkage-Thresholding network (Bayesian \textsc{lista}).
-We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation.
+An efficient posterior inference algorithm based on probabilistic backpropagation is developed.
 A series of experiments on sparse coding shows that the proposed framework provides both accurate predictions and sensible estimates of uncertainty in these predictions.
@@
 
-  In general, when distributions are included in the network, the complexity of Bayesian inference scales exponentially with the number of layers.
-Nevertheless, recently several techniques have been proposed to handle specific types of neural networks without this exponential growth.
+  In general, when distributions are included in a network, the complexity of Bayesian inference scales exponentially with the number of layers.
+Nevertheless, recently several techniques~\cite{ranganath2015deep, gal2016dropout} have been proposed to handle specific types of neural networks without this exponential growth.
 For example, feed-forward networks with the rectified linear unit nonlinearity~\cite{hernandez2015probabilistic}, networks with discrete distributions~\cite{soudry2014expectation}, recurrent networks~\cite{mcdermott2017bayesian}.
 
-  There are currently two approaches in Bayesian neural networks: explicit distributions of weights can be included in a network \cite{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing uncertainty \cite{gal2016dropout}.
+%  There are currently two approaches in Bayesian neural networks: explicit distributions of weights can be included in a network \cite{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing uncertainty \cite{gal2016dropout}.
 We use the former approach and impose prior distributions on the neural network's weights to obtain the posterior distributions of weights and posterior predictive distributions of target variables.
@@
 
-  In this paper, we propose a method to propagate uncertainty through the soft thresholding nonlinearity.
+A novel method to propagate uncertainty through the soft thresholding nonlinearity is proposed in this paper.
 At every layer the current distribution of the target vector is represented as a spike and slab distribution \cite{mitchell1988bayesian}, which represents the probabilities of each variable being zero, or Gaussian-distributed.
-We show that the spike and slab distribution of target vectors can be effectively combined with Gaussian weights of dense layers.
+%We show that the spike and slab distribution of target vectors can be effectively combined with Gaussian weights of dense layers.
 The distribution of the target vector propagated through a dense layer and the soft thresholding nonlinearity can then be closely approximated with a distribution from the same family.
-The proposed method of uncertainty propagation for the soft thresholding nonlinearity allows us to derive the gradients of the logarithms of normalisation constants, which can be used to update a weight distribution.
-We then develop a highly efficient Bayesian inference algorithm based on the probabilistic backpropagation paradigm while significantly expanding it.
+Using the proposed method of uncertainty propagation for the soft thresholding nonlinearity, the gradients of the logarithms of normalisation constants are derived, which can be used to update a weight distribution.
+An efficient Bayesian inference algorithm is then developed based on the probabilistic backpropagation paradigm while significantly expanding it.
+A novel Bayesian neural network for sparse coding is designed utilising both the proposed method of uncertainty propagation and Bayesian inference algorithm.
 
-  The main contributions of this paper are: (\textit{i}) for the first time we propose a method for uncertainty propagation through the soft thresholding nonlinearity for a Bayesian neural network; (\textit{ii}) we develop an efficient posterior inference algorithm for weights and outputs of neural networks with the soft thresholding nonlinearity; (\textit{iii}) we design a novel Bayesian neural network for sparse coding.
+  The main contributions of this paper are: (\textit{i}) for the first time a method for uncertainty propagation through the soft thresholding nonlinearity is proposed for a Bayesian neural network; (\textit{ii}) an efficient posterior inference algorithm for weights and outputs of neural networks with the soft thresholding nonlinearity is developed; (\textit{iii}) a novel Bayesian neural network for sparse coding is designed.
 
-  We introduce a novel Bayesian neural network in section \ref{sec:bayesian_lista} after reviewing neural networks for sparse coding in section \ref{sec:nn_sc}.
+ The rest of the paper is organised as follows.
+A novel Bayesian neural network is introduced in section \ref{sec:bayesian_lista}.
 The proposed forward uncertainty propagation and probabilistic backpropagation methods are given in sections \ref{sec:fprop} and \ref{sec:backpropagation}.
-We show the experimental results in section \ref{sec:experiments} and finish with discussion and conclusions in section \ref{sec:conclusions}.
+Section \ref{sec:experiments} provides the experimental results and section \ref{sec:conclusions} concludes the paper.
 
-\section{Neural networks for sparse coding}
-\label{sec:nn_sc}
+\section{Bayesian neural network for sparse coding}
+  \label{sec:bayesian_lista}
+  This section first reviews existing neural networks for sparse coding and then describes the novel Bayesian neural network.
+
+\subsection{Frequentist neural networks}  
+\label{subsec:nn_sc}
   The neural network approach to sparse coding is based on earlier Iterative Shrinkage and Thresholding Algorithm (\textsc{ista}) \cite{daubechies2004iterative}.
@@
   where $\lambda$ is a shrinkage parameter.
-  In \textsc{ista}, weights of the linear transformation are assumed fixed: $\mathbf{W} = \mathbf{X}^\top / E$, where $E$ is the upper bound of the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$, and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$, where $\mathbf{I}_{D \times D}$ is the identity matrix of size $D$.
+  In \textsc{ista}, weights of the linear transformation are assumed fixed: $\mathbf{W} = \mathbf{X}^\top / E$, where $E$ is the upper bound of the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$, and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$, where $\mathbf{I}_{D \times D}$ is the identity matrix of size~$D$.
 
-  In contrast to \textsc{ista}, Learned \textsc{ista} (\textsc{lista}) \cite{gregor2010learning} learns the values of matrices $\mathbf{W}$, $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
+  In contrast to \textsc{ista}, Learned \textsc{ista} (\textsc{lista}) \cite{gregor2010learning} learns the values of matrices $\mathbf{W}$ and $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
 To achieve this, the \textsc{ista} is limited with the fixed amount of iterations $L$ and interpreted as a recurrent neural network: every iteration $l$ of \textsc{ista} corresponds to the layer $l$ of \textsc{lista}.
@@
 
-  \begin{algorithm}[h]
+  \begin{algorithm}[t]
     \caption{\textsc{lista} forward propagation}
@@
       \REQUIRE observations $\mathbf{y}$, weights $\mathbf{W}, \mathbf{S}$, number of layers $L$
-      \STATE \textit{Initialisation.} Dense layer $\mathbf{b} \gets \mathbf{W}\mathbf{y}$ \label{eq:first_layer}
-      \STATE \textit{Initialisation.} Soft thresholding nonlinearity $\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$ \label{eq:thr_first}
+      \STATE Dense layer $\mathbf{b} \gets \mathbf{W}\mathbf{y}$ \label{eq:first_layer}
+      \STATE Soft thresholding nonlinearity~$\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$ \label{eq:thr_first}
       \FOR{$l=1$ \TO $L$}
@@
 
-  In \textsc{lista}, matrices $\mathbf{W}$, $\mathbf{S}$ are the parameters that are initialised as in the \textsc{ista} and then updated with the backpropagation algorithm.
+  In \textsc{lista}, matrices $\mathbf{W}$ and $\mathbf{S}$ are the parameters that are initialised as in the \textsc{ista} and then updated with the backpropagation algorithm.
 Vectors $\mathbf{c}_l$ and $\mathbf{b}$ are auxiliary vectors that describe forward propagation.
 
-  \section{Bayesian neural network for sparse coding}
-  \label{sec:bayesian_lista}
-  To formulate the Bayesian version of \textsc{lista} we impose the prior distributions on the unknown weights
+  \subsection{Baysian \textsc{lista}}
+  \label{subsec:bayesian_lista}
+  This section introduces the proposed Bayesian version of \textsc{lista}. The prior distributions are imposed on the unknown weights
   \begin{equation}
   \label{eq:ws}
-  p(\mathbf{W}) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij} ; 0, \eta^{-1}), \qquad
-  p(\mathbf{S}) = \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; 0, \eta^{-1}),
+  \begin{split}
+  p(\mathbf{W}) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij} ; 0, \eta^{-1}), \\
+  p(\mathbf{S}) &= \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; 0, \eta^{-1}),
+  \end{split}
   \end{equation}
@@
 
-  For every layer $l$ of Bayesian \textsc{lista}, we assume that $\widehat{\boldsymbol\beta}_{l}$ has the spike and slab distribution with the spike probability $\boldsymbol\omega$, the slab mean $\mathbf{m}$, and the slab variance $\mathbf{v}$
+  For every layer $l$ of Bayesian \textsc{lista}, $\widehat{\boldsymbol\beta}_{l}$ is assumed to have the spike and slab distribution with the spike probability $\boldsymbol\omega$, the slab mean $\mathbf{m}$, and the slab variance $\mathbf{v}$
   \begin{equation}
@@
   where $\delta_0$ is the delta-function that represents a spike, $[\cdot]_d$ denotes the $d$-th component of a vector.
-In section \ref{sec:fprop}, we show that the output of the next layer $\widehat{\boldsymbol\beta}_{l+1}$ can be approximated with a spike and slab distribution and, therefore, the output of the Bayesian \textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
+Section \ref{sec:fprop} shows that the output of the next layer $\widehat{\boldsymbol\beta}_{l+1}$ can be approximated with a spike and slab distribution and, therefore, the output of the Bayesian \textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
 
@@
   \label{eq:likelihood}
-  p(\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda) = \prod_{n=1}^N\prod_{d=1}^D\mathcal{N}\left(\beta_d^{(n)}; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}\right)
+  \begin{split}
+  p(\mathbf{B}| \mathbf{Y}, &\mathbf{W}, \mathbf{S}, \gamma, \lambda) \\
+  = &\prod_{n=1}^N\prod_{d=1}^D\mathcal{N}\left(\beta_d^{(n)}; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}\right)
+ \end{split}
   \end{equation}
-  We specify Gamma prior distributions with parameters~$a^{\cdot}$ and~$b^{\cdot}$ on the introduced Gaussian precisions
+  Gamma prior distributions with parameters~$a^{\cdot}$ and~$b^{\cdot}$ are specified on the introduced Gaussian precisions
   \begin{equation}
@@
   \label{eq:posterior}
-  p(\mathbf{W}, \mathbf{S}, \gamma, \eta | \mathbf{B}, \mathbf{Y}, \lambda) = \frac{p(\mathbf{B} | \mathbf{Y}, \mathbf{W},  \mathbf{S}, \gamma, \lambda) p(\mathbf{W} | \eta )p(\mathbf{S} | \eta) p(\eta) p(\gamma)}{p(\mathbf{B} | \mathbf{Y}, \lambda)}
+  \begin{split}
+  p(\mathbf{W}, \mathbf{S}, &\gamma, \eta | \mathbf{B}, \mathbf{Y}, \lambda) \\
+  = &\frac{p(\mathbf{B} | \mathbf{Y}, \mathbf{W},  \mathbf{S}, \gamma, \lambda) p(\mathbf{W} | \eta )p(\mathbf{S} | \eta) p(\eta) p(\gamma)}{p(\mathbf{B} | \mathbf{Y}, \lambda)}
+  \end{split}
   \end{equation}
@@
   \label{sec:fprop}
-  We modify \textsc{lista} forward propagation (Algorithm~\ref{alg:lista}) to include probability distributions of the random variables introduced in section~\ref{sec:bayesian_lista}.
-  We demonstrate that the output of every Bayesian \textsc{lista} layer $\widehat{\boldsymbol\beta}_l$ can be closely approximated with a spike and slab distribution.
-This leads to the proposed probabilistic backpropagation algorithm that is presented in section~\ref{sec:backpropagation}.
+  This section describes modification of \textsc{lista} forward propagation (Algorithm~\ref{alg:lista}) to include probability distributions of the random variables introduced in section~\ref{sec:bayesian_lista}.
 
   \subsection{Initialisation}
+  \label{subsec:forward_init}
   At step \ref{eq:first_layer} of \textsc{lista} (Algorithm~\ref{alg:lista}) the matrix $\mathbf{W}$ consists of Gaussian-distributed components $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y}$ is a deterministic vector.
-Since the sum of independent Gaussian-distributed variables is a Gaussian variable~\cite{eisenberg2008sum}, $\mathbf{b}$ is a vector of Gaussian-distributed components $b_d \sim \mathcal{N}(m^b_d, v^b_d)$
-  \begin{equation}
-  \label{eq:matrix_vector_product}
-  m^b_d = \sum_{k=1}^Ky_k m^w_{dk}, \qquad
-  v^b_d = \sum_{k=1}^Ky_k^2v^w_{dk}.
-  \end{equation}
+Then the output $\mathbf{b}$ is a vector of Gaussian-distributed components $b_d \sim \mathcal{N}(m^b_d, v^b_d)$, where $m^b_d = \sum_{k=1}^Ky_k m^w_{dk}$, and $v^b_d = \sum_{k=1}^Ky_k^2v^w_{dk}$.
+%  \begin{equation}
+%  \label{eq:matrix_vector_product}
+%  m^b_d = \sum_{k=1}^Ky_k m^w_{dk}, \qquad
+%  v^b_d = \sum_{k=1}^Ky_k^2v^w_{dk}.
+%  \end{equation}
 
   At step~\ref{eq:thr_first} of \textsc{lista} (Algorithm~\ref{alg:lista}) the Gaussian vector $\mathbf{b}$ is taken as an input of the soft thresholding function.
-
 When a Gaussian random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft thresholding function $x^* = h_{\lambda}(x)$, the probability mass of the resulting random variable $x^*$ is split into two parts.
@@
 The distribution of $x^* \neq 0$ then represents the tails of the original Gaussian distribution.
-
-  \begin{lemma}[Propagation of a Gaussian variable through soft thresholding]
-  \label{thm:soft_thresholding}
-  The distribution of $x^*$ can be parametrised by the probability of being zero, $\omega^*$, the mean $m^*$ and the variance $v^*$ of the truncated Gaussian distribution.
-  \end{lemma}
-
-  The proof of Lemma~\ref{thm:soft_thresholding} and expressions for $\omega^*$, $m^*$ and $v^*$ are given in the supplementary materials.
-Based on the results of Lemma~\ref{thm:soft_thresholding}, we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ at step~\ref{eq:thr_first} with a spike and slab distribution with parameters derived in the lemma: the spike probability $\omega$ is equal to $\omega^*$, the slab mean $m$ and variance $v$ are set to the corresponding parameters of the truncated Gaussian $m^*$ and $v^*$.
-The quality of this approximation is discussed in the supplementary materials.
+The distribution of $x^*$ can be then parametrised by the probability of being zero, $\omega^*$, the mean $m^*$ and the variance $v^*$ of the truncated Gaussian distribution.
+%  \begin{lemma}[Propagation of a Gaussian variable through soft thresholding]
+%  \label{thm:soft_thresholding}
+%  The distribution of $x^*$ can be parametrised by the probability of being zero, $\omega^*$, the mean $m^*$ and the variance $v^*$ of the truncated Gaussian distribution.
+%  \end{lemma}
+ %Based on the results of Lemma~\ref{thm:soft_thresholding}, 
+ Therefore, we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ at step~\ref{eq:thr_first} with a spike and slab distribution with the corresponding parameters: the spike probability $\omega^*$, the slab mean $m^*$ and variance $v^*$.
 
   \subsection{Main layers}
-  At step \ref{eq:l_dense_layer} of \textsc{lista} (Algorithm~\ref{alg:lista}) the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables.
-In order to determine the distribution of the output $\mathbf{c}_l$ we first formulate two lemmas.
+  At step \ref{eq:l_dense_layer} of \textsc{lista} (Algorithm~\ref{alg:lista}) the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components: $b_d \sim \mathcal{N}(m^b_d, v^b_d)$, $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables: $[\widehat{\beta}_{l-1}]_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
 
-  \begin{lemma}[Moments of a spike and slab distribution]
-  \label{thm:moments_spsl}
-  Let a random variable $\xi$ have a spike and slab distribution with the probability of spike $\omega$, the slab mean $m$ and slab variance $v$. Then its moments are
+ It can be shown that the expected value and variance of a spike and slab distributed variable $\xi$ with the probability of spike $\omega$, the slab mean $m$ and slab variance $v$ are:  
    \begin{equation}
+   \label{eq:spsl_moments}
   \mathbb{E}\xi = (1-\omega)m, \qquad \operatorname{Var}\xi = (1-\omega)(v + \omega m^2)
   \end{equation}
-  \end{lemma}
 
-  \begin{lemma}[Product of a Gaussian matrix and a spike and slab vector]
-    \label{thm:matrix_vector}
-  Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta }\in \mathbb{R}^D$ be a vector with spike-and-slab-distributed variables: $\widehat{\beta}_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
+ It can also be shown that if components of the matrix $\mathbf{S}$ and vector $\widehat{\boldsymbol\beta}_{l-1}$ are mutually independent then the components $[ \mathbf{e}_l ]_d$ of their product $\mathbf{e}_l = \mathbf{S} \widehat{\boldsymbol\beta}_{l-1}$ have the marginal mean and variances:
+  \begin{subequations}
+  \label{eq:e_moments}
+  \begin{align}
+  m^e_{d} \stackrel{\text{def}}{=} &\mathbb{E}[ \mathbf{e}_l ]_d = \sum_{d'=1}^D m^s_{dd'}(1-\omega_{d'})m_{d'}, \\
+   \begin{split}
+  v^e_{d} \stackrel{\text{def}}{=} &\operatorname{Var}[ \mathbf{e}_l ]_d = \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} \\
+   + &(1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}].
+   \end{split}
+   \end{align}
+  \end{subequations}
+
+ If the matrix $\mathbf{S}$ and vector $\widehat{\boldsymbol\beta}_{l-1}$ are assumed to be mutually independent, then according to the Central Limit Theorem $[ \mathbf{e}_l ]_d$ can be approximated as a Gaussian-distributed variable when $D$ is sufficiently large.
+The parameters of the of the approximating Gaussian distribution are set to the marginal mean and variance given in~(\ref{eq:e_moments}).
+
+%  In order to determine the distribution of the output $\mathbf{c}_l$ we first formulate two lemmas.
+%  
+%%  \begin{lemma}[Moments of a spike and slab distribution]
+%%  \label{thm:moments_spsl}
+%%  Let a random variable $\xi$ have a spike and slab distribution with the probability of spike $\omega$, the slab mean $m$ and slab variance $v$. Then its moments are
+%%  \begin{equation}
+%%  \mathbb{E}\xi = (1-\omega)m, \qquad \operatorname{Var}\xi = (1-\omega)(v + \omega m^2)
+%%  \end{equation}
+%%  \end{lemma}
+%  
+%  \begin{lemma}[Product of a Gaussian matrix and a spike and slab vector]
+%    \label{thm:matrix_vector}
+%  Let $\mathbf{S} \in \mathbb{R}^{D \times D}$ be a matrix of independent Gaussian-distributed random variables: $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta }\in \mathbb{R}^D$ be a vector with spike-and-slab-distributed variables: $\widehat{\beta}_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
 The components of the matrix $\mathbf{S}$ and the vector $\widehat{\boldsymbol\beta}$ are mutually independent.
@@
 Then the marginal mean and variance of the elements $e_d$ of the vector $\mathbf{e}$ are
-  \begin{subequations}
-  \begin{align}
-   \mathbb{E}e_d &= \sum_{d'=1}^D m^s_{dd'}(1-\omega_{d'})m_{d'}, \\
-   \begin{split}
-   \operatorname{Var}e_d &= \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} + (1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}].
-   \end{split}
-   \end{align}
-  \end{subequations}
-   \end{lemma}
-
-  The proofs of Lemmas~\ref{thm:moments_spsl} and~\ref{thm:matrix_vector} are given in the supplementary materials.
-
-  Let $\mathbf{e}_l$ denote the product $\mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at step \ref{eq:l_dense_layer} of \textsc{lista}.
+%  \begin{subequations}
+%  \begin{align}
+%   \mathbb{E}e_d &= \sum_{d'=1}^D m^s_{dd'}(1-\omega_{d'})m_{d'}, \\
+%   \begin{split}
+%   \operatorname{Var}e_d &= \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} + (1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}].
+%   \end{split}
+%   \end{align}
+%  \end{subequations}
+%   \end{lemma}
+%  
+%  The proofs of Lemmas~\ref{thm:moments_spsl} and~\ref{thm:matrix_vector} are given in the supplementary materials.
+%  
+%  Let $\mathbf{e}_l$ denote the product $\mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at step \ref{eq:l_dense_layer} of \textsc{lista}.
 We assume that $\mathbf{S}$ and $\widehat{\boldsymbol\beta}_{l-1}$ are mutually independent.
@@
   The output $\mathbf{c}_l$ at step \ref{eq:l_dense_layer} is then represented as a sum of two Gaussian-distributed vectors: $\mathbf{b}$ and~$\mathbf{e}_l$, i.e.
-it is a Gaussian-distributed vector with components $c_{d} \sim \mathcal{N}(m^c_{d}, v^c_{d})$
-  \begin{equation}
-  \label{eq:sum_vectors}
-  m^c_{d} = m^b_{d} + m^e_{d}, \qquad
-  v^c_{d} = v^b_{d} + v^e_{d}.
-  \end{equation}
+it is a Gaussian-distributed vector with components $c_{d} \sim \mathcal{N}(m^c_{d}, v^c_{d})$, where $m^c_{d} = m^b_{d} + m^e_{d}$ and $v^c_{d} = v^b_{d} + v^e_{d}$.
+%  \begin{equation}
+%  \label{eq:sum_vectors}
+%  m^c_{d} = m^b_{d} + m^e_{d}, \qquad
+%  v^c_{d} = v^b_{d} + v^e_{d}.
+%  \end{equation}
 
-  Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of \textsc{lista} (Algorithm~\ref{alg:lista}) is the result of soft thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first}.
-
-  \subsection{Bayesian \textsc{lista} forward propagation}
-  We have covered all steps of Bayesian \textsc{lista} and derived distributions for outputs of these steps.
-Now we can formulate the main result of this section that describes how the proposed uncertainty propagation scheme works.
-
-  \begin{enumerate}
-    \item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is the Gaussian distribution with parameters computed according to (\ref{eq:matrix_vector_product});
-    \item $\widehat{\boldsymbol\beta}_{0} = h_\lambda(\mathbf{b})$ is approximated with the spike and slab distribution, which parameters are computed according to Lemma \ref{thm:soft_thresholding}.
-    \item $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is approximated with the Gaussian distribution, which parameters are computed according to Lemma \ref{thm:matrix_vector};
-    \item $\mathbf{c}_l = \mathbf{b} + \mathbf{e}_l$ is the Gaussian distribution with parameters computed according to (\ref{eq:sum_vectors});
-    \item $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$ is approximated with the spike and slab distribution, which parameters are computed according to Lemma \ref{thm:soft_thresholding}.
-  \end{enumerate}
-
-  %\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_nmse_valid}}
-
-  %\begin{figure}[t]
-  %\includegraphics[width=\columnwidth]{d_testing}
-  %\caption{Approximation of product of Gaussians.}
-  %\label{fig:d_testing}
-  %\end{figure}
-  %
-  %\begin{figure}[t]
-  %\includegraphics[width=\columnwidth]{z_new_testing}
-  %\caption{Approximation of propagation through soft thresholding}
-  %\label{fig:z_new_testing}
-  %\end{figure}
+  Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of \textsc{lista} (Algorithm~\ref{alg:lista}) is the result of soft thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first} (section~\ref{subsec:forward_init}).
+  Thus, all the steps of Bayesian \textsc{lista} are covered and distributions for outputs of these steps are derived.
 
@@
   \begin{split}
-  q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} ; m^w_{dk}, v^w_{dk}) \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; m^s_{d'd''}, v^s_{d'd''}) \\
+  q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} ; m^w_{dk}, v^w_{dk}) \\
+  &\times\prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; m^s_{d'd''}, v^s_{d'd''}) \\
   &\times \text{Gam}(\gamma; a^\gamma, b^\gamma) \text{Gam}(\eta; a^\eta, b^\eta)
@@
 
-  For Bayesian inference we expand the probabilistic backpropagation algorithm~\cite{hernandez2015probabilistic} for updating parameters of distributions.
-They are updated with the assumed density filtering (ADF) and expectation propagation (EP) algorithms based on the derivatives of the logarithm of a normalisation constant.
+  Parameters of approximating distributions are updated with the assumed density filtering (ADF) and expectation propagation (EP) algorithms derived on the derivatives of the logarithm of a normalisation constant (based on~\cite{hernandez2015probabilistic}).
 ADF iteratively incorporates factors from the true posterior $p$ in (\ref{eq:posterior}) into the factorised approximating distribution $q$ in (\ref{eq:approximating_dsitribution}), whereas EP iteratively replaces factors in $q$ by factors from $p$.
@@
   where $Z$ is the normalisation constant and $f(a)$ is an arbitrary function, $a \in \{w_{dk}, s_{d'd''}\}$.
-
 According to \cite{minka2001thesis}, new parameters of the Gaussian distribution for $a$ can be computed as
@@
   \label{eq:param_update}
-  m^{\text{new}} = m + v \frac{\partial \log Z}{\partial m}, \qquad
-  v^{\text{new}} = v - v^2\left[ \left(\frac{\partial \log Z}{\partial m}\right)^2 - 2 \frac{\partial \log Z}{\partial v}\right]
+  m:= m + v \frac{\partial \log Z}{\partial m}, \,
+  v:= v - v^2\left[ \left(\frac{\partial \log Z}{\partial m}\right)^2 - 2 \frac{\partial \log Z}{\partial v}\right]
   \end{equation}
@@
 
-  With the likelihood factors~(\ref{eq:likelihood}) of the true posterior we employ the ADF approach and iteratively incorporate them into the approximating distribution $q$.
-The normalisation constant of the approximating distribution $q$ with the likelihood term for the data point $n$ incorporated can be computed as follows (to simplify notation the superscript $(n)$ is omitted)
+  With the likelihood factors~(\ref{eq:likelihood}) of the true posterior the ADF approach is employed and they are iteratively incorporated into $q$.
+The normalisation constant of $q$ with the likelihood term for the data point $n$ incorporated is (to simplify notation the superscript $(n)$ is omitted)
   \begin{equation}
-  Z  = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
+  \begin{split}
+  Z  = & \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}) \\
+  &\times q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
+  \end{split}
   \end{equation}
-  Assuming the spike and slab distribution for $\widehat{\boldsymbol\beta}$, the normalisation constant can be approximated as \footnote{Full derivation of the normalisation constant is given in the supplementary materials.}
+  Assuming the spike and slab distribution for $\widehat{\boldsymbol\beta}$, the normalisation constant can be approximated as
   \begin{equation}
   \label{eq:Z}
-  Z \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right],
+  \begin{split}
+  Z \approx & \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) \right.\\
+  &\left. + (1 - \omega^{\widehat{\boldsymbol\beta}}_d)\mathcal{N}(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d)\right],
+  \end{split}
   \end{equation}
   where $\{\omega^{\widehat{\boldsymbol\beta}}_d, m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\}$ are the parameters of the spike and slab distribution for $[\widehat{\boldsymbol\beta}]_d$.
-Parameters of the approximating posterior distribution $q$ are then updated with the derivatives of this normalisation constant according to (\ref{eq:param_update}).
+Parameters of $q$ are then updated with the derivatives of this normalisation constant according to (\ref{eq:param_update}).
 
-  Prior factors (\ref{eq:ws}), (\ref{eq:gamma_eta}) from $p$ are incorporated into $q$ with the EP algorithm~\cite{hernandez2015probabilistic}, i.e.
-they replace the corresponding approximating factors from $q$, and then $q$ is updated to minimise the KL divergence.
+  Prior factors (\ref{eq:ws}) and (\ref{eq:gamma_eta}) from $p$ are incorporated into $q$ with the EP algorithm~\cite{hernandez2015probabilistic}, i.e.
+they replace the corresponding approximating factors from $q$, and then $q$ is updated to minimise the Kullback–Leibler divergence.
 
@@
   \label{sec:experiments}
-  The proposed Bayesian \textsc{lista} model is evaluated in the context of the sparse coding problem with an overcomplete dictionary, where the number of measurements $K$ is much smaller than the dimensionality of the vector $\boldsymbol\beta$.
-
-  We compare Bayesian \textsc{lista} with \textsc{lista}~\cite{gregor2010learning} in terms of predictive accuracy.
-As baselines we also use \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
-\textsc{fista} adds the momentum to the \textsc{ista} and improves its convergence speed.
-We set the number of iterations in these algorithms and the number of layers in Bayesian and classic \textsc{lista} networks to $L$.
-To measure the performance of the algorithms the normalised mean square error (\textsc{nmse}) and F measure are used\footnote{\textsc{nmse} and F measure are defined in the supplementary materials.}.
-We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn.
+  The proposed Bayesian \textsc{lista} model is evaluated in the context of the sparse coding problem.
+Bayesian \textsc{lista} is compared with \textsc{lista}~\cite{gregor2010learning}, \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
+The number of iterations in \textsc{ista} and \textsc{fista}  and the number of layers in Bayesian and classic \textsc{lista} networks is $L$.
+For quantitative comparison the normalised mean square error (\textsc{nmse}) and F measure are used.
+%We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn.
 
@@
 To simulate observations $\mathbf{y}^{(n)}$, we generate the random Gaussian design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$.
-The observations are generated according to (\ref{eq:regression_problem}) with the zero-mean Gaussian noise with the standard deviation $0.5$.
+The observations are generated according to~(\ref{eq:regression_problem}) with the zero-mean Gaussian noise with the standard deviation $0.5$.
 The shrinkage parameter is set to~$\lambda = 0.1$.
@@
 
-  In Figures \ref{fig:nmse_n_layers_synthetic} and \ref{fig:f_meas_n_layers_synthetic} predictive performance for different number of layers $L$ is presented.
+  In Figures \ref{fig:nmse_n_layers_synthetic} and \ref{fig:f_meas_n_layers_synthetic} predictive performance for different number of layers (or iterations) $L$ is presented.
 The observation size is set to $K=50$.
@@
 
-  \begin{figure}[h]
+  \begin{figure}[t]
   \centering
@@
   %~
-  \subfloat[\textsc{nmse} for different $L$]{\includegraphics[width=0.4\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}
+  \subfloat[\textsc{nmse} for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}
   \label{fig:nmse_n_layers_synthetic}}
@@
   %~
-  \subfloat[F measure for different $L$]{\includegraphics[width=0.4\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}
+  \subfloat[F measure for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}
   \label{fig:f_meas_n_layers_synthetic}}\\[-13pt]
-  \subfloat[\textsc{nmse} for different $K$]{\includegraphics[width=0.4\columnwidth]{graphics/synthetic_undersampling/nmse_validation}
+  \subfloat[\textsc{nmse} for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/nmse_validation}
   \label{fig:nmse_undersampling_synthetic}}
@@
   %~
-  \subfloat[F measure for different $K$]{\includegraphics[width=0.4\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}
+  \subfloat[F measure for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}
   \label{fig:f_meas_undesampling_synthetic}}
@@
   Figures~\ref{fig:nmse_undersampling_synthetic} and~\ref{fig:f_meas_undesampling_synthetic} give the results of predictive performance for different observation sizes $K$.
-The number of layers is set as $L=4$.
+The number of layers (iterations) is set as $L=4$.
 In the previous experiment, Bayesian and classic \textsc{lista} show similar results with this number of layers.
@@
 
-  %We compare two versions of the proposed Bayesian LISTA: with shared weight matrices and with individual matrices at each layer --- and LISTA.
-
-  %The NMSE is presented in figure \ref{fig:validation_synthetic}.
-  %\begin{figure}[t]
-  %\includegraphics[width=\columnwidth]{loss_synthetic}
-  %\caption{Validation NMSE on synthetic data}
-  %\label{fig:validation_synthetic}
-  %\end{figure}
-
   \subsection{Predictive performance on \textsc{mnist} data}
-  In this experiment we evaluate Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \cite{lecun1998gradient}.
+  In this experiment the methods are evaluated on the \textsc{mnist} dataset \cite{lecun1998gradient}.
 The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
@@
 We use $100$ images for training and $100$ for test.
-The shrinkage parameter $\lambda$ is fixed as $0.1$.
+The shrinkage parameter $\lambda$ is fixed as~$0.1$.
 
@@
 Both baselines are unable to perform well in these experiments.
-Further results on investigation of the predicted posterior and clock time comparison are given in the supplementary materials.
 
@@
   %~
-  \subfloat[\textsc{nmse} for $K = 100$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/100_nmse_valid}}
+  \subfloat[\textsc{nmse} for $K = 100$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/100_nmse_valid}}
   %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
   %~
-  \subfloat[F measure for $K = 100$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/100_f_measure_valid}}\\[-13pt]
-  \subfloat[\textsc{nmse} for $K = 250$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/250_nmse_valid}}
+  \subfloat[F measure for $K = 100$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/100_f_measure_valid}}\\[-13pt]
+  \subfloat[\textsc{nmse} for $K = 250$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/250_nmse_valid}}
   %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
   %~
-  \subfloat[F measure for $K = 250$]{\includegraphics[width=0.4\columnwidth]{graphics/mnist/250_f_measure_valid}}
+  \subfloat[F measure for $K = 250$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/250_f_measure_valid}}
   \caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the observation size $K = 100$ (the top row) and $K = 250$ (the bottom row)}
@@
 One of the popular approaches in active learning is uncertainty sampling, when the data with the least certain predictions is chosen for labelling.
-We use a variance from Lemma~\ref{thm:moments_spsl} as a measure of uncertainty.
+We use a variance (\ref{eq:spsl_moments}) as a measure of uncertainty.
 
@@
 This means that the posterior distribution learnt by Bayesian \textsc{lista} is an adequate estimate of the true posterior.
-  \begin{figure}[h]
+  \begin{figure}[t]
   \centering
-  \subfloat[\textsc{nmse}]{\includegraphics[width=0.4\columnwidth]{graphics/active_mnist/nmse_validation}}%
-  \subfloat[F measure]{\includegraphics[width=0.4\columnwidth]{graphics/active_mnist/f_measure_validation}}
+  \subfloat[\textsc{nmse}]{\includegraphics[width=0.48\columnwidth]{graphics/active_mnist/nmse_validation}}%
+  \subfloat[F measure]{\includegraphics[width=0.48\columnwidth]{graphics/active_mnist/f_measure_validation}}
   \caption{Performance for the active learning experiment on the \textsc{mnist} data. }
@@
   To the best of our knowledge, this is the first implementation of a Bayesian deep sparse coding algorithm.
-Although there are works on Bayesian sparsity in context of neural networks \cite{he2017bayesian}, they are not the Bayesian neural networks in the same sense as Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
+%Although there are works on Bayesian sparsity in context of neural networks \cite{he2017bayesian}, they are not the Bayesian neural networks in the same sense as Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
 We find not only correct predictions but also useful posterior estimates for the predictions.
-
-  We have presented the new method for propagating uncertainty through the soft thresholding function. %To achieve this goal
-  We have approximated the outputs of the function with a spike and slab distribution, and we have shown that this distribution can stay within the same family after linear transformation with Gaussian weights and inputs of a neural network.
+  We have presented the new method for propagating uncertainty through the soft thresholding function.
+  %We have approximated the outputs of the function with a spike and slab distribution, and we have shown that this distribution can stay within the same family after linear transformation with Gaussian weights and inputs of a neural network.
   This allowed us to propose the Bayesian \textsc{lista} network and efficient inference algorithm that learns the distributions of the weights and makes the uncertainty estimates of the outputs.
-The forward propagation in the algorithm is based on the proposed uncertainty propagation method, the backward propagation is based on the probabilistic backpropagation method, that was remarkably expanded to account for multidimensionality of inputs and outputs, likelihood of Bayesian \textsc{lista} and its recurrent nature.
+%The forward propagation in the algorithm is based on the proposed uncertainty propagation method, the backward propagation is based on the probabilistic backpropagation method, that was remarkably expanded to account for multidimensionality of inputs and outputs, likelihood of Bayesian \textsc{lista} and its recurrent nature.
 

### 2018-10-23 icassp_2019/paper.tex
remove useless things

@@
 \begin{abstract}
-  While deep learning has an overwhelming success, uncertainty estimation is still a challenge for most modern deep learning methods.
-Bayesian learning allows to estimate the uncertainty of predictions in neural networks by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
-We propose a novel method of propagating the uncertainty through the soft thresholding nonlinearity.
-The method expands the area of Bayesian neural networks and enables the soft thresholding nonlinearity to be included in Bayesian deep neural networks for the first time.
+  Deep learning is actively used in the area of sparse coding.
+In current methods uncertainty of predictions is rarely estimated, thus providing the results that lack the quantitative justification.
+Bayesian learning provides the way to estimate the uncertainty of predictions in neural networks by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
+We propose a novel method of propagating the uncertainty through the sparsity-promoiting layers of neural networks for the first time.
 As an example, we design a Bayesian Learned Iterative Shrinkage-Thresholding network (Bayesian \textsc{lista}).
@@
 
-  The idea of Bayesian learning in neural networks \cite{neal2012bayesian} has recently regained its attention with the development of distributed approximate inference techniques \cite{li2015stochastic, hoffman2013stochastic} and general boost in popularity of deep learning.
-In addition to algorithms' predictions themselves, Bayesian learning naturally provides the uncertainty estimates of these predictions.
+  The idea of Bayesian learning in neural networks~\cite{neal2012bayesian} has recently gained an attention with the development of distributed approximate inference techniques~\cite{li2015stochastic, hoffman2013stochastic} and general boost in popularity of deep learning.
+In addition to predictions, Bayesian learning naturally provides the uncertainty estimates of these predictions.
 These uncertainty estimates are vital, e.g., in spheres that affect people's health, such as self-driving cars or medicine.
@@
 
-%  There are currently two approaches in Bayesian neural networks: explicit distributions of weights can be included in a network \cite{hernandez2015probabilistic, ranganath2015deep}, or dropout can be interpreted as an element introducing uncertainty \cite{gal2016dropout}.
-We use the former approach and impose prior distributions on the neural network's weights to obtain the posterior distributions of weights and posterior predictive distributions of target variables.
-
   In this paper, we consider the area of sparse coding.
 The sparse coding problem can be viewed as a linear regression problem with the additional assumption that the majority of the basis representation coefficients should be zeros.
-This sparsity assumption may be represented as $l1$ penalty~\cite{tibshirani1996regression}, or, in Bayesian interpretation, as a prior that has a sharp peak at zero~\cite{tipping2001sparse}.
-One of the modern approaches for sparse coding utilises neural networks with the soft thresholding nonlinearity~\cite{gregor2010learning, sprechmann2015learning}.
-At every layer this nonlinearity shifts current estimates of the target vectors towards zero, which allows to achieve sparsity of the target vectors.
+This sparsity assumption may be represented as $l1$-penalty~\cite{tibshirani1996regression}, or, in Bayesian interpretation, as a prior that has a sharp peak at zero~\cite{tipping2001sparse}.
+One of the modern approaches for sparse coding utilises neural networks with the soft-thresholding nonlinearity~\cite{gregor2010learning, sprechmann2015learning}.
+At every layer this nonlinearity shifts current estimates of the target vectors towards zero, which allows to achieve sparsity.
 Sparse coding is widely used in different applications, such as compressive sensing~\cite{candes2008introduction}, image and video processing~\cite{mairal2014sparse, wang2015deep}, neuroscience~\cite{baillet1997bayesian, jas2017learning}.
 
-A novel method to propagate uncertainty through the soft thresholding nonlinearity is proposed in this paper.
-At every layer the current distribution of the target vector is represented as a spike and slab distribution \cite{mitchell1988bayesian}, which represents the probabilities of each variable being zero, or Gaussian-distributed.
-%We show that the spike and slab distribution of target vectors can be effectively combined with Gaussian weights of dense layers.
-The distribution of the target vector propagated through a dense layer and the soft thresholding nonlinearity can then be closely approximated with a distribution from the same family.
-Using the proposed method of uncertainty propagation for the soft thresholding nonlinearity, the gradients of the logarithms of normalisation constants are derived, which can be used to update a weight distribution.
-An efficient Bayesian inference algorithm is then developed based on the probabilistic backpropagation paradigm while significantly expanding it.
+  A novel method to propagate uncertainty through the soft-thresholding nonlinearity is proposed in this paper.
+At every layer the current distribution of the target vector is represented as a spike and slab distribution~\cite{mitchell1988bayesian}, which represents the probabilities of each variable being zero, or Gaussian-distributed.
+Using the proposed method of uncertainty propagation for the soft-thresholding nonlinearity, the gradients of the logarithms of normalisation constants are derived, which can be used to update a weight distribution.
 A novel Bayesian neural network for sparse coding is designed utilising both the proposed method of uncertainty propagation and Bayesian inference algorithm.
 
-  The main contributions of this paper are: (\textit{i}) for the first time a method for uncertainty propagation through the soft thresholding nonlinearity is proposed for a Bayesian neural network; (\textit{ii}) an efficient posterior inference algorithm for weights and outputs of neural networks with the soft thresholding nonlinearity is developed; (\textit{iii}) a novel Bayesian neural network for sparse coding is designed.
+  The main contributions of this paper are: (\textit{i}) for the first time a method for uncertainty propagation through the soft-thresholding nonlinearity is proposed for a Bayesian neural network; (\textit{ii}) an efficient posterior inference algorithm for weights and outputs of neural networks with the soft-thresholding nonlinearity is developed; (\textit{iii}) a novel Bayesian neural network for sparse coding is designed.
 
  The rest of the paper is organised as follows.
-A novel Bayesian neural network is introduced in section \ref{sec:bayesian_lista}.
-The proposed forward uncertainty propagation and probabilistic backpropagation methods are given in sections \ref{sec:fprop} and \ref{sec:backpropagation}.
-Section \ref{sec:experiments} provides the experimental results and section \ref{sec:conclusions} concludes the paper.
+A novel Bayesian neural network is introduced in Section~\ref{sec:bayesian_lista}.
+The proposed forward uncertainty propagation and probabilistic backpropagation methods are given in Sections~\ref{sec:fprop} and~\ref{sec:backpropagation}.
+Section~\ref{sec:experiments} provides the experimental results and Section~\ref{sec:conclusions} concludes the paper.
 
-\section{Bayesian neural network for sparse coding}
+\section{Neural networks for sparse coding}
   \label{sec:bayesian_lista}
@@
 
-  At every iteration $l$, \textsc{ista} obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ that is propagated through the soft thresholding function $h_\lambda(\cdot)$
+  At every iteration $l$, \textsc{ista} obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ that is propagated through the soft-thresholding function $h_\lambda(\cdot)$
   \begin{equation}
@@
       \STATE Dense layer $\mathbf{b} \gets \mathbf{W}\mathbf{y}$ \label{eq:first_layer}
-      \STATE Soft thresholding nonlinearity~$\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$ \label{eq:thr_first}
+      \STATE soft-thresholding nonlinearity~$\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$ \label{eq:thr_first}
       \FOR{$l=1$ \TO $L$}
         \STATE Dense layer $\mathbf{c}_l \gets \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ \label{eq:l_dense_layer}
-        \STATE Soft thresholding nonlinearity $\widehat{\boldsymbol\beta}_{l} \gets h_\lambda(\mathbf{c}_l)$ \label{eq:l_thr}
+        \STATE Soft-thresholding nonlinearity $\widehat{\boldsymbol\beta}_{l} \gets h_\lambda(\mathbf{c}_l)$ \label{eq:l_thr}
       \ENDFOR
@@
 
-  \subsection{Baysian \textsc{lista}}
+  \subsection{Bayesian \textsc{lista}}
   \label{subsec:bayesian_lista}
@@
 
-  \section{Uncertainty propagation through soft thresholding}
+  \section{Uncertainty propagation through soft-thresholding}
   \label{sec:fprop}
@@
 
-  At step~\ref{eq:thr_first} of \textsc{lista} (Algorithm~\ref{alg:lista}) the Gaussian vector $\mathbf{b}$ is taken as an input of the soft thresholding function.
-When a Gaussian random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft thresholding function $x^* = h_{\lambda}(x)$, the probability mass of the resulting random variable $x^*$ is split into two parts.
-The values of $x$ from the interval $[-\lambda, \lambda]$ are converted to~$0$ by the soft thresholding operator.
+  At step~\ref{eq:thr_first} of \textsc{lista} (Algorithm~\ref{alg:lista}) the Gaussian vector $\mathbf{b}$ is taken as an input of the soft-thresholding function.
+When a Gaussian random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft-thresholding function $x^* = h_{\lambda}(x)$, the probability mass of the resulting random variable $x^*$ is split into two parts.
+The values of $x$ from the interval $[-\lambda, \lambda]$ are converted to~$0$ by the soft-thresholding operator.
 Therefore, the probability mass of the original distribution that lies in $[-\lambda, \lambda]$ is squeezed into the probability of $x^*$ being zero.
@@
 The distribution of $x^*$ can be then parametrised by the probability of being zero, $\omega^*$, the mean $m^*$ and the variance $v^*$ of the truncated Gaussian distribution.
-%  \begin{lemma}[Propagation of a Gaussian variable through soft thresholding]
+%  \begin{lemma}[Propagation of a Gaussian variable through soft-thresholding]
 %  \label{thm:soft_thresholding}
@@
 
-  Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of \textsc{lista} (Algorithm~\ref{alg:lista}) is the result of soft thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first} (section~\ref{subsec:forward_init}).
+  Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of \textsc{lista} (Algorithm~\ref{alg:lista}) is the result of soft-thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first} (section~\ref{subsec:forward_init}).
   Thus, all the steps of Bayesian \textsc{lista} are covered and distributions for outputs of these steps are derived.
@@
 The number of iterations in \textsc{ista} and \textsc{fista}  and the number of layers in Bayesian and classic \textsc{lista} networks is $L$.
-For quantitative comparison the normalised mean square error (\textsc{nmse}) and F measure are used.
+For quantitative comparison the normalised mean square error (\textsc{nmse}) is used.
 %We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn.
@@
 
-  In Figures \ref{fig:nmse_n_layers_synthetic} and \ref{fig:f_meas_n_layers_synthetic} predictive performance for different number of layers (or iterations) $L$ is presented.
+  In \figurename~\ref{fig:nmse_n_layers_synthetic} the predictive performance for different number of layers (or iterations) $L$ is presented.
 The observation size is set to $K=50$.
-Bayesian \textsc{lista} outperforms \textsc{lista} in terms of both measures.
-Although the baselines \textsc{ista} and \textsc{fista} show better performance in terms of F measure, Bayesian \textsc{lista} has the lowest \textsc{nmse}.
+Bayesian \textsc{lista} outperforms \textsc{lista}.
 
@@
   %~
-  \subfloat[F measure for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}
-  \label{fig:f_meas_n_layers_synthetic}}\\[-13pt]
+  %\subfloat[F measure for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}
+  %\label{fig:f_meas_n_layers_synthetic}}\\[-13pt]
   \subfloat[\textsc{nmse} for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/nmse_validation}
@@
   %~
-  \subfloat[F measure for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}
-  \label{fig:f_meas_undesampling_synthetic}}
-  \caption{Predictive accuracy on the synthetic data: the top row for different numbers of layers (for neural networks) or iterations (for baselines),  the bottom row for different sizes of observations}
+  %\subfloat[F measure for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}
+  %\label{fig:f_meas_undesampling_synthetic}}
+  \caption{Predictive accuracy on the synthetic data: for different numbers of layers (for neural networks) or iterations (for baselines), and for different sizes of observations}
   \label{fig:number_of_layers_synthetic}
@@
 
-  Figures~\ref{fig:nmse_undersampling_synthetic} and~\ref{fig:f_meas_undesampling_synthetic} give the results of predictive performance for different observation sizes $K$.
+  \figurename~\ref{fig:nmse_undersampling_synthetic} gives the predictive performance for different observation sizes $K$.
 The number of layers (iterations) is set as $L=4$.
 In the previous experiment, Bayesian and classic \textsc{lista} show similar results with this number of layers.
-The results of Figures~\ref{fig:nmse_undersampling_synthetic} and~\ref{fig:f_meas_undesampling_synthetic} confirm this competitive behaviour between two \textsc{lista} networks.
+The results of \figurename~\ref{fig:nmse_undersampling_synthetic} confirm this competitive behaviour between two \textsc{lista} networks.
 Baselines show similar results in terms of F measure and underperform in terms of \textsc{nmse}.
@@
   %~
-  \subfloat[F measure for $K = 100$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/100_f_measure_valid}}\\[-13pt]
+  %\subfloat[F measure for $K = 100$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/100_f_measure_valid}}\\[-13pt]
   \subfloat[\textsc{nmse} for $K = 250$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/250_nmse_valid}}
@@
   %~
-  \subfloat[F measure for $K = 250$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/250_f_measure_valid}}
-  \caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the observation size $K = 100$ (the top row) and $K = 250$ (the bottom row)}
+  %\subfloat[F measure for $K = 250$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/250_f_measure_valid}}
+  \caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the observation size $K = 100$ and $K = 250$}
   \label{fig:mnist}
@@
   \subsection{Active learning}
-  To demonstrate a potential scenario that can benefit from uncertainty estimates of Bayesian \textsc{lista}, we consider the active learning example \cite{settles.tr09}.
+  To demonstrate a potential scenario that can benefit from uncertainty estimates of Bayesian \textsc{lista}, we consider the active learning example~\cite{settles.tr09}.
 The active learning area researches ways to select new training subsets to reduce the total number of required supervision.
@@
   Figure \ref{fig:active_learning_mnist} demonstrates performance of the active and non-active methods of updates with Bayesian \textsc{lista}.
-The active approach with uncertainty sampling steadily demonstrates better results in terms of both quality measures.
+The active approach with uncertainty sampling steadily demonstrates better results.
 This means that the posterior distribution learnt by Bayesian \textsc{lista} is an adequate estimate of the true posterior.
@@
   \subfloat[\textsc{nmse}]{\includegraphics[width=0.48\columnwidth]{graphics/active_mnist/nmse_validation}}%
-  \subfloat[F measure]{\includegraphics[width=0.48\columnwidth]{graphics/active_mnist/f_measure_validation}}
+  %\subfloat[F measure]{\includegraphics[width=0.48\columnwidth]{graphics/active_mnist/f_measure_validation}}
   \caption{Performance for the active learning experiment on the \textsc{mnist} data. }
@@
 We find not only correct predictions but also useful posterior estimates for the predictions.
-  We have presented the new method for propagating uncertainty through the soft thresholding function.
+  We have presented the new method for propagating uncertainty through the soft-thresholding function.
   %We have approximated the outputs of the function with a spike and slab distribution, and we have shown that this distribution can stay within the same family after linear transformation with Gaussian weights and inputs of a neural network.

### 2018-10-23 icassp_2019/paper.tex
minor

@@
 
- If the matrix $\mathbf{S}$ and vector $\widehat{\boldsymbol\beta}_{l-1}$ are assumed to be mutually independent, then according to the Central Limit Theorem $[ \mathbf{e}_l ]_d$ can be approximated as a Gaussian-distributed variable when $D$ is sufficiently large.
+ According to the Central Limit Theorem $[ \mathbf{e}_l ]_d$ can be approximated as a Gaussian-distributed variable when $D$ is sufficiently large.
 The parameters of the of the approximating Gaussian distribution are set to the marginal mean and variance given in~(\ref{eq:e_moments}).

### 2018-10-23 icassp_2019/paper.tex
shorten further, almost there

@@
 
-\address{$^{\star}$ Department of Automatic Control and Systems Engineering,\\
+\address{$^{\dagger}$ Department of Automatic Control and Systems Engineering,\\
 University of Sheffield, Sheffield S1 3JD, UK\\
 e-mail: dkuzin1@sheffield.ac.uk; l.s.mihaylova@sheffield.ac.uk.\\
-$^{\dagger}$ Department of Engineering Science,\\
+$^{\star}$ Department of Engineering Science,\\
 University of Oxford, Oxford OX1 2JD, UK\\
@@
 
-  In general, when distributions are included in a network, the complexity of Bayesian inference scales exponentially with the number of layers.
-Nevertheless, recently several techniques~\cite{ranganath2015deep, gal2016dropout} have been proposed to handle specific types of neural networks without this exponential growth.
+  Recently several techniques~\cite{ranganath2015deep, gal2016dropout} have been proposed to handle specific types of neural networks with efficient Bayesian inference.
 For example, feed-forward networks with the rectified linear unit nonlinearity~\cite{hernandez2015probabilistic}, networks with discrete distributions~\cite{soudry2014expectation}, recurrent networks~\cite{mcdermott2017bayesian}.
@@
 One of the modern approaches for sparse coding utilises neural networks with the soft-thresholding nonlinearity~\cite{gregor2010learning, sprechmann2015learning}.
-At every layer this nonlinearity shifts current estimates of the target vectors towards zero, which allows to achieve sparsity.
 Sparse coding is widely used in different applications, such as compressive sensing~\cite{candes2008introduction}, image and video processing~\cite{mairal2014sparse, wang2015deep}, neuroscience~\cite{baillet1997bayesian, jas2017learning}.
@@
 At every layer the current distribution of the target vector is represented as a spike and slab distribution~\cite{mitchell1988bayesian}, which represents the probabilities of each variable being zero, or Gaussian-distributed.
-Using the proposed method of uncertainty propagation for the soft-thresholding nonlinearity, the gradients of the logarithms of normalisation constants are derived, which can be used to update a weight distribution.
+Using the proposed method of uncertainty propagation, the gradients of the logarithms of normalisation constants are derived, which can be used to update a weight distribution.
 A novel Bayesian neural network for sparse coding is designed utilising both the proposed method of uncertainty propagation and Bayesian inference algorithm.
@@
 
- The rest of the paper is organised as follows.
+% The rest of the paper is organised as follows.
 A novel Bayesian neural network is introduced in Section~\ref{sec:bayesian_lista}.
@@
 It addresses the sparse coding problem as the linear regression problem with the $l1$ penalty that promotes sparsity.
-For the linear regression model with observations $\mathbf{y} \in \mathbb{R}^K$, the design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$, and the sparse unknown vector of weights $\boldsymbol\beta \in \mathbb{R}^D$, \textsc{ista} minimises the energy function $E(\cdot)$ to find $\boldsymbol\beta$
+For the linear regression model with observations $\mathbf{y} \in \mathbb{R}^K$, the design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$, and the sparse unknown vector of weights $\boldsymbol\beta \in \mathbb{R}^D$, \textsc{ista} minimises
   \begin{equation}
   \label{eq:regression_problem}
-  E(\mathbf{y}, \boldsymbol\beta) = ||\mathbf{X}\boldsymbol\beta - \mathbf{y}||_2^2 + \alpha ||\boldsymbol\beta||_1,
+  ||\mathbf{X}\boldsymbol\beta - \mathbf{y}||_2^2 + \alpha ||\boldsymbol\beta||_1
   \end{equation}
-  where $\alpha$ is the parameter that controls the influence of the sparse penalty.
+w.r.t.  $\boldsymbol\beta$,  where $\alpha$ is the penalty parameter.
 
-  At every iteration $l$, \textsc{ista} obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ that is propagated through the soft-thresholding function $h_\lambda(\cdot)$
+  At every iteration $l$, \textsc{ista} obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ propagated through the soft-thresholding function %$h_\lambda(\cdot)$
   \begin{equation}
@@
   where $\lambda$ is a shrinkage parameter.
-  In \textsc{ista}, weights of the linear transformation are assumed fixed: $\mathbf{W} = \mathbf{X}^\top / E$, where $E$ is the upper bound of the largest eigenvalue of $\mathbf{X}^\top\mathbf{X}$, and $\mathbf{S} = \mathbf{I}_{D \times D} - \mathbf{W}\mathbf{X}$, where $\mathbf{I}_{D \times D}$ is the identity matrix of size~$D$.
+  In \textsc{ista}, weights $\mathbf{W}$ and $\mathbf{S}$ of the linear transformation are assumed fixed.
 
@@
 To achieve this, the \textsc{ista} is limited with the fixed amount of iterations $L$ and interpreted as a recurrent neural network: every iteration $l$ of \textsc{ista} corresponds to the layer $l$ of \textsc{lista}.
-A coefficient vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$ is predicted according to Algorithm~\ref{alg:lista}.
+A vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$ is predicted by Algorithm~\ref{alg:lista}.
 
@@
 
-  In \textsc{lista}, matrices $\mathbf{W}$ and $\mathbf{S}$ are the parameters that are initialised as in the \textsc{ista} and then updated with the backpropagation algorithm.
+ % In \textsc{lista}, matrices $\mathbf{W}$ and $\mathbf{S}$ are the parameters that are initialised as in the \textsc{ista} and then updated with the backpropagation algorithm.
 Vectors $\mathbf{c}_l$ and $\mathbf{b}$ are auxiliary vectors that describe forward propagation.
@@
  %Based on the results of Lemma~\ref{thm:soft_thresholding}, 
- Therefore, we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ at step~\ref{eq:thr_first} with a spike and slab distribution with the corresponding parameters: the spike probability $\omega^*$, the slab mean $m^*$ and variance $v^*$.
+ Therefore, we approximate the distribution of $\widehat{\boldsymbol\beta}_0$ at step~\ref{eq:thr_first} with a spike and slab distribution with parameters: the spike probability $\omega^*$, the slab mean $m^*$ and variance $v^*$.
 
@@
    \label{eq:spsl_moments}
-  \mathbb{E}\xi = (1-\omega)m, \qquad \operatorname{Var}\xi = (1-\omega)(v + \omega m^2)
+  \mathbb{E}\xi = (1-\omega)m, \qquad \operatorname{Var}\xi = (1-\omega)(v + \omega m^2).
   \end{equation}
@@
   \end{subequations}
-
 According to the Central Limit Theorem $[ \mathbf{e}_l ]_d$ can be approximated as a Gaussian-distributed variable when $D$ is sufficiently large.
-The parameters of the of the approximating Gaussian distribution are set to the marginal mean and variance given in~(\ref{eq:e_moments}).
+The parameters of this Gaussian distribution are the marginal mean and variance given in~(\ref{eq:e_moments}).
 
@@
   \begin{align}
+  q(&\mathbf{W}, \mathbf{S}, \gamma, \eta) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} ; m^w_{dk}, v^w_{dk}) \text{Gam}(\gamma; a^\gamma, b^\gamma)\nonumber\\
   \label{eq:approximating_dsitribution}
-  \begin{split}
-  q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} ; m^w_{dk}, v^w_{dk}) \\
-  &\times\prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; m^s_{d'd''}, v^s_{d'd''}) \\
-  &\times \text{Gam}(\gamma; a^\gamma, b^\gamma) \text{Gam}(\eta; a^\eta, b^\eta)
-  \end{split}
+  &\times\prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; m^s_{d'd''}, v^s_{d'd''}) \text{Gam}(\eta; a^\eta, b^\eta).
   \end{align}
@@
 
-  When a factor from $p$ is incorporated into $q$, $q$ as a function of weights $\mathbf{W}$ and $\mathbf{S}$ has the form
-  \begin{equation}
-  q(a) = Z^{-1}f(a)\mathcal{N}(a; m, v)
-  \end{equation}
+  When a factor from $p$ is incorporated into $q$, $q$ has the form $q(a) = Z^{-1}f(a)\mathcal{N}(a; m, v)$ as a function of weights $\mathbf{W}$ and $\mathbf{S}$,
+%  \begin{equation}
+%  q(a) = Z^{-1}f(a)\mathcal{N}(a; m, v)
+%  \end{equation}
   where $Z$ is the normalisation constant and $f(a)$ is an arbitrary function, $a \in \{w_{dk}, s_{d'd''}\}$.
-According to \cite{minka2001thesis}, new parameters of the Gaussian distribution for $a$ can be computed as
+New parameters of the Gaussian distribution for $a$ can be computed as~\cite{minka2001thesis}
   \begin{equation}
@@
   \end{equation}
+Then for new values of $\mathbf{W}$ and $\mathbf{S}$ derivatives of the logarithm of $Z$ are required when the factor of $p$ is incorporated in $q$.
 
-  Then to find new values of $\mathbf{W}$ and $\mathbf{S}$ we need to compute derivatives of the logarithm of $Z$ when the factor of the true posterior $p$ is incorporated in $q$.
-
-  With the likelihood factors~(\ref{eq:likelihood}) of the true posterior the ADF approach is employed and they are iteratively incorporated into $q$.
-The normalisation constant of $q$ with the likelihood term for the data point $n$ incorporated is (to simplify notation the superscript $(n)$ is omitted)
+  With the likelihood factors~(\ref{eq:likelihood}) of $p$ the ADF approach is employed and they are iteratively incorporated into $q$.
+The normalisation constant of $q$ with the likelihood term for the data point $n$ incorporated is (let $z_d$ denote  $[f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d$) %(to simplify notation the superscript $(n)$ is omitted)
   \begin{equation}
-  \begin{split}
-  Z  = & \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}) \\
-  &\times q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
-  \end{split}
+  Z  = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; z_d, \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
   \end{equation}
@@
   where $\{\omega^{\widehat{\boldsymbol\beta}}_d, m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\}$ are the parameters of the spike and slab distribution for $[\widehat{\boldsymbol\beta}]_d$.
-Parameters of $q$ are then updated with the derivatives of this normalisation constant according to (\ref{eq:param_update}).
+Parameters of $q$ are then updated with the derivatives of $Z$ according to (\ref{eq:param_update}).
 
@@
   \label{sec:experiments}
-  The proposed Bayesian \textsc{lista} model is evaluated in the context of the sparse coding problem.
-Bayesian \textsc{lista} is compared with \textsc{lista}~\cite{gregor2010learning}, \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
+  The proposed Bayesian \textsc{lista} model is evaluated on sparse coding problems and compared with \textsc{lista}~\cite{gregor2010learning}, \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
 The number of iterations in \textsc{ista} and \textsc{fista}  and the number of layers in Bayesian and classic \textsc{lista} networks is $L$.
@@
   \subsection{Predictive performance on synthetic data}
-  First, the predictive performance of Bayesian \textsc{lista} is analysed on synthetic data.
-We generate $N_\text{train}=1000$ and $N_{\text{test}} = 100$ sparse coefficient vectors $\boldsymbol\beta^{(n)}$ of size $D = 100$  from the spike and slab distribution with the truncated slab: each component $\beta^{(n)}_{d}$ is zero with the probability~$0.8$ or is sampled from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability~$0.2$.
-To simulate observations $\mathbf{y}^{(n)}$, we generate the random Gaussian design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$.
-The observations are generated according to~(\ref{eq:regression_problem}) with the zero-mean Gaussian noise with the standard deviation $0.5$.
+  First, performance is analysed on synthetic data.
+We generate $N_\text{train}=1000$ and $N_{\text{test}} = 100$ sparse vectors $\boldsymbol\beta^{(n)}$ of size $D = 100$  from the spike and slab distribution with the truncated slab: each component $\beta^{(n)}_{d}$ is zero with the probability~$0.8$ or is sampled from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability~$0.2$.
+The design matrix $\mathbf{X}$ is random Gaussian.
+The observations $\mathbf{y}^{(n)}$ are generated as in~(\ref{eq:regression_problem}) with the zero-mean Gaussian noise with the standard deviation $0.5$.
 The shrinkage parameter is set to~$\lambda = 0.1$.
-We train the algorithms using the training data of size $N_\text{train}$ and measure performance on the test data of size $N_{\text{test}}$.
+The algorithms are trained on the training data of size $N_\text{train}$ and evaluated on the test data of size $N_{\text{test}}$.
 
-  In \figurename~\ref{fig:nmse_n_layers_synthetic} the predictive performance for different number of layers (or iterations) $L$ is presented.
+  In \figurename~\ref{fig:nmse_n_layers_synthetic} \textsc{nmse} for different number of layers (or iterations) $L$ is presented.
 The observation size is set to $K=50$.
-Bayesian \textsc{lista} outperforms \textsc{lista}.
-
+Bayesian \textsc{lista} outperforms competitors.
   \begin{figure}[t]
@@
   \end{figure}
-
-  \figurename~\ref{fig:nmse_undersampling_synthetic} gives the predictive performance for different observation sizes $K$.
+   \figurename~\ref{fig:nmse_undersampling_synthetic} gives \textsc{nmse} for different observation sizes $K$.
 The number of layers (iterations) is set as $L=4$.
@@
 The results of \figurename~\ref{fig:nmse_undersampling_synthetic} confirm this competitive behaviour between two \textsc{lista} networks.
-Baselines show similar results in terms of F measure and underperform in terms of \textsc{nmse}.
-Overall, the experiments on the synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
+\textsc{ista} and \textsc{fista} underperform the neural networks.
+%Overall, the experiments on the synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
 
   \subsection{Predictive performance on \textsc{mnist} data}
-  In this experiment the methods are evaluated on the \textsc{mnist} dataset \cite{lecun1998gradient}.
+  In this experiment, the methods are evaluated on the \textsc{mnist} dataset \cite{lecun1998gradient}.
 The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
-The design matrix $\mathbf{X}$ is generated as standard random Gaussian.
-The resulting size of $\mathbf{X}$ is $K \times 784$.
-Then we generate observations as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta \in \mathbb{R}^{784}$ are flattened images.
+The design matrix $\mathbf{X}$ is standard random Gaussian.
+Observations are generated as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta \in \mathbb{R}^{784}$ are flattened images.
 We use $100$ images for training and $100$ for test.
-The shrinkage parameter $\lambda$ is fixed as~$0.1$.
+The shrinkage parameter $\lambda$ is~$0.1$.
 

### 2018-10-23 icassp_2019/paper.tex
icassp paper: shortened further, fit to 4 pages

@@
 In current methods uncertainty of predictions is rarely estimated, thus providing the results that lack the quantitative justification.
-Bayesian learning provides the way to estimate the uncertainty of predictions in neural networks by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
-We propose a novel method of propagating the uncertainty through the sparsity-promoiting layers of neural networks for the first time.
-As an example, we design a Bayesian Learned Iterative Shrinkage-Thresholding network (Bayesian \textsc{lista}).
+Bayesian learning provides the way to estimate the uncertainty of predictions in neural networks (NNs) by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
+We propose a novel method of propagating the uncertainty through the sparsity-promoiting layers of NNs for the first time.
+We design a Bayesian Learned Iterative Shrinkage-Thresholding network (Bayes\textsc{lista}).
 An efficient posterior inference algorithm based on probabilistic backpropagation is developed.
-A series of experiments on sparse coding shows that the proposed framework provides both accurate predictions and sensible estimates of uncertainty in these predictions.
+Experiments on sparse coding show that the proposed framework provides both accurate predictions and sensible estimates of uncertainty in these predictions.
 \end{abstract}
@@
 
-  The idea of Bayesian learning in neural networks~\cite{neal2012bayesian} has recently gained an attention with the development of distributed approximate inference techniques~\cite{li2015stochastic, hoffman2013stochastic} and general boost in popularity of deep learning.
+  The idea of Bayesian learning in neural networks (NNs)~\cite{neal2012bayesian} has recently gained an attention with the development of distributed approximate inference techniques~\cite{li2015stochastic, hoffman2013stochastic} and general boost in popularity of deep learning.
 In addition to predictions, Bayesian learning naturally provides the uncertainty estimates of these predictions.
@@
 
-  Recently several techniques~\cite{ranganath2015deep, gal2016dropout} have been proposed to handle specific types of neural networks with efficient Bayesian inference.
+  Recently several techniques~\cite{ranganath2015deep, gal2016dropout} have been proposed to handle specific types of NNs with efficient Bayesian inference.
 For example, feed-forward networks with the rectified linear unit nonlinearity~\cite{hernandez2015probabilistic}, networks with discrete distributions~\cite{soudry2014expectation}, recurrent networks~\cite{mcdermott2017bayesian}.
@@
 This sparsity assumption may be represented as $l1$-penalty~\cite{tibshirani1996regression}, or, in Bayesian interpretation, as a prior that has a sharp peak at zero~\cite{tipping2001sparse}.
-One of the modern approaches for sparse coding utilises neural networks with the soft-thresholding nonlinearity~\cite{gregor2010learning, sprechmann2015learning}.
+One of the modern approaches for sparse coding utilises NNs with the soft-thresholding nonlinearity~\cite{gregor2010learning, sprechmann2015learning}.
 Sparse coding is widely used in different applications, such as compressive sensing~\cite{candes2008introduction}, image and video processing~\cite{mairal2014sparse, wang2015deep}, neuroscience~\cite{baillet1997bayesian, jas2017learning}.
@@
 Using the proposed method of uncertainty propagation, the gradients of the logarithms of normalisation constants are derived, which can be used to update a weight distribution.
-A novel Bayesian neural network for sparse coding is designed utilising both the proposed method of uncertainty propagation and Bayesian inference algorithm.
+A novel Bayesian NN for sparse coding is designed utilising both the proposed method of uncertainty propagation and Bayesian inference algorithm.
 
-  The main contributions of this paper are: (\textit{i}) for the first time a method for uncertainty propagation through the soft-thresholding nonlinearity is proposed for a Bayesian neural network; (\textit{ii}) an efficient posterior inference algorithm for weights and outputs of neural networks with the soft-thresholding nonlinearity is developed; (\textit{iii}) a novel Bayesian neural network for sparse coding is designed.
+  The main contributions of this paper are: (\textit{i}) for the first time a method for uncertainty propagation through the soft-thresholding nonlinearity is proposed for a Bayesian NN; (\textit{ii}) an efficient posterior inference algorithm for weights and outputs of NNs with the soft-thresholding nonlinearity is developed; (\textit{iii}) a novel Bayesian NN for sparse coding is designed.
 
@@
   \label{sec:bayesian_lista}
-  This section first reviews existing neural networks for sparse coding and then describes the novel Bayesian neural network.
+  This section first reviews existing NNs for sparse coding and then describes the novel Bayesian NN.
 
@@
 \label{subsec:nn_sc}
-  The neural network approach to sparse coding is based on earlier Iterative Shrinkage and Thresholding Algorithm (\textsc{ista}) \cite{daubechies2004iterative}.
+  The NN approach to sparse coding is based on earlier Iterative Shrinkage and Thresholding Algorithm (\textsc{ista}) \cite{daubechies2004iterative}.
 It addresses the sparse coding problem as the linear regression problem with the $l1$ penalty that promotes sparsity.
@@
   In contrast to \textsc{ista}, Learned \textsc{ista} (\textsc{lista}) \cite{gregor2010learning} learns the values of matrices $\mathbf{W}$ and $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
-To achieve this, the \textsc{ista} is limited with the fixed amount of iterations $L$ and interpreted as a recurrent neural network: every iteration $l$ of \textsc{ista} corresponds to the layer $l$ of \textsc{lista}.
+To achieve this, the \textsc{ista} is limited with the fixed amount of iterations $L$ and interpreted as a recurrent NN: every iteration $l$ of \textsc{ista} corresponds to the layer $l$ of \textsc{lista}.
 A vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$ is predicted by Algorithm~\ref{alg:lista}.
@@
 
-  \subsection{Bayesian \textsc{lista}}
+  \subsection{Bayes\textsc{lista}}
   \label{subsec:bayesian_lista}
@@
 
-  For every layer $l$ of Bayesian \textsc{lista}, $\widehat{\boldsymbol\beta}_{l}$ is assumed to have the spike and slab distribution with the spike probability $\boldsymbol\omega$, the slab mean $\mathbf{m}$, and the slab variance $\mathbf{v}$
+  For every layer $l$ of Bayes\textsc{lista}, $\widehat{\boldsymbol\beta}_{l}$ is assumed to have the spike and slab distribution with the spike probability $\boldsymbol\omega$, the slab mean $\mathbf{m}$, and the slab variance $\mathbf{v}$
   \begin{equation}
@@
   where $\delta_0$ is the delta-function that represents a spike, $[\cdot]_d$ denotes the $d$-th component of a vector.
-Section \ref{sec:fprop} shows that the output of the next layer $\widehat{\boldsymbol\beta}_{l+1}$ can be approximated with a spike and slab distribution and, therefore, the output of the Bayesian \textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
+Section \ref{sec:fprop} shows that the output of the next layer $\widehat{\boldsymbol\beta}_{l+1}$ can be approximated with a spike and slab distribution and, therefore, the output of the Bayes\textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
 
-  To introduce the uncertainty of predictions, we assume that the true $\boldsymbol\beta$ is an output $f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$ of the Bayesian \textsc{lista} network corrupted by the additive Gaussian zero-mean noise with the precision~$\gamma$.
+  To introduce the uncertainty of predictions, we assume that the true $\boldsymbol\beta$ is an output $f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$ of the Bayes\textsc{lista} network corrupted by the additive Gaussian zero-mean noise with the precision~$\gamma$.
 Then the likelihood of $\mathbf{B}$ is defined as
@@
   Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of \textsc{lista} (Algorithm~\ref{alg:lista}) is the result of soft-thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first} (section~\ref{subsec:forward_init}).
-  Thus, all the steps of Bayesian \textsc{lista} are covered and distributions for outputs of these steps are derived.
+  Thus, all the steps of Bayes\textsc{lista} are covered and distributions for outputs of these steps are derived.
 
@@
   \label{sec:experiments}
-  The proposed Bayesian \textsc{lista} model is evaluated on sparse coding problems and compared with \textsc{lista}~\cite{gregor2010learning}, \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
-The number of iterations in \textsc{ista} and \textsc{fista}  and the number of layers in Bayesian and classic \textsc{lista} networks is $L$.
+
+   \begin{figure*}[!t]
+  \centering
+  \subfloat[Synthetic for different $L$]{\includegraphics[width=0.24\textwidth]{graphics/synthetic_number_of_layers/nmse_validation}
+  \label{fig:nmse_n_layers_synthetic}}
+  \hfil
+  \subfloat[Synthetic for different $K$]{\includegraphics[width=0.24\textwidth]{graphics/synthetic_undersampling/nmse_validation}
+  \label{fig:nmse_undersampling_synthetic}}
+  \hfil
+  \subfloat[\textsc{mnist} for $K = 100$]{\includegraphics[width=0.24\textwidth]{graphics/mnist/100_nmse_valid}
+  \label{fig:nmse_k_100}}
+  \hfil
+  \subfloat[\textsc{mnist} for $K = 250$]{\includegraphics[width=0.24\textwidth]{graphics/mnist/250_nmse_valid}
+  \label{fig:nmse_k_250}}
+  \caption{\textsc{nmse} results.
+The synthetic data for different number of layers (for NNs) or iterations (for \textsc{ista} and \textsc{fista}~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}.
+\textsc{mnist} data with the observation size $K = 100$~\protect\subref{fig:nmse_k_100} and $K = 250$~\protect\subref{fig:nmse_k_250}}
+  \label{fig:number_of_layers_synthetic}
+  \end{figure*}
+
+    \begin{figure}[!t]
+  \centering
+  \includegraphics[width=0.24\textwidth]{graphics/active_mnist/nmse_validation}
+  %\subfloat[F measure]{\includegraphics[width=0.48\columnwidth]{graphics/active_mnist/f_measure_validation}}
+  \caption{\textsc{nmse} for active learning experiment on \textsc{mnist} data. }
+  \label{fig:active_learning_mnist}
+  \end{figure}
+
+  Proposed Bayes\textsc{lista} is evaluated on sparse coding problems and compared with \textsc{lista}~\cite{gregor2010learning}, \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
+The number of iterations in \textsc{ista} and \textsc{fista}  and the number of layers in NNs is $L$.
 For quantitative comparison the normalised mean square error (\textsc{nmse}) is used.
@@
 The observation size is set to $K=50$.
-Bayesian \textsc{lista} outperforms competitors.
-  \begin{figure}[t]
-  \centering
-  %\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
-  %~
-  \subfloat[\textsc{nmse} for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}
-  \label{fig:nmse_n_layers_synthetic}}
-  %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
-  %~
-  %\subfloat[F measure for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}
-  %\label{fig:f_meas_n_layers_synthetic}}\\[-13pt]
-  \subfloat[\textsc{nmse} for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/nmse_validation}
-  \label{fig:nmse_undersampling_synthetic}}
-  %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
-  %~
-  %\subfloat[F measure for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}
-  %\label{fig:f_meas_undesampling_synthetic}}
-  \caption{Predictive accuracy on the synthetic data: for different numbers of layers (for neural networks) or iterations (for baselines), and for different sizes of observations}
-  \label{fig:number_of_layers_synthetic}
-  \end{figure}
+Bayes\textsc{lista} outperforms competitors.
+%  \begin{figure}[t]
+%  \centering
+%  \subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
+%  ~
+%  \subfloat[\textsc{nmse} for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}
+%  \label{fig:nmse_n_layers_synthetic}}
+%  \subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
+%  ~
+%  \subfloat[F measure for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}
+%  \label{fig:f_meas_n_layers_synthetic}}\\[-13pt]
+%  \subfloat[\textsc{nmse} for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/nmse_validation}
+%  \label{fig:nmse_undersampling_synthetic}}
+%  \subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
+%  ~
+%  \subfloat[F measure for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}
+%  \label{fig:f_meas_undesampling_synthetic}}
+%  \caption{Predictive accuracy on the synthetic data: for different numbers of layers (for neural networks) or iterations (for baselines), and for different sizes of observations}
+%  \label{fig:number_of_layers_synthetic}
+%  \end{figure}
    \figurename~\ref{fig:nmse_undersampling_synthetic} gives \textsc{nmse} for different observation sizes $K$.
@@
 In the previous experiment, Bayesian and classic \textsc{lista} show similar results with this number of layers.
-The results of \figurename~\ref{fig:nmse_undersampling_synthetic} confirm this competitive behaviour between two \textsc{lista} networks.
-\textsc{ista} and \textsc{fista} underperform the neural networks.
+\figurename~\ref{fig:nmse_undersampling_synthetic} confirms this competitive behaviour between two \textsc{lista}s.
+\textsc{ista} and \textsc{fista} underperform the NNs.
 %Overall, the experiments on the synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
@@
   \subsection{Predictive performance on \textsc{mnist} data}
-  In this experiment, the methods are evaluated on the \textsc{mnist} dataset \cite{lecun1998gradient}.
+  In this experiment, the methods are evaluated on \textsc{mnist} dataset \cite{lecun1998gradient}.
 The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
@@
 
-  Figure \ref{fig:mnist} presents quality results on the test set with observation sizes $100$ and $250$.
-The experiment with $K=100$ presents severe conditions for the algorithms: the very limited size of the training dataset combined with the small dimensionality of observations.
-Bayesian \textsc{lista} is able to learn under these conditions, outperforming \textsc{lista} that demonstrates poor results.
-Under better conditions of the second experiment with $K=250$, both \textsc{lista} networks converge to the similar results.
-However, Bayesian \textsc{lista} demonstrates remarkably better convergence rate.
-Both baselines are unable to perform well in these experiments.
+  Figures \ref{fig:nmse_k_100} and~\ref{fig:nmse_k_250} present \textsc{nmse} with observation sizes $100$ and $250$.
+The experiment with $K=100$ presents severe conditions for the algorithms: the limited size of the training dataset combined with the small dimensionality of observations.
+Bayes\textsc{lista} is able to learn under these conditions, significantly outperforming \textsc{lista}.
+Under better conditions of the second experiment with $K=250$, both NNs converge to the similar results.
+However, Bayes\textsc{lista} demonstrates a remarkably better convergence rate.
+\textsc{ista} and \textsc{fista} are unable to perform well in these experiments.
 
-  \begin{figure}[t!]
-  \centering
-  %\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
-  %~
-  \subfloat[\textsc{nmse} for $K = 100$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/100_nmse_valid}}
-  %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
-  %~
-  %\subfloat[F measure for $K = 100$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/100_f_measure_valid}}\\[-13pt]
-  \subfloat[\textsc{nmse} for $K = 250$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/250_nmse_valid}}
-  %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
-  %~
-  %\subfloat[F measure for $K = 250$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/250_f_measure_valid}}
-  \caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the observation size $K = 100$ and $K = 250$}
-  \label{fig:mnist}
-  \end{figure}
+%  \begin{figure}[t!]
+%  \centering
+%  %\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
+%  %~
+%  \subfloat[\textsc{nmse} for $K = 100$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/100_nmse_valid}}
+%  %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
+%  %~
+%  %\subfloat[F measure for $K = 100$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/100_f_measure_valid}}\\[-13pt]
+%  \subfloat[\textsc{nmse} for $K = 250$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/250_nmse_valid}}
+%  %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
+%  %~
+%  %\subfloat[F measure for $K = 250$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/250_f_measure_valid}}
+%  \caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the observation size $K = 100$ and $K = 250$}
+%  \label{fig:mnist}
+%  \end{figure}
 
   \subsection{Active learning}
-  To demonstrate a potential scenario that can benefit from uncertainty estimates of Bayesian \textsc{lista}, we consider the active learning example~\cite{settles.tr09}.
+  To demonstrate a potential scenario that can benefit from uncertainty estimates of Bayes\textsc{lista}, we consider the active learning example~\cite{settles.tr09}.
 The active learning area researches ways to select new training subsets to reduce the total number of required supervision.
@@
 
-  The data in this example is the \textsc{mnist} dataset with the observation size $K=100$.
-We use the training data of size $50$, the pool data of size $500$,  and the test data of size $100$.
-The algorithm learns on the training data for $50$ iterations and it is evaluated on the test data.
+  \textsc{mnist} dataset with the observation size $K=100$ is employed.
+We use the training data is of size $50$, the pool data of size $500$,  and the test data of size $100$.
+The algorithm learns on the training data and it is evaluated on the test data.
 To actively collect a next data point from the pool, the algorithm is used to predict a point with the highest uncertainty.
-The selected point is moved from the pool to the training data and the algorithm performs additional $10$ iterations on the updated training data.
+The selected point is moved from the pool to the training data and the algorithms learns on the updated training data.
 Overall, $10$ pool additions are performed.
 After every addition the performance is measured on the test data.
-We compare the actively updated approach of adding new points from the pool with the random approach that picks a new data point from the pool at random.
-The procedure is repeated for $20$ times with new randomly selected initial datasets.
+We compare the active approach of adding new points from the pool with the random approach that picks a new data point from the pool at random.
+The procedure is repeated for $20$ times.
 
-  Figure \ref{fig:active_learning_mnist} demonstrates performance of the active and non-active methods of updates with Bayesian \textsc{lista}.
+  Figure \ref{fig:active_learning_mnist} demonstrates performance of the active and non-active methods of updates with Bayes\textsc{lista}.
 The active approach with uncertainty sampling steadily demonstrates better results.
-This means that the posterior distribution learnt by Bayesian \textsc{lista} is an adequate estimate of the true posterior.
-  \begin{figure}[t]
-  \centering
-  \subfloat[\textsc{nmse}]{\includegraphics[width=0.48\columnwidth]{graphics/active_mnist/nmse_validation}}%
-  %\subfloat[F measure]{\includegraphics[width=0.48\columnwidth]{graphics/active_mnist/f_measure_validation}}
-  \caption{Performance for the active learning experiment on the \textsc{mnist} data. }
-  \label{fig:active_learning_mnist}
-  \end{figure}
+This means the posterior distribution learnt by Bayes\textsc{lista} is an adequate estimate of the true posterior.
 
@@
   \label{sec:conclusions}
-  To the best of our knowledge, this is the first implementation of a Bayesian deep sparse coding algorithm.
+ % To the best of our knowledge, this is the first implementation of a Bayesian deep sparse coding algorithm.
 %Although there are works on Bayesian sparsity in context of neural networks \cite{he2017bayesian}, they are not the Bayesian neural networks in the same sense as Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
@@
   %We have approximated the outputs of the function with a spike and slab distribution, and we have shown that this distribution can stay within the same family after linear transformation with Gaussian weights and inputs of a neural network.
-  This allowed us to propose the Bayesian \textsc{lista} network and efficient inference algorithm that learns the distributions of the weights and makes the uncertainty estimates of the outputs.
+  This allowed us to propose Bayes\textsc{lista} and efficient inference algorithm that learns the distributions of the weights and makes the uncertainty estimates of the outputs.
 %The forward propagation in the algorithm is based on the proposed uncertainty propagation method, the backward propagation is based on the probabilistic backpropagation method, that was remarkably expanded to account for multidimensionality of inputs and outputs, likelihood of Bayesian \textsc{lista} and its recurrent nature.
 
-  Experiments on the synthetic and \textsc{mnist} datasets demonstrate that the proposed algorithm preserves the predictive accuracy of non-Bayesian methods while also providing posterior estimates.
+%  Experiments on the synthetic and \textsc{mnist} datasets demonstrate that the proposed algorithm preserves the predictive accuracy of non-Bayesian methods while also providing posterior estimates.
 We also show that when the training data is very small the proposed algorithm significantly outperforms \textsc{lista} in terms of predictive accuracy.
-Active learning experiments demonstrate that Bayesian \textsc{lista} gives accurate posterior estimates that can be used to select new training data points.
+Active learning experiments demonstrate that Bayes\textsc{lista} gives accurate posterior estimates that can be used to select new training data points.
 

### 2018-10-25 icassp_2019/paper.tex
update graphics in paper

@@
   \caption{\textsc{nmse} results.
-The synthetic data for different number of layers (for NNs) or iterations (for \textsc{ista} and \textsc{fista}~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}.
-\textsc{mnist} data with the observation size $K = 100$~\protect\subref{fig:nmse_k_100} and $K = 250$~\protect\subref{fig:nmse_k_250}}
+The synthetic data for different number of layers~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}.
+\textsc{mnist} results for increasing number of iterations with the observation size $K = 100$~\protect\subref{fig:nmse_k_100} and $K = 250$~\protect\subref{fig:nmse_k_250}}
   \label{fig:number_of_layers_synthetic}

### 2018-10-27 icassp_2019/paper.tex
minor changes after proof-read in icassp paper

@@
 \usepackage{float}
-\usepackage{algorithm, algorithmic}
+\usepackage{algorithm,algorithmic}
 
@@
 \newtheorem{lemma}{Lemma}
+
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
 
@@
   \label{sec:bayesian_lista}
-  This section first reviews existing NNs for sparse coding and then describes the novel Bayesian NN.
+  This section first reviews existing NNs for sparse coding and then introduces the novel Bayesian NN.
 
@@
   \end{equation}
-w.r.t.  $\boldsymbol\beta$,  where $\alpha$ is the penalty parameter.
+w.r.t.  $\boldsymbol\beta$,  where $\alpha$ is a penalty parameter.
 
@@
   In contrast to \textsc{ista}, Learned \textsc{ista} (\textsc{lista}) \cite{gregor2010learning} learns the values of matrices $\mathbf{W}$ and $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
-To achieve this, the \textsc{ista} is limited with the fixed amount of iterations $L$ and interpreted as a recurrent NN: every iteration $l$ of \textsc{ista} corresponds to the layer $l$ of \textsc{lista}.
+To achieve this, \textsc{ista} is limited with the fixed amount of iterations $L$ and interpreted as a recurrent NN: every iteration $l$ of \textsc{ista} corresponds to the layer $l$ of \textsc{lista}.
 A vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$ is predicted by Algorithm~\ref{alg:lista}.
@@
   \label{subsec:bayesian_lista}
-  This section introduces the proposed Bayesian version of \textsc{lista}. The prior distributions are imposed on the unknown weights
+  This section introduces the proposed Bayesian version of \textsc{lista} (Bayes\textsc{lista}). The prior distributions are imposed on the unknown weights
   \begin{equation}
@@
   where $\delta_0$ is the delta-function that represents a spike, $[\cdot]_d$ denotes the $d$-th component of a vector.
-Section \ref{sec:fprop} shows that the output of the next layer $\widehat{\boldsymbol\beta}_{l+1}$ can be approximated with a spike and slab distribution and, therefore, the output of the Bayes\textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
+Section \ref{sec:fprop} shows that the output of the next layer $\widehat{\boldsymbol\beta}_{l+1}$ can be approximated with the spike and slab distribution and, therefore, the output of the Bayes\textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
 
@@
   \label{sec:fprop}
-  This section describes modification of \textsc{lista} forward propagation (Algorithm~\ref{alg:lista}) to include probability distributions of the random variables introduced in section~\ref{sec:bayesian_lista}.
+  This section describes modification of \textsc{lista} forward propagation (Algorithm~\ref{alg:lista}) to include probability distributions of the random variables introduced in section~\ref{subsec:bayesian_lista}.
 
@@
   Prior factors (\ref{eq:ws}) and (\ref{eq:gamma_eta}) from $p$ are incorporated into $q$ with the EP algorithm~\cite{hernandez2015probabilistic}, i.e.
-they replace the corresponding approximating factors from $q$, and then $q$ is updated to minimise the Kullback–Leibler divergence.
+they replace the corresponding approximating factors from $q$, and then $q$ is updated to minimise the Kullback--Leibler divergence.
 
@@
   \caption{\textsc{nmse} results.
-The synthetic data for different number of layers~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}.
-\textsc{mnist} results for increasing number of iterations with the observation size $K = 100$~\protect\subref{fig:nmse_k_100} and $K = 250$~\protect\subref{fig:nmse_k_250}}
+The synthetic data results for different number of layers~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}.
+The \textsc{mnist} results for increasing number of iterations with the observation size $K = 100$~\protect\subref{fig:nmse_k_100} and $K = 250$~\protect\subref{fig:nmse_k_250}}
   \label{fig:number_of_layers_synthetic}
@@
   %\subfloat[F measure]{\includegraphics[width=0.48\columnwidth]{graphics/active_mnist/f_measure_validation}}
-  \caption{\textsc{nmse} for active learning experiment on \textsc{mnist} data. }
+  \caption{\textsc{nmse} for the active learning experiment on \textsc{mnist} data. }
   \label{fig:active_learning_mnist}
@@
   \subsection{Predictive performance on \textsc{mnist} data}
-  In this experiment, the methods are evaluated on \textsc{mnist} dataset \cite{lecun1998gradient}.
+  In this experiment, the methods are evaluated on the \textsc{mnist} dataset \cite{lecun1998gradient}.
 The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
@@
 
-  \textsc{mnist} dataset with the observation size $K=100$ is employed.
-We use the training data is of size $50$, the pool data of size $500$,  and the test data of size $100$.
+ The \textsc{mnist} dataset with the observation size $K=100$ is utilised.
+We use the training data of size $50$, the pool data of size $500$,  and the test data of size $100$.
 The algorithm learns on the training data and it is evaluated on the test data.

### 2018-10-28 nips_workshop_2018/BayesianLISTA.tex
nips 2018 bayesian deep learning workshop paper added

--- 2018-10-27 icassp_2019/paper.tex
@@
 \documentclass{article}
-\usepackage{spconf,amsmath,graphicx}
 \usepackage{mathtools}
@@
 \usepackage{xcolor}
+
 \usepackage{times}
 \usepackage{float}
-\usepackage{algorithm,algorithmic}
+
+\usepackage[square,numbers]{natbib}
+\usepackage[final]{nips_2018}
+
+\usepackage{bbm}
+\usepackage{algorithm, algorithmic}
+\usepackage{wrapfig}
+\usepackage{lipsum}
 
@@
 
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
-
 \allowdisplaybreaks
 
-\title{Bayesian neural networks for sparse coding}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicreturn}{\textbf{Output:}}
 
-\name{Danil Kuzin$^{\dagger}$ \qquad Olga Isupova$^{\star}$ \qquad Lyudmila Mihaylova$^{\dagger}$}
+% \setlength{\belowcaptionskip}{-15pt}
+%  \usepackage[small,compact]{titlesec}
+%  \titlespacing{\section}{0pt}{1ex}{0.8ex}
+%  \titlespacing{\subsection}{0pt}{0.5ex}{0ex}
+%  \titlespacing{\subsubsection}{0pt}{0.2ex}{0ex}
+%  \expandafter\def\expandafter\normalsize\expandafter{%
+%      \normalsize
+%      \setlength\abovedisplayskip{2pt}
+%      \setlength\belowdisplayskip{2pt}
+%      \setlength\abovedisplayshortskip{0pt}
+%      \setlength\belowdisplayshortskip{0pt}
+%  }
+%  \renewcommand{\baselinestretch}{0.99}
 
-\address{$^{\dagger}$ Department of Automatic Control and Systems Engineering,\\
-University of Sheffield, Sheffield S1 3JD, UK\\
-e-mail: dkuzin1@sheffield.ac.uk; l.s.mihaylova@sheffield.ac.uk.\\
-$^{\star}$ Department of Engineering Science,\\
-University of Oxford, Oxford OX1 2JD, UK\\
-e-mail: olga.isupova@eng.ox.ac.uk}
+\title{Uncertainty propagation in neural networks for sparse coding}
+
+%\author{
+%  Danil Kuzin$^{\dagger}$, Olga Isupova$^{\star}$, Lyudmila Mihaylova$^{\dagger}$\\
+%  $^{\dagger}$Department of Automatic Control \qquad\qquad\qquad $^{\star}$ Department of Engineering Science\\
+%  and System Engineering \qquad\qquad\qquad\qquad\quad University of Oxford, UK\qquad\qquad\\
+%  \quad\qquad University of Sheffield, UK \qquad\qquad\qquad\qquad\quad \texttt{olga.isupova@eng.ox.ac.uk}\\
+%  \texttt{dkuzin1@sheffield.ac.uk} \qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\\
+%  \texttt{l.s.mihaylova@sheffield.ac.uk} \qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\\
+%}
+\author{
+Danil Kuzin$^{\dagger}$, Olga Isupova$^{\star}$, Lyudmila Mihaylova$^{\dagger}$\\
+$^{\dagger}$Department of Automatic Control
+and System Engineering,
+University of Sheffield, UK \\
+$^{\star}$Department of Engineering Science,
+University of Oxford, UK
+}
 
@@
 \maketitle
-
-\begin{abstract}
-  Deep learning is actively used in the area of sparse coding.
-In current methods uncertainty of predictions is rarely estimated, thus providing the results that lack the quantitative justification.
-Bayesian learning provides the way to estimate the uncertainty of predictions in neural networks (NNs) by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
-We propose a novel method of propagating the uncertainty through the sparsity-promoiting layers of NNs for the first time.
-We design a Bayesian Learned Iterative Shrinkage-Thresholding network (Bayes\textsc{lista}).
-An efficient posterior inference algorithm based on probabilistic backpropagation is developed.
-Experiments on sparse coding show that the proposed framework provides both accurate predictions and sensible estimates of uncertainty in these predictions.
-\end{abstract}
-
-\begin{keywords}
-Sparse regression, Bayesian neural networks, uncertainty estimation, compressive sensing
-\end{keywords}
+%\begin{abstract}
+%Bayesian learning allows to estimate uncertainty of predictions in neural networks by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
+We propose a novel method of propagating the uncertainty through the soft thresholding nonlinearity.
+The method expands the area of Bayesian neural networks and enables the soft thresholding nonlinearity to be included in Bayesian deep neural networks for the first time.
+We design a Bayesian Learned Iterative Shrinkage-Thresholding network (Bayesian \textsc{lista}).
+We develop an efficient posterior inference algorithm based on probabilistic backpropagation.
+A series of experiments on sparse coding shows that the proposed framework provides both accurate predictions and sensible estimates of uncertainty in these predictions.
+%\end{abstract}
 
 \section{Introduction}
-\label{sec:intro}
-
   The idea of Bayesian learning in neural networks (NNs)~\cite{neal2012bayesian} has recently gained an attention with the development of distributed approximate inference techniques~\cite{li2015stochastic, hoffman2013stochastic} and general boost in popularity of deep learning.
-In addition to predictions, Bayesian learning naturally provides the uncertainty estimates of these predictions.
-These uncertainty estimates are vital, e.g., in spheres that affect people's health, such as self-driving cars or medicine.
-
 Recently several techniques~\cite{ranganath2015deep, gal2016dropout} have been proposed to handle specific types of NNs with efficient Bayesian inference.
@@
   \label{sec:bayesian_lista}
-  This section first reviews existing NNs for sparse coding and then introduces the novel Bayesian NN.
+  The section first reviews existing NNs for sparse coding and then introduces the novel Bayesian NN.
 
@@
 
+ \begin{wrapfigure}[13]{l}{0.5\textwidth}  
+ \vspace{-10pt}
+\begin{minipage}{0.5\textwidth}
+  \begin{algorithm}[H]
+    \caption{\textsc{lista} forward propagation}
+\label{alg:lista}   
+    \begin{algorithmic}[1]
+      \REQUIRE observations $\mathbf{y}$, weights $\mathbf{W}, \mathbf{S}$, number of layers $L$
+      \STATE Dense layer $\mathbf{b} \gets \mathbf{W}\mathbf{y}$ \label{eq:first_layer}
+      \STATE Soft-thresholding function~$\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$ \label{eq:thr_first}
+      \FOR{$l=1$ \TO $L$}
+        \STATE Dense layer $\mathbf{c}_l \gets \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ \label{eq:l_dense_layer}
+        \STATE Soft-thresholding function $\widehat{\boldsymbol\beta}_{l} \gets h_\lambda(\mathbf{c}_l)$ \label{eq:l_thr}
+      \ENDFOR
+      \RETURN $\widehat{\boldsymbol\beta} \gets \widehat{\boldsymbol\beta}_{L}$
+    \end{algorithmic}
+  \end{algorithm}
+\end{minipage}
+\end{wrapfigure}  
 At every iteration $l$, \textsc{ista} obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ propagated through the soft-thresholding function %$h_\lambda(\cdot)$
@@
 
-  \begin{algorithm}[t]
-    \caption{\textsc{lista} forward propagation}
-    \label{alg:lista}
-    \begin{algorithmic}[1]
-      \REQUIRE observations $\mathbf{y}$, weights $\mathbf{W}, \mathbf{S}$, number of layers $L$
-      \STATE Dense layer $\mathbf{b} \gets \mathbf{W}\mathbf{y}$ \label{eq:first_layer}
-      \STATE soft-thresholding nonlinearity~$\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$ \label{eq:thr_first}
-      \FOR{$l=1$ \TO $L$}
-        \STATE Dense layer $\mathbf{c}_l \gets \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ \label{eq:l_dense_layer}
-        \STATE Soft-thresholding nonlinearity $\widehat{\boldsymbol\beta}_{l} \gets h_\lambda(\mathbf{c}_l)$ \label{eq:l_thr}
-      \ENDFOR
-      \RETURN $\widehat{\boldsymbol\beta} \gets \widehat{\boldsymbol\beta}_{L}$
-    \end{algorithmic}
-  \end{algorithm}
-
  % In \textsc{lista}, matrices $\mathbf{W}$ and $\mathbf{S}$ are the parameters that are initialised as in the \textsc{ista} and then updated with the backpropagation algorithm.
@@
   \label{eq:ws}
-  \begin{split}
-  p(\mathbf{W}) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij} ; 0, \eta^{-1}), \\
-  p(\mathbf{S}) &= \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; 0, \eta^{-1}),
-  \end{split}
+  p(\mathbf{W}) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij} ; 0, \eta^{-1}), \quad
+  p(\mathbf{S}) = \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; 0, \eta^{-1}),
   \end{equation}
@@
   where $\delta_0$ is the delta-function that represents a spike, $[\cdot]_d$ denotes the $d$-th component of a vector.
-Section \ref{sec:fprop} shows that the output of the next layer $\widehat{\boldsymbol\beta}_{l+1}$ can be approximated with the spike and slab distribution and, therefore, the output of the Bayes\textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
+In appendix we show that the output of the next layer $\widehat{\boldsymbol\beta}_{l+1}$ can be approximated with the spike and slab distribution and, therefore, the output of the Bayes\textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
 
@@
   \label{eq:likelihood}
-  \begin{split}
-  p(\mathbf{B}| \mathbf{Y}, &\mathbf{W}, \mathbf{S}, \gamma, \lambda) \\
-  = &\prod_{n=1}^N\prod_{d=1}^D\mathcal{N}\left(\beta_d^{(n)}; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}\right)
- \end{split}
+  p(\mathbf{B}| \mathbf{Y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda)
+  = \prod_{n=1}^N\prod_{d=1}^D\mathcal{N}\left(\beta_d^{(n)}; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}\right)
   \end{equation}
@@
   \label{eq:posterior}
-  \begin{split}
-  p(\mathbf{W}, \mathbf{S}, &\gamma, \eta | \mathbf{B}, \mathbf{Y}, \lambda) \\
-  = &\frac{p(\mathbf{B} | \mathbf{Y}, \mathbf{W},  \mathbf{S}, \gamma, \lambda) p(\mathbf{W} | \eta )p(\mathbf{S} | \eta) p(\eta) p(\gamma)}{p(\mathbf{B} | \mathbf{Y}, \lambda)}
-  \end{split}
+  p(\mathbf{W}, \mathbf{S}, \gamma, \eta | \mathbf{B}, \mathbf{Y}, \lambda)
+  = \frac{p(\mathbf{B} | \mathbf{Y}, \mathbf{W},  \mathbf{S}, \gamma, \lambda) p(\mathbf{W} | \eta )p(\mathbf{S} | \eta) p(\eta) p(\gamma)}{p(\mathbf{B} | \mathbf{Y}, \lambda)}
   \end{equation}
@@
 
-  \section{Uncertainty propagation through soft-thresholding}
+In the appendix we describe modification of \textsc{lista} forward propagation (Algorithm~\ref{alg:lista}) to include probability distributions of the random variables introduced in this section and also an efficient Bayesian inference algorithm.
+
+  \section{Experiments}
+  \label{sec:experiments}
+
+   \begin{figure}[!t]
+  \centering
+  \subfloat[Synthetic for different $L$]{\includegraphics[width=0.25\textwidth]{graphics/synthetic_number_of_layers/nmse_validation}
+  \label{fig:nmse_n_layers_synthetic}}
+  \hfil
+  \subfloat[Synthetic for different $K$]{\includegraphics[width=0.25\textwidth]{graphics/synthetic_undersampling/nmse_validation}
+  \label{fig:nmse_undersampling_synthetic}}
+  \hfil
+  \subfloat[Active learning example]{\includegraphics[width=0.25\textwidth]{graphics/active_mnist/nmse_validation}
+  \label{fig:active_learning_mnist}}
+  \caption{\textsc{nmse} results.
+The synthetic data results for different number of layers~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}.
+The active learning example results on the \textsc{mnist} data~\protect\subref{fig:active_learning_mnist}.}
+  \label{fig:number_of_layers_synthetic}
+  \end{figure}
+
+  Proposed Bayes\textsc{lista} is evaluated on sparse coding problems and compared with \textsc{lista}~\cite{gregor2010learning}, \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
+The number of iterations in \textsc{ista} and \textsc{fista}  and the number of layers in NNs is $L$.
+For quantitative comparison the normalised mean square error (\textsc{nmse}) is used.
+%We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn.
+
+  \subsection{Predictive performance on synthetic data}
+  First, performance is analysed on synthetic data.
+We generate $N_\text{train}=1000$ and $N_{\text{test}} = 100$ sparse vectors $\boldsymbol\beta^{(n)}$ of size $D = 100$  from the spike and slab distribution with the truncated slab: each component $\beta^{(n)}_{d}$ is zero with the probability~$0.8$ or is sampled from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability~$0.2$.
+The design matrix $\mathbf{X}$ is random Gaussian.
+The observations $\mathbf{y}^{(n)}$ are generated as in~(\ref{eq:regression_problem}) with the zero-mean Gaussian noise with the standard deviation $0.5$.
+The shrinkage parameter is set to~$\lambda = 0.1$.
+The algorithms are trained on the training data of size $N_\text{train}$ and evaluated on the test data of size $N_{\text{test}}$.
+
+  In \figurename~\ref{fig:nmse_n_layers_synthetic} \textsc{nmse} for different number of layers (or iterations) $L$ is presented.
+The observation size is set to $K=50$.
+Bayes\textsc{lista} outperforms competitors.
+%  \begin{figure}[t]
+%  \centering
+%  \subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
+%  ~
+%  \subfloat[\textsc{nmse} for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}
+%  \label{fig:nmse_n_layers_synthetic}}
+%  \subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
+%  ~
+%  \subfloat[F measure for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}
+%  \label{fig:f_meas_n_layers_synthetic}}\\[-13pt]
+%  \subfloat[\textsc{nmse} for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/nmse_validation}
+%  \label{fig:nmse_undersampling_synthetic}}
+%  \subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
+%  ~
+%  \subfloat[F measure for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}
+%  \label{fig:f_meas_undesampling_synthetic}}
+%  \caption{Predictive accuracy on the synthetic data: for different numbers of layers (for neural networks) or iterations (for baselines), and for different sizes of observations}
+%  \label{fig:number_of_layers_synthetic}
+%  \end{figure}
+   \figurename~\ref{fig:nmse_undersampling_synthetic} gives \textsc{nmse} for different observation sizes $K$.
+The number of layers (iterations) is set as $L=4$.
+In the previous experiment, Bayesian and classic \textsc{lista} show similar results with this number of layers.
+\figurename~\ref{fig:nmse_undersampling_synthetic} confirms this competitive behaviour between two \textsc{lista}s.
+\textsc{ista} and \textsc{fista} underperform the NNs.
+%Overall, the experiments on the synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
+
+  \subsection{Active learning}
+ To demonstrate a potential scenario that can benefit from uncertainty estimates of Bayes\textsc{lista}, we consider the active learning example~\cite{settles.tr09}.
+The active learning area researches ways to select new training subsets to reduce the total number of required supervision.
+One of the popular approaches in active learning is uncertainty sampling, when the data with the least certain predictions is chosen for labelling.
+We use a variance of the spike and slab distributed prediction as a measure of uncertainty.
+
+ The \textsc{mnist} dataset~\cite{lecun1998gradient} is utilised.
+The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
+The design matrix $\mathbf{X}$ is standard random Gaussian.
+Observations are generated as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta \in \mathbb{R}^{784}$ are flattened images.
+The shrinkage parameter $\lambda$ is~$0.1$, the observation size $K$ is $100$.
+
+ We use the training data of size $50$, the pool data of size $500$,  and the test data of size $100$.
+The algorithm learns on the training data and it is evaluated on the test data.
+To actively collect a next data point from the pool, the algorithm is used to predict a point with the highest uncertainty.
+The selected point is moved from the pool to the training data and the algorithms learns on the updated training data.
+Overall, $10$ pool additions are performed.
+After every addition the performance is measured on the test data.
+We compare the active approach of adding new points from the pool with the random approach that picks a new data point from the pool at random.
+The procedure is repeated for $20$ times.
+
+  Figure \ref{fig:active_learning_mnist} demonstrates performance of the active and non-active methods of updates with Bayes\textsc{lista}.
+The active approach with uncertainty sampling steadily demonstrates better results.
+This means the posterior distribution learnt by Bayes\textsc{lista} is an adequate estimate of the true posterior.
+
+ Appendix provides additional results on predictive performance on the \textsc{mnist} data.
+
+{\small
+\bibliography{bibliography}
+\bibliographystyle{unsrtnat}
+}
+
+\appendix
+  \section*{Appendix A: Uncertainty propagation through soft-thresholding}
   \label{sec:fprop}
@@
 
-  \subsection{Initialisation}
+  \subsection*{Initialisation}
   \label{subsec:forward_init}
@@
 
-  \subsection{Main layers}
+  \subsection*{Main layers}
   At step \ref{eq:l_dense_layer} of \textsc{lista} (Algorithm~\ref{alg:lista}) the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components: $b_d \sim \mathcal{N}(m^b_d, v^b_d)$, $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables: $[\widehat{\beta}_{l-1}]_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
@@
   m^e_{d} \stackrel{\text{def}}{=} &\mathbb{E}[ \mathbf{e}_l ]_d = \sum_{d'=1}^D m^s_{dd'}(1-\omega_{d'})m_{d'}, \\
-   \begin{split}
-  v^e_{d} \stackrel{\text{def}}{=} &\operatorname{Var}[ \mathbf{e}_l ]_d = \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'} \\
-   + &(1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}].
-   \end{split}
+  v^e_{d} \stackrel{\text{def}}{=} &\operatorname{Var}[ \mathbf{e}_l ]_d = \sum_{d'=1}^D [(m^s_{dd'})^2(1-\omega_{d'})^2v_{d'}
+   + (1-\omega_{d'})^2(m_{d'})^2v^s_{dd'} + v^s_{dd'}(1-\omega_{d'})^2v_{d'}].
    \end{align}
@@
 
-  \section{Backpropagation}
+  \section*{Appendix B: Backpropagation}
   \label{sec:backpropagation}
@@
 \begin{align}
-  q(&\mathbf{W}, \mathbf{S}, \gamma, \eta) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} ; m^w_{dk}, v^w_{dk}) \text{Gam}(\gamma; a^\gamma, b^\gamma)\nonumber\\
 \label{eq:approximating_dsitribution}
-  &\times\prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; m^s_{d'd''}, v^s_{d'd''}) \text{Gam}(\eta; a^\eta, b^\eta).
+\begin{split}
+q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} ; m^w_{dk}, v^w_{dk}) \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; m^s_{d'd''}, v^s_{d'd''}) \\
+&\times \text{Gam}(\gamma; a^\gamma, b^\gamma) \text{Gam}(\eta; a^\eta, b^\eta)
+\end{split}
 \end{align}
@@
   With the likelihood factors~(\ref{eq:likelihood}) of $p$ the ADF approach is employed and they are iteratively incorporated into $q$.
-The normalisation constant of $q$ with the likelihood term for the data point $n$ incorporated is (let $z_d$ denote  $[f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d$) %(to simplify notation the superscript $(n)$ is omitted)
+The normalisation constant of $q$ with the likelihood term for the data point $n$ incorporated is (let $z_d$ denote (to simplify notation the superscript $(n)$ is omitted)
   \begin{equation}
-  Z  = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; z_d, \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
+  Z  = \int \prod_{d=1}^{D} \mathcal{N}(\beta_d ; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}) q(\mathbf{W}, \mathbf{S}, \gamma, \eta) \mathrm{d}\mathbf{W} \mathrm{d}\mathbf{S} \mathrm{d}\gamma \mathrm{d}\eta
   \end{equation}
@@
 \label{eq:Z}
-  \begin{split}
-  Z \approx & \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) \right.\\
-  &\left. + (1 - \omega^{\widehat{\boldsymbol\beta}}_d)\mathcal{N}(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d)\right],
-  \end{split}
+Z \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right],
 \end{equation}
@@
 
-  \section{Experiments}
-  \label{sec:experiments}
-
-   \begin{figure*}[!t]
+   \begin{figure}[!t]
   \centering
-  \subfloat[Synthetic for different $L$]{\includegraphics[width=0.24\textwidth]{graphics/synthetic_number_of_layers/nmse_validation}
-  \label{fig:nmse_n_layers_synthetic}}
-  \hfil
-  \subfloat[Synthetic for different $K$]{\includegraphics[width=0.24\textwidth]{graphics/synthetic_undersampling/nmse_validation}
-  \label{fig:nmse_undersampling_synthetic}}
-  \hfil
-  \subfloat[\textsc{mnist} for $K = 100$]{\includegraphics[width=0.24\textwidth]{graphics/mnist/100_nmse_valid}
+  \subfloat[\textsc{mnist} for $K = 100$]{\includegraphics[width=0.25\textwidth]{graphics/mnist/100_nmse_valid}
   \label{fig:nmse_k_100}}
   \hfil
-  \subfloat[\textsc{mnist} for $K = 250$]{\includegraphics[width=0.24\textwidth]{graphics/mnist/250_nmse_valid}
+  \subfloat[\textsc{mnist} for $K = 250$]{\includegraphics[width=0.25\textwidth]{graphics/mnist/250_nmse_valid}
   \label{fig:nmse_k_250}}
-  \caption{\textsc{nmse} results.
-The synthetic data results for different number of layers~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}.
-The \textsc{mnist} results for increasing number of iterations with the observation size $K = 100$~\protect\subref{fig:nmse_k_100} and $K = 250$~\protect\subref{fig:nmse_k_250}}
+  \caption{\textsc{nmse} results on the \textsc{mnist} data for increasing number of iterations with the observation size $K = 100$~\protect\subref{fig:nmse_k_100} and $K = 250$~\protect\subref{fig:nmse_k_250}}
   \label{fig:number_of_layers_synthetic}
-  \end{figure*}
-
-    \begin{figure}[!t]
-  \centering
-  \includegraphics[width=0.24\textwidth]{graphics/active_mnist/nmse_validation}
-  %\subfloat[F measure]{\includegraphics[width=0.48\columnwidth]{graphics/active_mnist/f_measure_validation}}
-  \caption{\textsc{nmse} for the active learning experiment on \textsc{mnist} data. }
-  \label{fig:active_learning_mnist}
   \end{figure}
 
-  Proposed Bayes\textsc{lista} is evaluated on sparse coding problems and compared with \textsc{lista}~\cite{gregor2010learning}, \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
-The number of iterations in \textsc{ista} and \textsc{fista}  and the number of layers in NNs is $L$.
-For quantitative comparison the normalised mean square error (\textsc{nmse}) is used.
-%We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn.
-
-  \subsection{Predictive performance on synthetic data}
-  First, performance is analysed on synthetic data.
-We generate $N_\text{train}=1000$ and $N_{\text{test}} = 100$ sparse vectors $\boldsymbol\beta^{(n)}$ of size $D = 100$  from the spike and slab distribution with the truncated slab: each component $\beta^{(n)}_{d}$ is zero with the probability~$0.8$ or is sampled from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability~$0.2$.
-The design matrix $\mathbf{X}$ is random Gaussian.
-The observations $\mathbf{y}^{(n)}$ are generated as in~(\ref{eq:regression_problem}) with the zero-mean Gaussian noise with the standard deviation $0.5$.
-The shrinkage parameter is set to~$\lambda = 0.1$.
-The algorithms are trained on the training data of size $N_\text{train}$ and evaluated on the test data of size $N_{\text{test}}$.
-
-  In \figurename~\ref{fig:nmse_n_layers_synthetic} \textsc{nmse} for different number of layers (or iterations) $L$ is presented.
-The observation size is set to $K=50$.
-Bayes\textsc{lista} outperforms competitors.
-%  \begin{figure}[t]
-%  \centering
-%  \subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
-%  ~
-%  \subfloat[\textsc{nmse} for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}
-%  \label{fig:nmse_n_layers_synthetic}}
-%  \subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
-%  ~
-%  \subfloat[F measure for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}
-%  \label{fig:f_meas_n_layers_synthetic}}\\[-13pt]
-%  \subfloat[\textsc{nmse} for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/nmse_validation}
-%  \label{fig:nmse_undersampling_synthetic}}
-%  \subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
-%  ~
-%  \subfloat[F measure for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}
-%  \label{fig:f_meas_undesampling_synthetic}}
-%  \caption{Predictive accuracy on the synthetic data: for different numbers of layers (for neural networks) or iterations (for baselines), and for different sizes of observations}
-%  \label{fig:number_of_layers_synthetic}
-%  \end{figure}
-   \figurename~\ref{fig:nmse_undersampling_synthetic} gives \textsc{nmse} for different observation sizes $K$.
-The number of layers (iterations) is set as $L=4$.
-In the previous experiment, Bayesian and classic \textsc{lista} show similar results with this number of layers.
-\figurename~\ref{fig:nmse_undersampling_synthetic} confirms this competitive behaviour between two \textsc{lista}s.
-\textsc{ista} and \textsc{fista} underperform the NNs.
-%Overall, the experiments on the synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
-
-  \subsection{Predictive performance on \textsc{mnist} data}
-  In this experiment, the methods are evaluated on the \textsc{mnist} dataset \cite{lecun1998gradient}.
-The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
-The design matrix $\mathbf{X}$ is standard random Gaussian.
-Observations are generated as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta \in \mathbb{R}^{784}$ are flattened images.
-We use $100$ images for training and $100$ for test.
-The shrinkage parameter $\lambda$ is~$0.1$.
+\section*{Appendix C: Predictive performance on \textsc{mnist} data}
+In this experiment, the methods are evaluated on the \textsc{mnist} dataset in terms of predictive performance. We use $100$ images for training and $100$ for test.
 
@@
 
-%  \begin{figure}[t!]
-%  \centering
-%  %\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
-%  %~
-%  \subfloat[\textsc{nmse} for $K = 100$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/100_nmse_valid}}
-%  %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
-%  %~
-%  %\subfloat[F measure for $K = 100$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/100_f_measure_valid}}\\[-13pt]
-%  \subfloat[\textsc{nmse} for $K = 250$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/250_nmse_valid}}
-%  %\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
-%  %~
-%  %\subfloat[F measure for $K = 250$]{\includegraphics[width=0.48\columnwidth]{graphics/mnist/250_f_measure_valid}}
-%  \caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with the observation size $K = 100$ and $K = 250$}
-%  \label{fig:mnist}
-%  \end{figure}
-
-  \subsection{Active learning}
-  To demonstrate a potential scenario that can benefit from uncertainty estimates of Bayes\textsc{lista}, we consider the active learning example~\cite{settles.tr09}.
-The active learning area researches ways to select new training subsets to reduce the total number of required supervision.
-One of the popular approaches in active learning is uncertainty sampling, when the data with the least certain predictions is chosen for labelling.
-We use a variance (\ref{eq:spsl_moments}) as a measure of uncertainty.
-
- The \textsc{mnist} dataset with the observation size $K=100$ is utilised.
-We use the training data of size $50$, the pool data of size $500$,  and the test data of size $100$.
-The algorithm learns on the training data and it is evaluated on the test data.
-To actively collect a next data point from the pool, the algorithm is used to predict a point with the highest uncertainty.
-The selected point is moved from the pool to the training data and the algorithms learns on the updated training data.
-Overall, $10$ pool additions are performed.
-After every addition the performance is measured on the test data.
-We compare the active approach of adding new points from the pool with the random approach that picks a new data point from the pool at random.
-The procedure is repeated for $20$ times.
-
-  Figure \ref{fig:active_learning_mnist} demonstrates performance of the active and non-active methods of updates with Bayes\textsc{lista}.
-The active approach with uncertainty sampling steadily demonstrates better results.
-This means the posterior distribution learnt by Bayes\textsc{lista} is an adequate estimate of the true posterior.
-
-  \section{Conclusions}
-  \label{sec:conclusions}
- % To the best of our knowledge, this is the first implementation of a Bayesian deep sparse coding algorithm.
-%Although there are works on Bayesian sparsity in context of neural networks \cite{he2017bayesian}, they are not the Bayesian neural networks in the same sense as Bayesian \textsc{lista} but rather the interpretation of the sparse Bayesian  learning algorithm as the long short-term memory network.
-We find not only correct predictions but also useful posterior estimates for the predictions.
-  We have presented the new method for propagating uncertainty through the soft-thresholding function.
-  %We have approximated the outputs of the function with a spike and slab distribution, and we have shown that this distribution can stay within the same family after linear transformation with Gaussian weights and inputs of a neural network.
-  This allowed us to propose Bayes\textsc{lista} and efficient inference algorithm that learns the distributions of the weights and makes the uncertainty estimates of the outputs.
-%The forward propagation in the algorithm is based on the proposed uncertainty propagation method, the backward propagation is based on the probabilistic backpropagation method, that was remarkably expanded to account for multidimensionality of inputs and outputs, likelihood of Bayesian \textsc{lista} and its recurrent nature.
-
-%  Experiments on the synthetic and \textsc{mnist} datasets demonstrate that the proposed algorithm preserves the predictive accuracy of non-Bayesian methods while also providing posterior estimates.
-We also show that when the training data is very small the proposed algorithm significantly outperforms \textsc{lista} in terms of predictive accuracy.
-Active learning experiments demonstrate that Bayes\textsc{lista} gives accurate posterior estimates that can be used to select new training data points.
-
-% Below is an example of how to insert images. Delete the ``\vspace'' line,
-% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
-% with a suitable PostScript file name.
-% -------------------------------------------------------------------------
-% \begin{figure}[htb]
-
-% \begin{minipage}[b]{1.0\linewidth}
-%   \centering
-%   \centerline{\includegraphics[width=8.5cm]{image1}}
-% %  \vspace{2.0cm}
-%   \centerline{(a) Result 1}\medskip
-% \end{minipage}
-% %
-% \begin{minipage}[b]{.48\linewidth}
-%   \centering
-%   \centerline{\includegraphics[width=4.0cm]{image3}}
-% %  \vspace{1.5cm}
-%   \centerline{(b) Results 3}\medskip
-% \end{minipage}
-% \hfill
-% \begin{minipage}[b]{0.48\linewidth}
-%   \centering
-%   \centerline{\includegraphics[width=4.0cm]{image4}}
-% %  \vspace{1.5cm}
-%   \centerline{(c) Result 4}\medskip
-% \end{minipage}
-% %
-% \caption{Example of placing a figure with experimental results.}
-% \label{fig:res}
-% %
-% \end{figure}
-
-% % To start a new column (but not a new page) and help balance the last-page
-% % column length use \vfill\pagebreak.
-% % -------------------------------------------------------------------------
-% %\vfill
-% %\pagebreak
-
-% \section{COPYRIGHT FORMS}
-% \label{sec:copyright}
-
-% You must submit your fully completed, signed IEEE electronic copyright release
-% form when you submit your paper. We {\bf must} have this form before your paper
-% can be published in the proceedings.
-
-% \section{RELATION TO PRIOR WORK}
-% \label{sec:prior}
-
-% The text of the paper should contain discussions on how the paper's
-% contributions are related to prior work in the field. It is important
-% to put new work in  context, to give credit to foundational work, and
-% to provide details associated with the previous work that have appeared
-% in the literature. This discussion may be a separate, numbered section
-% or it may appear elsewhere in the body of the manuscript, but it must
-% be present.
-
-% You should differentiate what is new and how your work expands on
-% or takes a different path from the prior studies. An example might
-% read something to the effect: "The work presented here has focused
-% on the formulation of the ABC algorithm, which takes advantage of
-% non-uniform time-frequency domain analysis of data. The work by
-% Smith and Cohen \cite{Lamp86} considers only fixed time-domain analysis and
-% the work by Jones et al \cite{C2} takes a different approach based on
-% fixed frequency partitioning. While the present study is related
-% to recent approaches in time-frequency analysis [3-5], it capitalizes
-% on a new feature space, which was not considered in these earlier
-% studies."
-
-% \vfill\pagebreak
-
-% \section{REFERENCES}
-% \label{sec:refs}
-
-% List and number all bibliographical references at the end of the
-% paper. The references can be numbered in alphabetic order or in
-% order of appearance in the document. When referring to them in
-% the text, type the corresponding reference number in square
-% brackets as shown at the end of this sentence \cite{C2}. An
-% additional final page (the fifth page, in most cases) is
-% allowed, but must contain only references to the prior
-% literature.
-
-% % References should be produced using the bibtex program from suitable
-% % BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
-% % style file from IEEE produces unsorted bibliography list.
-% % -------------------------------------------------------------------------
-\bibliographystyle{IEEEbib}
-\bibliography{bibliography}
-
 \end{document}

### 2018-10-29 icassp_2019/paper.tex
minor updates

@@
   Deep learning is actively used in the area of sparse coding.
-In current methods uncertainty of predictions is rarely estimated, thus providing the results that lack the quantitative justification.
+In current deep sparse coding methods uncertainty of predictions is rarely estimated, thus providing the results that lack the quantitative justification.
 Bayesian learning provides the way to estimate the uncertainty of predictions in neural networks (NNs) by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
@@
       \STATE Dense layer $\mathbf{b} \gets \mathbf{W}\mathbf{y}$ \label{eq:first_layer}
-      \STATE soft-thresholding nonlinearity~$\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$ \label{eq:thr_first}
+      \STATE Soft-thresholding nonlinearity~$\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$ \label{eq:thr_first}
       \FOR{$l=1$ \TO $L$}
@@
 
-  In \figurename~\ref{fig:nmse_n_layers_synthetic} \textsc{nmse} for different number of layers (or iterations) $L$ is presented.
+  In \figurename~\ref{fig:nmse_n_layers_synthetic} \textsc{nmse} for up to 20 layers (or iterations) $L$ is presented.
 The observation size is set to $K=50$.

### 2018-10-29 icassp_2019/paper.tex
minor updates

@@
 \begin{keywords}
-Sparse regression, Bayesian neural networks, uncertainty estimation, compressive sensing
+sparse coding, Bayesian neural networks, uncertainty estimation, compressive sensing
 \end{keywords}
@@
 The sparse coding problem can be viewed as a linear regression problem with the additional assumption that the majority of the basis representation coefficients should be zeros.
-This sparsity assumption may be represented as $l1$-penalty~\cite{tibshirani1996regression}, or, in Bayesian interpretation, as a prior that has a sharp peak at zero~\cite{tipping2001sparse}.
+This sparsity assumption may be represented as $l1$ penalty~\cite{tibshirani1996regression}, or, in Bayesian interpretation, as a prior that has a sharp peak at zero~\cite{tipping2001sparse}.
 One of the modern approaches for sparse coding utilises NNs with the soft-thresholding nonlinearity~\cite{gregor2010learning, sprechmann2015learning}.
@@
   A novel method to propagate uncertainty through the soft-thresholding nonlinearity is proposed in this paper.
-At every layer the current distribution of the target vector is represented as a spike and slab distribution~\cite{mitchell1988bayesian}, which represents the probabilities of each variable being zero, or Gaussian-distributed.
+At every layer the current distribution of the target vector is approximated with a spike and slab distribution~\cite{mitchell1988bayesian}, which represents the probabilities of each variable being zero, or Gaussian-distributed.
 Using the proposed method of uncertainty propagation, the gradients of the logarithms of normalisation constants are derived, which can be used to update a weight distribution.
@@
   \label{eq:regression_problem}
-  ||\mathbf{X}\boldsymbol\beta - \mathbf{y}||_2^2 + \alpha ||\boldsymbol\beta||_1
+  ||\mathbf{X}\boldsymbol\beta - \mathbf{y}||_2^2 + \alpha ||\boldsymbol\beta||_1 \, \text{w.r.t.} \,\boldsymbol\beta,
   \end{equation}
-w.r.t.  $\boldsymbol\beta$,  where $\alpha$ is a penalty parameter.
+  where $\alpha$ is a regularisation parameter.
 

### 2018-10-29 icassp_2019/paper.tex
minor changes

@@
   Proposed Bayes\textsc{lista} is evaluated on sparse coding problems and compared with \textsc{lista}~\cite{gregor2010learning}, \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
-The number of iterations in \textsc{ista} and \textsc{fista}  and the number of layers in NNs is $L$.
-For quantitative comparison the normalised mean square error (\textsc{nmse}) is used.
+The number of iterations in \textsc{ista} and \textsc{fista} is same as the number of layers in NNs, denoted as $L$.
+Quality is measured as the normalised mean square error (\textsc{nmse}).
 %We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn.

### 2018-11-26 nips_workshop_2018/camera_ready/BayesianLISTA.tex
started poster

--- 2018-10-28 nips_workshop_2018/BayesianLISTA.tex
@@
 \usepackage[square,numbers]{natbib}
-\usepackage[final]{nips_2018}
+\usepackage[final]{bdl_2018}
 
@@
 
-%\author{
-%  Danil Kuzin$^{\dagger}$, Olga Isupova$^{\star}$, Lyudmila Mihaylova$^{\dagger}$\\
-%  $^{\dagger}$Department of Automatic Control \qquad\qquad\qquad $^{\star}$ Department of Engineering Science\\
-%  and System Engineering \qquad\qquad\qquad\qquad\quad University of Oxford, UK\qquad\qquad\\
-%  \quad\qquad University of Sheffield, UK \qquad\qquad\qquad\qquad\quad \texttt{olga.isupova@eng.ox.ac.uk}\\
-%  \texttt{dkuzin1@sheffield.ac.uk} \qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\\
-%  \texttt{l.s.mihaylova@sheffield.ac.uk} \qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\\
-%}
 \author{
@@
 $^{\star}$Department of Engineering Science,
-University of Oxford, UK
+University of Oxford, UK \\
+\texttt{\{dkuzin1,l.s.mihaylova\}@sheffield.ac.uk,olga.isupova@eng.ox.ac.uk}
 }
@@
 \begin{document}
-
 \maketitle
-%\begin{abstract}
-%Bayesian learning allows to estimate uncertainty of predictions in neural networks by imposing the prior distributions on weights, propagating the resulting uncertainty through the layers and computing the posterior distributions of predictions.
-We propose a novel method of propagating the uncertainty through the soft thresholding nonlinearity.
-The method expands the area of Bayesian neural networks and enables the soft thresholding nonlinearity to be included in Bayesian deep neural networks for the first time.
-We design a Bayesian Learned Iterative Shrinkage-Thresholding network (Bayesian \textsc{lista}).
-We develop an efficient posterior inference algorithm based on probabilistic backpropagation.
-A series of experiments on sparse coding shows that the proposed framework provides both accurate predictions and sensible estimates of uncertainty in these predictions.
-%\end{abstract}
-
 \section{Introduction}
@@
   \label{eq:regression_problem}
-  ||\mathbf{X}\boldsymbol\beta - \mathbf{y}||_2^2 + \alpha ||\boldsymbol\beta||_1
+  ||\mathbf{X}\boldsymbol\beta - \mathbf{y}||_2^2 + \alpha ||\boldsymbol\beta||_1 \, \text{w.r.t.} \, \boldsymbol\beta,
   \end{equation}
-w.r.t.  $\boldsymbol\beta$,  where $\alpha$ is a penalty parameter.
+where $\alpha$ is a regularisation parameter.
 
- \begin{wrapfigure}[13]{l}{0.5\textwidth}  
+ \begin{wrapfigure}[13]{r}{0.5\textwidth}  
  \vspace{-10pt}
@@
 To achieve this, \textsc{ista} is limited with the fixed amount of iterations $L$ and interpreted as a recurrent NN: every iteration $l$ of \textsc{ista} corresponds to the layer $l$ of \textsc{lista}.
-A vector $\boldsymbol\beta$ for an observation~$\mathbf{y}$ is predicted by Algorithm~\ref{alg:lista}.
+A vector $\widehat{\boldsymbol\beta}$ for an observation~$\mathbf{y}$ is predicted by Algorithm~\ref{alg:lista}.
 

### 2018-11-26 nips_workshop_2018/poster/BayesianLISTAposter.tex
started poster

\documentclass[25pt, a0paper, portrait, margin=0mm, innermargin=15mm, blockverticalspace=15mm, colspace=15mm, subcolspace=8mm]{tikzposter}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{wrapfig}
\usepackage{pgfplots}
\usepackage{subcaption}
\usepackage{etoolbox}
\usepackage{booktabs}

\title{Uncertainty propagation in neural networks for sparse coding}   \institute{University of Sheffield, UK, University of Oxford, UK }
\author{Danil Kuzin, Olga Isupova, Lyudmila Mihaylova}   \titlegraphic{Logo}
\usetheme{Autumn}
\usecolorstyle{Britain}
\begin{document}
  \maketitle
  \begin{columns}
    \column{0.5}
    \block{1-LISTA}{
      \innerblock{Sparse coding}{
        Reconstruct $\boldsymbol\beta$ from observations $\mathbf{y}$ collected as $\mathbf{y} = \mathbf{X} \boldsymbol\beta + \boldsymbol\varepsilon$, such that elements $\boldsymbol\beta$ contain zeros. 
      }
      \innerblock{LISTA}{
        \begin{itemize}
          \item Represent iterative soft-thresholding algorithm as a recurrent neural network with shared weights
          \item Learn weights with backpropagation through time
          \item Overfitting
          \item No uncertainty estimation
        \end{itemize}

        \begin{algorithmic}[1]
          \REQUIRE observation $\mathbf{y}$, current weights $\mathbf{W}, \mathbf{S}$, number of layers $L$
          \STATE \textit{Initialisation.} Dense layer $\mathbf{b} \gets \mathbf{W}\mathbf{y}$
          \STATE \textit{Initialisation.} Soft-thresholding nonlinearity $\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$
          \FOR{$l=1$ \TO $L$}
          \STATE Dense layer $\mathbf{c}_l \gets \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$
          \STATE Soft-thresholding nonlinearity $\widehat{\boldsymbol\beta}_{l} \gets h_\lambda(\mathbf{c}_l)$
          \ENDFOR
          \RETURN $\widehat{\boldsymbol\beta} \gets \widehat{\boldsymbol\beta}_{L}$
        \end{algorithmic}     
      }
    }
    \block{3-Uncertainty propagation}{
      \innerblock{Idea}{
        At every step the output of soft-thresholding can be closely approximated with spike and slab distribution
      \begin{enumerate}
        \item \(\mathbf{b} = \mathbf{W}\mathbf{y}\) is Gaussian-distributed
        \item \(\widehat{\boldsymbol\beta}_{0} = h_\lambda(\mathbf{b})\) is approximated with the spike and slab distribution
        \item \(\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}\) is approximated with the Gaussian distribution
        \item \(\mathbf{c}_l = \mathbf{b} + \mathbf{e}_l\) is Gaussian-distributed
        \item \(\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)\) is approximated with the spike and slab distribution
      \end{enumerate}
      }
      \innerblock{Advantages}{
        \begin{itemize}
          \item All latent variables are modelled with parametrised distributions
          \item We can apply approximate Bayesian inference methods
        \end{itemize}
      }
    }
    \column{0.5}
    \block{2-BayesLISTA}{ 
      \innerblock{Bayesian LISTA}{
      \begin{itemize}
        \item Add priors for NN weights
        \item Perform full Bayesian inference
        \item Estimate uncertainty of predictions
      \end{itemize}
      }
    }
    \block{4-BackProp-PBP}{Blocktext}
    \block{5-Results}{
      \innerblock{Synthetic Experiments}{
        \begin{tikzfigure}[Different depth performance]
          \subcaptionbox*{\emph{NMSE}}{%
                     \includegraphics[width=200pt]{graphics/synthetic_number_of_layers/nmse_validation}
          }
          \quad
          \subcaptionbox*{\emph{F measure}}{%
                     \includegraphics[width=200pt]{graphics/synthetic_number_of_layers/f_measure_validation}
          }
          %\captionsetup{labelformat=empty}
        \end{tikzfigure}

        \begin{tikzfigure}[Different observation size performance]
          \subcaptionbox*{\emph{NMSE}}{%
                     \includegraphics[width=200pt]{graphics/synthetic_undersampling/nmse_validation}
          }
          \quad
          \subcaptionbox*{\emph{F measure}}{%
                     \includegraphics[width=200pt]{graphics/synthetic_undersampling/f_measure_validation}
          }
          %\captionsetup{labelformat=empty}
        \end{tikzfigure}
      }

      \innerblock{MNIST Experiments}{
        \begin{tikzfigure}[Posterior parameters for an image of digit 7]
          \subcaptionbox*{posterior mean}{
            \includegraphics[width=200pt]{graphics/posterior_mean}
          }
          \quad
          \subcaptionbox*{posterior spike indicator}{
            \includegraphics[width=200pt]{graphics/posterior_spike_indicator}
          }
        \end{tikzfigure}

        \begin{tikzfigure}[Samples from the posterior for an image of digit 7]
          \subcaptionbox*{posterior sample 0}{
            \includegraphics[width=150pt]{graphics/posterior_sample_0}
          }
          \quad
          \subcaptionbox*{posterior sample 1}{
            \includegraphics[width=150pt]{graphics/posterior_sample_1}
          }
          \quad
          \subcaptionbox*{posterior sample 2}{
            \includegraphics[width=150pt]{graphics/posterior_sample_2}
          }
        \end{tikzfigure}
      }

      \innerblock{Active Learning}{
        Use the estimated uncertainty to choose next training data with largest variance
        \begin{tikzfigure}[Sequential pool additions]
        \subcaptionbox*{NMSE}{
            \includegraphics[width=200pt]{graphics/active_mnist/nmse_validation}
        }
        \subcaptionbox*{F measure}{
            \includegraphics[width=200pt]{graphics/active_mnist/f_measure_validation}
        }
        \end{tikzfigure}
      }
    }

    \block{6-Summary}{Blocktext}
    \note{Notetext}
  \end{columns}
\end{document}

### 2018-11-26 bayesian_lista_src/experiments/synthetic/undersampling/run_long_L_6.py

@@ -1,0 +1,101 @@
+import numpy as np
+import six.moves.cPickle as pickle
+
+import matplotlib
+matplotlib.use('TkAgg')
+import matplotlib.pyplot as plt
+from tqdm import tqdm, trange
+import os
+from comparator.compare_sequential import SequentialComparator
+from experiments.synthetic.experiments_parameters import load_long_experiment
+
+rseed, D, _, _, batch_size, validation_size, n_iter = load_long_experiment()
+np.random.seed(rseed)
+L = 6
+K_array = [10, 20, 30, 40, 50, 60, 70, 80, 90, 100]
+
+freq_train_loss = np.zeros((len(K_array), n_iter))
+freq_validation_loss = np.zeros((len(K_array), n_iter))
+freq_train_f_measure = np.zeros((len(K_array), n_iter))
+freq_validation_f_measure = np.zeros((len(K_array), n_iter))
+freq_time = np.zeros((len(K_array), n_iter))
+
+sh_bayes_train_loss = np.zeros((len(K_array), n_iter))
+sh_bayes_validation_loss = np.zeros((len(K_array), n_iter))
+sh_bayes_train_f_measure = np.zeros((len(K_array), n_iter))
+sh_bayes_validation_f_measure = np.zeros((len(K_array), n_iter))
+sh_bayes_time = np.zeros((len(K_array), n_iter))
+
+ista_train_loss = np.zeros((len(K_array), n_iter))
+ista_validation_loss = np.zeros((len(K_array), n_iter))
+ista_train_f_measure = np.zeros((len(K_array), n_iter))
+ista_validation_f_measure = np.zeros((len(K_array), n_iter))
+
+fista_train_loss = np.zeros((len(K_array), n_iter))
+fista_validation_loss = np.zeros((len(K_array), n_iter))
+fista_train_f_measure = np.zeros((len(K_array), n_iter))
+fista_validation_f_measure = np.zeros((len(K_array), n_iter))
+
+for rseed in tqdm(range(10)):
+    np.random.seed(rseed)
+    for i, K in enumerate(tqdm(K_array)):
+        comparator = SequentialComparator(D, K, L, learning_rate=0.0001, n_train_sample=batch_size,
+                                          n_validation_sample=validation_size, train_freq=True, train_bayes=False,
+                                          train_shared_bayes=True, use_ista=True, use_fista=True, save_history=False)
+        for _ in trange(n_iter):
+            comparator.train_iteration()
+
[…]

### 2018-11-26 bayesian_lista_src/tf_probability/spike_and_slab_model.py

@@ -1,0 +1,20 @@
+import tensorflow as tf
+import tensorflow_probability as tfp
+from tensorflow_probability import edward2 as ed
+
+def spike_and_slab_model(data_dim, latent_dim, num_datapoints, stddv_datapoints): # (unmodeled) data
+  w = ed.Normal(loc=tf.zeros([data_dim, latent_dim]),
+                scale=2.0 * tf.ones([data_dim, latent_dim]),
+                name="w")  # parameter
+  z = ed.Normal(loc=tf.zeros([latent_dim, num_datapoints]),
+                scale=tf.ones([latent_dim, num_datapoints]),
+                name="z")  # parameter
+  x = ed.Normal(loc=tf.matmul(w, z),
+                scale=stddv_datapoints * tf.ones([data_dim, num_datapoints]),
+                name="x")  # (modeled) data
+  return x, (w, z)
+
+def get_joint_fn():
+    log_joint = ed.make_log_joint_fn(spike_and_slab_model)
+
+    return log_joint

### 2018-11-26 bayesian_lista_src/tf_probability/spike_and_slab_model_test.py

@@ -1,0 +1,46 @@
+import tensorflow as tf
+
+from tf_probability.spike_and_slab_model import spike_and_slab_model
+
+
+class SpikeAndSlabModelTest(tf.test.TestCase):
+    def sample_from_model(self):
+        num_datapoints = 5000
+        data_dim = 2
+        latent_dim = 1
+        stddv_datapoints = 0.5
+
+        model = spike_and_slab_model(data_dim=data_dim,
+                                  latent_dim=latent_dim,
+                                  num_datapoints=num_datapoints,
+                                  stddv_datapoints=stddv_datapoints)
+
+        with tf.Session() as sess:
+            x_train, (actual_w, actual_z) = sess.run(model)
+
+        print("Principal axes:")
+        print(actual_w)
+
+        self.assertAllEqual(x_train.shape, (2, 3))
+
+    def sample_from_model2(self):
+        num_datapoints = 5000
+        data_dim = 2
+        latent_dim = 1
+        stddv_datapoints = 0.5
+
+        model = spike_and_slab_model(data_dim=data_dim,
+                                  latent_dim=latent_dim,
+                                  num_datapoints=num_datapoints,
+                                  stddv_datapoints=stddv_datapoints)
+
+        with tf.Session() as sess:
+            x_train, (actual_w, actual_z) = sess.run(model)
+
+        print("Principal axes:")
+        print(actual_w)
+
+        self.assertAllEqual(x_train.shape, (2, 3))
+
+if __name__ == '__main__':
+    tf.test.main()

### 2018-11-26 bayesian_lista_src/tf_probability/test_pca.py

@@ -1,0 +1,210 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import seaborn as sns
+
+import tensorflow as tf
+import tensorflow_probability as tfp
+from tensorflow_probability import edward2 as ed
+import warnings
+
+plt.style.use("ggplot")
+warnings.filterwarnings('ignore')
+
+
+
+
+
+
+
+
+
+
+
+num_datapoints = 5000
+data_dim = 2
+latent_dim = 1
+stddv_datapoints = 0.5
+
+model = probabilistic_pca(data_dim=data_dim,
+                          latent_dim=latent_dim,
+                          num_datapoints=num_datapoints,
+                          stddv_datapoints=stddv_datapoints)
+
+with tf.Session() as sess:
+  x_train, (actual_w, actual_z) = sess.run(model)
+
+print("Principal axes:")
+print(actual_w)
+
+
+
+
+plt.scatter(x_train[0, :], x_train[1, :], color='blue', alpha=0.1)
+plt.axis([-20, 20, -20, 20])
+plt.title("Data set")
+plt.show()
+
+
+
+
+tf.reset_default_graph()
+
+w = tf.Variable(np.ones([data_dim, latent_dim]), dtype=tf.float32)
+z = tf.Variable(np.ones([latent_dim, num_datapoints]), dtype=tf.float32)
+
+
+def target(w, z):
+  """Unnormalized target density as a function of the parameters."""
+  return log_joint(data_dim=data_dim,
+                   latent_dim=latent_dim,
+                   num_datapoints=num_datapoints,
+                   stddv_datapoints=stddv_datapoints,
+                   w=w, z=z, x=x_train)
+
+
+energy = -target(w, z)
+
+optimizer = tf.train.AdamOptimizer(learning_rate=0.05)
+train = optimizer.minimize(energy)
+
+init = tf.global_variables_initializer()
+
+t = []
+
+num_epochs = 200
+
+with tf.Session() as sess:
+  sess.run(init)
+
+  for i in range(num_epochs):
+    sess.run(train)
+    if i % 5 == 0:
+      cE, cw, cz = sess.run([energy, w, z])
+      t.append(cE)
+
+  w_inferred_map = sess.run(w)
+  z_inferred_map = sess.run(z)
+
+
+
+
[…]

### 2018-11-26 nips_workshop_2018/submission/BayesianLISTA.tex
started poster

--- 2018-11-26 nips_workshop_2018/camera_ready/BayesianLISTA.tex
@@
 \usepackage[square,numbers]{natbib}
-\usepackage[final]{bdl_2018}
+\usepackage[preprint]{nips_2018}
 
@@
   \centering
-  \subfloat[Synthetic for different $L$]{\includegraphics[width=0.25\textwidth]{graphics/synthetic_number_of_layers/nmse_validation}
+  \subfloat[Synthetic for different $L$]{\includegraphics[width=0.27\textwidth]{graphics/synthetic_number_of_layers/nmse_validation}
   \label{fig:nmse_n_layers_synthetic}}
   \hfil
-  \subfloat[Synthetic for different $K$]{\includegraphics[width=0.25\textwidth]{graphics/synthetic_undersampling/nmse_validation}
+  \subfloat[Synthetic for different $K$]{\includegraphics[width=0.27\textwidth]{graphics/synthetic_undersampling/nmse_validation}
   \label{fig:nmse_undersampling_synthetic}}
   \hfil
-  \subfloat[Active learning example]{\includegraphics[width=0.25\textwidth]{graphics/active_mnist/nmse_validation}
+  \subfloat[Active learning example]{\includegraphics[width=0.27\textwidth]{graphics/active_mnist/nmse_validation}
   \label{fig:active_learning_mnist}}
@@
   Proposed Bayes\textsc{lista} is evaluated on sparse coding problems and compared with \textsc{lista}~\cite{gregor2010learning}, \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
-The number of iterations in \textsc{ista} and \textsc{fista}  and the number of layers in NNs is $L$.
+The number of iterations in \textsc{ista} and \textsc{fista} is same as the number of layers in NNs, denoted as $L$.
 For quantitative comparison the normalised mean square error (\textsc{nmse}) is used.
@@
 We generate $N_\text{train}=1000$ and $N_{\text{test}} = 100$ sparse vectors $\boldsymbol\beta^{(n)}$ of size $D = 100$  from the spike and slab distribution with the truncated slab: each component $\beta^{(n)}_{d}$ is zero with the probability~$0.8$ or is sampled from the standard Gaussian distribution without interval $(-0.1, 0.1)$ with the probability~$0.2$.
-The design matrix $\mathbf{X}$ is random Gaussian.
-The observations $\mathbf{y}^{(n)}$ are generated as in~(\ref{eq:regression_problem}) with the zero-mean Gaussian noise with the standard deviation $0.5$.
+The design matrix $\mathbf{X}$ is standard random Gaussian.
+The observations $\mathbf{y}^{(n)}$ are generated as $\mathbf{X} \boldsymbol\beta^{(n)}$ with the additive zero-mean Gaussian noise with the standard deviation $0.5$.
 The shrinkage parameter is set to~$\lambda = 0.1$.
@@
 The design matrix $\mathbf{X}$ is standard random Gaussian.
-Observations are generated as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta \in \mathbb{R}^{784}$ are flattened images.
+Observations are generated as $\mathbf{y}^{(n)} = \mathbf{X}\boldsymbol\beta^{(n)}$, where $\boldsymbol\beta^{(n)} \in \mathbb{R}^{784}$ are flattened images.
 The shrinkage parameter $\lambda$ is~$0.1$, the observation size $K$ is $100$.
@@
 
-  Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of \textsc{lista} (Algorithm~\ref{alg:lista}) is the result of soft-thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first} (section~\ref{subsec:forward_init}).
+  Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of \textsc{lista} (Algorithm~\ref{alg:lista}) is the result of soft-thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first}.
   Thus, all the steps of Bayes\textsc{lista} are covered and distributions for outputs of these steps are derived.
@@
   With the likelihood factors~(\ref{eq:likelihood}) of $p$ the ADF approach is employed and they are iteratively incorporated into $q$.
-The normalisation constant of $q$ with the likelihood term for the data point $n$ incorporated is (let $z_d$ denote (to simplify notation the superscript $(n)$ is omitted)
+The normalisation constant of $q$ with the likelihood term for the data point $n$ incorporated is (to simplify notation the superscript $(n)$ is omitted)
   \begin{equation}
@@
   \centering
-  \subfloat[\textsc{mnist} for $K = 100$]{\includegraphics[width=0.25\textwidth]{graphics/mnist/100_nmse_valid}
+  \subfloat[\textsc{mnist} for $K = 100$]{\includegraphics[width=0.27\textwidth]{graphics/mnist/100_nmse_valid}
   \label{fig:nmse_k_100}}
   \hfil
-  \subfloat[\textsc{mnist} for $K = 250$]{\includegraphics[width=0.25\textwidth]{graphics/mnist/250_nmse_valid}
+  \subfloat[\textsc{mnist} for $K = 250$]{\includegraphics[width=0.27\textwidth]{graphics/mnist/250_nmse_valid}
   \label{fig:nmse_k_250}}

### 2018-11-26 nips_workshop_2018/poster/BayesianLISTAposter.tex
upd poster

@@
 \usepackage{mathtools}
-\usepackage{algorithm}
+\usepackage[boxed]{algorithm}
 \usepackage{algorithmic}
@@
 \usepackage{booktabs}
+
+\AtBeginEnvironment{algorithm}{%
+  \setlength{\columnwidth}{\linewidth}%
+}
 
@@
     \block{1-LISTA}{
-      \innerblock{Sparse coding}{
-        Reconstruct $\boldsymbol\beta$ from observations $\mathbf{y}$ collected as $\mathbf{y} = \mathbf{X} \boldsymbol\beta + \boldsymbol\varepsilon$, such that elements $\boldsymbol\beta$ contain zeros.
+      \begin{minipage}[t]{0.55\linewidth}
+        \vspace{0.1in}
+        \coloredbox{
+          Estimate \(\boldsymbol\beta \) from observations \(\mathbf{y}\) collected as \(\mathbf{y} = \mathbf{X} \boldsymbol\beta + \boldsymbol\varepsilon\), s.t.\ elements \(\boldsymbol\beta \) contain zeros.
         }
-      \innerblock{LISTA}{
+      \end{minipage}
+      \begin{minipage}[t]{0.4\linewidth}
+        \begin{tikzfigure}
+          \includegraphics[width=400pt]{graphics/sparse_problem.pdf}
+        \end{tikzfigure}
+      \end{minipage}
+
+      \begin{minipage}[t]{0.55\linewidth}
+        \emph{LISTA}
         \begin{itemize}
-          \item Represent iterative soft-thresholding algorithm as a recurrent neural network with shared weights
-          \item Learn weights with backpropagation through time
-          \item Overfitting
-          \item No uncertainty estimation
+          \item Represent iterative soft-thresholding algorithm as RNN with shared weights
+          \item Learn weights with BPTT
         \end{itemize} 
+      %\end{minipage}
 
-        \begin{algorithmic}[1]
-          \REQUIRE observation $\mathbf{y}$, current weights $\mathbf{W}, \mathbf{S}$, number of layers $L$
-          \STATE \textit{Initialisation.} Dense layer $\mathbf{b} \gets \mathbf{W}\mathbf{y}$
-          \STATE \textit{Initialisation.} Soft-thresholding nonlinearity $\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$
+      %\begin{minipage}[t]{0.55\linewidth}
+
+        \begin{algorithm}[H]
+          \begin{algorithmic}
+            \STATE \textit{Init.} Dense $\mathbf{b} \gets \mathbf{W}\mathbf{y}$
+            \STATE \textit{Init.} Soft-thresholding $\widehat{\boldsymbol\beta}_0 \gets h_\lambda(\mathbf{b})$
             \FOR{$l=1$ \TO $L$} 
-          \STATE Dense layer $\mathbf{c}_l \gets \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$
-          \STATE Soft-thresholding nonlinearity $\widehat{\boldsymbol\beta}_{l} \gets h_\lambda(\mathbf{c}_l)$
+            \STATE Dense $\mathbf{c}_l \gets \mathbf{b} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$
+            \STATE Soft-thresholding $\widehat{\boldsymbol\beta}_{l} \gets h_\lambda(\mathbf{c}_l)$
             \ENDFOR
@@
           \end{algorithmic}   
-      }
+        \end{algorithm}
+          \begin{itemize}
+            \item[] {\color{red}Overfitting}
+            \item[] {\color{red}No uncertainty estimation}
+          \end{itemize} 
+      \end{minipage} 
+      \begin{minipage}[t]{0.4\linewidth} 
+        \begin{tikzfigure}
+          \includegraphics[width=400pt]{graphics/LISTA_main.pdf}
+        \end{tikzfigure}
+      \end{minipage}
     }
@@
       \begin{itemize}
-        \item Add priors for NN weights
-        \item Perform full Bayesian inference
-        \item Estimate uncertainty of predictions
+        \item[] Add priors for NN weights
+        \begin{equation}
+          p(\mathbf{W}) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij} ; 0, \eta^{-1}), \quad
+          p(\mathbf{S}) = \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; 0, \eta^{-1}),
+        \end{equation}
+        \item[] Propagate distribution for $\widehat{\boldsymbol\beta}$ through layers
+        \item[] Compute prediction as noisy NN output
+        \begin{equation}
+          p(\mathbf{\boldsymbol\beta}| \mathbf{y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda)
+          = \prod_{d=1}^D\mathcal{N}\left(\beta_d; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}\right)
+        \end{equation}
+        \item[] Update weights with PBP
       \end{itemize}

### 2018-11-27 nips_workshop_2018/poster/BayesianLISTAposter.tex
upd poster
upd presentation

@@
   \setlength{\columnwidth}{\linewidth}%
+}
+
+\renewenvironment{tikzfigure}[1][]{
+  \def \rememberparameter{#1}
+  \vspace{10pt}
+  \refstepcounter{figurecounter}
+  \begin{center}
+  }{
+    \ifx\rememberparameter\@empty
+    \else %nothing
+    \\[10pt]
+    %{\small Fig.~\thefigurecounter: \rememberparameter}
+    {\small \rememberparameter}
+    \fi
+  \end{center}
 }
@@
     \block{3-Uncertainty propagation}{
-      \innerblock{Idea}{
+      %\innerblock{Idea}{
         At every step the output of soft-thresholding can be closely approximated with spike and slab distribution
@@
       \end{enumerate}
-      }
-      \innerblock{Advantages}{
+      \begin{tikzfigure}
+        \includegraphics[width=400pt]{graphics/spsl_propagation.pdf}
+      \end{tikzfigure}
+      %}
+      %\innerblock{Advantages}{
         \begin{itemize}
@@
         \end{itemize}
+      %}
     }
+    \block{6-References}{
+      \begin{itemize}
+        \item J. M. Hern{\'a}ndez-Lobato, R. Adams. Probabilistic backpropagation for scalable learning of Bayesian neural networks. ICML 2015.
+        \item K. Gregor, Y. LeCun. Learning fast approximations of sparse coding. ICML 2010.
+      \end{itemize}
     }
@@
     \block{2-BayesLISTA}{ 
-      \innerblock{Bayesian LISTA}{
       \begin{itemize}
-        \item[] Add priors for NN weights
+        \item Add priors for NN weights
         \begin{equation}
@@
         \end{equation}
-        \item[] Propagate distribution for $\widehat{\boldsymbol\beta}$ through layers
-        \item[] Compute prediction as noisy NN output
+        \item Propagate distribution for $\widehat{\boldsymbol\beta}$ through layers
+        \item Compute prediction as noisy NN output
         \begin{equation}
@@
         \end{equation}
-        \item[] Update weights with PBP
+        \item Update weights with PBP
       \end{itemize}
       }
+    \block{4-BackProp-PBP}{
+      Approximate posterior
+    \begin{align}
+    \label{eq:approximating_dsitribution}
+    \begin{split}
+    q(\mathbf{W}, \mathbf{S}, \gamma, \eta) &= \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{dk} ; m^w_{dk}, v^w_{dk}) \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; m^s_{d'd''}, v^s_{d'd''}) \\
+    &\times \text{Gam}(\gamma; a^\gamma, b^\gamma) \text{Gam}(\eta; a^\eta, b^\eta)
+    \end{split}
+    \end{align}
+
+    probabilistic backpropagation algorithm: derivatives of the logarithm of a normalisation constant
+
+    \begin{equation}
+    q(a) = Z^{-1}f(a)\mathcal{N}(a; m, v)
+    \end{equation}
+    \begin{equation}
+    Z \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right],
+    \end{equation}
+    where $\{\omega^{\widehat{\boldsymbol\beta}}_d, m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\}$ are the parameters of the spike and slab distribution for $[\widehat{\boldsymbol\beta}]_d$.
+
     }
-    \block{4-BackProp-PBP}{Blocktext}
     \block{5-Results}{
-      \innerblock{Synthetic Experiments}{
+      %\innerblock{Synthetic Experiments}{
+        \emph{Synthetic}
         \begin{tikzfigure}[Different depth performance]
           \subcaptionbox*{\emph{NMSE}}{%
-                     \includegraphics[width=200pt]{graphics/synthetic_number_of_layers/nmse_validation}
+                     \includegraphics[width=300pt]{graphics/synthetic_number_of_layers/nmse_validation}
           }
@@
           \subcaptionbox*{\emph{F measure}}{%
-                     \includegraphics[width=200pt]{graphics/synthetic_number_of_layers/f_measure_validation}
+                     \includegraphics[width=300pt]{graphics/synthetic_number_of_layers/f_measure_validation}
           }
@@
           \subcaptionbox*{\emph{NMSE}}{%
-                     \includegraphics[width=200pt]{graphics/synthetic_undersampling/nmse_validation}
+                     \includegraphics[width=300pt]{graphics/synthetic_undersampling/nmse_validation}
           }
@@
           \subcaptionbox*{\emph{F measure}}{%
-                     \includegraphics[width=200pt]{graphics/synthetic_undersampling/f_measure_validation}
+                     \includegraphics[width=300pt]{graphics/synthetic_undersampling/f_measure_validation}
           }
@@
         \end{tikzfigure}
-      }
-
-      \innerblock{MNIST Experiments}{
+      %}
+      \emph{MNIST}
+      %\innerblock{MNIST Experiments}{
         \begin{tikzfigure}[Posterior parameters for an image of digit 7]
@@
           \subcaptionbox*{posterior sample 0}{
-            \includegraphics[width=150pt]{graphics/posterior_sample_0}
+            \includegraphics[width=200pt]{graphics/posterior_sample_0}
           }
@@
           \subcaptionbox*{posterior sample 1}{
-            \includegraphics[width=150pt]{graphics/posterior_sample_1}
+            \includegraphics[width=200pt]{graphics/posterior_sample_1}
           }
@@
           \subcaptionbox*{posterior sample 2}{
-            \includegraphics[width=150pt]{graphics/posterior_sample_2}
+            \includegraphics[width=200pt]{graphics/posterior_sample_2}
           }
         \end{tikzfigure}
-      }
+      %}
 
-      \innerblock{Active Learning}{
+      %\innerblock{Active Learning}{
+      \emph{Active Learning}
         Use the estimated uncertainty to choose next training data with largest variance
@@
         \subcaptionbox*{NMSE}{
-            \includegraphics[width=200pt]{graphics/active_mnist/nmse_validation}
+            \includegraphics[width=300pt]{graphics/active_mnist/nmse_validation}
         }
         \subcaptionbox*{F measure}{
-            \includegraphics[width=200pt]{graphics/active_mnist/f_measure_validation}
+            \includegraphics[width=300pt]{graphics/active_mnist/f_measure_validation}
         }
         \end{tikzfigure}
+      %}
+
     }
-    }
-
-    \block{6-Summary}{Blocktext}
-    \note{Notetext}
   \end{columns}

### 2018-11-27 SparseUtils/plot_gaussian.py

@@ -11,5 +11,12 @@ betas = np.zeros(n,)
 x = np.linspace(-2, 2, n)
 y = norm.pdf(x)
 
-plt.plot(x, y)
+fig = plt.figure()
+ax = fig.add_subplot(111)
+ax.axvline(color='k', linestyle='--')
+ax.axhline(color='k', linestyle='--')
+ax.plot(x, y, linewidth=5)
+plt.tick_params(axis='x', which='both', bottom=False, top=False, labelbottom=False)
+plt.tick_params(axis='y', which='both', left=False, right=False, labelleft=False)
+plt.tight_layout()
 plt.savefig("gauss.pdf", format='pdf', dpi='figure')

### 2018-11-27 SparseUtils/plot_spsl.py

@@ -13,5 +13,12 @@ x = np.linspace(-2, 2, n)
 y = pi*norm.pdf(x)
 
 y[int(n / 2)] = (1-pi)
-plt.plot(x, y)
+fig = plt.figure()
+ax = fig.add_subplot(111)
+ax.axvline(color='k', linestyle='--')
+ax.axhline(color='k', linestyle='--')
+ax.plot(x, y, linewidth=5)
+plt.tick_params(axis='x', which='both', bottom=False, top=False, labelbottom=False)
+plt.tick_params(axis='y', which='both', left=False, right=False, labelleft=False)
+plt.tight_layout()
 plt.savefig("spsl.pdf", format='pdf', dpi='figure')

### 2018-11-28 nips_workshop_2018/camera_ready/BayesianLISTA.tex
upd paper

@@
 \usepackage[square,numbers]{natbib}
+%\usepackage[final]{nips_2018}
 \usepackage[final]{bdl_2018}
@@
 At every layer the current distribution of the target vector is represented as a spike and slab distribution~\cite{mitchell1988bayesian}, which represents the probabilities of each variable being zero, or Gaussian-distributed.
-Using the proposed method of uncertainty propagation, the gradients of the logarithms of normalisation constants are derived, which can be used to update a weight distribution.
+Using the proposed method of uncertainty propagation, the gradients of the logarithms of normalisation constants are derived, that can be used to update a weight distribution.
 A novel Bayesian NN for sparse coding is designed utilising both the proposed method of uncertainty propagation and Bayesian inference algorithm.
@@
 
-% The rest of the paper is organised as follows.
-A novel Bayesian neural network is introduced in Section~\ref{sec:bayesian_lista}.
-The proposed forward uncertainty propagation and probabilistic backpropagation methods are given in Sections~\ref{sec:fprop} and~\ref{sec:backpropagation}.
-Section~\ref{sec:experiments} provides the experimental results and Section~\ref{sec:conclusions} concludes the paper.
-
+ The rest of the paper is organised as follows.
+A NN approach for sparse coding is described in Section~\ref{subsec:nn_sc}.
+The Bayesian formulation is introduced in Section~\ref{subsec:bayesian_lista}.
+Section~\ref{sec:experiments} provides the experimental results.
+The proposed forward uncertainty propagation and probabilistic backpropagation methods are given in Appendices~\ref{sec:fprop} and~\ref{sec:backpropagation}.
 \section{Neural networks for sparse coding}
@@
 \label{subsec:nn_sc}
-  The NN approach to sparse coding is based on earlier Iterative Shrinkage and Thresholding Algorithm (\textsc{ista}) \cite{daubechies2004iterative}.
+  The NN approach to sparse coding is based on earlier Iterative Shrinkage and Thresholding Algorithm (ISTA) \cite{daubechies2004iterative}.
 It addresses the sparse coding problem as the linear regression problem with the $l1$ penalty that promotes sparsity.
-For the linear regression model with observations $\mathbf{y} \in \mathbb{R}^K$, the design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$, and the sparse unknown vector of weights $\boldsymbol\beta \in \mathbb{R}^D$, \textsc{ista} minimises
+For the linear regression model with observations $\mathbf{y} \in \mathbb{R}^K$, the design matrix $\mathbf{X} \in \mathbb{R}^{K \times D}$, and the sparse unknown vector of weights $\boldsymbol\beta \in \mathbb{R}^D$, ISTA minimises
   \begin{equation}
@@
   \begin{algorithm}[H]
-    \caption{\textsc{lista} forward propagation}
+    \caption{LISTA forward propagation}
 \label{alg:lista}   
@@
 \end{wrapfigure}  
-At every iteration $l$, \textsc{ista} obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ propagated through the soft-thresholding function %$h_\lambda(\cdot)$
+At every iteration $l$, ISTA obtains the new estimate $\widehat{\boldsymbol\beta}_l$ of the target vector $\boldsymbol\beta$ as the linear transformation $\mathbf{b} = \mathbf{W}\mathbf{y} + \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ propagated through the soft-thresholding function %$h_\lambda(\cdot)$
   \begin{equation}
@@
   where $\lambda$ is a shrinkage parameter.
-  In \textsc{ista}, weights $\mathbf{W}$ and $\mathbf{S}$ of the linear transformation are assumed fixed.
+  In ISTA, weights $\mathbf{W}$ and $\mathbf{S}$ of the linear transformation are assumed fixed.
 
-In contrast to \textsc{ista}, Learned \textsc{ista} (\textsc{lista}) \cite{gregor2010learning} learns the values of matrices $\mathbf{W}$ and $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
-To achieve this, \textsc{ista} is limited with the fixed amount of iterations $L$ and interpreted as a recurrent NN: every iteration $l$ of \textsc{ista} corresponds to the layer $l$ of \textsc{lista}.
+In contrast to ISTA, Learned ISTA (LISTA) \cite{gregor2010learning} learns the values of matrices $\mathbf{W}$ and $\mathbf{S}$ based on a set of pairs $\{\mathbf{Y}, \mathbf{B}\}=\{\mathbf{y}^{(n)}, \boldsymbol\beta^{(n)}\}_{n=1}^N$, where $N$ is the number of these pairs.
+To achieve this, ISTA is limited with the fixed amount of iterations $L$ and interpreted as a recurrent NN: every iteration $l$ of ISTA corresponds to the layer $l$ of LISTA.
 A vector $\widehat{\boldsymbol\beta}$ for an observation~$\mathbf{y}$ is predicted by Algorithm~\ref{alg:lista}.
 
- % In \textsc{lista}, matrices $\mathbf{W}$ and $\mathbf{S}$ are the parameters that are initialised as in the \textsc{ista} and then updated with the backpropagation algorithm.
+ % In LISTA, matrices $\mathbf{W}$ and $\mathbf{S}$ are the parameters that are initialised as in the ISTA and then updated with the backpropagation algorithm.
 Vectors $\mathbf{c}_l$ and $\mathbf{b}$ are auxiliary vectors that describe forward propagation.
 
-  \subsection{Bayes\textsc{lista}}
+  \subsection{BayesLISTA}
   \label{subsec:bayesian_lista}
-  This section introduces the proposed Bayesian version of \textsc{lista} (Bayes\textsc{lista}). The prior distributions are imposed on the unknown weights
+  This section introduces the proposed Bayesian version of LISTA (BayesLISTA). The prior distributions are imposed on the unknown weights
   \begin{equation}
@@
 
-  For every layer $l$ of Bayes\textsc{lista}, $\widehat{\boldsymbol\beta}_{l}$ is assumed to have the spike and slab distribution with the spike probability $\boldsymbol\omega$, the slab mean $\mathbf{m}$, and the slab variance $\mathbf{v}$
+  For every layer $l$ of BayesLISTA, $\widehat{\boldsymbol\beta}_{l}$ is assumed to have the spike and slab distribution with the spike probability $\boldsymbol\omega$, the slab mean $\mathbf{m}$, and the slab variance $\mathbf{v}$
   \begin{equation}
@@
   where $\delta_0$ is the delta-function that represents a spike, $[\cdot]_d$ denotes the $d$-th component of a vector.
-In appendix we show that the output of the next layer $\widehat{\boldsymbol\beta}_{l+1}$ can be approximated with the spike and slab distribution and, therefore, the output of the Bayes\textsc{lista} network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
+In appendix we show that the output of the next layer $\widehat{\boldsymbol\beta}_{l+1}$ can be approximated with the spike and slab distribution and, therefore, the output of the BayesLISTA network $\widehat{\boldsymbol\beta}$ has the spike and slab distribution.
 
-  To introduce the uncertainty of predictions, we assume that the true $\boldsymbol\beta$ is an output $f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$ of the Bayes\textsc{lista} network corrupted by the additive Gaussian zero-mean noise with the precision~$\gamma$.
+  To introduce the uncertainty of predictions, we assume that the true $\boldsymbol\beta$ is an output $f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)$ of the BayesLISTA network corrupted by the additive Gaussian zero-mean noise with the precision~$\gamma$.
 Then the likelihood of $\mathbf{B}$ is defined as
@@
 
-In the appendix we describe modification of \textsc{lista} forward propagation (Algorithm~\ref{alg:lista}) to include probability distributions of the random variables introduced in this section and also an efficient Bayesian inference algorithm.
+In the appendix we describe modification of LISTA forward propagation (Algorithm~\ref{alg:lista}) to include probability distributions of the random variables introduced in this section and also an efficient Bayesian inference algorithm.
 
@@
   \label{fig:active_learning_mnist}}
-  \caption{\textsc{nmse} results.
+  \caption{NMSE results.
 The synthetic data results for different number of layers~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}.
-The active learning example results on the \textsc{mnist} data~\protect\subref{fig:active_learning_mnist}.}
+The active learning example results on the MNIST data~\protect\subref{fig:active_learning_mnist}.}
   \label{fig:number_of_layers_synthetic}
@@
 
-  Proposed Bayes\textsc{lista} is evaluated on sparse coding problems and compared with \textsc{lista}~\cite{gregor2010learning}, \textsc{ista} \cite{daubechies2004iterative} and Fast \textsc{ista} (\textsc{fista}) \cite{beck2009fast}.
-The number of iterations in \textsc{ista} and \textsc{fista}  and the number of layers in NNs is $L$.
-For quantitative comparison the normalised mean square error (\textsc{nmse}) is used.
-%We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for \textsc{lista} to learn.
+  Proposed BayesLISTA is evaluated on sparse coding problems and compared with LISTA~\cite{gregor2010learning}, ISTA \cite{daubechies2004iterative} and Fast ISTA (FISTA) \cite{beck2009fast}.
+The number of iterations in ISTA and FISTA  and the number of layers in NNs is $L$.
+For quantitative comparison the normalised mean square error (NMSE) is used.
+%We demonstrate the performance on small datasets to highlight that the proposed algorithm can infer accurate predictions when the dataset size is not sufficient for LISTA to learn.
 
@@
 
-  In \figurename~\ref{fig:nmse_n_layers_synthetic} \textsc{nmse} for different number of layers (or iterations) $L$ is presented.
-The observation size is set to $K=50$.
-Bayes\textsc{lista} outperforms competitors.
+  In \figurename~\ref{fig:nmse_n_layers_synthetic} NMSE for different number of layers (or iterations) $L$ is presented. The observation size is set to $K=50$. BayesLISTA outperforms competitors.
 %  \begin{figure}[t]
 %  \centering
-%  \subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
+%  \subfloat[NMSE on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
 %  ~
-%  \subfloat[\textsc{nmse} for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}
+%  \subfloat[NMSE for different $L$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}
 %  \label{fig:nmse_n_layers_synthetic}}
@@
 %  \label{fig:f_meas_n_layers_synthetic}}\\[-13pt]
-%  \subfloat[\textsc{nmse} for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/nmse_validation}
+%  \subfloat[NMSE for different $K$]{\includegraphics[width=0.48\columnwidth]{graphics/synthetic_undersampling/nmse_validation}
 %  \label{fig:nmse_undersampling_synthetic}}
@@
 %  \end{figure}
-   \figurename~\ref{fig:nmse_undersampling_synthetic} gives \textsc{nmse} for different observation sizes $K$.
+   \figurename~\ref{fig:nmse_undersampling_synthetic} gives NMSE for different observation sizes $K$.
 The number of layers (iterations) is set as $L=4$.
-In the previous experiment, Bayesian and classic \textsc{lista} show similar results with this number of layers.
-\figurename~\ref{fig:nmse_undersampling_synthetic} confirms this competitive behaviour between two \textsc{lista}s.
-\textsc{ista} and \textsc{fista} underperform the NNs.
-%Overall, the experiments on the synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.
+In the previous experiment, Bayesian and classic LISTA show similar results with this number of layers.
+\figurename~\ref{fig:nmse_undersampling_synthetic} confirms this competitive behaviour between two LISTAs.
+ISTA and FISTA underperform the NNs.
+%Overall, the experiments on the synthetic data demonstrate that Bayesian LISTA provides competitive results in terms of predictive accuracy.
 
   \subsection{Active learning}
- To demonstrate a potential scenario that can benefit from uncertainty estimates of Bayes\textsc{lista}, we consider the active learning example~\cite{settles.tr09}.
+ To demonstrate a potential scenario that can benefit from uncertainty estimates of BayesLISTA, we consider the active learning example~\cite{settles.tr09}.
 The active learning area researches ways to select new training subsets to reduce the total number of required supervision.
@@
 
- The \textsc{mnist} dataset~\cite{lecun1998gradient} is utilised.
+ The MNIST dataset~\cite{lecun1998gradient} is utilised.
 The dataset contains images of handwritten digits of size $28 \times 28 = 784$.
@@
 
-  Figure \ref{fig:active_learning_mnist} demonstrates performance of the active and non-active methods of updates with Bayes\textsc{lista}.
+  Figure \ref{fig:active_learning_mnist} demonstrates performance of the active and non-active methods of updates with BayesLISTA.
 The active approach with uncertainty sampling steadily demonstrates better results.
-This means the posterior distribution learnt by Bayes\textsc{lista} is an adequate estimate of the true posterior.
+This means the posterior distribution learnt by BayesLISTA is an adequate estimate of the true posterior.
 
- Appendix provides additional results on predictive performance on the \textsc{mnist} data.
+ Appendix provides additional results on predictive performance on the MNIST data.
 
@@
 \appendix
-  \section*{Appendix A: Uncertainty propagation through soft-thresholding}
+  \section{Appendix: Uncertainty propagation through soft-thresholding}
   \label{sec:fprop}
-  This section describes modification of \textsc{lista} forward propagation (Algorithm~\ref{alg:lista}) to include probability distributions of the random variables introduced in section~\ref{subsec:bayesian_lista}.
+  This section describes modification of LISTA forward propagation (Algorithm~\ref{alg:lista}) to include probability distributions of the random variables introduced in section~\ref{subsec:bayesian_lista}.
 
@@
   \label{subsec:forward_init}
-  At step \ref{eq:first_layer} of \textsc{lista} (Algorithm~\ref{alg:lista}) the matrix $\mathbf{W}$ consists of Gaussian-distributed components $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y}$ is a deterministic vector.
+  At step \ref{eq:first_layer} of LISTA (Algorithm~\ref{alg:lista}) the matrix $\mathbf{W}$ consists of Gaussian-distributed components $w_{dk} \sim \mathcal{N}(m^w_{dk}, v^w_{dk})$, and $\mathbf{y}$ is a deterministic vector.
 Then the output $\mathbf{b}$ is a vector of Gaussian-distributed components $b_d \sim \mathcal{N}(m^b_d, v^b_d)$, where $m^b_d = \sum_{k=1}^Ky_k m^w_{dk}$, and $v^b_d = \sum_{k=1}^Ky_k^2v^w_{dk}$.
@@
 
-  At step~\ref{eq:thr_first} of \textsc{lista} (Algorithm~\ref{alg:lista}) the Gaussian vector $\mathbf{b}$ is taken as an input of the soft-thresholding function.
+  At step~\ref{eq:thr_first} of LISTA (Algorithm~\ref{alg:lista}) the Gaussian vector $\mathbf{b}$ is taken as an input of the soft-thresholding function.
 When a Gaussian random variable $x \sim \mathcal{N}(x; m, v)$ is propagated through the soft-thresholding function $x^* = h_{\lambda}(x)$, the probability mass of the resulting random variable $x^*$ is split into two parts.
@@
   \subsection*{Main layers}
-  At step \ref{eq:l_dense_layer} of \textsc{lista} (Algorithm~\ref{alg:lista}) the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components: $b_d \sim \mathcal{N}(m^b_d, v^b_d)$, $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables: $[\widehat{\beta}_{l-1}]_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
+  At step \ref{eq:l_dense_layer} of LISTA (Algorithm~\ref{alg:lista}) the vector $\mathbf{b}$ and matrix $\mathbf{S}$ consist of Gaussian components: $b_d \sim \mathcal{N}(m^b_d, v^b_d)$, $s_{d'd''} \sim \mathcal{N}(m^s_{d'd''}, v^s_{d'd''})$, and $\widehat{\boldsymbol\beta}_{l-1}$ is a vector of the spike and slab random variables: $[\widehat{\beta}_{l-1}]_d \sim \omega_d \delta_0 + (1 - \omega_d)\mathcal{N}(m_d, v_d)$.
 
@@
 %  
-%  Let $\mathbf{e}_l$ denote the product $\mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at step \ref{eq:l_dense_layer} of \textsc{lista}.
+%  Let $\mathbf{e}_l$ denote the product $\mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ at step \ref{eq:l_dense_layer} of LISTA.
 We assume that $\mathbf{S}$ and $\widehat{\boldsymbol\beta}_{l-1}$ are mutually independent.
@@
 
-  Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of \textsc{lista} (Algorithm~\ref{alg:lista}) is the result of soft-thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first} (section~\ref{subsec:forward_init}).
-  Thus, all the steps of Bayes\textsc{lista} are covered and distributions for outputs of these steps are derived.
+  Then $\widehat{\boldsymbol\beta}_{l}$ at step \ref{eq:l_thr} of LISTA (Algorithm~\ref{alg:lista}) is the result of soft-thresholding of a Gaussian variable, which is approximated with the spike and slab distribution,  similar to step \ref{eq:thr_first} (section~\ref{subsec:forward_init}).
+  Thus, all the steps of BayesLISTA are covered and distributions for outputs of these steps are derived.
 
-  \section*{Appendix B: Backpropagation}
+  \section{Appendix: Backpropagation}
   \label{sec:backpropagation}
@@
   \centering
-  \subfloat[\textsc{mnist} for $K = 100$]{\includegraphics[width=0.25\textwidth]{graphics/mnist/100_nmse_valid}
+  \subfloat[MNIST for $K = 100$]{\includegraphics[width=0.25\textwidth]{graphics/mnist/100_nmse_valid}
   \label{fig:nmse_k_100}}
   \hfil
-  \subfloat[\textsc{mnist} for $K = 250$]{\includegraphics[width=0.25\textwidth]{graphics/mnist/250_nmse_valid}
+  \subfloat[MNIST for $K = 250$]{\includegraphics[width=0.25\textwidth]{graphics/mnist/250_nmse_valid}
   \label{fig:nmse_k_250}}
-  \caption{\textsc{nmse} results on the \textsc{mnist} data for increasing number of iterations with the observation size $K = 100$~\protect\subref{fig:nmse_k_100} and $K = 250$~\protect\subref{fig:nmse_k_250}}
+  \caption{NMSE results on the MNIST data for increasing number of iterations with the observation size $K = 100$~\protect\subref{fig:nmse_k_100} and $K = 250$~\protect\subref{fig:nmse_k_250}}
   \label{fig:number_of_layers_synthetic}
@@
 
-\section*{Appendix C: Predictive performance on \textsc{mnist} data}
-In this experiment, the methods are evaluated on the \textsc{mnist} dataset in terms of predictive performance. We use $100$ images for training and $100$ for test.
+\section{Appendix: Predictive performance on MNIST data}
+In this experiment, the methods are evaluated on the MNIST dataset in terms of predictive performance. We use $100$ images for training and $100$ for test.
 
-  Figures \ref{fig:nmse_k_100} and~\ref{fig:nmse_k_250} present \textsc{nmse} with observation sizes $100$ and $250$.
+  Figures \ref{fig:nmse_k_100} and~\ref{fig:nmse_k_250} present NMSE with observation sizes $100$ and $250$.
 The experiment with $K=100$ presents severe conditions for the algorithms: the limited size of the training dataset combined with the small dimensionality of observations.
-Bayes\textsc{lista} is able to learn under these conditions, significantly outperforming \textsc{lista}.
+BayesLISTA is able to learn under these conditions, significantly outperforming LISTA.
 Under better conditions of the second experiment with $K=250$, both NNs converge to the similar results.
-However, Bayes\textsc{lista} demonstrates a remarkably better convergence rate.
-\textsc{ista} and \textsc{fista} are unable to perform well in these experiments.
+However, BayesLISTA demonstrates a remarkably better convergence rate.
+ISTA and FISTA are unable to perform well in these experiments.
 

### 2018-11-29 nips_workshop_2018/camera_ready/BayesianLISTA.tex
updated camera-ready

@@
   \label{sec:bayesian_lista}
-  The section first reviews existing NNs for sparse coding and then introduces the novel Bayesian NN.
-
+  This section presents background knowledge about networks for sparse coding and then describes the novel Bayesian neural network. 
 \subsection{Frequentist neural networks}  
@@
  \begin{wrapfigure}[13]{r}{0.5\textwidth}  
- \vspace{-10pt}
+ \vspace{-25pt}
 \begin{minipage}{0.5\textwidth}
@@
 
- Appendix provides additional results on predictive performance on the MNIST data.
+ Appendix~\ref{app:mnist} provides additional results on predictive performance on the MNIST data.
 
@@
 \section{Appendix: Predictive performance on MNIST data}
+\label{app:mnist}
 In this experiment, the methods are evaluated on the MNIST dataset in terms of predictive performance. We use $100$ images for training and $100$ for test.

### 2018-11-29 nips_workshop_2018/poster/BayesianLISTAposter.tex
add logos

@@
 
-\title{Uncertainty propagation in neural networks for sparse coding}   \institute{University of Sheffield, UK, University of Oxford, UK }
-\author{Danil Kuzin, Olga Isupova, Lyudmila Mihaylova}   \titlegraphic{Logo}
+\title{Uncertainty propagation in neural networks for sparse coding}   
+\institute{University of Sheffield, UK, University of Oxford, UK }
+\author{Danil Kuzin, Olga Isupova, Lyudmila Mihaylova}   
+\titlegraphic{\includegraphics[width=0.25\textwidth]{graphics/University_of_Sheffield_coat_of_arms}
+\vspace{-1in}\includegraphics[width=0.247\textwidth]{graphics/oxford_coat_of_arms}}
 \usetheme{Autumn}
 \usecolorstyle{Britain}
+
+\makeatletter
+\renewcommand\TP@maketitle{%
+    \begin{minipage}{0.2\linewidth}
+       \centering
+       \@titlegraphic
+    \end{minipage}
+    \hfill
+   \begin{minipage}{0.8\linewidth}
+        \centering
+        \color{titlefgcolor}
+        {\bfseries \Huge \sc \@title \par}
+        \vspace*{1em}
+        {\huge \@author \par}
+        \vspace*{1em}
+        {\LARGE \@institute}
+    \end{minipage}%
+}
+\makeatother
+
 \begin{document}

### 2018-11-29 nips_workshop_2018/poster/BayesianLISTAposter.tex
final poster

@@
 \usepackage{booktabs}
+
+\tikzposterlatexaffectionproofoff
 
@@
 
-\title{Uncertainty propagation in neural networks for sparse coding}   
-\institute{University of Sheffield, UK, University of Oxford, UK }
-\author{Danil Kuzin, Olga Isupova, Lyudmila Mihaylova}   
+\title{\parbox{\linewidth}{\centering Uncertainty propagation in neural networks \\ for sparse coding}}
+\institute{$^{\star}$University of Sheffield, UK \quad $^{\dagger}$University of Oxford, UK }
+\author{Danil Kuzin$^{\star}$, Olga Isupova$^{\dagger}$, Lyudmila Mihaylova$^{\star}$}   
 \titlegraphic{\includegraphics[width=0.25\textwidth]{graphics/University_of_Sheffield_coat_of_arms}
@@
     \column{0.5}
-    \block{1-LISTA}{
+    \block{1. LISTA}{
       \begin{minipage}[t]{0.55\linewidth}
@@
       \begin{minipage}[t]{0.55\linewidth}
-        \emph{LISTA}
+        \emph{LISTA} [G\&L]
         \begin{itemize}
@@
     }
-    \block{3-Uncertainty propagation}{
+    \block{3. Uncertainty propagation}{
       %\innerblock{Idea}{
-        At every step the output of soft-thresholding can be closely approximated with spike and slab distribution
+        At every step the output of soft-thresholding can be closely approximated with the spike and slab distribution
       \begin{enumerate}
         \item \(\mathbf{b} = \mathbf{W}\mathbf{y}\) is Gaussian-distributed
+        \begin{tikzfigure}
+          \includegraphics[width=440pt]{graphics/gauss_delta.pdf}
+        \end{tikzfigure}
         \item \(\widehat{\boldsymbol\beta}_{0} = h_\lambda(\mathbf{b})\) is approximated with the spike and slab distribution
+        \begin{tikzfigure}
+          \includegraphics[width=440pt]{graphics/spsl_propagation.pdf}
+        \end{tikzfigure}
         \item \(\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}\) is approximated with the Gaussian distribution
+        \begin{tikzfigure}
+          \includegraphics[width=440pt]{graphics/gauss_spsl.pdf}
+        \end{tikzfigure}
         \item \(\mathbf{c}_l = \mathbf{b} + \mathbf{e}_l\) is Gaussian-distributed
+        \begin{tikzfigure}
+          \includegraphics[width=440pt]{graphics/gauss_gauss.pdf}
+        \end{tikzfigure}
         \item \(\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)\) is approximated with the spike and slab distribution
+        \begin{tikzfigure}
+          \includegraphics[width=440pt]{graphics/spsl_propagation.pdf}
+        \end{tikzfigure}
     \end{enumerate}
-      \begin{tikzfigure}
-        \includegraphics[width=400pt]{graphics/spsl_propagation.pdf}
-      \end{tikzfigure}
       %}
@@
         \begin{itemize}
-          \item All latent variables are modelled with parametrised distributions
-          \item We can apply approximate Bayesian inference methods
+          \item[] {\color{blue}All latent variables are modelled with parametrised distributions}
+          \item[] {\color{blue}We can apply approximate Bayesian inference methods}
         \end{itemize}
@@
     }
-    \block{6-References}{
+    \block{6. References}{
       \begin{itemize}
-        \item J. M. Hern{\'a}ndez-Lobato, R. Adams. Probabilistic backpropagation for scalable learning of Bayesian neural networks. ICML 2015.
-        \item K. Gregor, Y. LeCun. Learning fast approximations of sparse coding. ICML 2010.
+        \item[] [HL\&A] J. M. Hern{\'a}ndez-Lobato, R. Adams. Probabilistic backpropagation for scalable learning of Bayesian neural networks. ICML 2015.
+        \item[] [G\&L] K. Gregor, Y. LeCun. Learning fast approximations of sparse coding. ICML 2010.
       \end{itemize}
@@
     \column{0.5}
-    \block{2-BayesLISTA}{ 
+    \block{2. BayesLISTA}{ 
       \begin{itemize}
         \item Add priors for NN weights
-        \begin{equation}
+        \begin{equation*}
           p(\mathbf{W}) = \prod_{d=1}^D\prod_{k=1}^K \mathcal{N}(w_{ij} ; 0, \eta^{-1}), \quad
           p(\mathbf{S}) = \prod_{d'=1}^D\prod_{d''=1}^D \mathcal{N}(s_{d'd''} ; 0, \eta^{-1}),
-        \end{equation}
+        \end{equation*}
         \item Propagate distribution for $\widehat{\boldsymbol\beta}$ through layers
         \item Compute prediction as noisy NN output
-        \begin{equation}
+        \begin{equation*}
           p(\mathbf{\boldsymbol\beta}| \mathbf{y}, \mathbf{W}, \mathbf{S}, \gamma, \lambda)
           = \prod_{d=1}^D\mathcal{N}\left(\beta_d; [f(\mathbf{y} ; \mathbf{S}, \mathbf{W}, \lambda)]_d, \gamma^{-1}\right)
-        \end{equation}
+        \end{equation*}
         \item Update weights with PBP
@@
       }
-    \block{4-BackProp-PBP}{
+    \block{4. BackProp-PBP}{
       Approximate posterior
-    \begin{align}
+    \begin{align*}
     \label{eq:approximating_dsitribution}
@@
     \end{split}
-    \end{align}
+    \end{align*}
 
-    probabilistic backpropagation algorithm: derivatives of the logarithm of a normalisation constant
-
-    \begin{equation}
+    \coloredbox{
+      Probabilistic backpropagation [HL\&A]: use derivatives of the logarithm of a normalisation constant to update weight distributions
+    }
+    \begin{equation*}
     q(a) = Z^{-1}f(a)\mathcal{N}(a; m, v)
-    \end{equation}
-    \begin{equation}
+    \end{equation*}
+    \begin{equation*}
     Z \approx \prod_{d=1}^D \left[\omega^{\widehat{\boldsymbol\beta}}_d  \mathcal{T}\left(\beta_d ; 0, \beta^\gamma / \alpha^\gamma, 2\alpha^\gamma\right) + \vphantom{m^{\widehat{\boldsymbol\beta}}_d} \left(1 - \omega^{\widehat{\boldsymbol\beta}}_d\right)\mathcal{N}\left(\beta_d ; m^{\widehat{\boldsymbol\beta}}_d,  \beta^\gamma / (\alpha^\gamma - 1) + v^{\widehat{\boldsymbol\beta}}_d\right)\right],
-    \end{equation}
+    \end{equation*}
     where $\{\omega^{\widehat{\boldsymbol\beta}}_d, m^{\widehat{\boldsymbol\beta}}_d, v^{\widehat{\boldsymbol\beta}}_d\}$ are the parameters of the spike and slab distribution for $[\widehat{\boldsymbol\beta}]_d$.
@@
     }
-    \block{5-Results}{
+    \block{5. Results}{
       %\innerblock{Synthetic Experiments}{
@@
         \begin{tikzfigure}[Different depth performance]
-          \subcaptionbox*{\emph{NMSE}}{%
                      \includegraphics[width=300pt]{graphics/synthetic_number_of_layers/nmse_validation}
-          }
 \quad
-          \subcaptionbox*{\emph{F measure}}{%
                      \includegraphics[width=300pt]{graphics/synthetic_number_of_layers/f_measure_validation}
-          }
           %\captionsetup{labelformat=empty}
@@
         \begin{tikzfigure}[Different observation size performance]
-          \subcaptionbox*{\emph{NMSE}}{%
                      \includegraphics[width=300pt]{graphics/synthetic_undersampling/nmse_validation}
-          }
           \quad
-          \subcaptionbox*{\emph{F measure}}{%
                      \includegraphics[width=300pt]{graphics/synthetic_undersampling/f_measure_validation}
-          }
           %\captionsetup{labelformat=empty}
@@
       %\innerblock{MNIST Experiments}{
-        \begin{tikzfigure}[Posterior parameters for an image of digit 7]
-          \subcaptionbox*{posterior mean}{
+        \begin{tikzfigure}[Posterior mean and spike indicator for an image of digit 7]
             \includegraphics[width=200pt]{graphics/posterior_mean}
-          }
           \quad
-          \subcaptionbox*{posterior spike indicator}{
             \includegraphics[width=200pt]{graphics/posterior_spike_indicator}
-          }
         \end{tikzfigure}
@@
         \begin{tikzfigure}[Samples from the posterior for an image of digit 7]
-          \subcaptionbox*{posterior sample 0}{
             \includegraphics[width=200pt]{graphics/posterior_sample_0}
-          }
           \quad
-          \subcaptionbox*{posterior sample 1}{
             \includegraphics[width=200pt]{graphics/posterior_sample_1}
-          }
           \quad
-          \subcaptionbox*{posterior sample 2}{
             \includegraphics[width=200pt]{graphics/posterior_sample_2}
-          }
         \end{tikzfigure}
@@
         \begin{tikzfigure}[Sequential pool additions]
-        \subcaptionbox*{NMSE}{
             \includegraphics[width=300pt]{graphics/active_mnist/nmse_validation}
-        }
-        \subcaptionbox*{F measure}{
             \includegraphics[width=300pt]{graphics/active_mnist/f_measure_validation}
-        }
         \end{tikzfigure}

### 2018-11-29 SparseUtils/plot_delta.py

@@ -1,0 +1,19 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+if __name__=="__main__":
+    n = 1000
+
+    x = np.linspace(-2, 2, n)
+    y = np.zeros_like(x)
+
+    y[int(n / 2)] = 1
+    fig = plt.figure()
+    ax = fig.add_subplot(111)
+    ax.axvline(color='k', linestyle='--')
+    ax.axhline(color='k', linestyle='--')
+    ax.plot(x, y, linewidth=5)
+    plt.tick_params(axis='x', which='both', bottom=False, top=False, labelbottom=False)
+    plt.tick_params(axis='y', which='both', left=False, right=False, labelleft=False)
+    plt.tight_layout()
+    plt.savefig("delta.pdf", format='pdf', dpi='figure')

### 2018-11-29 nips_workshop_2018/camera_ready/BayesianLISTA.tex
minor

@@
   \centering
-  \subfloat[Synthetic for different $L$]{\includegraphics[width=0.25\textwidth]{graphics/synthetic_number_of_layers/nmse_validation}
+  \subfloat[Synthetic for different $L$]{\includegraphics[width=0.28\textwidth]{graphics/synthetic_number_of_layers/nmse_validation}
   \label{fig:nmse_n_layers_synthetic}}
   \hfil
-  \subfloat[Synthetic for different $K$]{\includegraphics[width=0.25\textwidth]{graphics/synthetic_undersampling/nmse_validation}
+  \subfloat[Synthetic for different $K$]{\includegraphics[width=0.28\textwidth]{graphics/synthetic_undersampling/nmse_validation}
   \label{fig:nmse_undersampling_synthetic}}
   \hfil
-  \subfloat[Active learning example]{\includegraphics[width=0.25\textwidth]{graphics/active_mnist/nmse_validation}
+  \subfloat[Active learning example]{\includegraphics[width=0.28\textwidth]{graphics/active_mnist/nmse_validation}
   \label{fig:active_learning_mnist}}

### 2019-06-23 bayesian_lista_src/tf/algorithms/lista/handler.py
add final presentation, minor updates to code

@@ -1,7 +1,10 @@
 import tensorflow as tf
+from tqdm import trange
 
 from tf.algorithms.handler import Handler
 from tf.algorithms.lista.lista import Lista
+
+import time
 
 
 class ListaHandler(Handler):
@@ -9,22 +12,54 @@ class ListaHandler(Handler):
         super().__init__(D, K, L, X, initial_lambda)
 
         self.model = Lista(L, D, K, X, initial_lambda)
-        self.learning_rate = learning_rate
+        self.optimizer = tf.train.GradientDescentOptimizer(learning_rate=learning_rate)
+
+        self.train_loss = tf.contrib.eager.metrics.Mean()
+        self.validation_loss = tf.contrib.eager.metrics.Mean()
+        self.train_f_measure = tf.contrib.eager.metrics.Mean()
 
     def train_iteration(self, beta_train, y_train):
         with tf.GradientTape() as t:
-            current_loss = ListaHandler.loss(self.model(y_train), beta_train)
-        dW, dS, dLambda = t.gradient(current_loss, [self.model.W, self.model.S, self.model.thr_lambda])
-        self.model.W.assign_sub(self.learning_rate * dW)
-        self.model.S.assign_sub(self.learning_rate * dS)
-        self.model.thr_lambda.assign_sub(self.learning_rate * dLambda)
-        return current_loss.numpy(), Handler.f_measure(beta_train, self.model(y_train))
+            predictions = self.model(y_train)
+            current_loss = tf.losses.mean_squared_error(labels=beta_train, predictions=predictions)
+        grads = t.gradient(current_loss, self.model.trainable_variables)
+        self.optimizer.apply_gradients(zip(grads, self.model.trainable_variables))
 
-    def train(self, num_epochs, beta_train, y_train):
-        Ws, Ss, thr_lambdas = [], [], []
-        epochs = range(num_epochs)
-        for epoch in epochs:
-             self.train_iteration(beta_train, y_train)
+        self.train_loss(current_loss)
+        self.train_f_measure(tf.contrib.metrics.f1_score(labels=beta_train, predictions=predictions))
+
+        #return current_loss.numpy(), Handler.f_measure(beta_train, self.model(y_train))
+
+    def train(self, n_epochs, train_data):
+        train_summary_writer = tf.contrib.summary.create_file_writer("logs")
+
+        t = trange(n_epochs, desc='ML')
+        for epoch in t:
+            start_time = time.process_time()
[…]

### 2019-06-23 bayesian_lista_src/tf/algorithms/lista/lista.py

@@ -17,6 +17,7 @@ class Lista:
         self.S = tf.Variable(initial_value=S_init, name='S')
 
         self.thr_lambda = tf.Variable(initial_value=self.initial_lambda, name='thr_lambda')
+        self.trainable_variables = [self.W, self.S, self.thr_lambda]
 
     def __call__(self, y):
         b = tf.matmul(y, tf.transpose(self.W))

### 2019-06-23 bayesian_lista_src/tf/algorithms/lista/run.py

@@ -25,26 +25,8 @@ beta_valid, y_valid, _ = data_generator.new_sample(n_validation)
 train_data = tf.data.Dataset.from_tensor_slices((beta_train, y_train)).shuffle(10).batch(batch_size=batch_size)
 
 loss_hist, valid_loss_hist, f_meas_hist, valid_f_meas_hist, times = [], [], [], [], []
-t = trange(n_epochs, desc='ML')
-for i in t:
-    start_time = time.process_time()
-    for i, (beta_batch, y_batch) in enumerate(train_data):
-        handler.train_iteration(beta_train=beta_batch, y_train=y_batch)
-    elapsed_time = time.process_time() - start_time
 
-    train_pred = handler.model(y_train.astype(np.float32))
-    valid_pred = handler.model(y_valid.astype(np.float32))
-    loss = ListaHandler.loss(train_pred, beta_train)
-    f_meas = ListaHandler.f_measure(beta_train, train_pred)
-    valid_loss = ListaHandler.loss(valid_pred, beta_valid)
-    valid_f_meas = ListaHandler.f_measure(beta_valid, valid_pred)
-    t.set_description(
-        f'ML (loss={loss.numpy():.3f}, valid_loss={valid_loss.numpy():.3f} f-meas:{f_meas:.3f} valid_f-meas:{valid_f_meas:.3f})')
-    loss_hist.append(loss.numpy())
-    valid_loss_hist.append(valid_loss.numpy())
-    f_meas_hist.append(f_meas)
-    valid_f_meas_hist.append(valid_f_meas)
-    times.append(elapsed_time)
+handler.train(n_epochs, train_data)
 
 plt.plot(loss_hist)
 plt.plot(valid_loss_hist)
